### 2013-09-29 tex/scam/rebuttal_nips2013.txt
first init

We thank the reviewers for their thoughtful reviews. We would like to point out that this paper is not solely theoretical; the scalable practical optimization algorithm we develop is also a major contribution.

Reviewer 1:
(1) Thanks for pointing out these references. We are aware of these prior works and thought that a comprehensive comparison is more appropriate for a journal version.

(2) Yes, with the L_inf bound on f^*, the alpha decays with s. We did not investigate this further because this paper studies how n can scale with p as both go to infinity; we think of s as a bounded quantity. The key contribution and the most interesting aspect of the theorem is that the ambient dimension can scale exponentially in n; the actual dimension s is usually very small in practice. This is definitely a point we would clarify in the future revisions.

(3) E[f(X)|x_k] is a notational short-hand; it is not "an elementary mistake in math." Lemma 6.1 does not need or have the product distribution assumption; Proposition 6.1 uses it. Theorem 2.1 does assume that the distribution has a density; that was an oversight on our part. Please do let us know if there are other mistakes that you found.

Reviewer 5:
(1) The present version is not wrong. Uniqueness is obvious from the fact that the objective in Lemma 6.1 is a sum of squares and is therefore strongly convex in f_k(x_k) for every f_k(x_k). Do you have a counterexample in mind?

(2) The claim of Theorem 4.3 is not nonsense; it requires that s does not tend to infinity but it is otherwise correct. If we assume that the covariates are independent, then any affine function have support identifiability (sparsistency) even if the ambient dimension p ~ exp(n^c) for c < 1; no additional separation assumptions are needed.

(3) Theorem 2.1 is only one of the main contributions of the paper.

(4) The result announced in the introduction is, as stated in the introduction, proved in the two references [5][6].

Reviewer 7:
(1) Thanks for pointing out the two references. We would definitely add these to a longer version of this paper.

### 2013-09-29 tex/derivations.tex
first init

\documentclass{article}
\usepackage{minx_math}
\usepackage{framed, mathtools, epstopdf,subfigure}

\begin{document}

\section{No False Negatives}

Let us intuitively describe the logic.

Let $n$ be some large number and let $\hat{f}_S$ be the optimal solution with a false negative.

Let $f^*_S$ be the population optimal solution.

\begin{align*}
\hat{R}( \hat{f}_S ) &\geq R(\hat{f}_S) - gap_n \\
	&\geq R(f^*_S miss) - gap_n \\
	&\geq R(f^*_S) + gap - gap_n \\
	&\geq \hat{R}(f^*_S) + gap - 2 gap_n \\
	&\geq \hat{R}(f^*_S) + pen(f^*_S) - pen(f^*_S) + pen(\hat{f}_S) - pen(\hat{f}_S) + gap - 2 gap_n
\end{align*}

We have then that
\[
\hat{R}(\hat{f}_S) + pen(\hat{f}_S) \geq \hat{R}(f^*_S) + pen(f^*_S) + (pen(\hat{f}_S) - pen(f^*_S) + gap - 2 gap_n)
\]

Because $pen$ and $gap_n$ decreases with $n$ and $gap$ does not, for large enough $n$, we would reach a contradiction.

The only goal then is to figure out $gap_n$.

A more precisely statement is, with probability at least $1-\delta$, 
\[
\sup_{f_1, ..., f_s} | \hat{R}(f_S) - R(f_S) | \leq gap_n
\]

\subsection{Covering Number}

\section{Functions Which Are Not Additively Faithful}

\textbf{Example 1:}
\[
f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
\]
Note that for all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$.
An additive model would set $f_1 = 0$ and $f_2 = 0$.

\begin{figure}[htp]
\subfigure[Example 1]{\includegraphics[scale=0.5]{../code/figs/sine_wave_funct.eps}}
\subfigure[Example 2]{\includegraphics[scale=0.4]{../code/figs/rising_slope_funct.eps}}
\end{figure}

\textbf{Example 2:}
\[
f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1], x_2 \in [0,1]
\]
Note that for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive model.

This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.

\section{Convex Functions are Additively Faithful}

Let $\mu$ be a probability measure on $C=[0,1]^s$, $f(x)$ be a multivariate function on $C$. We say that $f$ depends on coordinate $i$ if there exist $x'_i \neq x_i$ such that $f(x'_i, x_{-i})$ and $f(x_i, x_{-i})$ are different functions of $x_{-i}$. (on some measurable set)

\begin{theorem}
Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

Suppose $f$ depends on all coordinates. Let $f_1,...,f_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$

 Then $f_1,...,f_n$ are non-constant functions.
 \end{theorem}

 \begin{lemma}
\label{lem:int_reduction}
Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.

Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$ \\

Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
\end{lemma}

 \begin{proof}

Let $f^*_1,...,f^*_s$ be the minimizers as defined. It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]

Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k}  \\
p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

 \end{proof}

 \begin{proposition}
Let $p$ be a probability distribution on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose $p$ is a product distribution.

Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$.

The following are equivalent:
\begin{packed_enum}
\item $f$ does not depends on coordinate $k$
\item For all $x_k$, $\E[ f(X) | x_k] = 0$.
\end{packed_enum}
\end{proposition}

\begin{proof}

The first condition trivially implies the second because $\E f(X) = 0$.\\

Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$. \\

By the assumption that $p$ is a product measure, we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

For every $\mathbf{x}_{-k}$, we define the derivative
\[
g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
\]
$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.\\

We now describe two facts about $g$.

Fact 1. By exchanging limit with the integral, we reason that 
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
\]

Fact 2. Because $f$ is convex, $g(\mathbf{x}_{-k})$ is a component of the subgradient $\partial_{\mathbf{x}} f(0, \mathbf{x}_{-k})$. (the subgradient coincides with the gradient by assumption that $f$ is twice differentiable)

Therefore, using the first order characterization of a convex function, we have
\begin{align*}
f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
\end{align*}

Because, for all $x_k, \mathbf{x}_{-k}$, 
\[
f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
\]
and
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
\]
we conclude that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.

The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.

By proposition from Horn and Johnson [TODO ref], such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. \\

Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function. It follows therefore that $g = 0$ because it integrates to 0. \\

So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.

\end{proof}

\section{Technical Details}

\subsection{Norm of Subgaussian Random Vector}

Let $V = [V_1,...,V_s] \in \R^s$ be a subgaussian random vector, each with subgaussian norm at most $\sigma$.

Then, with probability at least $1-\delta$, $\| V \|_\infty$ is at most $\sigma \sqrt{ \log \frac{s}{\delta}}$

Since $\|V\|_2 \leq \sqrt{s} \| V\|_\infty$, with probability at least $1-\delta$, $\| V \|_2 \leq \sigma \sqrt{\frac{s}{c} \log \frac{sC}{\delta}}$.

\subsection{$l_\infty$ norm bound on $\hat{r}$}

\begin{align*}
\hat{r}_i &= Y_i - \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
	&= f^*(X_S^{(i)}) + \epsilon_i - \bar{f^*} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
	&=  f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
\end{align*}

Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.\\

\textbf{Epsilon Bound}
Suppose $\epsilon_i$ is subgaussian with subgaussian norm $\sigma$. For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$. Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.

By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.\\

Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.\\

\textbf{Bounded Function Bound}

Suppose $|f^*(x)| \leq B$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.

Then $|\bar{f^*}| \leq B$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq (s+2) B$ therefore.

\textbf{Lipschitz Function Bound}
Suppose $f^*$ and $\hat{f}_k$ are all Lipschitz with Lipschitz constant at most $L_{\max}$. The composite function $\sum_{k \in S} \hat{f}_k$ is also $L_{\max}$-Lipschitz.

Let $u = \bar{ f^* }$. $X_S \mapsto f^*(X_S) - \bar{f^*}$ is still $L_{\max}$-Lipschitz of course.

Define $h(X^{(i)}_S) \coloneqq f^*(X^{(i)}_S) -u - \sum_{k \in S} \hat{f}_k(X^{(i)}_k)$ as a short-hand. $h$ is therefore Lipschitz with Lipschitz constant at least $2L_{\max}$.

Because $\sum_i h(X^{(i)}_S) = 0$, it must be that for some $i$, $h(X^{(i)}_S) \geq 0$ and for some $i$, $h(X^{(i)}_S) \leq 0$.

\[
\trm{Therefore,}\qquad \max_i |h(X^{(i)}_S)|\leq \max_{i,j} | h(X^{(i)}_S) - h(X^{(j)}_S)|
\]

\begin{align*}
| h(X^{(i)}_S) - h(X^{(j)}_S)|& \leq 2L_{\max} \| X^{(i)}_S - X^{(j)}_S \| \\
&\leq 2L_{\max} (\|X^{(i)}_S\| + \|X^{(j)}_S\|) \\
&\leq 4L_{\max} \max_i \|X^{(i)}_S\|
\end{align*}

Therefore, $\max_i | h(X^{(i)}_S)| \leq 4 L_{\max} \max_i \|X^{(i)}_S\|$.

Using the concentration inequality on norms of subgaussian random vectors and a union bound, we get that, with probability at least $1-\delta$, $\max_i \|X^{(i)}_S\| \leq \sqrt{ \frac{s}{c} \log \frac{nsC}{\delta} }$ (assuming that each coordinate of $X_S$ has subgaussian norm $1$.\\

Taking union bound across deviation for $\epsilon$ and the Lipschitz function term, we have that, with probability at least $1 - \delta$,
\[
\| \hat{r} \|_\infty \leq \sigma L_{\max} \sqrt{ \frac{s}{c} ( \log sn + \log \frac{C}{\delta})}
\]

\subsection{Sampling Without Replacement}

\begin{lemma} (Serfling) 
Let $x_1,..., x_N$ be a finite list, $\bar{x} = \mu$. Let $X_1,...,X_n$ be sampled from $x$ without replacement.

Let $b = \max_i x_i$ and $a = \min_i x_i$. Let $r_n = 1- \frac{n-1}{N}$. Let $S_n = \sum_i X_i$.
Then we have that
\[
P( S_n - n \mu \geq n \epsilon) \leq \exp( - 2 n \epsilon^2 \frac{1}{r_n (b-a)^2})
\]
\end{lemma}

\begin{corollary}
Suppose $\mu = 0$. 
\[
P( \frac{1}{N} S_n \geq \epsilon) \leq \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
\]

And, by union bound, we have that
\[
P( | \frac{1}{N} S_n| \geq \epsilon) \leq 2 \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
\]

\end{corollary}

A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.s

\begin{proof}
\[
P( \frac{1}{N} S_n \geq \epsilon) = P( S_n \geq \frac{N}{n} n \epsilon) \leq \exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} ) 
\]

We note that $r_n \leq 1$ always, and $n \leq N$ always. 
\[
\exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} )  \leq \exp( - 2 N \epsilon^2 \frac{1}{(b-a)^2})
\]
This completes the proof.

\end{proof}

\subsection{Bounding $\frac{1}{n} \hat{r}^\tran \max( X, X_{(j)} \mathbf{1})$}
\[
\frac{1}{n} \hat{r}^\tran \max(X, X_{(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_i, X_{(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) + \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

Where $A = \{ i : ord(i) \geq j\}$

We will bound both terms.\\

\textbf{Term 1.}
\[
\trm{Want to bound} \qquad F(X_1,...,X_n) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) 
\]

First, we assume that $X_i$ is bounded in the range $[-b,b]$.

We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate. \\

The order of coordinate $i$ in $X$ and $X'$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X)$ to $F(X')$. Therefore,

$$ | F(X_1, ..., X_n) - F(X'_1, ..., X_n) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$

By McDiarmid's inequality therefore, 
\[
P( | F(X) - \E F(X) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
\]

By symmetry and the fact that $\hat{r}$ is centered, $\E F(X) = 0$.

We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$. \\

\textbf{Term 2:}

\[
\trm{Want to bound}   \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

$A$ is a random set and is probabilistically independent of $\hat{r}$.  $\mathbf{1}_A^\tran \hat{r}_A$ is the sum of a sample of $\hat{r}$ without replacement. Therefore, according to Serfling's theorem, with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.

Since $|X_{(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.\\

\textbf{All Together}

Taking union bound across $p$ and $n$, we have that with probability at least $1-\delta$,

\[
| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
\]

Taking union bound and substituting in the probabilistic bound on $\|\hat{r}\|_\infty$, we get that with probability at least $1-\delta$,

$| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
\[
\sigma L_{\max} b \sqrt{ \frac{1}{c} \frac{s}{n} ( \log (spn) + \log \frac{C}{\delta})^2}
\]

\newpage

\textbf{DEPRECATED!}\\ %===%

\section{Additive Model}
\subsection{Proof Sketch}

FACT: A bounded convex function is Lipschitz. \\

FACT: If $f_k(x_k)$ are $L$-Lipschitz, then $\sum_k f_k(x_k)$ is also $L$-Lipschitz.

\[
| \sum_k f_k(x_k) - \sum_k f_k(x'_k) |^2 \leq \sum_k |f_k(x_k) - f_k(x'_k)|^2 \leq \sum_k L^2| x_k - x'_k |^2 \leq L^2 \| x - x' \|_2^2
\]

FACT: if $X$ is sub-gaussian random vector, then $g(X)$ is also sub-gaussian if $g$ is Lipschitz. This is true by McDiarmid's inequality.\\

ASSUMPTION: $X_k$ for $k=1,...,p$ are independent. We can use weaker assumptions. \\

Let $\hat{f}_k$ be the optimal solution to the optimization
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \hat{f}_s(X_s) \|_2^2 + \lambda\sum_{s=1}^p \| \partial \hat{f}_s(X_s)\|_2 \qquad \hat{f}_s \trm{ convex and } \sum_i \hat{f}_s (x_{is}) = 0 .
\]

ASSUMPTION: $Y$ has mean zero, $\hat{f}_k$ for all $k$ has mean zero, and $\hat{f}_k$ is Lipschitz with an universal upper bound on the Lipschitz constant.\\

CLAIM: If we set $\lambda = O \sqrt{\frac{\log (np) }{ n }}$, then $\hat{f}_k$ for an irrelevant $k$ is zero.

We fix an irrelevant dimension $k$, and define the residue $\hat{y} = y - \sum_{k' \neq k} \hat{f}_{k'}(X_{k'})$.

Using the reformulation, we can re-write the optimization, in term of just $f_k$, as the following.

\[
\min_{d, c}  \frac{1}{2n} \| \hat{y} - \Delta d - c \|_2^2 + \lambda \sum_{i=1}^n d_i + \lambda|d_0|  \qquad \trm{s.t.} \forall i>0, \, d_i \geq 0
\]
Where $d$ is a $n$-dim vector, $c$ scalar is the centering variable, and $\Delta$ is the $n \times n$ matrix of inter-sample distances.\\

Taking the subgradient with respect to $d$, we have that
\[
\frac{1}{n} (-\hat{y}^\tran \Delta + d^\tran \Delta^\tran \Delta ) + \lambda \mathbf{u} - \mu = 0
\]

where $\mathbf{u}$ is a $n$-dim vector whose first coordinate is $\partial | d_0 |$ and whose all other coordinates are $1$. $\mu$ is a $n$-dim vector whose first coordinate is $0$ and all other coordinates are the Lagrangian multipliers.\\

We now want to verify that if we substitute $d = 0$ into the subgradient, the subgradient equals 0. If $d=0$, then we can substitute $\mathbf{u} = \mathbf{1}$.

All we need to verify then is that $\lambda \mathbf{1} \geq \frac{1}{n} \hat{y}^\tran \Delta$.\\

Note that $\hat{y}$ is a sub-gaussian random vector with mean zero. Because $\hat{y}$ and $\Delta$ are independent, $\hat{y}^\tran \Delta$ is also a sub-gaussian mean-zero random vector. Note also that $\Delta$ is entirely positive.\\

The empirical mean $ \frac{1}{n} \hat{y}^\tran \Delta$ is then on the order of $\sqrt{ \frac{1}{n}}$ with high probability.

We need to take union bound across the $n$-dimensions of $\hat{y}^\tran \Delta$ and across the $p$ dimensions.

Therefore, setting $\lambda = O \sqrt{\frac{\log (np)}{n}}$ suffices.

\subsection{Reformulation}

The objective is, again
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \hat{f}_s(X_s) \|_2^2 + \sum_{s=1}^p \| \partial \hat{f}_s(X_s)\|_2 \qquad \hat{f}_s \trm{ convex and } \sum_i \hat{f}_s (x_{is}) = 0
\]

Let us try to simplify this form. We can replace the identifiability constraint with $\hat{f}_s( 0 ) = 0$ or $\hat{f}_s(-1) = 0$. Let's go with the latter formulation and define $x_{s(0)}$ as $-1$.

Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large.\\

Then  $\hat{f}_s(x_{s(1)}) = \hat{f}_s(x_{s(0)}) + \hat{\beta}_{s(0)} (x_{s(1)}-x_{s(0)} )$

and $\hat{f}_s(x_{s(2)}) = \hat{\beta}_{s(0)} (x_{s(1)}-x_{s(0)} ) + \hat{\beta}_{s(1)} (x_{s(2)}-x_{s(1)} )$\\

Some additional transformation. Let's define $\hat{d}_{s(0)}$ as the gradient increments. $\hat{d}_{s(0)} = \hat{\beta}_{s(0)}$, and $\hat{d}_{s(1)} = \hat{\beta}_{s(1)} - \hat{\beta}_{s(0)}$.\\

Therefore, $\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.

\[
\hat{f}_s(x_{s(1)}) = \hat{f}_s(x_{s(0)}) + \hat{d}_{s(0)} ( x_{s(1)} - x_{s(0)})
\]

\begin{align*}
\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s(1)} ( x_{s(2)} - x_{s(1)}) \\
 &= \hat{d}_{s(0)} ( x_{s(1)} - x_{s(0)}) + (\hat{d}_{s(0)}+\hat{d}_{s(1)}) (x_{s(2)} - x_{s(1)}) \\
 &= \hat{d}_{s(0)} (x_{s(2)}-x_{s(0)} ) + \hat{d}_{s(1)} (x_{s(2)}-x_{s(1)} )
\end{align*}

\[
\hat{f}_s(x_{s(i)}) = \hat{d}_{s(0)} ( x_{s(i)} - x_{s(0)}) + \hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
\]

Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. With this definition, we can re-write

\[
\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si})
\]

With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 0$.\\

\textbf{Notation:} We will also define $\Delta_s$ as a $(n \times n)$ matrix whose $i,j$-th entry is $\Delta(j, x_{si})$.

With this short-hand, we can write $\hat{f}_s(x_s) = \Delta_s\hat{d}_s$.

\subsection{Consistency with Short-hand}

We can now attempt the consistency proof with our short-hand notation.

First, what is the objective? $\| \partial \hat{f}_s(X_s) \|_\infty$ becomes $\| \hat{d}_s \|_1$.

The objective is therefore
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \Delta_s \hat{d}_s \|_2^2 + \sum_{s=1}^p \|\hat{d}_s \|_1 .
\]

Taking the same form as before, we have
\[
\frac{1}{2n} \left\{ 
  \| \sum_s \Delta_s ( \hat{d}_s - d^*_s) \|_2^2 +
\sum_s \langle \Delta_s ( \hat{d}_s - d^*_s) , \epsilon \rangle \right\} \leq
\lambda \sum_s \|d^*_s \|_1 - \lambda \sum_s \|\hat{d}_s \|_1
\]

The cross term can be bounded.
\begin{align*}
\frac{1}{2n} |\sum_s \langle \Delta_s ( \hat{d}_s - d^*_s), \epsilon \rangle| &\leq  \frac{1}{2} \sum_s \langle \hat{d}_s - d^*_s, \frac{1}{n}\Delta_s^\tran \epsilon \rangle \\
&\leq \frac{1}{2} \sum_s \| \hat{d}_s - d_s^* \|_1 \| \frac{1}{n}\Delta_s^\tran \epsilon \|_\infty \\
&\leq \frac{1}{2} \lambda \sum_s \| \hat{d}_s - d_s^* \|_1
\end{align*}

Continuing, we have
\[
\frac{1}{2n}\| \sum_s \Delta_s ( \hat{d}_s - d^*_s) \|_2^2 + \frac{\lambda}{2} \sum_{s \in S^c} \| \hat{d}_s \|_1 \leq \frac{3\lambda}{2} \sum_{s \in S} \| \hat{d}_s - d^*_s \|_1  
\]

Inside the loss function, we have $\Delta v$ where $\Delta$ is a $n \times n \times p$ Tensor and $v = \hat{d} - d^*$ is a $p \times n$ matrix.

The tensor multiplication can be re-written 
\[
\sum_{s,i} \Delta_{si} v_{si} = \tilde{\Delta} \tilde{v} \qquad \trm{where $\tilde{\Delta}$ is $n \times np$, $\tilde{v}$ is $np$-vector.}
\]

\subsection{Consistency}

First we have to establish framework and notation. The optimization can be written in many different ways, with or without constraint. 
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \hat{f}_s(X_s) \|_2^2 + \sum_{s=1}^p \| \partial \hat{f}_s(X_s)\|_2 \qquad \hat{f}_s \trm{ convex}
\]
$X \in \R^{n\times p}$ and $X_s \in \R^n$ where $s = 1,...,p$. $\hat{f}_s(X_s) = [ \hat{f}_s(X_{is}) ]_i$ is also a $n$-dim vector.

\textbf{Step 1:}\\

Transforming the objective. We claim that each $\hat{f}_s$ is associated with pairs of real numbers $\{ \hat{\alpha}_{s k}, \hat{\beta}_{s k} \}_k$ such that $\hat{f}_s(X_{ks}) = \hat{\alpha}_{s k} + \hat{\beta}_{s k} X_{ks}$.

The alphas and betas must satisfy $\hat{\alpha}_{s k'}, \hat{\beta}_{s k'} = \argmax_k \hat{\alpha}_{s k} + \hat{\beta}_{s k} X_{k' s}$.\\

Our starting point will be the same as before. 
\begin{align*}
& Y = \sum_{s=1}^p f^*_s(X_s) + \epsilon \\
& \frac{1}{2n} \| Y - \sum_{s=1}^p \hat{f}_s(X_s) \|_2^2 + \sum_{s=1}^p \| \partial \hat{f}_s(X_s)\|_{2,1} \geq \frac{1}{2n} \| Y - \sum_{s=1}^p f^*_s(X_s) \|_2^2 + \sum_{s=1}^p \| \partial f^*_s(X_s)\|_2
\end{align*}

\textbf{Note to self:} $f^*_s$'s are not unique. Will this be a problem?\\

We can do algebra and get the following conclusion.

\[
\frac{1}{2n} \left\{ \| \sum_s f^*_s(X_s) - \sum_s \hat{f}_s(X_s) \|_2^2 + \sum_s \langle f^*_s(X_s) - \hat{f}_s(X_s), \epsilon \rangle \right\} \leq \lambda \sum_s \| \partial f^*_s(X_s)\|_2 - \lambda  \sum_s \| \partial \hat{f}_s(X_s)\|_2 
\]

\textbf{Cross-term.} We fix $s$. 
\begin{align*}
& \langle f^*_s(x_s) - \hat{f}_s(x_s), \epsilon \rangle \\
=& \sum_{k=1}^n [ \alpha^*_{sk} + \beta^*_{sk} x_{ks} - \hat{\alpha}_{sk} - \hat{\beta}_{sk} x_{ks} ] \epsilon_k \\
=& \sum_{k=1}^n [\alpha^*_{sk} - \hat{\alpha}_{sk}] \epsilon_k + [\beta^*_{sk} - \hat{\beta}_{sk}] \epsilon_k x_{ks} \\
\leq & \| \alpha^*_s - \hat{\alpha}_s \|_2 \| \epsilon \|_2 + \| \beta^*_s - \hat{\beta}_s \|_2 \| x_s \epsilon \|_2 \quad \trm{ $x_s \epsilon$ is a $n$-dim vector}
\end{align*}

It follows that $\| \epsilon \|_2$ and $\| x_s \epsilon \|_2$ are both on the order of $O(\sqrt{n})$.\\

Here lies the difficulty. In vanilla Lasso, there is only ``one'' parameter vector, $\beta$. Therefore, the inner product is easy to bound:

\begin{align*}
\frac{1}{n} \langle X \Delta, \epsilon \rangle = \langle \Delta, \frac{1}{n}X^\tran \epsilon \rangle
\end{align*}

And $\frac{1}{ n} X^\tran \epsilon$ is the empirical average of samples from a mean-zero distribution.

In new Lasso, the problem is that there are ``as many'' parameter vectors as there are samples. Let $i$ index a sample and let $s$ index a dimension.

\begin{align*}
& \frac{1}{n} \sum_i X_i^\tran \Delta_i \epsilon_i \\
=& \frac{1}{n} \sum_i \sum_s X_{is} \Delta_{is} \epsilon_i \\
=& \frac{1}{n} \sum_s \sum_i \Delta_{is} ( X_{is} \epsilon_i )
\end{align*}

The problem now is that we are forced to take the norm of $( \Delta_{is} X_{is} )_i$, which is of too large of an order.

\textbf{Continuing.}

First, we have to formally define $\| \partial f_s^*(X_s) \|_2$, which we define as $\| \alpha^*_s \|_2 + \| \beta^*_s\|_2$.

Therefore, by setting $\lambda$ appropriately, the derivation becomes:

\begin{align*}
 \frac{1}{2n} \| \sum_s f^*_s(X_s) - \sum_s \hat{f}_s(X_s) \|_2^2 - \frac{\lambda}{2} \| f^* - \hat{f} \|_{2,1}  &\leq \lambda \|f^*\|_{2,1} - \lambda  \| \hat{f} \|_{2,1}  \quad \trm{note $\|f^* \|_{2,1} \equiv \sum_s \| f^*_s \|_2$.}\\
\frac{1}{2n} \| \sum_s f^*_s(X_s) - \sum_s \hat{f}_s(X_s) \|_2^2 &\leq \frac{3\lambda}{2} \| f^* - \hat{f}_S \|_{2,1} - \frac{\lambda}{2} \| \hat{f}_{S^c} \|_{2,1}
\end{align*}

\section{Simultaneous Update for $h$ and $S$}

\subsection{Stopping Criteria}

If we can condense the updates, then it is possible to have a sensible stopping criteria for ADMM.

The stopping criteria check the fulfillment of the stationarity condition and the primal feasibility condition.

\subsection{The Derivations}

The matrix of the form $\sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) (\mathbf{e}_j - \mathbf{e}_i)^\tran$ has an explicit form:

It is $2n -2$ on the diagonal and $-2$ everywhere else.\\

We do this for the vanilla implementation--no quadratic term, no additive asssumption etc.

We must solve the following linear equation:
\begin{align*}
( \frac{1}{\mu} \mathbf{I} + 2L ) \mathbf{h} &= \left( \frac{1}{\mu} \mathbf{y} + \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) ((x_j - x_i)^\tran B_i + S_{ij} - \frac{1}{\mu} W_{ji}) \right) \\
S_{ji} &= h_j - h_i - B_i^\tran (x_j - x_i) + \frac{1}{\mu} W_{ji}
\end{align*}

$L$ is a matrix of the form $D - A$ where $A$ is the all ones matrix and $D$ is the degree matrix of $A$. Therefore, $L$ is all negative ones everywhere except for the diagonal, where it is $n-1$.

\textbf{Step 1.} We separate the variables.
\begin{align*}
( \frac{1}{\mu} \mathbf{I} + 2L ) \mathbf{h} - \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) S_{ij} &= \left( \frac{1}{\mu} \mathbf{y} + \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) ((x_j - x_i)^\tran B_i - \frac{1}{\mu} W_{ji}) \right) \\
S_{ji} - h_j + h_i &= - B_i^\tran (x_j - x_i) + \frac{1}{\mu} W_{ji}
\end{align*}

\textbf{Step 2.} We describe the matrix form.
\[
\boxed{\trm{Big Matrix}} \left[\begin{array}{c} \mathbf{h} \\ \mathbf{S} \end{array}\right] = \boxed{\trm{Big Vector}}
\]

The Big Matrix is $(n+n^2) \times (n+n^2)$ and is block structured:
\[
\left[\begin{array}{cc} 
\mu^{-1} \mathbf{I} + 2L & \trm{Operator h-S} \\
\trm{Operator S-h} & \mathbf{I}_{|S|}
\end{array}\right]
\]

Operator h-S is $n \times n^2$ and represented by $-\sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) S_{ji}$, which is the output vector when we multiply by $S$

Operator S-h is $n^2 \times n$ and represented by $ - h_j + h_i$, which is the $(j,i)$-th entry of the output $n^2$-vector when we multiply by $h$.

We must also describe what the \fbox{Big Vector} is. Its form can be directly read from the equation array in step 1.

\textbf{Step 3.} We apply schur complement to invert.

Schur complement, abstractly written, is the following identity:
\[
\left[ \begin{array}{cc} A & B \\ C & D \end{array} \right]^{-1} = 
\left[ \begin{array}{cc} I_p & 0 \\ -D^{-1} C & I_q \end{array} \right]
\left[ \begin{array}{cc} (A - BD^{-1}C)^{-1} & 0 \\ 0 & D^{-1} \end{array} \right]
\left[ \begin{array}{cc} I_p & - B D^{-1} \\ 0 & I_q \end{array} \right]
\]

In our situation, $D$ is identity.

\textbf{Step 4.} We perform step 1 of the Schur complement

We now apply a $n+n^2 \times n+n^2$ matrix onto a $n + n^2$-vector and describe the resulting vector. We do not want to store a large matrix in memory.

Let $\left[ \begin{array}{c} \mathbf{h}' \\ \mathbf{S}' \end{array} \right]$ be the input vector.

The result is
\[
\left[ \begin{array}{c}
\mathbf{h}' + \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) \mathbf{S}'_{ji} \\
\mathbf{S}'
\end{array}\right]
\]

\textbf{Step 5.} We perform step 2 of the Schur complement

We must first compute the composition Operator h-S $\circ$ Operator S-h.

Let $\mathbf{h}'$ be a vector, then after Operator S-h, we have a matrix whose $(j,i)$ entry is $ - \mathbf{h}'_j + \mathbf{h}'_i$.

After an application of Operator h-S, we now have a vector of the form $- \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) ( - \mathbf{h}'_j + \mathbf{h}'_i)$.

That can be re-written as: $\sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) (\mathbf{e}_j - \mathbf{e}_i)^\tran \mathbf{h}'$.

Hence, the combined operator is $2L$.

Because $A$ is $\mu^{-1} \mathbf{I} + L$, the second step is just a multiplication of the first part by $\mu$ and an identity operation on the second part.

Thus, continuing our calculation from the previous step, the vector $\mathbf{h}'$ and $\mathbf{S}'$ have now become:

\[
\left[ \begin{array}{c}
\mu \mathbf{h}' + \mu \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) \mathbf{S}'_{ji} \\
\mathbf{S}'
\end{array}\right]
\]

\textbf{Step 6.} We perform step 3 of the Schur complement

We must now apply negative Operator S-h onto $\mu \mathbf{h}' + \mu \sum_{ij} (\mathbf{e}_j - \mathbf{e}_i) \mathbf{S}'_{ji} $

Applying Operator S-h onto $\mathbf{h}'$ results in $[- \mathbf{h}'_s + \mathbf{h}'_t]_{s,t}$

The second part is harder. A naive application gives $[\sum_{ij} (\mathbf{e}_j(s) - \mathbf{e}_i(s) - (\mathbf{e}_j(t) - \mathbf{e}_i(t))) \mathbf{S}'_{ji} ]_{s,t}$\\

We may distribute the $S'_{ji}$ into the differences and get:
\[
\sum_i S'_{si} - \sum_j S'_{js} - \sum_i S'_{ti} + \sum_j S'_{jt}
\]
To check for correctness, we remember that the constraints are, in order, $j=s$, $i=s$, $j=t$, $i=t$.

\textbf{Implementation Note:} We have: rowsum(s)-colsum(s)-rowsum(t)+colsum(t). For efficient implementation, we first compute all row and column sums of $S'$. We then construct a matrix whose $(s,t)$-th entry is $rowsum(s) - rowsum(t)$.

\section{ADMM with Gap and Quadratic Term}

Let $B$ be a $p\times n$ matrix, and let $D$ also be a $p\times n$ matrix. $C$ is then a $p\times 2n$ matrix; let $C = [C_B, C_D]$.

\begin{align*}
\min_{\mathbf{h}, \mathbf{B}, \mathbf{C},\mathbf{S},\mathbf{D}}
& \frac{1}{2n}\sum_{i=1}^n(y_i - h_i)^2 + \lambda \|C\|_{\infty,1} + \gamma \frac{1}{n} \sum_{ij} S_{ji} \\
\trm{s.t.} & C_B = B, C_D = D, S_{ji} \geq 0 \\
	& S_{ji} = h_j - h_i - B_i^\tran(X^j - X^i) - \sum_{k=1}^p D_{ik} (X^j_k - X^i_k)^2
\end{align*}

The corresponding ADMM objective is similar to before:
\begin{align*}
\min_{\mathbf{h},\mathbf{B},\mathbf{C},\mathbf{D},\mathbf{S},\mathbf{W},\mathbf{M}} &
\frac{1}{2}\sum_{i=1}^n (y_i - h_i)^2 + \lambda \|C\|_{\infty,1} + \gamma \sum_{ij}S_{ji} \\
& +\sum_{ij} (W_{ji} \cdot [ h_j - h_i - B_i^\tran(X^j - X^i) - \sum_{k=1}^p \mathbf{D}_{ik} (X^j_k - X^i_k)^2 - S_{ji}]) \\
& + \frac{\mu}{2} \sum_{ij} ( h_j - h_i - B_i^\tran (X^j - X^i) -\sum_{k=1}^p \mathbf{D}_{ik} (X^j_k - X^i_k)^2-S_{ji})^2 \\
& + \trace(M^\tran (C - [B,D])) + \frac{\mu}{2} \| C - [B,D]\|^2 \trm{ s.t. } S_{ji} \geq 0
\end{align*}

I need to introduce additional columns to $C, M$, introduce $D$. 
The updates for $\mathbf{h}$ and $\mathbf{B}$ and $\mathbf{W}$ are easy. The updates for $\mathbf{C},\mathbf{W},\mathbf{M}$ are easy.\\

\subsection{Update for $\mathbf{C}$}

The original update was:
\begin{align*}
& \min_{\mathbf{C}} \lambda \|\mathbf{C}\|_{\infty,1} + \frac{\mu}{2} \| \mathbf{C} - (B - \frac{1}{\mu} M ) \|_2^2 \\
\end{align*}

$\mathbf{C}$ is thus $\mathbf{C}$ subtracts a projection of $B - \frac{1}{\mu} M$ onto $\|\cdot\|_1$ ball of radius $\frac{\lambda}{\mu}$.

The new update is 
\begin{align*}
& \min_{\mathbf{C}} \lambda \|\mathbf{C}\|_{\infty,1} + \frac{\mu}{2} \| \mathbf{C} - ([B,D] - \frac{1}{\mu} M ) \|_2^2 \\
\end{align*}

Same basic code. No change.

\begin{framed}
We take a brief digression to discuss how to solve problems of the form:
\[
\min_{z \in \R^M} \| z - x\|_2^2 + \nu \|z \|_q
\]

The subgradient optimality condition states that 
\[
x - z \in \frac{\nu}{2} \partial \| z \|_q
\]

Define $\Psi^*(y) = \sup_z \langle z, y \rangle - \Psi(z)$ as the Fenchel conjugate of $\Psi(z) = \frac{\nu}{2} \| z \|_q$.

FACT: For any Fenchel conjugate pairs $f,g$, it holds that $y \in \partial f(x)$ iff $x \in \partial g(y)$.

Therefore, we have that 
\[
z \in \partial \Psi^*(x - z) \Rightarrow x \in x-z - \partial \Psi^*(x-z)
\]

It is claimed that $\Psi^*(y) = \Xi_{B^{q'}(\nu/2)}(y)$ is the indicator function. Why is this?
Let us look at $\sup_x \langle x, y\rangle - \Psi(x)$ for different values of $y$. If $\|y\|_{q'} \leq \frac{\nu}{2}$, then $\frac{\nu}{2} \|x\|_q \geq \langle x,y\rangle$ for all $x$ because $\|y\|_{q'} = \sup_x \langle \frac{x}{\|x\|_q},y\rangle $. 
If $\|y\|_{q'} > \frac{\nu}{2}$, then there would exist an $x$ such that $\langle x, y\rangle > \frac{\nu}{2} \|x\|_q$.

FACT: $y \in w + \partial \Xi_C(w)$ for an $\infty$-indicator function $\Xi_C(w)$ of a convex set $C$ iff we have that $w = \argmin_{w' \in C} \|w' - y\|_2^2$. 
PROOF:

Suppose the primus holds. Then $(y-w)^\tran (w' - w) \leq \Xi_C(w') - \Xi_C(w)$ for all $w' \in C$, this implies that $(y-w)^\tran (w' - w) \leq 0$ for all $w' \in C$.

The optimization can be restated with the indicator function: $\min_{w'} \|w' - y \|_2^2 \trm{ s.t. } \Xi_C(w') \leq 0$. We can then form the Lagrangian.

Note: $v \in \partial \Xi_C(w)$ is equivalent to $v$ in the tangent cone of $C$ at $w$.

In any case, we establish the connection. $x-z$ is the projection of $x$ onto the $\frac{\nu}{2}$ ball of the dual norm.

\end{framed}

\subsection{Update for $\mathbf{B}$}

Recall $\mathbf{B}$ is $p\times n$. The original update. $B_i$ is column of $\mathbf{B}$
\[
\min_{B_i} \sum_{j=1}^n \frac{\mu}{2} (h_j - (h_i + B_i^\tran (X^j - X^i) + S_{ji} ) + \frac{1}{\mu}W_{ji})^2 + \frac{\mu}{2} \| B_i - (\mathbf{C}_i + \frac{1}{\mu} \mathbf{M}_i) \|_2^2
\]
\[
B_i = \left( \mathbf{I} + \sum_{j=1}^n (X^j - X^i)(X^j - X^i)^\tran \right)^{-1} 
	\left( \mathbf{C}_i + \frac{1}{\mu}\mathbf{M}_i + \sum_{j=1}^n (X^j - X^i)(h_j - h_i - S_{ji} + \frac{1}{\mu} W_{ji}) \right)
\]

The new forms should be:
\[
\min_{B_i} \sum_{j=1}^n \frac{\mu}{2} \left(h_j - (h_i + B_i^\tran (X^j - X^i) + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 + S_{ji} ) + \frac{1}{\mu}W_{ji}\right)^2 + \frac{\mu}{2} \| B_i - (\mathbf{C}_{B, i} + \frac{1}{\mu} \mathbf{M}_{B,i}) \|_2^2
\]
\[
B_i = \left( \mathbf{I} + \sum_{j=1}^n (X^j - X^i)(X^j - X^i)^\tran \right)^{-1} 
	\left( \mathbf{C}_{B,i} + \frac{1}{\mu}\mathbf{M}_{B,i} + \sum_{j=1}^n (X^j - X^i)(h_j - h_i - \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2+ S_{ji} + \frac{1}{\mu} W_{ji}) \right)
\]

\subsection{Updates for $\mathbf{h}$}

Before
\[
\min_{\mathbf{h}} \frac{1}{2} \sum_{i=1}^n (y_i - h_i)^2 + \sum_{j=1}^n \frac{\mu}{2} \left(h_j - (h_i + B_i^\tran (X^j - X^i) + S_{ji} ) + \frac{1}{\mu}W_{ji}\right)^2
\]
\begin{align*}
h = & \left( \frac{1}{\mu} \mathbf{I} + \sum_{ij} (e_j - e_i)(e_j - e_i)^\tran\right)^{-1} \\
	& \left( \frac{1}{\mu} y + \sum_{ij} (e_j - e_i)((X^j - X^i)^\tran B_i + S_{ji} - \frac{1}{\mu} W_{ji} )\right)
\end{align*}

After
\[
\min_{\mathbf{h}} \frac{1}{2} \sum_{i=1}^n (y_i - h_i)^2 + \sum_{j=1}^n \frac{\mu}{2} \left(h_j - (h_i + B_i^\tran (X^j - X^i) + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 + S_{ji} ) + \frac{1}{\mu}W_{ji}\right)^2
\]
\begin{align*}
h = & \left( \frac{1}{\mu} \mathbf{I} + \sum_{ij} (e_j - e_i)(e_j - e_i)^\tran\right)^{-1} \\
	& \left( \frac{1}{\mu} y + \sum_{ij} (e_j - e_i)((X^j - X^i)^\tran B_i + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 + S_{ji} - \frac{1}{\mu} W_{ji} )\right)
\end{align*}

Note: $\sum_{j} e_j M_{ij}$ is the $i$-th row of $M$.

\subsection{Update for $\mathbf{S}$}

Before
\[
\min_{S_{ji}} \frac{\mu}{2} \left(h_j - (h_i + B_i^\tran (X^j - X^i)  + S_{ji} ) + \frac{1}{\mu}W_{ji}\right)^2  \trm{ s.t. } S_{ji} \geq 0
\]
\[
S_{ji} = \max(h_j - (h_i + B_i^\tran (X^j - X^i)) + \frac{1}{\mu} W_{ji}, 0)
\]
After
\[
\min_{S_{ji}} \frac{\mu}{2} \left(h_j - (h_i + B_i^\tran (X^j - X^i) + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 + S_{ji} ) + \frac{1}{\mu}W_{ji}\right)^2 + \gamma S_{ji} \trm{ s.t. } S_{ji} \geq 0
\]
\[
S_{ji} = \max(h_j - (h_i + B_i^\tran (X^j - X^i) + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 ) + \frac{1}{\mu} W_{ji} - \gamma, 0)
\]

\subsection{Updates for $\mathbf{W}$, $\mathbf{M}$}

Before:
\[
W_{ji} = W_{ji} + \mu ( h_j - (h_i + B_i^\tran (X^j - X^i) + S_{ji})),  \,\,\, M = M + \mu ( \mathbf{C} - [\mathbf{B},\mathbf{D}])
\]

After:
\begin{align*}
W_{ji} &= W_{ji} + \mu ( h_j - (h_i + B_i^\tran (X^j - X^i) + \sum_{k=1}^p \mathbf{D}^i_k (X^j_k - X^i_k)^2 + S_{ji})) \\
M &= M + \mu ( \mathbf{C} - [\mathbf{B},\mathbf{D}])
\end{align*}

\subsection{Updates for $\mathbf{D}$}

\begin{align*}
\min_D & \sum_{ij} (W_{ji} \cdot [ h_j - h_i - B_i^\tran(X^j - X^i) - \sum_{k=1}^p \mathbf{D}_{ik} (X^j_k - X^i_k)^2 - S_{ji}]) \\
& + \frac{\mu}{2} \sum_{ij} ( h_j - h_i - B_i^\tran (X^j - X^i) -\sum_{k=1}^p \mathbf{D}_{ik} (X^j_k - X^i_k)^2-S_{ji})^2 \\
& + \trace(M_D^\tran (C_D - D)) + \frac{\mu}{2} \| C_D - D\|^2
\end{align*}

Simplifying things, we have 
\[
\min_{D_i} \sum_{j=1}^n \left( h_j - h_i - B_i^\tran (X^j - X^i) - S_{ji} - D_i^\tran \Delta_{ij} + \frac{1}{\mu} W_{ji} \right)^2 \frac{\mu}{2} + \frac{\mu}{2} \| D_i - (C_{D,i} + \frac{1}{\mu} M_{D,i}) \|_2^2
\]
where $\Delta_{ij}$ is a $p$-dim vector and $\Delta_{ij}(k) = (X^j_k - X^i_k)^2$.

Taking a cue from the update for $B_i$, I would guess that the update for $D_i$ is the following:

\begin{align*}
D_i &= \left( \mathbf{I} + \sum_{j=1}^n \Delta_{ij} \Delta_{ij}^\tran \right)^{-1} \\
	& \left( \mathbf{C}_{D,i} + \frac{1}{\mu} \mathbf{M}_{D,i} + \sum_{j=1}^n \Delta_{ij} ( h_j - h_i - S_{ji} - B_i^\tran (X^j - X_i) + \frac{1}{\mu} W_{ji} ) \right)
\end{align*}

\section{High-Dimensional Consistency Analysis}
This proof strategy first bounds denoising error and then use the fact that convex functions are Lipschitz on a compact set to bound the interpolation error.\\

We augment $X$, a $p \times n$ regressor matrix, with one more row of all ones. Then any convex function can be expressed as $\max B^\tran X$ for some $B$ matrix which is $(p+1) \times n$, the max-operation is taken column-wise, that is, over the $n$ columns of $B$ matrix.

Let $\hat{B}$ be the empirical risk minimizer.\\

\textbf{Note:} Even without noise, there could be infinite number of convex functions that agrees with the ground truth on the $n$ data points we sample. The equivalence class of such convex functions become smaller as $n$ increases. We will compare our piece-wise linear convex function against an \emph{arbitrary} piece-wise linear function, which we represent by $B^*$, that agrees with the true function $g^*$ on $X_1,...,X_n$.

 \begin{align*}
\frac{1}{2n} \| Y - \max \hat{B}^\tran X \|_2^2 + \lambda \|\hat{B}\|_{2,1} &\leq
				\frac{1}{2n}\| Y - \max B^{*\tran} X\|_2^2 + \lambda \| B^*\|_{2,1}
\end{align*}

FACT 1: $\frac{1}{2n}\|Y - \max B^{*\tran} X\|_2^2 = \frac{1}{2n}\| \epsilon \|_2^2$.

FACT 2: 
\begin{align*}
\frac{1}{2n} \| Y - \max \hat{B}^\tran X \|_2^2  &= \frac{1}{2n} \| \max B^{* \tran} X - \max \hat{B}^\tran X + \epsilon  \|_2^2\\
&=  \frac{1}{2n} \left\{ \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2 + \|\epsilon\|_2^2 + 
\langle \max B^{* \tran} X - \max \hat{B}^\tran X, \epsilon \rangle \right\}
\end{align*}

Putting these two facts back into the original inequality, we have:

\begin{align*}
\frac{1}{2n} \left\{ \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2 + 
\langle \max B^{* \tran} X - \max \hat{B}^\tran X, \epsilon \rangle \right\} \leq \lambda \| B^* \|_{2,1} - \lambda \|\hat{B}\|_{2,1}
\end{align*}

Let us consider the cross term first. We write $[\max B^{* \tran} X]_i = B^{*\tran}_i X^i$, where $B^*_i$ is a column of the $B^*$ matrix.

Then we have, through two applications of Holder's inequality
\begin{align*}
\frac{1}{2n} |\langle \max B^{* \tran} X - \max \hat{B}^\tran X, \epsilon \rangle| 
				&\leq \frac{1}{2n} \sum_{i=1}^n \epsilon_i \sum_{s=1}^p (B^*_{si} - \hat{B}_{si}) X^i(s) \\
				&\leq \sum_{s=1}^p \frac{1}{2n} \sum_{i=1}^n ( \epsilon_i X^i(s))(B^*_{si} - \hat{B}_{si}) \\
				&\leq \sum_{s=1}^p \| B^*_{s \cdot} - \hat{B}_{s \cdot} \|_2 \frac{1}{2n} \sqrt{\sum_{i=1}^n \epsilon^2_i X^{i 2}(s)} \\
				&\leq \| B^* - \hat{B}\|_{2,1} \max_{s=1,..,p} \frac{1}{2n} \sqrt{\sum_{i=1}^n \epsilon^2_i X^{i 2}(s)} 
\end{align*}

Let us temporarily impose the strong condition that the $\epsilon_i$'s are iid and that $X^i \sim N(0,I_p)$, then the second term $\frac{1}{2n} \sqrt{\sum_{i=1}^n \epsilon^2_i X^{i 2}(s)}  \leq \sigma \sqrt{\frac{\log p}{n}}$ with high probability.

Returning to the main bound, we have:
\begin{align*}
\frac{1}{2n} \left\{ \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2 + 
\langle \max B^{* \tran} X - \max \hat{B}^\tran X, \epsilon \rangle \right\} &\leq \lambda \| B^* \|_{2,1} - \lambda \|\hat{B}\|_{2,1} 
\end{align*}
Shuffling the terms, we have
\begin{align*}
\frac{1}{2n} \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2 &\leq \lambda \| B^* \|_{2,1} - \lambda \|\hat{B}\|_{2,1}  + \sigma \sqrt{\frac{\log p}{n}} \| B^* - \hat{B} \|_{2,1} 
\end{align*}

Say $\frac{\lambda}{2} \equiv \sigma \sqrt{\frac{\log p}{n}}$. Now we break apart the norms. Let $S \subset \{1,...,p\}$ be the set of relevant entries of $B^*$. Let $B^*_S$ be a submatrix of $B^*$ where \emph{we restrict the rows} to only $S$--so $B^*_S$ is a

FACT 1: $ \| B^* \|_{2,1} - \|\hat{B}\|_{2,1} \leq \| B^* - \hat{B}_S \|_{2,1} + \| \hat{B}_{S^c} \|_{2,1}$

FACT 2: $\| B^* - \hat{B} \|_{2,1} = \| B^* - \hat{B}_S \|_{2,1} + \| \hat{B}_{S^c} \|_{2,1}$

These two facts combined give us an \textbf{important} intermediate result:
\begin{align}
\frac{1}{2n}  \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2  &\leq \lambda \| B^* \|_{2,1} - \lambda \|\hat{B}\|_{2,1}  + \frac{\lambda}{2} \| B^* - \hat{B} \|_{2,1}  \notag \\
			&\leq \frac{3\lambda}{2} \| B^* - \hat{B}_S \|_{2,1} - \frac{\lambda}{2} \| \hat{B}_{S^c} \|_{2,1} \label{eqn:intermediate}
\end{align}

In normal Lasso derivation, we would bound the RHS with the restricted eigenvalue (RE) condition. Let us make the following \textbf{assumption}, which is like the RE condition:\\

\begin{framed}
\textbf{The KEY Assumption:} Let $\{ B^*_i \}$ be $s$-sparse vectors.
\begin{align*}
 & \frac{1}{2n} \sum_{i=1}^n ((B_i - B^*_i)^\tran X^i)^2 \geq \kappa^2 \| B_S - B^* \|^2_F \,\,;\:\,\forall B \in \mathcal{B} \\ 
			& \mathcal{B} \equiv \{ B \in \R^{(p+1) \times n} \,:\, (B_i - B_j)^\tran X_i \geq 0 \forall i,j ; \|B_{S^c}\|_{2,1} \leq 3 \| B_S \|_{2,1}\}
\end{align*}
$\kappa$ is some constant, hopefully strictly positive, and hopefully does not decrease too quickly with $n, p$
\end{framed}

Let us optimistically continue to tame the inequality:
\begin{align*}
\frac{1}{2n}  \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2^2 &\leq \frac{3\lambda}{2} \| B^* - \hat{B}_S \|_{2,1} - \frac{\lambda}{2} \| \hat{B}_{S^c} \|_{2,1}\\
				&\leq \frac{3 \lambda}{2} \sqrt{|S|} \| B^* - \hat{B}_S \|_F - \frac{\lambda}{2} \|\hat{B}_{S^c} \|_{2,1} \\
				&\leq \frac{3 \lambda}{2}\sqrt{\frac{1}{2n}} \frac{\sqrt{|S|}}{\kappa} \| \max B^{* \tran} X - \max \hat{B}^\tran X \|_2 - \frac{\lambda}{2} \|\hat{B}_{S^c} \|_{2,1}
\end{align*}

Reshuffling and discarding unnecessary terms, we get
\begin{align*}
\sqrt{\frac{1}{2n}} \| \max B^{* \tran} X - \max \hat{B}^\tran X  \|_2  &\leq \frac{3\lambda}{2} \sqrt{|S|}  \frac{1}{\kappa} \\
					&\leq \frac{3}{2} \sqrt{ \frac{ |S| \log p}{n}} \frac{1}{\kappa}
\end{align*}

\textbf{Conclusion 1: } We can denoise well. The estimated convex function $\hat{g}$ and the true convex function $g^*$ agree on the observed $X^i$'s.

Going back to Equation~\ref{eqn:intermediate} and the KEY assumption, we can derive other results:

\[
\| \hat{B}_S - B^* \|_F^2 \leq \frac{3}{2} \sqrt{\frac{|S| \log p}{n} } \frac{1}{\kappa^2}
\]

\textbf{Conclusion 2: } Our estimated convex function $\hat{g}$ agrees with $g^*$ on the relevant dimensions.

\begin{align*}
\| \hat{B}_{S^c} \|_{2,1} & \leq 3 \| \hat{B}_S - B^* \|_{2,1} \\
				&\leq 3 \sqrt{\frac{1}{2n}} \| \max B^{*\tran} X - \max \hat{B}^\tran X \|_2\\
				&\leq \frac{9}{2} \sqrt{\frac{|S|\log p}{n}} \frac{1}{\kappa}
\end{align*}

\textbf{Conclusion 3: } Our estimated regression function is small on the irrelevant dimensions.\\

The next step of the analysis is to bound the interpolation error.

\begin{framed}
The Lipschitz assumption. (can be proven) We suppose that $\hat{g}$ and $g^*$ are both $L$-Lipschitz on a compact subset of $\R^{|S|}$, which is the space of the relevant dimensions; that implies that they must both be $L$-Lipschitz on a compact subset of $\R^{p+1}$ as well.\\

\textbf{Note: } We might only be able to prove a weaker condition described below; but that weaker condition may be sufficient. 
\[
|\hat{g}(x) - \hat{g}(x') | \leq L \| x _S - x'_S \|_2 + O\left( \sqrt{\frac{|S| \log p}{n}} \right)
\]
\end{framed}

Now we can begin to bound the interpolation error. Let $x$ be an arbitrary point in the compact set on which $\hat{g}, g^*$ are Lipschitz and let $X^i$ be the sample in our training data that is closest to $x$.
\begin{align*}
\E|\hat{g}(x) - g^*(x) | & \leq \E| \hat{g}(x) - \hat{g}(X^i) + \hat{g}(X^i) - g^*(X^i) + g^*(X^i) - g^*(x) | \\
		&\leq 2L\E\| x_S - X^i_S \|_2 + O\left( \sqrt{\frac{|S|\log p}{n} } \right)
\end{align*}

For many distributions, $\E\| x_S - X^i_S \|_2$ is on the order of $n^{- \frac{1}{s}}$.

\subsection{Intuition on the KEY Assumption}

Let us suppose $B^* = 0$ for now. Then the KEY assumption becomes:
\begin{align*}
 & \frac{1}{2n} \sum_{i=1}^n (B_i^\tran X^i)^2 \geq \kappa^2 \|B_S \|_F^2 \,\,;\:\,\forall B \in \mathcal{B} \\ 
			& \mathcal{B} \equiv \{ B \in \R^{(p+1) \times n} \,:\, (B_i - B_j)^\tran X_i \geq 0\forall i,j ; \|B_{S^c}\|_{2,1} \leq 3 \| B_S \|_{2,1} ; \}
\end{align*}

\section{Looking at Subgradient}

The linear inequality case:
\begin{align*}
\min_{\beta}  & \|\beta\|_1 \\
\trm{s.t.} & X\beta \leq y
\end{align*}

The Lagrangian optimization is
\[
\max_w \min_\beta \|\beta\|_1 + w^\tran (X\beta - y) 
\]

The KKT condition is that $- w^\tran X \in \partial \|\beta\|_1$ and that $w^\tran X\beta = w^\tran y$.

$w$ is a vector in $\R^n$ and the dual optimization is:
\begin{align*}
\min_w & w^\tran y \\
\trm{s.t.} & X^\tran w \in [-1,1]^p \\
&	w \geq 0
\end{align*}

FACT: Suppose I increase the penalty to $\lambda$--a large number--on the irrelevant coordinates, then the dual becomes
\begin{align*}
\min_w & w^\tran y \\
\trm{s.t.} & X_S^\tran w \in [-1,1]^s \\
& X_{S^c}^\tran w \in [-\lambda, \lambda]^{p-s} \\
&	w \geq 0
\end{align*}

FACT: if an oracle lights up the true support, then the dual becomes:
\begin{align*}
\min_w & w^\tran y \\
\trm{s.t.} & X_S^\tran w \in [-1,1]^s\\
& w \geq 0
\end{align*}
This has strictly fewer constraints than full dimensional problem.

Lastly, we can also compare against\\
\begin{align*}
\min_w & w^\tran X_S \beta^* \\
\trm{s.t.} & X_S^\tran w \in [-1,1]^s\\
& w \geq 0
\end{align*}

Let us consider an easy pair of problems:
\begin{align*}
\min_{\beta}  & \|\beta\|_1 \\
\trm{s.t.} & M \beta \leq M \beta^*
\end{align*}

\begin{align*}
\min_{\beta_S}  & \|\beta_S\|_1 \\
\trm{s.t.} & M_S \beta_S \leq M_S \beta^*_S
\end{align*}
where $M_S$ is a subset of the columns of $M$.

Note that $M \beta = M_S \beta_S + M_{S^c} \beta_{S^c}$.

\section{Using Second-order Information}

\end{document}

### 2013-09-29 tex/discussion_notes.tex
first init

\documentclass{article}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{minx_math}
\usepackage{subfigure,mathtools}

%\usepackage{xypic}
%\xyoption{pdf}

\begin{document}
\section{(7/26/2013)}

Conditional Likelihood Maximization. We compute the marginalization
$$
p(x) = \int \exp(f(x, \xi)) d \xi
$$
where $x \in \R^{d-1}$.

The overall conditional density is

$\log p(y|x) = \log p(y,x) - \log p(x)$.

\section{(5/22/2013) Meeting Notes}

The list of concepts that we need to formalize:
\begin{packed_enum}
\item We need a high probability bound on $\|Y\|_2^2$ and therefore on $\| \hat{r} \|_2^2$ as well.
\item We need to impose a hard constraint on derivative of $\hat{f}_s$ for all $s$, and use it to derive a high probability bound on the $l_\infty$ norm of $\hat{r}$.
\item We need to formally argue that $F(X) = \sum_{i=1}^n X_i \hat{r}_i \delta_{ ord(i) > j}$ is a coordinatewise-Lipschitz function
\item We need to formally argue that random sampling of coordinates of $\hat{r}$ converges exponentially to zero.
\item We need to take union bound $np$ times. Each time, we also need to take a union bound between the two terms.
\end{packed_enum}

\section{(5/10/2013) Meeting Notes}

\subsection{Sparsistency}

First, we briefly review our inner approximation short-hand notation:

\[f_k(X_{ki}) = \Delta_k d_k  - c_k \mathbf{1}\]

where $\Delta_k$ is a $n\times n-1$ matrix: $\Delta_{k (ij)} = \left\{ \begin{array}{cc} 0 & \trm{ if } order(i) \leq j \\ X_{ki} - X_{k(j)} & \trm{ else } \end{array} \right.$

$d_k$ is a $(n-1)$-dimensional vector. $d_{k1} = \beta_{k1}$, $d_{ki} = \beta_{ki} - \beta_{k (i-1)}$. Therefore, all coordinates of $d_k$ except the first are positive.

$c_k$ is a constant to ensure that $\sum_i f_k(X_{ki}) = 0$, that the fitted function is centered.\\

We will, for convenient, use the penalty $h(d_k) = |d_{k1}| + \sum_{i=2}^n d_{k2}$. The penalty that correspond to actual $l_\infty$ norm is $h'(d_k) = \max( |d_{k1}|, d_{k1} + \sum_{i=2}^n d_{k2})$. We claim however that $h'(d_k) \leq h(d_k) \leq 2h'(d_k)$; this is because $h(d_k)$ is at most magnitude of the left-most derivative plus the right-most derivative.

\subsubsection{Proof}

FACT: A bounded convex function on a compact set is Lipschitz. The Lipschitz constant depends on $\max_{x \in C} f(x)$\\

FACT: If $f_k(x_k)$ are $L$-Lipschitz, then $\sum_k f_k(x_k)$ is also $L$-Lipschitz.
\[
| \sum_k f_k(x_k) - \sum_k f_k(x'_k) |^2 \leq \sum_k |f_k(x_k) - f_k(x'_k)|^2 \leq \sum_k L^2| x_k - x'_k |^2 \leq L^2 \| x - x' \|_2^2
\]

FACT: if $X$ is sub-gaussian random vector, then $g(X)$ is also sub-gaussian if $g$ is Lipschitz. This is true by McDiarmid's inequality.\\

Let $\hat{f}_k$ be the optimal solution to the optimization
\[
\frac{1}{2n} \| Y - \sum_{k=1}^p \hat{f}_k(X_k) \|_2^2 + \lambda\sum_{k=1}^p \| \partial \hat{f}_k(X_k)\|_\infty \qquad \hat{f}_k \trm{ convex and } \sum_i \hat{f}_k (x_{ik}) = 0 .
\]
We note that using our reformulation, we can also write our objective as
\[
F(d_1,..., d_p) = \frac{1}{2n} \| Y - \sum_{k=1}^p \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{k=1}^p ( |d_{k1}| + d_{k2} ... d_{kn} ) .
\]
We can also write the Lagrangian as 
\[
L(d_1,..., d_p) = \frac{1}{2n} \| Y - \sum_{k=1}^p (\Delta_k d_k + c_k )\|_2^2 + \lambda \sum_{k=1}^p ( |d_{k1}| + d_{k2} ... d_{kn} )  - \sum_{k=1}^p \mu_k^\tran d_k - \sum_{k=1}^p \gamma_k (c_k - \frac{1}{n} \mathbf{1}^\tran \Delta_k d_k)
\]
where for every $k$, $\mu_k$ has to be a positive vector.

\textbf{ASSUMPTIONS: }
\begin{packed_enum}
\item $Y' = f(X_S) + \epsilon$ for some Lipschitz function $f$ and sub-gaussian $\epsilon$. $Y = Y' - \bar{Y'}$.
\item The relevant and irrelevant dimensions $X_S, X_{S^c}$ are independent. (We can relax this into a deterministic irrepresentability condition)
\end{packed_enum}

\textbf{CLAIM:}
If we set $\lambda = O \sqrt{\frac{\log (np) }{ n }}$, then (1) $\hat{f}_{S^c} = 0$ with high probability and (2) $\hat{f}_S$ is the solution to the \emph{restricted} regression $\frac{1}{2n} \| Y - \sum_{s \in S} \hat{f}_s(X_s) \|_2^2 + \lambda\sum_{s \in S} \| \partial \hat{f}_s(X_s)\|_\infty$\\

\textbf{NOTE:} 
\begin{packed_enum}
\item We will assume for now, though I think it can be proven, that $\hat{f}_k$ all have, with high probability, bounded Lipschitz constant independent of $n, p$.
\item We made very weak assumption on the true function $f$ but very strong assumptions on the covariates. I think we can trade-off the two: we can still satisfy the deterministic irrespresentability condition with stronger assumptions on the true $f$ and weaker assumptions on the covariates.
\item The proof is similar to Primal Dual Witness but we take gradient with respect to one dimension at a time. This is much more convenient for our case.
\end{packed_enum}

{\bf PROOF:}
We will show that there exists a sparse solution and that the irrelevant dual variables for this solution has magnitude strictly $< 1$. We will later argue that all solutions must then be sparse also.\\

Define $\hat{f}$ as the solution described in the claim. We will prove stationarity, complementary slackness, on the Lagrangrian.

In particular, we will show that with $\hat{f}$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k} L(\hat{d})  = 0$ for all $k$.

Define residue $\hat{r} = Y - \sum_{s \in S} \hat{f}_s(X_s)$. \\

We observe that $\hat{r}$ is independent of $X_{S^c}$ because $\hat{f}_{S}$ is the solution to the restricted regression and is therefore independent of $X_{S^c}$.

Using the reformulation, we can re-write the Lagrangian $L$, in term of just $f_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| \hat{r} - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
\]
First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{f}_k$ satisfy stationarity with dual variables that satisfy complementary slackness. \\

Now, let us fix $k \in S^c$ and prove that $\hat{d}_k = 0, \hat{c}_k=0$ is an optimal solution.

\begin{align*}
\partial d_k :& \qquad \frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad \frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k - c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.\\

We now substitute in $\hat{d}_k = 0, \hat{c}_k=0$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

\begin{align*}
\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{1}  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
Note that $\mathbf{u}$ became $\mathbf{1}$.\\

First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
\[
\lambda \mathbf{1} > \frac{1}{n} \Delta_k^\tran\hat{r}. 
\]
We need strict inequality to later argue that ALL solutions are sparse. We need to prove that $| \frac{1}{n} \Delta_k^\tran\hat{r}|$ is of the order $O\sqrt{ \frac{\log(1/\delta)}{n}}$ with probability at least $1- \delta$. \\

Obvious Facts:
\begin{packed_enum}
\item Column $j$ of $\Delta_k$ is $ \max( X_k - X_{k(j)} \mathbf{1}, 0)$. It is all positive with many zeros for large $j$.
\item Coordinates of $\hat{r}$ are identically distributed but not independent. And $\| \hat{r} \|_2^2 = F_S(\hat{f}_S) \leq F_S(0) = \| Y \|_2^2$. 
\item Columns of $\Delta_k$ and $\hat{r}$ are independent. And $\hat{r}$ sums to 0.
\end{packed_enum}

For $j=1$, the deviation bound is easy. 
\[
\Delta_{k, j}^\tran \hat{r} = (X_k  - X_{k(1)} \mathbf{1})^\tran \hat{r} = X_k^\tran \hat{r} - X_{k(1)} \mathbf{1}^\tran \hat{r} = X_k^\tran \hat{r} 
\]
And because $X_k \in \R^n$ is iid subgaussian vector with mean 0 and is independent of $\hat{r}$, the desired deviation bound holds with the desired probability.\\

Non-obvious Facts:\\
We claim that each coordinate of $\hat{r}$ is at most $O\sqrt{|S| \log(n/\delta)}$ with probability at least $1-\delta$. That is because $\hat{r} = Y - \sum_{k \in S} \hat{f}_k (X_k)$. With probability at least $1-\delta$, for all $i$, $|Y_i | \leq \sqrt{\log(n/\delta)}$. Let us suppose $\hat{f}_S = \sum_{k \in S} \hat{f}_k$ is $L$-Lipschitz, and so 
\[
\max_i | \hat{f}_S(X_S^{(i)})| \leq \max_{i,i'} | \hat{f}_S(X_S^{(i)}) - \hat{f}_S(X_S^{(i')}) | \leq L \max_{i,i'} \| X_S^{(i)} - X_S^{(i')} \| \leq 2L \max_i \| X_S^{(i)} \|
\]

%Now, we recall that $\Delta_k$ and $\hat{r}$ are independent, that $\Delta_k$ is a positive matrix with (whp) bounded entries and that $\hat{r} = r_1 - \bar{r}_1$ where $r_1$ is a $n$-vector of independent zero-mean subgaussian random variables and $\bar{r}_1$ is the empirical mean of $r_1$.

%Every coordinate of $\frac{1}{n} \Delta_k^\tran r_1$ must then be of order $O( \sqrt{\frac{1}{n}})$ by standard concentration and $\frac{1}{n} \Delta_k^\tran \mathbf{1} \bar{r}_1$ must also be of order $O(\sqrt{\frac{1}{n}})$.

%We need to take union bounds across all $n$ coordinates of $\frac{1}{n} \Delta_k^\tran \hat{r}$ as well as all $p-|S|$ irrelevant dimensions. Therefore, setting $\lambda = O \sqrt{\frac{\log (np)}{n}}$ suffices.

\newpage

\section{(5/3/2013) Meeting Notes}

\subsection{Short-hand}

The objective is
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \hat{f}_s(X_s) \|_2^2 + \sum_{s=1}^p \| \partial \hat{f}_s(X_s)\|_2 \qquad \hat{f}_s \trm{ convex and } \sum_i \hat{f}_s (x_{is}) = 0
\]

Let us try to simplify this form. Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large.\\

Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\

Then  
\begin{align*}
\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
\end{align*}

We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
\[
D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
\]

And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.

\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment. $\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$. The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\

$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.

\[
\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
\]

\begin{align*}
\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
\end{align*}

\[
\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
\]

Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write

\[
\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
\]

With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\

\textbf{Notation:} We will also define $\Delta_s$ as a $(n \times n-1)$ matrix whose $i,j$-th entry is $\Delta(j, x_{si})$.

With this short-hand, we can write $\hat{f}_s(x_s) = \Delta_s\hat{d}_s$.\\

Row $i$ of $\Delta_s$ is the vector $[ \Delta(1, x_{si}), \Delta(2,x_{si}) ..., \Delta(n-1, x_{si})]$. It is $n-1$ dimensional.\\

Column $j$ of $\Delta_s$ is the vector $[ \Delta(j, x_{s1}), \Delta(j, x_{s2}), ..., \Delta(j, x_{sn}) ]$. \\

\emph{Examples:} $\Delta(j, x_{si}) = \max(x_{si} - x_{s(j)}, 0)$

\subsection{Consistency with Short-hand}

We can now attempt the consistency proof with our short-hand notation.

First, what is the objective? 
\[
\| \partial \hat{f}_s(X_s) \|_\infty = \| \hat{\beta}_{si} \|_\infty 
\]

For simplicity, we can use a different but very similar constraint: $ |\hat{d}_{s0}| + \sum_{i=1}^n \hat{d}_{si}$.

The objective is therefore
\[
\frac{1}{2n} \| Y - \sum_{s=1}^p \Delta_s \hat{d}_s \|_2^2 + \sum_{s=1}^p \left[ |\hat{d}_{s0}| + \sum_{i=1}^n \hat{d}_{si} \right].
\]

\section{(4/19/2013) Meeting Notes}
\subsection{Main Result}

\begin{lemma}
\label{lem:int_reduction}
Let $f(x_1, x_2)$ be a 2D convex function defined on $C = [0,1]^2$. Suppose $h(x_1), g(x_2)$ minimizes $ \int_C | f (x_1, x_2) - h(x_1) - g(x_2) |^2 dx$ among all univariate convex functions.\\

$h(x_1)$ is not a constant function iff $\int_{x_2} f(x_1,x_2) dx_2$ is not constant with respect to $x_1$.
\end{lemma}

This following proposition combined with Lemma~\ref{lem:int_reduction} gives the desired result.

\begin{proposition}
Let $f(x_1, x_2)$ be a bivariate convex function defined on $C = [0,1]^2$. Suppose $f$ is \emph{continuous} on $C$ and is twice differentiable. (It must be continuous on the interior of $C$) \\

The following are equivalent:
\begin{packed_enum}
\item For all $x_2$, $f(\cdot, x_2)$ as univariate functions of $x_1$ are identical.
\item For all $x_2$, the integrals $\int_{x_1} f(x_1, x_2) d x_1$ are identical.
\end{packed_enum}
\end{proposition}

\begin{proof}
The first condition trivially implies the second condition.\\

Suppose that for all $x_2$, the integral $\int_{x_1} f(x_1,x_2) dx_1$ is, without loss of generality, equal to $0$. \\

For a fixed $x_1$, define the \emph{right directional derivative} as 
\[
g(x_1) \equiv \lim_{x_2 \rightarrow 0^+} \frac{f(x_1, x_2) - f(x_1, 0)}{x_2}
\]
This limit has to exist by assumption of continuity and by the fact that $f(x_1, \cdot)$ is a univariate convex function with respect to $x_2$.\\

\textbf{Fact 1:} $\int_{x_1} g(x_1) d x_1 = 0$ because $\int_{x_1} f(x_1, x_2) d x_1 = 0$ for all $x_2$. We can invoke the bounded convergence theorem to make this deduction more formal.\\

\textbf{Fact 2:} Because $f$ is convex, $g(x_1)$ is also a component of the 2-dimensional subgradient $\partial f(x_1,0)$, that is, $g(x_1) = \partial f(x_1, 0)^\tran \mathbf{e}_2$.

Therefore, for all $x_1$, $f(x_1, x_2) \geq f(x_1, 0) + x_2 g(x_1)$. \\

Since $\int_{x_1} f(x_1, 0) + x_2 g(x_1) dx_1 = 0$ and $\int_{x_1} f(x_1, x_2) dx_1 = 0$, it must be that $f(x_1, x_2) =  f(x_1, 0) + x_2 g(x_1)$ for all $x_1$. \\

The Hessian of $f(x_1, x_2)$ at a point $x_1, x_2$ is of the form
\[
\left[ \begin{array}{cc}
	a & b \\
	b & 0 
	\end{array} \right]
\]
where $a \equiv \partial^2 f(x_1,0)/ \partial^2 x_1$ and $ b \equiv \partial g(x_1) / \partial x_1$.  Note that $a,b$ depend on $x_1$ only. The characteristic polynomial is $-\lambda ( a -\lambda) - b^2$.

Apply the quadratic formula to solve the characteristic polynomial, we get the solutions $\frac{ a \pm \sqrt{a^2 + 4 b^2}}{2}$. The Hessian is therefore NOT positive-semidefinite unless $b=0$. \\

Thus, $g'(x_1) = 0$ for all $x_1$, and $g(x_1)$ is necessarily $0$.\\
\end{proof}

\subsection{Lemmas}
\begin{lemma}
Let $f(x)$ be a univariate function, integrable. We approximate $f(x)$ with a constant: $c^* \equiv \min_c \int_C | c - f(x) |^2 dx$.\\
Define $A = \int_C 1 dx$ as the measure of $C$, 
\[
\trm{then we have that} \quad c^* = \frac{1}{A} \int_C f(x) dx
\]
\end{lemma}
\begin{proof} (of lemma)\\

Because the objective is convex with respect to $c$, we can use the KKT theorem. The stationarity condition implies that
\begin{align*}
2 \int_C c^* - f(x) dx &= 0 \\
\int_C c^* dx &= \int_C f(x) dx \\
\end{align*}
\end{proof}

Let us also assume that $C = [0, 1]^2$ for simplicity; $C$ has area 1 and when restricted to either $x_1$ or $x_2$, $C$ is a line with length $1$. \\

We claim that $h(x_1) = \int_ {x_2} f(x_1,x_2) d x_2 - \alpha$ for some constant $\alpha$. Why? If we solve $ \min_h \int_C | f (x_1, x_2) - h(x_1) - g(x_2) |^2 dx$ \emph{without} requiring that $h$ is a convex function, the optimal solution is, by lemma, $ x_1 \mapsto \int_ {x_2} f(x_1,x_2) - g(x_2) d x_2$; but because the sum of convex functions is still convex, the solution actually satisfies the convex requirement; and because $\int_{x_2} g(x_2) d x_2$ is a constant, we can define it to be $\alpha$.\\

Therefore, $h(x_1)$ is a constant function iff for all $x_1$, $\int_{x_2} f(x_1,x_2) dx_2$ is a constant. This proves Lemma~\ref{lem:int_reduction}.\\

A lemma that we might not use.
\begin{lemma}
Let $f$ be a convex function on $C \subset \R^n$. Let $x, y \in C$, then for all $x'$ on the line from $x$ to $y$:
\[
f(x') - f(x) \leq \frac{f(y) - f(x)}{(y-x)} (x' - x)
\]
\end{lemma}

Simply put, if we draw a line, in $R^{n+1}$, from $(x, f(x))$ to $(y, f(y))$, then $f$ applied to $[x,y]$ must lie ``below'' this line.\\

\newpage
\section{(4/12/2013) Meeting Notes}

\subsection{A Summary of Current Affairs}

We have tried fitting piecewise linear convex (PLC) functions, reweighted PLC functions, additive PLC functions, PLC and quadratic functions.\\

Out of all these methods, only reweighted PLC function succeeds in exact variable selection. The reweighted PLC function is however difficult to analyze; we may need to analyze it as we would a ``thresholded'' PLC function.\\

All of these methods however give reasonable results: for reasonably sized $n$, the weights of the irrelevant variables are much smaller than the weights of the relevant variables.\\

This suggest then that we should use a weaker criterion for success, which Minhua has already begun to do.

\begin{definition} (Consistency-like Criterion)\\
Let $f(n,p,s)$ be some scaling function, i.e. $f(n,p,s) = \sqrt{\frac{s\log p}{n}}$.

We declare success if, for some constant $c$ independent of $n,p$:
\begin{align*}
\| \hat{\beta}_j \|_\infty &\geq c \quad \forall j \in S, \; n,p \rightarrow \infty \; f(n,p,s) \rightarrow 0 \\
\| \hat{\beta}_j \|_\infty &\rightarrow 0 \quad \forall j \in S^c
\end{align*}
\end{definition}

I don't know for what scaling function $f(n,p,s)$ does the PLC fitting satisfy the above criterion. Perhaps we can search for an answer via experiments on the cluster.\\

I also suggested a criterion before--stronger than the one I write now--which I think does not hold for PLC methods.
\[
\lim_{n \rightarrow \infty} \frac{\| B_S \|_{1,\infty}}{\|B \|_{1,\infty}} \rightarrow 1
\]

\subsection{A Good Simpler Problem to Consider?}

Multi-task lasso where each task has only one sample:

$p$ dimensions, $k$ tasks. \emph{There is no $n$.}\\

$B$ is $p \times k$. The rows of $B$ are different but have same support.

$Y \in \R^k$. $X$ is $k \times p$.

$ Y  = \trm{diag}(X B) + \epsilon$

\begin{align*}
\min_{B} \frac{1}{2}\| Y - \trm{diag}(XB) \|_2^2 + \lambda \| B \|_{1,\infty}
\end{align*}

\subsection{Reweighted PLC}

\begin{figure}[htp]
\includegraphics[scale=0.8]{../code/figs/reweight_exact2.eps}
\end{figure}

\newpage
\section{(4/5/2013) Meeting Notes}

\subsection{Quadratic Optimization Results}

\begin{align*}
\min_{\mathbf{h}, \mathbf{B}, \mathbf{C},\mathbf{S},\mathbf{D}}
& \frac{1}{2n}\sum_{i=1}^n(y_i - h_i)^2 + \lambda \|C\|_{\infty,1} + \gamma \frac{1}{n} \sum_{ij} S_{ji} \\
\trm{s.t.} & C_B = B, C_D = D, S_{ji} \geq 0 \\
	& S_{ji} = h_j - h_i - B_i^\tran(X^j - X^i) - \sum_{k=1}^p D_{ik} (X^j_k - X^i_k)^2
\end{align*}

\begin{figure}[htp]
\subfigure[$f^*$ is piece-wise linear]{ \includegraphics[scale=0.4]{../code/figs/FigureLin.eps}}
\subfigure[$f^*$ is log-sum-exp]{ \includegraphics[scale=0.4]{../code/figs/FigureLogexp.eps}}
\subfigure[$f^*$ is a sum of quadratic and piece-wise -linear]{ \includegraphics[scale=0.4]{../code/figs/FigureQuadLin.eps}}
\subfigure[$f^*$ is a cubic]{ \includegraphics[scale=0.4]{../code/figs/FigureCube.eps}}
\caption{For all these figures, we have $n=100, p=40, s=3$}
\end{figure}

\begin{figure}[htp]
\subfigure[$n=120, \gamma =0.5$]{ \includegraphics[scale=0.4]{../code/figs/FigureQuadLin.eps}}
\subfigure[$n=120, \gamma =0.05$]{ \includegraphics[scale=0.4]{../code/figs/FigureQuadLin2.eps}}
\subfigure[$n=300,\gamma = 0.5$]{ \includegraphics[scale=0.4]{../code/figs/FigureQuadLin3.eps}}
\caption{For all these figures, $f^*$ is a sum of quadratic and piece-wise linear function.}
\end{figure}

\subsection{Reweighted Plot}

\begin{figure}[htp]
\includegraphics[scale=0.5]{../code/figs/Reweighted_exact_recovery.eps}
\end{figure}

\newpage
\section{(3/28/2013) Meeting Notes}

We know that learning a sparse gradient at one point $x$ is too formidable a task, that is why we impose the $l_\infty-l_1$ penalty to link and sync the learning of all the gradients.

The $l_\infty-l_1$ penalty seems to not be enough. One idea is to use reweighing. We brainstorm some other ideas in the following note.

\subsection{K-means and Fused Lasso penalty for Piecewise-Linear Convex Functions}

If the true function is piecewise-linear-convex, then the gradients for many of the $x$'s are the same. Therefore, we can either use the $K$-means formulation or the convex fused lasso penalty $\sum_{i,j = 1,...,n} \| B_i - B_j \|_q$ for some norm.

Preliminary experiments with the $K$-means optimization suggest that this can be effective. We need the true number of ``pieces'' to be small and we need $K$-means to pick up the clusters correctly; the second requirement can be possibly waived if we use the fused lasso penalty.

\begin{figure}
\subfigure[k-means with $K* = 3$]{ \includegraphics{../code/figs/k_means_recovery_K03.eps}}
\subfigure[k-means with $K* = 7$]{ \includegraphics{../code/figs/k_means_recovery_K07.eps}}
\end{figure}

\subsection{Quadratic Term}

If a convex function $f$ is strongly convex at a point $x$, then the linear form is a poor approximation, i.e. $f(y)$ can be much larger than $f(x) + \partial f(x) (y - x)$. The usefulness of the data point $y$ in estimating the gradient at $x$ diminishes as $y$ distances itself from $x$ and the approximation gap widens. \\

A natural method that arises out of this observation is to add an additional quadratic term into the optimization objective:

\begin{align*}
\min_{B, \mathbf{c}} & \frac{1}{n} \sum_{i=1}^n | y_i - h_i|^2 + \| [B; \mathbf{c}] \|_{\infty,1} + S_{ij}  \\
\trm{s.t.} & S_{ij} = h_i - h_j - B_j^\tran (X^i - X^j) - \sum_{k=1}^p \mathbf{c}^j_k (X^i_k - X^j_k)^2 \\
			& S_{ij} \geq 0 \\
			& \mathbf{c}^j \geq 0 \\
\end{align*}

Each $\mathbf{c}^j$ is in $\R^p$ and share the same group penalty as the gradients $B_j$'s.

The optimization is not difficult because the constraints are linear with respect to the new $\mathbf{c}^j$ variables.

\newpage

\section{Some Insight}

Let us again consider this noiseless optimization:
\begin{align*}
& \min_B \| B \|_{\infty, 1}\\
&\trm{s.t. } y_j \geq y_i + B_i^\tran (X^j - X^{i*}) \forall i,j
\end{align*}

First, notice that, because (1) each constraint involves only one $B^i$ and (2) the $y_j$'s are not variables, the optimization can be decomposed into $n$ sub-optimizations each done independently.

\begin{align*}
& \min_{\beta \in \R^p} \| \beta \|_{1}\\
&\trm{s.t. } y_j \geq y_{i*} + \beta^\tran (X^j - X^{i*}) \forall j
\end{align*}

This optimization is analogous to finding a subgradient at just $X^{i*}$. This decomposition allows us to compare directly with the linear case because now, in both cases, we are solving for a single vector.\\

Let us simply the expression further. Define $\Delta \in \R^{p \times n}$ where the $j$-th row $\Delta_j = X^j - X^{i^*}$, and define $\mathbf{v} \in \R^n$ where $\mathbf{v}_j = y_j - y^{i*}$. Now the optimization takes on a familiar form.

\begin{align*}
& \min_{\beta \in \R^p} \| \beta \|_{1}\\
&\trm{s.t. } \mathbf{v} \geq \beta^\tran \Delta
\end{align*}

The optimization is similar to the linear case, but we have an inequality instead of a strict equality here. The inequality is the culprit!\\

The solution to the optimization will lie on the intersection of the boundary of the constraint set and the boundary of a $L_1$ norm ball of some minimal radius. \\

Let $\hat{\beta}$ be the solution to the above optimization. Because $\hat{\beta}$ lies on the boundary of the constraint set, some inequalities must be equalities. Let $I$ be the set of inequalities which becomes equalities when we plug in $\hat{\beta}$. Then $\hat{\beta}$ is equivalently the solution of the following optimization:

\begin{align*}
& \min_{\beta \in \R^p} \| \beta \|_{1}\\
&\trm{s.t. } \mathbf{v}_I = \beta^\tran \Delta_I
\end{align*}

where $\Delta_I$ is a $p \times |I|$ sub-matrix and $\mathbf{v}$ is a $|I|$-dimensional sub-vector. Now we see the problem: if $|I|$ is very small, then it is as if we are solving lasso with very few samples--$|I|$ number of samples instead of $n$!\\

How do we interpret $I$? Intuitively, I think of it as all $j$ for which $y_j \approx y_{i*} + B_{i*}^\tran (X^j - X^{i*})$. That is, it is the set of points for which the convex function is close to linear. For strongly convex functions like $\|x\|^2_2$, $I$ would be very small. For linear functions like $\beta^{*\tran} x$, $|I| = n$. \\

Therefore, this explains why our optimization gives sparse solution if the true function is linear and highly non-sparse solution if the true function is strongly convex.

\section{Experiments}

In the soft-recovery experiment, we measure $\frac{ \| B_S \|_{\infty,1}}{\|B\|_{\infty, 1}}$.
\begin{figure}
\includegraphics[trim=150 200 150 200]{../code/figs/soft_recovery.pdf}
\end{figure}
The recovery curve plateaus. It should converge to 1 but appears to be doing so very slowly.

As a thought experiment, let's consider a noiseless support recovery optimization:
\begin{align*}
& \min_B \| B \|_{\infty, 1}\\
&\trm{s.t. } y_i \geq y_j + B_j^\tran (X^i - X_j) \forall i,j
\end{align*}
The optimum of this program should become exactly sparse as $n \rightarrow \infty$, but may become sparse at a very slow rate with respect to $n$. The penalized least-square solution then, like a heat-seeking missile thrown off target by a decoy, homes in to the non-sparse optimum rather than the actual sparse solution.

We have not implemented this optimization but can still approximate it with the penalized square error optimization by setting lambda very small.

What we see if that we must weigh the dimensions to exactly recover the support. We must use a weighed form of the objective.

\begin{align*}
& \min_B \sum_{s=1}^p \lambda_s\| B_{s\cdot} \|_{\infty}\\
&\trm{s.t. } y_i \geq y_j + B_j^\tran (X^i - X_j) \forall i,j
\end{align*}

Where $\lambda_s$ is small for $s \in S$ and large for $s \notin S$.

\begin{figure}
\includegraphics[trim= 150 200 150 200]{../code/figs/guided_recovery.pdf}
\end{figure}

\end{document}

### 2013-09-29 tex/result.tex
first init

\documentclass{article}
\usepackage{minx_math}
\usepackage{framed, mathtools, epstopdf,subfigure}

% eqn:alternate_opt

\begin{document}

\section{Setting and Notations}

\textbf{Setting:}
\begin{packed_enum}
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
\item Let $S \subset \{1,...,p\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$ and let $s \coloneqq |S|$.
\end{packed_enum}

\textbf{Assumptions:}
\begin{packed_enum}
\item[A1] Suppose that $X_S, X_{S^c}$ are independent.
\item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
\item[A2] Suppose that $\|f_0\|_\infty \leq B$.
\item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
\item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
\end{packed_enum}

\textbf{Notation:}
$\mathbf{1}_n$ is an all-ones vector of dimension $n$. If $X \in \R^p$ and $S \subset \{1,...,p\}$, then $X_S$ is a subvector of $X$ restricted to coordinates in $S$. Let $v \in \R^n$, then $v_{(1)}$ denotes the largest coordinate of $v$ in magnitude, $v_{(j)}$ denotes the $j$-th largest. \\

\subsection{Reformulation}

Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large. Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\

Then  
\begin{align*}
\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
\end{align*}

We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
\[
D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
\]

And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.

\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment. $\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$. The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\

$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.

\[
\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
\]

\begin{align*}
\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
\end{align*}

\[
\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
\]

Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write

\[
\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
\]

With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

We will impose the boundness and smoothness constraints only in our theoretical analysis when we control the rate of false negatives.

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k \in S} ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:restricted_alternate_opt} \\
\trm{s.t. $\forall k \in S$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

In the proof, we will reason with the solution of the optimization \ref{opt:alternate_opt} when we restricted $k$ to be only in the subset $S$. This is of course a theoretical construct only and we refer to it as \emph{restricted regression}.\\

Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w \|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.

For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - g \|_n^2$ and define $R_s(g) \coloneqq \E | f_0(X)  + w - g(X) |^2$.

For an additive function $g$, define $\rho_n(g) = \sum_{k=1}^s \| \partial g_k \|_\infty$. Because we use outer approximation in our optimization program, we define $\ds \| \partial g_k\|_\infty \coloneqq \max_{i=1,...,n-1} |\frac{ g_k(X^{(i)}) - g_k(X^{(i+1)})}{ X^{(i)} - X^{(i+1)}}|$.

Let $\mathcal{C}[b,B,L]$ be the set of 1 dimensional convex functions on $[-b,b]$ that are bounded by $B$ and $L$-Lipschitz.

Let $\mathcal{C}^s[b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
\[
\mathcal{C}^s[b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
\]

\section{Functions Which Are Not Additively Faithful}

\textbf{Example 1:}
\[
f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
\]
Note that for all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$.
An additive model would set $f_1 = 0$ and $f_2 = 0$.

\begin{figure}[htp]
\subfigure[Example 1]{\includegraphics[scale=0.5]{../code/figs/sine_wave_funct.eps}}
\subfigure[Example 2]{\includegraphics[scale=0.4]{../code/figs/rising_slope_funct.eps}}
\end{figure}

\textbf{Example 2:}
\[
f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1], x_2 \in [0,1]
\]
Note that for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive model.

This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.

\section{Convex Functions are Additively Faithful}

Let $\mu$ be a probability measure on $C=[0,1]^s$, $f(x)$ be a multivariate function on $C$. We say that $f$ depends on coordinate $i$ if there exist $x'_i \neq x_i$ such that $f(x'_i, x_{-i})$ and $f(x_i, x_{-i})$ are different functions of $x_{-i}$. (on some measurable set)

\begin{theorem}
Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

Suppose $f$ depends on all coordinates. Let $f_1,...,f_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$

 Then $f_1,...,f_s$ are non-constant functions.
 \end{theorem}

 \begin{lemma}
\label{lem:int_reduction}
Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.

Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$ \\

Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
\end{lemma}

 \begin{proof}

Let $f^*_1,...,f^*_s$ be the minimizers as defined. It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]

Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k}  \\
p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

 \end{proof}

 \begin{proposition}
Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$.

The following are equivalent:
\begin{packed_enum}
\item $f$ does not depends on coordinate $k$
\item For all $x_k$, $\E[ f(X) | x_k] = 0$.
\end{packed_enum}
\end{proposition}

\begin{proof}

The first condition trivially implies the second because $\E f(X) = 0$.\\

Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$. \\

By the assumption that $p$ is a product measure, we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

For every $\mathbf{x}_{-k}$, we define the derivative
\[
g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
\]
$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.\\

We now describe two facts about $g$.

Fact 1. By exchanging limit with the integral, we reason that 
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
\]

Fact 2. Because $f$ is convex, $g(\mathbf{x}_{-k})$ is a component of the subgradient $\partial_{\mathbf{x}} f(0, \mathbf{x}_{-k})$. (the subgradient coincides with the gradient by assumption that $f$ is twice differentiable)

Therefore, using the first order characterization of a convex function, we have
\begin{align*}
f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
\end{align*}

Because, for all $x_k, \mathbf{x}_{-k}$, 
\[
f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
\]
and
\[
\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
\]
we conclude that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.

The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.

By proposition from Horn and Johnson [TODO ref], such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. \\

Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function. It follows therefore that $g = 0$ because it integrates to 0. \\

So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.

\end{proof}

\section{Deterministic Conditions}

\begin{theorem} (Deterministic) \\
The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.\\

For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\

Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:restricted_alternate_opt}. 
Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.\\

Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.\\

Suppose for all $j,k$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.

Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}

\begin{proof}
We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.\\

We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \sum_{k \in S} (\Delta_k d_k - c_k \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.\\

First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness. \\

Now, let us fix $k \in S^c$ and prove that $\hat{d}_k = 0, \hat{c}_k=0$ is an optimal solution.

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k - c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.\\

We now substitute in $\hat{d}_k = 0, \hat{c}_k=0$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.\\

First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
\[
\lambda \mathbf{u} - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
\]

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$. Because we have strict inequality, Lemma [TODO:get wainwright lemma] shows that all solutions must be zero on $S^c$.
\end{proof}

\subsection{Probabilistic Condition: Controlling False Positives}

\begin{theorem} (Probabilistic: Controlling False Positives) \\
Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\ref{opt:alternate_opt} with the $B$-boundness constraint.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt}, with boundedness constraint, is zero on $S^c$.
\end{theorem}

\begin{proof}
The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is not a function of $X_{S^c}$ at all.

\textbf{Step 1.} We first get a high probability bound on $\| \hat{r} \|_\infty$.

\begin{align*}
\hat{r}_i &= Y_i - \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
	&= f^*(X_S^{(i)}) + \epsilon_i - \bar{f^*} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
	&=  f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
\end{align*}
Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.\\

Suppose $\epsilon_i$ is subgaussian with subgaussian norm $\sigma$. For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$. Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.

By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.\\

Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.\\

We know that $|f^*(x)| \leq B$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.

Then $|\bar{f^*}| \leq B$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq 3s B$.

Therefore, taking an union bound, we have that with probability at least $1-\frac{C}{n}$, 
\[
\| \hat{r} \|_\infty \leq (3 s B + c\sigma\sqrt{\log n}) 
\]

\textbf{Step 2.} We now bound $\frac{1}{n} \hat{r}^\tran \max( X, X_{(j)} \mathbf{1})$.

\[
\frac{1}{n} \hat{r}^\tran \max(X, X_{(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_i, X_{(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) + \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

Where $A = \{ i : ord(i) \geq j\}$

We will bound both terms.\\

\textbf{Term 1.}
\[
\trm{Want to bound} \qquad F(X_1,...,X_n) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) 
\]

First, we note that $X_i$ is bounded in the range $[-b,b]$.

We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate. \\

The order of coordinate $i$ in $X$ and $X'$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X)$ to $F(X')$. Therefore,

$$ | F(X_1, ..., X_n) - F(X'_1, ..., X_n) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$

By McDiarmid's inequality therefore, 
\[
P( | F(X) - \E F(X) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
\]

By symmetry and the fact that $\hat{r}$ is centered, $\E F(X) = 0$.

We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$. \\

\textbf{Term 2:}

\[
\trm{Want to bound}   \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
\]

$A$ is a random set and is probabilistically independent of $\hat{r}$.  $\mathbf{1}_A^\tran \hat{r}_A$ is the sum of a sample of $\hat{r}$ without replacement. Therefore, according to Serfling's theorem, with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.

Since $|X_{(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.\\

Now we put everything together.

Taking union bound across $p$ and $n$, we have that with probability at least $1-\delta$,

\[
| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
\]

Taking union bound and substituting in the probabilistic bound on $\|\hat{r}\|_\infty$, we get that with probability at least $1-\frac{C}{n}$,

$| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
\[
 c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn) }
\]

\end{proof}

\subsection{Probabilistic Condition: Controlling False Negatives}

\begin{theorem} (Probabilistic: Controlling False Negatives)\\
Suppose assumptions A1', A2', A3 hold. Suppose we run optimization~\ref{opt:alternate_opt} with both the $B$-boundedness and $L$-Lipschitz constraint. Suppose $f_0$ depends on all $s$-variables.

Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}^s[b,B,L], f_k \trm{ centered} \}$.

Suppose $n$ is large enough such that $c L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \right) < C_{\trm{thresh}}(f_0)$.\\

Then, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$ and therefore, the solution to optimization~\ref{opt:alternate_opt} is non-zero on $S$.
\end{theorem}

\begin{proof}
Let us first sketch out the rough idea of the proof. We know that in the population setting, the best approximate additive function $f^{*s}$ has $s$ non-zero components. We also know that the empirical risk approaches the population risk. Therefore, it cannot be that the empirical risk minimizer maintains a zero component for all $n$; if that were true, then we can construct a feasible solution to the empirical risk optimization, based on $f^{*s}$, that achieves lower empirical risk.

Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \E f_k(X_k) = 0\}$.

Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.\\

By [TODO:population no false negative theorem], $R_s(f^*_s) - R_s(f^*_{(s-1)}) \geq \alpha > 0$.\\

$f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered. Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$. \\

\begin{align*}
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq \| y - f^{*s} + \bar{f}^{*s} \|_n^2  - \| y - f^{*s}\|_n^2 \\
	&\leq 2\|y-f^{*s}\|_n \|\bar{f}^{*s}\|_n + \|\bar{f}^{*s}\|_n^2 
\end{align*}

Because each $f_k^{*s}$ is bounded by $B$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}_k^{*s}| \leq B\sqrt{\frac{1}{cn} \log n}$. By an union bound therefore, with probability at least $1-\frac{C}{n}$, $\|\bar{f}^{*s}\|_n \leq B\sqrt{\frac{1}{cn} \log sn}$.

\begin{align*}
\| y - f^{*s} \|_n &= \| f_0 + w - f^{*s} \|_n \\
	&\leq \| f_0 - f^{*s} \|_n + \|w\|_n \\
\end{align*}

$f_0 - f^{*s}$ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$. Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.

So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
\[
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})|\leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
\]

Suppose $\hat{f}$ has at most $s-1$ non-zero components. Then
\begin{align*}
\hat{R}_s( \hat{f}) &\geq R_s(\hat{f}) - \tau_n \\
	&\geq R_s(f^{*(s-1)}) - \tau_n \\
	&\geq R_s(f^{*s}) + \alpha - \tau_n \\
	&\geq \hat{R}_s(f^{*s}) + \alpha - 2 \tau_n \\
	&\geq \hat{R}_s(f^{*s} - \bar{f}^{*s}) -\tau'_n + \alpha - 2\tau_n 
\end{align*}
Where $\tau_n$ is the deviation between empirical risk and true risk and $\tau'_n$ is the approximation error incurred by empirically sampling $f^{*s}$.

Adding and subtracting $ \lambda_n \rho_n(f^{*s} - \bar{f}^{*s})$ and $ \lambda_n \rho_n(\hat{f})$, we arrive at the conclusion that
\[
\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{f}) \geq \hat{R}_s(f^{*s} - \bar{f}^{*s}) + \lambda_n \rho_n(f^{*s} - \bar{f}^{*s}) - ( \lambda_n \rho_n(f^{*s} - \bar{f}^{*s}) + \lambda_n \rho_n(\hat{f}) ) -\tau'_n + \alpha - 2 \tau_n
\]

$\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $L$. By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.\\

$|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2L \lambda_n$.\\

$\tau'_n$, as shown above, is at most $2sB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.

For $n$ large enough such that
\[
c\max(L\lambda_n,  bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
\]
we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction.

\end{proof}

%

\begin{theorem}
\label{thm:uniform_risk_deviation}
For all $n > n_0$, we have that, with probability at least $1 - \frac{C}{n}$, 
\[
\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq B\sigma(B+\sigma)Lb\sqrt{ \frac{1}{cn^{4/5}} s^5 \log sn}
\]
\end{theorem}

\begin{proof}

Let $\mathcal{C}_0^{s}[b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}^s[b,B,L]$.

For all $f \in \mathcal{C}^s[b,B,L]$,
\[
\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
\]
where $f' \in \mathcal{C}_0^s[b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\

We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.

\begin{align*}
|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 + w - f \|_n^2 - \| f_0 + w - f' \|_n^2| \\
	&\leq 2 \langle f_0 + w , f' - f \rangle_n + \| f \|_n^2 - \| f' \|_n^2\\
	&\leq 2 \| f_0 + w \|_n \| f' - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
\end{align*}

$\| f_0 + w \|_n \leq \| f_0 \|_n + \|w \|_n$. $\| w \|^2_n = \frac{1}{n}\sum_{i=1}^n w_i^2$ is the average of subexponential random variables. Therefore, for all $n$ larger than some absolute constant $n_0$, with probability at least $1-\frac{C}{n}$, $|\|w\|^2_n - \E|w|^2 | < \sigma^2 \sqrt{\frac{1}{cn} \log n}$. The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$. \\

$\|f_0\|^2_n$ is the average of random variables bounded by $B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E |f_0(X)|^2 | \leq B^2\sqrt{ \frac{1}{cn} \log n}$.

Since $\E|w|^2 \leq c\sigma^2$ and $\E| f_0(X)|^2 \leq B^2$, we have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 + w \|_n \leq c(B+\sigma)$.\\

$\| f' - f \|_\infty \leq \epsilon$ implies that $\| f' - f\|_n \leq \epsilon$. And therefore, $\| f \|_n - \|f'\|_n \leq \| f - f' \|_n \leq \epsilon$. \\

$f,f'$ are all bounded by $sB$, and so $\|f \|_n, \| f' \|_n \leq sB$.\\

Thus, we have that, for all $n > n_0$,
\begin{align}
|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation1}
\end{align}
with probability at least $1-\frac{C}{n}$.\\

Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
\begin{align}
|R_s(f') - R_s(f)| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation2}
\end{align}

Lastly, we bound $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} \hat{R}_s(f') - R_s(f')$.

For a fixed $f'$, we have that, by definition
\[
\| f_0 + w - f' \|_n^2 = \| f_0 - f'\|_n^2 + 2 \langle w, f_0 - f'\rangle_n + \| w \|_n^2 \\
\]
Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $4(sB)^2$.

Using Hoeffding Inequality then, we know that the probability $| \| f_0 - f' \|_n^2 - \E(f_0(X) - f '(X))^2 | \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$. \\

Consider now the term $2 \langle w, f_0 - f' \rangle_n \coloneqq \frac{2}{n} \sum_{i=1}^n w_i ( f_0(X^{(i)}) - f'(X^{(i)}))$. We note that $w_i$ and $X^{(i)}$ are independent, $w_i$ is subgaussian.

The $n$-dimensional vector $\{ \frac{1}{n} ( f_0(X^{(i)}) - f'(X^{(i)})) \}_i$ has norm at most $\frac{sB}{\sqrt{n}}$. Therefore, $|2 \langle w, f_0 - f' \rangle_n | \geq t$ with probability at most $C \exp( - c n t^2 \frac{1}{\sigma^2(sB)^2})$. \\

The last term $\| w \|_n^2 = \frac{1}{n} \sum_{i=1}^n w_i^2$. Using subexponential concentration, we know that $ |\| w \|_n^2 - \E|w|^2 | \geq t$ occurs with probability at most $C \exp( - c n \frac{1}{\sigma^2} )$ for $n$ larger than some $n_0$.\\

Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
\[
C \exp( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} )
\]
for all $n > n_0$.

Restating, we have that with probability at most $1- \frac{1}{n}$, the deviation is at most 
\begin{align}
\sqrt{ \frac{1}{cn} \sigma^2 (sB)^4 \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
\end{align}
Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} becomes $\sqrt{ \frac{1}{cn^{4/5}} \sigma^2 s^5 B^4 \log Cn}$.

Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (B+\sigma)$.

\end{proof}

\section{Supporting Technical Results}

\subsection{Concentration of Measure}

\textbf{Sub-Exponential} random variable is the square of a subgaussian random variable.

\begin{proposition} 
Let $X_1,...,X_N$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
\[
P( | \frac{1}{N} \sum_{i=1}^N X_i | \geq \epsilon) \leq
	2 \exp \left[ -c N \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) \right]
\]
where $c > 0$ is an absolute constant.
\end{proposition}

For uncentered subexponential random variables, we can use the following fact. If $X_i$ subexponential with scale $K$, then $X_i - \E[X_i]$ is also subexponential with scale at most $2K$.

\textbf{Restating}. We can set
\[
c \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) = \frac{1}{N} \log \frac{1}{\delta}.
\]
Thus, with probability at least $1-\delta$, the deviation at most
\[
K \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}},  \frac{1}{cn} \log \frac{C}{\delta} \right)
\]

\begin{corollary}
Let $w_1,...,w_n$ be $n$ independent subgaussian random variables with subgaussian scale $\sigma$.

Then, for all $n > n_0$, with probability at least $1- \frac{1}{n}$,
\[
\frac{1}{n} \sum_{i=1}^n w_i^2 \leq c \sigma^2 
\]
\end{corollary}

\begin{proof}
Using the subexponential concentration inequality, we know that, with probability at least $1-\frac{1}{n}$,

\[
| \frac{1}{n} \sum_{i=1}^n w_i^2 - \E w^2 | \leq \sigma^2 \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}}, \frac{1}{cn}\log \frac{C}{\delta} \right)
\]

First, let $\delta = \frac{1}{n}$. Suppose $n$ is large enough such that $ \frac{1}{cn} \log Cn < 1$. Then, we have, with probability at least $1-\frac{1}{n}$,
\begin{align*}
 \frac{1}{n} \sum_{i=1}^n w_i^2 &\leq c\sigma^2 (1+\sqrt{\frac{1}{cn} \log Cn}) \\
		&\leq 2 c \sigma^2
 \end{align*}

\end{proof}

\subsubsection{Sampling Without Replacement}

\begin{lemma} (Serfling) 
Let $x_1,..., x_N$ be a finite list, $\bar{x} = \mu$. Let $X_1,...,X_n$ be sampled from $x$ without replacement.

Let $b = \max_i x_i$ and $a = \min_i x_i$. Let $r_n = 1- \frac{n-1}{N}$. Let $S_n = \sum_i X_i$.
Then we have that
\[
P( S_n - n \mu \geq n \epsilon) \leq \exp( - 2 n \epsilon^2 \frac{1}{r_n (b-a)^2})
\]
\end{lemma}

\begin{corollary}
Suppose $\mu = 0$. 
\[
P( \frac{1}{N} S_n \geq \epsilon) \leq \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
\]

And, by union bound, we have that
\[
P( | \frac{1}{N} S_n| \geq \epsilon) \leq 2 \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
\]

\end{corollary}

A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.s

\begin{proof}
\[
P( \frac{1}{N} S_n \geq \epsilon) = P( S_n \geq \frac{N}{n} n \epsilon) \leq \exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} ) 
\]

We note that $r_n \leq 1$ always, and $n \leq N$ always. 
\[
\exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} )  \leq \exp( - 2 N \epsilon^2 \frac{1}{(b-a)^2})
\]
This completes the proof.

\end{proof}

\subsection{Covering Number for Lipschitz Convex Functions}

\begin{definition}
$\{ f_1,..., f_N\} \subset \mathcal{C}[b,B,L]$ is an $\epsilon$-covering of $\mathcal{C}[b,B,L]$ if for all $f \in \mathcal{C}[b,B,L]$, there exist $f_i$ such that $\| f - f_i \|_\infty \leq \epsilon$.

We define $N_\infty( \epsilon, \mathcal{C}[b,B,L])$ as the size of the minimum covering.
\end{definition}

\begin{lemma} (Bronshtein 1974)
\[
\log N_\infty (\epsilon, \mathcal{C}[b,B,L]) \leq C\left( \frac{bBL}{\epsilon} \right)^{1/2}
\]
For some absolute constant $C$.
\end{lemma}

\begin{lemma}
\[
\log N_\infty( \epsilon, \mathcal{C}^s[b,B,L])  \leq C s \left(\frac{bBLs}{\epsilon}\right)^{1/2}
\]
For some absolute constant $C$.
\end{lemma}

\begin{proof}
Let $f = \sum_{k=1}^s f_k$ be a convex additive function. Let $\{ f'_k \}_{k=1,..,s}$ be $k$ functions from a $\frac{\epsilon}{s}$ $L_\infty$ covering of $\mathcal{C}[b,B,L]$.

Let $f' \coloneqq = \sum_{k=1}^s f'_k$, then 
\[
\| f' - f \|_{\infty} \leq \sum_{k=1}^s \| f_k - f'_k \|_\infty \leq s \frac{\epsilon}{s} \leq \epsilon
\]

Therefore, a product of $s$ $\frac{\epsilon}{s}$-coverings of univariate functions induces an $\epsilon$-covering of the additive functions.
\end{proof}

\end{document}

### 2013-09-29 tex/scam/additive_faithful.tex
first init

\section{Additive Faithfulness}

The additive approximation may mark a relevant variable as
irrelevant. Such mistakes are inherent to the approximation and may
persist even with infinite
samples.  Lemma~\ref{lem:general_int_reduction} below provides
examples of errors made by the additive approximations that minimize
the $L_2$ distance.

\begin{lemma}
\label{lem:general_int_reduction}
Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let
$X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
integrable function and suppose, without loss of generality, that $\E f(X) = 0$.
Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E \bigl( f(X) -
\sum_{k=1}^s f_k(X_k) \bigr)^2 \,:\, \E f_k(X_k) = 0\}$. Then $f^*_k(x_k) = \E[ f(X) \given x_k]$ is unique.
\end{lemma}

Lemma~\ref{lem:general_int_reduction} follows from the stationarity
condition of the optimal solution. If $F$ is the uniform distribution,
then $f^*_k(x_k) = \int_{\mathbf{x}_{-k}} f(x_k, \mathbf{x}_{-k})
d\mathbf{x}_{-k}$.

\begin{example} We give two examples of additive unfaithfulness under
  the uniform distribution. First, consider the following function:
\[
\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
\]
For all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all
$x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$. An additive approximation
would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
\[
\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1],\; x_2 \in [0,1].
\]
For all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive approximation. This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.
\end{example}

\begin{figure}[htp]
\vskip-10pt
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		{\includegraphics[width=0.75\textwidth]{figs/sine_wave_funct3}}
		\caption{egg carton}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		{\includegraphics[width=0.75\textwidth]{figs/tilting_slope_funct3}}
		\caption{tilting slope}
	\end{subfigure}

\caption{Two additively unfaithful functions. Relevant variables are
  zeroed out under an additive approximation because every ``slice''
  of the function integrates to zero.}
\vskip-10pt
\end{figure}

It is important to understand the kind of functions for which the
additive approximation can accurately capture all of the relevant variables.
We call this property \emph{additive faithfulness}.

\begin{definition}
  Let $\mathbf{C}=[0,1]^s$, and $f:\mathbf{C}\rightarrow \R$. We say
  that $f$ \emph{depends on} coordinate $k$ if there exist $x'_k \neq
  x_k$ such that $f(x'_k, \mathbf{x}_{-k})$ and $f(x_k,
  \mathbf{x}_{-k})$ are different functions of $\mathbf{x}_{-k}$.

Let $F$ be a probability distribution on $\mathbf{C}$ and
assume without loss of generality that $\E f(X) = 0$. Let 
$$\ds f^*_1,...,f^*_s \coloneqq \arg\min \Bigl\{ \E ( f(X) - \sum_{k=1}^s
f_k(X_k) )^2 \,:\, \E f_k(X_k) = 0, \forall k\Bigr\}.$$
We say that $f$ is \emph{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
\end{definition}
% We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^s$, then $f$
% is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.

Remarkably, under product distributions, a convex multivariate function can always be faithfully approximated by an additive function.

\begin{theorem}
\label{thm:convex_faithful}
Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p$. If $f$ is convex and twice differentiable, then $f$ is additively faithful under $F$.
\end{theorem}

We give the full proof in Section~\ref{sec:faithful_proof} of the
Appendix, but pause here to provide some intuition. From
Lemma~\ref{lem:general_int_reduction}, we know intuitively that the
additive approximation zeroes out $k$ when, fixing $x_k$, every
``slice'' of $f$ integrates to zero. We prove
Theorem~\ref{thm:convex_faithful} by showing that ``slices'' of convex
functions that integrate to zero cannot be ``glued'' together while
still maintaining convexity.

Theorem~\ref{thm:convex_faithful} plays an important role in our
sparsistency analysis, in which we prove that the additive
approximation is variable selection consistent (or ``sparsistent'') \emph{even when the true function is not
additive.}

\begin{remark}
  We assume twice differentiability in
  Theorem~\ref{thm:convex_faithful} to simplify the proof. We believe
  this smoothness condition is not necessary because every non-smooth
  convex function can be approximated arbitrarily well by a smooth
  one.  Without restrictions on the distribution, a convex
  function may not be additively faithful. Intuitively, an arbitrarily shaped
  density $p$
  may ``undo'' the convexity of $f$ so that the product
  $p(\mathbf{x}) \, f(\mathbf{x})$ resembles an egg carton or a
  tilting slope.  With appropriate conditions on the density $p$,
  however, it is possible to relax the independence assumption.  We leave this to
  future work.
\end{remark}

### 2013-09-29 tex/scam/appendix.tex
first init

--- 2013-09-29 tex/result.tex
@@
-\documentclass{article}
-\usepackage{minx_math}
-\usepackage{framed, mathtools, epstopdf,subfigure}
+\section*{Appendix}
 
-% eqn:alternate_opt
+\subsection{Proof of Additive Faithfulness}
+\label{sec:faithful_proof}
 
-\begin{document}
-
-\section{Setting and Notations}
-
-\textbf{Setting:}
-\begin{packed_enum}
-\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
-\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
-\item Let $S \subset \{1,...,p\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$ and let $s \coloneqq |S|$.
-\end{packed_enum}
-
-\textbf{Assumptions:}
-\begin{packed_enum}
-\item[A1] Suppose that $X_S, X_{S^c}$ are independent.
-\item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
-\item[A2] Suppose that $\|f_0\|_\infty \leq B$.
-\item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
-\item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
-\end{packed_enum}
-
-\textbf{Notation:}
-$\mathbf{1}_n$ is an all-ones vector of dimension $n$.
-If $X \in \R^p$ and $S \subset \{1,...,p\}$, then $X_S$ is a subvector of $X$ restricted to coordinates in $S$.
-Let $v \in \R^n$, then $v_{(1)}$ denotes the largest coordinate of $v$ in magnitude, $v_{(j)}$ denotes the $j$-th largest.
-\\
-
-\subsection{Reformulation}
-
-Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large. Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\
-
-Then  
-\begin{align*}
-\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
-\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
-\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
-\end{align*}
-
-We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
-\[
-D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
-\]
-
-And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.
-
-\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment.
-$\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$.
-The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\
-
-$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.
-
-\[
-\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
-\]
-
-\begin{align*}
-\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
- &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
- &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
-\end{align*}
-
-\[
-\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
-\]
-
-Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write
-
-\[
-\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
-\]
-
-With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\
-
-\begin{align}
-\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:alternate_opt} \\
-\trm{s.t. $\forall k$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
-	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
-	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
-	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
-\end{align}
-
-We will impose the boundness and smoothness constraints only in our theoretical analysis when we control the rate of false negatives.
-
-\begin{align}
-\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k \in S} ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:restricted_alternate_opt} \\
-\trm{s.t. $\forall k \in S$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
-	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
-	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
-	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
-\end{align}
-
-In the proof, we will reason with the solution of the optimization \ref{opt:alternate_opt} when we restricted $k$ to be only in the subset $S$.
-This is of course a theoretical construct only and we refer to it as \emph{restricted regression}.\\
-
-Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w \|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.
-
-For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - g \|_n^2$ and define $R_s(g) \coloneqq \E | f_0(X)  + w - g(X) |^2$.
-
-For an additive function $g$, define $\rho_n(g) = \sum_{k=1}^s \| \partial g_k \|_\infty$.
-Because we use outer approximation in our optimization program, we define $\ds \| \partial g_k\|_\infty \coloneqq \max_{i=1,...,n-1} |\frac{ g_k(X^{(i)}) - g_k(X^{(i+1)})}{ X^{(i)} - X^{(i+1)}}|$.
-
-Let $\mathcal{C}[b,B,L]$ be the set of 1 dimensional convex functions on $[-b,b]$ that are bounded by $B$ and $L$-Lipschitz.
-
-Let $\mathcal{C}^s[b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
-\[
-\mathcal{C}^s[b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
-\]
-
-\section{Functions Which Are Not Additively Faithful}
-
-\textbf{Example 1:}
-\[
-f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
-\]
-Note that for all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$.
-An additive model would set $f_1 = 0$ and $f_2 = 0$.
-
-\begin{figure}[htp]
-\subfigure[Example 1]{\includegraphics[scale=0.5]{../code/figs/sine_wave_funct.eps}}
-\subfigure[Example 2]{\includegraphics[scale=0.4]{../code/figs/rising_slope_funct.eps}}
-\end{figure}
-
-\textbf{Example 2:}
-\[
-f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1], x_2 \in [0,1]
-\]
-Note that for all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive model.
-
-This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.
-
-\section{Convex Functions are Additively Faithful}
-
-Let $\mu$ be a probability measure on $C=[0,1]^s$, $f(x)$ be a multivariate function on $C$.
-We say that $f$ depends on coordinate $i$ if there exist $x'_i \neq x_i$ such that $f(x'_i, x_{-i})$ and $f(x_i, x_{-i})$ are different functions of $x_{-i}$.
-(on some measurable set)
-
-\begin{theorem}
-Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
-
-Suppose $f$ depends on all coordinates. Let $f_1,...,f_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
-
- Then $f_1,...,f_s$ are non-constant functions.
- \end{theorem}
+We start with a lemma similar to Lemma~\ref{lem:general_int_reduction} and whose proofs are identical.
 
@@
 \label{lem:int_reduction}
-Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.
+Let $F$ be a product distribution on $C=[0,1]^s$ with density function $p$. Let $f: C \rightarrow \R$ be a convex function. Suppose that $\E f(X) = 0$.
 
-Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$ \\
+Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
 
-Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
+Then $f^*_k(x_k) = \E[ f(X) \given x_k]$.
 \end{lemma}
@@
 
-Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
+Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$, for all $x_k$,  uniquely minimizes 
 \[
@@
 \]
+If this is true, then the function $x_k \mapsto \E[ f(X) \given x_k]$ is the unique $f^*_k(x_k)$ that minimizes the expected square error.
 
-Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
+Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
 \begin{align*}
 \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\  
-p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
+   p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\
+f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(\mathbf{x}) d \mathbf{x}_{-k} 
  \end{align*}
+Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption.
+The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.
+
+The square error objective is strongly convex.
+The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
+Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ]$ is unique.
 
 Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex.
-The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
 
@@
 
+ The next proposition, combined with the previous Lemma, proves Theorem~\ref{thm:convex_faithful}.
+
  \begin{proposition}
-Let $p$ be a product probability distribution on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
+Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
 
@@
 
-The first condition trivially implies the second because $\E f(X) = 0$.\\
+The first condition trivially implies the second because $\E f(X) = 0$.
 
-Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$. \\
+Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$.
 
-By the assumption that $p$ is a product measure, we know that, for all $x_k$,
+By the assumption that , we know that, for all $x_k$,
 \begin{align*}
-p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
-		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
+p(x_k) \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
 \end{align*}
@@
 \]
-$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.\\
+$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
 
@@
 
-Fact 1. By exchanging limit with the integral, we reason that 
+Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
 \[
@@
 
-Because, for all $x_k, \mathbf{x}_{-k}$, 
+For all $x_k, \mathbf{x}_{-k}$, 
 \[
@@
 \]
-we conclude that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
+Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
 
@@
 
-By proposition from Horn and Johnson [TODO ref], such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero. \\
+By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero.
+(to prove this, one can first work with a 2 by 2 matrix and then use the fact that every principal submatrix of a PSD matrix must be PSD)
 
@@
 It follows therefore that $g = 0$ because it integrates to 0.
-\\
 
@@
 
-\section{Deterministic Conditions}
+ \subsection{Proof of the Deterministic Condition for Sparsistency}
+ \label{sec:deterministic_proof}
 
-\begin{theorem} (Deterministic) \\
-The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.\\
+ We restate Theorem~\ref{thm:deterministic} first for convenience.
 
-For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\
+\begin{theorem} 
+The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.
 
-Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:restricted_alternate_opt}. 
-Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.\\
+For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$.
 
-Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.\\
+Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:alternate_opt}. 
+Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
+
+Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.
 
@@
 \begin{proof}
-We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.\\
+We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.
 
@@
 \]
-where $r_k \coloneqq Y - \sum_{k \in S} (\Delta_k d_k - c_k \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.\\
+where $r_k \coloneqq Y - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.
 
-First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness. \\
+First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness.
 
@@
 \begin{align*}
-\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
-\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k - c_k \mathbf{1}) + \gamma_k
+\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
+\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
 \end{align*}
-In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.\\
+In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.
 
@@
 \end{align*}
-where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.\\
+where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.
 
@@
 \]
-then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$.
-Because we have strict inequality, Lemma [TODO:get wainwright lemma] shows that all solutions must be zero on $S^c$.
+then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.
+
+Because we have strict inequality in the above equation, Lemma 1 from ~\cite{Wain:09a} show that all solutions must be zero on $S^c$.
 \end{proof}
 
-\subsection{Probabilistic Condition: Controlling False Positives}
+ \subsection{Proof of False Positive Control}
+ \label{sec:false_positive_proof}
 
-\begin{theorem} (Probabilistic: Controlling False Positives) \\
-Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\ref{opt:alternate_opt} with the $B$-boundness constraint.
+ We first restate the theorem for convenience.
+
+\begin{theorem} 
+Suppose assumptions A1, A2, A3 hold.
 
@@
 \]
-And therefore, the solution to the optimization~\ref{opt:alternate_opt}, with boundedness constraint, is zero on $S^c$.
+And therefore, the solution to the optimization~\ref{opt:alternate_opt} is zero on $S^c$.
 \end{theorem}
@@
 \begin{proof}
-The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is not a function of $X_{S^c}$ at all.
+The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is only dependent on $X_{S}$.
 
@@
 \end{align*}
-Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.\\
+Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.
 
-Suppose $\epsilon_i$ is subgaussian with subgaussian norm $\sigma$.
+$\epsilon_i$ is subgaussian with subgaussian norm $\sigma$.
 For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$.
@@
 
-By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.\\
+By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.
 
-Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.\\
+Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.
 
@@
 \[
-\frac{1}{n} \hat{r}^\tran \max(X, X_{(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_i, X_{(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) + \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
+\frac{1}{n} \hat{r}^\tran \max(X, X_{(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_i, X_{(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) \geq j) + \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
 \]
 
-Where $A = \{ i : ord(i) \geq j\}$
+Where $A = \{ i : ord(i) \geq j\}$ and $ord(i)$ is the order of sample $i$ where $(1)$ is the smallest element.
 
-We will bound both terms.\\
+We will bound both terms.
 
@@
 \[
-\trm{Want to bound} \qquad F(X_1,...,X_n) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) < j) 
+\trm{Want to bound} \qquad F(X_1,...,X_n) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) \geq j) 
 \]
@@
 
-We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate. \\
+We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate.
 
@@
 
-We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$. \\
+We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$.
 
@@
 $\mathbf{1}_A^\tran \hat{r}_A$ is the sum of a sample of $\hat{r}$ without replacement.
-Therefore, according to Serfling's theorem, with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
+Therefore, according to Serfling's theorem (Corollary~\ref{cor:serfling}), with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
 
-Since $|X_{(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.\\
+Since $|X_{(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
 
@@
 
-\subsection{Probabilistic Condition: Controlling False Negatives}
+ \subsection{Proof of False Negative Control}
+ \label{sec:false_negative_proof}
 
-\begin{theorem} (Probabilistic: Controlling False Negatives)\\
-Suppose assumptions A1', A2', A3 hold. Suppose we run optimization~\ref{opt:alternate_opt} with both the $B$-boundedness and $L$-Lipschitz constraint. Suppose $f_0$ depends on all $s$-variables.
+ We will use covering number and uniform convergence and will thus need to first introduce some notations.
+
+ Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w \|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.
+
+For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - g(X) |^2$ as the population risk.
+
+For an additive function $g$, define $\rho_n(g) = \sum_{k=1}^s \| \partial g_k \|_\infty$.
+Because we always use the secant linear piece-wise function in our optimization program, we define $\ds \| \partial g_k\|_\infty \coloneqq \max_{i=1,...,n-1} |\frac{ g_k(X^{(i)}) - g_k(X^{(i+1)})}{ X^{(i)} - X^{(i+1)}}|$.
+
+Let $\mathcal{C}[b,B,L]$ be the set of 1 dimensional convex functions on $[-b,b]$ that are bounded by $B$ and $L$-Lipschitz.
+
+Let $\mathcal{C}[s,b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
+\[
+\mathcal{C}[s,b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
+\]
+
+We now restate the theorem in our newly defined notation.
+
+\begin{theorem} 
+Suppose assumptions A1', A2', A3 hold. Suppose $f_0$ depends on all $s$-variables.
 
@@
 
-Suppose $n$ is large enough such that $c L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \right) < C_{\trm{thresh}}(f_0)$.\\
+Suppose $n$ is large enough such that $c L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \right) \rightarrow 0$.
 
-Then, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$ and therefore, the solution to optimization~\ref{opt:alternate_opt} is non-zero on $S$.
+Then, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
 \end{theorem}
@@
 We know that in the population setting, the best approximate additive function $f^{*s}$ has $s$ non-zero components.
-We also know that the empirical risk approaches the population risk.
+We also know that the empirical risk approaches the population risk uniformly.
 Therefore, it cannot be that the empirical risk minimizer maintains a zero component for all $n$; if that were true, then we can construct a feasible solution to the empirical risk optimization, based on $f^{*s}$, that achieves lower empirical risk.
@@
 
-Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.\\
+Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.
 
-By [TODO:population no false negative theorem], $R_s(f^*_s) - R_s(f^*_{(s-1)}) \geq \alpha > 0$.\\
+By Theorem~\ref{thm:convex_faithful}, $R_s(f^*_s) - R_s(f^*_{(s-1)}) \geq \alpha > 0$.
 
@@
 Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$.
-\\
 
@@
 $\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $L$.
-By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.\\
+By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.
 
-$|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2L \lambda_n$.\\
+$|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2L \lambda_n$.
 
@@
 
-\begin{theorem}
+\begin{theorem} (Uniform Risk Deviation)
 \label{thm:uniform_risk_deviation}
@@
 
-Let $\mathcal{C}_0^{s}[b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}^s[b,B,L]$.
+Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$.
 
@@
 \]
-where $f' \in \mathcal{C}_0^s[b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\
+where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\
 
-We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
+Step 1. We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
 
@@
 The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$.
-\\
 
@@
 
-Since $\E|w|^2 \leq c\sigma^2$ and $\E| f_0(X)|^2 \leq B^2$, we have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 + w \|_n \leq c(B+\sigma)$.\\
+Since $\E|w|^2 \leq c\sigma^2$ and $\E| f_0(X)|^2 \leq B^2$, we have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 + w \|_n \leq c(B+\sigma)$.
 
-$\| f' - f \|_\infty \leq \epsilon$ implies that $\| f' - f\|_n \leq \epsilon$. And therefore, $\| f \|_n - \|f'\|_n \leq \| f - f' \|_n \leq \epsilon$. \\
+$\| f' - f \|_\infty \leq \epsilon$ implies that $\| f' - f\|_n \leq \epsilon$. And therefore, $\| f \|_n - \|f'\|_n \leq \| f - f' \|_n \leq \epsilon$.
 
-$f,f'$ are all bounded by $sB$, and so $\|f \|_n, \| f' \|_n \leq sB$.\\
+$f,f'$ are all bounded by $sB$, and so $\|f \|_n, \| f' \|_n \leq sB$.
 
@@
 \end{align}
-with probability at least $1-\frac{C}{n}$.\\
+with probability at least $1-\frac{C}{n}$.
 
@@
 
-Using Hoeffding Inequality then, we know that the probability $| \| f_0 - f' \|_n^2 - \E(f_0(X) - f '(X))^2 | \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$. \\
+Using Hoeffding Inequality then, we know that the probability $| \| f_0 - f' \|_n^2 - \E(f_0(X) - f '(X))^2 | \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
 
@@
 Therefore, $|2 \langle w, f_0 - f' \rangle_n | \geq t$ with probability at most $C \exp( - c n t^2 \frac{1}{\sigma^2(sB)^2})$.
-\\
 
 The last term $\| w \|_n^2 = \frac{1}{n} \sum_{i=1}^n w_i^2$.
-Using subexponential concentration, we know that $ |\| w \|_n^2 - \E|w|^2 | \geq t$ occurs with probability at most $C \exp( - c n \frac{1}{\sigma^2} )$ for $n$ larger than some $n_0$.\\
+Using subexponential concentration, we know that $ |\| w \|_n^2 - \E|w|^2 | \geq t$ occurs with probability at most $C \exp( - c n \frac{1}{\sigma^2} )$ for $n$ larger than some $n_0$.
 
@@
 
-\section{Supporting Technical Results}
+ \subsection{Supporting Technical Material}
 
-\subsection{Concentration of Measure}
+ \subsubsection{Concentration of Measure}
 
-\textbf{Sub-Exponential} random variable is the square of a subgaussian random variable.
+\textbf{Sub-Exponential} random variable is the square of a subgaussian random variable\cite{vershynin2010introduction}.
 
-\begin{proposition} 
+\begin{proposition} (Subexponential Concentration \cite{vershynin2010introduction})
 Let $X_1,...,X_N$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
@@
 
-\begin{lemma} (Serfling) 
+\begin{lemma} (Serfling \cite{serfling1974probability}) 
 Let $x_1,..., x_N$ be a finite list, $\bar{x} = \mu$. Let $X_1,...,X_n$ be sampled from $x$ without replacement.
@@
 \begin{corollary}
+\label{cor:serfling}
 Suppose $\mu = 0$. 
@@
 
-\subsection{Covering Number for Lipschitz Convex Functions}
+\subsubsection{Covering Number for Lipschitz Convex Functions}
 
@@
 \end{proof}
-
-\end{document}

### 2013-09-29 tex/scam/icml14/example_paper.tex
first init

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2014 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2014,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2014} with
% \usepackage[nohyperref]{icml2014} above.
\usepackage{hyperref}

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2014} 
% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2014}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2014}

\begin{document}

\twocolumn[
\icmltitle{Submission and Formatting Instructions for the Thirty-first \\ 
           International Conference on Machine Learning (ICML 2014)}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2014
% package.
\icmlauthor{Your Name}{email@yourdomain.edu}
\icmladdress{Your Fantastic Institute,
            314159 Pi St., Palo Alto, CA 94306 USA}
\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
\icmladdress{Their Fantastic Institute,
            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

\vskip 0.3in
]

\begin{abstract} 
There are two review cycles for ICML 2014, with full paper submissions 
due on October 4, 2013 and January 31, 2014. Reviewing 
will be blind to the identities of the authors, and therefore identifying
information must not appear in any way in papers submitted for review. 
Submissions must be in PDF, with an 8 page length limit ( 9 pages are allowed if the 9-th page contains \emph{only} references).
\end{abstract}

\section{Electronic Submission}
\label{submission}

As in the past few years, ICML will rely exclusively on
electronic formats for submission and review.

\subsection{Templates for Papers}

Electronic templates for producing papers for submission are available
for \LaTeX\/ and Microsoft Word. Templates are accessible on the World
Wide Web at:\\
\textbf{\texttt{http://icml.cc/2014/}}

\noindent
Send questions about these electronic templates to
\texttt{program@icml.cc}.

The formatting instructions below will be enforced for initial submissions and camera-ready copies. 
\begin{itemize}
\item The maximum paper length is 8 pages excluding references, and 
9 pages including references.
\item Do not alter the style template; in particular, do not compress the paper format 
by reducing the vertical spaces.
\item Do not include author information or acknowledgments in your
  initial submission. 
\item Place figure captions {\em under} the figure (and omit titles from
  inside the graphic file itself).  Place table captions {\em over}
  the table.
\item References must include page numbers whenever possible and be as
  complete as possible.  Place multiple citations in chronological order.  
\end{itemize}
Please see below for details on each of these items.

\subsection{Submitting Papers}

Submission to ICML 2014 will be entirely electronic, via a web site
(not email).  The URL and information about the submission process
are available on the conference web site at

\textbf{\texttt{http://icml.cc/2014/}}

{\bf Paper Deadline:} The deadline for paper submission to ICML 2014
is at 23:59 Universal Time (3:59 Pacific Daylight Time) on the due dates
(October 4, or January 31, depending on the review cycle).  
If your full submission does not reach us by this time, it will 
not be considered for publication. There is no separate abstract submission.

{\bf Anonymous Submission:} To facilitate blind review, no identifying
author information should appear on the title page or in the paper
itself.  Section~\ref{author info} will explain the details of how to
format this.

{\bf Simultaneous Submission:} ICML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. ICML submissions must not be
submitted to other conferences during ICML's review period. Authors
may submit to ICML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

To ensure our ability to print submissions, authors must provide their
manuscripts in \textbf{PDF} format.  Furthermore, please make sure
that files contain only Type-1 fonts (e.g.,~using the program {\tt
  pdffonts} in linux or using File/DocumentProperties/Fonts in
Acrobat).  Other fonts (like Type-3) might come from graphics files
imported into the document.

Authors using \textbf{Word} must convert their document to PDF.  Most
of the latest versions of Word have the facility to do this
automatically.  Submissions will not be accepted in Word format or any
format other than PDF. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} to format their accepted papers need to
pay close attention to the typefaces used.  Specifically, when
producing the PDF by first converting the dvi output of \LaTeX\ to Postscript
the default behavior is to use non-scalable Type-3 PostScript bitmap
fonts to represent the standard \LaTeX\ fonts. The resulting document
is difficult to read in electronic form; the type appears fuzzy. To
avoid this problem, dvips must be instructed to use an alternative
font map.  This can be achieved with
something like the following commands:\\[0.5em]
{\bf dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi}\\
{\bf ps2pdf paper.ps}\\[0.5em]
Note that it is a zero following the ``-G''.  This tells dvips to use
the config.pdf file (and this file refers to a better font mapping).

Another alternative is to use the \textbf{pdflatex} program instead of
straight \LaTeX. This program avoids the Type-3 font problem, however
you must ensure that all of the fonts are embedded (use {\tt
pdffonts}). If they are not, you need to configure pdflatex to use a
font map file that specifies that the fonts be embedded. Also you
should ensure that images are not downsampled or otherwise compressed
in a lossy way.

Note that the 2014 style files use the {\tt hyperref} package to
make clickable links in documents.  If this causes problems for you,
add {\tt nohyperref} as one of the options to the {\tt icml2014}
usepackage statement.

\subsection{Reacting to Reviews}
We will continue the ICML tradition in which the authors are given the
option of providing a short reaction to the initial reviews. These
reactions will be taken into account in the discussion among the
reviewers and area chairs.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except of
course that the normal author information (names and affiliations)
should be given.  See Section~\ref{final author} for details of how to
format this.

The footnote, ``Preliminary work.  Under review by the International
Conference on Machine Learning (ICML).  Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{31}^{st}$ International Conference on Machine Learning},
Beijing, China, 2014.  JMLR: W\&CP volume 32. 
Copyright 2014 by the author(s).''

For those using the \textbf{\LaTeX} style file, simply change
$\mathtt{\backslash usepackage\{icml2014\}}$ to

\verb|\usepackage[accepted]{icml2014}|

\noindent
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one.  The running title consists of a
single line centered above a horizontal rule which is $1$ point thick.
The running head should be centered, bold and in $9$ point type.  The
rule should be $10$ points above the main text.  For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the {\tt fancyhdr} package which is included in the ICML
2014 style file package.  In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the same format to ensure the printer can
reproduce them without problems and to let readers more easily find
the information that they desire.

\subsection{Length and Dimensions}

Papers must not exceed eight (8) pages, including all figures, tables,
and appendices, but excluding references. When references are included,
the paper must not exceed nine (9) pages. Any submission that exceeds 
this page limit or that diverges significantly from the format specified 
herein will be rejected without review.

The text of the paper should be formatted in two columns, with an
overall width of 6.75 inches, height of 9.0 inches, and 0.25 inches
between the columns. The left margin should be 0.75 inches and the top
margin 1.0 inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times  typeface throughout the text.
%Please use the default typeface (Computer Modern) throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

To facilitate blind review, author information must not appear.  If
you are using \LaTeX\/ and the \texttt{icml2014.sty} file, you may use
\verb+\icmlauthor{...}+ to specify authors.  The author information
will simply not be printed until {\tt accepted} is an argument to the
style file. Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If your are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we 
have shown \ldots'').

Do not anonymize citations in the reference section by removing or
blacking out author names. The only exception are manuscripts that are
not yet published (e.g. under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have 
to be submitted
as Supplementary Material via CMT. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look a the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches
below the bottom rule surrounding the title. The authors' names should
appear in 10~point bold type, electronic mail addresses in 10~point
small capitals, and physical addresses in ordinary 10~point type.
Each author's name should be flush left, whereas the email address
should be flush right on the same line. The author's physical address
should appear flush left on the ensuing line, on a single line if
possible. If successive authors have the same affiliation, then give
their physical address only once.

A sample file (in PDF) with author names is included in the ICML2014 
style file package.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below
the final address. The heading `Abstract' should be centered, bold,
and in 11~point type. The abstract body should use 10~point type, with
a vertical spacing of 11~points, and should be indented 0.25~inches
more than normal on left-hand and right-hand margins. Insert
0.4~inches of blank space after the body. Keep your abstract brief and 
self-contained,
limiting it to one paragraph and no more than six or seven sentences.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{For the sake of readability, footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper. 
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
  Machine Learning Conferences (ICML 1993 -- ICML 2008) and
  International Workshops on Machine Learning (ML 1988 -- ML
  1992). At the time this figure was produced, the number of
  accepted papers for ICML 2008 was unknown and instead estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to help readers visualize
your approach and your results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
{\it after\/} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
Figure~\ref{icml-historical}.  The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left.  You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment {\tt figure*} in \LaTeX), but always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic'' 
environments to format pseudocode. These require 
the corresponding stylefiles, algorithm.sty and 
algorithmic.sty, which are supplied with this package. 
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$} 
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like 
figures, these should be centered, legible, and numbered consecutively. 
However, place the title {\it above\/} the table with at least 
0.1~inches of space before the title and the same after it, as in 
Table~\ref{sample-table}. The table title should be set in 9~point 
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing 
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible 
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\hline
\abovespace\belowspace
Data set & Naive & Flexible & Better? \\
\hline
\abovespace
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
\belowspace
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material that can be typeset, as contrasted 
with figures, which contain graphical material that must be drawn. 
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns, but place two-column tables at the
top or bottom of the page.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic 
facility, use {\tt natbib.sty} and {\tt icml2014.bst} 
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and 
use a hanging indent style, with the first line of the reference flush
against the left margin and subsequent lines indented by 10 points. 
The references at the end of this document give examples for journal
articles \cite{Samuel59}, conference publications \cite{langley00}, book chapters \cite{Newell81}, books \cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, 
technical reports \cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

\subsection{Software and Data}

We strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate.  This can be
done by including a URL in the camera-ready copy.  However, do not
include URLs that reveal your institution or identity in your
submission for review.  Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system.  Note that reviewers are not required to look a this material
when writing their review.

% Acknowledgements should only appear in the accepted version. 
\section*{Acknowledgments}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas, 
and to funding agencies and corporate sponsors that provided financial 
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2014}

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was
% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
% slightly modified from the 2009 version by Kiri Wagstaff and 
% Sam Roweis's 2008 version, which is slightly modified from 
% Prasad Tadepalli's 2007 version which is a lightly 
% changed version of the previous year's version by Andrew Moore, 
% which was in turn edited from those of Kristian Kersting and 
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2013-09-29 tex/scam/nips13/SCAM.tex
first init

\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx,caption,subcaption,amsmath,amsthm,amssymb}
\newcommand{\bds}[1]{\boldsymbol{#1}}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09

\title{Formatting Instructions for NIPS 2013}

\author{
David S.~Hippocampus\thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213 \\
\texttt{hippo@cs.cranberry-lemon.edu} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
(if needed)\\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\maketitle

\begin{abstract}
...
\end{abstract}

\newpage
\section{Sparse Convex Additive Model}
We consider the following nonparametric regression problem
\begin{equation}\nonumber
          y_{i} = h(\bds{x}_{i}) + \epsilon_{i} = \sum_{d=1}^{p}h_{d}(x_{di}) + \epsilon_{i} \quad (i=1,2,\cdots,n)
\end{equation}
where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the response and $\epsilon_{i}$ is the noise. The regression function $h(\cdot)$ is the summation of 
functions $h_{d}(\cdot)$ in each variable dimension. For high-dimensional data, it would be interesting to select the active variables, or equivalently, non-zero $h_{d}(\cdot)$
that contributes to $h(\cdot)$. Without further assumptions, this is the Sparse Additive Model (SpAM). Here we impose an additional constraint that each $h_{d}(\cdot)$ is 
a convex function, which can be represented by its supporting hyperplanes, i.e.,
\begin{equation}\nonumber
      h_{dj} \geq h_{di} + \beta_{di}(x_{dj}-x_{di}) \quad (\forall i,j)
\end{equation}
where $h_{di}\triangleq{}h_{d}(x_{di})$ and $\beta_{di}$ is the subgradient at point $x_{di}$. Hence we can formulate a convex program for the nonparametric regression problem:
\begin{equation}\label{nnp}
     \min_{\bds{h},\bds{\beta}} \ \frac{1}{2n}\sum_{i=1}^{n}(y_{i}-\sum_{d=1}^{p}h_{di})^{2} + \lambda\|\bds{\beta}\|_{\infty,1}  \ \ 
     \textrm{s.t.} \ \sum_{i=1}^{n}h_{di}=0  \  (\forall d), \ \ h_{dj} \geq h_{di} + \beta_{di}(x_{dj}-x_{di}) \  (\forall i,j,d).
\end{equation}
The regularization term $\|\bds{\beta}\|_{\infty,1}$ is used for variable selection, and the equality constraint is an identifiability constraint.

The program (\ref{nnp}) contains $O(n^{2}p)$ constraints,  which is computationally expensive for large scale problems. Since for scalar convex functions, the subgradient
should increase monotonically, thus we can reformulate (\ref{nnp}) with only $O(np)$ constraints as
\begin{equation}\begin{split}\label{np}
       &\min_{\bds{h},\bds{\beta}} \ \frac{1}{2n}\sum_{i=1}^{n}(y_{i}-\sum_{d=1}^{p}h_{di})^{2} + \lambda\sum_{d=1}^{p}\|\bds{\beta}_{d\cdot}\|_{\infty} \\
       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{di}=0, \ h_{d(i+1)} = h_{d(i)} + \beta_{d(i)}(x_{d(i+1)}-x_{d(i)}), \ \beta_{d(i+1)} \geq \beta_{d(i)} \ (\forall d, i)
\end{split}\end{equation}
Here $\{(1),(2),\cdots,(n)\}$ is a reordering of $\{1,2,\cdots,n\}$ such that $x_{d(1)}\leq{}x_{d(2)}\leq\cdots\leq{}x_{d(n)}$
It is easy to verify that the constraints in (\ref{np}) satisfies the constraints in (\ref{nnp}), as
\begin{eqnarray}
  \nonumber \forall j\geq{}i, h_{d(j)}-h_{d(i)} & = \sum\limits_{t=i}^{j-1}(h_{d(t+1)}-h_{d(t)}) = \sum\limits_{t=i}^{j-1}\beta_{d(t)}(x_{d(t+1)}-x_{d(t)})\\ \nonumber
                                                                             & \geq \beta_{d(i)}\sum\limits_{t=i}^{j-1}(x_{d(t+1)}-x_{d(t)}) = \beta_{d(i)}(x_{d(j)}-x_{d(i)}) \\
  \nonumber \forall j<i,         h_{d(j)}-h_{d(i)} &= \sum\limits_{t=j}^{i-1}(h_{d(t)}-h_{d(t+1)}) = \sum\limits_{t=j}^{i-1}\beta_{d(t)}(x_{d(t)}-x_{d(t+1)}) \\ \nonumber
                                                                             & \geq \beta_{d(i)}\sum\limits_{t=j}^{i-1}(x_{d(t)}-x_{d(t+1)}) = \beta_{d(i)}(x_{d(j)}-x_{d(i)}), 
\end{eqnarray}
hence $h_{d(j)}\geq{}h_{d(i)}+\beta_{d(i)}(x_{d(j)}-x_{d(i)}) \ (\forall j)$, which means $\beta_{d(i)}$ is really a subgradient at point $x_{d(i)}$. 
We call the model (\ref{np}) Sparse Convex Additive Model (SCAM). Notice that if we replace $\beta_{d(i+1)} \geq \beta_{d(i)}$ with
$\beta_{d(i+1)}=\beta_{d(i)}$, then it reduces to LASSO.

\section{Optimization}
SPAM in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints. 
Directly applying a QP solver would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
in different feature dimensions are only coupled in the term $(y_{i}-\sum_{d=1}^{p}h_{di})^{2}$. Hence we can apply the coordinate descent method,
where in each step we solve the following QP subproblem for $\{\bds{h}_{d\cdot},\bds{\beta}_{d\cdot}\}$ with other variables fixed:
\begin{equation}\begin{split}\nonumber
       &\min_{\bds{h}_{d\cdot},\bds{\beta}_{d\cdot},\gamma_{d}} \ \frac{1}{2n}\sum_{i=1}^{n}((y_{i}-\sum_{r\neq{d}}h_{ri})-h_{di})^{2} + \lambda\gamma_{d} \\
        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{di}=0, \ h_{d(i+1)} = h_{d(i)} + \beta_{d(i)}(x_{d(i+1)}-x_{d(i)}), \ \beta_{d(i+1)} \geq \beta_{d(i)}, \ -\gamma_{d}\leq\beta_{d(i)}\leq\gamma_{d} \ (\forall i).
\end{split}\end{equation}
The extra variable $\gamma_{d}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
which can be solved efficiently using optimization packages (e.g., MOSEK).  We cycle through all feature dimensions ($d$) from $1$ to $p$ multiple times until convergence.
Empirically we observe that the algorithm converges in only a few cycles. We also implemented an ADMM solver for (\ref{np}), but found that it is not as efficient as this QP solver.

\newpage
\section{Experiments}
\subsection{Simulations}
Support recovery result goes here ...

\subsection{Boston housing data}
We take the Boston housing data~\cite{?} as a real example. This data set
contains 13 covariates, 506 samples and one response variable, which is
the housing values in suburb of Boston. The data and detailed description
can be found on the UCI website~\cite{?}.

We first use all $n=506$ samples (with normalization) to train SCAM, using
a set of candidate $\{\lambda^{(t)}\}$ with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
we obtain a vector $\|\bds{\beta}^{(t)}\|_{\infty}$ of dimension $p=13$. And non-zero
elements in this vector indicates the variables selected using $\lambda^{(t)}$. 
We then plot $\|\bds{\beta}^{(t)}\|_{\infty}$ versus the normalized
norm $\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$ in Figure \ref{SCAM}.
As a comparison we plot the LASSO/LARS result in a similar way in Figure \ref{LASSO}.
From the figure we observe that the first three variables selected by SCAM (corresponding to $\lambda^{(t)}=0.1$) 
and LASSO are the same: LSTAT, RM and PTRATIO, which is consistent with previous findings~\cite{?}.
We then refit SCAM with only these three variables without regularization, and plot the inferred additive
functions in Figure \ref{Convex}. As can be seen, these functions contain clear nonlinear effects which cannot be captured
by LASSO. The shapes of these functions are also in good agreement with those obtained by SpAM~\cite{?}.

Next, in order to quantitatively  study the predictive performance, we run 10 times 5-fold cross validation, following
the same procedure described above (training, variable selection and refitting), and plot the mean and standard
deviation of the predictive MSE in Figure \ref{MSE}. Since for SCAM, the same $\lambda^{(t)}$ may lead to
slightly different number of selected features in different folds and runs, the x-axis (average number of selected features)
for SCAM is not necessarily an integer. Nevertheless, the figure clearly shows that SCAM has a much lower predictive MSE than LASSO. 
We also compare the performance of SCAM with that of Additive Forward Regression (AFR) presented in~\cite{Xi}, and found that they are similar.
The main advantages of SCAM compared with AFR and SpAM are 1) There are no other tuning parameters (such as bandwidth)
besides $\lambda$. 2) SCAM is formulated as a convex program, which guarantees a global optimum.

\begin{figure}[!htpb]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{Additive}
                 \caption{Variable selection result using SCAM.}
                \label{SCAM}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{LASSO}
                \caption{Variable selection result using LASSO.}
                \label{LASSO}
        \end{subfigure}\\
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{Convex}
                \caption{Inferred additive convex functions by SCAM.}
                \label{Convex}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{MSE}
                 \caption{Predictive MSE of SCAM and LASSO.}
                 \label{MSE}
        \end{subfigure}
        \caption{Results on Boston housing data.}\label{Boston}
\end{figure}

\subsubsection*{References}

\end{document}

### 2013-09-29 tex/scam/nips13/appendix.tex
first init

--- 2013-09-29 tex/scam/appendix.tex
@@
 
-We start with a lemma similar to Lemma~\ref{lem:general_int_reduction} and whose proofs are identical.
+We start with a lemma similar, and whose proof is identical to Lemma~\ref{lem:general_int_reduction}.
 
@@
 \label{lem:int_reduction}
-Let $F$ be a product distribution on $C=[0,1]^s$ with density function $p$. Let $f: C \rightarrow \R$ be a convex function. Suppose that $\E f(X) = 0$.
+Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.
 
@@
 
-Then $f^*_k(x_k) = \E[ f(X) \given x_k]$.
+Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
 \end{lemma}
@@
 
-Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$, for all $x_k$,  uniquely minimizes 
+Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
 \[
@@
 \]
-If this is true, then the function $x_k \mapsto \E[ f(X) \given x_k]$ is the unique $f^*_k(x_k)$ that minimizes the expected square error.
 
-Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
+Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
 \begin{align*}
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\  
-   p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\
-f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(\mathbf{x}) d \mathbf{x}_{-k} 
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k}  
+p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
  \end{align*}
-Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption.
-The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.
-
-The square error objective is strongly convex.
-The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
-Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ]$ is unique.
 
 Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex.
-The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
 
@@
  \begin{proposition}
-Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
+Let $p$ be a product probability distribution supported and positive on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
 
@@
 
-By the assumption that , we know that, for all $x_k$,
+By the assumption that $p$ is a product measure, we know that, for all $x_k$,
 \begin{align*}
-p(x_k) \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
+p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
+		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
 \end{align*}
@@
 
-Let $\mathcal{C}[s,b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
+Let $\mathcal{C}^s[b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
 \[
-\mathcal{C}[s,b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
+\mathcal{C}^s[b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
 \]
@@
 
-Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$.
+Let $\mathcal{C}_0^{s}[b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}^s[b,B,L]$.
 
@@
 \]
-where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\
+where $f' \in \mathcal{C}_0^s[b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.
 
-Step 1. We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
+We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
 

### 2013-09-29 tex/scam/nips13/introduction.tex
first init

\section{Introduction}

We consider the problem of estimating a convex function of several
variables from noisy values of the function at a finite sample of
input points.  Recent work \cite{Guntu:12,Guntu:13} shows that the
minimax rate for convex function estimation in $p$ dimensions is
$n^{-4/(4+p)}$.  Loosely speaking, this shows that the
geometric convexity constraint is statistically equivalent to
requiring two derivatives of the function, and thus is
subject to the same curse of dimensionality.
However, if the function is sparse, with $s\ll p$ relevant variables,
then the faster rate $n^{-4/(4+s)}$ may be achievable if the $s$
variables can be identified.  To determine the relevant variables, we
show that it suffices to estimate a sum of $p$ one-dimensional convex
functions, leading to significant computational and statistical
advantages.  In addition, we introduce algorithms and supporting
statistical theory for a practical, effective approach to this
variable selection problem.

The sparse nonparametric regression problem is considered in
\cite{lafferty2008rodeo}, where it is shown that computationally
efficient, near minimax-optimal estimation is possible, but in ambient
dimensions that scale only as $p = O(\log n)$.  This is in stark
contrast to the exponential scaling $p = O\bigl(e^{n^c}\bigr)$ enjoyed
by sparse linear models \cite{Wain:09a}.  Sparse additive models
\cite{Ravikumar:09} provide a practical alternative to fully
nonparametric function estimation.  But the additive assumption is
limited.  In particular, the natural idea of first selecting the
single variable effects, then the pairwise effects, and so on, does
not in general lead to consistent variable selection.  In other words,
the general nonparametric model is not additively faithful.
Remarkably, the additional assumption of convexity does lead to
additive faithfulness, as we show here.  In addition, we show that
exponential scaling is achievable for sparse convex additive models.
Thus, the geometric convexity constraint is quite different from the
smoothness constraints imposed in traditional nonparametric
regression.

A key to our approach is the observation that least squares
nonparametric estimation under convexity constraints is equivalent to
a finite dimensional quadratic program.  Specifically, the infinite
dimensional optimization 
\begin{eqnarray}
& \text{minimize} &\sum_{i=1}^n (Y_i - m(x_i))^2 \\
& \text{subject to} & m:\reals^p\rightarrow\reals\ \text{is convex}
\end{eqnarray}
is precisely equivalent to the finite dimensional quadratic
program 
\begin{eqnarray}
& \text{minimize}_{h, \beta} &\sum_{i=1}^n (Y_i - h_i)^2 \\
& \text{subject to} & h_j \geq h_i + \beta_i^T (x_j-x_i),\; \text{for
    all $i,j$}.
\label{eq:outer}
\end{eqnarray}
See \cite{Boyd04}, Section 6.5.5.
Here $h_i$ is the estimated function value $m(x_i)$, and the vectors
$\beta_i \in \reals^d$ represent supporting hyperplanes to the
epigraph of $m$.  Importantly, this finite dimensional quadratic program does
not have tuning parameters for smoothing the function. Such parameters are the bane
of nonparametric estimation.

Estimation of convex functions arises naturally in several
applications.  Examples include geometric programming \cite{Boyd04},
computed tomography \cite{Prince:90}, target reconstruction
\cite{Lele:92}, image analysis \cite{Golden:06} and circuit design
\cite{Hannah:12}.  Other applications include queuing theory
\cite{Chen:01} and economics, where it is of interest to estimate
concave utility functions \cite{Pratt:68}.  See \cite{Lim:12} for
other applications.  Beyond cases where the assumption of convexity is
natural, we offer that the convexity assumption is attractive as a
tractable, nonparamametric relaxation of the linear model.  In
addition to the lack of tuning parameters, other than the
regularization parameter $\lambda$ to control the level of sparsity,
the global convexity leads to effective, scalable algorithms.  We
demonstrate use of our approach on experiments with standard
regression data sets, in a comparison with sparse linear models
(lasso).

%In the following section we give a high-level summary of our technical
%results, including additive faithfulness, variable selection 
%consistency, and high dimensional scaling.  In Section~X...

\def\mathbf#1{\mbox{\boldmath $#1$}}

\textbf{Notation.} If
$\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
vector with $k$-th coordinate removed. Let $\mathbf{v} \in \R^n$, then
$v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
is all ones. If $X \in \R^p$ and $S \subset
\{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
$\bar{X}$ to denote empirical average.

### 2013-09-29 tex/scam/nips13/sparsistency.tex
first init

\section{Analysis of Variable Selection Consistency}

We divide our analysis into two parts. We first establish a sufficient
\emph{deterministic} condition for sparsistency.  We then consider the
stochastic setting and argue that the deterministic conditions hold with high probability.

\subsection{Deterministic Setting}

We follow Wainwright \cite{Wain:09a} and define a purely theoretical construct called \emph{restricted regression}.
\begin{definition}
In \emph{restricted regression}, we restrict the indices $k$ in
optimization (\ref{opt:alternate_opt}) to lie in the support $S$ instead of ranging from $1,...,p$. 
\end{definition}

Our analysis then diverges from the now-standard ``primal-dual witness
technique''~\cite{Wain:09a}. Primal-dual witness explicitly solves all the dual variables. Because our optimization is more complex, we do not solve the dual variables on $S$, we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
\hat{c}_k \mathbf{1})$ be the restricted regression residual. For $k
\in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
\hat{r}^\tran \Delta_{k,j}|$. Then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}
This result holds regardless of whether we impose the boundness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.

\begin{remark}
  The incoherence condition of \cite{Wain:09a} is implicitly encoded
  in our condition on $\lambda_n, \hat{r}, \Delta_{k,j}$. We can
  reconstruct the incoherence condition if we assume that the true
  function $f_0$ is linear and that our fitted functions $\hat{f}_k$
  are linear as well.
\end{remark}

Theorem~\ref{thm:deterministic} allows us to analyze false negative
rates and false positive rates separately. To control false positives,
we study when the condition $\lambda_n > | \frac{1}{n} \hat{r}^\tran
\Delta_{k,j}|$ is fulfilled for all $j$ and all $k \in S^c$. To
control false negatives, we study the restricted regression.

\subsection{Probabilistic Setting}

We use the following statistical setting:

\begin{packed_enum}
\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $S \subset \{1,...,p\}$ denote the relevant variables, i.e.,
  $f_0(X) = f_0(X_S)$, with $s \coloneqq |S|$. 
\end{packed_enum}

Each of our statistical theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
\item[A2:] $\|f_0\|_\infty \leq B$. \  A2': $f_0$ is convex,
  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
\end{packed_enum}

We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3 to control the probability of false negatives.

\begin{remark}
  We make strong assumptions on the covariates in A1 in order to make
  very weak assumptions on the true regression function $f_0$ in
  A2. In particular, we do not assume that $f_0$ is additive. Relaxing
  these assumptions is an interesting direction for future work.
  %Strong assumptions on the covariates are not uncommon in nonparametric
  %variable selection analysis~\cite{lafferty2008rodeo}. 
  %[TODO: refer to correlated design experiment].
\end{remark}

\begin{theorem} (Controlling false positives) 
\label{thm:false_positive}
Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\eqref{opt:alternate_opt} with the $B$-boundness constraint. Let $c,C$ be absolute constants.
Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n
  \log (pn)}$.  Then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$, $\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$.
Therefore, any solution to the full regression (\ref{opt:alternate_opt}), with boundedness constraint, is zero on $S^c$. 
\end{theorem}

The proof of Theorem~\ref{thm:false_positive} exploits independence of
$\hat{r}$ and $\Delta_{k,j}$ from A1, and then uses concentration of
measure results to argue that $| \frac{1}{n} \hat{r}^\tran
\Delta_{k,j}|$ concentrates around zero at a desired rate. The fact
that $\hat{r}$ is a centered vector is crucial to our proof, and our
theory thus further illustrates the importance of imposing the
centering constraints in optimization \eqref{opt:alternate_opt}. Our
proof uses the concentration of the average of
data sampled \emph{without} replacement
\cite{serfling1974probability}, illustrating that the proof method is not a
trivial application of existing techniques. The full proof of
Theorem~\ref{thm:false_positive} is in
Section~\ref{sec:false_positive_proof} of the Appendix.

\begin{theorem} (Controlling false negatives)
\label{thm:false_negative}
Suppose assumptions A1', A2', A3 hold. Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint. Let $c,C$ be absolute constants.
Suppose $L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \right) \rightarrow 0$.
Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
\neq 0$ for all $k \in S$ with probability at least $1-\frac{C}{n}$.
\end{theorem}

This is a finite sample version of
Theorem~\ref{thm:convex_faithful}. We need stronger assumptions in
Theorem~\ref{thm:false_negative} to use our additive faithfulness
result, Theorem~\ref{thm:convex_faithful}. We also include an extra
Lipschitz constraint so that we can use existing covering number
results \cite{Bronshtein:76}. Recent work
\cite{Guntu:13} shows that the Lipschitz constraint
is not required with more advanced empirical process theory
techniques. We give the full proof of Theorem~\ref{thm:false_negative}
in Section~\ref{sec:false_negative_proof} of the Appendix.

Combining Theorem~\ref{thm:false_positive} and
~\ref{thm:false_negative} and ignoring dependencies on $b,B,L,\sigma$,
we have the following result.
\begin{corollary}
  Assume A1', A2', A3. Let $\lambda_n = \Theta\left( \sqrt{
  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $\lambda_n
  \rightarrow 0$ and $\sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow
  0$. Let $\hat{f_n}$ be a solution to (\ref{opt:alternate_opt}) with
  boundedness and Lipschitz constraints. Then 
  $\P( \trm{supp}(\hat{f_n}) = \trm{supp}(f_0) ) \rightarrow 1$.
\end{corollary}
The above corollary implies that sparsistency is achievable at the same exponential scaling of the ambient dimension $p = O(\exp(n^c)), c<1$ rate as parametric models. The cost of nonparametric modeling is reflected in the scaling with respect to $s$, which can only scale at $o(n^{4/25})$.

%\textbf{Comparison with Related Work.}

### 2013-09-29 tex/scam/optimization.tex
first init

\section{Optimization for Sparse Convex Additive Models}

We consider the following nonparametric regression problem
\begin{equation}\nonumber
          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
\end{equation}
where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
functions $f_{k}(\cdot)$ in each variable dimension.  
We impose an additional constraint that each $f_{k}(\cdot)$ is 
an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
\begin{equation}\label{hyper}
      h_{kj} \geq h_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
\end{equation}
where $h_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
subgradient at point $x_{ki}$. We apparently need $O(n^2 p)$ constraints to
impose the supporting hyperplane constraints, which is computationally
expensive for large scale problems.  In fact, only $O(np)$
constraints suffice, since univariate convex functions are
characterized by the condition that the subgradient, which is a scalar, must
increase monotonically. This observation leads to our optimization
program:
\begin{equation}\begin{split}\label{np}
       &\min_{\bds{h},\bds{\beta}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl(y_{i}-\sum_{k=1}^{p}h_{ki}\Bigr)^{2} + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
\end{split}\end{equation}
Let $\{(1),(2),\ldots,(n)\}$ be a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.  It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
\begin{eqnarray}
  \nonumber \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ \nonumber
                                                                             & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
  \nonumber \forall j<i,         &h_{k(j)}-h_{k(i)} = \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ \nonumber
                                                                             & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
\end{eqnarray}
The $\ell_\infty/\ell_1$ penalty
$\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty}$ encourages group
sparsity of the vectors $\bds{\beta}_{k\cdot}$, and thus performs
variable selection.  We refer to this framework as the sparse convex
additive model (SCAM). Notice that if we replace $\beta_{k(i+1)} \geq
\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
reduces to the lasso.  Note while one can use
supporting hyperplanes to the epigraph as in \eqref{eq:outer}, 
SCAM uses the \emph{inner  piece-wise linear function}
that approximates the graph with secant lines.

%\begin{SCfigure}
%\label{fig:outer_approximation}
%\includegraphics[width=0.3\textwidth]{figs/outer_approximation.pdf}
%\caption{With the 5 sample points $(X_i, h(X_i))$, the
%  black and the blue convex function represent equivalent fits. SCAM
%  chooses the inner piece-wise linear convex functions.}
%\end{SCfigure}

The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints. 
Directly applying a QP solver would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
where in each step we solve the following QP subproblem for
$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
\begin{equation}\begin{split}\nonumber
       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} + \lambda\gamma_{k} \\
        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
\end{split}\end{equation}
The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
which can be solved efficiently using optimization packages (e.g., MOSEK: \verb+http://www.mosek.com/+).  We cycle through all feature dimensions ($k$) from $1$ to $p$ multiple times until convergence.
Empirically, we observe that the algorithm converges in only a few cycles. We also implemented an ADMM solver for (\ref{np}), but found that it is not as efficient as this QP solver.

After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
\begin{equation}\nonumber
      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj}) = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\}.
\end{equation}

%% Why hats here?  Turning them off (JDL)
\def\hat#1{#1}

\subsection{Alternative Formulation}
Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives. The alternative formulation replaces the ordering
constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity
constraints, which simplifies theoretical analysis.
Define $\hat{d}_{k(i)}$ as the gradient increment:
$\hat{d}_{k(1)} = \hat{\beta}_{k(1)}$, and $\hat{d}_{k(2)} =
\hat{\beta}_{k(2)} - \hat{\beta}_{k(1)}$. The convexity constraint is
equivalent to the constraint that $\hat{d}_{k(i)} \geq 0$ for all $i >
1$.

It is easy to verify that $\hat{\beta}_{k(i)} = \sum_{j \leq i} \hat{d}_{k(i)}$ and 
\[
\hat{f}_k(x_{k(i)}) = \hat{f}_k({x_{k(1)}}) +\hat{d}_{k(1)} ( x_{k(i)}
- x_{k(1)}) + \hat{d}_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + \hat{d}_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
\]
Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
$\Delta(j,x_{ki})= x_{ki} -
x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
$n-1$ dimensional vector. Then $\hat{f}_k(x_{ki}) = \Delta(x_{ki})^\tran \hat{d}_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$. Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$. Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
\begin{align}
\min_{\{d_k \in \R^{n-1}, c_k \in \R\}}& \frac{1}{2n} \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
\end{align}
$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.

\begin{remark}
\label{rem:bounded_lipschitz_constraints}
For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|\hat{f}_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $\hat{f}_k$ must be $L$-Lipschitz. We use these constraints only in the proof for technical reasons; we never need nor use these constraints in our experiments.
\end{remark}

%% turn the hat back on (JDL)
\def\hat#1{\widehat{#1}}

### 2013-09-29 tex/scam/result.tex
first init

--- 2013-09-29 tex/result.tex
@@
 \begin{packed_enum}
-\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
-\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
-\item Let $S \subset \{1,...,p\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$ and let $s \coloneqq |S|$.
+\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'_1,...,Y'_n$, we input into our optimization $Y = Y' - \bar{Y}'$.
+\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$with positive density $p$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
+\item Let $s \leq p$ be a positive integer and let $S = \{1,...,s\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$.
+\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \E(f_0(X) - \sum_{k\in S} f_k(X_k))^2$ be the population optimal additive components
 \end{packed_enum}
@@
 \item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
-\item[A2] Suppose that $\|f_0\|_\infty \leq B$.
+\item[A2] Suppose that $\|f_0\|_\infty \leq sB$.
 \item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
 \item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
+\item[A4] Suppose that, for all $k\in S$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some constant $\alpha > 0$.  
 \end{packed_enum}
@@
 
-\subsection{Reformulation}
-
-Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large. Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\
-
-Then  
-\begin{align*}
-\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
-\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
-\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
-\end{align*}
-
-We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
-\[
-D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
-\]
-
-And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.
-
-\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment.
-$\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$.
-The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\
-
-$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.
-
-\[
-\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
-\]
-
-\begin{align*}
-\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
- &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
- &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
-\end{align*}
-
-\[
-\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
-\]
-
-Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write
-
-\[
-\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
-\]
-
-With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\
-
 \begin{align}
@@
 	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
-	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
+	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber\\
 \end{align}
@@
 	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
-	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
+	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber\\ 
 \end{align}
@@
 then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$.
-Because we have strict inequality, Lemma [TODO:get wainwright lemma] shows that all solutions must be zero on $S^c$.
+We need strict inequality to argue that all solutions are sparse.
 \end{proof}
@@
 \begin{theorem} (Probabilistic: Controlling False Positives) \\
-Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\ref{opt:alternate_opt} with the $B$-boundness constraint.
+Suppose assumptions A1, A2, A3 hold.
 
@@
 \begin{theorem} (Probabilistic: Controlling False Negatives)\\
-Suppose assumptions A1', A2', A3 hold. Suppose we run optimization~\ref{opt:alternate_opt} with both the $B$-boundedness and $L$-Lipschitz constraint. Suppose $f_0$ depends on all $s$-variables.
+Suppose assumptions A1', A2', A3 hold. Suppose $f_0$ depends on all $s$-variables.
 

### 2013-09-29 code/Kmean_curve_plots.m

@@ -1,0 +1,52 @@
+clc; clear all; close all;
+
+p = 60;
+K0 = 7;
+s = 3;
+K = 10; 
+
+n_ls = [50,100,200,300,400,500];
+noise=0.05;
+
+num_trials = 10;
+record_ls = zeros(length(n_ls),1);
+
+for ii=1:length(n_ls)
+    n = n_ls(ii);
+    num_succ = 0;
+    
+    for it=1:num_trials    
+        beta_stars = randn(p,K0);
+        beta_stars((s+1):p,:)=0;
+        alpha_stars = randn(K0,1)*0.2;
+        Xs = randn(n,p); [Ys,c0] = max(Xs*beta_stars + ones(n,1)*alpha_stars', [], 2);
+        [c0,ndx] = sort(c0); Xs = Xs(ndx,:); Ys = Ys(ndx) + noise*randn(n,1);
+
+        c = randsample(K,n,true); 
+        lambda = max(noise*sqrt(s*log(p)/n)*n,0.001*n); mu = 1; maxit = 1000;
+
+        beta = zeros(p,K);
+        alpha = zeros(1,K);
+        for iter = 1:30
+            [beta,alpha,obj,h,c,Ln] = Piecewise_KPlanesADMM(Xs',Ys,c,lambda,mu,maxit,beta,alpha);
+
+            disp(['sparsity level: ' num2str(sum(max(abs(beta),[],2)<1e-5))]);
+
+            disp(['Iteration ' num2str(iter) ' Objective ' num2str(obj(end))]);
+            figure(1); subplot(3,2,1); plot(max(abs(beta_stars),[],2),'b*'); subplot(3,2,2); plot(Ln,'r.');
+            subplot(3,2,3); plot(c0,'b.'); subplot(3,2,4); plot(c,'r.');
+            subplot(3,2,[5,6]); plot(1:n,Ys,'ko',1:n,h,'r+'); drawnow;
+        end
+        close all;
+        
+        has_false_positive = sum(max(abs(beta((s+1):p,:)),[],2)) > 1e-2;
+        has_false_negative = sum(max(abs(beta(1:s,:)),[],2)) < 1e-2;
+        
+        if (~has_false_positive && ~has_false_negative)
+            num_succ = num_succ + 1;
+        end
+        
+    end
+    record_ls(ii) = num_succ/num_trials;
+end
+    

### 2013-09-29 code/Piecewise2.m

@@ -1,0 +1,43 @@
+function [beta,h,obj] = Piecewise_Convex(X,y,lambda,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); M = zeros(p,n);
+iter = 0; obj = zeros(1,maxit); 
+while iter < maxit
+    iter = iter + 1;
+    
+    C = beta-1/mu*M; C = repmat(max(1-lambda/mu./sqrt(sum(C.^2,2)),0),[1,n]).*C;
+    
+    xb = sum(X.*beta,1);
+    h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
+        X'*sum(beta,2) + n*xb' - sum(xb) - beta'*sum(X,2);
+    h = 1/(1/mu+2*n)*(h+2*mu*sum(h));
+
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); % Could be computed in advance.
+        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
+        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0);
+        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); M(:,i) = M(:,i) + mu*(C(:,i)-beta(:,i));
+    end
+    
+    obj(iter) = 0.5*sum((y-h).^2,1) + lambda*sum(sqrt(sum(C.^2,2)));
+    mu = min(1.1*mu,10^6);
+    if mod(iter,10)==0, 
+        disp(['Iter ' num2str(iter) ' Obj ' num2str(obj(iter))]); 
+        figure(999); clf; subplot(2,1,1); plot(1:n,y,'ko',1:n,h,'r+');
+        subplot(2,1,2); plot(sqrt(sum(beta.^2,2)),'r.'); drawnow;
+    end
+end
+return
+
+%% Testing quadratic function.
+clc; clear all; close all; randn('state',0); randn('state',0);
+
+p = 100; n = 200; s = 5; ord = randperm(p); b = zeros(1,p); b(ord(1:s)) = 1;
+Xs = randn(n,p)/sqrt(p); Ys = sum(Xs(:,b==1).^2,2);
+
[…]

### 2013-09-29 code/Piecewise_Additive.m

@@ -1,0 +1,50 @@
+function [beta,z,obj,Ln] = Piecewise_Additive(X,y,lambda,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); z = zeros(p,n);
+S = zeros(p,n,n); W = zeros(p,n,n); M = zeros(p,n); C = zeros(p,n); q = zeros(p,1);
+iter = 0; obj = []; tmp0 = 1/mu*repmat(y',[p,1]);
+while iter < maxit
+    iter = iter + 1;
+    for j = 1:p, C(j,:) = Piecewise_Inf(beta(j,:)-1/mu*M(j,:),lambda/mu); end
+    
+    tmp1 = repmat(sum(beta,2),[1,n]).*X - repmat(sum(beta.*X,2),[1,n]) ...
+        - repmat(sum(X,2),[1,n]).*beta + n*X.*beta + squeeze(sum(S,3))-squeeze(sum(S,2)) ...
+        - 1/mu*(squeeze(sum(W,3))-squeeze(sum(W,2))) - 1/mu*repmat(q,[1,n]);
+    z = tmp0 + tmp1;
+    [ialpha,igamma,is] = Piecewise_Inverse(2*n*ones(p,1),ones(p,1),-1/mu);
+    z = repmat(ialpha,[1,n]).*z - is*igamma*(igamma'*z); zs = sum(z,2);
+    [alpha,gamma,s] = Piecewise_Inverse(ones(p,1)-n*ialpha,igamma,-n*is);
+    zs = alpha.*zs - s*gamma*(gamma'*zs); zs = ialpha.*zs - is*igamma*(igamma'*zs);
+    z = z + repmat(zs,[1 n]);
+    
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); zi = z - repmat(z(:,i),[1,n]);
+        beta(:,i) = (C(:,i)+1/mu*M(:,i)+sum(Xi.*(zi-S(:,:,i)+1/mu*W(:,:,i)),2))./(1+sum(Xi.^2,2));
+        xbi = Xi.*repmat(beta(:,i),[1,n]);
+        S(:,:,i) = max(zi-xbi+1/mu*W(:,:,i),0); W(:,:,i) = W(:,:,i) + mu*(zi-xbi-S(:,:,i));
+    end
+    q = q + mu*sum(z,2); M = M + mu*(C-beta);
[…]

### 2013-09-29 code/Piecewise_CAP.m

@@ -1,0 +1,318 @@
+function [alpha, beta, abStruct] = Piecewise_CAP(x,y,convexFlag,logMult,knotNum)
+
+% CAPnew runs the CAP algorithm on input data x,y to create a piecewise
+% linear convex or concave function
+%
+% Inputs:
+%   - x             : training data covariates (n by d)
+%   - y             : training data response (n by 1)
+%   - convexFlag    : 0 if convex, 1 if concave (convex by default)
+%   - logMult       : multiplier of log(n) decides minimal number of
+%                     observations per partition; default is 3
+%
+% Outputs:
+%   - alpha         : vector of intercepts for CAP estimator
+%   - beta          : vector of slopes for estimator
+%   - abStruct      : structure array of (alpha,beta), residuals,
+%                     partitions and BIC for k = 1,...,K; save using "Save
+%                     Workspace"
+
+
+[n,d] = size(x);
+
+if ((nargin == 2)||(isempty(convexFlag)))
+    convexFlag = 0;
+end
+if ((nargin < 4)||(isempty(logMult)))
+    logMult = 3; % 5
+end
+if ((nargin < 5)||(isempty(knotNum)))
+    knotNum = 10;
+end
+
+minNode = max(n/(logMult*log(n)),2*(d+1));
+
+alpha = [];
+beta = [];
+abStruct = [];
+
+keepGoing = true;
+
+% Initialize with one partition
+K = 1;
+if (n > 2*(d+1))
+    ab = regress(y,[ones(n,1), x]);
+else
+    ab = zeros(d+1);
+    ab(1) = mean(y);
+end
+
+g = [ones(n,1), x]*ab;
+res = y - g;
+varG = getVar(y - g,K,d);
+    
+BIC = mean((y-g).^2)/(1-K*(d+1)/n)^2;
+
+alpha = ab(1);
+beta = ab(2:end);
+idList = ones(n,1); % Parition of observations
+
+abStruct(1).alpha = alpha;
+abStruct(1).beta = beta;
+abStruct(1).residuals = res;
+abStruct(1).idList = idList;
+
+BICvec = [];
+
+BICvec = [BICvec; BIC];
+MSEvec = [];
+MSEvec = [MSEvec; mean(res.^2)];
+GCVvec = [];
+GCVvec = [GCVvec; sum(res.^2)/(n*(1-(K*(d+1))/n)^2)];
+
+abStruct(1).BIC = BIC;
+
[…]

### 2013-09-29 code/Piecewise_Convex.m

@@ -1,0 +1,28 @@
+function [beta,h,obj] = Piecewise_Convex(X,y,lambda,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
+M = zeros(p,n); iter = 0; obj = []; 
+while iter < maxit 
+    iter = iter + 1;
+    C = beta-1/mu*M; C = repmat(max(1-lambda/mu./sqrt(sum(C.^2,2)),0),[1,n]).*C; 
+    
+    xb = sum(X.*beta,1);
+    h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
+        X'*sum(beta,2) + n*xb' - sum(xb) - beta'*sum(X,2);
+    h = 1/(1/mu+2*n)*(h+2*mu*sum(h));
+    
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); % Could be computed in advance.
+        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
+        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0);
+        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); M(:,i) = M(:,i) + mu*(C(:,i)-beta(:,i)); 
+    end
+    
+    obj(iter) = 0.5*sum((y-h).^2,1) + lambda*sum(sqrt(sum(C.^2,2)));
+    
+    if mod(iter,50)==0, 
+        disp(['   Iter ' num2str(iter) ' Obj ' num2str(obj(iter))]); 
+        figure(998); subplot(2,1,1); plot(1:n,y,'ko',1:n,h,'r+');
+        subplot(2,1,2); plot(sqrt(sum(beta.^2,2)),'r.'); drawnow;
+    end
+end
+return

### 2013-09-29 code/Piecewise_Inf.m

@@ -1,0 +1,9 @@
+function z = Piecewise_Inf(x,v)
+n = length(x); [xa,ndx] = sort(abs(x),'descend');
+b = [xa(2:n) 0] - (cumsum(xa)-v)./(1:n); z = zeros(1,n); 
+if b(n) < 0
+    pos = find(b<0,1); zinf = (sum(abs(x(ndx(1:pos))))-v)/pos;
+    z(ndx(1:pos)) = sign(x(ndx(1:pos))).*zinf;
+    z(ndx(pos+1:n)) = x(ndx(pos+1:n));
+end
+return

### 2013-09-29 code/Piecewise_Infinity.m

@@ -1,0 +1,68 @@
+function [beta,h,obj] = Piecewise_Infinity(X,y,lambda,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
+M = zeros(p,n); iter = 0; obj = []; C = zeros(p,n);
+
+num_lambda = length(lambda);
+if (num_lambda < p)
+    lambda = ones(p,1)*lambda;
+end
+
+while iter < maxit 
+    iter = iter + 1;
+    for j = 1:p, C(j,:) = Piecewise_Inf(beta(j,:)-1/mu*M(j,:),lambda(j)/mu); end
+    
+    xb = sum(X.*beta,1); %a row of dimension n
+    h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
+        X'*sum(beta,2) + n*xb' - sum(xb) - beta'*sum(X,2);
+    h = 1/(1/mu+2*n)*(h+2*mu*sum(h));
+    
+    prev_beta = beta;
+    all_xb = zeros(n,n);
+    all_prev_xb = zeros(n,n);
+    h_mat = zeros(n,n);
+    
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); 
+        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
+        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0); 
+        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); M(:,i) = M(:,i) + mu*(C(:,i)-beta(:,i)); 
+        
+        %for stopping criteria
+        all_xb(i,:) = xbi';
+        all_prev_xb(i,:) = prev_beta(:,i)'*Xi;
+        h_mat(:,i) = h-h(i)-xbi;
+    end
+    
+    obj(iter) = 0.5*sum((y-h).^2,1);
+    
+    %=- verify stopping criteria -=
+    criterion1 = norm(all_xb - all_prev_xb,'fro')/n;
+    criterion2 = norm(S - h_mat, 'fro')/n;
+    criterion3 = norm(C - beta,'fro')/sqrt(n*p);
+    
+    threshold = 5e-5;
[…]

### 2013-09-29 code/Piecewise_InfinityADMM.m

@@ -1,0 +1,37 @@
+function [beta,h,obj,Ln] = Piecewise_InfinityADMM(X,y,lambda,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
+M = zeros(p,n); iter = 0; obj = []; C = zeros(p,n);
+while iter < maxit 
+    iter = iter + 1;
+    for j = 1:p, C(j,:) = Piecewise_Inf(beta(j,:)-1/mu*M(j,:),lambda/mu); end
+    
+    xb = sum(X.*beta,1);
+    h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
+        X'*sum(beta,2) + n*xb' - sum(xb) - beta'*sum(X,2);
+    h = 1/(1/mu+2*n)*(h+2*mu*sum(h));
+    
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); % Could be computed in advance.
+        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
+        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0);
+        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); M(:,i) = M(:,i) + mu*(C(:,i)-beta(:,i)); 
+    end
+    
+    Ln = max(abs(C),[],2); obj(iter) = 0.5*sum((y-h).^2,1) + lambda*sum(Ln);
+    if mod(iter,10000)==0, 
+        disp(['   Iter ' num2str(iter) ' Obj ' num2str(obj(iter))]); 
+        figure(1); subplot(2,1,1); plot(1:n,y,'ko',1:n,h,'r+');
+        subplot(2,1,2); plot(Ln,'r.'); drawnow;
+    end
+end
+return
+
+function z = Piecewise_Inf(x,v)
+n = length(x); [xa,ndx] = sort(abs(x),'descend');
+b = [xa(2:n) 0] - (cumsum(xa)-v)./(1:n); z = zeros(1,n); 
+if b(n) < 0
+    pos = find(b<0,1); zinf = (sum(abs(x(ndx(1:pos))))-v)/pos;
[…]

### 2013-09-29 code/Piecewise_Inverse.m

@@ -1,0 +1,4 @@
+function [ialpha,igamma,is] = Piecewise_Inverse(alpha,gamma,s)
+% inv(diag(alpha)-s*gamma*gamma') = diag(ialpha)-is*igamma*igamma'.
+ialpha = 1./alpha; igamma = gamma./alpha; is = - 1/(1/s-gamma'*igamma);
+return

### 2013-09-29 code/Piecewise_KPlanesADMM.m

@@ -1,0 +1,45 @@
+function [beta,alpha,obj,h,c,Ln] = Piecewise_KPlanesADMM(X,y,c,lambda,mu,maxit,beta,alpha)
+[p,n] = size(X); K = max(c); 
+
+if (~exist('beta'))
+    beta = zeros(p+1,K);  
+else
+    beta = [alpha; beta];
+    beta = beta(:,1:K);
+end
+
+M = zeros(p,K); C = zeros(p,K); iter = 0; obj = []; h = zeros(n,1);
+while iter < maxit 
+    iter = iter + 1;
+    
+    % C = beta(2:p+1,:)-1/mu*M; C = repmat(max(1-lambda/mu./sqrt(sum(C.^2,2)),0),[1,K]).*C; 
+    
+    for k = 1:K
+        Xk = [ones(1,sum(c==k)); X(:,c==k)]; 
+        beta(:,k) = (1/mu*Xk*Xk'+diag([10^-3;ones(p,1)]))\...
+                    (1/mu*Xk*y(c==k)+[0;C(:,k)+1/mu*M(:,k)]);
+        M(:,k) = M(:,k) + mu*(C(:,k)-beta(2:p+1,k)); h(c==k) = Xk'*beta(:,k);
+    end
+    
+    for j = 1:p, C(j,:) = Piecewise_Inf(beta(j+1,:)-1/mu*M(j,:),lambda/mu); end
+    
+    Ln = max(abs(C),[],2); obj(iter) = 0.5*sum((y-h).^2,1) + lambda*sum(Ln);
+    
+    if (iter > 1 && abs(obj(iter) - obj(iter-1)) < obj(iter)*1e-5)
+        break;
+    end
+    
+end
+alpha = beta(1,:); beta = C; resp = X'*beta + ones(n,1)*alpha; 
+[nul,c] = max(resp,[],2); [c1,c2,c] = unique(c);
+return
+
+function z = Piecewise_Inf(x,v)
+n = length(x); [xa,ndx] = sort(abs(x),'descend');
+b = [xa(2:n) 0] - (cumsum(xa)-v)./(1:n); z = zeros(1,n); 
+if b(n) < 0
+    pos = find(b<0,1); zinf = (sum(abs(x(ndx(1:pos))))-v)/pos;
+    z(ndx(1:pos)) = sign(x(ndx(1:pos))).*zinf;
+    z(ndx(pos+1:n)) = x(ndx(pos+1:n));
+end
+return

### 2013-09-29 code/Piecewise_QP.m

@@ -1,0 +1,22 @@
+function [beta,h,val] = Piecewise_QP(X,y)
+[p,n] = size(X); % With l2 regularization on beta.
+H = zeros(n*(p+1),n*(p+1)); H((n*p+(0:n-1))*(n*(p+1))+n*p+(1:n)) = 1;
+H = sparse(H); 
+f = [zeros(n*p,1);-y];
+A = zeros(n*(n-1),n*(p+1));
+row = 0;
+for i = 1:n
+    for j = 1:n
+        if j~=i
+            row = row + 1;
+            A(row,((i-1)*p+1):(i*p)) = (X(:,j)-X(:,i))';
+            A(row,n*p+j) = -1; A(row,n*p+i) = 1;
+        end
+    end
+end
+b = zeros(n*(n-1),1);
+options = optimset('Algorithm','interior-point-convex','Display','off',...
+                   'MaxIter',1000,'TolFun',10^-16,'TolX',10^-16);
+[x,val] = quadprog(H,f,A,b,[],[],[],[],[],options); val = val + 0.5*y'*y;
+beta = reshape(x(1:n*p),[p,n]); h = x(n*p+1:n*(p+1));
+return

### 2013-09-29 code/Piecewise_Slope.m

@@ -1,0 +1,68 @@
+function [C,h,obj,Ln] = Piecewise_Slope(X,y,lambda,mu,maxit)
+[p,n] = size(X); dX = zeros(p,n-1); ord = zeros(p,n);
+for d = 1:p, [Xd,ord(d,:)] = sort(X(d,:)); dX(d,:) = Xd(2:n)-Xd(1:n-1); end
+beta = zeros(p,n-1); M = zeros(p,n-1); S = zeros(p,n-2); W = zeros(p,n-2);
+C = zeros(p,n-1); O = zeros(p,n-1); q = zeros(p,1); iter = 0; obj = [];
+G = gallery('tridiag',-ones(1,n-2),[2 3*ones(1,n-3) 2],-ones(1,n-2));
+A = gallery('tridiag',-ones(1,n-1),[1 2*ones(1,n-2) 1],-ones(1,n-1));
+B = inv(A+ones(n,n)); B1 = zeros(n,n); B2 = eye(n);
+for d = 1:p, B1(ord(d,:),:) = B; B1(:,ord(d,:)) = B1; B2 = B2+1/mu*B1; end
+
+while iter < maxit
+    iter = iter + 1;
+    for d = 1:p, C(d,:) = Piecewise_Inf(beta(d,:)-1/mu*O(d,:),lambda/mu); end
+    
+    h = zeros(p,n); eta = 1/mu*repmat(y',[p 1])-1/mu*repmat(q,[1 n]);
+    for d = 1:p
+        resp = dX(d,:).*beta(d,:)-1/mu*M(d,:);
+        eta(d,ord(d,1:n)) = eta(d,ord(d,1:n)) + ([0 resp] - [resp 0]);
+        h(d,ord(d,:)) = eta(d,ord(d,:))*B;
+    end
+    vec = B2\(sum(h,1)');
+    for d = 1:p, h(d,ord(d,:)) = h(d,ord(d,:)) - 1/mu*vec(ord(d,:))'*B; end
+    
+    for d = 1:p
+        dh = h(d,ord(d,2:n))-h(d,ord(d,1:n-1));
+        gd = C(d,:)+1/mu*O(d,:) + [0 S(d,:)-1/mu*W(d,:)] - [S(d,:)-1/mu*W(d,:) 0] + ...
+            dX(d,:).*(dh+1/mu*M(d,:));
+        Gd = G; rg = (0:n-2)*(n-1)+(1:n-1); Gd(rg) = Gd(rg) + dX(d,:).^2;
[…]

### 2013-09-29 code/Piecewise_TestCAP.m

@@ -1,0 +1,42 @@
+function err = Piecewise_TestCAP(type,n)
+randn('state',0); rand('state',0);
+ntrain = 5; err = zeros(ntrain,3);
+switch type
+    case 1
+        p = 5; Xt = randn(p,n);
+        yt = ((Xt(1,:) + 0.5*Xt(2,:) + Xt(3,:)).^2 - Xt(4,:) + 0.25*Xt(5,:).^2)';
+    case 2
+        p = 10; 
+        prob = gamrnd(ones(p,1),1); prob = prob./sum(prob); 
+        Xt = randn(p,n); yt = exp(Xt'*prob);
+    otherwise, return
+end
+
+for run = 1:ntrain
+    switch type
+        case 1
+            X = randn(p,n);
+            y = ((X(1,:) + 0.5*X(2,:) + X(3,:)).^2 - X(4,:) + 0.25*X(5,:).^2)' + randn(n,1);
+        case 2
+            X = randn(p,n); y = exp(X'*prob) + 0.1*randn(n,1);
+        otherwise, return
+    end
+
+    [alpha1,beta1] = Piecewise_CAP(X',y); % Lauren A. Hannah's code
+    y1 = max([ones(n,1),Xt']*[alpha1; beta1],[],2);
+    err(run,1) = sum((y1-yt).^2)/n;
+
+    [beta2,h2,obj2] = Piecewise_Convex(X,y,0,0.01,200);
+    % figure(1); plot(obj2,'r.'); drawnow;
+    alpha2 = h2' - sum(X.*beta2,1);
+    y2 = max([ones(n,1),Xt']*[alpha2; beta2],[],2);
+    err(run,2) = sum((y2-yt).^2)/n;
+
+    [beta3,h3,obj3] = Piecewise_QP(X,y);
+    alpha3 = h3' - sum(X.*beta3,1);
+    y3 = max([ones(n,1),Xt']*[alpha3; beta3],[],2);
+    err(run,3) = sum((y3-yt).^2)/n;
+
+    disp(['Finished type=' num2str(type) ' n=' num2str(n) ' run=' num2str(run)]);
+end
+return

### 2013-09-29 code/Piecewise_TestInfinity.m

@@ -1,0 +1,25 @@
+clc; clear all; close all; randn('state',123); rand('state',0);
+noise = 0.2; 
+n = 100; p = 80; s = 3; lambda = 2*noise*sqrt(s*log(p)/n)*n; maxit = 10000; mu = 0.01;
+lambda = max(lambda,1e-3*n);
+prob = zeros(p,1); 
+%ord = randperm(p); 
+ord = 1:p;
+prob(ord(1:s)) = gamrnd(10*ones(s,1),1);
+prob(ord(1:s)) = prob(ord(1:s))/sum(prob(ord(1:s)));
+X = randn(p,n); 
+%X = X./(ones(p,1)*sqrt(sum(X.^2,1)));
+%X = 0.5*rand(p,n)+1;
+
+y = diag(X(1:s,:)'*eye(s)*X(1:s,:)) + noise*randn(n,1);
+
+%y = exp(X'*prob) + noise*randn(n,1);
+%y = log(sum(exp(X'*prob),2)) + noise*randn(n,1);
+
+%[beta1,h1,obj1] = Piecewise_Convex(X,y,lambda,mu,maxit); % L-2-1 norm
+%[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda,mu,maxit); % L-infinity-1 norm
+
+%gamma = 1/sqrt(n);
+gamma = 1e7;
+
+[beta1,D,h1,obj1] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit); % L-2-1 norm

### 2013-09-29 code/Piecewise_TestInfinity_tmp_version.m

@@ -1,0 +1,63 @@
+clc; clear all; close all; randn('state',113); rand('state',0);
+noise = 0.00; 
+n = 2000; p = 20; s = 4; 
+%lambda = max(.5*noise*sqrt(s*log(p)/n),.0001); 
+lambda = 0.001*n;
+%lambda = 0;
+maxit = 1000; 
+%mu = 0.1; 
+mu = 0.01;
+
+prob = zeros(p,1); 
+%ord = randperm(p); 
+ord = 1:p;
+prob(ord(1:s)) = gamrnd(10*ones(s,1),1);
+prob(ord(1:s)) = prob(ord(1:s))/sum(prob(ord(1:s)));
+
+X = rand(p,n); 
+%X = X./(ones(p,1)*sqrt(sum(X.^2,1)));
+
+%X = 0.3*rand(p,n)+0.3;
+%X = sign(rand(p,n)-0.5).*X;
+%X = X./(sqrt(sum(X.^2,2))*ones(1,n));        
+
+A = rand(s,s);
+A = A + .5*eye(s);
+A = A/norm(A,2);
+%A = (1/2)*eye(s);
+y = diag(X(1:s,:)'*A*X(1:s,:)) + noise*randn(n,1);
+
+        K = 30;
+        beta_stars = randn(p,K);
+        
+        beta_stars = beta_stars./(ones(p,1)*sqrt(sum(beta_stars.^2,1)));
+        beta_stars((s+1):p,:) = 0;
+        %alpha_stars = randn(K,1);
+        alpha_stars = zeros(K,1);
+
+        
+        noiseless_Y = max(X'*beta_stars + ones(n,1)*alpha_stars', [], 2);
+        %y = noiseless_Y + randn(n,1)*noise;       
+        
+%y = exp(X'*prob) + noise*randn(n,1);
+%y = X'*prob + noise*randn(n,1);
+%y = log(sum(exp(X'*prob),2)) + noise*randn(n,1);
+
+%[beta1,h1,obj1] = Piecewise_Convex(X,y,lambda/sqrt(n),mu,maxit); % L-2-1 norm
+lambda2 = lambda*ones(p,1);
+[beta1,h1,obj1] = Piecewise_Infinity(X,y,lambda2,mu,maxit); % L-infinity-1 norm
+
+
+%lambda2(1:s) = lambda/2;
+%[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda2,mu,maxit); % L-infinity-1 norm
+
[…]

### 2013-09-29 code/Piecewise_TestKPlanes.m

@@ -1,0 +1,32 @@
+clc; clear all; close all; %randn('state',1); rand('state',1);
+p = 100; K0 = 4; s = 4; n = 200; noise=0.1;
+beta_stars = randn(p,K0); ord = randperm(p); beta_stars(ord((s+1):p),:) = 0;
+alpha_stars = randn(K0,1);
+Xs = randn(n,p); [Ys,c0] = max(Xs*beta_stars + ones(n,1)*alpha_stars', [], 2);
+[c0,ndx] = sort(c0); Xs = Xs(ndx,:); Ys = Ys(ndx) + noise*randn(n,1);
+% K-means
+K = 8; c = randsample(K,n,true); lambda = max(noise*sqrt(s*log(p)/n)*n,0.01*n); mu = 1; maxit = 1000;
+
+%Xs = 10*Xs./(ones(n,1)*sqrt(sum(Xs.^2,1)));
+%Ys = sum(Xs(:,1:s),2).^2;
+
+beta = zeros(p,K);
+alpha = zeros(1,K);
+
+for iter = 1:20
+    [beta,alpha,obj,h,c,Ln] = Piecewise_KPlanesADMM(Xs',Ys,c,lambda,mu,maxit,beta,alpha);
+    
+    disp(['sparsity level: ' num2str(sum(max(abs(beta),[],2)<1e-5))]);
+    
+    disp(['Iteration ' num2str(iter) ' Objective ' num2str(obj(end))]);
+    figure(1); subplot(3,2,1); plot(max(abs(beta_stars),[],2),'b*'); subplot(3,2,2); plot(Ln,'r.');
+    subplot(3,2,3); plot(c0,'b.'); subplot(3,2,4); plot(c,'r.');
+    subplot(3,2,[5,6]); plot(1:n,Ys,'ko',1:n,h,'r+'); drawnow;
+end
+
+% Convex
+%lambda = 1; mu = 0.01;
+%[beta,h,obj,Ln] = Piecewise_InfinityADMM(Xs',Ys,lambda,mu,maxit);
+%figure(2); subplot(3,2,1); plot(max(abs(beta_stars),[],2),'b*'); subplot(3,2,2); plot(Ln,'r.');
+%subplot(3,2,3); plot(c0,'b.'); % subplot(3,2,4); plot(c,'r.');
+%subplot(3,2,[5,6]); plot(1:n,Ys,'ko',1:n,h,'r+'); drawnow;

### 2013-09-29 code/Piecewise_TestQP.m

@@ -1,0 +1,5 @@
+clc; clear all; close all; 
+type = 2; n = 100; len1 = length(type); len2 = length(n);
+out = Piecewise_TestCAP(type,n); err = sum(out,1)/size(out,1)
+
+

### 2013-09-29 code/Quadratic_Infinity.m

@@ -1,0 +1,81 @@
+function [beta,D,h,obj] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit)
+[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
+M = zeros(p,2*n); iter = 0; obj = []; C = zeros(p,2*n); D = zeros(p,n);
+
+num_lambda = length(lambda);
+if (num_lambda < p)
+    lambda = ones(p,1)*lambda;
+end
+
+Delta = zeros(p,n,n);
+for j=1:n
+    Delta(:,j,:) = (X(:,j)*ones(1,n) - X).^2;
+end
+
+while iter < maxit 
+    iter = iter + 1;
+    for j = 1:p, C(j,:) = Piecewise_Inf([beta(j,:),D(j,:)]-1/mu*M(j,:),lambda(j)/mu); end
+    
+    Dexpand = permute(repmat(D,[1,1,n]),[1,3,2]);
+    tmp = reshape(Delta.*Dexpand,[p,n*n]);
+    DDelta = reshape(ones(1,p)*tmp,n,n);
+    DDelta = shiftdim(DDelta);
+    
+    % DDelta(j,i) is D_i'Delta_{ji}, (n--by--n) matrix
+
+    xb = sum(X.*beta,1); %a row of dimension n
+    h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
+        X'*sum(beta,2) + n*xb' - sum(xb) - beta'*sum(X,2) + ...
+        sum(DDelta,2) - sum(DDelta,1)';
+    h = 1/(1/mu+2*n)*(h+2*mu*sum(h));
+    
+    
+    %W here is (ji) j indexes row, i indexes column
+    
+    % X'*sum(beta,2) is a vector, dimension n
+    % sum(beta,2) has dimension p
+   
+    % X'*sum(beta,2)   X'*beta   is n*n matrix, row by X, col by beta
+    % sum over columns of X'*beta, produce a column
+    
+    for i = 1:n
+        Xi = X - repmat(X(:,i),[1,n]); 
+        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-DDelta(:,i)-S(:,i)+1/mu*W(:,i)));
[…]

### 2013-09-29 code/REkappa_test.m

@@ -1,0 +1,41 @@
+n_ls = 100:50:500;
+
+s = 3;
+p = 40;
+kappa_ls = zeros(length(n_ls),1);
+
+num_trial = 10000;
+
+for ii=1:length(n_ls)
+    cur_n = n_ls(ii);
+    
+    X = randn(p,cur_n);
+    
+    %generate Bstar
+    Bstar_candidates = randn(3*cur_n, s);
+    Bstar_candidates = [Bstar_candidates,zeros(3*cur_n,p-s)];
+    total_prods = Bstar_candidates*X;
+    [vals,ixs] = max(total_prods,[],1);
+    Bstar = Bstar_candidates(ixs,:);
+    %Bstar = zeros(cur_n, p);
+    
+    kappa = 10e10;
+    for it = 1:num_trial        
+        B_candidates = randn(3*cur_n,s);
+        B_candidates = [B_candidates, zeros(3*cur_n,p-s)];
+        B_candidates(:,(s+1):p) = randn(3*cur_n, p-s)*0.4;
+        total_prods = B_candidates*X;
+        [vals,ixs] = max(total_prods,[],1);
+        B = B_candidates(ixs,:);
+        
+        LHS = (1/cur_n)*sum(diag((B-Bstar)*X).^2);
+        %RHS = norm(B-Bstar,'fro')^2;
+        RHS = norm(max(abs(B(:,1:s)-Bstar(:,1:s)),[],1))^2;
+        
+        cur_kappa = LHS/RHS;
+        kappa = min(kappa,cur_kappa);
+    end
+    kappa
+    kappa_ls(ii) = kappa;
+    
+end

### 2013-09-29 code/SCAM_QP.m

@@ -1,0 +1,59 @@
+function [beta,z,obj,Ln] = SCAM_QP(X,y,lambda,maxit,tol)
+[p,n] = size(X); z = zeros(p,n); Ln = zeros(p,1); beta = zeros(p,n-1);
+res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
+while iter < maxit && change > tol
+    iter = iter + 1; 
+    
+    for d = 1:p
+        res = res + z(d,:)';
+        [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK(res,X(d,:),lambda);
+        res = res - z(d,:)'; 
+    end
+
+    obj(iter) = 0.5/n*sum(res.^2) + lambda*sum(Ln); 
+    if iter>1, change = abs(obj(iter-1)-obj(iter))/obj(iter-1); end
+    disp(['   SCAM_QP:    Iteration ' num2str(iter) ' Objective ' num2str(obj(iter))]);
+    figure(9); subplot(2,1,1); plot(1:n,y,'ko',1:n,sum(z,1)','r+'); title('Response');
+    subplot(2,1,2); plot(1:p,Ln,'r.'); title('L\infty norm'); drawnow;
+end
+return
+
+function [beta,z,Ln] = SCAM_MOSEK(y,x,lambda)
+n = length(x); [Xd,ord] = sort(x'); dX = Xd(2:n)-Xd(1:n-1);
+
+Hi = 1:n; Hj = 1:n; Hs = ones(1,n)/n; 
+H = sparse(Hi,Hj,Hs,2*n,2*n); f = [-y/n; zeros(n-1,1); lambda];
+
+Ai = []; Aj = []; As = []; row = 0; ndx = 0;
+valmat = [ones(n-2,1) -ones(n-2,1)];
+rowmat = [(1:(n-2))' (1:(n-2))'] + row;
+colmat = [((n+1):(2*n-2))' ((n+2):(2*n-1))'];
+rg = (ndx+1):(ndx+2*(n-2)); row = row + (n-2); ndx = ndx + 2*(n-2);
+Ai(rg) = rowmat(:); Aj(rg) = colmat(:); As(rg) = valmat(:);
+
+valmat = [ones(n-1,1) -ones(n-1,1) -ones(n-1,1) -ones(n-1,1)];
[…]

### 2013-09-29 code/Test_Quadratic_Infinity.m

@@ -1,0 +1,38 @@
+clc; clear all; close all; 
+
+%randn('state',123); rand('state',0);
+noise = 0; 
+n = 70; p = 20; s = 3; lambda = 2*noise*sqrt(s*log(p)/n)*n; 
+
+maxit = 5000; mu = .1;
+lambda = max(lambda,1e-3*n);
+
+X = randn(p,n); 
+
+
+%X = X./(ones(p,1)*sqrt(sum(X.^2,1)));
+%X = 0.5*rand(p,n)+1;
+
+K = 10;
+beta_star = randn(p,K);
+beta_star((s+1):p,:)=0;
+
+tmp = randn(s,s);
+A = tmp*tmp';
+A = A/norm(A,2);
+%A = eye(s);
+
+y = diag(X(1:s,:)'*A*X(1:s,:)) + max(X'*beta_star,[],2) + noise*randn(n,1);
+
+%y = exp(X'*prob) + noise*randn(n,1);
+%y = log(sum(exp(X'*prob),2)) + noise*randn(n,1);
+
+%[beta1,h1,obj1] = Piecewise_Convex(X,y,lambda,mu,maxit); % L-2-1 norm
+%[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda,mu,maxit); % L-infinity-1 norm
+
+%gamma = 1/sqrt(n);
+%gamma = 1/sqrt(n);
+%gamma = 1/n;
+gamma = 1;
+
+[beta1,D,h1,obj1] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit); % L-2-1 norm

### 2013-09-29 code/a_curious_function.m

@@ -1,0 +1,18 @@
+x1s = (0:1e2)/1e2;
+x2s = (0:1e2)/1e2;
+
+f = zeros(length(x1s),length(x2s));
+
+for ii = 1:length(x1s)
+    for jj=1:length(x2s)
+        x1 = x1s(ii);
+        x2 = x2s(jj);
+        
+        if (x1 < x2)
+            f(ii,jj) = -2*(x1/x2) + 1;
+        else 
+            f(ii,jj) = x1*(2/(1-x2)) - 2/(1-x2) + 1;
+        end
+    end
+end
+

### 2013-09-29 code/additive_counterexample.m

@@ -1,0 +1,39 @@
+
+x1 = (0:1:3e1)/3e1;
+x2 = (0:1:3e1)/3e1;
+
+Y = zeros(length(x1),length(x2));
+for ii = 1:length(x1)
+    for jj=1:length(x2)
+        Y(ii,jj) = sin(x1(ii)*2*pi)*sin(x2(jj)*2*pi);
+    end
+end
+figure;
+mesh(x1,x2,Y);
+colormap(copper)
+
+
+x1 = 2*(0:1:3e1)/3e1-1;
+x2 = (0:1:3e1)/3e1;
+
+Y = zeros(length(x1),length(x2));
+for ii = 1:length(x1)
+    for jj=1:length(x2)
+        Y(ii,jj) = x1(ii)*x2(jj);
+    end
+end
+figure;
+mesh(x1,x2,Y);
+colormap(copper);
+
+n=5000;
+Xs = [rand(n,1), 2*rand(n,1)-1];
+Ys = Xs(:,1).*Xs(:,2);
+[beta,z,obj] = SCAM_QP(Xs', Ys, 0.001, 100, 1e-5);
+
+
+n=5000;
+Xs = [rand(n,1), rand(n,1)];
+Ys = sin(Xs(:,1)*(2*pi)).*sin(Xs(:,2)*(2*pi));
+[beta,z,obj] = SCAM_QP(Xs', Ys, 0.001, 100, 1e-5);
+

### 2013-09-29 code/convexNoiseless.m

@@ -1,0 +1,37 @@
+%Delta should be (p--by--n)
+
+function [beta,s] = convexNoiseless(Delta, v, gamma)
+
+    n = size(Delta,2);
+    p = size(Delta,1);
+
+    f = [zeros(1,p), 0*ones(1,n), ones(1,p)];
+    %f = [zeros(1,p), 0*ones(1,n), 0.01*ones(1,3), ones(1,(p-3))];
+    
+    Aeq = zeros(n, n+2*p);
+    Aeq(:,1:p) = Delta';
+    Aeq(:,(p+1):(p+n)) = -eye(n);
+    %Aeq(:,(n+p+1):(n+2*p)) = zeros(n,p);
+    
+    beq = v;
+    
+    A = zeros(n+2*p, n+p+p);
+    for ii=1:p
+        A(ii,ii) = 1;
+        A(ii,ii+n+p) = -1;
+        
+        A(ii+n+p, ii) = -1;
+        A(ii+n+p, ii+n+p) = -1;
+    end
+    
+    for ii=1:n
+        A(ii+p, ii+p) = 1;
+    end
+    
+    b = zeros(n+2*p,1);
+    
+    [soln] = linprog(f,A,b,Aeq,beq);
+    
+    beta = soln(1:p);
+    s = soln((p+1):(p+n));
+    

### 2013-09-29 code/noiseless_test.m

@@ -1,0 +1,36 @@
+n = 40;
+p = 200;
+
+s = 1;
+
+X = randn(p,n);
+%X = X./(sqrt(sum(X.^2,2))*ones(1,n));  
+
+A = eye(s);
+%y = (1/2)*diag(X(1:s,:)'*A*X(1:s,:));
+%y = randn(n,1);
+%beta = zeros(p,1);
+%beta(1:s) = 0.5;
+%noise = rand(n,1)*2;
+%noise(1)=0;
+%y = X'*beta + noise;
+y = X(1,:)';
+
+Delta = zeros(p,n);
+
+%v = zeros(n,1);
+
+%for ii=1:n
+%    Delta(:,ii) = X(:,ii) - X(:,1);
+%    v(ii) = y(ii) - y(1);
+%end
+
+%[beta,S] = convexNoiseless(Delta,v,0);
+
+[beta,S] = convexNoiseless(X,y,0);
+
+norm(beta,1)
+norm(X(1:s,1),1)
+
+plot(abs(beta),'r.')
+

### 2013-09-29 code/outer_approximation_plot.m

@@ -1,0 +1,15 @@
+x1 = (-100:1:100)/100;
+x2=  [-1,-.6,-.1,.4,1]
+
+y1 = -.5*(1-x1.^2).^(1/2);
+y2 = -.5*(1-x2.^2).^(1/2);
+
+figure;
+hold on;
+plot(x1,y1,'LineWidth',2);
+plot(x2,y2,'k','LineWidth',2);
+plot(x2,y2,'o','MarkerFaceColor','black','MarkerSize',7);
+
+set(gca,'XTick',[]);
+set(gca,'YTick',[]);
+axis off;

### 2013-09-29 code/plot_several_variable_selection_experiments.m

@@ -1,0 +1,46 @@
+variable_selection_manual = 1;
+
+p=200; k=10; s=5; n=200; sigma=0;
+lambda = 0.001; mu=0.01; maxiter=300;
+
+variable_selection_script;
+
+figure;
+plot(1:p, sum(abs(beta),2), '*r');
+title('p=200, k=10, s=5, n=200, sigma=0');
+
+%%%%%%
+
+p=200; k=20; s=5; n=200; sigma=0;
+lambda = 0.001; mu=0.01; maxiter=300;
+
+variable_selection_script;
+
+figure;
+plot(1:p, sum(abs(beta),2), '*r');
+title('p=200, k=20, s=5, n=200, sigma=0');
+
+%%%%%%%%%%%%%
+
+p=200; k=20; s=5; n=400; sigma=0;
+lambda = 0.001; mu=0.01; maxiter=300;
+
+variable_selection_script;
+
+figure;
+plot(1:p, sum(abs(beta),2), '*r');
+title('p=200, k=20, s=5, n=400, sigma=0');
+
+%%%%%%%%%%%
+
+p=100; k=10; s=5; n=300; sigma=0.1;
+lambda = 0.0001*n; mu=0.01; maxiter=500;
+
+variable_selection_script;
+
+figure;
+plot(1:p, sum(abs(beta),2), '*r');
+%title('p=100, k=10, s=5, n=300, sigma=0.1');
+
+[sum(beta.^2,2),sum(beta_stars.^2,2)]
+

### 2013-09-29 code/runAndPlot.m

@@ -1,0 +1,70 @@
+function [out] = runAndPlot(params)
+
+n=params.n;   p=params.p;   noise=params.noise;
+s=params.s;
+gamma = params.gamma;
+fig_name = params.fig_name;
+
+use_quad=params.use_quad;   use_lin=params.use_lin;
+use_cube=params.use_cube;   use_logexp=params.use_logexp;
+
+maxit = 3000;
+mu = .1;
+
+lambda = noise*sqrt(s*log(p)/n)*n; 
+lambda = max(lambda,1e-3*n);
+
+X = randn(p,n)/2;
+
+K = 4;
+beta_star = randn(p,K);
+beta_star((s+1):p,:)=0;
+y_lin = max(X'*beta_star,[],2);
+
+tmp = randn(s,s);
+A = tmp*tmp' + 0.5*eye(s);
+A = A/norm(A,2);
+y_quad = diag(X(1:s,:)'*A*X(1:s,:));
+
+y_cube = sum(abs(X(1:s,:)).^3,1)';
+
+beta_exp = rand(s,1)+0.2;
+y_logexp = log(sum(exp((beta_exp*ones(1,n)).*X(1:s,:)),1))';
+
+y = use_lin*y_lin + use_quad*y_quad + ...
+    use_cube*y_cube + use_logexp*y_logexp + noise*randn(n,1);
+
+[beta1,D,h1,obj1] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit);
+[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda,mu,maxit);
+
+fig_handle = figure;
+% plot things here!
+C = [beta1,D];
+weights1 = max(abs(C),[],2);
+weights2 = max(abs(beta2),[],2);
+
+weights1 = min(weights1,0.5);
+weights2 = min(weights2,0.5);
+
+hold on;
+plot(1:p, weights1,'or','MarkerSize',7);
+plot(1:p, weights2, '*b', 'MarkerSize',7);
+
+mean1 = [mean(weights1(1:s))*ones(s,1); mean(weights1(s+1:p))*ones(p-s,1)];
+mean2 = [mean(weights2(1:s))*ones(s,1); mean(weights2(s+1:p))*ones(p-s,1)];
+
+plot(1:p, mean1, '--r', 'LineWidth',1);
+plot(1:p, mean2, '--b', 'LineWidth',1);
+
[…]

### 2013-09-29 code/runAndPlot_script.m

@@ -1,0 +1,131 @@
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 300;
+params.p = 40;
+params.noise = 0.05;
+params.s = 3;
+params.gamma = 0.5;
+
+params.fig_name = 'QuadLin3';
+params.use_quad = 1;
+params.use_lin = 1;
+params.use_cube = 0;
+params.use_logexp = 0;
+
+out = runAndPlot(params);
+
+
+%==========%
+
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 120;
+params.p = 40;
+params.noise = 0.05;
+params.s = 3;
+params.gamma = 0.05;
+
+params.fig_name = 'QuadLin2';
+params.use_quad = 1;
+params.use_lin = 1;
+params.use_cube = 0;
+params.use_logexp = 0;
+
+out = runAndPlot(params);
+
+%==========%
+
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 120;
+params.p = 40;
+params.noise = 0.05;
+params.s = 3;
+params.gamma = 0.5;
+
+params.fig_name = 'QuadLin';
+params.use_quad = 1;
+params.use_lin = 1;
+params.use_cube = 0;
+params.use_logexp = 0;
+
+out = runAndPlot(params);
+
+%==========%
+
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 100;
+params.p = 40;
+params.noise = 0.02;
+params.s = 3;
+params.gamma = 0.5;
+
+params.fig_name = 'Quadratic';
+params.use_quad = 1;
+params.use_lin = 0;
+params.use_cube = 0;
+params.use_logexp = 0;
+
+out = runAndPlot(params);
+
+%==========%
+
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 100;
+params.p = 40;
+params.noise = 0.02;
+params.s = 3;
+params.gamma = 0.5;
+
+params.fig_name = 'Logexp';
+params.use_quad = 0;
+params.use_lin = 0;
+params.use_cube = 0;
+params.use_logexp = 1;
+
+out = runAndPlot(params);
+
+%==========%
+
+clc; clear all; close all;
+randn('state',123); rand('state',0);
+
+params.n = 100;
+params.p = 40;
+params.noise = 0.02;
+params.s = 3;
[…]

### 2013-09-29 code/side_exp/grouplasso_script.r

@@ -1,0 +1,55 @@
+
+# OUT:  
+#   "gold" is smallest magnitude of correct
+#   "lead" is the largest magnitude of incorr
+
+runExp <- function(p, s, k, sigma, lambda){
+
+	mu = rbind(matrix(abs(rnorm(s*k)),s,k), matrix(0,p-s,k));
+	# mu = [non-zero; zero]
+	
+	epsilon = matrix(rnorm(p*k)*sigma, p,k);
+	
+	y = mu+epsilon;
+	
+	mu_hat = matrix(0,p,k);
+	for (i in 1:p){
+		mu_hat[i,] = y[i,] - l1Project(y[i,], lambda);
+	}
+	
+	weights = apply(abs(mu_hat), 1, max);
+	
+	gold = min(weights[1:s]);
+	lead = max(weights[(s+1):p]);
+	
+	return(list(gold=gold, lead=lead));
+}
+
+l1Project <- function(vec, lambda) {
+	abs_ix = order(abs(vec),decreasing=TRUE);
+	n = length(abs_ix);
+	
+	quantities = cumsum(abs( vec[abs_ix]) ) - 
+				c( abs( vec[abs_ix[2:n]] ),0) *  1:n;
+	
+	if (quantities[n] < lambda) {
+		return(vec);
+	} else {	
+		j_star = which (quantities >= lambda)[1];
+	}
+	
+	
+	if (j_star < n){
+		vec[abs_ix[(j_star+1):n]] = 0;
+	}
+	current_sum = sum(abs(vec[abs_ix[1:j_star]]));
+	
+	vec[abs_ix[1:j_star]] = sign( vec[abs_ix[1:j_star]] ) * 
+		(	abs(vec[abs_ix[1:j_star]]) -  (current_sum - lambda)/j_star );
+		
+	return(vec);
+}	
+
+k = 1000;
+res = runExp(1000,3,k,0.5,k*0.05*log(k));
+print(res)

### 2013-09-29 code/side_exp/multiLasso.r

@@ -1,0 +1,103 @@
+#IN:  "X"  (k--by--p) matrix 
+#		"Y"  (k) vector,		"lambda"
+#		
+#OUT: "B"  (p--by--k) matrix
+#
+# solves:
+# 1/2 | Y - diag(X*B) |^2 + lambda | B |_{1,inf}
+
+multiLasso <- function(X, Y, lambda){
+
+	k = nrow(X);  p=ncol(X);  max_iter = 200;
+	B = matrix(0, p, k);
+	
+	prev_obj = Inf;
+	stepsize = 0.5;
+	armijo_sigma = 0.2;
+	armijo_beta = 0.9;
+	
+	for (it in 1:max_iter){
+		
+		# loss_gradient
+		loss_gradient = - diag( as.vector( Y - diag(X %*% B )) )%*% X;
+		loss_gradient = t(loss_gradient); # p--by--k after tranpose
+		
+		# penalty_gradient
+		#max_ixs = apply(abs(B), 1, which.max);
+		#max_ixs2 = cbind(1:p, max_ixs);
+		#pen_gradient = matrix(0, p, k);
+		#pen_gradient[max_ixs2] = lambda*sign(B[max_ixs2]) * matrix(1,p,1);
+		
+		new_B = matrix(0, p, k);
+		new_obj = 0;
+		while(TRUE){
+			tmp = B - stepsize*loss_gradient;
+			for (ii in 1:p){
+				new_B[ii,] = tmp[ii,] - l1Project(tmp[ii,], lambda);
+			}
+			
+			new_obj = 0.5 * sum( (Y - diag(X %*% new_B)) ^ 2) + lambda * sum(apply(abs(new_B), 1, max));
+			
+			if ( new_obj < prev_obj + 
+			          sum(diag( t(loss_gradient) %*% (new_B - B) )) + 
+					   1/(2*stepsize) * sum(apply((new_B - B)^2,1,sum)) ){
+				break;
+			} else {
+				stepsize = stepsize*armijo_beta;
+			}
+			
+			if (stepsize < 1e-5){
+				print(c(prev_obj, new_obj));
+				print("Line search does not terminate");
+				return(0);
+			}
+		} #end-while
+		
+		B = new_B;		
+		print(c("iter:", it, "obj:", new_obj, "stepsize:", stepsize)); 
+		flush.console();
[…]

### 2013-09-29 code/support_recovery_script.m

@@ -1,0 +1,93 @@
+%clc; clear all; close all; randn('state',123); rand('state',0);
+
+noise = 0.05;
+s = 3; K = 6;
+
+lambda0 = 1;
+%lambda_ls = [lambda0/30, lambda0/10, lambda0/3, lambda0, lambda0*3];
+lambda_ls = 0.5;
+
+p_ls = 50;
+n_ls = 1200:100:1400;
+succ_prob_ls = zeros(length(n_ls),length(p_ls),length(lambda_ls));
+false_discovery = zeros(length(n_ls),length(p_ls),length(lambda_ls));
+false_neglect = zeros(length(n_ls),length(p_ls),length(lambda_ls));
+
+maxit = 2000; mu = 0.1;
+
+num_trials = 5;
+
+for ii=1:length(n_ls)
+for ij=1:length(p_ls)
+    n = n_ls(ii);
+    p = p_ls(ij);
+   
+    %lambda0 = max(noise*sqrt(s*log(p)/n)*n, 1e-5); 
+   
+    
+    
+    for il=1:length(lambda_ls)
+    num_succ=0;
+    num_false_discovery=0;
+    num_false_neglect=0;
+    for it = 1:num_trials
+        disp(sprintf('ii:%d   it:%d     num_succ:%d\n', ii, it, num_succ));
+        
+        lambda = lambda_ls(il);
+        beta_stars = randn(p,K);
+        beta_stars = beta_stars./(ones(p,1)*sqrt(sum(beta_stars.^2,1)));
+        beta_stars((s+1):p,:) = 0;
+        %alpha_stars = randn(K,1);
+        alpha_stars = zeros(K,1);
+        
+        X = 2*rand(n,p)-1;
+        %X = X./(sqrt(sum(X.^2,2))*ones(1,p));
+        
+        y_lin = max(X*beta_stars + ones(n,1)*alpha_stars', [], 2);
+        
+        A = randn(s,s);
+        A = A*A' + .5*eye(s);
+        A = A/norm(A,2);
+        y_quad = diag(X(:,1:s)*A*X(:,1:s)');
+        
+        y_cube = sum(abs(X(:,1:(s-1))).^3,2);
+        
+        Y = .5*y_cube+.3*y_lin + .5*y_quad + randn(n,1)*noise;
+        
+        %lambda = lambda/10;
[…]

### 2013-09-29 code/support_recovery_script2.m

@@ -1,0 +1,53 @@
+clc; clear all; close all; randn('state',123); rand('state',0);
+
+noise = 0.005;
+s = 4; K = 20;
+
+p_ls = [50,100];
+n_ls = [100,200,300,400,500,600,700,800];
+succ_prob_ls = zeros(length(n_ls),length(p_ls));
+maxit = 1500; mu = 0.01;
+
+num_trials = 10;
+
+for ii=1:length(n_ls)
+for ij=1:length(p_ls)
+    n = n_ls(ii);
+    p = p_ls(ij);
+    lambda = max(0.2*noise*sqrt(s*log(p)/n)*n, 0); 
+    
+    extra_weight = 0;
+    for it = 1:num_trials
+        disp(sprintf('ii:%d   ii:%d     extra_weight:%d\n', ii, it, extra_weight));
+        succ_prob_ls'
+        
+        beta_stars = randn(p,K);
+        beta_stars = beta_stars./(ones(p,1)*sqrt(sum(beta_stars.^2,1)));
+        beta_stars((s+1):p,:) = 0;
+        %alpha_stars = randn(K,1);
+        alpha_stars = zeros(K,1);
+        
+        X = randn(n,p);
+        %X = X./(ones(n,1)*sqrt(sum(X.^2,1)));
+        X = X./5;
+        
+        Y = diag(X(:,1:s)*eye(s)*X(:,1:s)') + noise*randn(n,1);
+        %noiseless_Y = max(X*beta_stars + ones(n,1)*alpha_stars', [], 2);
+        %Y = noiseless_Y + randn(n,1)*noise;
+        
+        [beta2,h2,obj2] = Piecewise_Infinity(X',Y,lambda,mu,maxit);
+        %extra_weight = extra_weight+sum(max(abs(beta2((s+1):p,n)),[],2));
+        
+        %prods = X*beta_stars;
+        %[vals,ixs] = max(prods,[],2);
+        %beta_golds = beta_stars(:,ixs);
+        %extra_weight = extra_weight+sum(max(abs(beta_golds - beta2),[],2))/sum(max(abs(beta_golds),[],2));
+        extra_weight = extra_weight+sum(max(abs(beta2(1:s,:)),[],2))/sum(max(abs(beta2),[],2));
+        
+        close all;
+        %[beta1,h1,obj1] = Piecewise_Convex(X,y,lambda/sqrt(n),mu,maxit);        
+    end
[…]

### 2013-09-29 code/variable_selection_script.m

@@ -1,0 +1,32 @@
+% variable selection
+
+if (~exist('variable_selection_manual'))
+    p = 100; K = 10; s = 4; n = 700; sigma=0;
+    lambda = 0.001; mu = 0.01; maxiter = 1000;
+end
+
+beta_stars = randn(p,K);
+beta_stars = sign(beta_stars).*(abs(beta_stars)+0.2);
+%normalization
+beta_stars = beta_stars./(ones(p,1)*sqrt(sum(beta_stars.^2,1)));
+
+beta_stars((s+1):p,:) = 0; %only the first s coordinates are relevant
+
+alpha_stars = randn(K,1);
+alpha_stars = alpha_stars/norm(alpha_stars);
+
+Xs = randn(n,p);
+Xs = Xs./max(max(abs(Xs)))*3;
+
+Ys = max(Xs*beta_stars + ones(n,1)*alpha_stars', [], 2);
+% Xs*-beta_stars is (n--by--K)
+
+Ys = Ys + randn(n,1)*sigma;
+Ys = Ys - mean(Ys);
+
+[beta,z,obj] = SCAM_QP(Xs',Ys, lambda, maxiter, 1e-4);
+
+% beta is (p--by--n)
+%figure;
+%plot(1:p, sum(abs(beta),2),'.r');
+%[sum(beta.^2,2),sum(beta_stars.^2,2)]

### 2013-09-29 tex/scam/nips13/SCAM_code/C1.m

@@ -1,0 +1,86 @@
+function C1(version)
+% Non-diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 500; v = 0.8;
+    case 01, n = 100; v = 0.2;
+    case 02, n = 200; v = 0.2;
+    case 03, n = 300; v = 0.2;
+    case 04, n = 400; v = 0.2;
+    case 05, n = 500; v = 0.2;
+    case 06, n = 600; v = 0.2;
+    case 07, n = 700; v = 0.2;
+    case 08, n = 800; v = 0.2;
+    case 09, n = 900; v = 0.2;
+    case 10, n =1000; v = 0.2;
+        
+    case 11, n = 100; v = 0.4;
+    case 12, n = 200; v = 0.4;
+    case 13, n = 300; v = 0.4;
+    case 14, n = 400; v = 0.4;
+    case 15, n = 500; v = 0.4;
+    case 16, n = 600; v = 0.4;
+    case 17, n = 700; v = 0.4;
+    case 18, n = 800; v = 0.4;
+    case 19, n = 900; v = 0.4;
+    case 20, n =1000; v = 0.4;
+        
+    case 21, n = 100; v = 0.6;
+    case 22, n = 200; v = 0.6;
+    case 23, n = 300; v = 0.6;
+    case 24, n = 400; v = 0.6;
+    case 25, n = 500; v = 0.6;
+    case 26, n = 600; v = 0.6;
+    case 27, n = 700; v = 0.6;
+    case 28, n = 800; v = 0.6;
+    case 29, n = 900; v = 0.6;
+    case 30, n =1000; v = 0.6;
+        
+    case 31, n = 100; v = 0.8;
+    case 32, n = 200; v = 0.8;
+    case 33, n = 300; v = 0.8;
+    case 34, n = 400; v = 0.8;
+    case 35, n = 500; v = 0.8;
+    case 36, n = 600; v = 0.8;
+    case 37, n = 700; v = 0.8;
+    case 38, n = 800; v = 0.8;
+    case 39, n = 900; v = 0.8;
+    case 40, n =1000; v = 0.8;
+    otherwise, return
+end
+
+p = 128; k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6;
+nrun = 200; J = ones(p,nrun)==0; Ln = zeros(p,nrun);
[…]

### 2013-09-29 tex/scam/nips13/SCAM_code/LASSO.m

@@ -1,0 +1,34 @@
+function LASSO(data)
+clc; close all; format long; randn('state',0); rand('state',0);
+switch data
+    case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
+            [p,n] = size(X); q = p; 
+    case 2, load diabetes; X = diabetes.x'; y = diabetes.y; [p,n] = size(X); q = p;
+    otherwise, return
+end
+mrun = 10; b = 5; m = fix(n/b); err = zeros(2,q+1,mrun);
+for run = 1:mrun
+    ord = randperm(n); 
+    for i = 1:b
+        ndx = ones(n,1)==0; 
+        if i<b, ndx(ord((i-1)*m+1:i*m))=1==1; else ndx(ord((i-1)*m+1:end))=1==1; end
+        erri = LASSO_Main(X,y,ndx,q); 
+        err(:,:,run) = err(:,:,run) + erri./([b-1; 1]*ones(1,q+1));
+    end
+end
+out = [(0:q)' mean(err,3)' std(err,1,3)']
+save(['SCAM/LASSO_' num2str(data) '.mat'],'out');
+return
+
+function [err,yo] = LASSO_Main(X,y,ndx,q)
+[p,n] = size(X); [X1,X2] = SCAM_Unit(X,ndx);
+y1 = y(~ndx); ym = mean(y1); y2 = y(ndx);
+beta0 = lars(X1',y1-ym,'lasso',0,0,[],0); 
+num = sum(abs(beta0)>10^-8,2); err = zeros(2,q+1); yo = zeros(n,q+1);
+for j = 1:q+1 % Refitting
+    row = find(num==j-1,1); active = find(abs(beta0(row,:))>10^-8); 
+    beta1 = (X1(active,:)')\(y1-ym); % beta1 = beta0(row,active)';
+    yo(~ndx,j) = X1(active,:)'*beta1+ym; yo(ndx,j) = X2(active,:)'*beta1+ym;
+    err(:,j) = [sum((yo(~ndx,j)-y1).^2); sum((yo(ndx,j)-y2).^2)]/n;
+end
+return

### 2013-09-29 tex/scam/nips13/SCAM_code/R.m

@@ -1,0 +1,94 @@
+function R(version)
+% Non-diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 100; alpha = 0.2;
+    case 01, n = 100; alpha = 0.0;
+    case 02, n = 200; alpha = 0.0;
+    case 03, n = 300; alpha = 0.0;
+    case 04, n = 400; alpha = 0.0;
+    case 05, n = 500; alpha = 0.0;
+    case 06, n = 600; alpha = 0.0;
+    case 07, n = 700; alpha = 0.0;
+    case 08, n = 800; alpha = 0.0;
+    case 09, n = 900; alpha = 0.0;
+    case 10, n =1000; alpha = 0.0;
+        
+    case 11, n = 100; alpha = 0.2;
+    case 12, n = 200; alpha = 0.2;
+    case 13, n = 300; alpha = 0.2;
+    case 14, n = 400; alpha = 0.2;
+    case 15, n = 500; alpha = 0.2;
+    case 16, n = 600; alpha = 0.2;
+    case 17, n = 700; alpha = 0.2;
+    case 18, n = 800; alpha = 0.2;
+    case 19, n = 900; alpha = 0.2;
+    case 20, n =1000; alpha = 0.2;
+        
+    case 21, n = 100; alpha = 0.5;
+    case 22, n = 200; alpha = 0.5;
+    case 23, n = 300; alpha = 0.5;
+    case 24, n = 400; alpha = 0.5;
+    case 25, n = 500; alpha = 0.5;
+    case 26, n = 600; alpha = 0.5;
+    case 27, n = 700; alpha = 0.5;
+    case 28, n = 800; alpha = 0.5;
+    case 29, n = 900; alpha = 0.5;
+    case 30, n =1000; alpha = 0.5;
+        
+    case 31, n = 100; alpha = 1.0;
+    case 32, n = 200; alpha = 1.0;
+    case 33, n = 300; alpha = 1.0;
+    case 34, n = 400; alpha = 1.0;
+    case 35, n = 500; alpha = 1.0;
+    case 36, n = 600; alpha = 1.0;
+    case 37, n = 700; alpha = 1.0;
+    case 38, n = 800; alpha = 1.0;
+    case 39, n = 900; alpha = 1.0;
+    case 40, n =1000; alpha = 1.0;
[…]

### 2013-09-29 tex/scam/nips13/SCAM_code/README.m

@@ -1,0 +1,21 @@
+%=====================================%
+% Sparse Convex Additive Model
+% Author name withheld
+% Last Edit: 5/31/2013
+%
+% use the MOSEK matlab toolbox (academic license availabe for free) for best effect
+% uses the MOSEK quadprog function
+
+% main function is SCAM_QP.m
+% T.m file contains code for synthetic experiment
+
+% Example usage:
+
+n = 600;
+p = 100;
+k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6; Q = eye(k);
+X = randn(p,n); y = sum(X(1:k,:).*(Q*X(1:k,:)),1)' + randn(n,1);
+[beta,h,obj] = SCAM_QP(X,y-mean(y),lambda,maxit,tol);
+
+% magnitudes is p-dimensional, large magnitudes == relevant variables
+magnitudes = max(abs(beta),[],2);

### 2013-09-29 tex/scam/nips13/SCAM_code/SCAM.m

@@ -1,0 +1,38 @@
+function SCAM(version)
+clc; close all; format long; randn('state',0); rand('state',0);
+lambda0 = {[0.00 .005 0.01 .015 0.02 0.04 0.06 0.07 0.08 0.09 0.10 0.12 0.20 0.30 0.40],...
+           };
+nd = size(lambda0,2); nv = zeros(1,nd); for i = 1:nd, nv(i) = length(lambda0{i}); end
+data = sum(version>cumsum(nv)) + 1; lambda = lambda0{data}(version - sum(nv(1:data-1)));
+switch data
+    case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
+    % case 2, 
+    otherwise, return
+end
+
+[p,n] = size(X); mrun = 10; b = 5; m = fix(n/b); % 5-fold CV
+err = zeros(2,mrun); num = zeros(1,mrun);
+for run = 1:mrun
+    ord = randperm(n);
+    for i = 1:b
+        ndx = ones(n,1)==0;
+        if i<b, ndx(ord((i-1)*m+1:i*m))=1==1; else ndx(ord((i-1)*m+1:end))=1==1; end
+        [erri,numi] = SCAM_Main(X,y,ndx,lambda);
+        err(:,run) = err(:,run) + erri./[b-1; 1]; num(run) = num(run) + numi/b;
+        disp(['run=' num2str(run) ' cv=' num2str(i)]);
+    end
+end
+out = [mean(num) mean(err,2)' std(err,1,2)']
+save(['SCAM/SCAM_' num2str(version) '.mat'],'out');
+return
+
+function [err,num,yo] = SCAM_Main(X,y,ndx,lambda)
+[p,n] = size(X); [X1,X2] = SCAM_Unit(X,ndx);
+y1 = y(~ndx); ym = mean(y1); y2 = y(ndx); maxit = 20; tol = 10^-6;
+[beta0,h0,obj0,Ln0] = SCAM_QP(X1,y1-ym,lambda,maxit,tol);
+active = find(abs(Ln0)>10^-8); num = length(active);
+[beta1,h1,obj1,Ln1] = SCAM_QP(X1(active,:),y1-ym,0,maxit,tol);
+h2 = SCAM_Eval(X2(active,:),X1(active,:),beta1,h1);
[…]

### 2013-09-29 tex/scam/nips13/SCAM_code/SCAM_Unit.m

@@ -1,0 +1,5 @@
+function [X1,X2,Xm,Xstd] = SCAM_Unit(X,ndx)
+[p,n] = size(X); n1 = sum(~ndx); X1 = X(:,~ndx); Xm = mean(X1,2);
+X1 = X1 - Xm*ones(1,n1); Xstd = sqrt(sum(X1.^2,2))+eps; X1 = X1./(Xstd*ones(1,n1)); 
+X2 = (X(:,ndx) - Xm*ones(1,n-n1))./(Xstd*ones(1,n-n1));
+return

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/C.m

@@ -1,0 +1,83 @@
+function C(version)
+% Diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 100; v = 0.0;
+    case 01, n = 100; v = 0.0;
+    case 02, n = 200; v = 0.0;
+    case 03, n = 300; v = 0.0;
+    case 04, n = 400; v = 0.0;
+    case 05, n = 500; v = 0.0;
+    case 06, n = 600; v = 0.0;
+    case 07, n = 700; v = 0.0;
+    case 08, n = 800; v = 0.0;
+    case 09, n = 900; v = 0.0;
+    case 10, n =1000; v = 0.0;
+        
+    case 11, n = 100; v = 0.2;
+    case 12, n = 200; v = 0.2;
+    case 13, n = 300; v = 0.2;
+    case 14, n = 400; v = 0.2;
+    case 15, n = 500; v = 0.2;
+    case 16, n = 600; v = 0.2;
+    case 17, n = 700; v = 0.2;
+    case 18, n = 800; v = 0.2;
+    case 19, n = 900; v = 0.2;
+    case 20, n =1000; v = 0.2;
+        
+    case 21, n = 100; v = 0.5;
+    case 22, n = 200; v = 0.5;
+    case 23, n = 300; v = 0.5;
+    case 24, n = 400; v = 0.5;
+    case 25, n = 500; v = 0.5;
+    case 26, n = 600; v = 0.5;
+    case 27, n = 700; v = 0.5;
+    case 28, n = 800; v = 0.5;
+    case 29, n = 900; v = 0.5;
+    case 30, n =1000; v = 0.5;
+  
+    case 31, n = 100; v = 0.9;
+    case 32, n = 200; v = 0.9;
+    case 33, n = 300; v = 0.9;
+    case 34, n = 400; v = 0.9;
+    case 35, n = 500; v = 0.9;
+    case 36, n = 600; v = 0.9;
+    case 37, n = 700; v = 0.9;
+    case 38, n = 800; v = 0.9;
+    case 39, n = 900; v = 0.9;
+    case 40, n =1000; v = 0.9;
+    otherwise, return
+end
+
+p = 128; k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6;
+nrun = 200; J = ones(p,nrun)==0; Ln = zeros(p,nrun); Q = eye(k);
+
[…]

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/SCAM_ADMM.m

@@ -1,0 +1,59 @@
+function [C,h,obj,Ln] = SCAM_ADMM(X,y,lambda,mu,maxit)
+[p,n] = size(X); dX = zeros(p,n-1); ord = zeros(p,n); Ln = zeros(p,maxit);
+for d = 1:p, [Xd,ord(d,:)] = sort(X(d,:)); dX(d,:) = Xd(2:n)-Xd(1:n-1); end
+beta = zeros(p,n-1); M = zeros(p,n-1); S = zeros(p,n-2); W = zeros(p,n-2);
+C = zeros(p,n-1); O = zeros(p,n-1); q = zeros(p,1); iter = 0; obj = [];
+G = gallery('tridiag',-ones(1,n-2),[2 3*ones(1,n-3) 2],-ones(1,n-2));
+A = gallery('tridiag',-ones(1,n-1),[1 2*ones(1,n-2) 1],-ones(1,n-1));
+B = inv(A+ones(n,n)); B1 = zeros(n,n); B2 = eye(n);
+for d = 1:p, B1(ord(d,:),:) = B; B1(:,ord(d,:)) = B1; B2 = B2+1/(mu*n)*B1; end; B2 = inv(B2);
+rg = (0:n-2)*(n-1)+(1:n-1); ndx = (ord-1)*p + repmat((1:p)',[1 n]);
+ndx1 = (ord(:,1:n-1)-1)*p + repmat((1:p)',[1 n-1]);
+ndx2 = (ord(:,2:n)-1)*p + repmat((1:p)',[1 n-1]);
+while iter < maxit
+    iter = iter + 1;
+    for d = 1:p, C(d,:) = Piecewise_Inf(beta(d,:)-1/mu*O(d,:),lambda/mu); end
+    
+    h = zeros(p,n); eta = 1/(mu*n)*repmat(y',[p 1])-1/mu*repmat(q,[1 n]);
+    resp = dX.*beta-1/mu*M; eta(ndx) = eta(ndx) + [zeros(p,1) resp] - [resp zeros(p,1)];
+    h(ndx) = eta(ndx)*B; vec = B2*(sum(h,1)'); h(ndx) = h(ndx) - 1/(mu*n)*vec(ord)*B;
+    
+    dh = h(ndx2) - h(ndx1);
[…]

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/SCAM_Eval.m

@@ -1,0 +1,8 @@
+function ht = SCAM_Eval(Xt,X,beta,h)
+[p,n] = size(X); nt = size(Xt,2); ht = zeros(p,nt);
+for d = 1:p
+    [vv,ss] = sort(X(d,:)); 
+    ht(d,:) = max(repmat(h(d,ss(1:n-1)),[nt,1]) + repmat(beta(d,:),[nt,1]) ...
+        .*(repmat(Xt(d,:)',[1,n-1])-repmat(X(d,ss(1:n-1)),[nt,1])),[],2);
+end
+return

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/SCAM_QP.m

@@ -1,0 +1,60 @@
+function [beta,z,obj,Ln] = SCAM_QP(X,y,lambda,maxit,tol)
+[p,n] = size(X); z = zeros(p,n); Ln = zeros(p,1); beta = zeros(p,n-1);
+res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
+while iter < maxit && change > tol
+    iter = iter + 1;
+    
+    for d = 1:p
+        res = res + z(d,:)';
+        [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK(res,X(d,:),lambda);
+        res = res - z(d,:)';
+    end
+    
+    obj(iter) = 0.5/n*sum(res.^2) + lambda*sum(Ln);
+    if iter>1, change = abs(obj(iter-1)-obj(iter))/obj(iter-1); end
+    if mod(iter,10)==0
+        disp(['   SCAM_QP:    Iteration ' num2str(iter) ' Objective ' num2str(obj(iter))]);
+        figure(9); subplot(2,1,1); plot(1:n,y,'ko',1:n,sum(z,1)','r+'); title('Response');
+        subplot(2,1,2); plot(1:p,Ln,'r.'); title('L\infty norm'); drawnow;
+    end
+end
+return
+
+function [beta,z,Ln] = SCAM_MOSEK(y,x,lambda)
+n = length(x); [Xd,ord] = sort(x'); dX = Xd(2:n)-Xd(1:n-1);
+Hi = 1:2*n; Hj = 1:2*n; Hs = [ones(1,n)/n,10^-6*ones(1,n)];
+% Use 10^-6 instead of 0 to make this QP strictly convex.
+H = sparse(Hi,Hj,Hs,2*n,2*n); f = [-y/n; zeros(n-1,1); lambda];
+Ai = []; Aj = []; As = []; row = 0; ndx = 0;
+valmat = [ones(n-2,1) -ones(n-2,1)];
+rowmat = [(1:(n-2))' (1:(n-2))'] + row;
+colmat = [((n+1):(2*n-2))' ((n+2):(2*n-1))'];
+rg = (ndx+1):(ndx+2*(n-2)); row = row + (n-2); ndx = ndx + 2*(n-2);
[…]

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/SCAM_View.m

@@ -1,0 +1,58 @@
+data = 1;
+clc; close all; format long; randn('state',0); rand('state',0);
+lambda0 = {[0.00 .005 0.01 .015 0.02 0.04 0.06 0.07 0.08 0.09 0.10 0.12 0.20 0.30 0.40],...
+           };
+nd = size(lambda0,2); nv = zeros(1,nd); for i = 1:nd, nv(i) = length(lambda0{i}); end
+switch data
+    case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
+    % case 2, 
+    otherwise, return
+end
+
+[p,n] = size(X); output = zeros(nv(data),5);
+for version = sum(nv(1:data-1))+1:sum(nv(1:data))
+    load(['SCAM/SCAM_' num2str(version) '.mat']); output(version-sum(nv(1:data-1)),:) = out;
+end
+load(['SCAM/LASSO_' num2str(data) '.mat']);
+figure(1); set(gca,'FontSize',14);
+errorbar(out(:,1),out(:,3),out(:,5),'g--','LineWidth',2); hold on
+errorbar(output(:,1),output(:,3),output(:,5),'k:','LineWidth',2); hold off
+legend('LASSO','SCAM'); xlim([-1 out(end,1)+1])
+xlabel('Average number of seleted features'); ylabel('Testing Mean Squared Error')
+title('Testing errors for LASSO and SCAM');
+
+% Analysis using all the data.
+names = {{'CRIM','ZN','INDUS','CHAS','NOX','RM','AGE','DIS','RAD','TAX','PTRATIO','B','LSTAT'},...
+         }; 
+
+X1 = SCAM_Unit(X,ones(1,n)==0); ym = mean(y); maxit = 20; tol = 10^-6; beta = []; Ln = [];
+for run = 1:nv(data)
+    [beta(:,:,run),h,obj,Ln(:,run)] = SCAM_QP(X1,y-ym,lambda0{data}(run),maxit,tol); 
+end
+ratio = sum(Ln,1)/sum(Ln(:,1),1);
+figure(2); set(0,'DefaultAxesColorOrder',[1 0 0;0 1 0;0 0 1;0 0 0;1 1 0],...
+      'DefaultAxesLineStyleOrder','-|--|:|-.'); set(gca,'FontSize',12);
+fg2 = plot(ratio,Ln,'LineWidth',2);
[…]

### 2013-09-29 tex/scam/nips13/scam_nips_appendix_and_code/SCAM_code/lars.m

@@ -1,0 +1,218 @@
+function beta = lars(X, y, method, stop, useGram, Gram, trace)
+% LARS  The LARS algorithm for performing LAR or LASSO.
+%    BETA = LARS(X, Y) performs least angle regression on the variables in
+%    X to approximate the response Y. Variables X are assumed to be
+%    normalized (zero mean, unit length), the response Y is assumed to be
+%    centered.
+%    BETA = LARS(X, Y, METHOD), where METHOD is either 'LARS' or 'LARS'  
+%    determines whether least angle regression or lasso regression should
+%    be performed. 
+%    BETA = LARS(X, Y, METHOD, STOP) with nonzero STOP will perform least
+%    angle or lasso regression with early stopping. If STOP is negative,
+%    STOP is an integer that determines the desired number of variables. If
+%    STOP is positive, it corresponds to an upper bound on the L1-norm of
+%    the BETA coefficients.
+%    BETA = LARS(X, Y, METHOD, STOP, USEGRAM) specifies whether the Gram
+%    matrix X'X should be calculated (USEGRAM = 1) or not (USEGRAM = 0).
+%    Calculation of the Gram matrix is suitable for low-dimensional
+%    problems. By default, the Gram matrix is calculated.
+%    BETA = LARS(X, Y, METHOD, STOP, USEGRAM, GRAM) makes it possible to
+%    supply a pre-computed Gram matrix. Set USEGRAM to 1 to enable. If no
+%    Gram matrix is available, exclude argument or set GRAM = [].
+%    BETA = LARS(X, Y, METHOD, STOP, USEGRAM, GRAM, TRACE) with nonzero
+%    TRACE will print the adding and subtracting of variables as all
+%    LARS/lasso solutions are found.
+%    Returns BETA where each row contains the predictor coefficients of
+%    one iteration. A suitable row is chosen using e.g. cross-validation,
+%    possibly including interpolation to achieve sub-iteration accuracy.
+
+
+%% Input checking
+% Set default values.
+if nargin < 7
+    trace = 0;
+end
+if nargin < 6
+  Gram = [];
+end
+if nargin < 5
+  useGram = 1;
+end
+if nargin < 4
+  stop = 0;
+end
+if nargin < 3
[…]

### 2013-09-29 tex/scam/optimization.tex
various edits. Added new mean parameter to opti

@@
 \begin{equation}\nonumber
-          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
+          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
+                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
 \end{equation}
@@
 \begin{equation}\begin{split}\label{np}
-       &\min_{\bds{h},\bds{\beta}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl(y_{i}-\sum_{k=1}^{p}h_{ki}\Bigr)^{2} + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
-       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
+       &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
+                     \Bigl( y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
+                         + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
+       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), 
+                                 \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
 \end{split}\end{equation}
-Let $\{(1),(2),\ldots,(n)\}$ be a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+Where $\mu \in \R$ is a mean parameter introduced because $f$ may not have zero-mean, and where $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
 It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
-\begin{eqnarray}
-  \nonumber \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ \nonumber
+\begin{align*}
+  \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = 
+            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = 
+            \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
       & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \nonumber \forall j<i,         &h_{k(j)}-h_{k(i)} = \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ \nonumber
+  \forall j<i, &h_{k(j)}-h_{k(i)} =
+                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = 
+                \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
      & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
-\end{eqnarray}
+\end{align*}
 The $\ell_\infty/\ell_1$ penalty
@@
 The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints.
-Directly applying a QP solver would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
+The optimal $\mu$ has a closed form solution of $\mu = \frac{1}{n}\sum_{i=1}^n Y_i$, which is easy to derive from the KKT theorem and the constraints that $\sum_i h_{ki} = 0$ for all $k$.
+Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
 in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
@@
 \begin{equation}\begin{split}\nonumber
-       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} + \lambda\gamma_{k} \\
+       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
+                       \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri}-\mu)-h_{ki}\Bigr)^{2} 
+                         + \lambda\gamma_{k} \\
         &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
@@
 \begin{equation}\nonumber
-      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj}) = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\}.
+      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj})+\mu = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} + \mu.
 \end{equation}
-
-%% Why hats here?  Turning them off (JDL)
-\def\hat#1{#1}
 
@@
 constraints, which simplifies theoretical analysis.
-Define $\hat{d}_{k(i)}$ as the gradient increment:
-$\hat{d}_{k(1)} = \hat{\beta}_{k(1)}$, and $\hat{d}_{k(2)} =
-\hat{\beta}_{k(2)} - \hat{\beta}_{k(1)}$. The convexity constraint is
-equivalent to the constraint that $\hat{d}_{k(i)} \geq 0$ for all $i >
+Define $d_{k(i)}$ as the second derivative:
+$d_{k(1)} = \beta_{k(1)}$, and $d_{k(2)} =
+\beta_{k(2)} - \beta_{k(1)}$. The convexity constraint is
+equivalent to the constraint that $d_{k(i)} \geq 0$ for all $i >
 1$.
 
-It is easy to verify that $\hat{\beta}_{k(i)} = \sum_{j \leq i} \hat{d}_{k(i)}$ and 
+It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(i)}$ and 
 \[
-\hat{f}_k(x_{k(i)}) = \hat{f}_k({x_{k(1)}}) +\hat{d}_{k(1)} ( x_{k(i)}
-- x_{k(1)}) + \hat{d}_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + \hat{d}_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
+f_k(x_{k(i)}) = f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)}
+- x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
 \]
@@
 $n-1$ dimensional vector.
-Then $\hat{f}_k(x_{ki}) = \Delta(x_{ki})^\tran \hat{d}_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$.
+Then $f_k(x_{ki}) = \Delta(x_{ki})^\tran d_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$.
 Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$.
@@
 \begin{align}
-\min_{\{d_k \in \R^{n-1}, c_k \in \R\}}& \frac{1}{2n} \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
+\min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
+               \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) -\mu \Bigr\|_2^2 
+               + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
 \trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
@@
 \label{rem:bounded_lipschitz_constraints}
-For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|\hat{f}_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $\hat{f}_k$ must be $L$-Lipschitz.
+For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|f_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $f_k$ must be $L$-Lipschitz.
 We use these constraints only in the proof for technical reasons; we never need nor use these constraints in our experiments.
 \end{remark}
-
-%% turn the hat back on (JDL)
-\def\hat#1{\widehat{#1}}

### 2013-09-29 tex/scam/sparsistency.tex
various edits. Added new mean parameter to opti

--- 2013-09-29 tex/scam/nips13/sparsistency.tex
@@
 technique''~\cite{Wain:09a}.
-Primal-dual witness explicitly solves all the dual variables.
-Because our optimization is more complex, we do not solve the dual variables on $S$, we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.
+Primal-dual witness explicitly solves all the dual variables, but because our optimization is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.
 
@@
 \label{thm:deterministic}
-Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$.
+Let $\{\hat{d}_k, \hat{c}_k, \hat{\mu} \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$.
 Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
 Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
-\hat{c}_k \mathbf{1})$ be the restricted regression residual. For $k
+\hat{c}_k \mathbf{1}) - \hat{\mu}$ be the restricted regression residual. For $k
 \in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
@@
 \item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
-\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
-\item Let $S \subset \{1,...,p\}$ denote the relevant variables, i.e.,
-  $f_0(X) = f_0(X_S)$, with $s \coloneqq |S|$. 
+\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be $n$ samples of $Y$.
+\item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
+  $f_0(X) = f_0(X_S)$.
+\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \Ef(X)$.
 \end{packed_enum}
@@
 \item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
-\item[A2:] $\|f_0\|_\infty \leq B$. \  A2': $f_0$ is convex,
+\item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
   twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
 \item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
+\item[A4:] For all $k=1,...,s$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
 \end{packed_enum}
 
-We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3 to control the probability of false negatives.
+We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
 

### 2013-09-29 tex/scam/appendix.tex
various updates

@@
 \begin{theorem} 
-The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.
+The following holds regardless of whether we impose the boundedness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.
 
@@
 
-Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.
+Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residue.
 
@@
 \begin{proof}
-We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.
+We will omit the boundedness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.
 
-We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.
+We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.\\
 
@@
 \[
-\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
+\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 
+        + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| 
+        - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}_n^\tran\Delta_k d_k)
 \]
-where $r_k \coloneqq Y - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.
+where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.
 
@@
 \begin{align*}
-\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
-\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
+\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r}_k - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
+\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r}_k - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
 \end{align*}

### 2013-09-29 tex/scam/sparsistency.tex
various updates

@@
 \label{thm:deterministic}
-Let $\{\hat{d}_k, \hat{c}_k, \hat{\mu} \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$.
+Let $\{\hat{d}_k, \hat{c}_k\}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$.
 Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
-Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
-\hat{c}_k \mathbf{1}) - \hat{\mu}$ be the restricted regression residual. For $k
-\in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
+Let $\hat{r} \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k -
+\hat{c}_k \mathbf{1}_n)$ be the restricted regression residual. For $k
+\in \{1,...,p\}$, Let $\Delta_{k, j}$ be the $j$-th column of $\Delta_k$, i.e. the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\
+
 Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
 \hat{r}^\tran \Delta_{k,j}|$.
-Then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
+Then $\hat{\mu}$ and $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
 \end{theorem}
-This result holds regardless of whether we impose the boundness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
+
+This result holds regardless of whether we impose the boundedness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
 The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.
@@
 \begin{packed_enum}
-\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
-\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be $n$ samples of $Y$.
+\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be iid samples from $F$.
+\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be iid samples.
 \item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
   $f_0(X) = f_0(X_S)$.
-\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \Ef(X)$.
+\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \E f(X)$.
 \end{packed_enum}

### 2013-09-30 tex/scam/appendix.tex
typos

@@
 
-Suppose for all $j,k$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
+Suppose for all $j=1,...,n, k\in S^c$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
 
@@
 \begin{align*}
-\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r}_k - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
-\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r}_k - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
+\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k \d_k 
+       + \c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
+\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \r_k - \Delta_k \d_k 
+       + \c_k \mathbf{1}) + \gamma_k
 \end{align*}
@@
 
-We now substitute in $\hat{d}_k = 0, \hat{c}_k=0$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
+We now substitute in $d_k = \hat{d}_k = 0, c_k=\hat{c}_k=0, r_k = \hat{r}_k = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
 
 \begin{align*}
--\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
+-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} 
+           - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
 -\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\

### 2013-09-30 tex/scam/appendix.tex
various edits and typo fixes

@@
 
-Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residue.
+Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residual.
 
@@
 \begin{align*}
-\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k \d_k 
-       + \c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
-\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \r_k - \Delta_k \d_k 
-       + \c_k \mathbf{1}) + \gamma_k
+\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k d_k 
+       + c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
+\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( r_k - \Delta_k d_k 
+       + c_k \mathbf{1}) + \gamma_k
 \end{align*}
@@
 
-Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
+Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j=1,...,n,k \in S^c$,
 \[
@@
 \begin{proof}
-The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k,j$ because $\hat{r}$ is only dependent on $X_{S}$.
+The key is to note that $\hat{r}$ and $\Delta_{k,j}$ are independent for all $k \in S^c,j=1,...,n$ because $\hat{r}$ is only dependent on $X_{S}$.
+
+We remind the reader that $\Delta_{k,j} = \max(X_k, - X_{k(j)} \mathbf{1}_n, 0)$. Because $\hat{r}$ is empirically centered,
+
+\begin{align*}
+\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}) 
+                                            - \frac{1}{n} \hat{r}^\tran X_{k(j)} \\
+                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})
+\end{align*}
+Our goal in this proof is to bound $\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})$ from above.
 
@@
 \begin{align*}
-\hat{r}_i &= Y_i - \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
-	&= f^*(X_S^{(i)}) + \epsilon_i - \bar{f^*} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
-	&=  f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
+\hat{r}_i &= Y_i - \bar{Y}_i -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
+	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
+	&=  f_0(X_S^{(i)}) - \bar{f_0} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
 \end{align*}
-Where $\bar{f^*} = \frac{1}{n} \sum_{i=1}^n f^*(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.
+Where $\bar{f_0} = \frac{1}{n} \sum_{i=1}^n f_0(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.
 
@@
 
-We know that $|f^*(x)| \leq B$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.
+We know that $|f_0(x)| \leq sB$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.
 
-Then $|\bar{f^*}| \leq B$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq 3s B$.
+Then $|\bar{f_0(x)}| \leq sB$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq 3s B$.
 
@@
 
-\textbf{Step 2.} We now bound $\frac{1}{n} \hat{r}^\tran \max( X, X_{(j)} \mathbf{1})$.
+\textbf{Step 2.} We now bound $\frac{1}{n} \hat{r}^\tran \max( X, X_{k(j)} \mathbf{1})$.
 
 \[
-\frac{1}{n} \hat{r}^\tran \max(X, X_{(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_i, X_{(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) \geq j) + \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
+\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_{ki}, X_{k(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) + \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
 \]
@@
 \[
-\trm{Want to bound} \qquad F(X_1,...,X_n) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_i \delta(ord(i) \geq j) 
+\trm{Want to bound} \qquad F(X_{k1},...,X_{kn}) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) 
 \]
 
-First, we note that $X_i$ is bounded in the range $[-b,b]$.
+First, we note that $X_{ki}$ is bounded in the range $[-b,b]$.
 
-We claim then that $F$ is coordinatewise-Lipschitz. Let $X = (X_1, X_2,...,X_n)$ and $X' = (X'_1, X_2, ..., X_n)$ differ only on the first coordinate.
+We claim then that $F$ is coordinatewise-Lipschitz. Let $X_k = (X_{k1}, X_{k2},...,X_{kn})$ and $X'_k = (X'_{k1}, X_{k2}, ..., X_{kn})$ differ only on the first coordinate.
 
-The order of coordinate $i$ in $X$ and $X'$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X)$ to $F(X')$. Therefore,
+The order of coordinate $i$ in $X_k$ and $X'_k$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X_k)$ to $F(X'_k)$ and
 
-$$ | F(X_1, ..., X_n) - F(X'_1, ..., X_n) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$
+$$ | F(X_{k1}, ..., X_{kn}) - F(X'_{k1}, ..., X'_{kn}) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$
 
@@
 \[
-P( | F(X) - \E F(X) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
+P( | F(X_k) - \E F(X_k) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
 \]
 
-By symmetry and the fact that $\hat{r}$ is centered, $\E F(X) = 0$.
+By symmetry and the fact that $\hat{r}$ is centered, $\E F(X_k) = 0$.
 
-We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$.
+We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X_k)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$.
 
@@
 \[
-\trm{Want to bound}   \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A
+\trm{Want to bound}   \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
 \]
@@
 
-Since $|X_{(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
+Since $|X_{k(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
 
@@
 \[
-| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
+| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
 \]
@@
 
-$| \frac{1}{n} \max(X, X_{(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
+$| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
 \[

### 2013-09-30 tex/scam/sparsistency.tex
various edits and typo fixes

@@
 
-We follow Wainwright \cite{Wain:09a} and define a purely theoretical construct called \emph{restricted regression}.
+We follow \cite{Wain:09a} and define the \emph{restricted regression} purely for theoretical purposes.
 \begin{definition}
@@
 
-Our analysis then diverges from the now-standard ``primal-dual witness
+Our analysis then differs from the now-standard ``primal-dual witness
 technique''~\cite{Wain:09a}.
@@
 \hat{c}_k \mathbf{1}_n)$ be the restricted regression residual. For $k
-\in \{1,...,p\}$, Let $\Delta_{k, j}$ be the $j$-th column of $\Delta_k$, i.e. the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\
+\in \{1,...,p\}$, Let $\Delta_{k, j} \in R^n$ be the $j$-th column of $\Delta_k$, i.e. $\max( X_k - X_{k (j)} \mathbf{1}_n, 0)$. \\
 
@@
 \begin{packed_enum}
-\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be iid samples from $F$.
-\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be iid samples.
-\item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
+\item Let $F$ be a distribution supported and positive on $\mathcal{X}=[-b,b]^p$. Let $X^{(1)},..., X^{(n)} \sim F$ be iid.
+\item Let $Y = f_0(X) + \epsilon$ where $\epsilon$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
+\item Let $S = \{1,...,s\}$ denote the relevant variables where $s\leq p$, i.e.,
   $f_0(X) = f_0(X_S)$.
-\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \E f(X)$.
+\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
 \end{packed_enum}
 
-Each of our statistical theorems will use a subset of the following assumptions:
+Each of our theorems will use a subset of the following assumptions:
 \begin{packed_enum}
@@
 We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
+The $\alpha$ in assumption A4 can be interpreted as the signal strength of the relevant variable detection problem.
 

### 2013-09-30 tex/scam/icml14/experiments_icml.tex
first attempt at icml format

\section{Experiments}
%\subsection{Simulations}
We first illustrate our methods using a simulation of the following regression problem
\begin{equation}\nonumber
         y_i = \bds{x}_{iS}^{\top}\bds{Q}\bds{x}_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
\end{equation}
Here $\bds{x}_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0},\bds{I}_{p})$, 
$\bds{x}_{iS}$ is a subset of $\bds{x}_i$ with dimension $|S|=5$, where $S$ represents the active feature set, and 
$\epsilon_i$ is the additive noise drawn from $\mathcal{N}(0,1)$. 
$\bds{Q}$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
Notice that if $\bds{Q}$ is diagonal, then the true function is convex additive; otherwise the true function is convex but not additive.
For all the simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.

In the first simulation, we set $\bds{Q}=\bds{I}_{|S|}$ (the additive
case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256,512$.
For each $(n,p)$ combination, we generate $200$ independent data
sets. For each data set we use SCAM to infer the model parameterized
by $\bds{h}$ and $\bds{\beta}$; see equation \eqref{np}. If
$\|\bds{\beta}_{k\cdot}\|_{\infty}<10^{-8}\ (\forall k\not\in{}S)$ and
$\|\bds{\beta}_{k\cdot}\|_{\infty}>10^{-8}\ (\forall k\in{}S)$, then
we declare correct support recovery. We then plot the probability of
support recovery over the $200$ data sets in Figure \ref{Support}(a).  We
observe that SCAM performs consistent variable selection when the true
function is convex additive.  
To give the reader a
sense of the running speed, the code runs in about $2$ minutes on one
data set with $n=1000$ and $p=512$, on a MacBook with 2.3 GHz Intel
Core i5 CPU and 4 GB memory.

In the second simulation, we study the case in which the true function
is convex but not additive. We generate four $\bds{Q}$ matrices
plotted in Figure \ref{Support}(b), where the diagonal elements are all $1$ and
the off-diagonal elements are $0.5$ with probability $\alpha$
($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
$n=100,200,\ldots,1000$. We again run the SCAM optimization on $200$
independently generated data sets and plot the probability of recovery
in Figure \ref{Support}(c). The results demonstrate that SCAM performs
consistent variable selection even if the true function is not additive (but
still convex).

In the third simulation, we study the case of correlated design, where
$\bds{x}_{i}$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\bds{Q}$ with
$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=02, 0.4,
0.6, 0.8$ are depicted in Figure \ref{Support}(d). As can be seen, for
design of moderate correlation, SCAM can still select relevant
variables well.

%\begin{figure}[!htpb]
%        \centering
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Curve1}
%                 \caption{Additive model.}
%                \label{Curve1}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Q}
%                \caption{Four $\bds{Q}$ matrices.}
%                \label{Q}
%        \end{subfigure}\\
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Curve2}
%                \caption{Additive and non-additive models.}
%                \label{Curve2}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Curve3}
%                \caption{Correlated design for non-additive model.}
%                \label{Curve3}
%        \end{subfigure}
%        \caption{Result of support recovery.}\label{Support}
%\end{figure}

%\begin{figure}[ht]
%\begin{center}
%\begin{tabular}{cccc}
%\hskip-20pt
%\includegraphics[width=.27\textwidth]{figs/Curve1} &
%\hskip-17pt
%\includegraphics[width=.27\textwidth]{figs/Q} &
%\hskip-17pt
%\includegraphics[width=.27\textwidth]{figs/Curve2} &
%\hskip-17pt
%\includegraphics[width=.27\textwidth]{figs/Curve3}  \\
%(a) additive model & (b) four $\bds{Q}$ matrices &
%(c) non-additive models & (d) correlated design
%\end{tabular}
%\end{center}
%\caption{Result of support recovery.}\label{Support}
%\end{figure}

%\subsection{Boston housing data}

We next use the Boston housing data rather than simulated data. This data set
contains 13 covariates, 506 samples and one response variable
indicating housing values in suburbs of Boston. The data and detailed description
can be found on the UCI Machine Learning Repository website~\verb+http://archive.ics.uci.edu/ml/datasets/Housing+.

We first use all $n=506$ samples (with normalization) to train SCAM, using
a set of candidate $\{\lambda^{(t)}\}$ with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
we obtain a subgradient matrix $\bds{\beta}^{(t)}$ with $p=13$ rows. The non-zero
rows in this matrix indicate the variables selected using $\lambda^{(t)}$. 
We plot $\|\bds{\beta}^{(t)}\|_{\infty}$ and the row-wise mean of $\bds{\beta}^{(t)}$ versus the normalized
norm $\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$ in Figures \ref{Boston}(a) and \ref{Boston}(b).
As a comparison we plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
From the figures we observe that the first three variables selected by SCAM
and LASSO are the same: LSTAT, RM and PTRATIO, which is consistent with previous findings~\cite{SpAM:07}.
The fourth variable selected by SCAM is TAX (with $\lambda^{(t)}=0.09$).
We then refit SCAM with only these four variables without regularization, and plot the inferred additive
functions in Figure \ref{Boston}(e). As can be seen, these functions contain clear nonlinear effects which cannot be captured
by LASSO. The shapes of these functions are in agreement with those obtained by SpAM~\cite{SpAM:07}.

Next, in order to quantitatively study the predictive performance, we run 10 times 5-fold cross validation, following
the same procedure described above (training, variable selection and
refitting).  A plot of the mean and standard
deviation of the predictive Mean Squared Error (MSE) in in Figure \ref{Boston}(d). Since for SCAM the same $\lambda^{(t)}$ may lead to
slightly different number of selected features in different folds and runs, the values on the x-axis (average number of selected features)
for SCAM are not necessarily integers. Nevertheless, the figure clearly shows that SCAM has a much lower predictive MSE than LASSO. 
We also compared the performance of SCAM with that of Additive Forward Regression (AFR) presented in~\cite{Xi:09}, and found that they are similar.
The main advantages of SCAM compared with AFR and SpAM are 1) there are no other tuning parameters (such as bandwidth)
besides $\lambda$; 2) SCAM is formulated as a convex program, which guarantees a global optimum.

%\begin{figure}[!htpb]
%        \centering
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Additive}
%                 \caption{Variable selection result using SCAM.}
%                \label{SCAM}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Additive1}
%                 \caption{Variable selection result using SCAM.}
%                \label{SCAM1}
%        \end{subfigure}\\
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/LASSO}
%                \caption{Variable selection result using LASSO.}
%                \label{LASSO}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/MSE}
%                 \caption{Predictive MSE of SCAM and LASSO.}
%                 \label{MSE}
%        \end{subfigure}\\
%        \begin{subfigure}[b]{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{figs/Convex}
%                \caption{Inferred additive convex functions by SCAM.}
%                \label{Convex}
%        \end{subfigure}
%        \caption{Results on Boston housing data.}\label{Boston}
%\end{figure}

\begin{figure*}[!t]
\begin{center}
\begin{tabular}{cccc}
\hskip-20pt
\includegraphics[width=.29\textwidth]{../figs/Curve1} &
\hskip-20pt
\includegraphics[width=.29\textwidth]{../figs/Q} &
\hskip-20pt
\includegraphics[width=.29\textwidth]{../figs/Curve2} &
\hskip-20pt
\includegraphics[width=.29\textwidth]{../figs/Curve3}  \\
\hskip-10pt (a) additive model & 
\hskip-10pt (b) four $\bds{Q}$ matrices &
\hskip-10pt (c) non-additive models & 
\hskip-10pt (d) correlated design
\end{tabular}
\end{center}
\caption{Support recovery results where the additive assumption is
  correct (a), incorrect (b), (c), and with correlated design (d).}\label{Support}
\vskip10pt

\begin{center}
\begin{tabular}{ccc}
\hskip-10pt
  \includegraphics[width=.35\textwidth]{../figs/Additive} &
\hskip-25pt
  \includegraphics[width=.35\textwidth]{../figs/Additive1} &
\hskip-25pt
  \includegraphics[width=.35\textwidth]{../figs/LASSO} 
\\
\hskip-10pt 
SCAM $\|\beta_k\|_\infty$ paths & 
\hskip-25pt 
SCAM $\text{mean}(\beta_k)$ paths &
\hskip-25pt
LASSO $\beta_k$ paths
\end{tabular}
\begin{tabular}{cc}
  \includegraphics[width=.37\textwidth]{../figs/MSE} &
  \includegraphics[width=.43\textwidth]{../figs/Convex}
\\
predictive MSE & inferred functions from SCAM
\end{tabular}
\end{center}
\caption{Results on Boston housing data, showing regularization paths,
 MSE and fitted functions.}\label{Boston}
\end{figure*}

### 2013-09-30 tex/scam/icml14/optimization_icml.tex
first attempt at icml format

--- 2013-09-29 tex/scam/optimization.tex
@@
 \end{split}\end{equation}
-Where $\mu \in \R$ is a mean parameter introduced because $f$ may not have zero-mean, and where $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+We introduce a mean parameter $\mu \in \R$ because $f$ may not have zero-mean.
+We can in fact solve $\mu$ explicitly here: the optimal $\mu = \frac{1}{n} \sum_{i=1}^n y_i = \bar{y}$ because of KKT and the constraints that $\sum_i h_{ki} = 0$.
+$\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
 It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
@@
        &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
-                       \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri}-\mu)-h_{ki}\Bigr)^{2} 
+             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\bar{y}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} 
                       + \lambda\gamma_{k} \\
@@
 \]
-Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
-$\Delta(j,x_{ki})= x_{ki} -
-x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
-$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
-$n-1$ dimensional vector.
-Then $f_k(x_{ki}) = \Delta(x_{ki})^\tran d_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$.
-Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$.
-Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
+We can write this more compactly in matrix notations. First define $\Delta_{k(j)}(x_{ki}) = \max( x_{ki} - x_{k(j)}, 0)$. 
+\[
+\left[ \begin{array}{c}
+    f_k(x_{k1}) \\
+    ... \\
+    f_k(x_{kn}) \\
+\end{array} \right] =
+\left[ \begin{array}{ccc}
+    \Delta_{k(1)}(x_{k1}) & ... & \Delta_{k(n-1)}(x_{k1}) \\
+    ... & & \\
+    \Delta_{k(1)}(x_{kn}) & ... & \Delta_{k(n-1)}(x_{kn}) 
+\end{array} \right]
+\left[ \begin{array}{c}
+    d_{k(1)} \\
+    ... \\
+    d_{k(n-1)}
+\end{array} \right] \coloneqq \Delta_k d_k
+\]
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = \Delta_{k(j)}(x_{k(i)})$ and $d_k = (d_{k(1)} ,..., d_{k(n-1)})$.
+We can now reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
 \begin{align}
 \min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
-               \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) -\mu \Bigr\|_2^2 
+       \Bigl\| Y - \bar{Y}\mathbf{1}_n - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 
                + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
-\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
-	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
+\trm{s.t. $\forall k$, }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0 	
+               \qquad &\trm{(convexity)} \nonumber \\ 
+	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	
+               \qquad &\trm{(centering)} \nonumber 
 \end{align}

### 2013-09-30 tex/scam/icml14/paper.tex
first attempt at icml format

\documentclass{article}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,caption,subcaption,sidecap,custom_math}
\usepackage[hscale=0.7,vscale=0.8]{geometry}

\bibliographystyle{plain}

\title{Variable Selection in Convex Function Estimation}

\author{
Min Xu, Minhua Chen, John Lafferty
}

% ENVIRONMENTS
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheoremstyle{remark}{\topsep}{\topsep}%
     {\normalfont}% Body font
     {}           % Indent amount (empty = no indent, \parindent = para indent)
     {\bfseries}  % Thm head font
     {.}          % Punctuation after thm head
     {.5em}       % Space after thm head (\newline = linebreak)
     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{definition}{Definition}[section]

\begin{document}

% John's macros
\def\X{\mathcal{X}}
\def\comma{\unskip,~}
\def\truep{p^*}
\def\div{\|\,}
\long\def\comment#1{}
\def\reals{{\mathbb R}}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\Cov{\mathop{\text{Cov}}}
\def\supp{\mathop{\text{supp}\kern.2ex}}
\def\argmin{\mathop{\text{\rm arg\,min}}}
\def\arginf{\mathop{\text{\rm arg\,inf}}}
\def\argmax{\mathop{\text{\rm arg\,max}}}
\let\tilde\widetilde
\def\csd{${}^*$}
\def\mld{${}^\dag$}
\def\dos{${}^\ddag$}
\def\W{\widetilde Y}
\def\Z{\widetilde X}
\let\hat\widehat
\let\tilde\widetilde
\def\given{{\,|\,}}
\def\ds{\displaystyle}
\def\bs{\backslash}
\def\1{{(1)}}
\def\2{{(2)}}
\def\pn{{(n)}}
\def\ip{{(i)}}
\def\Xbar{\overline{X}}
\def\except{\backslash}
\def\npn{\mathop{\textit{NPN\,}}}
\def\i{{(i)}}
\def\cE{{\mathcal{C}}}
\def\cM{{\mathcal{M}}}
\def\cF{{\mathcal{F}}}
\def\cP{{\mathcal{P}}}
\def\cG{{\mathcal{G}}}
\def\tr{\mathop{\text{tr}}}
\long\def\comment#1{}
\def\ti#1{#1}
\def\titi#1{\textit{#1}}
\def\cram{{\sc cram}}
\def\spam{{\small\sc SpAM}}
\def\diag{\mathop{\rm diag}}
\def\ones{\mathbf{1}}
\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
\def\fatnorm#1{\threebars #1 \threebars}
\def\rank{\mathop{\rm rank}}
\def\S{\mathcal{S}}
\def\H{\mathcal{H}}
\def\K{{K}}
\def\rank{\mathop{\rm rank}}
\def\half{{1/2}}
\def\Y{\mathbb{Y}}
\def\M{\mathbb{M}}
\def\F{\mathbb{F}}
\def\pinv{{-1}}
%\def\ones{\mathds{1}}
%\def\ones{1}
\def\Res{Z}
\def\Proj{P}
\def\cN{{\mathcal N}}
\def\cT{{\mathcal H}}
\def\coloneqq{:=}
\def\mathbf#1{\mbox{\boldmath $#1$}} 
\def\bar#1{\overline{#1}}

\maketitle

\begin{abstract}
  We consider the problem of estimating a sparse convex function of
  many variables.  In constrast to classical nonparametric
  regression with smoothness constraints, we show that convexity is
  additively faithful---it suffices to estimate a convex additive
  model for variable selection.  We develop algorithms for estimating
  sparse convex additive models, including an approach using iterative
  quadratic programming.  Supporting experiments and statistical
  theory are presented, showing variable selection consistency in
  dimensions that can scale exponentially in the sample size.  An
  attractive feature of this framework is the lack of tuning parameters
  for smoothness.
\end{abstract}
\vskip10pt

\input{introduction}
%\input{related_work}
\input{summary}
\input{additive_faithful}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}

\clearpage

\bibliography{local}

\newpage
\input{appendix}

\end{document}

### 2013-10-01 tex/scam/icml14/introduction_icml.tex
test commit
edits on intro

--- 2013-09-29 tex/scam/nips13/introduction.tex
@@
 
-The sparse nonparametric regression problem is considered in
+The general sparse nonparametric regression problem is considered in
 \cite{lafferty2008rodeo}, where it is shown that computationally
@@
 dimensional optimization 
-\begin{eqnarray}
-& \text{minimize} &\sum_{i=1}^n (Y_i - m(x_i))^2 \\
-& \text{subject to} & m:\reals^p\rightarrow\reals\ \text{is convex}
-\end{eqnarray}
+\begin{align}
+\begin{split}
+\text{minimize} & \quad \sum_{i=1}^n (Y_i - m(x_i))^2 \\
+\text{subject to} &  \quad m:\reals^p\rightarrow\reals\ \text{is
+  convex}
+\end{split}
+\end{align}
 is precisely equivalent to the finite dimensional quadratic
 program 
-\begin{eqnarray}
-& \text{minimize}_{h, \beta} &\sum_{i=1}^n (Y_i - h_i)^2 \\
-& \text{subject to} & h_j \geq h_i + \beta_i^T (x_j-x_i),\; \text{for
+\begin{align}
+\begin{split}
+\label{eq:outer}
+\text{minimize}_{h, \beta} & \;\; \sum_{i=1}^n (Y_i - h_i)^2 \\
+\text{subject to} & \;\; h_j \geq h_i + \beta_i^T (x_j-x_i),\; \text{for
     all $i,j$}.
-\label{eq:outer}
-\end{eqnarray}
-See \cite{Boyd04}, Section 6.5.5.
+\end{split}
+\end{align}
+%\end{equation}
+%See \cite{Boyd04}, Section 6.5.5.
 Here $h_i$ is the estimated function value $m(x_i)$, and the vectors
@@
 regularization parameter $\lambda$ to control the level of sparsity,
-the global convexity leads to effective, scalable algorithms.  We
+the global convexity assumption leads to effective, scalable algorithms.  We
 demonstrate use of our approach on experiments with standard
@@
 $\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
-vector with $k$-th coordinate removed. Let $\mathbf{v} \in \R^n$, then
+vector with the $k$-th coordinate removed. If $\mathbf{v} \in \R^n$, then
 $v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
 magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
-is all ones. If $X \in \R^p$ and $S \subset
+is the all ones vector. If $X \in \R^p$ and $S \subset
 \{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
-coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
-$\bar{X}$ to denote empirical average.
+the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
+$\bar{X}$ to denote the empirical average.

### 2013-10-01 tex/scam/icml14/additive_faithful_icml.tex
first attempt at icml format
minor edits
edits on intro

--- 2013-09-29 tex/scam/additive_faithful.tex
@@
 
-The additive approximation may mark a relevant variable as
-irrelevant. Such mistakes are inherent to the approximation and may
-persist even with infinite
-samples.  Lemma~\ref{lem:general_int_reduction} below provides
-examples of errors made by the additive approximations that minimize
-the $L_2$ distance.
+For general regression, additive approximation may result in a
+relevant variable being incorrectly marked as irrelevant. Such
+mistakes are inherent to the approximation and may persist even with
+infinite samples.  In this section we give
+examples of this phenomenon, and then show how the convexity
+assumption
+changes the behavior of the additive approximation.  We begin
+with a lemma that implies uniqueness of the additive regression function.
+
+\begin{figure*}[htp]
+\vskip-10pt
+	\centering
+	\subfigure[egg carton]{
+		\centering
+		{\includegraphics[width=0.4\textwidth]{../figs/sine_wave_funct3}}
+	}
+	\subfigure[tilting slope]{
+		\centering
+		{\includegraphics[width=0.4\textwidth]{../figs/tilting_slope_funct3}}
+	}
+\caption{Two additively unfaithful functions. Relevant variables are
+  zeroed out under an additive approximation because every ``slice''
+  of the function integrates to zero.}
+\vskip-10pt
+\end{figure*}
 
@@
 integrable function and suppose, without loss of generality, that $\E f(X) = 0$.
-Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E \bigl( f(X) -
-\sum_{k=1}^s f_k(X_k) \bigr)^2 \,:\, \E f_k(X_k) = 0\}$. Then $f^*_k(x_k) = \E[ f(X) \given x_k]$ is unique.
+Let 
+\begin{equation}
+f^* \coloneqq \argmin_{f_1,\ldots, f_s} \Bigl\{ \E \bigl( f(X) -
+\sum_{k=1}^s f_k(X_k) \bigr)^2 \,:\, \E f_k(X_k) = 0\Bigr\}.
+\end{equation}
+Then $f^*_k(x_k) = \E[ f(X) \given x_k]$ is unique.
 \end{lemma}
@@
 Lemma~\ref{lem:general_int_reduction} follows from the stationarity
-condition of the optimal solution. If $F$ is the uniform distribution,
-then $f^*_k(x_k) = \int_{\mathbf{x}_{-k}} f(x_k, \mathbf{x}_{-k})
+conditions of the optimal solution. If $F$ is the uniform distribution,
+then $f^*_k(x_k) = \int f(x_k, \mathbf{x}_{-k})
 d\mathbf{x}_{-k}$.
@@
 \[
-\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2) \qquad \trm{ for } (x_1, x_2) \in [0,1]^2
+\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)
 \]
-For all $x_1$, $\int_{x_2} f(x_1, x_2) d x_2 = 0$ and also, for all
-$x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$. An additive approximation
+defined for $(x_1, x_2) \in [0,1]^2$.  Then
+$\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
+$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
 would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
 \[
-\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2 \qquad \trm{ for } x_1 \in [-1,1],\; x_2 \in [0,1].
+\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2
 \]
-For all $x_2$, $\int_{x_1} f(x_1, x_2) d x_1 = 0$, therefore, we expect $f_2 = 0$ under the additive approximation.
-This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope exactly $x_2$.
+defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
+$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation.
+This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
 \end{example}
 
-\begin{figure}[htp]
-\vskip-10pt
-	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\centering
-		{\includegraphics[width=0.75\textwidth]{figs/sine_wave_funct3}}
-		\caption{egg carton}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\centering
-		{\includegraphics[width=0.75\textwidth]{figs/tilting_slope_funct3}}
-		\caption{tilting slope}
-	\end{subfigure}
-
-\caption{Two additively unfaithful functions. Relevant variables are
-  zeroed out under an additive approximation because every ``slice''
-  of the function integrates to zero.}
-\vskip-10pt
-\end{figure}
-
-It is important to understand the kind of functions for which the
-additive approximation can accurately capture all of the relevant variables.
+In order to exploit additive models, it is important to understand when the
+additive approximation accurately captures all of the relevant variables.
 We call this property \emph{additive faithfulness}.
@@
 assume without loss of generality that $\E f(X) = 0$. Let 
-$$\ds f^*_1,...,f^*_s \coloneqq \arg\min \Bigl\{ \E ( f(X) - \sum_{k=1}^s
-f_k(X_k) )^2 \,:\, \E f_k(X_k) = 0, \forall k\Bigr\}.$$
+\begin{equation}
+f^* \coloneqq \argmin_{f_1,\ldots, f_s} \Bigl\{ \E ( f(X) - \sum_{k=1}^s
+f_k(X_k) )^2 \,:\, \E f_k(X_k) = 0 \Bigr\}.
+\end{equation}
 We say that $f$ is \emph{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
@@
 Appendix, but pause here to provide some intuition. From
-Lemma~\ref{lem:general_int_reduction}, we know intuitively that the
+Lemma~\ref{lem:general_int_reduction}, we know that the
 additive approximation zeroes out $k$ when, fixing $x_k$, every
@@
 Theorem~\ref{thm:convex_faithful} plays an important role in our
-sparsistency analysis, in which we prove that the additive
-approximation is variable selection consistent (or ``sparsistent'') \emph{even when the true function is not
-additive.}
+sparsistency analysis, where we show that the additive
+approximation is variable selection consistent (or ``sparsistent''), even when the true function is not
+additive.
 

### 2013-10-01 tex/scam/icml14/optimization_icml.tex
changes

@@
 
-We consider the following nonparametric regression problem
+We now consider the following nonparametric regression problem
 \begin{equation}\nonumber
-          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
+          Y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
                   \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
 \end{equation}
-where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
+where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $Y_{i}$ is the
 response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
@@
        &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
-                     \Bigl( y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
+                     \Bigl( Y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
                          + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
@@
 We introduce a mean parameter $\mu \in \R$ because $f$ may not have zero-mean.
-We can in fact solve $\mu$ explicitly here: the optimal $\mu = \frac{1}{n} \sum_{i=1}^n y_i = \bar{y}$ because of KKT and the constraints that $\sum_i h_{ki} = 0$.
+We can in fact solve $\mu$ explicitly here: the optimal $\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ because of KKT and the constraints that $\sum_i h_{ki} = 0$.
 $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
@@
 Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
-in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
+in different feature dimensions are only coupled in the term $(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
 where in each step we solve the following QP subproblem for
@@
        &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
-             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\bar{y}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} 
+             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} 
                       + \lambda\gamma_{k} \\

### 2013-10-01 tex/scam/icml14/optimization_icml.tex
changes

@@
 We impose an additional constraint that each $f_{k}(\cdot)$ is 
-an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
+a univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
 \begin{equation}\label{hyper}
@@
 program:
-\begin{equation}\begin{split}\label{np}
-       &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
+\begin{equation}
+\begin{split}
+       \min_{\bds{h},\bds{\beta},\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
                      \Bigl( Y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
                          + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
-       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), 
-                                 \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
-\end{split}\end{equation}
-We introduce a mean parameter $\mu \in \R$ because $f$ may not have zero-mean.
-We can in fact solve $\mu$ explicitly here: the optimal $\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ because of KKT and the constraints that $\sum_i h_{ki} = 0$.
-$\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+       \textrm{subject to} &\;\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \\
+                     & \;\; \sum_{i=1}^{n}h_{ki}=0,\\
+                     & \;\; \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
+\end{split}
+\label{np}
+\end{equation}
+Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.  We introduce a mean parameter $\mu \in \R$ because $f$ may not have
+zero mean. We can in fact solve for $\mu$ explicitly, as  
+$\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ which follows from the
+KKT conditions
+and the constraints $\sum_i h_{ki} = 0$.
 It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
@@
 variable selection.  We refer to this framework as the sparse convex
-additive model (SCAM). Notice that if we replace $\beta_{k(i+1)} \geq
-\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
-reduces to the lasso.  Note while one can use
+additive model (SCAM). While one can use
 supporting hyperplanes to the epigraph as in \eqref{eq:outer}, 
 SCAM uses the \emph{inner  piece-wise linear function}
-that approximates the graph with secant lines.
+that approximates the graph with secant lines. Notice that if we replace $\beta_{k(i+1)} \geq
+\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
+reduces to the lasso.
 

### 2013-10-01 tex/scam/appendix.tex

@@
  We will use covering number and uniform convergence and will thus need to first introduce some notations. 
+ \subsubsection{Notation}
 
@@
 \]
+
+Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \, \E f_k(X_k) = 0\}$.
+
+Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \, \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.
+
+\subsubsection{Proof}
+
+\begin{lemma}
+
+\end{lemma}
+
+By Theorem~\ref{thm:convex_faithful}, $R_s(f^{*s}) - R_s(f^{*(s-1)}) \geq \alpha > 0$.
 
@@
 
-Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \E f_k(X_k) = 0\}$.
-
-Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.
-
-By Theorem~\ref{thm:convex_faithful}, $R_s(f^*_s) - R_s(f^*_{(s-1)}) \geq \alpha > 0$.
-
 $f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered.
@@
 
-$f_0 - f^{*s}$ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$. Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.
+$\|f_0 - f^{*s}\|_n \leq \|f_0 - f^{*s}\|_\infty $ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$.
+Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.
 
@@
 \[
-|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})|\leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
+|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
 \]

### 2013-10-01 tex/scam/icml14/optimization_icml.tex
changes

@@
 \begin{align*}
-  \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = 
-            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = 
-            \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
-      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \forall j<i, &h_{k(j)}-h_{k(i)} =
-                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = 
-                \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
-     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
+  \forall j\geq{}i,\; h_{k(j)}-h_{k(i)}  &= 
+            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) \\
+      & = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
+      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) \\
+      & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
+  \forall j<i,\;  h_{k(j)}-h_{k(i)} &=
+                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) \\
+     &= \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
+     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)})  \\
+     &= \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
 \end{align*}
@@
 
-The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints.
-The optimal $\mu$ has a closed form solution of $\mu = \frac{1}{n}\sum_{i=1}^n Y_i$, which is easy to derive from the KKT theorem and the constraints that $\sum_i h_{ki} = 0$ for all $k$.
-Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
-in different feature dimensions are only coupled in the term $(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
-where in each step we solve the following QP subproblem for
-$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
+The SCAM optimization in (\ref{np}) is a quadratic program (QP) with
+$O(np)$ variables and $O(np)$ constraints. 
+Directly applying a QP solver for $\bds{h},
+\bds{\beta}$ would be computationally expensive for relatively large
+$n$ and $p$. However, notice that variables in different feature
+dimensions are only coupled in the term
+$(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block
+coordinate descent method, where in each step we solve the following
+QP subproblem for $\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the
+other variables fixed:
 \begin{equation}\begin{split}\nonumber

### 2013-10-01 tex/scam/icml14/optimization_icml.tex
changes

@@
 other variables fixed:
-\begin{equation}\begin{split}\nonumber
-       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
+\begin{equation}
+\begin{split}\nonumber
+       \min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} &
              \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} 
                       + \lambda\gamma_{k} \\
-        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
-\end{split}\end{equation}
+        \textrm{such that} & \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}),\\
+        &\ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k}\\
+        &\  \sum_{i=1}^{n}h_{ki}=0, \ (\forall i).
+\end{split}
+\end{equation}
 The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
@@
 After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
-\begin{equation}\nonumber
-      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj})+\mu = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} + \mu.
+\begin{equation}
+\begin{split}
+\nonumber
+      f(\bds{x}_j) & = \sum_{k=1}^{p}f_k(x_{kj})+\mu \\ 
+    & = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} +
+      \mu.
+\end{split}
 \end{equation}

### 2013-10-02 tex/scam/appendix.tex
updated proof of additive faithfulness

@@
 
-Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
+Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
 
-Then $f^*_k(x_k) = \E[ f(X) \given x_k]$.
+Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
 \end{lemma}
@@
 
-Let $f^*_1,...,f^*_s$ be the minimizers as defined.
-It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
+Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
 
-Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$, for all $x_k$,  uniquely minimizes 
+We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
+This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.\\
+
+We now turn our attention toward the $f^*_k$'s.
+
+It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
+
+Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
 \[
@@
 \]
-If this is true, then the function $x_k \mapsto \E[ f(X) \given x_k]$ is the unique $f^*_k(x_k)$ that minimizes the expected square error.
+It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.
 
@@
 \begin{align*}
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\  
-   p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\
-f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(\mathbf{x}) d \mathbf{x}_{-k} 
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
+  \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+      ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
+p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} 
+       p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
+              d \mathbf{x}_{-k} \\
+f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
+       p(\mathbf{x}_{-k}) (f(\mathbf{x}) -\mu^*) d \mathbf{x}_{-k} 
  \end{align*}
@@
 The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
-Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ]$ is unique.
+Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.
 
-Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex.
-The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and is convex.
+The former is clearly true; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
 
@@
 
-Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$.
+Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$.
 
@@
 \item $f$ does not depends on coordinate $k$
-\item For all $x_k$, $\E[ f(X) | x_k] = 0$.
+\item For all $x_k$, $\E[ f(X) | x_k] = \E f(X) $.
 \end{packed_enum}
@@
 
-The first condition trivially implies the second because $\E f(X) = 0$.
+The first condition trivially implies the second.
 
-Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = 0$.
+Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = \E f(X)$.
 
@@
 \begin{align*}
-p(x_k) \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
+ \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
 \end{align*}
@@
 \]
-Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
+Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
 
@@
 \begin{lemma}
+Suppose assumptions A1' and A4 hold.
 
+Then $R(f^{*(s-1)}) - R(f^{*s}) \geq \alpha$, where $\alpha$ lower bounds the norm of the population optimal additive components as defined in assumpation A4.
 \end{lemma}
 
-By Theorem~\ref{thm:convex_faithful}, $R_s(f^{*s}) - R_s(f^{*(s-1)}) \geq \alpha > 0$.
+\begin{proof}
+
+\begin{align*}
+R(f^{*(s-1)}) - R(f^{*s}) &= \E(f^{*(s-1)}(X) - f_0(X))^2 - \E(f^{*s}(X) - f_0(X))^2 \\
+    &= \E( f^{*(s-1)}(X) - f^{*s}(X) + f^{*s}(X) - f_0(X))^2 - \E(f^{*s}(X) - f_0(X))^2 \\
+    &= \E( f^{*(s-1)}(X) - f^{*s}(X))^2 - 2 \E[ (f^{*(s-1)}(X) - f^{*s}(X)) (f^{*s}(X) - f_0(X) ) ]
+\end{align*}
+
+\end{proof}
 
@@
 \begin{theorem} 
-Suppose assumptions A1', A2', A3 hold. Suppose $f_0$ depends on all $s$-variables.
+Suppose assumptions A1', A2', A3, A4 hold.
 

### 2013-10-02 tex/scam/icml14/optimization_icml.tex
updated proof of additive faithfulness

@@
 \end{equation}
-Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.  We introduce a mean parameter $\mu \in \R$ because $f$ may not have
-zero mean. We can in fact solve for $\mu$ explicitly, as  
+Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$. We can solve for $\mu$ explicitly, as  
 $\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ which follows from the

### 2013-10-02 tex/scam/icml14/optimization_icml.tex
formatted optimization section

@@
 It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(i)}$ and 
-\[
-f_k(x_{k(i)}) = f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)}
-- x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
-\]
+\begin{equation}
+\begin{split}
+f_k(x_{k(i)}) = & f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)} \\
+& - x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots  \\
+& + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
+\end{split}
+\end{equation}
 We can write this more compactly in matrix notations. First define $\Delta_{k(j)}(x_{ki}) = \max( x_{ki} - x_{k(j)}, 0)$.
-\[
-\left[ \begin{array}{c}
-    f_k(x_{k1}) \\
-    ... \\
-    f_k(x_{kn}) \\
-\end{array} \right] =
-\left[ \begin{array}{ccc}
+
+\begin{equation*}
+\begin{split}
+&(f_k(x_{k1}) ,..., f_k(x_{kn}))^\tran = \Delta_k d_k \coloneqq \\
+\vspace{0.1in}
+&\left[ \begin{array}{ccc}
     \Delta_{k(1)}(x_{k1}) & ... & \Delta_{k(n-1)}(x_{k1}) \\
@@
     d_{k(n-1)}
-\end{array} \right] \coloneqq \Delta_k d_k
-\]
+\end{array} \right] 
+\end{split}
+\end{equation*}
+
 Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = \Delta_{k(j)}(x_{k(i)})$ and $d_k = (d_{k(1)} ,..., d_{k(n-1)})$.
@@
 \begin{align}
-\min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
-       \Bigl\| Y - \bar{Y}\mathbf{1}_n - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 
-               + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
-\trm{s.t. $\forall k$, }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0 	
-               \qquad &\trm{(convexity)} \nonumber \\ 
+\min_{d_k, c_k}& \frac{1}{2n} 
+       \Bigl\| Y - \bar{Y}\mathbf{1}_n - \sum_{k=1}^p 
+             ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 \nonumber \\
+               & + \lambda_n \sum_{k=1}^p \|d_k\|_1   \label{opt:alternate_opt} \\
+\trm{s.t. }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0  	
+               \qquad \trm{(convexity)} \nonumber \\ 
 	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	
-               \qquad &\trm{(centering)} \nonumber 
+               \qquad \trm{(centering)} \nonumber 
 \end{align}

### 2013-10-02 tex/scam/appendix.tex
formatted optimization section
added lots of proof details

@@
       ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
-p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} 
+p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
      p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
@@
 
- The next proposition, combined with the previous Lemma, proves Theorem~\ref{thm:convex_faithful}.
+Our reasoning actually proves something stronger. It proves the following lemma:
+
+\begin{lemma}
+\label{lem:additive_component}
+
+$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
+\[
+min_{f_k} \{ \E( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k))^2 \,:\, \E f_k(X_k) = 0 \}
+\]
+for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
+\end{lemma}
+
+ The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.
 
@@
 
-For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - g(X) |^2$ as the population risk.
+For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0 + w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0 + w} = \frac{1}{n} \sum_i f_0(X^{(i)}) + w_i $ and $\mu = \E f_0(X)$.
+Note that we \emph{subtract} out the mean in the two risk definitions.
 
@@
 \subsubsection{Proof}
+\label{sec:false_negative_proof_proof}
 
 \begin{lemma}
+\label{lem:minus_one_risk_increase}
 Suppose assumptions A1' and A4 hold.
@@
 \begin{align*}
-R(f^{*(s-1)}) - R(f^{*s}) &= \E(f^{*(s-1)}(X) - f_0(X))^2 - \E(f^{*s}(X) - f_0(X))^2 \\
-    &= \E( f^{*(s-1)}(X) - f^{*s}(X) + f^{*s}(X) - f_0(X))^2 - \E(f^{*s}(X) - f_0(X))^2 \\
-    &= \E( f^{*(s-1)}(X) - f^{*s}(X))^2 - 2 \E[ (f^{*(s-1)}(X) - f^{*s}(X)) (f^{*s}(X) - f_0(X) ) ]
+R(f^{*(s-1)}) - R(f^{*s}) &= \E\Big(f^{*(s-1)}(X) - f_0(X) + \mu\Big)^2 
+                              - \E\Big(f^{*s}(X) - f_0(X) + \mu\Big)^2 \\
+    &= \E\Big( f^{*(s-1)}(X) - f^{*s}(X) + f^{*s}(X) - f_0(X) + \mu\Big)^2 
+                                 - \E\Big(f^{*s}(X) - f_0(X) + \mu\Big)^2 \\
+    &= \E\Big( f^{*(s-1)}(X) - f^{*s}(X)\Big)^2 
+                - 2 \E\Big[ (f^{*(s-1)}(X) - f^{*s}(X)) (f^{*s}(X) - (f_0(X)-\mu)) \Big]
 \end{align*}
+
+We will argue that all the components of the additive function $f^{*(s-)}$ are also in $f^{*s}$.
+Let us denote the components of $f^{*s} = \sum_{k=1}^s f_k^*$.
+We will now invoke Lemma~\ref{lem:additive_component}, which is valid because we assume $X_1,...,X_s$ are independent by assumption A1'.
+By Lemma~\ref{lem:additive_component}, if we set $f^*_k = 0$, the resulting additive function $\sum_{k'\neq k} f_{k'}^*$ minimizes the population risk subject to the constraint that $f_k = 0$.
+By definition, $f^{*s}$ is $\argmin_k \sum_{k'\neq k} f_{k'}^*$ and thus share components with $f^{*s}$.
+
+Therefore, there exist some $k$ such that $f^{*(s-1)} - f^{*s} = f^*_k$, and we can continue the bound
+\begin{align*}
+R(f^{*(s-1)}) - R(f^{*s}) &= \E f^*_k(X_k)^2 - 2 \E[ f^*_k(X_k) ( f^{*s}(X) - (f_0(X)-\mu) )] \\
+    &= \E f^*_k(X_k)^2 - 2 \E[ f^*_k(X_k) f^{*s} (X)] + 2 \E[ f^*_k(X_k) (f_0(X)-\mu) ] 
+\end{align*}
+
+\begin{align*}
+\E[ f^*_k(X_k) f^{*s} (X)]  &= \E\Big[ f^*_k (X_k) \E[ f^{*s} (X) \,|\, X_k ] \Big] = \E f^*_k(X_k)^2  \\
+\E[ f^*_k(X_k)(f_0(X) - \mu) ] &= \E\Big[ f^*_k(X_k) \E[ f_0(X) - \mu \,|\, X_k ] \Big] = \E f^*_k(X_k)^2 
+\end{align*}
+
+Where we used the fact that $\E f^*_{k'} (X_{k'}) = 0$ for all $k'$ and the fact that $\E[ f_0(X) - \mu \,|\, X_k] = f^*_k(X_k)$ (Lemma~\ref{lem:int_reduction}).
+
+Thus, $R(f^{*(s-1)}) - R(f^{*s}) \geq \E f^*_k(X_k)^2 \geq \alpha$ by Assumption A4.
 
@@
 
+Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.
+
 Suppose $\hat{f}$ has at most $s-1$ non-zero components. Then
@@
 \end{align*}
-Where $\tau_n$ is the deviation between empirical risk and true risk and $\tau'_n$ is the approximation error incurred by empirically sampling $f^{*s}$.
+The third line follows from Lemma~\ref{lem:minus_one_risk_increase}.
+$\tau_n$ is the deviation between empirical risk and true risk and $\tau'_n$ is the approximation error incurred by empirically sampling $f^{*s}$.
 
@@
 \]
+
 Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $4(sB)^2$.
@@
 \end{proof}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "icml14/scam_icml.tex" ***
+%%% End: ***

### 2013-10-04 tex/scam/appendix.tex
appendix update
proof and result update

@@
 \[
-\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
+\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)\big|^2 d \mathbf{x}_{-k}.
 \]
@@
 \[
-min_{f_k} \{ \E( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k))^2 \,:\, \E f_k(X_k) = 0 \}
+min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
+                    \,:\, \E f_k(X_k) = 0 \}
 \]
@@
 
-By the assumption that , we know that, for all $x_k$,
+Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
 \begin{align*}
@@
 
-For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0 + w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0 + w} = \frac{1}{n} \sum_i f_0(X^{(i)}) + w_i $ and $\mu = \E f_0(X)$.
+For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0} - \bar{w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0} = \frac{1}{n} \sum_i f_0(X^{(i)})$ and $\bar{w} = \frac{1}{n}\sum_{i=1}^n w_i $ and $\mu = \E f_0(X)$.
 Note that we \emph{subtract} out the mean in the two risk definitions.
@@
 
+\textbf{Note:} By definition of the Lipschitz condition, $f_k \in \mathcal{C}[b,B,L]$ implies that $\| \partial f_k \|_\infty \leq L$.
+$f = \sum_k f_k \in \mathcal{C}[s,b,B,L]$ implies that $\rho_n(f) \leq sL$.
+
 \subsubsection{Proof}
@@
 
+We first start with a lemma that converts assumption A4 into a more easily applicable condition.
 \begin{lemma}
@@
 
-Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}^s[b,B,L], f_k \trm{ centered} \}$.
+Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}[s,b,B,L], f_k \trm{ centered} \}$.
 
-Suppose $n$ is large enough such that $c L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \right) \rightarrow 0$.
+Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \rightarrow 0$.
 
-Then, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
+Then, for all large enough $n$, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
 \end{theorem}
@@
 
-$f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered.
+\textbf{Step 1:} $f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered.
 Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$.
@@
 \begin{align*}
-|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq \| y - f^{*s} + \bar{f}^{*s} \|_n^2  - \| y - f^{*s}\|_n^2 \\
-	&\leq 2\|y-f^{*s}\|_n \|\bar{f}^{*s}\|_n + \|\bar{f}^{*s}\|_n^2 
+|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq 
+               \| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w}\mathbf{1}_n 
+                     - f^{*s} + \bar{f}^{*s}\mathbf{1}_n \|_n^2  - \| y - f^{*s}\|_n^2 \\
+	&\leq 2\| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n -f^{*s}\|_n 
+                \|\bar{f}^{*s} \mathbf{1}_n \|_n 
+                  + \|\bar{f}^{*s} \mathbf{1}_n \|_n^2 \\
+        &\leq 2 | \bar{f}^{*s} | \| f_0 + w 
+           - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n - f^{*s} \|_n + |\bar{f}^{*s}|^2 
 \end{align*}
 
-Because each $f_k^{*s}$ is bounded by $B$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}_k^{*s}| \leq B\sqrt{\frac{1}{cn} \log n}$.
-By an union bound therefore, with probability at least $1-\frac{C}{n}$, $\|\bar{f}^{*s}\|_n \leq B\sqrt{\frac{1}{cn} \log sn}$.
+Because each $f^{*s}$ is bounded by $sB$ and $\E f^{*s}(X) = 0$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}^{*s}| \leq sB \sqrt{\frac{1}{cn} \log n}$.
 
 \begin{align*}
-\| y - f^{*s} \|_n &= \| f_0 + w - f^{*s} \|_n \\
-	&\leq \| f_0 - f^{*s} \|_n + \|w\|_n \\
+\| f_0 + w -\bar{f}_0\mathbf{1}_n 
+                       - \bar{w} \mathbf{1}_n - f^{*s} \|_n 
+	\leq \| f_0 - f^{*s} \|_n + \|w\|_n + |\bar{f}_0| + |\bar{w}|\\
 \end{align*}
@@
 
+$| \bar{f}_0 | \leq s B$ and $| \bar{w} | \leq c \sigma \sqrt{\frac{1}{n}}$ with probability at least $1-\frac{C}{n}$ by Chernoff bound.
+
 So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
 \[
-|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
+|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2c (sB+\sigma) sB \sqrt{\frac{1}{cn} \log n}
 \]
 
-Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.
+\textbf{Step 2:} Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.
 
@@
 
-$\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $L$.
+Because we assume that we impose the Lipschitz constraint in our optimization, $\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $sL$ and so $|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2 sL \lambda_n$.
+
 By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.
 
-$|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2L \lambda_n$.
-
-$\tau'_n$, as shown above, is at most $2sB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.
+$\tau'_n$, as shown above, is at most $2 (sB+\sigma) sB \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.
 
@@
 \[
-c\max(L\lambda_n,  bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
+c s L \lambda_n < \alpha \trm{ and } bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
 \]
-we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction.
+we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction since we assumed that $\hat{f}$ minimizes the regularized empirical risk.
 
@@
 \begin{proof}
+This proof uses a standard covering number argument.
 
-Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$.
+Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$ such that for all $f \in \mathcal{C}[s,b,B,L]$, there exists $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ such that $\| f - f'\|_\infty \leq \epsilon$.
 
-For all $f \in \mathcal{C}^s[b,B,L]$,
+For all $f \in \mathcal{C}[s,b,B,L]$,
 \[
@@
 
-Step 1. We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
+\textbf{Step 1.} We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
 
 \begin{align*}
-|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 + w - f \|_n^2 - \| f_0 + w - f' \|_n^2| \\
-	&\leq 2 \langle f_0 + w , f' - f \rangle_n + \| f \|_n^2 - \| f' \|_n^2\\
-	&\leq 2 \| f_0 + w \|_n \| f' - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
+|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 - \bar{f}_0 + w - \bar{w} - f \|_n^2 
+                                - \| f_0 - \bar{f}_0 + w -\bar{w} - f' \|_n^2| \\
+	&\leq 2 \langle f_0 - \bar{f}_0 + w -\bar{w}, f' - f \rangle_n 
+                            + \| f \|_n^2 - \| f' \|_n^2\\
+	&\leq 2 \| f_0 - \bar{f}_0 + w -\bar{w} \|_n \| f' 
+                   - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
 \end{align*}
 
-$\| f_0 + w \|_n \leq \| f_0 \|_n + \|w \|_n$.
+We now want to bound $\| f_0 - \bar{f}_0 + w -\bar{w} \|_n \leq \| f_0 \|_n  + \|w \|_n + |\bar{f}| + |\bar{w}|$.
+
 $\| w \|^2_n = \frac{1}{n}\sum_{i=1}^n w_i^2$ is the average of subexponential random variables.
@@
 The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$.
+Since $\E w^2 \leq \sigma^2$, for all $n > n_0$, with probability at least $1 - \frac{C}{n}$, for some constant $c$, $\| w \|^2_n \leq c \sigma^2$.
 
-$\|f_0\|^2_n$ is the average of random variables bounded by $B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E |f_0(X)|^2 | \leq B^2\sqrt{ \frac{1}{cn} \log n}$.
+By Chernoff bound and the fact that $\E w = 0$, we know that $|\bar{w}| \leq c \sigma \sqrt{\frac{1}{n}}$ with high probability.
 
-Since $\E|w|^2 \leq c\sigma^2$ and $\E| f_0(X)|^2 \leq B^2$, we have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 + w \|_n \leq c(B+\sigma)$.
+%$\|f_0\|^2_n$ is the average of random variables bounded by $s^2 B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E f_0(X)^2 | \leq s^2B^2\sqrt{ \frac{1}{cn} \log n}$.
+Since $\E f_0(X)^2 \leq s^2B^2$, we have that, for all $n > n_0$, with probability at least $1-\frac{C}{n}$, for some constant $c$, $\| f_0 \|_n^2 \leq c s^2 B^2$.
+
+$\|f_0\|^2_n = \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})^2$. Since $f_0(X^{(i)})^2 \leq s^2 B^2$, $\|f_0\|^2_n \leq s^2 B^2$.
+
+$|\bar{f}_0| = | \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})| \leq s B$.
+
+Combining these together, We have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c ( s^2 B^2 +\sigma^2 )$, and so
+
+\[
+\|f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c (sB + \sigma)
+\]
 
@@
 \begin{align}
-|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation1}
+|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon c( sB + \sigma ) \label{eqn:approx_deviation1}
 \end{align}
@@
 
-Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
+\textbf{Step 2:} Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
 \begin{align}
-|R_s(f') - R_s(f)| \leq \epsilon cs(B + \sigma) \label{eqn:approx_deviation2}
+|R_s(f') - R_s(f)| \leq \epsilon c(sB + \sigma) \label{eqn:approx_deviation2}
 \end{align}
 
-Lastly, we bound $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} \hat{R}_s(f') - R_s(f')$.
+\textbf{Step 3:} Lastly, we bound $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} \hat{R}_s(f') - R_s(f')$.
 
 For a fixed $f'$, we have that, by definition
-\[
-\| f_0 + w - f' \|_n^2 = \| f_0 - f'\|_n^2 + 2 \langle w, f_0 - f'\rangle_n + \| w \|_n^2 \\
-\]
+\begin{align*}
+\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
+     &= \| f_0  - \bar{f}_0\mathbf{1}_n - f'\|_n^2 
+       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n - f'\rangle_n + \| w \|_n^2 + |\bar{w}|\\
+R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
+     &= \E\big(f_0(X) - \mu - f'(X)\big)^2 + \E w^2  
+\end{align*}
 
-Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $4(sB)^2$.
+Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
 
-Using Hoeffding Inequality then, we know that the probability $| \| f_0 - f' \|_n^2 - \E(f_0(X) - f '(X))^2 | \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
+Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
 
@@
 
-Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_0^s[b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
+Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
 \[
-C \exp( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} )
+C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} \big)
 \]

### 2013-10-04 tex/scam/icml14/sparsistency_icml.tex
updated proof of additive faithfulness
proof and result update

--- 2013-09-30 tex/scam/sparsistency.tex
@@
   $f_0(X) = f_0(X_S)$.
-\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
+\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
 \end{packed_enum}
@@
   twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
-\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
-\item[A4:] For all $k=1,...,s$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
+\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq \E e^{\sigma^2 t^2 / 2}$.
+\item[A4:] For all $k=1,...,s$, $\E(f^*_s(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
 \end{packed_enum}
@@
 We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
-The $\alpha$ in assumption A4 can be interpreted as the signal strength of the relevant variable detection problem.
 
@@
   %[TODO: refer to correlated design experiment].
+\end{remark}
+
+\begin{remark}
+Assumption A4 ensures that the relevant variables are ``relevant enough''.
+Under A4, the population risk of an additive function with $s-1$ components is at least $\alpha$ larger than the population risk of the optimal additive function with $s$ components.
+Lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
 \end{remark}
@@
 \label{thm:false_negative}
-Suppose assumptions A1', A2', A3 hold.
+Suppose assumptions A1', A2', A3, A4 hold.
 Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint.
 Let $c,C$ be absolute constants.
-Suppose $L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \right) \rightarrow 0$.
+Suppose $s L \lambda_n \rightarrow 0$ and $bL (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow 0$.
 Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
@@
 \begin{corollary}
-  Assume A1', A2', A3. Let $\lambda_n = \Theta\left( \sqrt{
-  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $\lambda_n
+  Assume A1', A2', A3, A4. Let $\lambda_n = \Theta\left( \sqrt{
+  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $s \lambda_n
   \rightarrow 0$ and $\sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow
@@
 %\textbf{Comparison with Related Work.}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "scam_icml.tex" ***
+%%% End: ***

### 2013-10-04 tex/scam/icml14/optimization_icml.tex
minor edits

@@
 \begin{align*}
-  \forall j\geq{}i,\; h_{k(j)}-h_{k(i)}  &= 
+  \forall & j\geq{}i, \; h_{k(j)}-h_{k(i)}  = 
             \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) \\
-      & = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
-      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) \\
+      & = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})
+       \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) \\
       & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \forall j<i,\;  h_{k(j)}-h_{k(i)} &=
+  \forall & j<i,\;  h_{k(j)}-h_{k(i)} =
                 \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) \\
-     &= \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
-     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)})  \\
+     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) 
+     \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)})  \\
      &= \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
@@
 
-Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = \Delta_{k(j)}(x_{k(i)})$ and $d_k = (d_{k(1)} ,..., d_{k(n-1)})$.
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = \Delta_{k(j)}(x_{ki})$ and $d_k = (d_{k(1)} ,..., d_{k(n-1)})$.
 We can now reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
@@
 \end{align}
-$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.
+$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 4\|\bds{\beta}_{k\cdot}\|_{\infty}$.
 

### 2013-10-04 tex/scam/appendix.tex
appendix update

@@
 \end{align*}
-In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.
+In the derivatives, $\mathbf{u}_k$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.
 
@@
 \begin{align*}
--\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} 
+-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u}_k 
            - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
@@
 \end{align*}
-where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.
+where $\mathbf{u}_k$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.
 
@@
 \[
-\lambda \mathbf{u} - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
+\lambda \mathbf{u}_k - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
 \]
@@
 \]
-then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.
+then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.
 
@@
 \begin{align*}
-\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}) 
-                                            - \frac{1}{n} \hat{r}^\tran X_{k(j)} \\
+\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= 
+              \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n) 
+                                       - \frac{1}{n} \hat{r}^\tran \mathbf{1}_n X_{k(j)} \\
                   &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})
@@
 \hat{r}_i &= Y_i - \bar{Y}_i -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
-	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
-	&=  f_0(X_S^{(i)}) - \bar{f_0} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) + \epsilon_i - \bar{\epsilon}
+	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- 
+                      \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
+	&=  f_0(X_S^{(i)}) - \bar{f_0} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) 
+                   + \epsilon_i - \bar{\epsilon}
 \end{align*}
@@
 \hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
-     &= \| f_0  - \bar{f}_0\mathbf{1}_n - f'\|_n^2 
-       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n - f'\rangle_n + \| w \|_n^2 + |\bar{w}|\\
+     &= \| f_0  - \bar{f}_0\mathbf{1}_n - \bar{w}\mathbf{1}_n - f'\|_n^2 
+       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n -\bar{w}\mathbf{1}_n - f'\rangle_n 
+       + \| w \|_n^2 \\
 R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
@@
 \begin{proposition} (Subexponential Concentration \cite{vershynin2010introduction})
-Let $X_1,...,X_N$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
+Let $X_1,...,X_n$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
 \[
-P( | \frac{1}{N} \sum_{i=1}^N X_i | \geq \epsilon) \leq
-	2 \exp \left[ -c N \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) \right]
+P( | \frac{1}{n} \sum_{i=1}^n X_i | \geq \epsilon) \leq
+	2 \exp \left[ -c n \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) \right]
 \]
@@
 \[
-c \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) = \frac{1}{N} \log \frac{1}{\delta}.
+c \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) = \frac{1}{n} \log \frac{1}{\delta}.
 \]
@@
 
-A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.s
+A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n|$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.
 

### 2013-10-04 tex/scam/icml14/related_work_icml.tex
changes

\section{Related Work}

\cite{Raskutti:12,Kolch:10,dalalyan:12,bertin:08,devore:11}

%* Laetitia Comminges, Arnak S. Dalalyan 
%Tight conditions for consistency of variable selection 
%In the context of high dimensionality. 
%Ann. Statist, 40(5), 2667-2696, 2012 
%
%Comment: They estimate the coefficient of the regression function with respect to a Fourier basis and then threshold the estimated coefficients. They prove that sparsistency is achievable so long as $n > log p$ and $n > exp(s)$. They assume that the functions are smooth with respect to the Fourier basis. The fourier coefficients however seem difficult to estimate; it appears that the knowledge of the true density is required. They also provide lower bounds showing that sparsistency is un-achievable if $n < log p$ or if $n < exp(s)$.
%
%
%* Bertin, K. and Lecu´e, G. (2008). Selection of variables 
%and dimension reduction in high-dimensional non-parametric 
%regression. Electron. J. Stat. 2 1224–1241 
%
%Comment: They assume Holder smoothness and use multiple L1 regularized local polynomial smoothing to detect the sparsity pattern. They require that $p < log n$.
%
%
%* "Approximation of Functions of Few Variables in High Dimensions" 
%by DeVore, Petrova and Wojtaszczyk. 
%
%Comment: They show that variable selection under a scaling of $n > log
%p, n > exp(s)$ is possible if one adaptively selects the points on
%which the high-dimensional functions are evaluated.
%

### 2013-10-04 tex/scam/icml14/related_work_icml.tex
added section on related work

@@
 
-\cite{Raskutti:12,Kolch:10,dalalyan:12,bertin:08,devore:11}
+Variable selection in general nonparametric regression or function
+estimation is a notoriously difficult problem.  In even moderate
+dimensions, nonparametric regression is subject to the curse
+of dimensionality.  But if the function is sparse, depending
+on only a few covariates, there is hope that by identifying
+the relevant variables one can effectively reduce the 
+dimension, and  estimate the function at the
+corresponding lower dimensional statistical rate of convergence.
+
+\citet{lafferty2008rodeo} develop a greedy procedure for
+adjusting bandwidths in a local linear regression estimator,
+and show that the procedure achieves the minimax rate
+as if the relevant variables were isolated in advance.
+But the method does not carry out explicit variable selection.
+Moreover, it only provably scales to dimensions $p$ that 
+grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  Note that this
+is the opposite of the high dimensional scaling behavior
+known to hold for sparsity selection in linear models
+using $\ell_1$ penalization, where the sample size $n$
+is logarithmic in the dimension $p$. \citet{bertin:08}
+develop an optimization-based approach in
+the nonparametric setting, applying the lasso
+in a local linear model at each test point.  Here again,
+however, the method only scales as $p = O(\log n)$,
+the low-dimensional regime.
+An approximation theory approach to the same
+problem is presented in \cite{devore:11}, 
+using techniques based on hierarchical hashing schemes,
+similar to those used for ``junta'' problems \cite{mossel:04}.
+Here it is shown that the sample complexity scales as $n > \log p$ 
+if one adaptively selects the points on
+which the high-dimensional function is evaluated.
+\citet{dalalyan:12} give
+support for the intrinsic difficulty of variable
+selection in nonparametric regression, giving lower bounds 
+showing that sparsistency is not possible if $n < \log p$ or if $n <
+\exp s$, where $s$ is the number of relevant variables.
+Variable selection over kernel classes is studied
+by \citet{Kolch:10}.
+
+Perhaps most closely related to the present work, is the framework
+studied by \cite{Raskutti:12} for sparse additive models, where sparse
+regression is considered under an additive assumption, with each
+component function belonging to an RKHS.  An advantage of working over
+an RKHS, in contrast to the other papers mentioned above, is that
+regression with a sparsity-inducing regularization penalty can be
+formulated as a finite dimensional convex cone optimization.
+On the other hand, 
+smoothing parameters for the component Hilbert spaces
+must be chosen, leading to extra tuning parameters
+that are difficult to select in practice.  In addition, 
+the additive model must be assumed to
+be correct for sparsistent variable selection.
+
+An attraction of the convex function estimation
+framework we consider in this paper
+is that the additive model can be
+used for convenience, without assuming it
+to actually hold.  Moreover, our estimator has
+no tuning parameters.  As we show below,
+our method scales to high dimensions, with
+a dependence on the intrinsic dimension $s$ 
+that scales polynomially, rather than exponentially
+as in the general case analyzed in \cite{dalalyan:12}.
 
@@
 The fourier coefficients however seem difficult to estimate; it appears that the knowledge of the true density is required.
-They also provide lower bounds showing that sparsistency is un-achievable if $n < log p$ or if $n < exp(s)$.
+They also provide
 %
@@
 %
-%Comment: They show that variable selection under a scaling of $n > log
-%p, n > exp(s)$ is possible if one adaptively selects the points on
-%which the high-dimensional functions are evaluated.
+%Comment: They show that variable selection under a scaling of
 %

### 2013-10-04 tex/scam/icml14/related_work_icml.tex
changed related work section

@@
 Variable selection in general nonparametric regression or function
-estimation is a notoriously difficult problem.  In even moderate
-dimensions, nonparametric regression is subject to the curse
-of dimensionality.  But if the function is sparse, depending
+estimation is a notoriously difficult problem.  
+Nonparametric regression is subject to the curse
+of dimensionality,
+and may be inaccurate even in moderate dimensions,
+without any additional assumptions.  But if the function is sparse, depending
 on only a few covariates, there is hope that by identifying
@@
 dimension, and  estimate the function at the
-corresponding lower dimensional statistical rate of convergence.
+corresponding faster statistical rate of convergence.
 
@@
 which the high-dimensional function is evaluated.
+
 \citet{dalalyan:12} give
@@
 an RKHS, in contrast to the other papers mentioned above, is that
-regression with a sparsity-inducing regularization penalty can be
+nonparametric regression with a sparsity-inducing regularization penalty can be
 formulated as a finite dimensional convex cone optimization.
@@
 
-An attraction of the convex function estimation
-framework we consider in this paper
-is that the additive model can be
-used for convenience, without assuming it
-to actually hold.  Moreover, our estimator has
-no tuning parameters.  As we show below,
-our method scales to high dimensions, with
-a dependence on the intrinsic dimension $s$ 
-that scales polynomially, rather than exponentially
-as in the general case analyzed in \cite{dalalyan:12}.
+An attraction of the convex function estimation framework we consider
+in this paper is that the additive model can be used for convenience,
+without assuming it to actually hold.  While nonparametric, the
+problem is naturally formulated using finite dimensional convex
+optimization, but with no additional tuning parameters.  As we show
+below, our method scales to high dimensions, with a dependence on the
+intrinsic dimension $s$ that scales polynomially, rather than
+exponentially as in the general case analyzed in \cite{dalalyan:12}.
 

### 2013-10-04 tex/scam/appendix.tex
appendix

@@
 \min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
-         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)\big|^2 d \mathbf{x}_{-k}.
+         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\big|^2 
+                 d \mathbf{x}_{-k}.
 \]
@@
 \]
-where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.
+where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^{n-1}$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n-1$.
 
@@
 \]
-then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.
+then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n-1$.
 
@@
                                        - \frac{1}{n} \hat{r}^\tran \mathbf{1}_n X_{k(j)} \\
-                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})
+                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n)
 \end{align*}
@@
 \begin{align*}
-\hat{r}_i &= Y_i - \bar{Y}_i -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
+\hat{r}_i &= Y_i - \bar{Y} -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
 	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- 
@@
 
- Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w \|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.
+ Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w\|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.
+We will also abuse notation and let $\| f + c \|_n^2 = \frac{1}{n} \sum_{i=1}^n (f(X^{(i)}) + c)^2$ if $c$ is a scalar.
+
+We let $\langle f, g \rangle_n \coloneqq \frac{1}{n} \sum_{i=1}^n f(X^{(i)}) g(X^{(i)})$. It then follows that:
+\begin{packed_enum}
+\item $\| f + g \|_n^2 = \|f\|_n^2 + 2 \langle f, g \rangle_n + \|g \|_n^2$
+\item $\langle f, g \rangle_n \leq \|f\|_n \| g \_n$
+\end{packed_enum}
 
@@
 
-We will argue that all the components of the additive function $f^{*(s-)}$ are also in $f^{*s}$.
+We will argue that all the components of the additive function $f^{*(s-1)}$ are also in $f^{*s}$.
 Let us denote the components of $f^{*s} = \sum_{k=1}^s f_k^*$.
@@
 |\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq 
-               \| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w}\mathbf{1}_n 
-                     - f^{*s} + \bar{f}^{*s}\mathbf{1}_n \|_n^2  - \| y - f^{*s}\|_n^2 \\
-	&\leq 2\| f_0 + w - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n -f^{*s}\|_n 
-                \|\bar{f}^{*s} \mathbf{1}_n \|_n 
-                  + \|\bar{f}^{*s} \mathbf{1}_n \|_n^2 \\
+         \| f_0 + w - \bar{f}_0 - \bar{w}
+         - f^{*s} + \bar{f}^{*s} \|_n^2  - \| f_0 + w - \bar{f}_0 - \bar{w} - f^{*s}\|_n^2 \\
+   &\leq 2 \langle f_0 + w - \bar{f}_0 - \bar{w} - f^{*s}, \bar{f}^{*s} \rangle_n 
+         + \| \bar{f}^{*s} \|_n^2 \\
+   &\leq 2\| f_0 + w - \bar{f}_0 - \bar{w} -f^{*s}\|_n 
+                \|\bar{f}^{*s} \|_n 
+                  + \|\bar{f}^{*s} \|_n^2 \\
    &\leq 2 | \bar{f}^{*s} | \| f_0 + w 
-           - \bar{f}_0 \mathbf{1}_n - \bar{w} \mathbf{1}_n - f^{*s} \|_n + |\bar{f}^{*s}|^2 
+           - \bar{f}_0 - \bar{w} - f^{*s} \|_n + |\bar{f}^{*s}|^2 
 \end{align*}
@@
 \begin{align*}
-\| f_0 + w -\bar{f}_0\mathbf{1}_n 
-                       - \bar{w} \mathbf{1}_n - f^{*s} \|_n 
+\| f_0 + w -\bar{f}_0 - \bar{w} - f^{*s} \|_n 
 	\leq \| f_0 - f^{*s} \|_n + \|w\|_n + |\bar{f}_0| + |\bar{w}|\\
@@
 \begin{align*}
-\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
-     &= \| f_0  - \bar{f}_0\mathbf{1}_n - \bar{w}\mathbf{1}_n - f'\|_n^2 
-       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n -\bar{w}\mathbf{1}_n - f'\rangle_n 
-       + \| w \|_n^2 \\
+\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0 - \bar{w} - f' \|_n^2\\
+      &= \|f_0 - \bar{f}_0 - f'\|_n^2 + 2 \langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n
+             + \| w - \bar{w}\|_n^2\\
 R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
@@
 
-Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
+Therefore:
+\begin{align*}
+\hat{R}_s(f') - R_s(f') = & \|f_0 -\bar{f}_0 - f'\|_n^2 - \E(f_0(X) - \mu - f'(X))^2 \\
+            &+ \|w - \bar{w}\|_n^2 - \E w^2 \\
+            &+ 2\langle w-\bar{w}, f_0 - \bar{f}_0 - f'\rangle_n
+\end{align*}
+
+\textbf{Step 3.1:} We first bound $2 \langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n$.
+\begin{align*}
+\langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n &=
+      \langle w, f_0 - \bar{f}_0 - f'\rangle_n 
+      - \langle \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n \\
+\end{align*}
+
+The first term, fully expanded, is $\frac{1}{n} \sum_{i=1}^n w_i (f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)}))$.
+Since $w_i$ and $X^{(i)}$ are independent, we use the sub-Gaussian concentration inequality.
+Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle| > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.
+
+The second term, fully expanded, is $\bar{w} \bar{f'}$. $\bar{f'} \leq sB$ and so $|\bar{w}\bar{f'}| > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2(sB)^2} \big)$ as well.
+
+\textbf{Step 3.2} We now bound $\| w - \bar{w} \|_n^2 - \E w^2$. 
+\begin{align*}
+\|w - \bar{w} \|_n^2 &= \|w\|_n^2 - 2 \langle w, \bar{w} \rangle_n + \|\bar{w}\|_n \\
+               &= \|w\|_n^2 - \bar{w}^2
+\end{align*}
+
+Using sub-Exponential concentration, we know that $| \|w\|_n^2 - \E w^2 | \geq t$ with probability at most $C \exp( - c n \frac{1}{\sigma^2})$.
+
+$\bar{w} \leq \sigma\frac{1}{cn}$ with probability at least $1-\frac{C}{n}$.
+
+\textbf{Step 3.3:} We now bound $\| f_0 - \bar{f}_0 - f'\|_n^2 - \E(f_0(X) - \mu - f'(X))^2$.
+
+Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
 
@@
 
-Collecting all these results and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
+and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
 \[
@@
 
-Let $f' \coloneqq = \sum_{k=1}^s f'_k$, then 
+Let $f' \coloneqq \sum_{k=1}^s f'_k$, then 
 \[

### 2013-10-04 tex/scam/appendix.tex
appendix fixed

@@
 
-Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \rightarrow 0$.
+Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.
 
@@
 
-By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.
+By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  Lb (sB+\sigma) sB \sqrt{ \frac{s}{cn^{4/5}} \log n}$.
 
@@
 \[
-c s L \lambda_n < \alpha \trm{ and } bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
+c s L \lambda_n < \frac{\alpha}{2} \trm{ and } Lb sB (sB+\sigma) \sqrt{ \frac{s}{n^{4/5}} \log sn}) < \frac{\alpha}{4}
 \]
@@
 \[
-\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq B\sigma(B+\sigma)Lb\sqrt{ \frac{1}{cn^{4/5}} s^5 \log sn}
+\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq Lb(sB+\sigma)sB\sqrt{ \frac{s}{cn^{4/5}} \log sn}
 \]
@@
 Since $w_i$ and $X^{(i)}$ are independent, we use the sub-Gaussian concentration inequality.
-Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle| > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.
+Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle_n | > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.
 
@@
 
-$\bar{w} \leq \sigma\frac{1}{cn}$ with probability at least $1-\frac{C}{n}$.
+$\bar{w} \leq \sigma\sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$.
+Thus, $| \bar{w}|^2 \leq \sigma^2 \frac{1}{cn}$ with high probability, has a second order effect, and can be safely ignored in the bound.
 
@@
 
-Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
+\begin{align*}
+\| f_0 - \bar{f}_0 - f'\|_n^2 &= \|f_0 -\mu+\mu - \bar{f}_0 - f'\|_n^2 \\
+      &= \| f_0 - \mu - f'\|_n^2 + 2 \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n 
+          + \|\mu - \bar{f}_0 \|_n^2 
+\end{align*}
 
-Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
+Using similar reasoning as before, we know that $| \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n | \geq t $ with probability at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
 
-Consider now the term $2 \langle w, f_0 - f' \rangle_n \coloneqq \frac{2}{n} \sum_{i=1}^n w_i ( f_0(X^{(i)}) - f'(X^{(i)}))$. We note that $w_i$ and $X^{(i)}$ are independent, $w_i$ is subgaussian.
+Likewise, $| \mu - \bar{f}_0 | \leq sB \sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$.
+Thus, $| \mu - \bar{f}_0 |^2 \leq (sB)^2 \frac{1}{cn}$, has a second order effect, and can be safely ignored in the bound.
 
-The $n$-dimensional vector $\{ \frac{1}{n} ( f_0(X^{(i)}) - f'(X^{(i)})) \}_i$ has norm at most $\frac{sB}{\sqrt{n}}$.
-Therefore, $|2 \langle w, f_0 - f' \rangle_n | \geq t$ with probability at most $C \exp( - c n t^2 \frac{1}{\sigma^2(sB)^2})$.
+Because $f_0(X^{(i)}) -\mu - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 -\mu- f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
 
-The last term $\| w \|_n^2 = \frac{1}{n} \sum_{i=1}^n w_i^2$.
-Using subexponential concentration, we know that $ |\| w \|_n^2 - \E|w|^2 | \geq t$ occurs with probability at most $C \exp( - c n \frac{1}{\sigma^2} )$ for $n$ larger than some $n_0$.
+Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) -\mu - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
 
-and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
+Applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
 \[
-C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} \big)
+C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2(sB)^2 + (sB)^4} \big)
 \]
@@
 \begin{align}
-\sqrt{ \frac{1}{cn} \sigma^2 (sB)^4 \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
+(sB+\sigma)sB\sqrt{ \frac{1}{cn} \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
 \end{align}
-Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} becomes $\sqrt{ \frac{1}{cn^{4/5}} \sigma^2 s^5 B^4 \log Cn}$.
+Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} can be upper bounded by $sB(\sigma+sB)\sqrt{ \frac{s}{cn^{4/5}} \log Cn}$.
 
-Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (B+\sigma)$.
+Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} from \textbf{Step 1} and \textbf{Step 2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (sB+\sigma)$.
+
+We can arrive at the statement of the theorem by summing these up and absorbing any constants into the symbols $c$ and $C$.
 

### 2013-11-01 tex/discussion_notes.tex
journal

@@
 
-\begin{document}
+\begin{document}\
+
+\section{10/25/2013: Convex + Concave function}
+
+Now we consider variable selection for $h(x) = f(x) + g(x)$ where $f$ is convex and $g$ is concave.
+
+\subsection{Separation Approach}
+
+Here is one line of thought.
+We are given $h_i = h(x_i)$ for a bunch of sample points.
+Suppose we can learn the decomposition $f_i + g_i = h_i$, then we can use additive faithfulness to recover the relevant variables of $f$ and $g$.
+
+The separation may not be easy however. Perhaps the following optimization:
+
+\begin{align*}
+\min_{\beta, \theta}&\sum_{j=1}^p \Big( \|\beta_j\|_\infty + \| \theta_j\|_\infty \Big) \\
+ \trm{s.t. } & h_i = f_i + g_i \\
+ & f_i \geq f_{i'} + \theta_{i'}^\tran (x_i - x_{i'}) \\
+ & g_i \leq g_{i'} + \beta_{i'}^\tran (x_i - x_{i'}) 
+\end{align*}
+
+Of course, we have identifiability issues. There exist two sets of functions $\mathcal{F}$ and $\mathcal{G}$ such that for all $f \in \mathcal{F}$, there exist $g \in \mathcal{g}$ such that $f+g = h$.
+
+The gradient penalty in the optimization program is then critical because it may let us learn a \textbf{sparse} $f,g$.
+
+We emphasize that we do not attempt to do variable selection at all in the separation optimization, we only want to recover the values $f_i$ and $g_i$.
+The sparsity patterns of $\beta$ and $\theta$ are of no importance.
+
+\newpage
+
 \section{(7/26/2013)}

### 2013-11-01 tex/scam/additive_faithful.tex
journal

@@
 
-The additive approximation may mark a relevant variable as
-irrelevant. Such mistakes are inherent to the approximation and may
-persist even with infinite
-samples.  Lemma~\ref{lem:general_int_reduction} below provides
-examples of errors made by the additive approximations that minimize
-the $L_2$ distance.
+For general regression, additive approximation may result in a
+relevant variable being incorrectly marked as irrelevant. Such
+mistakes are inherent to the approximation and may persist even with
+infinite samples.  In this section we give
+examples of this phenomenon, and then show how the convexity
+assumption
+changes the behavior of the additive approximation.  We begin
+with a lemma that implies uniqueness of the additive regression function.
+
+\begin{figure*}[htp]
+\vskip-10pt
+	\centering
+	\subfigure[egg carton]{
+		\centering
+		{\includegraphics[width=0.4\textwidth]{figs/sine_wave_funct3}}
+	}
+	\subfigure[tilting slope]{
+		\centering
+		{\includegraphics[width=0.4\textwidth]{figs/tilting_slope_funct3}}
+	}
+\caption{Two additively unfaithful functions. Relevant variables are
+  zeroed out under an additive approximation because every ``slice''
+  of the function integrates to zero.}
+\vskip-10pt
+\end{figure*}
 
@@
 $X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
-integrable function and suppose, without loss of generality, that $\E f(X) = 0$.
-Let $\ds f^*_1,...,f^*_s \coloneqq \arg\min \{ \E \bigl( f(X) -
-\sum_{k=1}^s f_k(X_k) \bigr)^2 \,:\, \E f_k(X_k) = 0\}$. Then $f^*_k(x_k) = \E[ f(X) \given x_k]$ is unique.
+integrable function.
+Let 
+\begin{equation}
+\begin{split}
+f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ \E \bigl( f(X) & -
+ \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \\
+       & \,:\, \E f_k(X_k) = 0\Bigr\}.
+\end{split}
+\end{equation}
+Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
 \end{lemma}
@@
 assume without loss of generality that $\E f(X) = 0$. Let 
-$$\ds f^*_1,...,f^*_s \coloneqq \arg\min \Bigl\{ \E ( f(X) - \sum_{k=1}^s
-f_k(X_k) )^2 \,:\, \E f_k(X_k) = 0, \forall k\Bigr\}.$$
+\begin{equation}
+\begin{split}
+f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
+             \E ( f(X) &- \sum_{k=1}^s f_k(X_k) -\mu )^2 \\
+         &\,:\, \E f_k(X_k) = 0 \Bigr\}.
+\end{split}
+\end{equation}
 We say that $f$ is \emph{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
@@
   convex function can be approximated arbitrarily well by a smooth
-  one.  Without restrictions on the distribution, a convex
+  one.  
+\end{remark}
+\begin{remark}
+Without restrictions on the distribution, a convex
   function may not be additively faithful. Intuitively, an arbitrarily shaped
@@
 \end{remark}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2013-11-01 tex/scam/appendix.tex
journal

@@
-\section*{Appendix}
+\section{Appendix}
 
@@
 
-We start with a lemma similar to Lemma~\ref{lem:general_int_reduction} and whose proofs are identical.
+We start with a proof of Lemma~\ref{lem:general_int_reduction}. We restate the lemma here for convenience.
 
 \begin{lemma}
-\label{lem:int_reduction}
-Let $F$ be a product distribution on $C=[0,1]^s$ with density function $p$. Let $f: C \rightarrow \R$ be a convex function. Suppose that $\E f(X) = 0$.
+Let $F$ be a product distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
 
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
+Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
 
@@
 We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
-This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.\\
+This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.
+\\
 
@@
 
-Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and is convex.
-The former is clearly true; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+Now, we note that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
 
@@
 
+The next lemma adapts Lemma~\ref{lem:general_int_reduction} to convex functions.
+
+\begin{lemma}
+\label{lem:int_reduction}
+Let $F$ be a product distribution on $C=[0,1]^s$ with positive density function $p$. Let $f: C \rightarrow \R$ be a convex function.
+
+Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
+
+Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
+\end{lemma}
+
+\begin{proof}
+The proof is identical to that of Lemma~\ref{lem:general_int_reduction}. We need only verify that $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ is convex.
+
+This is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+\end{proof}
+
  The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.
@@
 \begin{proposition}
+\label{prop:faithful_condition}
 Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
 
-Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$.
+Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
 
@@
 
+\textbf{Note:} the symbols $c,C$ represent absolute constants.
+We will often abuse notation and ``absorb'' new absolute constants into $c, C$; the actual value of $c, C$ could thus vary from line to line.
+
  We first restate the theorem for convenience.
@@
 
+\textbf{Note:} the symbols $c,C$ represent absolute constants.
+We will often abuse notation and ``absorb'' new absolute constants into $c, C$; the actual value of $c, C$ could thus vary from line to line.
+
  We will use covering number and uniform convergence and will thus need to first introduce some notations. 
@@
 \item $\| f + g \|_n^2 = \|f\|_n^2 + 2 \langle f, g \rangle_n + \|g \|_n^2$
-\item $\langle f, g \rangle_n \leq \|f\|_n \| g \_n$
+\item $\langle f, g \rangle_n \leq \|f\|_n \| g \|_n$
 \end{packed_enum}
@@
 \begin{align*}
- \frac{1}{n} \sum_{i=1}^n w_i^2 &\leq c\sigma^2 (1+\sqrt{\frac{1}{cn} \log Cn}) \\
+ \frac{1}{n} \sum_{i=1}^n w_i^2 &\leq c\sigma^2 \Big(1+\sqrt{\frac{1}{cn} \log Cn}\Big) \\
 		&\leq 2 c \sigma^2

### 2013-11-01 tex/scam/experiments.tex
journal

--- 2013-09-30 tex/scam/icml14/experiments_icml.tex
@@
 indicating housing values in suburbs of Boston. The data and detailed description
-can be found on the UCI Machine Learning Repository website~\verb+http://archive.ics.uci.edu/ml/datasets/Housing+.
+can be found on the UCI Machine Learning Repository website~\footnote{\texttt{http://archive.ics.uci.edu/ml/datasets/Housing}}.
 
@@
 \hskip-20pt
-\includegraphics[width=.29\textwidth]{../figs/Curve1} &
+\includegraphics[width=.29\textwidth]{figs/Curve1} &
 \hskip-20pt
-\includegraphics[width=.29\textwidth]{../figs/Q} &
+\includegraphics[width=.29\textwidth]{figs/Q} &
 \hskip-20pt
-\includegraphics[width=.29\textwidth]{../figs/Curve2} &
+\includegraphics[width=.29\textwidth]{figs/Curve2} &
 \hskip-20pt
-\includegraphics[width=.29\textwidth]{../figs/Curve3}  \\
+\includegraphics[width=.29\textwidth]{figs/Curve3}  \\
 \hskip-10pt (a) additive model & 
@@
 \hskip-10pt
-  \includegraphics[width=.35\textwidth]{../figs/Additive} &
+  \includegraphics[width=.35\textwidth]{figs/Additive} &
 \hskip-25pt
-  \includegraphics[width=.35\textwidth]{../figs/Additive1} &
+  \includegraphics[width=.35\textwidth]{figs/Additive1} &
 \hskip-25pt
-  \includegraphics[width=.35\textwidth]{../figs/LASSO} 
+  \includegraphics[width=.35\textwidth]{figs/LASSO} 
 \\
@@
 \begin{tabular}{cc}
-  \includegraphics[width=.37\textwidth]{../figs/MSE} &
-  \includegraphics[width=.43\textwidth]{../figs/Convex}
+  \includegraphics[width=.37\textwidth]{figs/MSE} &
+  \includegraphics[width=.43\textwidth]{figs/Convex}
 \\
@@
 \end{figure*}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2013-11-01 tex/scam/icml14/additive_faithful_icml.tex
updated proof of additive faithfulness
journal

@@
 $X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
-integrable function and suppose, without loss of generality, that $\E f(X) = 0$.
+integrable function.
 Let 
 \begin{equation}
-f^* \coloneqq \argmin_{f_1,\ldots, f_s} \Bigl\{ \E \bigl( f(X) -
-\sum_{k=1}^s f_k(X_k) \bigr)^2 \,:\, \E f_k(X_k) = 0\Bigr\}.
+\begin{split}
+f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ \E \bigl( f(X) & -
+ \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \\
+       & \,:\, \E f_k(X_k) = 0\Bigr\}.
+\end{split}
 \end{equation}
-Then $f^*_k(x_k) = \E[ f(X) \given x_k]$ is unique.
+Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
 \end{lemma}
@@
 \begin{equation}
-f^* \coloneqq \argmin_{f_1,\ldots, f_s} \Bigl\{ \E ( f(X) - \sum_{k=1}^s
-f_k(X_k) )^2 \,:\, \E f_k(X_k) = 0 \Bigr\}.
+\begin{split}
+f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
+             \E ( f(X) &- \sum_{k=1}^s f_k(X_k) -\mu )^2 \\
+         &\,:\, \E f_k(X_k) = 0 \Bigr\}.
+\end{split}
 \end{equation}

### 2013-11-01 tex/scam/icml14/introduction_icml.tex
journal

@@
 
-The general sparse nonparametric regression problem is considered in
-\cite{lafferty2008rodeo}, where it is shown that computationally
-efficient, near minimax-optimal estimation is possible, but in ambient
-dimensions that scale only as $p = O(\log n)$.  This is in stark
-contrast to the exponential scaling $p = O\bigl(e^{n^c}\bigr)$ enjoyed
-by sparse linear models \cite{Wain:09a}.  Sparse additive models
-\cite{Ravikumar:09} provide a practical alternative to fully
+The general sparse nonparametric regression problem is considered in \cite{lafferty2008rodeo}, where it is shown that computationally efficient, near minimax-optimal estimation is possible, but in ambient
+dimensions that scale only as $p = O(\log n)$ instead of $p=O\bigl(e^{n^c}\bigr)$ as enjoyed by sparse linear models.
+\citet{dalalyan:12} do achieve exponential scaling $p=O(e^n)$ under certain Fourier smoothness conditions but they show that variable selection is still hard in that the number of relevant variables $s$ must be less than $\log n$.
+
+% The general sparse nonparametric regression problem is considered in
+% \cite{lafferty2008rodeo}, where it is shown that computationally
+% efficient, near minimax-optimal estimation is possible, but in ambient
+% dimensions that scale only as $p = O(\log n)$.  This is in stark
+% contrast to the exponential scaling $p = O\bigl(e^{n^c}\bigr)$ enjoyed
+% by sparse linear models \cite{Wain:09a}.
+
+Approximating the regression function by a sum of one-dimensional functions, known as sparse additive models, \cite{Ravikumar:09} is a practical alternative to fully
 nonparametric function estimation.  But the additive assumption is
@@
 Remarkably, the additional assumption of convexity does lead to
-additive faithfulness, as we show here.  In addition, we show that
-exponential scaling is achievable for sparse convex additive models.
-Thus, the geometric convexity constraint is quite different from the
+consistent variable selection, as we show here. In addition, we show that
+the scaling $p = O(\log n)$ and $n = O\big(\textrm{poly}(s)\big)$ is achievable for sparse convex additive models. Thus, the geometric convexity constraint is quite different from the
 smoothness constraints imposed in traditional nonparametric
@@
 concave utility functions \cite{Pratt:68}.  See \cite{Lim:12} for
-other applications.  Beyond cases where the assumption of convexity is
+other applications.
+
+Beyond cases where the assumption of convexity is
 natural, we offer that the convexity assumption is attractive as a
@@
 \def\mathbf#1{\mbox{\boldmath $#1$}}
-
-\textbf{Notation.} If
-$\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
-vector with the $k$-th coordinate removed. If $\mathbf{v} \in \R^n$, then
-$v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
-magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
-is the all ones vector. If $X \in \R^p$ and $S \subset
-\{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
-the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
-$\bar{X}$ to denote the empirical average.

### 2013-11-01 tex/scam/icml14/optimization_icml.tex
appendix update
journal

@@
           Y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
-                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
+                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \mu + \epsilon_{i} \quad i=1,2,\cdots,n
 \end{equation}
@@
 response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
-functions $f_{k}(\cdot)$ in each variable dimension.  
+functions $f_{k}(\cdot)$ in each variable dimension and a scalar offset $\mu$.  
 We impose an additional constraint that each $f_{k}(\cdot)$ is 
@@
 \subsection{Alternative Formulation}
-Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives. The alternative formulation replaces the ordering
+Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives, a form which we analyze in our theoretical analysis. The alternative formulation replaces the ordering
 constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity

### 2013-11-01 tex/scam/icml14/sparsistency_icml.tex
fixed url of uci
appendix fixed
journal

@@
   $f_0(X) = f_0(X_S)$.
-\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
+\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E\Big(f_0(X) -\E f_0(X) - \sum_{k=1}^s f_k(X_k)\Big)^2 \,|\, \E[f_k(X_k)] = 0 \}$.
 \end{packed_enum}
@@
 \item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
-  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
-\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq \E e^{\sigma^2 t^2 / 2}$.
+  twice-differentiable, and $L$-Lipschitz.
+\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
 \item[A4:] For all $k=1,...,s$, $\E(f^*_s(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
@@
 
-We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
+We will use assumptions A1, A2, A3 to control the probability of false
+positives and the stronger assumptions A1', A2', A3, A4 to control the
+probability of false negatives.  Assumption A4 can be
+weakened so that the relevant functions satisfy
+$\E(f^*_s(X_k))^2 \geq \alpha_n$ for $\alpha_n$ decaying to zero 
+at an appropriate rate.
 
@@
 Under A4, the population risk of an additive function with $s-1$ components is at least $\alpha$ larger than the population risk of the optimal additive function with $s$ components.
-Lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
+See lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
 \end{remark}
@@
 Let $c,C$ be absolute constants.
-Suppose $s L \lambda_n \rightarrow 0$ and $bL (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow 0$.
+Suppose $s L \lambda_n \rightarrow 0$ and $Lb(sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.
 Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
@@
 
+\citet{dalalyan:12} have shown that under tradtional smoothness constraints, variable selection is achievable only if $n > O(e^s)$.
+It is interesting to observe that because of additive faithfulness, the convexity assumption enables a much better scaling of $n = O(\textrm{poly}(s))$, demonstrating that geometric constraints can be quite different from the previously studied smoothness conditions.
+
 %\textbf{Comparison with Related Work.}

### 2013-11-05 tex/scam/additive_faithful.tex
massive journal edit

@@
 changes the behavior of the additive approximation. We begin
-with a lemma that implies uniqueness of the additive regression function.
+with a lemma that characterizes the components of the additive approximation under mild conditions.
+
+% OLD lemma, requires product distribution
+% \begin{lemma}
+% \label{lem:general_int_reduction}
+% Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let
+% $X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
+% integrable function.
+% Let 
+% \begin{equation}
+% f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ \E \bigl( f(X)  -
+%  \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 
+%         \,:\, \E f_k(X_k) = 0\Bigr\}.
+% \end{equation}
+% Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
+% \end{lemma}
+
+\begin{lemma}
+\label{lem:general_int_reduction}
+Let $F$ be a distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
+
+Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq 
+\arg\min \{ \E \big( f(X) - \sum_{k=1}^s f_k(X_k) - \mu \big)^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
+
+Then 
+$$ f^*_k(x_k) = \E[ f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) \given x_k] - \E f(X) $$
+ and $\mu^* = \E f(X)$ and this solution is unique.
+\end{lemma}
+
+Lemma~\ref{lem:general_int_reduction} follows from the stationarity
+conditions of the optimal solution.
+
+\begin{proof}
+Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
+
+We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
+This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.
+Uniqueness is apparent because the second derivative is strictly larger than 0 and strong convexity is guaranteed.
+
+We now turn our attention toward the $f^*_k$'s.
+
+It must be that $f^*_k$ minimizes $\Big\{ \E \big( f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k) \big)^2 \,:\, \E f_k(X_k) = 0 \Big\}$.
+
+Fix $x_k$, we will show that the value 
+$\E[ f(X) - \sum_{k' \neq k} f_{k'}(X_{k'}) \given x_k] - \mu^*$, for all $x_k$,  
+uniquely minimizes 
+\[
+\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+         \Big( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\Big)^2 
+                 d \mathbf{x}_{-k}.
+\]
+It easily follows then that the function $x_k \mapsto \E[ f(X) - \sum_{k'} f_{k'} (X_{k'}) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.We focus our attention on $f^*_K$, and fix $x_k$.
+
+The first-order optimality condition gives us:
+
+\begin{align*}
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
+  \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+      ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
+p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
+     p(\mathbf{x}_{-k} \given x_k ) 
+     ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
+              d \mathbf{x}_{-k} \\
+f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
+       p(\mathbf{x}_{-k} \given x_k ) 
+     (f(\mathbf{x}) - \sum_{k'\neq k} f_{k'} (x_{k'})  -\mu^*) d \mathbf{x}_{-k} 
+ \end{align*}
+
+The square error objective is strongly convex.
+The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
+Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.
+
+Now, we note that as a function of $x_k$, $\E[ f(X) -\sum_{k'\neq k} f_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
+\end{proof}
+
+In the case that the distribution in Lemma~\ref{lem:general_int_reduction} is a product distribution, we get particularly clean expressions for the additive components.
+
+\begin{corollary}
+\label{cor:product_int_reduction}
+Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let $\mu^*, f^*_k(x_k)$ be defined as in Lemma~\ref{lem:general_int_reduction}.
+Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
+\end{corollary}
+
+If $F$ is the uniform distribution,
+then $f^*_k(x_k) = \int f(x_k, \mathbf{x}_{-k})
+d\mathbf{x}_{-k}$.
+
+\begin{example} Using Corollary~\ref{cor:product_int_reduction}, we give two examples of \emph{additive unfaithfulness} under
+  the uniform distribution, that is, examples where relevant variables are erroneously marked as irrelevant under an additive approximation. First, consider the following function:
+\[
+\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)
+\]
+defined for $(x_1, x_2) \in [0,1]^2$.  Then
+$\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
+$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
+would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
+\[
+\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2
+\]
+defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
+$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation.
+This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
+\end{example}
 
@@
 
-\begin{lemma}
-\label{lem:general_int_reduction}
-Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let
-$X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
-integrable function.
-Let 
-\begin{equation}
-\begin{split}
-f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ \E \bigl( f(X) & -
- \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \\
-       & \,:\, \E f_k(X_k) = 0\Bigr\}.
-\end{split}
-\end{equation}
-Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
-\end{lemma}
-
-Lemma~\ref{lem:general_int_reduction} follows from the stationarity
-conditions of the optimal solution. If $F$ is the uniform distribution,
-then $f^*_k(x_k) = \int f(x_k, \mathbf{x}_{-k})
-d\mathbf{x}_{-k}$.
-
-\begin{example} We give two examples of additive unfaithfulness under
-  the uniform distribution. First, consider the following function:
-\[
-\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)
-\]
-defined for $(x_1, x_2) \in [0,1]^2$.  Then
-$\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
-$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
-would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
-\[
-\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2
-\]
-defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
-$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation.
-This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
-\end{example}
-
 In order to exploit additive models, it is important to understand when the
 additive approximation accurately captures all of the relevant variables.
-We call this property \emph{additive faithfulness}.
+We call this property \textbf{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{depends on} a coordinate $x_k$.
 
 \begin{definition}
-  Let $\mathbf{C}=[0,1]^s$, and $f:\mathbf{C}\rightarrow \R$. We say
-  that $f$ \emph{depends on} coordinate $k$ if there exist $x'_k \neq
-  x_k$ such that $f(x'_k, \mathbf{x}_{-k})$ and $f(x_k,
-  \mathbf{x}_{-k})$ are different functions of $\mathbf{x}_{-k}$.
+  Let $F$ be a distribution on $\mathbf{C}=[0,1]^s$, and $f:\mathbf{C}\rightarrow \R$.
 
-Let $F$ be a probability distribution on $\mathbf{C}$ and
-assume without loss of generality that $\E f(X) = 0$. Let 
+We say that $f$ \textbf{depends on} coordinate $k$ if, for all $x_k \in [0,1]$, the set 
+$\big\{ x'_k \in [0, 1] \,:\, f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k}) 
+\trm{ for almost all  $\mathbf{x}_{-k}$} \big\}$ 
+has measure strictly less than 1.\\
+
+Suppose we have the additive approximation:
 \begin{equation}
-\begin{split}
 f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
-             \E ( f(X) &- \sum_{k=1}^s f_k(X_k) -\mu )^2 \\
-         &\,:\, \E f_k(X_k) = 0 \Bigr\}.
-\end{split}
+             \E ( f(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 
+         \,:\, \E f_k(X_k) = 0 \Bigr\}.
 \end{equation}
-We say that $f$ is \emph{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
+We say that $f$ has \textbf{additive recall} under $F$ if $f^*_k = 0 \Rightarrow \trm{$f$ does not depend on coordinate $k$}$.
+
+We say that $f$ is \textbf{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
 \end{definition}
@@
 
-Remarkably, under product distributions, a convex multivariate function can always be faithfully approximated by an additive function.
+Additive faithfulness is an attractive property because it implies that, in the population setting, the additive approximation yields consistent variable selection.
+Additive recall is a weaker condition but still useful: we can be sure that the additive approximation is conservative, that it does not exclude important variables.
+
+Remarkably, under a general class of distributions which we characterize below, convex multivariate functions has additive recall and under product distributions, convex functions are additively faithful.
+
+\begin{definition}
+Given a conditional density $p(\mathbf{x}_{-j} \given x_j)$, we say that $\mathbf{X}_{-j}$ is \textbf{intermittently independent} of $X_j$ if the set of $x_j$ for which $\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j} = 0$ for all $\mathbf{x}_{-j}$ is either the whole line $[0,1]$, or a collection of at least two disjoint closed intervals.
+
+Let $F$ be a distribution on $[0,1]^s$.
+We say that $F$ is an \textbf{intermittently independent} distribution if $F$ has a non-zero density $p$ with the property that, for all $j=1,...,s$, $\mathbf{X}_{-j}$ is intermittently independent of $X_j$.
+\end{definition}
+
+\begin{example} There are many examples of distributions which satisfy intermittent independence:
+\begin{packed_enum}
+\item $F$ is a product distribution.
+\item $F$ has a density $p$ that is piece-wise constant on a gridding of $[0,1]^s$.
+\item $F$ has a density $p$ that is, for some $\frac{1}{2} > \epsilon > 0$,  arbitrary on $(\epsilon, 1-\epsilon)^s$ but constant elsewhere. 
+\end{packed_enum}
+\end{example}
+
+\begin{theorem}
+\label{thm:convex_recall}
+Let $F$ be an \textbf{intermittently independent} distribution supported on $C=[0,1]^s$ with positive density $p$.
+If $f$ is convex and twice differentiable, then $f$ has the \emph{additive recall} property under $F$.
+\end{theorem}
 
@@
 \label{thm:convex_faithful}
-Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p$. If $f$ is convex and twice differentiable, then $f$ is additively faithful under $F$.
+Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p$. If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $F$.
 \end{theorem}
 
-We give the full proof in Section~\ref{sec:faithful_proof} of the
-Appendix, but pause here to provide some intuition. From
-Lemma~\ref{lem:general_int_reduction}, we know that the
+% We give the full proof in Section~\ref{sec:faithful_proof} of the
+% Appendix, but pause here to provide some intuition.
+
+In the case of Theorem~\ref{thm:convex_faithful}, we can give some intuition: Lemma~\ref{lem:general_int_reduction}, we know that the
 additive approximation zeroes out $k$ when, fixing $x_k$, every
@@
 still maintaining convexity.
+
+We give the proof of Theorem~\ref{thm:convex_recall}, which also proves one direction of Theorem~\ref{thm:convex_faithful}. The other direction of Theorem~\ref{thm:convex_faithful} is trivial to show.
+
+\begin{proof} (of Theorem~\ref{thm:convex_recall})\\
+Fix $k$.
+Using the result of Lemma~\ref{lem:general_int_reduction}, we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ implies that $f$ does not depend on coordinate $k$.\\
+
+By assumption, we know that there exist at least two disjoint closed intervals $R_0, R_1$ where $p(\mathbf{x}_{-k} \given x_k)$ is independent on $x_k$.
+That is, there exist density functions $\phi_0(\mathbf{x}_{-k})$ and $\phi_1(\mathbf{x}_{-k})$ such that $p(\mathbf{x}_{-k} \given x_k) = \phi_0(\mathbf{x}_{-k})$ for all $x_k \in R_0$ and $p(\mathbf{x}_{-k} \given x_k) = \phi_1(\mathbf{x}_{-k})$ for all $x_k \in R_1$.
+
+Let $x^0_k$ be an interior point of $R_0$.
+
+For every $\mathbf{x}_{-k}$, we define $g$ as the derivative of $f$ with respect to $x_k$ at the point $(\mathbf{x}_{-k}, x^0_k)$.
+\[
+g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow x^0_k} 
+     \frac{f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k})}{x_k - x^0_k}
+\]
+$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
+
+Now, we use $r(\mathbf{x}_{-k})$ as a short-hand for $\sum_{k'\neq k} f_{k'}(x_{k'})$ and derive that for all $x_k \in R_0$, we have:
+\begin{align*} 
+& \int_{\mathbf{x}_{-k}}  \phi_0(\mathbf{x}_{-k}) 
+   \Big( f(x_k, \mathbf{x}_{-k}) - f(x_k^0, \mathbf{x}_{-k}) \Big) d\mathbf{x}_{-k} \\
+ &= \int_{\mathbf{x}_{-k}}  \phi_0(\mathbf{x}_{-k})
+   \Big( \big(f(x_k, \mathbf{x}_{-k}) - r(\mathbf{x}_{-k}) - \mu^* \big) - 
+         \big(f(x^0_k, \mathbf{x}_{-k}) - r(\mathbf{x}_{-k}) - \mu^* \big) \Big)
+     d \mathbf{x}_{-k} \\
+ &= 0
+\end{align*}
+
+Since $x^0_k$ is in the interior of $R_0$, we use the bounded convergence theorem and conclude that $\int_{\mathbf{x}_{-k}} \phi_0( \mathbf{x}_{-k}) g(\mathbf{x}_{-k}) = 0$ as well.
+
+We now note that $g(\mathbf{x}_{-k})$ is a component of the subgradient 
+$\partial_{\mathbf{x}} f(x^0_k, \mathbf{x}_{-k})$.
+
+Therefore, the first-order characterization of convex functions gives us that
+\begin{align*}
+f(x_k, \mathbf{x}_{-k}) \geq f(x^0_k, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) (x_k - x^0_k)
+   \quad \trm{for all } x_k, \mathbf{x}_{-k}
+\end{align*}
+
+Or, equivalently, for all $x_k, \mathbf{x}_{-k}$, 
+\[
+f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) (x_k-x^0_k) \geq 0
+\]
+
+Now, for all $x_k \in R_0$, 
+\[
+\int_{\mathbf{x}_{-k}} \phi_0(\mathbf{x}_{-k}) 
+     \Big(f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k}) 
+     - g(\mathbf{x}_{-k}) (x_k - x^0_k) \Big) d\mathbf{x}_{-k} = 0
+\]
+Since $\phi_0$ is positive by assumption, we conclude that for all $x_k \in R_0$, for all $\mathbf{x}_{-k}$, 
+$$
+f(x_k, \mathbf{x}_{-k}) = f(x^0_k, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) (x_k - x^0_k)
+$$
+
+The Hessian of $f$ at $(x_k, \mathbf{x}_{-k})$ for $x_k \in R$ then has a zero at the $k$-th main diagonal entry.
+A positive semidefinite matrix with a zero on the $k$-th main diagonal entry must have only zeros on the $k$-th row and column \footnote{ See proposition 7.1.10 of \citet{HJ90}}, which means that $g(\mathbf{x}_{-k})$ must be a constant function.
+Since $g$ integrates to 0 under $\phi_0(\mathbf{x}_{-k})$, it must be 0.\\
+
+Thus, $f(x_k, \mathbf{x}_{-k}) = f(x^0_k, \mathbf{x}_{-k})$ for all $x_k \in R_0$ and for all $\mathbf{x}_{-k}$.\\
+
+We can go through the same reasoning for $R_1$  and get that $f(x_k, \mathbf{x}_{-k})$ is a constant function of $x_k$ for all $x_k \in R_1$, that is, $f(x_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})$ for all $x_k \in R_1$ for some interior point $x^1_k$ of $R_1$.
+
+However, if $f(x_k, \mathbf{x}_{-k})$, as an one-dimensional convex function of $x_k$, is constant on two disjoint closed intervals, it must be constant for all $x_k \in [0,1]$.
+Therefore, for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a constant as a function of $x_k$ and $f$ does not depend on $x_k$.
+
+\end{proof}
 
@@
   We assume twice differentiability in
-  Theorem~\ref{thm:convex_faithful} to simplify the proof. We believe
+  Theorems~\ref{thm:convex_faithful} and~\ref{thm:convex_recall} to simplify the proof. 
+  We believe
   this smoothness condition is not necessary because every non-smooth
@@
 \end{remark}
-\begin{remark}
-Without restrictions on the distribution, a convex
-  function may not be additively faithful. Intuitively, an arbitrarily shaped
-  density $p$
-  may ``undo'' the convexity of $f$ so that the product
-  $p(\mathbf{x}) \, f(\mathbf{x})$ resembles an egg carton or a
-  tilting slope.  With appropriate conditions on the density $p$,
-  however, it is possible to relax the independence assumption.  We leave this to
-  future work.
-\end{remark}
+
+% \begin{remark}
+% Without restrictions on the distribution, a convex
+%   function may not be additively faithful. Intuitively, an arbitrarily shaped
+%   density $p$
+%   may ``undo'' the convexity of $f$ so that the product
+%   $p(\mathbf{x}) \, f(\mathbf{x})$ resembles an egg carton or a
+%   tilting slope.  With appropriate conditions on the density $p$,
+%   however, it is possible to relax the independence assumption.  We leave this to
+%   future work.
+% \end{remark}
 

### 2013-11-05 tex/scam/appendix.tex
massive journal edit

@@
 
-\subsection{Proof of Additive Faithfulness}
-\label{sec:faithful_proof}
+% \subsection{Proof of Additive Faithfulness}
+% \label{sec:faithful_proof}
 
-We start with a proof of Lemma~\ref{lem:general_int_reduction}. We restate the lemma here for convenience.
+% We start with a proof of Lemma~\ref{lem:general_int_reduction}. We restate the lemma here for convenience.
 
-\begin{lemma}
-Let $F$ be a product distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
+% \begin{lemma}
+% Let $F$ be a product distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
 
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
+% Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
 
-Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
-\end{lemma}
+% Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
+% \end{lemma}
 
- \begin{proof}
+%  \begin{proof}
 
-Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
+% Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
 
-We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
+% We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
 This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.
@@
 
-We now turn our attention toward the $f^*_k$'s.
+% We now turn our attention toward the $f^*_k$'s.
 
-It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
+% It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
 
-Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
-\[
-\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
-         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\big|^2 
-                 d \mathbf{x}_{-k}.
-\]
-It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.
+% Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
+% \[
+% \min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+%          \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\big|^2 
+%                  d \mathbf{x}_{-k}.
+% \]
+% It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.
 
-Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
-\begin{align*}
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
-  \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
-      ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
-p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
-     p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
-              d \mathbf{x}_{-k} \\
-f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
-       p(\mathbf{x}_{-k}) (f(\mathbf{x}) -\mu^*) d \mathbf{x}_{-k} 
- \end{align*}
-Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption.
+% Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
+% \begin{align*}
+% \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
+%   \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
+%       ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
+% p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
+%      p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
+%               d \mathbf{x}_{-k} \\
+% f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
+%        p(\mathbf{x}_{-k}) (f(\mathbf{x}) -\mu^*) d \mathbf{x}_{-k} 
+%  \end{align*}
+% Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption.
 The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.
 
-The square error objective is strongly convex.
+% The square error objective is strongly convex.
 The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
@@
 
-Now, we note that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
+% Now, we note that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
 
- \end{proof}
+%  \end{proof}
 
-Our reasoning actually proves something stronger. It proves the following lemma:
+% Our reasoning actually proves something stronger. It proves the following lemma:
 
-\begin{lemma}
-\label{lem:additive_component}
+% \begin{lemma}
+% \label{lem:additive_component}
 
-$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
-\[
-min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
-                    \,:\, \E f_k(X_k) = 0 \}
-\]
-for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
-\end{lemma}
+% $f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
+% \[
+% min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
+%                     \,:\, \E f_k(X_k) = 0 \}
+% \]
+% for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
+% \end{lemma}
 
-The next lemma adapts Lemma~\ref{lem:general_int_reduction} to convex functions.
+% The next lemma adapts Lemma~\ref{lem:general_int_reduction} to convex functions.
 
-\begin{lemma}
-\label{lem:int_reduction}
-Let $F$ be a product distribution on $C=[0,1]^s$ with positive density function $p$. Let $f: C \rightarrow \R$ be a convex function.
+% \begin{lemma}
+% \label{lem:int_reduction}
+% Let $F$ be a product distribution on $C=[0,1]^s$ with positive density function $p$. Let $f: C \rightarrow \R$ be a convex function.
 
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
+% Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
 
-Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
-\end{lemma}
+% Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
+% \end{lemma}
 
-\begin{proof}
-The proof is identical to that of Lemma~\ref{lem:general_int_reduction}. We need only verify that $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ is convex.
+% \begin{proof}
+% The proof is identical to that of Lemma~\ref{lem:general_int_reduction}. We need only verify that $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ is convex.
 
-This is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
-\end{proof}
+% This is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
+% \end{proof}
 
- The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.
+%  The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.
 
-\begin{proposition}
-\label{prop:faithful_condition}
-Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
+% \begin{proposition}
+% \label{prop:faithful_condition}
+% Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
 
-Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
+% Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
 
-The following are equivalent:
-\begin{packed_enum}
-\item $f$ does not depends on coordinate $k$
-\item For all $x_k$, $\E[ f(X) | x_k] = \E f(X) $.
-\end{packed_enum}
-\end{proposition}
+% The following are equivalent:
+% \begin{packed_enum}
+% \item $f$ does not depends on coordinate $k$
+% \item For all $x_k$, $\E[ f(X) | x_k] = \E f(X) $.
+% \end{packed_enum}
+% \end{proposition}
 
-\begin{proof}
+% \begin{proof}
 
-The first condition trivially implies the second.
+% The first condition trivially implies the second.
 
-Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = \E f(X)$.
+% Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = \E f(X)$.
 
-Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
-\begin{align*}
- \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
-\end{align*}
+% Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
+% \begin{align*}
+%  \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
+% \end{align*}
 
-For every $\mathbf{x}_{-k}$, we define the derivative
-\[
-g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
-\]
-$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
+% For every $\mathbf{x}_{-k}$, we define the derivative
+% \[
+% g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
+% \]
+% $g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
 
-We now describe two facts about $g$.
+% We now describe two facts about $g$.
 
-Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
-\[
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
-\]
+% Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
+% \[
+% \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
+% \]
 
-Fact 2.
+% Fact 2.
 Because $f$ is convex, $g(\mathbf{x}_{-k})$ is a component of the subgradient $\partial_{\mathbf{x}} f(0, \mathbf{x}_{-k})$.
@@
 
-Therefore, using the first order characterization of a convex function, we have
-\begin{align*}
-f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
-f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
-\end{align*}
+% Therefore, using the first order characterization of a convex function, we have
+% \begin{align*}
+% f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
+% f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
+% \end{align*}
 
-For all $x_k, \mathbf{x}_{-k}$, 
-\[
-f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
-\]
-and
-\[
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
-\]
-Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
+% For all $x_k, \mathbf{x}_{-k}$, 
+% \[
+% f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
+% \]
+% and
+% \[
+% \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
+% \]
+% Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
 
-The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.
+% The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.
 
-By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero.
+% By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero.
 (to prove this, one can first work with a 2 by 2 matrix and then use the fact that every principal submatrix of a PSD matrix must be PSD)
 
-Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function.
+% Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function.
 It follows therefore that $g = 0$ because it integrates to 0.
 
-So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.
+% So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.
 
-\end{proof}
+% \end{proof}
 
@@
 %%% mode:latex ***
-%%% TeX-master: "icml14/scam_icml.tex" ***
+%%% TeX-master: "paper.tex" ***
 %%% End: ***

### 2013-11-05 tex/scam/optimization.tex
massive journal edit

@@
 
-We consider the following nonparametric regression problem
+We now consider the following nonparametric regression problem
 \begin{equation}\nonumber
-          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
-                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
+          Y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
+                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \mu + \epsilon_{i} \quad i=1,2,\cdots,n
 \end{equation}
-where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
+where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $Y_{i}$ is the
 response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
-functions $f_{k}(\cdot)$ in each variable dimension.  
+functions $f_{k}(\cdot)$ in each variable dimension and a scalar offset $\mu$.  
 We impose an additional constraint that each $f_{k}(\cdot)$ is 
-an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
+a univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
 \begin{equation}\label{hyper}
@@
 program:
-\begin{equation}\begin{split}\label{np}
-       &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
-                     \Bigl( y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
+\begin{equation}
+\begin{split}
+       \min_{\bds{h},\bds{\beta},\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
+                     \Bigl( Y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
                          + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
-       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), 
-                                 \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
-\end{split}\end{equation}
-Where $\mu \in \R$ is a mean parameter introduced because $f$ may not have zero-mean, and where $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+       \textrm{subject to} &\;\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \\
+                     & \;\; \sum_{i=1}^{n}h_{ki}=0,\\
+                     & \;\; \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
+\end{split}
+\label{np}
+\end{equation}
+Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$. We can solve for $\mu$ explicitly, as  
+$\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ which follows from the
+KKT conditions
+and the constraints $\sum_i h_{ki} = 0$.
 It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
 \begin{align*}
-  \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = 
-            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = 
-            \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
-      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \forall j<i, &h_{k(j)}-h_{k(i)} =
-                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = 
-                \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
-     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
+  \forall & j\geq{}i, \; h_{k(j)}-h_{k(i)}  = 
+            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) \\
+      & = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})
+       \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) \\
+      & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
+  \forall & j<i,\;  h_{k(j)}-h_{k(i)} =
+                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) \\
+     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) 
+     \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)})  \\
+     &= \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
 \end{align*}
@@
 
-The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints.
-The optimal $\mu$ has a closed form solution of $\mu = \frac{1}{n}\sum_{i=1}^n Y_i$, which is easy to derive from the KKT theorem and the constraints that $\sum_i h_{ki} = 0$ for all $k$.
-Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
-in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
-where in each step we solve the following QP subproblem for
-$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
-\begin{equation}\begin{split}\nonumber
-       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
-                       \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri}-\mu)-h_{ki}\Bigr)^{2} 
+The SCAM optimization in (\ref{np}) is a quadratic program (QP) with
+$O(np)$ variables and $O(np)$ constraints. 
+Directly applying a QP solver for $\bds{h},
+\bds{\beta}$ would be computationally expensive for relatively large
+$n$ and $p$. However, notice that variables in different feature
+dimensions are only coupled in the term
+$(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block
+coordinate descent method, where in each step we solve the following
+QP subproblem for $\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the
+other variables fixed:
+\begin{equation}
+\begin{split}\nonumber
+       \min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} &
+             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}
+                -\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} 
                       + \lambda\gamma_{k} \\
-        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
-\end{split}\end{equation}
+        \textrm{such that} & \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}),\\
+        &\ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k}\\
+        &\  \sum_{i=1}^{n}h_{ki}=0, \ (\forall i).
+\end{split}
+\end{equation}
 The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
@@
 It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(i)}$ and 
-\[
-f_k(x_{k(i)}) = f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)}
-- x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
-\]
-Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
-$\Delta(j,x_{ki})= x_{ki} -
-x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
-$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
-$n-1$ dimensional vector.
-Then $f_k(x_{ki}) = \Delta(x_{ki})^\tran d_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$.
-Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$.
-Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
+\begin{equation}
+\begin{split}
+f_k(x_{k(i)}) = & f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)} \\
+& - x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots  \\
+& + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
+\end{split}
+\end{equation}
+We can write this more compactly in matrix notations. First define $\Delta_{k(j)}(x_{ki}) = \max( x_{ki} - x_{k(j)}, 0)$.
+
+\begin{equation*}
+\begin{split}
+&(f_k(x_{k1}) ,..., f_k(x_{kn}))^\tran = \Delta_k d_k \coloneqq \\
+\vspace{0.1in}
+&\left[ \begin{array}{ccc}
+    \Delta_{k(1)}(x_{k1}) & ... & \Delta_{k(n-1)}(x_{k1}) \\
+    ... & & \\
+    \Delta_{k(1)}(x_{kn}) & ... & \Delta_{k(n-1)}(x_{kn}) 
+\end{array} \right]
+\left[ \begin{array}{c}
+    d_{k(1)} \\
+    ... \\
+    d_{k(n-1)}
+\end{array} \right] 
+\end{split}
+\end{equation*}
+
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = \Delta_{k(j)}(x_{ki})$ and $d_k = (d_{k(1)} ,..., d_{k(n-1)})$.
+We can now reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
 \begin{align}
-\min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
-               \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) -\mu \Bigr\|_2^2 
-               + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
-\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
-	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
+\min_{d_k, c_k}& \frac{1}{2n} 
+       \Bigl\| Y - \bar{Y}\mathbf{1}_n - \sum_{k=1}^p 
+             ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 
+               + \lambda_n \sum_{k=1}^p \|d_k\|_1   \label{opt:alternate_opt} \\
+\trm{s.t. }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0  	
+               \qquad \trm{(convexity)} \nonumber \\ 
+	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	
+               \qquad \trm{(centering)} \nonumber 
 \end{align}
-$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.
+$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 4\|\bds{\beta}_{k\cdot}\|_{\infty}$.
 
@@
 \end{remark}
+
+\subsection{Convex + Concave Functions}
+
+Although convex regression enjoys good properties from both statistical and optimization perspective, convexity can be too strong of a shape constraint for some nonparametric regression problems.
+We can in fact significantly relax the shape constraint in the same optimization framework by learning a regression function $f$ that is a sum of a convex and a concave functions.
+That is, there exist a convex function $g$ and a concave function $h$ such that $f = g + h$.
+
+To learn a convex-plus-concave function, we need only modify the objective in optimization~\ref{np} to be
+\[
+\min_{h, g, \bds{\beta}, \bds{\theta}, \mu} 
+   \frac{1}{2n}\sum_{i=1}^{n}
+                     \Bigl( Y_{i}-\sum_{k=1}^{p} (h_{ki} + g_{ki}) - \mu \Bigr)^{2} 
+                         + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} 
+                         + \lambda\sum_{k=1}^{p}\|\bds{\theta}_{k\cdot}\|_{\infty}
+\]
+and add linear constraints to enforce the concavity of the $g_k$'s with $\bds{\theta}$ representing the secants of $g_k$.
+The optimization is still convex and efficient; the runtime is on the same order as that of convex additive regression.
+
+Convex-plus-concavity is a much less stringent condition than convexity; as shown in Figure~\ref{fig:concavex}, it encompasses a variety of interestingly shaped functions.
+And because convex-plus-concave functions can be efficiently fitted without the need to tune a smoothing parameter, it is an attract alternative to the traditional smoothing kernel approach in nonparametric regression.
+
+Convex-plus-concave functions unfortunately do not inherit equally good additive faithfulness properties; the tilting slope example $f(x_1, x_2) = x_1 x_2 = \frac{1}{2}(x_1 + x_2)^2 - \frac{1}{2}(x_1^2 + x_2^2)$ is a concave-plus-convex function.
+
+\begin{figure}[htp]
+\subfigure[$|x| - (x-0.1)^2$]{
+   \centering
+   {\includegraphics[width=0.3\textwidth]{concavex1.pdf}}
+}
+\subfigure[$0.5(x-0.3)^4 - x^2$]{
+   \centering
+   {\includegraphics[width=0.3\textwidth]{concavex2.pdf}}
+}
+\subfigure[$0.5 x^2 + 1 - x^4$]{
+   \centering
+   {\includegraphics[width=0.3\textwidth]{concavex3.pdf}}
+}
+\caption{Examples of one-dimensional concave-plus-convex functions.}
+\label{fig:concavex}
+\end{figure}
+
+% examples of convex + concave functions
+% no additive faithfulness
+% same optimization procedure.
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2013-11-05 tex/scam/paper.tex
minor edits
journal
massive journal edit

--- 2013-09-30 tex/scam/icml14/paper.tex
@@
 \documentclass{article}
-\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,caption,subcaption,sidecap,custom_math}
+\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
 \usepackage[hscale=0.7,vscale=0.8]{geometry}
 
-\bibliographystyle{plain}
+\usepackage{subfigure}
+\usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{authblk}
+
+\bibliographystyle{plainnat}
 
@@
 
-\author{
-Min Xu, Minhua Chen, John Lafferty
-}
+%\author{
+%Min Xu, Minhua Chen, John Lafferty
+%}
+
+\author[1]{Min Xu}
+\author[2,3]{Minhua Chen}
+\author[2,3]{John Lafferty}
+
+\affil[1]{Machine Learning Department, Carnegie Mellon University}
+\affil[2]{Department of Statistics, University of Chicago}
+\affil[3]{Department of Computer Science, University of Chicago}
 
@@
 
+% \tableofcontents
+
 \input{introduction}
-%\input{related_work}
+\input{related_work}
 \input{summary}
@@
 
+%\bibliographystyle{plain}
 \bibliography{local}
@@
 \input{appendix}
+%\newpage
+%\input{notes}
 

### 2013-11-05 tex/scam/related_work.tex
massive journal edit

--- 2013-10-04 tex/scam/icml14/related_work_icml.tex
@@
 Variable selection in general nonparametric regression or function
-estimation is a notoriously difficult problem.  
-Nonparametric regression is subject to the curse
-of dimensionality,
-and may be inaccurate even in moderate dimensions,
-without any additional assumptions.  But if the function is sparse, depending
-on only a few covariates, there is hope that by identifying
-the relevant variables one can effectively reduce the 
-dimension, and  estimate the function at the
-corresponding faster statistical rate of convergence.
-
-\citet{lafferty2008rodeo} develop a greedy procedure for
+estimation is a notoriously difficult problem. \citet{lafferty2008rodeo} develop a greedy procedure for
 adjusting bandwidths in a local linear regression estimator,
@@
 as if the relevant variables were isolated in advance.
-But the method does not carry out explicit variable selection.
-Moreover, it only provably scales to dimensions $p$ that 
+But the method only provably scales to dimensions $p$ that 
 grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  Note that this
@@
 
-\citet{dalalyan:12} give
+\citet{dalalyan:12} show that the exponential scaling $p=O(\log n)$ is achievable if the underlying function is assumed to be smooth with respect to a Fourier basis. They also give
 support for the intrinsic difficulty of variable
@@
 
+\textbf{Notation.} If
+$\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
+vector with the $k$-th coordinate removed. If $\mathbf{v} \in \R^n$, then
+$v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
+magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
+is the all ones vector. If $X \in \R^p$ and $S \subset
+\{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
+the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
+$\bar{X}$ to denote the empirical average. Given a random variable $X_k$ and a scalar $x_k$, we use $\E[\cdot \given x_k]$ as a shorthand for $\E[ \cdot \given X_k = x_k]$.
+
 %* Laetitia Comminges, Arnak S. Dalalyan 

### 2013-11-12 tex/scam/additive_faithful.tex
more update

@@
 \trm{ for almost all  $\mathbf{x}_{-k}$} \big\}$ 
-has measure strictly less than 1.\\
+has probability strictly less than 1.\\
 
@@
 Additive recall is a weaker condition but still useful: we can be sure that the additive approximation is conservative, that it does not exclude important variables.
+
+\subsection{Additive Faithfulness of Convex Functions}
 
@@
 
-In the case of Theorem~\ref{thm:convex_faithful}, we can give some intuition: Lemma~\ref{lem:general_int_reduction}, we know that the
+We pause to give some intuition before we present the full proof: 
+suppose the underlying distribution is a product distribution for a second, 
+then we know from lemma~\ref{lem:general_int_reduction} that the
 additive approximation zeroes out $k$ when, fixing $x_k$, every
@@
 
-We give the proof of Theorem~\ref{thm:convex_recall}, which also proves one direction of Theorem~\ref{thm:convex_faithful}. The other direction of Theorem~\ref{thm:convex_faithful} is trivial to show.
+We give the proof of Theorem~\ref{thm:convex_recall}, which also proves one direction of Theorem~\ref{thm:convex_faithful}. The other direction of Theorem~\ref{thm:convex_faithful} is trivial.
 
@@
 
-By assumption, we know that there exist at least two disjoint closed intervals $R_0, R_1$ where $p(\mathbf{x}_{-k} \given x_k)$ is independent on $x_k$.
+Let us assume that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $.\\
+
+By the intermittent independence assumption, we know that there exists at least two disjoint closed intervals $R_0, R_1$ where $p(\mathbf{x}_{-k} \given x_k)$ is independent of $x_k$.
 That is, there exist density functions $\phi_0(\mathbf{x}_{-k})$ and $\phi_1(\mathbf{x}_{-k})$ such that $p(\mathbf{x}_{-k} \given x_k) = \phi_0(\mathbf{x}_{-k})$ for all $x_k \in R_0$ and $p(\mathbf{x}_{-k} \given x_k) = \phi_1(\mathbf{x}_{-k})$ for all $x_k \in R_1$.
@@
 
-Since $x^0_k$ is in the interior of $R_0$, we use the bounded convergence theorem and conclude that $\int_{\mathbf{x}_{-k}} \phi_0( \mathbf{x}_{-k}) g(\mathbf{x}_{-k}) = 0$ as well.
+The last equality follows because we assumed that $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ for all $x_k$. \\
+
+Since $x^0_k$ is in the interior of $R_0$, and since the domain of $f$ is a compact set, we use the bounded convergence theorem and conclude that $\int_{\mathbf{x}_{-k}} \phi_0( \mathbf{x}_{-k}) g(\mathbf{x}_{-k}) = 0$ as well.\\
 
@@
 
-Now, for all $x_k \in R_0$, 
+Now, the critical observation we make is that, for all $x_k \in R_0$, 
 \[
@@
 \]
-Since $\phi_0$ is positive by assumption, we conclude that for all $x_k \in R_0$, for all $\mathbf{x}_{-k}$, 
+Since $\phi_0$ is positive by assumption and the second term is non-negative, we conclude that the second term must be exactly zero, that is, for all $x_k \in R_0$, for all $\mathbf{x}_{-k}$, 
 $$

### 2013-11-12 tex/scam/appendix.tex
more update

@@
 Let us denote the components of $f^{*s} = \sum_{k=1}^s f_k^*$.
-We will now invoke Lemma~\ref{lem:additive_component}, which is valid because we assume $X_1,...,X_s$ are independent by assumption A1'.
-By Lemma~\ref{lem:additive_component}, if we set $f^*_k = 0$, the resulting additive function $\sum_{k'\neq k} f_{k'}^*$ minimizes the population risk subject to the constraint that $f_k = 0$.
+We will now invoke Corollary~\ref{cor:product_int_reduction}, which is valid because we assume $X_1,...,X_s$ are independent by assumption A1'.
+By Corollary~\ref{cor:product_int_reduction}, if we set $f^*_k = 0$, the resulting additive function $\sum_{k'\neq k} f_{k'}^*$ minimizes the population risk subject to the constraint that $f_k = 0$.
 By definition, $f^{*s}$ is $\argmin_k \sum_{k'\neq k} f_{k'}^*$ and thus share components with $f^{*s}$.
@@
 
-Where we used the fact that $\E f^*_{k'} (X_{k'}) = 0$ for all $k'$ and the fact that $\E[ f_0(X) - \mu \,|\, X_k] = f^*_k(X_k)$ (Lemma~\ref{lem:int_reduction}).
+Where we used the fact that $\E f^*_{k'} (X_{k'}) = 0$ for all $k'$ and the fact that $\E[ f_0(X) - \mu \,|\, X_k] = f^*_k(X_k)$ (Lemma~\ref{lem:general_int_reduction}).
 

### 2013-11-12 tex/scam/sparsistency.tex
more update

@@
   $f_0(X) = f_0(X_S)$.
-\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$.
+\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E\Big(f_0(X) -\E f_0(X) - \sum_{k=1}^s f_k(X_k)\Big)^2 \,|\, \E[f_k(X_k)] = 0 \}$.
 \end{packed_enum}
@@
 \item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
-  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
-\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
-\item[A4:] For all $k=1,...,s$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
+  twice-differentiable, and $L$-Lipschitz.
+\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
+\item[A4:] For all $k=1,...,s$, $\E(f^*_s(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
 \end{packed_enum}
 
-We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
-The $\alpha$ in assumption A4 can be interpreted as the signal strength of the relevant variable detection problem.
+We will use assumptions A1, A2, A3 to control the probability of false
+positives and the stronger assumptions A1', A2', A3, A4 to control the
+probability of false negatives.  Assumption A4 can be
+weakened so that the relevant functions satisfy
+$\E(f^*_s(X_k))^2 \geq \alpha_n$ for $\alpha_n$ decaying to zero 
+at an appropriate rate.
 
@@
   %[TODO: refer to correlated design experiment].
+\end{remark}
+
+\begin{remark}
+Assumption A4 ensures that the relevant variables are ``relevant enough''.
+Under A4, the population risk of an additive function with $s-1$ components is at least $\alpha$ larger than the population risk of the optimal additive function with $s$ components.
+See lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
 \end{remark}
@@
 data sampled \emph{without} replacement
-\cite{serfling1974probability}, illustrating that the proof method is not a
-trivial application of existing techniques. The full proof of
+\cite{serfling1974probability}. The full proof of
 Theorem~\ref{thm:false_positive} is in
@@
 \label{thm:false_negative}
-Suppose assumptions A1', A2', A3 hold.
+Suppose assumptions A1', A2', A3, A4 hold.
 Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint.
 Let $c,C$ be absolute constants.
-Suppose $L \max \left(\lambda_n, b (B+\sigma)B\sigma \sqrt{\frac{s^5}{n^{4/5}} \log sn} \right) \rightarrow 0$.
+Suppose $s L \lambda_n \rightarrow 0$ and $Lb(sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.
 Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
@@
 is not required with more advanced empirical process theory
-techniques. We give the full proof of Theorem~\ref{thm:false_negative}
+techniques; we leave the incorporation of this development as future work. 
+We give the full proof of Theorem~\ref{thm:false_negative}
 in Section~\ref{sec:false_negative_proof} of the Appendix.
@@
 
+\begin{remark}
+\citet{dalalyan:12} have shown that under tradtional smoothness constraints, variable selection is achievable only if $n > O(e^s)$.
+It is interesting to observe that because of additive faithfulness, the convexity assumption enables a much better scaling of $n = O(\textrm{poly}(s))$, demonstrating that geometric constraints can be quite different from the previously studied smoothness conditions.
+\end{remark}
+
 %\textbf{Comparison with Related Work.}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2013-11-16 tex/scam/additive_faithful.tex
update paper

@@
 
+\begin{remark}
+With only intermittent independence assumption, it is difficult to prove the other direction of additive faithfulness, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
+Consider as a conceptual example a 3D distribution over $(X_1, X_2, X_3)$; suppose $X_1, X_2$ are independent, and $f$ is only a function of $X_1, X_2$.
+We can then let $X_3 = f(X_1, X_2) - f^*_1(X_1) - f^*_2(X_2)$, that is, we let $X_3$ exactly capture the additive approximation error, then the best additive approximation of $f$ would have a component $f^*_3(X_3) = X_3$ even though $f$ does not depend on $X_3$.
+This is, of course, unlikely to occur in practice and we leave as future work analysis under reasonable assumptions that rules out such psychotic phenomenon.
+\end{remark}
+
 % \begin{remark}

### 2013-11-16 code/Piecewise_Infinity.m

@@ -35,6 +35,8 @@ while iter < maxit
     
     obj(iter) = 0.5*sum((y-h).^2,1);
     
+    
+    
     %=- verify stopping criteria -=
     criterion1 = norm(all_xb - all_prev_xb,'fro')/n;
     criterion2 = norm(S - h_mat, 'fro')/n;
@@ -48,6 +50,7 @@ while iter < maxit
     end
     
     if mod(iter,10)==0, 
+        [criterion1, criterion2, criterion3]
         disp(['   Iter ' num2str(iter) ' Obj ' num2str(obj(iter)) ' Score ' num2str(stop_score)]); 
         figure(999); subplot(2,1,1); plot(1:n,y,'ko',1:n,h,'r+');
         subplot(2,1,2); plot(max(abs(beta),[],2),'r.'); drawnow;

### 2013-11-16 code/variable_selection_script.m

@@ -1,8 +1,8 @@
 % variable selection
 
 if (~exist('variable_selection_manual'))
-    p = 100; K = 10; s = 4; n = 700; sigma=0;
-    lambda = 0.001; mu = 0.01; maxiter = 1000;
+    p = 50; K = 5; s = 4; n = 400; sigma=0.2;
+    lambda = 0.5; mu = 0.05; maxiter = 1200;
 end
 
 beta_stars = randn(p,K);
@@ -16,15 +16,21 @@ alpha_stars = randn(K,1);
 alpha_stars = alpha_stars/norm(alpha_stars);
 
 Xs = randn(n,p);
-Xs = Xs./max(max(abs(Xs)))*3;
+% Xs = Xs./max(max(abs(Xs)))*3;
 
 Ys = max(Xs*beta_stars + ones(n,1)*alpha_stars', [], 2);
 % Xs*-beta_stars is (n--by--K)
 
-Ys = Ys + randn(n,1)*sigma;
-Ys = Ys - mean(Ys);
+noise = randn(n,1)*sigma;
+noisy_Ys = Ys + noise;
 
-[beta,z,obj] = SCAM_QP(Xs',Ys, lambda, maxiter, 1e-4);
+mean_Y = mean(noisy_Ys);
+noisy_Ys = noisy_Ys - mean_Y;
+
+lambda = lambda*sqrt(n);
+[beta,z,obj] = Piecewise_Infinity(Xs',noisy_Ys, lambda, mu, maxiter);
+
+
 
 % beta is (p--by--n)
 %figure;

### 2013-12-13 tex/scam/additive_faithful.tex
major proof revamp. three-points property

@@
 \end{equation}
-We say that $f$ has \textbf{additive recall} under $F$ if $f^*_k = 0 \Rightarrow \trm{$f$ does not depend on coordinate $k$}$.
 
-We say that $f$ is \textbf{additively faithful} under $F$ in case $f^*_k = 0$ iff $f$ does not depend on coordinate $k$. 
+We say that $f$ is \textbf{additively faithful} under $F$ in case $f^*_k = 0 \Rightarrow \trm{$f$ does not depend on coordinate $k$}$.
+
 \end{definition}
@@
 Additive faithfulness is an attractive property because it implies that, in the population setting, the additive approximation yields consistent variable selection.
-Additive recall is a weaker condition but still useful: we can be sure that the additive approximation is conservative, that it does not exclude important variables.
 
@@
 
-Remarkably, under a general class of distributions which we characterize below, convex multivariate functions has additive recall and under product distributions, convex functions are additively faithful.
+Remarkably, under a general class of distributions which we characterize below, convex multivariate functions are additively faithful.
 
 \begin{definition}
-Given a conditional density $p(\mathbf{x}_{-j} \given x_j)$, we say that $\mathbf{X}_{-j}$ is \textbf{intermittently independent} of $X_j$ if the set of $x_j$ for which $\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j} = 0$ for all $\mathbf{x}_{-j}$ is either the whole line $[0,1]$, or a collection of at least two disjoint closed intervals.
-
-Let $F$ be a distribution on $[0,1]^s$.
-We say that $F$ is an \textbf{intermittently independent} distribution if $F$ has a non-zero density $p$ with the property that, for all $j=1,...,s$, $\mathbf{X}_{-j}$ is intermittently independent of $X_j$.
+\label{defn:three-point}
+Let $p(\mathbf{x})$ be a density supported on $[0,1]^s$, $p$ satisfies the \emph{three-points property} if, for all $j$, and for all $\mathbf{x}_{-j}$:
+\begin{packed_enum}
+\item $\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  = 0$ at $x_k = 0, x_k = 1$ and a third point $x_k^M \in (0,1)$.
+\item $\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0$ at $x_k = 0, x_k = 1$.
+\end{packed_enum}
 \end{definition}
 
-\begin{example} There are many examples of distributions which satisfy intermittent independence:
-\begin{packed_enum}
-\item $F$ is a product distribution.
-\item $F$ has a density $p$ that is piece-wise constant on a gridding of $[0,1]^s$.
-\item $F$ has a density $p$ that is, for some $\frac{1}{2} > \epsilon > 0$,  arbitrary on $(\epsilon, 1-\epsilon)^s$ but constant elsewhere. 
-\end{packed_enum}
-\end{example}
+The three-points property is a weak condition.
+For instance, it is satisfied when the density is flat at the boundary of support and has at least one peak in the interior of the support.
+More precisely, when the \emph{joint density} satisfies the properties that $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} = 0$ at points $x_j = 0, x_j= 1$ and a third point $x_j^M \in (0,1)$ and $\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at points $x_j = 0, x_j=1$.
+The three-points property is also trivially satisfied when $p$ is the density of any product distributions.
 
-\begin{theorem}
-\label{thm:convex_recall}
-Let $F$ be an \textbf{intermittently independent} distribution supported on $C=[0,1]^s$ with positive density $p$.
-If $f$ is convex and twice differentiable, then $f$ has the \emph{additive recall} property under $F$.
-\end{theorem}
+The following theorem is the main result of this section.
 
@@
 \label{thm:convex_faithful}
-Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p$. If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $F$.
+Let $p$ be a positive density supported on $C=[0,1]^s$ that satisfies the three-points property (definition~\ref{defn:three-point}).
+If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $p$.
 \end{theorem}
@@
 
-We give the proof of Theorem~\ref{thm:convex_recall}, which also proves one direction of Theorem~\ref{thm:convex_faithful}. The other direction of Theorem~\ref{thm:convex_faithful} is trivial.
-
-\begin{proof} (of Theorem~\ref{thm:convex_recall})\\
+\begin{proof} (of Theorem~\ref{thm:convex_faithful})\\
 Fix $k$.
@@
 
-Let us assume that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $.\\
+Let us then use the shorthand notation that $r(\mathbf{x}_{-k}) = \sum_{k' \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that $\mu = 0$. We then assume that for all $x_k$,
 
-By the intermittent independence assumption, we know that there exists at least two disjoint closed intervals $R_0, R_1$ where $p(\mathbf{x}_{-k} \given x_k)$ is independent of $x_k$.
-That is, there exist density functions $\phi_0(\mathbf{x}_{-k})$ and $\phi_1(\mathbf{x}_{-k})$ such that $p(\mathbf{x}_{-k} \given x_k) = \phi_0(\mathbf{x}_{-k})$ for all $x_k \in R_0$ and $p(\mathbf{x}_{-k} \given x_k) = \phi_1(\mathbf{x}_{-k})$ for all $x_k \in R_1$.
+\[
+ \E[ f(X) - r(X_{-k})  \given x_k] \equiv 
+ \int_{\mathbf{x}_{-k}}  p(\mathbf{x}_{-k} \given x_k ) 
+ \big(f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) = 0
+\]
 
-Let $x^0_k$ be an interior point of $R_0$.
+We let $p'(\mathbf{x}_{-k} \given x_k)$ denote 
+$\frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k}$ and 
+$p''(\mathbf{x}_{-k} \given x_k)$ denote 
+$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k, \mathbf{x}_{-k})$.
+We then differentiate under the integral, which is valid because all functions are bounded.
 
-For every $\mathbf{x}_{-k}$, we define $g$ as the derivative of $f$ with respect to $x_k$ at the point $(\mathbf{x}_{-k}, x^0_k)$.
-\[
-g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow x^0_k} 
-     \frac{f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k})}{x_k - x^0_k}
-\]
-$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
+\begin{align}
+& \int_{\mathbf{x}_{-k}} p'(\mathbf{x}_{-k} \given x_k) 
+\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) + 
+p(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}  = 0 
+\label{eqn:integral1a} \\
+& \int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
+\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 
+2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
+p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 
+\end{align}
 
-Now, we use $r(\mathbf{x}_{-k})$ as a short-hand for $\sum_{k'\neq k} f_{k'}(x_{k'})$ and derive that for all $x_k \in R_0$, we have:
+By the three-points property, we have that $p''(\mathbf{x}_{-k} \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k = x_k^0 \equiv 0$.
+The integral equations reduce to the following then:
+\begin{align}
+& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f'(x^0_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}= 0 \label{eqn:integral1b} \\
+& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f''(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} = 0
+\end{align}
+
+Because $f$ is convex, $f(x_k, \mathbf{x}_{-k})$ must be a convex function of $x_k$ for all $\mathbf{x}_{-k}$.
+Therefore, for all $\mathbf{x}_{-k}$, $f''(x^0_k, \mathbf{x}_{-k}) \geq 0$.
+Since $p(\mathbf{x}_{-k} \given x^0_k) > 0$ by assumption that $p$ is a positive density, we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.\\
+
+The Hessian of $f$ at $(x^0_k, \mathbf{x}_{-k})$ then has a zero at the $k$-th main diagonal entry.
+A positive semidefinite matrix with a zero on the $k$-th main diagonal entry must have only zeros on the $k$-th row and column \footnote{ See proposition 7.1.10 of \citet{HJ90}}, which means that \emph{at all $\mathbf{x}_{-k}$, the gradient of $f'(x^0_k, \mathbf{x}_{-k})$ with respect to $\mathbf{x}_{-k}$ must be zero}.
+
+Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be a constant.
+By equation~\ref{eqn:integral1b}, we conclude then that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
+We can use the same reasoning for the case where $x_k = x_k^1$ and deduce that $f'(x^1_k, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
+\\
+
+Now we apply the first-order condition of convex functions to the two points $(x^0_k, \mathbf{x}_{-k})$ and $(x^1_k, \mathbf{x}_{-k})$:
+
 \begin{align*}
-& \int_{\mathbf{x}_{-k}}  \phi_0(\mathbf{x}_{-k}) 
-   \Big( f(x_k, \mathbf{x}_{-k}) - f(x_k^0, \mathbf{x}_{-k}) \Big) d\mathbf{x}_{-k} \\
- &= \int_{\mathbf{x}_{-k}}  \phi_0(\mathbf{x}_{-k})
-   \Big( \big(f(x_k, \mathbf{x}_{-k}) - r(\mathbf{x}_{-k}) - \mu^* \big) - 
-         \big(f(x^0_k, \mathbf{x}_{-k}) - r(\mathbf{x}_{-k}) - \mu^* \big) \Big)
-     d \mathbf{x}_{-k} \\
- &= 0
+\forall \mathbf{x}_{-k}, f(x^1_k, \mathbf{x}_{-k}) & \leq f(x^0_k, \mathbf{x}_{-k}) 
+  + f'(x^0_k, \mathbf{x}_{-k}) ( x^1_k - x^0_k) \\ 
+f(x^1_k, \mathbf{x}_{-k}) &\leq f(x^0_k, \mathbf{x}_{-k}) \\
+\forall \mathbf{x}_{-k}, f(x^0_k, \mathbf{x}_{-k}) & \leq f(x^1_k, \mathbf{x}_{-k}) 
+  + f'(x^1_k, \mathbf{x}_{-k}) ( x^0_k - x^1_k) \\ 
+f(x^0_k, \mathbf{x}_{-k}) &\leq f(x^1_k, \mathbf{x}_{-k})
 \end{align*}
 
-The last equality follows because we assumed that $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ for all $x_k$. \\
+We thus have that $f(x^0_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$.
+By convexity of $f$, we know that for all $x_k \in (0,1)$, it must be that for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) \leq f(x^0_k, \mathbf{x}_k)$.\\
 
-Since $x^0_k$ is in the interior of $R_0$, and since the domain of $f$ is a compact set, we use the bounded convergence theorem and conclude that $\int_{\mathbf{x}_{-k}} \phi_0( \mathbf{x}_{-k}) g(\mathbf{x}_{-k}) = 0$ as well.\\
+We now use the middle point condition.
 
-We now note that $g(\mathbf{x}_{-k})$ is a component of the subgradient 
-$\partial_{\mathbf{x}} f(x^0_k, \mathbf{x}_{-k})$.
+At $x_k = x^M_k$, equation~\ref{eqn:integral1a} becomes:
+\begin{align}
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^M_k) 
+  f'(x^M_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0 \label{eqn:integral1c}
+\end{align}
 
-Therefore, the first-order characterization of convex functions gives us that
+Using the first order condition, we have that:
 \begin{align*}
-f(x_k, \mathbf{x}_{-k}) \geq f(x^0_k, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) (x_k - x^0_k)
-   \quad \trm{for all } x_k, \mathbf{x}_{-k}
+f(x^0_k, \mathbf{x}_{-k}) &\leq f(x^M_k, \mathbf{x}_{-k}) 
++ f'(x^M_k, \mathbf{x}_{-k})(x^0_k - x^M_k)  \quad \Rightarrow \\
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}_k \given x^M_0) 
+f(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  
+&\leq \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^M_k)
+\big( f(x^M_k, \mathbf{x}_{-k}) 
++ f'(x^M_k, \mathbf{x}_{-k})(x^0_k - x^M_k) \big) d\mathbf{x}_{-k} 
 \end{align*}
 
-Or, equivalently, for all $x_k, \mathbf{x}_{-k}$, 
+By equation~\ref{eqn:integral1c} then, we have that $
+\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x_k) \big(f(x^0_k, \mathbf{x}_{-k}) -
+ f(x^M_k, \mathbf{x}_{-k}) \big) d\mathbf{x}_{-k} \leq 0$
+
+However, we have previously argued that for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) \leq f(x^0_k, \mathbf{x}_{-k})$ for all $x_k \in (0,1)$.
+Since $p(\mathbf{x}_{-k} \given x_k) > 0$, it must be that $f(x^0_k, \mathbf{x}_{-k}) = f(x^M_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$.\\
+
+Thus, we have shown that for all $\mathbf{x}_{-k}$, 
 \[
-f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) (x_k-x^0_k) \geq 0
+f(x^0_k, \mathbf{x}_{-k}) = f(x^M_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})
 \]
-
-Now, the critical observation we make is that, for all $x_k \in R_0$, 
-\[
-\int_{\mathbf{x}_{-k}} \phi_0(\mathbf{x}_{-k}) 
-     \Big(f(x_k, \mathbf{x}_{-k}) - f(x^0_k, \mathbf{x}_{-k}) 
-     - g(\mathbf{x}_{-k}) (x_k - x^0_k) \Big) d\mathbf{x}_{-k} = 0
-\]
-Since $\phi_0$ is positive by assumption and the second term is non-negative, we conclude that the second term must be exactly zero, that is, for all $x_k \in R_0$, for all $\mathbf{x}_{-k}$, 
-$$
-f(x_k, \mathbf{x}_{-k}) = f(x^0_k, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) (x_k - x^0_k)
-$$
-
-The Hessian of $f$ at $(x_k, \mathbf{x}_{-k})$ for $x_k \in R$ then has a zero at the $k$-th main diagonal entry.
-A positive semidefinite matrix with a zero on the $k$-th main diagonal entry must have only zeros on the $k$-th row and column \footnote{ See proposition 7.1.10 of \citet{HJ90}}, which means that $g(\mathbf{x}_{-k})$ must be a constant function.
-Since $g$ integrates to 0 under $\phi_0(\mathbf{x}_{-k})$, it must be 0.\\
-
-Thus, $f(x_k, \mathbf{x}_{-k}) = f(x^0_k, \mathbf{x}_{-k})$ for all $x_k \in R_0$ and for all $\mathbf{x}_{-k}$.\\
-
-We can go through the same reasoning for $R_1$  and get that $f(x_k, \mathbf{x}_{-k})$ is a constant function of $x_k$ for all $x_k \in R_1$, that is, $f(x_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})$ for all $x_k \in R_1$ for some interior point $x^1_k$ of $R_1$.
-
-However, if $f(x_k, \mathbf{x}_{-k})$, as an one-dimensional convex function of $x_k$, is constant on two disjoint closed intervals, it must be constant for all $x_k \in [0,1]$.
-Therefore, for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a constant as a function of $x_k$ and $f$ does not depend on $x_k$.
-
+This implies that $f(x_k, \mathbf{x}_{-k})$, as a convex function of $x_k$, must be a constant. This proves that $f$ does not depend on $x_k$. 
 \end{proof}
@@
   We assume twice differentiability in
-  Theorems~\ref{thm:convex_faithful} and~\ref{thm:convex_recall} to simplify the proof. 
+  Theorems~\ref{thm:convex_faithful} to simplify the proof. 
   We believe
@@
 \begin{remark} 
-With only intermittent independence assumption, it is difficult to prove the other direction of additive faithfulness, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
+It is difficult to prove the opposite direction of additive faithfulness, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
 Consider as a conceptual example a 3D distribution over $(X_1, X_2, X_3)$; suppose $X_1, X_2$ are independent, and $f$ is only a function of $X_1, X_2$.

### 2013-12-13 tex/scam/additive_faithful.tex
boundary-point condition

@@
 \begin{definition}
-\label{defn:three-point}
-Let $p(\mathbf{x})$ be a density supported on $[0,1]^s$, $p$ satisfies the \emph{three-points property} if, for all $j$, and for all $\mathbf{x}_{-j}$:
-\begin{packed_enum}
-\item $\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  = 0$ at $x_k = 0, x_k = 1$ and a third point $x_k^M \in (0,1)$.
-\item $\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0$ at $x_k = 0, x_k = 1$.
-\end{packed_enum}
+\label{defn:boundary-point}
+Let $p(\mathbf{x})$ be a density supported on $[0,1]^s$, $p$ satisfies the \emph{boundary-points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
+
+\[
+\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
+\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
+\quad \trm{at } x_k = 0, x_k = 1
+\]
+
 \end{definition}
 
-The three-points property is a weak condition.
-For instance, it is satisfied when the density is flat at the boundary of support and has at least one peak in the interior of the support.
-More precisely, when the \emph{joint density} satisfies the properties that $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} = 0$ at points $x_j = 0, x_j= 1$ and a third point $x_j^M \in (0,1)$ and $\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at points $x_j = 0, x_j=1$.
-The three-points property is also trivially satisfied when $p$ is the density of any product distributions.
+The boundary-points condition is a weak condition.
+For instance, it is satisfied when the density is flat at the boundary of support, more precisely, when the \emph{joint density} satisfies the properties that $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =  \frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at points $x_j = 0, x_j=1$.
+The boundary-points property is also trivially satisfied when $p$ is the density of any product distributions.
 
@@
 \label{thm:convex_faithful}
-Let $p$ be a positive density supported on $C=[0,1]^s$ that satisfies the three-points property (definition~\ref{defn:three-point}).
+Let $p$ be a positive density supported on $C=[0,1]^s$ that satisfies the boundary-points property (definition~\ref{defn:boundary-point}).
 If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $p$.
@@
 
-By the three-points property, we have that $p''(\mathbf{x}_{-k} \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k = x_k^0 \equiv 0$.
+By the boundary-points condition, we have that $p''(\mathbf{x}_{-k} \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k = x_k^0 \equiv 0$.
 The integral equations reduce to the following then:
@@
 
-Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be a constant.
+Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be constant for all $\mathbf{x}_{-k}$.
 By equation~\ref{eqn:integral1b}, we conclude then that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
@@
 
-Now we apply the first-order condition of convex functions to the two points $(x^0_k, \mathbf{x}_{-k})$ and $(x^1_k, \mathbf{x}_{-k})$:
+Because $f(x_k, \mathbf{x}_{-k})$ as a function of $x_k$ is convex, it must be that, for all $x_k \in (0,1)$ and for all $\mathbf{x}_{-k}$:
+\[
+0 = f'(x_k^0, \mathbf{x}_{-k}) \leq f'(x_k, \mathbf{x}_{-k}) \leq 
+    f'(x_k^1, \mathbf{x}_{-k}) = 0
+\]
+
+Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:
 
 \begin{align*}
-\forall \mathbf{x}_{-k}, f(x^1_k, \mathbf{x}_{-k}) & \leq f(x^0_k, \mathbf{x}_{-k}) 
-  + f'(x^0_k, \mathbf{x}_{-k}) ( x^1_k - x^0_k) \\ 
-f(x^1_k, \mathbf{x}_{-k}) &\leq f(x^0_k, \mathbf{x}_{-k}) \\
-\forall \mathbf{x}_{-k}, f(x^0_k, \mathbf{x}_{-k}) & \leq f(x^1_k, \mathbf{x}_{-k}) 
-  + f'(x^1_k, \mathbf{x}_{-k}) ( x^0_k - x^1_k) \\ 
-f(x^0_k, \mathbf{x}_{-k}) &\leq f(x^1_k, \mathbf{x}_{-k})
+\forall \mathbf{x}_{-k}, f(x'_k, \mathbf{x}_{-k}) & \leq f(x_k, \mathbf{x}_{-k}) 
+  + f'(x_k, \mathbf{x}_{-k}) ( x'_k - x_k) \\ 
+f(x'_k, \mathbf{x}_{-k}) &\leq f(x_k, \mathbf{x}_{-k}) \\
+\forall \mathbf{x}_{-k}, f(x_k, \mathbf{x}_{-k}) & \leq f(x'_k, \mathbf{x}_{-k}) 
+  + f'(x'_k, \mathbf{x}_{-k}) ( x_k - x'_k) \\ 
+f(x_k, \mathbf{x}_{-k}) &\leq f(x'_k, \mathbf{x}_{-k})
 \end{align*}
 
-We thus have that $f(x^0_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$.
-By convexity of $f$, we know that for all $x_k \in (0,1)$, it must be that for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) \leq f(x^0_k, \mathbf{x}_k)$.\\
-
-We now use the middle point condition.
-
-At $x_k = x^M_k$, equation~\ref{eqn:integral1a} becomes:
-\begin{align}
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^M_k) 
-  f'(x^M_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0 \label{eqn:integral1c}
-\end{align}
-
-Using the first order condition, we have that:
-\begin{align*}
-f(x^0_k, \mathbf{x}_{-k}) &\leq f(x^M_k, \mathbf{x}_{-k}) 
-+ f'(x^M_k, \mathbf{x}_{-k})(x^0_k - x^M_k)  \quad \Rightarrow \\
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_k \given x^M_0) 
-f(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  
-&\leq \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^M_k)
-\big( f(x^M_k, \mathbf{x}_{-k}) 
-+ f'(x^M_k, \mathbf{x}_{-k})(x^0_k - x^M_k) \big) d\mathbf{x}_{-k} 
-\end{align*}
-
-By equation~\ref{eqn:integral1c} then, we have that $
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x_k) \big(f(x^0_k, \mathbf{x}_{-k}) -
- f(x^M_k, \mathbf{x}_{-k}) \big) d\mathbf{x}_{-k} \leq 0$
-
-However, we have previously argued that for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) \leq f(x^0_k, \mathbf{x}_{-k})$ for all $x_k \in (0,1)$.
-Since $p(\mathbf{x}_{-k} \given x_k) > 0$, it must be that $f(x^0_k, \mathbf{x}_{-k}) = f(x^M_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$.\\
-
-Thus, we have shown that for all $\mathbf{x}_{-k}$, 
-\[
-f(x^0_k, \mathbf{x}_{-k}) = f(x^M_k, \mathbf{x}_{-k}) = f(x^1_k, \mathbf{x}_{-k})
-\]
-This implies that $f(x_k, \mathbf{x}_{-k})$, as a convex function of $x_k$, must be a constant. This proves that $f$ does not depend on $x_k$. 
+We thus have that $f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$ and all pairs $x_k, x'_k \in (0,1)$. This proves that $f$ does not depend on $x_k$.
 \end{proof}

### 2014-02-14 tex/discussion_notes.tex
brief update

@@
 
-\begin{document}\
+\begin{document}
 
+\section{2/7/2014}
+
+\subsection{Best Shape-Constrained Projection}
+
+Even if a function $f_0$ is non-zero, it may be possible that the best convex approximation is zero.
+But, it cannot be that the best convex approximation and the best concave approximation are both zero.
+
+\begin{theorem}
+Let $f_0: C \rightarrow \R$ be a function with a bounded Hessian; let $p$ be some distribution on $C$.
+Suppose 
+\[
+\argmin_{f \in \mathcal{C}_x \cup \mathcal{C}_v} 
+   \E (f_0(x) - f(x))^2  = 0
+\]
+ then $f_0 = 0$ necessarily.
+\end{theorem}
+
+\begin{proof}
+
+Suppose that the $\argmin_{f \in \mathcal{C}_x \cup \mathcal{C}_v} \E( f_0(x) - f(x))^2 = 0$, then it must be that 
+\[
+\argmin_{c \in \R} \E\Big( f_0(x) - c x^\tran x \Big)^2 = 0
+\]
+Since the optimal $c$ in the above optimization is 
+$c^* = \frac{\E[ f_0(x) x^\tran x ]}{\E (x^\tran x)^2 }$, 
+we have that $\E[ f_0(x) x^\tran x]=0$.
+
+We know that there exists a convex function $f'$ such that $f' = f_0 + r x^\tran c$ for some large $r > 0$.
+
+By assumption and convexity of $f'$, it must be that 
+\[
+\argmin_{c \in \R} \E\Big( f_0(x) - c f'(x) \Big)^2 = 0
+\]
+We know by similar argument then that $\E[ f_0(x) f'(x) ] =0$.
+
+However, $\E[ f_0(x) f'(x) ] = \E[f_0(x)^2 + r f_0(x) x^\tran x ] = \E[ f_0(x)^2]$. This is a contradiction.
+
+\end{proof}
+
+Thus, if we tried both convex and concave projection and the solution is zero, then we can be sure that the original function is identically zero.
+
+The same argument applies if we consider the best single component approximation:
+\[
+\argmin_{f_k \in \mathcal{C}_x \cup \mathcal{C}_v} 
+\E\Big( f_0(x) - f_k(x_k) \Big)^2
+\]
+Because $\E[ f_0(x) x_k^2 ] = \E\Big[ \E[f_0(x) \given x_k] x_k^2\Big] 
+= \E[ f^*_k(x_k) x_k^2]$.
+Thus, we can apply the same argument and use $f^*_k(x_k)$ where needed.
+
+\newpage
+
+\section{1/23/2014}
+
+\subsection{Additive Faithfulness Case Study with Quadratic Function and Gaussian Distribution}
+
+We consider a quadratic function $f(x) = x^\tran H x + c^\tran x$ and a Gaussian distribution $X \sim N(0, \Sigma)$.
+
+We then have a closed form for the additive approximation.
+\begin{itemize}
+\item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
+\item If $f$ depends on $x_j$, then, letting $H_j$ be the $j$-th row of $H$ and $\Sigma_j$ be the $j$-th row of $\Sigma$:
+\[
+f^*_j(x_j) = H_j^\tran \Sigma_j \frac{1}{\Sigma_{jj}} x_j^2 + c_j x_j
+\]
+
+\end{itemize}
+
+Let us assume $\Sigma_{jj} = 1$ for all $j$ and that $c=0$ for convenience. We then have two direct corollaries:
+
+\textbf{Corollary:} We have additive convexity if and only if $\trm{diag}(H \Sigma) \geq 0$.
+
+\textbf{Corollary:} We have additive faithfulness if and only if $\trm{diag}(H \Sigma) \neq 0$.
+
+As an example where additive convexity and additive faithfulness are violated.
+Let $H = [1, 2; 2, 5]$ and $\Sigma = [1, -c; -c, 1]$.
+For $c=0.5$, additive faithfulness is violated; for $c > 0.5$, additive convexity is violated.
+
+\begin{proof}
+We will show that the $f^*_j(x_j)$'s, so described, satisfy the KKT stationarity equations.
+\[
+f^*_j(x_j) = \E[ f(x) - \sum_{k \neq j} f^*_k(x_k) \given x_j ]  \qquad \trm{for all } j
+\]
+
+To prove this, we use the following conditional mean and conditional covariance property of the multivariate Gaussian distribution.
+\begin{align*}
+& \E[ x_k \given x_j ] = \Sigma_{jk} \Sigma_{jj}^{-1} x_j \\
+& \E[ x_k x_{k'} \given x_j] \trm{ is some constant for all $x_j$ } \\
+& \E[ x_k^2 \given x_j ] \trm{ is some constant for all $x_j$ } 
+\end{align*}
+\end{proof}
+
+Why can Gaussian distribution violate additive faithfulness? Because $\frac{\partial p( x_{-j} \given x_j) }{\partial x_j}$ is always large for some values of $x_{-j}$.
+
+\newpage
+
+\section{1/2/2014}
+
+\subsection{Convex-minus-Quadratic Estimation}
+
+Instead of estimating a convex-plus-concave function, it is theoretically sufficient to estimate a convex-minus-quadratic function.
+
+\begin{theorem}
+Any function $h : \R^d \rightarrow \R$ with a bounded Hessian can be decomposed as $h(x) = f(x) - q(x)$ where $f(x)$ is convex and $q(x)$ is $c x^\tran x$ for some $c \geq 0$. 
+\end{theorem}
+
+\begin{proof}
+For large enough $c$, the Hessian of $h + c$ is a positive semidefinite. The function $f$ is thus convex.
+\end{proof}
+
+Convex-minus-quadratic functions are faster to learn. The optimization program has about twice as few variables. It is also possibly easier to analyze. \\
+
+\subsubsection{Implementation}
+
+For additive modeling, I use the following optimization program. There are two parameters $\lambda$ and $L$. 
+\begin{align*}
+\min_{f_1, ..., f_p} & \frac{1}{n} \sum_i 
+  \Big(y_i - \sum_j f_j(x_{ij}) + c_j x_{ij}^2 \Big)^2 + 
+  \lambda \sum_j \| \partial f_j - 2 c_j x_j^2 \|_\infty \\
+\trm{s.t. } & f_j \trm{ is convex} \\
+  & c_j \geq 0 \quad \trm{ and } \quad c_j \leq L
+\end{align*}
+
+The second $L$ parameter is necessary.
+A similar parameter is required in convex-plus-concave estimation as well, which I will explain in the next section.
+$L$ can be interpreted as a lower bound on the second derivative of the estimated regression function.
+We set $L=200$ in experiments.
+
+\textbf{Demonstration:} We estimate a one-dimensional function so that we can visualize the behavior of convex-minus-quadratic functions. We set $lambda = 0$. The result is in figure~\ref{fig:quad}.
+
+Here, $n=300$, the $SNR$ is about $0.6$ (high noise).  \\
+
+\begin{figure}[htp]
+\label{fig:quad}
+\centering
+\includegraphics[scale=0.6]{figs/convex_quad.png}
+\end{figure}
+
+\subsection{Tuning Parameters for Convex-plus-Concave Estimation}
+
+Convex-plus-concave estimation is not free of tuning parameters. Arbitrary sum of convex and concave functions can represent any function with a bounded Hessian.\\
+
+In Minhua's original SCCAM implementation, the objective is augmented with a square-penalty on the value of the gradients of $f$ and $g$, the convex and the concave functions.
+The penalty looks like $10^{-6} \| \trm{gradient} \|_2^2$.
+This penalty is not just for numerical stability; its magnitude affects the estimation.
+
+\textbf{Demonstration:}
+
+The experimental set-up is the same as before. The result is in figure~\ref{fig:tuning}
+
+\begin{figure}[htp]
+\label{fig:tuning}
+\centering
+\includegraphics[scale=0.6]{figs/convex_concave_tune.png}
+\end{figure}
+
+As one can see, when the tuning parameter (the coefficient for the $\| \trm{gradient} \|_2^2$ penalty) is too small, the estimated function is fitting noise.
+When the tuning parameter is too large, the estimated function is too smooth.
+
+\subsection{Convex-Concave Separation}
+
+We study the problem of variable selection on a convex-plus-concave function $h$. The approach has two steps: 
+\begin{packed_enum}
+\item Learn \textbf{sparse non-additive} convex function $f$ and concave function $g$ such that $h = f + g$. This is the separation stage.
+\item Apply sparse additive model on $f$ and $g$.
+\end{packed_enum}
+
+Preliminary results are favorable.
+In our experiment, we let $p=30, n=300$.
+The true function is $h(x) = 2 x_1 x_2$ and uses only the first two variables.
+The SNR is $4$.
+$h$ is an example of a function that cannot be consistently estimated by additive modeling.
+
+We can indeed identify the correct variables by applying additive model on $f$ after separation.
+
+\begin{figure}[htp]
+\label{fig:after_separation}
+\centering
+\includegraphics[scale=0.6]{figs/scam_separation.png}
+\end{figure}
+
+Without separation however, the additive model indeed fails.
+
+\begin{figure}[htp]
+\label{fig:before_separation}
+\centering
+\includegraphics[scale=0.6]{figs/sccam_before_separation.png}
+\end{figure}
+
+\end{document}
+
+\newpage
 \section{10/25/2013: Convex + Concave function}

### 2014-02-14 code/SCAM_QP.m

@@ -4,13 +4,35 @@
 %
 function [beta,z,obj,Ln] = SCAM_QP(X,y,lambda,maxit,tol)
 [p,n] = size(X); z = zeros(p,n); Ln = zeros(p,1); beta = zeros(p,n-1);
+
+z2 = zeros(p,n);
+Ln2 = zeros(p,1);
+
 res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
 while iter < maxit && change > tol
     iter = iter + 1; 
     
     for d = 1:p
         res = res + z(d,:)';
+        
+        % MOSEK_f is much slower
+        % both sometimes errs
+        % 
+        
+        %disp('new')
+        %[z2(d,:), Ln2(d)] = SCAM_MOSEK_f(res, X(d,:), lambda);
+        %disp('old')
         [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK(res,X(d,:),lambda);
+
+        %[Xd, ord] = sort(X(d,:));
+        %'test'
+        %diff_magn = norm(z(d,:)-z2(d,:))/norm(z(d,:));
+        %disp(['diff:' num2str( diff_magn )])
+        
+        %if (diff_magn > 1)
+        %    'err'
+        %end
+        
         res = res - z(d,:)'; 
     end
 
@@ -20,6 +42,56 @@ while iter < maxit && change > tol
     figure(9); subplot(2,1,1); plot(1:n,y,'ko',1:n,sum(z,1)','r+'); title('Response');
     subplot(2,1,2); plot(1:p,Ln,'r.'); title('L\infty norm'); drawnow;
 end
+return
+
+function [z,Ln] = SCAM_MOSEK_f(y,x,lambda)
+n = length(x); [Xd,ord] = sort(x'); dX = Xd(2:n)-Xd(1:n-1);
+
+yord = y(ord);
+
+Hi = 1:n; Hj = 1:n; Hs = ones(1,n)/n; 
+H = sparse(Hi,Hj,Hs,n+1,n+1); f = [-yord/n; lambda];
+
+Ai = []; Aj = []; As = []; row = 0; 
+
+%put in Linf norm constraints
+valmat = [ones(n, 1) -ones(n, 1) -ones(n,1) -ones(n,1)];
[…]

### 2014-02-14 code/variable_selection_script.m

@@ -1,8 +1,8 @@
 % variable selection
 
 if (~exist('variable_selection_manual'))
-    p = 50; K = 5; s = 4; n = 400; sigma=0.2;
-    lambda = 0.5; mu = 0.05; maxiter = 1200;
+    p = 10; K = 5; s = 5; n = 1000; sigma=0.1;
+    lambda = 0.0001; mu = 0.05; maxiter = 1200;
 end
 
 beta_stars = randn(p,K);
@@ -27,10 +27,10 @@ noisy_Ys = Ys + noise;
 mean_Y = mean(noisy_Ys);
 noisy_Ys = noisy_Ys - mean_Y;
 
-lambda = lambda*sqrt(n);
-[beta,z,obj] = Piecewise_Infinity(Xs',noisy_Ys, lambda, mu, maxiter);
+%lambda = lambda*sqrt(n);
+%[beta,z,obj] = Piecewise_Infinity(Xs',noisy_Ys, lambda, mu, maxiter);
 
-
+[beta,z,obj] = SCAM_QP(Xs',noisy_Ys, lambda, maxiter, 1e-6);
 
 % beta is (p--by--n)
 %figure;

### 2014-02-14 code/side_exp/variable_selection_script.m
massive add

@@ -1,0 +1,38 @@
+% variable selection
+
+if (~exist('variable_selection_manual'))
+    p = 10; K = 5; s = 5; n = 500; sigma=0.1;
+    lambda = 0.0001; mu = 0.05; maxiter = 1200;
+end
+
+beta_stars = randn(p,K);
+beta_stars = sign(beta_stars).*(abs(beta_stars)+0.2);
+%normalization
+beta_stars = beta_stars./(ones(p,1)*sqrt(sum(beta_stars.^2,1)));
+
+beta_stars((s+1):p,:) = 0; %only the first s coordinates are relevant
+
+alpha_stars = randn(K,1);
+alpha_stars = alpha_stars/norm(alpha_stars);
+
+Xs = randn(n,p);
+% Xs = Xs./max(max(abs(Xs)))*3;
+
+Ys = max(Xs*beta_stars + ones(n,1)*alpha_stars', [], 2);
+% Xs*-beta_stars is (n--by--K)
+
+noise = randn(n,1)*sigma;
+noisy_Ys = Ys + noise;
+
+mean_Y = mean(noisy_Ys);
+noisy_Ys = noisy_Ys - mean_Y;
+
+%lambda = lambda*sqrt(n);
+%[beta,z,obj] = Piecewise_Infinity(Xs',noisy_Ys, lambda, mu, maxiter);
+
+[beta,z,obj] = SCAM_QP(Xs',noisy_Ys, lambda, maxiter, 1e-6);
+
+% beta is (p--by--n)
+%figure;
+%plot(1:p, sum(abs(beta),2),'.r');
+%[sum(beta.^2,2),sum(beta_stars.^2,2)]

### 2014-03-22 tex/discussion_notes.tex
lots of changes

@@
 
+\section{3/1/2014}
+
+This note analyzes SCAM where we penalize $\| f \|_\infty$ instead of $\| \partial f \|_\infty$.
+
+\subsection{Changes to Optimization}
+
+The optimization program must change. We modify two formulations of the optimization. The first is the formulation in which we use both $f$ and $\beta$ as variables.
+
+\begin{align*}
+\min_{h_k, \beta_k, \gamma_k} & \frac{1}{2n} \sum_{i=1}^n
+  \Big( y_i - \sum_{k' \neq k} h_{k' i} - h_{ki} \Big)^2 + \lambda \sum_k \| h_k \|_\infty \\
+\textrm{s.t. } & h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)} - x_{k(i)}) \\
+  & \beta_{k(i+1)} \geq \beta_{k(i)}, \mathbf{1} h_k = 0
+\end{align*}
+
+Of course, the $\lambda \| h_k \|_\infty$ penalty can be replaced by $\lambda \gamma_k$ and linear inequalities involving $\gamma_k$.\\
+
+Now we reformulate the optimization program that is in term of the discretized second derivative $d_k$.
+\begin{align*}
+\min_{d_k} &\frac{1}{2n} \| Y - \sum_{k=1}^p \Delta_k d_k \|_2^2 
+    + \lambda \sum_{k=1}^p \| \Delta_k d_k \|_\infty \\
+\textrm{s.t. } & d_{k(2)}, ..., d_{k(n-1)} \geq 0 \\
+& \mathbf{1}_n^\tran \Delta_k d_k = 0 \quad \forall k
+\end{align*}
+
+\subsection{Subgradient analysis}
+
+We take the subgradient of the optimization program with $d_k$.
+
+First, we note that the subgradient of the sup-norm $\partial \| x \|_\infty$ at $x=0$ is $\{ z : \sum_i z_i = 1 \}$.
+
+We fix one dimension $k$, let $Y' = Y - \sum_{k' \neq k} \Delta_{k'} d_{k'}$.
+
+The Lagrangian form of the optimization is
+\[
+\mathcal{L}(d_k, v, \gamma) =
+  \frac{1}{2n} \| Y' -  \Delta_k d_k \|_2^2 + \lambda \| \Delta_k d_k \|_\infty
+  - \sum_{i=2}^{n-1} v_i d_{ki} + \gamma \mathbf{1}_n^\tran \Delta_k d_k
+\]
+with the constraint that $v_i \geq 0$ for all $i$.
+
+We want to find under what conditions does the solution $d_k = 0$ satisfy the KKT conditions.
+
+\[
+\partial_{d_k} \mathcal{L} = 
+  \frac{1}{n} \Delta_k^\tran ( Y' - \Delta_k d_k) + \lambda \Delta_k^\tran z 
+  - v + \gamma \mathbf{1}_n^\tran \Delta_k
+\]
+
+where $z \in \partial \| \Delta_k d_k \|_\infty$.
+
+If we evaluate the subgradient at $d_k = 0$, then we have that
+\[
+\partial_{d_k} \mathcal{L} \Big|_{d_k=0} = \frac{1}{n} \Delta_k^\tran Y' + \lambda \Delta_k^\tran z - v + \gamma \mathbf{1}_n^\tran \Delta_k
+\]
+where $\| z \|_1 \leq 1$. \\
+
+We want to argue that $d_k = 0$ is an optimal solution.
+If $d_k = 0$, then complementary slackness and primal feasibility are obvious satisfied.
+We need only verify stationarity and dual feasibility then.\\
+
+Let us take a brief digression and understand the $\Delta_k$ matrix a little bit more.
+$\Delta_k$ is $n \times n-1$.
+Each row corresponds to sample $i$; each column corresponds to an order $(j)$.
+Each entry $(i,j)$ is $[ X_{ki} - X_{k(j)}]_+$.
+Let us reorder the samples so that the $i$-th sample is the $i$-smallest sample.
+\\
+
+We will construct $\gamma = 0$, and $z = (0, 0, ..., a)$ for some $0 < a < 1$. (coordinates of $z$ correspond to the new sample ordering) We then just need to show that
+\begin{align*}
+\frac{1}{n} \Delta_k^\tran Y' + \lambda \Delta_k^\tran z &\geq 0 \\
+\frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) Y'_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
+   \textrm{for each } j \\
+\frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} Y'_i 
+    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
+\frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} Y'_i 
+    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
+\frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran Y' 
+   + \lambda (X_{kn} - X_{kj})a &\geq 0 
+\end{align*}
+
+Where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. (with respect to ordered indices) The notation $\mathbf{1}_{i':n}$ is a vector that is one on the last $i'$ to $n$ coordinates and zero elsewhere.
+
+Suppose we show that $\frac{1}{n} \mathbf{1}_{i:n}^\tran Y'$ is on the order of $O( \frac{1}{\sqrt{n}})$, then we would be done. Here, we will need to bound $\| Y' \|_\infty$.
+
+\subsection{False Negative Analysis}
+
+Before we begin, we keep in mind that the analysis should be flexible and should be easy to modify to accomodate the following:
+\begin{enumerate}
+\item choice of norm in the penalty
+\item with or without a Lipschitz constraint, boundedness constraint
+\end{enumerate}
+
+\subsubsection{Preliminary}
+We start with the definitions.
+Let $y = (y_1, ..., y_n)$ and $y_i = f_0(x_i) + w_i$.
+We assume $f_0$ to be convex.
+\footnote{We can probably relax this assumption to be a little bit more general.} We assume that all $x_i \in [-b, b]^s$ \\
+
+Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
+Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions.
+\\
+
+Define $\mathcal{C}^s$ as the set of convex additive functions
+\[
+\mathcal{C}^s \equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
+   f_k \in \mathcal{C}^1 \}
+\]
+We will also define classes of bounded and Lipschitz convex additive functions. 
+\begin{align*}
+\mathcal{C}^s_B &= \{ f \in \mathcal{C}^s \,:\, 
+  \| f \|_\infty \leq B \} \\
+\mathcal{C}^s_L &= \{ f \in \mathcal{C}^s \,:\, 
+f = \sum_{k=1}^s f_k, \, \| \partial f_k \|_\infty \leq L \}
+\end{align*}
+
+Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
+\[
+f^* = \arg\min_{f \in \mathcal{C}^s} \E \Big( f_0(X) - f^*(X) \Big)^2
+\]
+
+We let $B$ be an upper bound on $\|f_0\|_\infty$ and $\| f^* \|_\infty$ and let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.
+
+In the finite sample context where we have $n$ samples $x_1, ..., x_n$, we will abuse notation and let $y, f_0, f^*, w$ denote their de-meaned counterpart, that is, $f_0$ is an $n$-dimensional vector whose coordinate $i$ is $f_0(x_i) - \frac{1}{n} \sum_i f_0(x_i)$.
+
+We define $\hat{f}$ as the empirical risk minimizer:
+\[
+\hat{f} = \arg\min \{ \| y - f \|_n^2 + \lambda \sum_{k=1}^s \| f_k \|_\infty 
+    \,:\, f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0 \}
+\]
+
+We also define $\hat{f}^*$ as the noiseless empirical risk minimizer:
+\[
+\hat{f}^* = \arg\min \{ \| f_0 - f \|_n^2 \,:\, 
+f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0\}
+\]
+
+\subsubsection{Proof}
+
+We start from the definition.
+
+\begin{align*}
+\| y - \hat{f} \|_n^2 + \lambda \sum_{k=1}^s \| \hat{f}_k \|_\infty &\leq
+  \| y - \hat{f}^* \|_n^2 + \lambda \sum_{k=1}^s \| \hat{f}^*_k \|_\infty \\
+\| f_0 + w - \hat{f} \|_n^2 + \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
+    \| \hat{f}^*_k \|_\infty \Big) &\leq \|f_0 + w - \hat{f}^* \|_n^2 \\
+\| f_0 - \hat{f} \|_n^2 + 2\langle w, f_0 - \hat{f} \rangle_n 
+     +  \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
+    \| \hat{f}^*_k \|_\infty \Big) &\leq \| f_0 - \hat{f}^* \|_n^2 + 
+    2 \langle w, f_0 - \hat{f}^* \rangle \\
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - \hat{f}^* \|_n^2 + 
+    \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
+    \| \hat{f}^*_k \|_\infty \Big) &\leq 2 \langle w, \hat{f} - \hat{f}^* \rangle
+\end{align*}
+
+\newpage
+
+\section{2/15/2014}
+
+The two step procedure for variable selection:
+
+\begin{enumerate}
+\item Jointly convex approximation:\\ $\{f^c_k\}_{k=1,..,p} = \arg\min_{f_k \in \mathcal{C}_x} \mathbb{E}\Big( f(X) - \sum_{k=1}^p f_k(X_k) \Big)^2$
+\item Separate concave post-processing, for each $k=1,...,p$: \\
+$f^v_k = \arg\min_{f_k \in \mathcal{C}_v} 
+    \mathbb{E}\Big( f(X) - \sum_{k' \neq k} f^c_{k'}(X_{k'}) - f_k(X_k) \Big)^2$
+\end{enumerate}
+
+We consider as irrelevant any $k$ where $f^c_k = 0$ and $f^v_k = 0$.\\
+
+\textbf{Claim:} Let $f : C \rightarrow \R$ where $C = [0,1]^p$. Suppose $p(x)$ is a positive density on $C$ and that it satisfies the boundary-points condition.
+
+Suppose $f(x)$ and $\nabla f(x)$ are continuous and for all $k$, that $\partial_{x_k} p(x \given x_k)$ and $\partial^2_{x_k} p(x \given x_k)$ are also continuous as functions on $C$.
+
+Then, the two step procedure is faithful, that is, $f^c_k = 0$ and $f^v_k =0$ implies that $\partial_{x_k} f(x) = 0$.\\
+
+\begin{proof}
+We focus on a specific $k$ and suppose that $f^c_k$ and $f^v_k$ are both $0$.\\
+
+We now invoke proposition~\ref{prop:shape_approx_univariate} by letting $g(x) = f(x) - \sum_{k'\neq k} f^c_{k'}(x_{k'})$.
+It is easy to verify that derivative continuity requirements on $g$ and $p(x \given x_k)$ are all met.
+We can therefore conclude that $g^*_k(x) = \E[ f(X) - \sum_{k'\neq k} f^c_{k'}(X_{k'}) \given x_k] = 0$.
+
+We now use corollary~\ref{cor:faithfulness_extension} by letting $\phi(x_{-k}) = \sum_{k'\neq k} f^c_{k'}(x_{k'})$. We therefore derive that $\partial_{x_k} f(x) = 0$ and thus prove faithfulness.
+
+\end{proof}
+
+\subsection{Analysis}
+
+To prove the faithfulness of this procedure, we use the following extension of additive faithfulness.
+
+\begin{corollary} 
+\label{cor:faithfulness_extension}
+Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary-points condition.
+
+For any function $\phi(X_{-k})$ that does not depend on $X_k$:
+ \begin{align*}
+f^*_k(x_k) &= \arg\min_{f_k} \mathbb{E} \Big( f(X) 
+           - \phi(X_{-k}) - f_k(X_k) \Big)^2 
+      = \mathbb{E}\Big[ f(X) - \phi(X_{-k}) \,|\, x_k\Big] 
+\end{align*}
+We have that $ f^*_k = 0 \Rightarrow \partial_{x_k} f(x) = 0$.
+\end{corollary}
+
+\begin{proof}
+Identical to the proof of additive faithfulness.
+\end{proof}
+
+We also use the following form of the shape-constrained projection theorem.
+
+\begin{proposition}
+\label{prop:shape_approx_univariate}
+Let $C \subset \R^p$ be a compact set and let $g : C \rightarrow \R$. Let $p(x)$ be a positive density on $C$ and suppose $\E g(X) = 0$.
+
+Suppose that $\partial_{x_k} g(x)$, $\partial_{x_k} p( x \given x_k)$, and $\partial^2_{x_k} p( x \given x_k )$ are all continuous as functions on $C$. Suppose that $\partial^2_{x_k} g(x) \geq 0$.
+
+Let $f^c_k(x_k) = \arg\min_{f_k \in \mathcal{C}_x} \E \Big( g(X) - f_k(X_k) \Big)^2$ and 
+$f^v_k(x_k) = \arg\min_{f_k \in \mathcal{C}_v} \E \Big( g(X) - f_k(X_k) \Big)^2$ be the best convex and concave univariate approximation respectively.
+
+Then, $f^c_k = 0$ and $f^v_k = 0$ iff $g^*_k(x_k) = \E[ g(X) \given x_k ] = 0$.
+\end{proposition}
+
+\begin{proof}
+
+First, we will establish that $g^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} g^*_k(x_k)$ is lower bounded.
+
+\begin{align*}
+g^*_k(x_k) &= \E[ g(X) \given x_k] \\
+  &= \int_{x_{-k}} g(x) p(x \given x_k) \\
+\partial^2_{x_k} g^*_k(x_k) &= \int_{x_{-k}} g''(x) p(x \given x_k) +
+  2 g'(x) p'(x \given x_k) + g(x) p''(x \given x_k) dx_{-k} 
+\end{align*}
+
+The first term $g''(x) p(x \given x_k)$ is strictly positive.
+By assumption, the remaining terms are continuous and hence bounded on a compact set.
+$\partial^2_{x_k} g^*_k(x_k)$ is therefore lower bounded.\\
+
+Before proceeding, we also note that because $\E g(X) = 0$, it must be that $\E g^*_k(X_k) = 0$.
+
+Now suppose $f^x_k = 0$ and $f^v_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
+\[
+\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( g(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
+\]
+Since optimal $c^* = \frac{\mathbb{E} [ g(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
+we know $\mathbb{E} [ g(X) X_k^2 ] = 
+\mathbb{E} \Big[ \mathbb{E}[ g(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
+
+Because $\partial^2_{x_k} g^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $g^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
+\[
+\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( g(X) 
+       - c (g^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
+\]
+Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
+            g^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
+        \big( g^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
+\begin{align*}
+\mathbb{E}[ g(X) \big( g^*_k(X_k) + \alpha X_k^2 \big) ] &= 
+\mathbb{E}[ g(X) g^*_k(X_k) ] \\
+& = \mathbb{E}\Big[ \mathbb{E}[g(X) | X_k]  g^*_k(X_k) \Big] \\
+& = \mathbb{E} g^*_k(X_k)^2 = 0
+\end{align*}
+Therefore, $g^*_k(x_k) = 0$.
+
+\end{proof}
+
+\newpage
 \section{2/7/2014}

### 2014-03-22 code/SCAM_QP.m

@@ -27,6 +27,7 @@ while iter < maxit && change > tol
         %disp('old')
         [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK(res,X(d,:),lambda);
 
+        
         %[Xd, ord] = sort(X(d,:));
         %'test'
         %diff_magn = norm(z(d,:)-z2(d,:))/norm(z(d,:));

### 2014-03-22 code/additive_counterexample.m

@@ -1,3 +1,4 @@
+% Produces mesh-plot of egg carton and tilting slope
 
 x1 = (0:1:3e1)/3e1;
 x2 = (0:1:3e1)/3e1;
@@ -26,14 +27,16 @@ figure;
 mesh(x1,x2,Y);
 colormap(copper);
 
+% Verify that these are unfaithful via simulation
+
 n=5000;
-Xs = [rand(n,1), 2*rand(n,1)-1];
+Xs = [2*rand(n,1)-1, 2*rand(n,1)-1];
 Ys = Xs(:,1).*Xs(:,2);
 [beta,z,obj] = SCAM_QP(Xs', Ys, 0.001, 100, 1e-5);
 
 
 n=5000;
-Xs = [rand(n,1), rand(n,1)];
+Xs = [2*rand(n,1)-1, 2*rand(n,1)-1];
 Ys = sin(Xs(:,1)*(2*pi)).*sin(Xs(:,2)*(2*pi));
 [beta,z,obj] = SCAM_QP(Xs', Ys, 0.001, 100, 1e-5);
 

### 2014-04-18 tex/discussion_notes.tex
paper update

@@
 %\xyoption{pdf}
+
+\mathchardef\mh="2D
 
@@
 
+$Y'_i = Y_i - \hat{f}(X_i) = f_0(X_i) + w_i - \hat{f}(X_i)$. Both $f_0(X_i)$ and $\hat{f}(X_i)$ are bounded by $2 sLb$.
+
+For a single $w_i$, we know that with probability at least $1-\delta$, $|w_i| \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta} }$.
+Therefore, taking an union bound and setting $\delta = 1/n$, we have that $\max_i |w_i| \leq \mathbf{c} \sigma \sqrt{\log n} $ with probability at least $1 - \frac{1}{n}$.
+
+Putting this together, $\| Y' \|_\infty \leq \mathbf{c}(sLb + \sigma\sqrt{\log n}) \leq
+ \mathbf{c} sLb \sigma\sqrt{\log n}$.\\
+
+Now, we also need to bound the mean of $Y'$:
+
+\begin{align*}
+&\frac{1}{n} \sum_{i=1}^n f_0(X_i) + w_i - \hat{f}(X_i) \\
+=& \frac{1}{n} \sum_{i=1}^n f_0(X_i) + w_i 
+\end{align*}
+The first mean $\frac{1}{n} \sum_{i=1}^n f_0(X_i)$ is the average of $n$ bounded zero-mean random variables since $| f_0(X_i) | \leq 2 s L b$.
+Therefore, the first term is at most $ sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}$ with probability at least $1-\delta$.
+
+The second mean is the average of $n$ subgaussian random variables with subgaussian scale $\sigma$. Therefore, the second term is at most $\sigma\sqrt{\frac{1}{n} \log \frac{2}{\delta}}$.
+
+The mean of $Y'$ is therefore at most $\mathbf{c} (sLb + \sigma) \sqrt{ \frac{1}{n} \log n}$ with probability at least $1 - \frac{1}{n}$.
+
+By Serfling and union bound, with probability at least $1-\frac{1}{n}$, we have that the deviation for all $i$
+\begin{align*}
+\Big| \frac{1}{n} \mathbf{1}_{i:n}^\tran Y' \Big| &\leq \mathbf{c} sLb\sigma \sqrt{\log n} 
+\sqrt{\frac{1}{n} \log 2np} + \mathbf{c} (sLb + \sigma) \sqrt{\frac{1}{n} \log np}\\
+  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log n \log np }
+\end{align*}
+
+Plugging this in and plugging in $\lambda > \mathbf{c} sLb \sigma \sqrt{
+  \frac{1}{n} \log n \log np}$, we have that:
+
+\begin{align*}
+\frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran Y' 
+   + \lambda (X_{kn} - X_{kj})a &\geq 
+ \lambda (X_{kn} - X_{kj}) a 
+    - \sum_{i'>j}\mathsf{gap}_{i'} \mathbf{c} sLb\sigma \sqrt{\frac{1}{n} \log n \log np} \\
+&\geq \lambda (X_{kn} - X_{kj}) a - (X_{kn} - X_{kj}) 
+    \mathbf{c} s Lb \sigma \sqrt{\frac{1}{n} \log n \log np} \\
+&\geq 0 
+\end{align*}
+
+\newpage
 \subsection{False Negative Analysis}
@@
 
+\subsubsection{Notation}
+
+Where $f : \R^p \rightarrow \R$, we let $\| f \|_P \equiv \E f(X)^2 $.
+
 \subsubsection{Preliminary}
@@
 
-Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
+\begin{itemize}
+
+\item Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
 Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions.
@@
 
-Define $\mathcal{C}^s$ as the set of convex additive functions
+\item Define $\mathcal{C}^s$ as the set of convex additive functions
 \[
@@
 \]
-We will also define classes of bounded and Lipschitz convex additive functions. 
+\item We will also define classes of bounded and Lipschitz convex additive functions. 
 \begin{align*}
@@
 
-Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
-\[
-f^* = \arg\min_{f \in \mathcal{C}^s} \E \Big( f_0(X) - f^*(X) \Big)^2
-\]
-
-We let $B$ be an upper bound on $\|f_0\|_\infty$ and $\| f^* \|_\infty$ and let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.
-
-In the finite sample context where we have $n$ samples $x_1, ..., x_n$, we will abuse notation and let $y, f_0, f^*, w$ denote their de-meaned counterpart, that is, $f_0$ is an $n$-dimensional vector whose coordinate $i$ is $f_0(x_i) - \frac{1}{n} \sum_i f_0(x_i)$.
-
-We define $\hat{f}$ as the empirical risk minimizer:
+\item Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
+\[
+f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f^* \|_P^2
+\]
+
+\item We let $B$ be an upper bound on $\|f_0\|_\infty$ and $\| f^* \|_\infty$ and let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.
+
+\item We define $\hat{f}$ as the empirical risk minimizer:
 \[
@@
 
-We also define $\hat{f}^*$ as the noiseless empirical risk minimizer:
+\item We also define $\hat{f}^*$ as the noiseless empirical risk minimizer:
 \[
@@
 
-\subsubsection{Proof}
-
-We start from the definition.
+\item For $k \in \{1,...,s\}$, define $g^*_k$ to be decoupled concave population risk minimizer
+\[
+g^*_k \equiv \min_{g_k \in \mh \mathcal{C}} \| f_0 - f^*_{-k} - g_k \|_P^2
+\]
+In our proof, we will analyze $g^*_k$ for $k$'s such that $f^*_k = 0$.
+
+\item Also, we define the noiseless empirical version:
+\[
+\hat{g}^*_k \equiv \min_{g_k \in \mh \mathcal{C}_L} \| f_0 - f^*_{-k} - g_k \|_n^2
+\]
+
+\item Likewise, we define the empirical version
+\[
+\hat{g}_k \equiv \min_{g_k \in \mh \mathcal{C}_L} \| y - \hat{f} - g_k \|_n^2
+\]
+By the definition of the ACDC procedure, $\hat{g}_k$ exist only for $k$ that have zero in their convex additive approximation.
+
+\end{itemize}
+
+\newpage
+\subsubsection{Proof outline}
+
+The \textbf{final step} is to show the following:
+\begin{align*}
+\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
+\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P \quad \trm{for all $k \in \{1,...,s\}$ where $f^*_k = 0$}
+\end{align*}
+where the difference is a term that decreases with $n$.
+
+Suppose $\hat{f}_k = 0$ and $f^*_k \neq k$, then for large enough $n$, there must be a contradiction because $\| f_0 - f^* \|_P > \| f_0 - f^{*(s-1)} \|_P$. We would have a contradiction.
+
+Suppose $f^*_k = 0$, then $g^*_k \neq 0$. We would have another contradiction.
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+Concavity, \textbf{removing} sample-dependent convex fucntions.\\
+
+For arbitrary function $g$, we have the following:
+\begin{align*}
+\| f_0 - \hat{f} - g \|_n = \| f_0 - \hat{f} + f^* - f^* - g \|_n 
+   & \leq \| f_0 - f^* -g \|_n
+       + \| \hat{f} - f^* \|_n \\
+   &\geq \| f_0 - f^* - g \|_n - \| \hat{f} - f^* \|_n 
+\end{align*}
+
+Therefore:
+\begin{align*}
+\| f_0 - f^* - g \|_n^2 - 2 \| f_0 - f^* - g\|_n \| \hat{f} - f^* \|_n \leq
+  \| f_0 - \hat{f} - g \|_n^2 \leq
+  \| f_0 - f^* -g \|_n^2 + 2 \| f_0 - f^* - g \|_n \| \hat{f} - f^* \|_n 
+\end{align*}
+
+The radius of approximation is $2 \| f_0 - f^* - g \|_n \| \hat{f} - f^* \|_n$, which we need to upper bound. $\| f_0 - f^* - g \|_n \leq \mathbf{c} sLb$.
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+We \textbf{start} from the definition. We don't need to force $y$ to be zero-mean.
 
@@
 
+The $\| f_0 - \hat{f} \|_n^2 - \| f_0 - \hat{f}^* \|_n^2$ term is always positive. We want to lower bound the second term with a negative quantity.
+
+One way to proceed:
+$\| \hat{f}^*_k \|_\infty \leq 2bL$. And because $\hat{f}^*$ minimizes
+
+\textbf{Note:}
+The $\hat{f}^*$ here could be any function that does depend on the noise.
+The advantage of having $\hat{f}^*$ is that $\| f_0 - \hat{f} \|_n^2 - \| f_0 - \hat{f}^* \|_n^2 \geq \| \hat{f} - \hat{f}^* \|_n^2$.
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Continuation from start}.
+Taking the \textbf{start} derivation and instead of comparing against $\hat{f}^*$, we will instead compare against $f^*$ (de-meaned).
+
+Since the samples $X_1, ..., X_n$ are clear from context, we denote $\bar{f}^*$ as $\frac{1}{n} \sum_{i=1}^n f^*(X_i)$.
+
+All parts still work and we get down to the following inequality:
+\begin{align*}
+\| f_0 - \hat{f} \|_n^2 - \|f_0 - f^* + \bar{f}^* \|_n^2 &\leq 
+      2 | \langle w, \hat{f} - f^* + \bar{f}^* \rangle | + \lambda 2sLb \\
+  &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} \log 4n } + 
+   \lambda 2 s L b
+\end{align*}
+with probability at least $1-\frac{1}{n}$.\\
+
+We use the \emph{centering effect} analysis. Since with high probability ($1-\frac{1}{n}$) 
+\[
+\|f_0 - \hat{f}\|_n^2 - 
+  \Big( \|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log 4n \Big) \leq 
+\|f_0 - \hat{f} \|_n^2 - \|f_0 - f^* + \bar{f}^*\|_n^2
+\]
+Therefore, with probability at least $1-\frac{2}{n}$,
+\begin{align*}
+\|f_0 - \hat{f}\|_n^2 - \|f_0 -f^*\|_n^2 &\leq \mathbf{c}(sLb)^2 \frac{1}{n} \log 4n
+      + \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log 4n } + \lambda 2 sLb \\
+ &\leq \mathbf{c} (Lb)^2\sigma \sqrt{\frac{s^4}{n} \log 4n} + \lambda 2 sLb
+\end{align*}
+
+Now, we use the the \emph{uniform convergence} result. With probability at least $1-\frac{3}{n}$
+
+\begin{align*}
+\| f_0 - \hat{f}\|_P^2 - \| f_0 - f^*\|_P^2 & \leq
+   \mathbf{c} (Lb)^2 \sigma \sqrt{\frac{s^4}{n} \log 4n} + \lambda 2 s Lb +
+   \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 2n} \\
+ &\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 s Lb
+\end{align*}
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{f convergence}.
+
+Here, our goal is to bound $\| \hat{f} - f^* \|_n^2$.
+
+Since $f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f \|_P^2$, we have that
+\begin{align*}
+\|f^* - \hat{f} \|_P^2 &\leq \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 \\
+ &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2s Lb
+\end{align*}
+
+Now, by \emph{uniform convergence} again, we have:
+
+\[
+\| f^* - \hat{f} \|_n^2 \leq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 4n} + 
+      \mathbf{c} \lambda s L b
+\]
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Centering Effect}
+
+Here, we bound the difference of $\| f_0 - f^* + \bar{f}^* \|_n^2$ and $\| f_0 - f^* \|_n^2$.
+
+\begin{align*}
+\| f_0 - f^* + \bar{f}^* \|_n^2 &= \| f_0 - f^* \|_n^2 
+    + 2 \langle f_0 - f^*, \bar{f}^* \rangle + \bar{f}^{*2} \\
+  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \langle f_0 - f^*, \mathbf{1} \rangle_n + 
+    \bar{f}^{*2} \\
+  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \bar{f}_0 - \bar{f}^{*2}
+\end{align*}
+
+$\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 s L b \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.
+
+The same reasoning likewise applies to $\bar{f}_0 = \frac{1}{n} \sum_{i=1}^n f_0(X_i)$.
+
+Taking a union bound and letting $\delta = \frac{1}{n}$, we have that, with probability at least $1- \frac{1}{n}$,
+
+\begin{align*}
+| \bar{f}^* | | \bar{f}_0 | &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n \\
+\bar{f}^{*2} &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n
+\end{align*}
+
+Therefore, with probability $1-\frac{1}{n}$,
+\[
+\|f_0 - f^*\|_n^2 - \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n \leq
+    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
+\|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n
+\]
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Denoising}
+
+Here we outline how to bound $\langle w, \hat{f} - \hat{f}^* \rangle$ where $\hat{f}^*$ can be any function that doesn't depend on $w$.
+
+We suppose that both $\hat{f}, \hat{f}^*s \in \mathcal{C}^s_L$.
+
+By Bronshtein, we know that:
+\begin{align*}
+\log N_\infty(\epsilon, \mathcal{C}_L^1) &= C bL \epsilon^{-1/2} \\
+\log N_\infty(\epsilon, \mathcal{C}_L^s) &= C sbL s^{1/2} \epsilon^{-1/2} 
+\end{align*}
+
+Clearly, the covering number would not change if we center the set $\mathcal{C}_L^s$ around $\hat{f}^*$, call this $\mathcal{G}$. The difference $\hat{f} - \hat{f}^* \in \mathcal{G}$
+
+For all $h \in \mathcal{G}$:
+\begin{align*}
+|\langle w, h \rangle_n | &= |\langle w, h - h_\epsilon \rangle_n | 
+     + |\langle w, h_\epsilon \rangle_n | \\
+ &\leq \frac{1}{n} \| w \|_1  \epsilon + |\langle w, h_\epsilon \rangle_n \| 
+\end{align*}
+
+Therefore
+\[
+\sup_{g \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
+      \frac{1}{n} \|w\|_1 \epsilon + 
+      \sup_{h_\epsilon \in \mathcal{G}_\epsilon} | \langle w, h_\epsilon \rangle_n |
+\]
+
+The final goal is to show that $\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
+\textrm{constants} \cdot \sqrt{\frac{1}{n^{4/5}}}$.
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Chaining}.
+
+Our goal is to give a precise bound for $\sup_{h \in \mathcal{G}} | \langle w, h \rangle|$.
+
+We first restate the chaining theorem. Suppose $\| g \|_n \leq R$ for all $g \in \mathcal{G}$.
+
+Suppose $\epsilon > \frac{1}{\sqrt{n}}\sigma \mathbf{c} \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R $. 
+Then we have that
+\[
+P\Big( \sup_{g \in \mathcal{G}} \langle w, g \rangle_n \geq \epsilon \Big) \leq
+  4 \exp \Big( - \frac{ n \epsilon^2}{ \mathbf{c} R^2 \sigma^2} \Big)
+\]
+In our case, $R \leq sLb$.
+
+Restated, we have that, with probablity at least $1-\delta$,
+\[
+\sup_{g \in \mathcal{G}} | \langle w, g \rangle_n | \leq 
+   \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
+      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
+       \mathbf{c} \sigma \sqrt{\frac{1}{n}} 
+\]
+
+Now we evaluate the integral. Since $N_2(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_2(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.
+
+\begin{align*}
+\int_0^R \sqrt{\log N_2(t, \mathcal{G})} dt &\leq 
+      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
+ &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
+ &= \sqrt{C s^{1.5} b L} \, \mathbf{c} (sLb)^{3/4} \\
+ &\leq \mathbf{c} (s b L)^2
+\end{align*}
+
+Coming back, we have, with probability at least $1-\delta$,
+\begin{align*}
+\sup_{g \in \mathcal{G}} | \langle w, g \rangle | &\leq 
+    \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
+    \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
+ &\leq \mathbf{c} (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
+\end{align*}
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Uniform convergence}:
+
+The goal is to bound 
+$\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big|$. \\
+
+Again, let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_L - f_0$.
+
+First, note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s b L$.
+
+Because $\| h \|_n = \| h - h_\epsilon + h_\epsilon \|_n$, we have that
+\begin{align*}
+\|h_\epsilon \|_n - \| h - h_\epsilon \|_n &\leq 
+    \| h \|_n \leq \|h_\epsilon \|_n + \| h - h_\epsilon \|_n \\
+\|h_\epsilon \|_n - \epsilon &\leq 
+    \| h \|_n \leq \|h_\epsilon \|_n + \epsilon  \\
+\| h_\epsilon \|^2_n - 8 \epsilon (s L b)  &\leq \| h  \|^2_n  \leq
+   \| h_\epsilon \|_n^2 + 8 \epsilon (s L b) 
+\end{align*}
+where we used the fact that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$ and $ \| h_\epsilon \|_n \leq \| h_\epsilon \|_\infty \leq 4 s L b$.
+
+And likewise:
+\begin{align*}
+\| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
+   \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
+\end{align*}
+
+Therefore, 
+\begin{align*}
+\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+        + \epsilon (16 sLb)
+\end{align*}
+
+Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
+\begin{align*}
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+  (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
+&\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
+\end{align*}
+
+We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$ and $\delta = \frac{1}{n}$. 
+Therefore:
+\begin{align*}
+\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + s n^{1/5}  \big) } \\
+  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log 2n }
+\end{align*}
+And
+\begin{align*}
+\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
+  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log 2 n}
+     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
+  &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 2n}
+\end{align*}
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+\textbf{Concavity start}.
+
+We start from the very beginning, where $\hat{g}_k$ is defined as $\min_{g_k \in \mathcal{C}^1_L} \| y - \hat{f} - g_k \|_n^2 + \lambda \| g_k \|_\infty$.
+
+\begin{align*}
+\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
+   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
+\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2 Lb \\
+ &\\
+\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
+   +\lambda 2 Lb \\
+\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
+   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2Lb
+\end{align*}
+
+Using the chaining result, setting $s=1$, we have, with probability at least $1-\delta$,
+\begin{align*}
+\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
+  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
+\end{align*}
+
+Setting $\delta = 1/n$, using \emph{uniform convergence}, we have
+\begin{align*}
+\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
+  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log 4n }+ \lambda 2 Lb +
+  \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 2n } \\
+ &\leq \mathbf{c}(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 Lb
+\end{align*}
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
+Now comes \textbf{concavity removal version 2}.
+
+The goal is to bound radius of approximation between $\| f_0 - \hat{f} - g^*_k \|_P^2$ and $\| f_0 - f^* - g^*_k \|_P^2$ and likewise for $\hat{g}_k$.
+
+\begin{align*}
+\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
+    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
+   + 2 \langle f_0 - f^*, g^*_k \rangle \\
+ &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb + 
+    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
+ &\leq  \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb + 
+    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
+&\leq  \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb +
+   \mathbf{c} 2Lb \sqrt{ (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2sLb} 
+\end{align*}
+
+The same bound likewise holds for $\hat{g}_k$.
+
+\rule{5cm}{0.4pt}
+\vspace{0.2in}
+
 \newpage
-
 \section{2/15/2014}

### 2014-04-18 tex/scam/additive_faithful.tex
lots of changes
paper update

@@
 \label{lem:general_int_reduction}
-Let $F$ be a distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
+Let $F$ be a distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function。
 
 Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq 
-\arg\min \{ \E \big( f(X) - \sum_{k=1}^s f_k(X_k) - \mu \big)^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
+\arg\min \{ \E \big( f(X) - \sum_{k=1}^s f_k(X_k) - mu \big)^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
 
@@
 
+If $f$ is differentiable, then $f$ depends on $k$ if $\partial_{x_k} f \neq 0$ with probability greater than 0.\\
+
 Suppose we have the additive approximation:
 \begin{equation}
+\label{eqn:unconstrained_additive}
 f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
@@
 Fix $k$.
-Using the result of Lemma~\ref{lem:general_int_reduction}, we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ implies that $f$ does not depend on coordinate $k$.\\
+Using the result of Lemma~\ref{lem:general_int_reduction}, we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ implies that $f$ does not depend on coordinate $k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ for all $\mathbf{x}$.\\
 
@@
 
-Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:
+$f$ thus does not depend on $x_k$.
+% Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:
 
-\begin{align*}
-\forall \mathbf{x}_{-k}, f(x'_k, \mathbf{x}_{-k}) & \leq f(x_k, \mathbf{x}_{-k}) 
-  + f'(x_k, \mathbf{x}_{-k}) ( x'_k - x_k) \\ 
-f(x'_k, \mathbf{x}_{-k}) &\leq f(x_k, \mathbf{x}_{-k}) \\
-\forall \mathbf{x}_{-k}, f(x_k, \mathbf{x}_{-k}) & \leq f(x'_k, \mathbf{x}_{-k}) 
-  + f'(x'_k, \mathbf{x}_{-k}) ( x_k - x'_k) \\ 
-f(x_k, \mathbf{x}_{-k}) &\leq f(x'_k, \mathbf{x}_{-k})
-\end{align*}
+% \begin{align*}
+% \forall \mathbf{x}_{-k}, f(x'_k, \mathbf{x}_{-k}) & \leq f(x_k, \mathbf{x}_{-k}) 
+%   + f'(x_k, \mathbf{x}_{-k}) ( x'_k - x_k) \\ 
+% f(x'_k, \mathbf{x}_{-k}) &\leq f(x_k, \mathbf{x}_{-k}) \\
+% \forall \mathbf{x}_{-k}, f(x_k, \mathbf{x}_{-k}) & \leq f(x'_k, \mathbf{x}_{-k}) 
+%   + f'(x'_k, \mathbf{x}_{-k}) ( x_k - x'_k) \\ 
+% f(x_k, \mathbf{x}_{-k}) &\leq f(x'_k, \mathbf{x}_{-k})
+% \end{align*}
 
-We thus have that $f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$ and all pairs $x_k, x'_k \in (0,1)$. This proves that $f$ does not depend on $x_k$.
+% We thus have that $f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$ and all pairs $x_k, x'_k \in (0,1)$. This proves that $f$ does not depend on $x_k$.
 \end{proof}
@@
 We can then let $X_3 = f(X_1, X_2) - f^*_1(X_1) - f^*_2(X_2)$, that is, we let $X_3$ exactly capture the additive approximation error, then the best additive approximation of $f$ would have a component $f^*_3(X_3) = X_3$ even though $f$ does not depend on $X_3$.
-This is, of course, unlikely to occur in practice and we leave as future work analysis under reasonable assumptions that rules out such psychotic phenomenon.
 \end{remark}
+
+\subsection{Convex Additive Model}
+
+Although convex functions are additively faithful, it is difficult to estimate the optimal additive functions $f^*_k$'s (as defined in equation~\ref{eqn:unconstrained_additive}) because $f^*_k$ need not be a convex function.
+
+Because the true regression function $f$ is convex, it is natural to consider an convex additive model:
+\begin{equation}
+\label{eqn:convex_additive}
+\{ f^*_k \}_{k=1}^s = \arg\min \Big \{ 
+    \E\big( f(X) - \sum_{k=1}^s f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
+\end{equation}
+where $\mathcal{C}^1$ is the set of univariate convex functions.
+
+The convex functions $f^*_k$'s are not additively faithful by themselves but faithfulness can be restored by coupling the $f^*_k$'s with a set of concave functions:
+\begin{equation}
+\label{eqn:concave_postprocess}
+g^*_k = \arg\min \Big\{
+   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 
+    \,:\, g_k \in \mh \mathcal{C}^1, \E g_k(X_k) = 0 
+  \Big\}
+\end{equation}
+
+\begin{theorem}
+\label{thm:acdc_faithful}
+Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary-points condition. Suppose that $f$ is convex and twice-differentiable.
+
+Suppose that $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$ are all continuous as functions on $C$.\\
+
+Then, $f^*_k = 0$ and $g^*_k = 0$ (as defined in equation~\ref{eqn:convex_additive} and equation~\ref{eqn:concave_postprocess}) implies that $f$ does not depend on $x_k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ with probability 1.
+\end{theorem}
+
+Theorem~\ref{thm:acdc_faithful} suggests a two-stage screening procedure for variable selection.
+We first fit a sparse \emph{convex} additive model and then, for every variable marked as irrelevant in the first stage, we allow ourself to change our mind by fitting an univariate \emph{concave} function.
+We refer to this procedure as AC/DC (additive convex / decoupled concave) and describe it in more details in section~\ref{sec:acdc}.
+
+\begin{proof} (of theorem~\ref{thm:acdc_faithful}) \\
+Fix $k$. Let $f^*_k, g^*_k$'s be defined as equation~\ref{eqn:convex_additive} and equation~\ref{eqn:concave_postprocess}.
+
+By definition of $f^*_k$ and $g^*_k$, we have that:
+\begin{align*}
+f^*_k &= \arg\min_{f_k} \Big\{
+   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 
+    \,:\, f_k \in  \mathcal{C}^1,\, \E f_k(X_k) = 0 
+  \Big\} \\
+g^*_k &= \arg\min_{g_k} \Big\{
+   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 
+    \,:\, g_k \in \mh \mathcal{C}^1,\, \E g_k(X_k) = 0 
+  \Big\}
+\end{align*}
+
+Therefore, $f^*_k = 0$ and $f^*_k = 0$ implies that $\E[ f(X) - \sum_{k'\neq k} f^*_{k'}(X_{k'}) \given x_k] = 0$.
+
+Now we use corollary~\ref{cor:faithfulness_extension}. We let $\phi(\mathbf{x}_{-k}) = f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that $f$ does not depend on $x_k$. 
+\end{proof}
+
+\begin{corollary} 
+\label{cor:faithfulness_extension}
+Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary-points condition.
+
+For any function $\phi(X_{-k})$ that does not depend on $X_k$:
+ \begin{align*}
+f^*_k(x_k) &= \arg\min_{f_k} \mathbb{E} \Big( f(X) 
+           - \phi(X_{-k}) - f_k(X_k) \Big)^2 
+      = \mathbb{E}\Big[ f(X) - \phi(X_{-k}) \,|\, x_k\Big] 
+\end{align*}
+We have that $ f^*_k = 0 \Rightarrow \partial_{x_k} f(x) = 0$.
+\end{corollary}
+
+\begin{proof}
+In the proof of theorem~\ref{thm:convex_faithful}, the only property of $r(\mathbf{x}_{-k})$ we used was the fact that $\partial_{x_k} r(\mathbf{x}_{-k}) = 0$.
+Therefore, the proof here is identical to that of theorem~\ref{thm:convex_faithful} except we let $\phi(\mathbf{x}_{-k})= r(\mathbf{x}_{-k}).$
+\end{proof}
+
+\begin{proposition}
+\label{prop:shape_approx_univariate}
+Let $C \subset \R^p$ be a compact set and let $h : C \rightarrow \R$.
+Let $p(x)$ be a positive density on $C$ and suppose $\E h(X) = 0$.
+Suppose that $\partial_{x_k} h(x)$, $\partial_{x_k} p( x \given x_k)$, and $\partial^2_{x_k} p( x \given x_k )$ are all continuous as functions on $C$.
+Suppose that $\partial^2_{x_k} h(x) \geq 0$.
+
+Let 
+\begin{align*}
+f^*_k(x_k) &= \arg\min_{f_k} \Big\{
+   \E \Big( h(X) - f_k(X_k) \Big)^2 \,:\, f_k \in \mathcal{C}^1,\, \E f_k = 0 \Big\} \\
+g^*_k(x_k) &= \arg\min_{g_k} \Big \{
+   \E \Big( h(X) - g_k(X_k) \Big)^2 \,:\, g_k \in \mh \mathcal{C}^1 ,\, \E g_k = 0 \Big\}
+\end{align*}
+be the best convex and concave univariate approximation respectively.\\
+
+Then, $f^*_k = 0$ and $g^*_k = 0$ iff $h^*_k(x_k) \equiv \E[ h(X) \given x_k ] = 0$.
+\end{proposition}
+
+\begin{proof}
+
+First, we will establish that $h^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded.
+
+\begin{align*}
+h^*_k(x_k) &= \E[ h(X) \given x_k] \\
+  &= \int_{x_{-k}} h(x) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
+\partial^2_{x_k} h^*_k(x_k) 
+  &= \int_{\mathbf{x}_{-k}} h''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) +
+  2 h'(x) p'(\mathbf{x}_{-k} \given x_k) + h(x) p''(\mathbf{x}_{-k} \given x_k) 
+  d\mathbf{x}_{-k} 
+\end{align*}
+
+The first term $h''(x) p(\mathbf{x}_{-k} \given x_k)$ is strictly positive.
+By assumption, the remaining terms are continuous and hence bounded on a compact set.
+$\partial^2_{x_k} h^*_k(x_k)$ is therefore lower bounded.
+Before proceeding, we also note that because $\E h(X) = 0$, it must be that $\E h^*_k(X_k) = 0$.
+
+Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
+\[
+\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
+\]
+Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
+we know $\mathbb{E} [ h(X) X_k^2 ] = 
+\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
+
+Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
+\[
+\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
+       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
+\]
+Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
+            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
+        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
+\begin{align*}
+\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
+\mathbb{E}[ h(X) h^*_k(X_k) ] \\
+& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
+& = \mathbb{E} h^*_k(X_k)^2 = 0
+\end{align*}
+Therefore, $h^*_k(x_k) = 0$.
+
+\end{proof}
 

### 2014-04-18 tex/scam/appendix.tex
paper update

--- 2013-11-01 tex/scam/appendix.tex
@@
 \section{Appendix}
-
-\subsection{Proof of Additive Faithfulness}
-\label{sec:faithful_proof}
-
-We start with a proof of Lemma~\ref{lem:general_int_reduction}. We restate the lemma here for convenience.
-
-\begin{lemma}
-Let $F$ be a product distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function.
-
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
-
-Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
-\end{lemma}
-
- \begin{proof}
-
-Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
-
-We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
-This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.
-\\
-
-We now turn our attention toward the $f^*_k$'s.
-
-It must be then that $f^*_k$ minimizes $\{ \E | f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k)|^2 \,:\, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
-
-Fix $x_k$, we will show that the value $\E[ f(X) | x_k] - \mu^*$, for all $x_k$,  uniquely minimizes 
-\[
-\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
-         \big| f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k) -\mu^*\big|^2 
-                 d \mathbf{x}_{-k}.
-\]
-It easily follows then that the function $x_k \mapsto \E[ f(X) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.
-
-Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
-\begin{align*}
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
-  \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
-      ( f(\mathbf{x})-\sum_{k' \neq k} f^*_{k'}(x_{k'})-\mu^*) d \mathbf{x}_{-k} \\  
-p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(x_k)
-     p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})-\mu^*) 
-              d \mathbf{x}_{-k} \\
-f_k(x_k) &= \int_{\mathbf{x}_{-k}} 
-       p(\mathbf{x}_{-k}) (f(\mathbf{x}) -\mu^*) d \mathbf{x}_{-k} 
- \end{align*}
-Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption.
-The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.
-
-The square error objective is strongly convex.
-The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
-Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.
-
-Now, we note that as a function of $x_k$, $\E[ f(X) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
-
- \end{proof}
-
-Our reasoning actually proves something stronger. It proves the following lemma:
-
-\begin{lemma}
-\label{lem:additive_component}
-
-$f^*_k(x_k) = \E[ f(X) | x_k] - \mu^*$ is the unique optimal solution to 
-\[
-min_{f_k} \{ \E\Big( f(X) - \E f(X) - \sum_{k'\neq k} f_{k'}(X_{k'}) - f_k (X_k)\Big)^2 
-                    \,:\, \E f_k(X_k) = 0 \}
-\]
-for \emph{any} set of component functions $\{ f_{k'} \}_{k'\neq k}$ that satisfies $\E f_{k'}(X_{k'}) = 0$.
-\end{lemma}
-
-The next lemma adapts Lemma~\ref{lem:general_int_reduction} to convex functions.
-
-\begin{lemma}
-\label{lem:int_reduction}
-Let $F$ be a product distribution on $C=[0,1]^s$ with positive density function $p$. Let $f: C \rightarrow \R$ be a convex function.
-
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq \arg\min \{ \E | f(X) - \sum_{k=1}^s f_k(X_k) - \mu |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0\}$
-
-Then $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and $\mu^* = \E f(X)$ and this solution is unique.
-\end{lemma}
-
-\begin{proof}
-The proof is identical to that of Lemma~\ref{lem:general_int_reduction}. We need only verify that $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ is convex.
-
-This is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.
-\end{proof}
-
- The next proposition, combined with Lemma~\ref{lem:int_reduction}, proves Theorem~\ref{thm:convex_faithful}.
-
-\begin{proposition}
-\label{prop:faithful_condition}
-Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.
-
-Let $f^*_1,...,f^*_s \coloneqq \arg\min \{ \E | f(X) -\E f(X) - \sum_k f_k(X_k) |^2 \,:\, \forall k, f_k \trm{ convex }, \E f_k(X_k) = 0 \}$.
-
-The following are equivalent:
-\begin{packed_enum}
-\item $f$ does not depends on coordinate $k$
-\item For all $x_k$, $\E[ f(X) | x_k] = \E f(X) $.
-\end{packed_enum}
-\end{proposition}
-
-\begin{proof}
-
-The first condition trivially implies the second.
-
-Fix $k$. Suppose that, for all $x_k$, $\E[ f(X) | x_k] = \E f(X)$.
-
-Because we assume that $p(\mathbf{x}) = \prod_k p(x_k)$, we see that, for all $x_k$,
-\begin{align*}
- \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} = \E f(X)
-\end{align*}
-
-For every $\mathbf{x}_{-k}$, we define the derivative
-\[
-g(\mathbf{x}_{-k}) \coloneqq  \lim_{x_k \rightarrow 0^+} \frac{f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k})}{x_k}
-\]
-$g(\mathbf{x}_{-k})$ is well-defined by the assumption that $f$ is everywhere differentiable.
-
-We now describe two facts about $g$.
-
-Fact 1. By exchanging limit with the integral, which is valid by bounded convergence theorem, we reason that 
-\[
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) g(\mathbf{x}_{-k}) d \mathbf{x}_{-k} = 0
-\]
-
-Fact 2.
-Because $f$ is convex, $g(\mathbf{x}_{-k})$ is a component of the subgradient $\partial_{\mathbf{x}} f(0, \mathbf{x}_{-k})$.
-(the subgradient coincides with the gradient by assumption that $f$ is twice differentiable)
-
-Therefore, using the first order characterization of a convex function, we have
-\begin{align*}
-f(\mathbf{x}') &\geq f( \mathbf{x}) + \partial_{\mathbf{x}} f(\mathbf{x})^\tran (\mathbf{x}' - \mathbf{x}) \quad \trm{ for all } \mathbf{x}', \mathbf{x} \\
-f(x_k, \mathbf{x}_{-k}) &\geq f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k \quad \trm{ for all } x_k, \mathbf{x}_{-k}
-\end{align*}
-
-For all $x_k, \mathbf{x}_{-k}$, 
-\[
-f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k \geq 0
-\]
-and
-\[
-\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) (f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k) d\mathbf{x}_{-k} = 0
-\]
-Since $f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k$ is a continuous function of $\mathbf{x}_{-k}$ and the density $p(\mathbf{x}_{-k})$ is, by assumption, non-zero on the support, we conclude that for all $x_k, f(x_k, \mathbf{x}_{-k}) - f(0, \mathbf{x}_{-k}) - g(\mathbf{x}_{-k}) x_k =0 $ necessarily and thus for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k}) + g(\mathbf{x}_{-k}) x_k$.
-
-The Hessian of $f$ then (guaranteed to exist by assumption) has a zero on the $k$-th main diagonal entry.
-
-By proposition 7.1.10 from Horn and Johnson~\cite{HJ90},  such a matrix is positive semidefinite if and only if the $k$-th row and column are also zero.
-(to prove this, one can first work with a 2 by 2 matrix and then use the fact that every principal submatrix of a PSD matrix must be PSD)
-
-Since $k$-th row and column correspond precisely to the gradient of $g(\mathbf{x}_{-k})$, we conclude that $g$ must be a constant function.
-It follows therefore that $g = 0$ because it integrates to 0.
-
-So we have that for all $x_k, \mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k}) = f(0, \mathbf{x}_{-k})$, which concludes our proof.
-
-\end{proof}
 
@@
 \begin{theorem} 
-The following holds regardless of whether we impose the boundedness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.
+The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.
 
-For $k \in \{1,...,p\}$, let $\Delta_{k, j}$ denote the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$.
+Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
+Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\
 
-Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression optimization program~\ref{opt:alternate_opt}. 
-Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
+Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
+\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\
 
-Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residual.
-
-Suppose for all $j=1,...,n, k\in S^c$, $\lambda_n > | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$, then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
-
+Then the following are true:
+\begin{enumerate}
+\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}.
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
+\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
+\end{enumerate}
 \end{theorem}
@@
 \begin{proof} 
-We will omit the boundedness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.
+We will omit the Lipschitz constraint in our proof here. It is easy to add that in and check that the result of the theorem still holds.\\
 
-We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.\\
+We first consider the first item in the conclusion of the theorem.
 
-we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
+We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.\\
+
+The Lagrangian is
+\begin{equation}
+\label{eqn:full_lagrange}
+\mathcal{L}( \{ d_k \}, \nu) = 
+  \frac{1}{2n} \Big\| 
+    Y - \sum_{k=1}^p  \bar{\Delta}_k d_k  \Big\|_2^2 + 
+    \lambda \sum_{k=1}^p \| \bar{\Delta}_k d_k \|_\infty -
+    \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki} 
+\end{equation}
+with the constraint that $\nu_{ki} \geq 0$ for all $k,i$.
+
+Because $\{\hat{d}_k\}_{k \in S}$ is by definition the optimal solution of the restricted regression, it is a consequence that stationarity holds for $k \in S$, that is, $\partial_{ \{ d_k \}_{k \in S} } \mathcal{L}(d) = 0$, and that the dual variables $\nu_k$ for $k \in S$ satisfy complementary slackness.
+
+We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$.
+
+The Lagrangian form of the optimization, in term of just $d_k$, is
 \[
-\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 
-        + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| 
-        - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}_n^\tran\Delta_k d_k)
+\mathcal{L}(d_k, \nu_k) =
+  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
+  -  \bar{\Delta}_k d_k \big\|_2^2 
+   + \lambda \| \bar{\Delta}_k d_k\|_\infty
+  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
 \]
-where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^{n-1}$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n-1$.
+with the constraint that $v_i \geq 0$ for all $i$.
 
-First, note that by definition as solution of the restricted regression, for $k \in S$, $\hat{d}_k, \hat{c}_k$ satisfy stationarity with dual variables that satisfy complementary slackness.
+The derivative of the Lagrangian is:
+\begin{align*}
+\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
+        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
+      - \nu_k
+\end{align*}
+where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.
 
-Now, let us fix $k \in S^c$ and prove that $\hat{d}_k = 0, \hat{c}_k=0$ is an optimal solution.
+We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
 
 \begin{align*}
-\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k d_k 
-       + c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
-\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( r_k - \Delta_k d_k 
-       + c_k \mathbf{1}) + \gamma_k
+\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
+           - \nu_k = 0 
 \end{align*}
-In the derivatives, $\mathbf{u}_k$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.
+where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$.
+It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ hwere the inequality is element-wise.
 
-We now substitute in $d_k = \hat{d}_k = 0, c_k=\hat{c}_k=0, r_k = \hat{r}_k = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
+Let us reorder the samples so that the $i$-th sample is the $i$-smallest sample. \\
+
+We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for some $0 < a < 1/2$. (coordinates of $\mathbf{u}$ correspond to the new sample ordering) We then just need to show that
+\begin{align*}
+- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
+- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
+- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
+   \textrm{for each } j \\
+- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
+    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
+- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
+    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
+- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
+   + \lambda (X_{kn} - X_{kj})a &\geq 0 
+\end{align*}
+where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that:
 
 \begin{align*}
--\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u}_k 
-           - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
--\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
+- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
+   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
+- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
+- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0
 \end{align*}
-where $\mathbf{u}_k$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.
 
-First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
+The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way.
+
+The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is:
 \[
-\lambda \mathbf{u}_k - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
+\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
+  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
+  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki}
 \]
 
-Suppose
-\[
-\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
-\]
-then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n-1$.
+The exact same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
 
-Because we have strict inequality in the above equation, Lemma 1 from ~\cite{Wain:09a} show that all solutions must be zero on $S^c$.
 \end{proof}
@@
 \begin{theorem} 
-Suppose assumptions A1, A2, A3 hold.
+Suppose assumptions A1-A4 hold.
 
-Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j=1,...,n,k \in S^c$,
+Suppose $\lambda_n \geq \mathbf{c} s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
 \[
-\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
+\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
 \]
-And therefore, the solution to the optimization~\ref{opt:alternate_opt} is zero on $S^c$.
+
+And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\ref{opt:alternate_opt_concave} are zero.
 \end{theorem}
@@
 
-We remind the reader that $\Delta_{k,j} = \max(X_k, - X_{k(j)} \mathbf{1}_n, 0)$. Because $\hat{r}$ is empirically centered,
+Fix $j$ and $i$.
+$\hat{r}^\tran \mathbf{1}_{(i':n)}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$.
+We will then use Serfling's theorem on the concentration of measure of sampling without replacement.
+(corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.\\
+
+\textbf{Step 1}: Bounding $\| \hat{r} \|_\infty$.
+
+$\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where $\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex additive function outputted by the restricted regression.
+
+Both $f_0(x_i)$ and $\hat{f}(x_i)$ are coordinate-wise $L$-Lipschitz and therefore are bounded by $2 sLb$.
+
+Because $w_i$ is subgaussian, $|w_i| \leq \mathbf{c} \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.
+
+We now put this together and take another union bound across all $j$ and all $i'$:
+\begin{align*}
+\| \hat{r} \|_\infty &\leq \mathbf{c} (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
+      &\leq \mathbf{c} sLb \sigma \sqrt{\log \frac{2}{\delta}}
+\end{align*}
+with probability at least $1 - n^2 p \delta$. We supposed that both $sLb \geq 2$ and $\sigma\sqrt{\log \frac{2}{\delta}} \geq 2$.
+
+\textbf{Step 2}: Bounding $| \frac{1}{n} \hat{r}^\tran \mathbf{1} |$.
 
 \begin{align*}
-\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= 
-              \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n) 
-                                       - \frac{1}{n} \hat{r}^\tran \mathbf{1}_n X_{k(j)} \\
-                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n)
+\frac{1}{n} \hat{r}^\tran \mathbf{1} &= 
+    \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i - \hat{f}(x_i) \\
+  &= \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i \quad \trm{ ($\hat{f}$ is centered)}
 \end{align*}
-Our goal in this proof is to bound $\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})$ from above.
 
-\textbf{Step 1.} We first get a high probability bound on $\| \hat{r} \|_\infty$.
+Because $|f_0(x_i)| \leq sLb$, the first term $| \frac{1}{n} \sum_{i=1}^n f_0(x_i)|$ is at most $2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$ by Hoeffding Inequality.
+
+Because $w_i$ is subgaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $2 \sigma \sqrt{ \frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+
+Taking an union bound, we have that
 
 \begin{align*}
-\hat{r}_i &= Y_i - \bar{Y} -  \sum_{k \in S} \hat{f}_k (X_k^{(i)}) \\
-	&= f_0(X_S^{(i)}) + \epsilon_i - \bar{f_0} - \bar{\epsilon}- 
-                      \sum_{k \in S} \hat{f}_k(X_k^{(i)}) \\
-	&=  f_0(X_S^{(i)}) - \bar{f_0} - \sum_{k \in S} \hat{f}_k(X_k^{(i)}) 
-                   + \epsilon_i - \bar{\epsilon}
+| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
+  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
 \end{align*}
-Where $\bar{f_0} = \frac{1}{n} \sum_{i=1}^n f_0(X_S^{(i)})$ and likewise for $\bar{\epsilon}$.
+with probability at least $1-2\delta$.\\
 
-$\epsilon_i$ is subgaussian with subgaussian norm $\sigma$.
-For a single $\epsilon_i$, we have that $P( |\epsilon_i| \geq t ) \leq C \exp( - c \frac{1}{\sigma^2} t^2)$.
-Therefore, with probability at least $1-\delta$, $|\epsilon_i| \leq \sigma\sqrt{ \frac{1}{c} \log \frac{C}{\delta}}$.
+\textbf{Step 3}: We now apply Serfling's theorem.
 
-By union bound, with probability at least $1-\delta$, $\max_i |\epsilon_i| \leq \sigma \sqrt{ \frac{1}{c} \log \frac{2nC}{\delta}}$.
-
-Also, $|\bar{\epsilon}| \leq \sigma \sqrt{\frac{c}{n} \log \frac{C}{\delta}}$ with probability at least $1 - \delta$.
-
-We know that $|f_0(x)| \leq sB$ and $|\hat{f}_k(x_k)| \leq B$ for all $k$.
-
-Then $|\bar{f_0(x)}| \leq sB$ as well, and $|f^*(X_S^{(i)}) - \bar{f^*} - \sum_{k \in S} \hat{f}_k(X_k^{(i)})| \leq 3s B$.
-
-Therefore, taking an union bound, we have that with probability at least $1-\frac{C}{n}$, 
+Serfling's theorem states that with probability at least $1 - \delta$:
 \[
-\| \hat{r} \|_\infty \leq (3 s B + c\sigma\sqrt{\log n}) 
+\Big
+|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)}\Big| \leq
+   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
+   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
 \]
 
-\textbf{Step 2.} We now bound $\frac{1}{n} \hat{r}^\tran \max( X, X_{k(j)} \mathbf{1})$.
-
-\[
-\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)} \mathbf{1}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i \max(X_{ki}, X_{k(j)}) = \frac{1}{n} \sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) + \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
-\]
-
-Where $A = \{ i : ord(i) \geq j\}$ and $ord(i)$ is the order of sample $i$ where $(1)$ is the smallest element.
-
-We will bound both terms.
-
-\textbf{Term 1.}
-\[
-\trm{Want to bound} \qquad F(X_{k1},...,X_{kn}) \coloneqq \frac{1}{n}\sum_{i=1}^n \hat{r}_i X_{ki} \delta(ord(i) \geq j) 
-\]
-
-First, we note that $X_{ki}$ is bounded in the range $[-b,b]$.
-
-We claim then that $F$ is coordinatewise-Lipschitz. Let $X_k = (X_{k1}, X_{k2},...,X_{kn})$ and $X'_k = (X'_{k1}, X_{k2}, ..., X_{kn})$ differ only on the first coordinate.
-
-The order of coordinate $i$ in $X_k$ and $X'_k$ can change by at most $1$ for $i \neq 1$. Therefore, of the $j-1$ terms of the series, at most 2 terms differ from $F(X_k)$ to $F(X'_k)$ and
-
-$$ | F(X_{k1}, ..., X_{kn}) - F(X'_{k1}, ..., X'_{kn}) | \leq \frac{4 b \|\hat{r}\|_\infty}{n} $$
-
-By McDiarmid's inequality therefore, 
-\[
-P( | F(X_k) - \E F(X_k) | \geq t ) \leq C \exp( - c n\frac{t^2}{ (4 b \|\hat{r}\|_\infty)^2})
-\]
-
-By symmetry and the fact that $\hat{r}$ is centered, $\E F(X_k) = 0$.
-
-We can fold the 4 into the constant $c$. With probability $1-\delta$, $|F(X_k)| \leq b \|\hat{r}\|_\infty \sqrt{   \frac{1}{cn} \log \frac{C}{\delta}}$.
-
-\textbf{Term 2:}
-
-\[
-\trm{Want to bound}   \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A
-\]
-
-$A$ is a random set and is probabilistically independent of $\hat{r}$.
-$\mathbf{1}_A^\tran \hat{r}_A$ is the sum of a sample of $\hat{r}$ without replacement.
-Therefore, according to Serfling's theorem (Corollary~\ref{cor:serfling}), with probability at least $1-\delta$, $|\frac{1}{n} \mathbf{1}_A^\tran \hat{r}_A|$ is at most $\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
-
-Since $|X_{k(j)}|$ is at most $b$, we obtain that with probability at least $1-\delta$, $| \frac{1}{n} X_{k(j)} \mathbf{1}_A^\tran \hat{r}_A| \leq b\| \hat{r} \|_\infty \sqrt{ \frac{1}{cn} \log \frac{C}{\delta}}$.
-
-Now we put everything together.
-
-Taking union bound across $p$ and $n$, we have that with probability at least $1-\delta$,
-
-\[
-| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}| \leq b \|\hat{r}\|_\infty \sqrt{ \frac{1}{c} \frac{1}{n} \log \frac{np C }{\delta}}
-\]
-
-Taking union bound and substituting in the probabilistic bound on $\|\hat{r}\|_\infty$, we get that with probability at least $1-\frac{C}{n}$,
-
-$| \frac{1}{n} \max(X_k, X_{k(j)}\mathbf{1})^\tran \hat{r}|$ is at most 
-\[
- c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn) }
-\]
+Taking an union bound across previous events, we have that with probability at least $1 - 3n^2 p \delta$, for all $j \in S^c$, for all $i'=1,...,n$:
+\begin{align*}
+\Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
+  \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
+\end{align*}
+Setting $\delta = \frac{1}{n^3 p}$ gives the desired result.
 
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
- We will use covering number and uniform convergence and will thus need to first introduce some notations. 
+ We first introduce notations.
  \subsubsection{Notation} 
+\label{sec:false_negative_proof_notations}
 
- Given samples $X^{(1)},...,X^{(n)}$, let $f, g$ be a function and $w$ be a $n$-dimensional random vector, then we denote $\| f - g + w\|_n^2 \coloneqq \frac{1}{n} \sum_{i=1}^n ( f(X^{(i)}) - g(X^{(i)}) + w_i )^2$.
-We will also abuse notation and let $\| f + c \|_n^2 = \frac{1}{n} \sum_{i=1}^n (f(X^{(i)}) + c)^2$ if $c$ is a scalar.
+Let $f : \mathbb{R}^s \rightarrow \R$, we denote $\| f \|_P \equiv \E f(X)^2$. \\
+Given samples $X_1,...,X_n$, we denote $\| f \|_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i)^2$ and $\langle f, g \rangle_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i) g(X_i)$. \\
 
-We let $\langle f, g \rangle_n \coloneqq \frac{1}{n} \sum_{i=1}^n f(X^{(i)}) g(X^{(i)})$. It then follows that:
-\begin{packed_enum}
-\item $\| f + g \|_n^2 = \|f\|_n^2 + 2 \langle f, g \rangle_n + \|g \|_n^2$
-\item $\langle f, g \rangle_n \leq \|f\|_n \| g \|_n$
-\end{packed_enum}
+Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
+Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions.
+\\
 
-For a function $g : \R^s \rightarrow \R$, define $\hat{R}_s(g) \coloneqq \| f_0 + w - \bar{f_0} - \bar{w} - g \|_n^2$ as the objective of the \emph{restricted} regression and define $R_s(g) \coloneqq \E | f_0(X)  + w - \mu - g(X) |^2$ as the population risk, where $\bar{f_0} = \frac{1}{n} \sum_i f_0(X^{(i)})$ and $\bar{w} = \frac{1}{n}\sum_{i=1}^n w_i $ and $\mu = \E f_0(X)$.
-Note that we \emph{subtract} out the mean in the two risk definitions.
+Define $\mathcal{C}^s$ as the set of convex additive functions and $\mathcal{C}^s_L$ likewise as the set of $L$-Lipschitz convex additive functions.
+\begin{align*}
+\mathcal{C}^s &\equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
+   f_k \in \mathcal{C}^1 \} \\
+\mathcal{C}^s_L &\equiv \{ f \in \mathcal{C}^s \,:\, 
+f = \sum_{k=1}^s f_k, \, \| \partial f_k \|_\infty \leq L \}
+\end{align*}
 
-For an additive function $g$, define $\rho_n(g) = \sum_{k=1}^s \| \partial g_k \|_\infty$.
-Because we always use the secant linear piece-wise function in our optimization program, we define $\ds \| \partial g_k\|_\infty \coloneqq \max_{i=1,...,n-1} |\frac{ g_k(X^{(i)}) - g_k(X^{(i+1)})}{ X^{(i)} - X^{(i+1)}}|$.
-
-Let $\mathcal{C}[b,B,L]$ be the set of 1 dimensional convex functions on $[-b,b]$ that are bounded by $B$ and $L$-Lipschitz.
-
-Let $\mathcal{C}[s,b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
+Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
 \[
-\mathcal{C}[s,b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
+f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f^* \|_P^2
 \]
 
-Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \, \E f_k(X_k) = 0\}$.
+We let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.
+Since $f_0, f^*$ are supported on $[-b, b]^s$, it follows that $\| f_0 \|_\infty, \|f^* \|_\infty \leq s L b$.
 
-Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \, \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.
+We define $\hat{f}$ as the empirical risk minimizer:
+\[
+\hat{f} = \arg\min \Big \{ \| y - f \|_n^2 + \lambda \sum_{k=1}^s \| f_k \|_\infty 
+    \,:\, f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0 \Big \}
+\]
 
-\textbf{Note:} By definition of the Lipschitz condition, $f_k \in \mathcal{C}[b,B,L]$ implies that $\| \partial f_k \|_\infty \leq L$.
-$f = \sum_k f_k \in \mathcal{C}[s,b,B,L]$ implies that $\rho_n(f) \leq sL$.
+For $k \in \{1,...,s\}$, define $g^*_k$ to be decoupled concave population risk minimizer
+\[
+g^*_k \equiv \argmin_{g_k \in \mh \mathcal{C}^1} \| f_0 - f^* - g_k \|_P^2 
+\]
+In our proof, we will analyze $g^*_k$ for $k$'s such that $f^*_k = 0$. Likewise, we define the empirical version:
+\[
+\hat{g}_k \equiv \argmin \Big\{ \| f_0 - \hat{f} - g_k \|_n^2 \,:\, g_k \in \mh \mathcal{C}^1_L \,, \mathbf{1}_n^\tran g_k = 0 \Big\}
+\]
+By the definition of the ACDC procedure, $\hat{g}_k$ exist only for $k$ that have zero in their convex additive approximation.
 
 \subsubsection{Proof}
-\label{sec:false_negative_proof_proof}
 
-We first start with a lemma that converts assumption A4 into a more easily applicable condition.
-\begin{lemma}
-\label{lem:minus_one_risk_increase}
-Suppose assumptions A1' and A4 hold.
+By additive faithfulness of the ACDC procedure, it is necessary that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\
 
-Then $R(f^{*(s-1)}) - R(f^{*s}) \geq \alpha$, where $\alpha$ lower bounds the norm of the population optimal additive components as defined in assumpation A4.
-\end{lemma}
+Intuitively, we would like to show the following:
+\begin{align*}
+\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
+\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P 
+       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
+\end{align*}
+where the difference is a term that decreases with $n$.
+
+Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough, there must exist a contradiction because the population risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger than the population risk of the best approximation whose $k$-th component is constrained to be zero.
+
+Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction. \\
+
+\begin{theorem}
+\label{thm:convex_consistent}
+Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq \mathbf{c} sLb\sqrt{ \frac{1}{n} \log^2 np}$.
+
+Then, with probability at least $1-\delta$,
+\begin{align}
+\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
+&\leq \mathbf{c} (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
+\end{align}
+
+\end{theorem}
 
@@
 
+\textbf{Step 1.} We start from the definition.
+
 \begin{align*}
-R(f^{*(s-1)}) - R(f^{*s}) &= \E\Big(f^{*(s-1)}(X) - f_0(X) + \mu\Big)^2 
-                              - \E\Big(f^{*s}(X) - f_0(X) + \mu\Big)^2 \\
-    &= \E\Big( f^{*(s-1)}(X) - f^{*s}(X) + f^{*s}(X) - f_0(X) + \mu\Big)^2 
-                                 - \E\Big(f^{*s}(X) - f_0(X) + \mu\Big)^2 \\
-    &= \E\Big( f^{*(s-1)}(X) - f^{*s}(X)\Big)^2 
-                - 2 \E\Big[ (f^{*(s-1)}(X) - f^{*s}(X)) (f^{*s}(X) - (f_0(X)-\mu)) \Big]
+\| y - \hat{f} \|_n^2 + \lambda \sum_{k=1}^s \| \hat{f}_k \|_\infty &\leq
+  \| y - f^* + \bar{f}^* \|_n^2 + \lambda \sum_{k=1}^s \| f^*_k - \bar{f}^* \|_\infty 
+\end{align*}
+We plug in $y = f_0 + w$:
+\begin{align*}
+\| f_0 + w - \hat{f} \|_n^2 + \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
+    \| f^*_k - \bar{f}^*_k \|_\infty \Big) &\leq \|f_0 + w - f^* + \bar{f}^* \|_n^2 \\
+\| f_0 - \hat{f} \|_n^2 + 2\langle w, f_0 - \hat{f} \rangle_n 
+     +\lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - \|f^*_k -\bar{f}^*_k\|_\infty \Big) 
+    &\leq \| f_0 - f^* + \bar{f}^* \|_n^2 + 
+    2 \langle w, f_0 - f^* + \bar{f}^* \rangle \\
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 + 
+    \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
+ \| f^*_k - \bar{f}^*_k \|_\infty \Big) &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle
 \end{align*}
 
-We will argue that all the components of the additive function $f^{*(s-1)}$ are also in $f^{*s}$.
-Let us denote the components of $f^{*s} = \sum_{k=1}^s f_k^*$.
-We will now invoke Lemma~\ref{lem:additive_component}, which is valid because we assume $X_1,...,X_s$ are independent by assumption A1'.
-By Lemma~\ref{lem:additive_component}, if we set $f^*_k = 0$, the resulting additive function $\sum_{k'\neq k} f_{k'}^*$ minimizes the population risk subject to the constraint that $f_k = 0$.
-By definition, $f^{*s}$ is $\argmin_k \sum_{k'\neq k} f_{k'}^*$ and thus share components with $f^{*s}$.
+The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4Lb$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.
 
-Therefore, there exist some $k$ such that $f^{*(s-1)} - f^{*s} = f^*_k$, and we can continue the bound
 \begin{align*}
-R(f^{*(s-1)}) - R(f^{*s}) &= \E f^*_k(X_k)^2 - 2 \E[ f^*_k(X_k) ( f^{*s}(X) - (f_0(X)-\mu) )] \\
-    &= \E f^*_k(X_k)^2 - 2 \E[ f^*_k(X_k) f^{*s} (X)] + 2 \E[ f^*_k(X_k) (f_0(X)-\mu) ] 
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b 
 \end{align*}
 
+Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
+\begin{align}
+\label{eqn:first_step_inequality}
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+\end{align}
+
+[TOOD: at this point, we still have to choose a value for $\lambda$]\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% 
+%% Step 2
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with theorem~\ref{thm:chaining}.\\
+
+Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_L\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
+Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
+
+According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma \mathbf{c} \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
+\[
+P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
+  4 \exp \Big( - \frac{ n \epsilon^2}{ \mathbf{c} R^2 \sigma^2} \Big)
+\]
+where $R = 4sLb$ for our purpose.
+
+Restated, we have that, with probablity at least $1-\delta$,
+\[
+\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
+   \mathbf{c} R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
+      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
+       \mathbf{c} \sigma \sqrt{\frac{1}{n}} 
+\]
+
+Now we evaluate the integral. Since $N_{\|\cdot\|_n}(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.
+
 \begin{align*}
-\E[ f^*_k(X_k) f^{*s} (X)]  &= \E\Big[ f^*_k (X_k) \E[ f^{*s} (X) \,|\, X_k ] \Big] = \E f^*_k(X_k)^2  \\
-\E[ f^*_k(X_k)(f_0(X) - \mu) ] &= \E\Big[ f^*_k(X_k) \E[ f_0(X) - \mu \,|\, X_k ] \Big] = \E f^*_k(X_k)^2 
+\int_0^R \sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} dt &\leq 
+      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
+ &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
+ &= \sqrt{C s^{1.5} b L} \, \mathbf{c} (sLb)^{3/4} \\
+ &\leq \mathbf{c} (s b L)^2
 \end{align*}
 
-Where we used the fact that $\E f^*_{k'} (X_{k'}) = 0$ for all $k'$ and the fact that $\E[ f_0(X) - \mu \,|\, X_k] = f^*_k(X_k)$ (Lemma~\ref{lem:int_reduction}).
+Coming back, we have, with probability at least $1-\delta$,
+\begin{align*}
+\sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
+    \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
+    \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
+ &\leq \mathbf{c} (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
+\end{align*}
 
-Thus, $R(f^{*(s-1)}) - R(f^{*s}) \geq \E f^*_k(X_k)^2 \geq \alpha$ by Assumption A4.
+Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
+\begin{align}
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
+   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+   + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
+\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
+   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+   + \lambda 4 s L b    \label{eqn:second_step_inequality}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% Step 3.
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{Step 3.} We continue from equation~\ref{eqn:second_step_inequality}, use lemma~\ref{lem:uniform_convergence}, use another union bound, with probability at least $1-3\delta$,
+
+\begin{align}
+\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
+   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+ +\lambda 4 s L b + \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+    \nonumber \\
+&\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
+\end{align}
+
+Substituting in $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
 
@@
 
-We now restate the theorem in our newly defined notation.
+%% End of "No False Negative" proof for the f's
 
 \begin{theorem}
-Suppose assumptions A1', A2', A3, A4 hold.
+\label{thm:concave_consistent}
+Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$.\\
 
-Let $\ds \hat{f} \coloneqq \arg\min \{ \hat{R}_s(f) + \lambda_n \rho_n(f) \,:\, f \in \mathcal{C}[s,b,B,L], f_k \trm{ centered} \}$.
+Suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\
 
-Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.
-
-Then, for all large enough $n$, with probability at least $1-\frac{C}{n}$, $\hat{f}_k \neq 0$ for all $k =1,...,s$.
-\end{theorem}
-
-\begin{proof}
-Let us first sketch out the rough idea of the proof.
-We know that in the population setting, the best approximate additive function $f^{*s}$ has $s$ non-zero components.
-We also know that the empirical risk approaches the population risk uniformly.
-Therefore, it cannot be that the empirical risk minimizer maintains a zero component for all $n$; if that were true, then we can construct a feasible solution to the empirical risk optimization, based on $f^{*s}$, that achieves lower empirical risk.
-
-\textbf{Step 1:} $f^{*s}$ is not directly a feasible solution to the empirical risk minimization program because it is not empirically centered.
-Given $n$ samples, $f^{*s} - \bar{f}^{*s}$ is a feasible solution where $\bar{f}^{*s} = \sum_{k=1}^s \bar{f}_k^{*s}$ and $\bar{f}_k^{*s} = \frac{1}{n} \sum_{i=1}^n f_k^{*s}(X^{(i)})$.
-
-\begin{align*}
-|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| &\leq 
-         \| f_0 + w - \bar{f}_0 - \bar{w}
-         - f^{*s} + \bar{f}^{*s} \|_n^2  - \| f_0 + w - \bar{f}_0 - \bar{w} - f^{*s}\|_n^2 \\
-   &\leq 2 \langle f_0 + w - \bar{f}_0 - \bar{w} - f^{*s}, \bar{f}^{*s} \rangle_n 
-         + \| \bar{f}^{*s} \|_n^2 \\
-   &\leq 2\| f_0 + w - \bar{f}_0 - \bar{w} -f^{*s}\|_n 
-                \|\bar{f}^{*s} \|_n 
-                  + \|\bar{f}^{*s} \|_n^2 \\
-   &\leq 2 | \bar{f}^{*s} | \| f_0 + w 
-           - \bar{f}_0 - \bar{w} - f^{*s} \|_n + |\bar{f}^{*s}|^2 
-\end{align*}
-
-Because each $f^{*s}$ is bounded by $sB$ and $\E f^{*s}(X) = 0$, by Hoeffding inequality, with probability at least $1-\frac{C}{n}$, $|\bar{f}^{*s}| \leq sB \sqrt{\frac{1}{cn} \log n}$.
-
-\begin{align*}
-\| f_0 + w -\bar{f}_0 - \bar{w} - f^{*s} \|_n 
-	\leq \| f_0 - f^{*s} \|_n + \|w\|_n + |\bar{f}_0| + |\bar{w}|\\
-\end{align*}
-
-$\|f_0 - f^{*s}\|_n \leq \|f_0 - f^{*s}\|_\infty $ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$.
-Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.
-
-$| \bar{f}_0 | \leq s B$ and $| \bar{w} | \leq c \sigma \sqrt{\frac{1}{n}}$ with probability at least $1-\frac{C}{n}$ by Chernoff bound.
-
-So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
+Then, with probability at least $1- s\delta$, for all $k=1,...,s$:\\
 \[
-|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2c (sB+\sigma) sB \sqrt{\frac{1}{cn} \log n}
-\]
-
-\textbf{Step 2:} Now that we bounded the cost of approximating $f^{*s}$ with the empirically centered $f^{*s} - \bar{f}^{*s}$, we move on to the proof of the main result.
-
-Suppose $\hat{f}$ has at most $s-1$ non-zero components. Then
-\begin{align*}
-\hat{R}_s( \hat{f}) &\geq R_s(\hat{f}) - \tau_n \\
-	&\geq R_s(f^{*(s-1)}) - \tau_n \\
-	&\geq R_s(f^{*s}) + \alpha - \tau_n \\
-	&\geq \hat{R}_s(f^{*s}) + \alpha - 2 \tau_n \\
-	&\geq \hat{R}_s(f^{*s} - \bar{f}^{*s}) -\tau'_n + \alpha - 2\tau_n 
-\end{align*}
-The third line follows from Lemma~\ref{lem:minus_one_risk_increase}.
-$\tau_n$ is the deviation between empirical risk and true risk and $\tau'_n$ is the approximation error incurred by empirically sampling $f^{*s}$.
-
-Adding and subtracting $ \lambda_n \rho_n(f^{*s} - \bar{f}^{*s})$ and $ \lambda_n \rho_n(\hat{f})$, we arrive at the conclusion that
-\[
-\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{f}) \geq \hat{R}_s(f^{*s} - \bar{f}^{*s}) + \lambda_n \rho_n(f^{*s} - \bar{f}^{*s}) - ( \lambda_n \rho_n(f^{*s} - \bar{f}^{*s}) + \lambda_n \rho_n(\hat{f}) ) -\tau'_n + \alpha - 2 \tau_n
-\]
-
-Because we assume that we impose the Lipschitz constraint in our optimization, $\rho_n(\hat{f}), \rho_n(f^{*s} - \bar{f}^{*s})$ are at most $sL$ and so $|\lambda_n \rho_n(\hat{f}) - \lambda_n \rho_n(f^*_s)| \leq 2 sL \lambda_n$.
-
-By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  Lb (sB+\sigma) sB \sqrt{ \frac{s}{cn^{4/5}} \log n}$.
-
-$\tau'_n$, as shown above, is at most $2 (sB+\sigma) sB \sqrt{\frac{1}{cn} \log sn}$ with probability at least $1-\frac{C}{n}$ for $n > n_0$.
-
-For $n$ large enough such that
-\[
-c s L \lambda_n < \frac{\alpha}{2} \trm{ and } Lb sB (sB+\sigma) \sqrt{ \frac{s}{n^{4/5}} \log sn}) < \frac{\alpha}{4}
-\]
-we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction since we assumed that $\hat{f}$ minimizes the regularized empirical risk.
-
-\end{proof}
-
-%
-
-\begin{theorem} (Uniform Risk Deviation)
-\label{thm:uniform_risk_deviation}
-For all $n > n_0$, we have that, with probability at least $1 - \frac{C}{n}$, 
-\[
-\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq Lb(sB+\sigma)sB\sqrt{ \frac{s}{cn^{4/5}} \log sn}
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  \mathbf{c}(Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
 \]
@@
 \begin{proof}
-This proof uses a standard covering number argument.
+The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same covering number.
 
-Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$ such that for all $f \in \mathcal{C}[s,b,B,L]$, there exists $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ such that $\| f - f'\|_\infty \leq \epsilon$.
+\textbf{Step 1.} We start from the definition of $\hat{g}_k$:
+\begin{align*}
+\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
+   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
+\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2 Lb \\
+ &\\
+\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
+   +\lambda 2 Lb \\
+\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
+   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2Lb
+\end{align*}
 
-For all $f \in \mathcal{C}[s,b,B,L]$,
-\[
-\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
-\]
-where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\
+Using the chaining result (theorem~\ref{thm:chaining}), setting $s=1$, we have, with probability at least $1-\delta$,
+\begin{align*}
+\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
+  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
+\end{align*}
 
-\textbf{Step 1.} We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.
+Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
+\begin{align*}
+\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
+  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
+  \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
+ &\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
+\end{align*}
+
+Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
+\begin{align*}
+\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
+\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
+    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
+\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
+\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
+\end{align*}
+
+\textbf{Step 2.} The goal is to bound the quality of approximation between $\| f_0 - \hat{f} - g^*_k \|_P^2$ and $\| f_0 - f^* - g^*_k \|_P^2$ and likewise for $\hat{g}_k$.
 
 \begin{align*}
-|\hat{R}_s(f) - \hat{R}_s(f')| &= |\| f_0 - \bar{f}_0 + w - \bar{w} - f \|_n^2 
-                                - \| f_0 - \bar{f}_0 + w -\bar{w} - f' \|_n^2| \\
-	&\leq 2 \langle f_0 - \bar{f}_0 + w -\bar{w}, f' - f \rangle_n 
-                            + \| f \|_n^2 - \| f' \|_n^2\\
-	&\leq 2 \| f_0 - \bar{f}_0 + w -\bar{w} \|_n \| f' 
-                   - f \|_n + ( \| f \|_n - \|f'\|_n)( \| f \|_n + \|f'\|_n)\\
+\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
+    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
+   + 2 \langle f_0 - f^*, g^*_k \rangle \\
+ &\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
+    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
+ &\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
+&\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+   \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
+&\leq  \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
 \end{align*}
 
-We now want to bound $\| f_0 - \bar{f}_0 + w -\bar{w} \|_n \leq \| f_0 \|_n  + \|w \|_n + |\bar{f}| + |\bar{w}|$.
+The same bound likewise holds for $\hat{g}_k$.
 
-$\| w \|^2_n = \frac{1}{n}\sum_{i=1}^n w_i^2$ is the average of subexponential random variables.
-Therefore, for all $n$ larger than some absolute constant $n_0$, with probability at least $1-\frac{C}{n}$, $|\|w\|^2_n - \E|w|^2 | < \sigma^2 \sqrt{\frac{1}{cn} \log n}$.
-The absolute constant $n_0$ is determined so that for all $n > n_0$, $\sqrt{\frac{1}{cn} \log n} < 1$.
-Since $\E w^2 \leq \sigma^2$, for all $n > n_0$, with probability at least $1 - \frac{C}{n}$, for some constant $c$, $\| w \|^2_n \leq c \sigma^2$.
+\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
+\begin{align*}
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
+   \mathbf{c}(Lb)^{2.5} \sigma^{0.5} 
+     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
+\end{align*}
 
-By Chernoff bound and the fact that $\E w = 0$, we know that $|\bar{w}| \leq c \sigma \sqrt{\frac{1}{n}}$ with high probability.
+Taking an union bound across $k=1,...,s$ dimensions completes the result.
 
-%$\|f_0\|^2_n$ is the average of random variables bounded by $s^2 B^2$ and therefore, with probability at least $1-\frac{C}{n}$, $|\| f_0 \|^2_n - \E f_0(X)^2 | \leq s^2B^2\sqrt{ \frac{1}{cn} \log n}$.
-Since $\E f_0(X)^2 \leq s^2B^2$, we have that, for all $n > n_0$, with probability at least $1-\frac{C}{n}$, for some constant $c$, $\| f_0 \|_n^2 \leq c s^2 B^2$.
+\end{proof}
 
-$\|f_0\|^2_n = \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})^2$. Since $f_0(X^{(i)})^2 \leq s^2 B^2$, $\|f_0\|^2_n \leq s^2 B^2$.
+\subsubsection{Support Lemmas}
 
-$|\bar{f}_0| = | \frac{1}{n} \sum_{i=1}^n f_0(X^{(i)})| \leq s B$.
+%%%%%%%%%%
+%% Uniform convergence lemma
+%%
+%%
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%
 
-Combining these together, We have that for all $n \geq n_0$, with probability at least $1-\frac{C}{n}$, $\| f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c ( s^2 B^2 +\sigma^2 )$, and so
+\begin{lemma}
+\label{lem:uniform_convergence}
+With probability at least $1-\delta$:
+\begin{align*}
+\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
+   \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+\end{align*}
 
+\end{lemma}
+
+\begin{proof}
+Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_L - f_0$.
+Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s b L$.\\
+
+For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-cover of $\mathcal{G}$ closest to $h$.
+It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\
+
+Because $\| h \|_n = \| h - h_\epsilon + h_\epsilon \|_n$, we have that
+\begin{align*}
+\|h_\epsilon \|_n - \| h - h_\epsilon \|_n &\leq 
+    \| h \|_n \leq \|h_\epsilon \|_n + \| h - h_\epsilon \|_n \\
+\|h_\epsilon \|_n - \epsilon &\leq 
+    \| h \|_n \leq \|h_\epsilon \|_n + \epsilon  \\
+\| h_\epsilon \|^2_n - 8 \epsilon (s L b)  &\leq \| h  \|^2_n  \leq
+   \| h_\epsilon \|_n^2 + 8 \epsilon (s L b) 
+\end{align*}
+where we used the fact that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$ and $ \| h_\epsilon \|_n \leq \| h_\epsilon \|_\infty \leq 4 s L b$.
+
+And likewise:
+\begin{align*}
+\| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
+   \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
+\end{align*}
+
+Therefore, 
+\begin{align*}
+\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+        + \epsilon (16 sLb)
+\end{align*}
+
+Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
+\begin{align*}
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+  (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
+&\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
+\end{align*}
+
+We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
+Therefore:
+\begin{align*}
+\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+        + s n^{1/5}  \big) } \\
+  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
+\end{align*}
+And
+\begin{align*}
+\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
+\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
+  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
+     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
+  &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+\end{align*}
+
+\end{proof}
+
+\begin{lemma}
+\label{lem:remove_centering}
+
+Let $f_0, f^*$ be defined as in section~\ref{sec:false_negative_proof_notations}. Define $\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$.
+
+Then, with probability at least $1 - 2\delta$,
 \[
-\|f_0 - \bar{f}_0 + w -\bar{w} \|^2_n \leq c (sB + \sigma)
+\Big | \| f_0 - f^* \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 \Big| \leq
+    \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
+\]
+\end{lemma}
+
+\begin{proof} (of lemma~\ref{lem:remove_centering})
+\begin{align*}
+\| f_0 - f^* + \bar{f}^* \|_n^2 &= \| f_0 - f^* \|_n^2 
+    + 2 \langle f_0 - f^*, \bar{f}^* \rangle + \bar{f}^{*2} \\
+  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \langle f_0 - f^*, \mathbf{1} \rangle_n + 
+    \bar{f}^{*2} \\
+  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \bar{f}_0 - \bar{f}^{*2}
+\end{align*}
+
+$\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 s L b \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.
+
+The same reasoning likewise applies to $\bar{f}_0 = \frac{1}{n} \sum_{i=1}^n f_0(X_i)$.
+
+Taking a union bound and we have that, with probability at least $1- 2\delta$,
+
+\begin{align*}
+| \bar{f}^* | | \bar{f}_0 | &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
+\bar{f}^{*2} &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+\end{align*}
+
+Therefore, with probability at least $1 - 2\delta$,
+\[
+\|f_0 - f^*\|_n^2 - \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
+    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
+\|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
 \]
 
-$\| f' - f \|_\infty \leq \epsilon$ implies that $\| f' - f\|_n \leq \epsilon$. And therefore, $\| f \|_n - \|f'\|_n \leq \| f - f' \|_n \leq \epsilon$.
+\end{proof}
 
-$f,f'$ are all bounded by $sB$, and so $\|f \|_n, \| f' \|_n \leq sB$.
-
-Thus, we have that, for all $n > n_0$,
-\begin{align}
-|\hat{R}_s(f) - \hat{R}_s(f')| \leq \epsilon c( sB + \sigma ) \label{eqn:approx_deviation1}
-\end{align}
-with probability at least $1-\frac{C}{n}$.
-
-\textbf{Step 2:} Now we bound $R_s(f') - R_s(f)$. The steps follow the bounds before, and we have that 
-\begin{align}
-|R_s(f') - R_s(f)| \leq \epsilon c(sB + \sigma) \label{eqn:approx_deviation2}
-\end{align}
-
-\textbf{Step 3:} Lastly, we bound $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} \hat{R}_s(f') - R_s(f')$.
-
-For a fixed $f'$, we have that, by definition
-\begin{align*}
-\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0 - \bar{w} - f' \|_n^2\\
-      &= \|f_0 - \bar{f}_0 - f'\|_n^2 + 2 \langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n
-             + \| w - \bar{w}\|_n^2\\
-R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
-     &= \E\big(f_0(X) - \mu - f'(X)\big)^2 + \E w^2 
-\end{align*}
-
-Therefore:
-\begin{align*}
-\hat{R}_s(f') - R_s(f') = & \|f_0 -\bar{f}_0 - f'\|_n^2 - \E(f_0(X) - \mu - f'(X))^2 \\
-            &+ \|w - \bar{w}\|_n^2 - \E w^2 \\
-            &+ 2\langle w-\bar{w}, f_0 - \bar{f}_0 - f'\rangle_n
-\end{align*}
-
-\textbf{Step 3.1:} We first bound $2 \langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n$.
-\begin{align*}
-\langle w - \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n &=
-      \langle w, f_0 - \bar{f}_0 - f'\rangle_n 
-      - \langle \bar{w}, f_0 - \bar{f}_0 - f'\rangle_n \\
-\end{align*}
-
-The first term, fully expanded, is $\frac{1}{n} \sum_{i=1}^n w_i (f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)}))$.
-Since $w_i$ and $X^{(i)}$ are independent, we use the sub-Gaussian concentration inequality.
-Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle_n | > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.
-
-The second term, fully expanded, is $\bar{w} \bar{f'}$. $\bar{f'} \leq sB$ and so $|\bar{w}\bar{f'}| > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2(sB)^2} \big)$ as well.
-
-\textbf{Step 3.2} We now bound $\| w - \bar{w} \|_n^2 - \E w^2$. 
-\begin{align*}
-\|w - \bar{w} \|_n^2 &= \|w\|_n^2 - 2 \langle w, \bar{w} \rangle_n + \|\bar{w}\|_n \\
-               &= \|w\|_n^2 - \bar{w}^2
-\end{align*}
-
-Using sub-Exponential concentration, we know that $| \|w\|_n^2 - \E w^2 | \geq t$ with probability at most $C \exp( - c n \frac{1}{\sigma^2})$.
-
-$\bar{w} \leq \sigma\sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$.
-Thus, $| \bar{w}|^2 \leq \sigma^2 \frac{1}{cn}$ with high probability, has a second order effect, and can be safely ignored in the bound.
-
-\textbf{Step 3.3:} We now bound $\| f_0 - \bar{f}_0 - f'\|_n^2 - \E(f_0(X) - \mu - f'(X))^2$.
-
-\begin{align*}
-\| f_0 - \bar{f}_0 - f'\|_n^2 &= \|f_0 -\mu+\mu - \bar{f}_0 - f'\|_n^2 \\
-      &= \| f_0 - \mu - f'\|_n^2 + 2 \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n 
-          + \|\mu - \bar{f}_0 \|_n^2 
-\end{align*}
-
-Using similar reasoning as before, we know that $| \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n | \geq t $ with probability at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
-
-Likewise, $| \mu - \bar{f}_0 | \leq sB \sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$.
-Thus, $| \mu - \bar{f}_0 |^2 \leq (sB)^2 \frac{1}{cn}$, has a second order effect, and can be safely ignored in the bound.
-
-Because $f_0(X^{(i)}) -\mu - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 -\mu- f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.
-
-Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) -\mu - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.
-
-Applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
-\[
-C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2(sB)^2 + (sB)^4} \big)
-\]
-for all $n > n_0$.
-
-Restating, we have that with probability at most $1- \frac{1}{n}$, the deviation is at most 
-\begin{align}
-(sB+\sigma)sB\sqrt{ \frac{1}{cn} \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
-\end{align}
-Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} can be upper bounded by $sB(\sigma+sB)\sqrt{ \frac{s}{cn^{4/5}} \log Cn}$.
-
-Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} from \textbf{Step 1} and \textbf{Step 2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (sB+\sigma)$.
-
-We can arrive at the statement of the theorem by summing these up and absorbing any constants into the symbols $c$ and $C$.
-
-\end{proof}
+%%%%%%%%%%%%%
+%% Technical Material
+%%
+%%
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%
 
@@
 
+In our proofs, we will use the Dudley's chaining: [TODO:cite van de geer]
+
+\begin{theorem} (Dudley's Chaining) \\
+\label{thm:chaining}
+Let $\mathcal{G} = \{ g : \| g \|_n \leq R \}$.
+Let $M( \epsilon, R)$ be the size of the minimal $\epsilon$-covering of $\mathcal{G}$ with respect to the $\| \cdot \|_n$ norm.
+Suppose $w = (w_1, ..., w_n)$ is a vector of i.i.d.
+subgaussian random variables with scale $\sigma$.\\
+
+Suppose $\delta > 0$ is such that
+\[
+\sqrt{n} \delta \geq \sigma \Big( 
+   14 \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
+      \Big)\vee 70 \log 2 R
+\]
+Then we have that 
+\[
+P\Big( \sup_{g \in \mathcal{G}} \langle w, g \rangle_n \geq \delta \Big) \leq
+  4 \exp \Big( - \frac{n \delta^2}{(70R)^2\sigma^2} \Big)
+\]
+\end{theorem}
+
+For convenience, we can upper bound the metric-entropy sum with an integral: \\
+$\ds \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
+  \leq \int_0^R \sqrt{\log M(t, \mathcal{G}) } dt
+$
+
 % DO NOT CHANGE; RefTex variables -minx

### 2014-04-18 tex/scam/estimation.tex
paper update

\section{Estimation Procedure}
\label{sec:acdc}

Theorem~\ref{thm:acdc_faithful} suggest a two stage procedure for variable selection in convex regression--first learning a sparse convex additive model and then, on the residual, separately learning an univariate concave function for each of the dimensions.

More precisely, given samples $(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, we perform the following procedure, which we refer to as AC/DC (additively convex / decoupled concave):
\begin{enumerate}
\item Compute: 
\begin{equation}
\label{eqn:scam}
\hat{f}_1, ..., \hat{f}_p = \argmin_{f_1,...,f_p \in \mathcal{C}^1} 
   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \sum_{k=1}^p f_k(x_{ki}) \Big)^2 
       + \lambda \sum_{k=1}^p \| f_k \|_\infty
\end{equation}
\item Compute, for each $k$ such that $\| \hat{f}_k \| = 0$:
\begin{equation}
\label{eqn:dc}
\hat{g}_k = \argmin_{g_k \in \mathcal{C}^1} 
   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \sum_{k'} \hat{f}_{k'}(x_{k'i}) 
    - g_k(x_{ki})\Big)^2 
      + \lambda \| g_k \|_\infty
\end{equation}
\item Output as the set of relevant variables: 
$\{ k \,:\, \| \hat{f}_k \|_\infty > 0 
  \textrm{ or } \| \hat{g}_k \|_\infty > 0 \}$ 
\end{enumerate}

We added an $\ell_\infty/\ell_1$ penalty in equation~\ref{eqn:scam} and the $\ell_\infty$ penalty in equation~\ref{eqn:dc} to encourage sparsisty. There are other forms of penalty that can also produce sparse estimates such as a penalty on the derivative of each of the component functions; we find the form we use to be convenient both for theoretical analysis and implementation.

% DO NOT CHANGE; RefTex variables -minx

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "paper.tex" ***
%%% End: ***

### 2014-04-18 tex/scam/optimization.tex
more update
paper update

--- 2013-09-29 tex/scam/optimization.tex
@@
-\section{Optimization for Sparse Convex Additive Models}
+\section{Optimization}
 
-We consider the following nonparametric regression problem
-\begin{equation}\nonumber
-          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
-                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
-\end{equation}
-where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
-response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
-functions $f_{k}(\cdot)$ in each variable dimension.  
+We describe in detail the optimization algorithm for the additive convex regression stage, the second decoupled concave regression stage follows almost identical procedure.
+
+We let $\bds{x}_{i}\in\mathbb{R}^{p}$ be the covariate, $Y_{i}$ be the
+response and $\epsilon_{i}$ be the mean zero noise. The regression function $f(\cdot)$ we estimate is the summation of 
+functions $f_{k}(\cdot)$ in each variable dimension and a scalar offset $\mu$.  
 We impose an additional constraint that each $f_{k}(\cdot)$ is 
@@
 \begin{equation}\label{hyper}
-      h_{kj} \geq h_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
+      f_{kj} \geq f_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
 \end{equation}
-where $h_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
+where $f_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
 subgradient at point $x_{ki}$. We apparently need $O(n^2 p)$ constraints to
@@
 program:
-\begin{equation}\begin{split}\label{np}
-       &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
-                     \Bigl( y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
-                         + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
-       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), 
-                                 \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
-\end{split}\end{equation}
-Where $\mu \in \R$ is a mean parameter introduced because $f$ may not have zero-mean, and where $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+\begin{equation}
+\begin{split}
+       \min_{\bds{h},\bds{\beta},\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
+                     \Bigl( Y_{i}-\sum_{k=1}^{p}f_{ki} - \mu \Bigr)^{2} 
+                         + \lambda\sum_{k=1}^{p}\|\bds{f}_{k\cdot}\|_{\infty} \\
+       \textrm{subject to} &\;\; f_{k(i+1)} = f_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \\
+                     & \;\; \sum_{i=1}^{n}f_{ki}=0,\\
+                     & \;\; \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
+\end{split}
+\label{np}
+\end{equation}
+Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+
+We can solve for $\mu$ explicitly, as  
+$\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ which follows from the
+KKT conditions
+and the constraints $\sum_i f_{ki} = 0$.
 It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
 \begin{align*}
-  \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = 
-            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = 
-            \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
-      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \forall j<i, &h_{k(j)}-h_{k(i)} =
-                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = 
-                \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
-     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
+  \forall & j\geq i, \; f_{k(j)}-f_{k(i)}  = \sum\limits_{t=i}^{j-1}(f_{k(t+1)}-f_{k(t)}) \\
+   &= \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})
+   \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) 
+  = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
+  \forall & j<i,\;  f_{k(j)}-f_{k(i)} =
+                \sum\limits_{t=j}^{i-1}(f_{k(t)}-f_{k(t+1)}) \\
+     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) 
+     \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
 \end{align*}
-The $\ell_\infty/\ell_1$ penalty
-$\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty}$ encourages group
-sparsity of the vectors $\bds{\beta}_{k\cdot}$, and thus performs
-variable selection.  We refer to this framework as the sparse convex
-additive model (SCAM). Notice that if we replace $\beta_{k(i+1)} \geq
-\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
-reduces to the lasso.  Note while one can use
-supporting hyperplanes to the epigraph as in \eqref{eq:outer}, 
-SCAM uses the \emph{inner  piece-wise linear function}
-that approximates the graph with secant lines.
 
@@
 
-The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints.
-The optimal $\mu$ has a closed form solution of $\mu = \frac{1}{n}\sum_{i=1}^n Y_i$, which is easy to derive from the KKT theorem and the constraints that $\sum_i h_{ki} = 0$ for all $k$.
-Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
-in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
-where in each step we solve the following QP subproblem for
-$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
-\begin{equation}\begin{split}\nonumber
-       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
-                       \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri}-\mu)-h_{ki}\Bigr)^{2} 
+The sparse convex additive model optimization in (\ref{np}) is a quadratic program (QP) with
+$O(np)$ variables and $O(np)$ constraints. 
+Directly applying a QP solver for $\bds{h},
+\bds{\beta}$ would be computationally expensive for relatively large
+$n$ and $p$. However, notice that variables in different feature
+dimensions are only coupled in the term
+$(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block
+coordinate descent method, where in each step we solve the following
+QP subproblem for $\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the
+other variables fixed. We present the one-block optimization in matrix notation:
+\begin{align*}
+\min_{ \bds{f}_k, \bds{\beta}_k, \gamma_k}& \frac{1}{2n} \| \bds{r}_{\mh k} - \bds{f}_k \|_2^2 
+     + \lambda \gamma_k \\
+ \textrm{s.t. } & P \bds{f}_k = \diag(P \bds{x}_k)  \bds{\beta}_k \\
+   & D \bds{\beta}_k \leq 0 ,
+   \quad -\gamma_k \mathbf{1}_n \leq \bds{f}_k \leq \gamma_k \mathbf{1}_n,
+   \quad \mathbf{1}_n^\tran \bds{f}_k = 0
+\end{align*}
+
+where $\bds{f}_k \in \R^n$ and equals $(f_{k1}, ..., f_{kn})$, $\bds{\beta}_k \in \R^{n-1}$ and equals $(\beta_{k1}, ..., \beta_{k(n-1)})$.
+$\bds{r}_{\mh k} \in \R^n$ is the residual vector: $\bds{r}_{\mh k}(i) = Y_i - \bar{Y} - \sum_{k' \neq k} f_{k' i}$.
+$\bds{x}_k \in \R^n$ and equals $(x_{k1}, ..., x_{kn})$.
+\\
+
+$P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i'$-th row $P_{i' \cdot}$ is all zero except $-1$ at the $(i')$-th smallest coordinate of $\bds{x}_k$ and $1$ at the $(i'+1)$-th smallest coordinate of $\bds{x}_k$.
+$D \in \R^{(n-2) \times (n-1)}$ is another permutation matrix where the $i'$-th row is all zero except $1$ at position $i'$ and $-1$ at position $i'+1$.
+$\diag( v )$ for a vector $v$ is a diagonal matrix whose diagonal entries are $v$.
+
+\begin{equation}
+\label{eqn:opt_1d}
+\begin{split}
+       \min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} &
+             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}
+                -\sum_{r\neq{k}}f_{ri})-f_{ki}\Bigr)^{2} 
                       + \lambda\gamma_{k} \\
-        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
-\end{split}\end{equation}
+        \textrm{such that} & \ f_{k(i+1)} = f_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}),\\
+        &\ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq f_{ki}\leq\gamma_{k}\\
+        &\  \sum_{i=1}^{n}f_{ki}=0, \ (\forall i).
+\end{split}
+\end{equation}
 The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
@@
 After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
-\begin{equation}\nonumber
-      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj})+\mu = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} + \mu.
+\begin{equation}
+\begin{split}
+\nonumber
+      f(\bds{x}_j) & = \sum_{k=1}^{p}f_k(x_{kj})+\mu \\ 
+    & = \sum_{k=1}^{p}\max_{i} \{f_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} +
+      \mu.
+\end{split}
 \end{equation}
 
+The univariate concave function estimation is a straightforward modification of optimization~\ref{eqn:opt_1d}.
+We need only modify one linear inequality constraint to enforce that the subgradients must be non-increasing: $\beta_{k(i+1)} \leq \beta_{k(i)}$.
+
 \subsection{Alternative Formulation}
-Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives. The alternative formulation replaces the ordering
+Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives, a form which we analyze in our theoretical analysis. The alternative formulation replaces the ordering
 constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity
@@
 
-It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(i)}$ and 
+It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(j)}$ and 
+\begin{align*}
+f_k(x_{k(i)}) = & f_k(x_{k(i-1)}) + \beta_{k(i-1)}(x_{k(i)} - x_{k(i-1)}) \\
+ =& f_k(x_{k1}) + \sum_{j < i} \beta_{k(j)} (x_{k(j)} - x_{k(j-1)}) \\
+ =& f_k(x_{k1}) + \sum_{j < i} \sum_{j' \leq j} d_{k(j')} (x_{k(j)} - x_{k(j-1)})\\
+ =& f_k(x_{k1}) + \sum_{j' < i} d_{k(j')} \sum_{i > j \geq j'} (x_{k(j)} - x_{k(j-1)}) \\
+ =& f_k(x_{k1}) + \sum_{j' < i} d_{k(j')} (x_{k(i)} - x_{k(j')})
+\end{align*}
+We can write this more compactly in matrix notations.
+\begin{equation*}
+\begin{split}
+\left[ \begin{array}{c}
+f_k(x_{k1}) \\
+... \\
+f_k(x_{kn}) 
+\end{array} \right] =
+\left[ \begin{array}{ccc}
+    |x_{k1} - x_{k(1)}|_+ & ... & |x_{k1} - x_{k(n-1)}|_+ \\
+    ... & & \\
+    |x_{kn} - x_{k(1)}|_+ & ... & |x_{kn} - x_{k(n-1)}|_+ 
+\end{array} \right]
+\left[ \begin{array}{c}
+    d_{k(1)} \\
+    ... \\
+    d_{k(n-1)}
+\end{array} \right] 
++ c_k \equiv \Delta_k d_k + c_k
+\end{split}
+\end{equation*}
+
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = |x_{ki} - x_{k(j)}|_+$, $d_k = (d_{k(1)} ,..., d_{k(n-1)})$, and $c_k = f_k(x_{k1})$.
+
+Because $f_k$ has to be centered, $c_k = - \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k$, therefore:
 \[
-f_k(x_{k(i)}) = f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)}
-- x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
+\Delta_k d_k + c_k \mathbf{1}_n = 
+   \Delta_k d_k - \frac{1}{n} \mathbf{1}_n \mathbf{1}_n^\tran \Delta_k d_k = 
+   \bar{\Delta}_k d_k 
 \]
-Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
-$\Delta(j,x_{ki})= x_{ki} -
-x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
-$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
-$n-1$ dimensional vector.
-Then $f_k(x_{ki}) = \Delta(x_{ki})^\tran d_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$.
-Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$.
-Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
+where $\bar{\Delta}_k \equiv \Delta_k - \frac{1}{n} \mathbf{1}_n \mathbf{1}_n^\tran \Delta_k$ is $\Delta_k$ with the mean of each column subtracted.
+
+We can now reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
 \begin{align}
-\min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
-               \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) -\mu \Bigr\|_2^2 
-               + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
-\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
-	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
+\min_{d_k}& \frac{1}{2n} 
+       \Bigl\| Y - \sum_{k=1}^p 
+              \bar{\Delta}_k d_k \Bigr\|_2^2 
+               + \lambda_n \sum_{k=1}^p \|\bar{\Delta}_k d_k \|_\infty   
+     \label{opt:alternate_opt} \\
+\trm{s.t. }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0  	
+               \qquad \trm{(convexity)} \nonumber 
 \end{align}
-$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.
 
-\begin{remark}
-\label{rem:bounded_lipschitz_constraints}
-For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|f_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $f_k$ must be $L$-Lipschitz.
-We use these constraints only in the proof for technical reasons; we never need nor use these constraints in our experiments.
-\end{remark}
+The decoupled concave postprocessing stage optimization is again similar.
+Suppose $\hat{d}_k$'s are the output of optimization~\ref{opt:alternate_opt}, define $\hat{r} = Y - \sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$.
+\begin{align}
+\textrm{for all}&\textrm{ $k$ such that $\hat{d}_k = 0$: }  \nonumber \\
+  \min_{d_k} & 
+      \frac{1}{2n} \Bigl \| \hat{r} - \bar{\Delta}_k d_k \Bigr \|_2^2
+      + \lambda_n \| \bar{\Delta}_k d_k \|_\infty 
+      \label{opt:alternate_opt_concave}\\
+ \trm{s.t.} & d_{k(2)}, \ldots, d_{k(n-1)} \leq 0 \qquad \trm{(concavity)} \nonumber
+\end{align}
+
+\textbf{Note:} in sparsistency analysis, we assume that an upper bound $L$ to the Lipschitz smoothness of the true function $f_0$ is known and that we constrain our estimate $\hat{f}$ to obey the same Lipschitz condition, that is, each $\hat{f}_k$ must be $L$-Lipschitz.
+This Lipschitz constraint can be easily added to our optimization program.
+In optimization~\ref{opt:alternate_opt}, we can enforce the Lipschitz condition by adding two constraints: $d_{k(1)} \geq - L$ and $\sum_{j=2}^{n-1} d_{k(j)} \leq L$.
+We emphasize that we use the Lipschitz constraint only in our theoretical analysis; all of our experiments do not impose any Lipschitz condition.
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2014-04-18 tex/scam/sparsistency.tex
paper update

@@
 technique''~\cite{Wain:09a}.
-Primal-dual witness explicitly solves all the dual variables, but because our optimization is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.
+Primal-dual witness explicitly solves all the dual variables, but because our optimization program is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.
 
@@
 \label{thm:deterministic}
-Let $\{\hat{d}_k, \hat{c}_k\}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$.
-Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
-Let $\hat{r} \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k -
-\hat{c}_k \mathbf{1}_n)$ be the restricted regression residual. For $k
-\in \{1,...,p\}$, Let $\Delta_{k, j} \in R^n$ be the $j$-th column of $\Delta_k$, i.e. $\max( X_k - X_{k (j)} \mathbf{1}_n, 0)$. \\
+Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
+Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\
 
-Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
-\hat{r}^\tran \Delta_{k,j}|$.
-Then $\hat{\mu}$ and $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}.
+Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
+\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\
+
+Then the following are true:
+\begin{enumerate}
+\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}.
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
+\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
+\end{enumerate}
+
 \end{theorem}
 
-This result holds regardless of whether we impose the boundedness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
-The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.
-
-\begin{remark}
-  The incoherence condition of \cite{Wain:09a} is implicitly encoded
-  in our condition on $\lambda_n, \hat{r}, \Delta_{k,j}$. We can
-  reconstruct the incoherence condition if we assume that the true
-  function $f_0$ is linear and that our fitted functions $\hat{f}_k$
-  are linear as well.
-\end{remark}
+This result holds regardless of whether we impose the Lipschitz conditions in optimization~\ref{opt:alternate_opt} and~\ref{opt:alternate_opt_concave} or not.
+The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.\\
 
@@
 rates and false positive rates separately. To control false positives,
-we study when the condition $\lambda_n > | \frac{1}{n} \hat{r}^\tran
-\Delta_{k,j}|$ is fulfilled for all $j$ and all $k \in S^c$. To
-control false negatives, we study the restricted regression.
+we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression.
 
@@
 \item Let $F$ be a distribution supported and positive on $\mathcal{X}=[-b,b]^p$. Let $X^{(1)},..., X^{(n)} \sim F$ be iid.
-\item Let $Y = f_0(X) + \epsilon$ where $\epsilon$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
-\item Let $S = \{1,...,s\}$ denote the relevant variables where $s\leq p$, i.e.,
-  $f_0(X) = f_0(X_S)$.
-\item Let $f^*_1,...,f^*_s \coloneqq \argmin_{f_1,...,f_s} \{ \E\Big(f_0(X) -\E f_0(X) - \sum_{k=1}^s f_k(X_k)\Big)^2 \,|\, \E[f_k(X_k)] = 0 \}$.
+\item Let $Y = f_0(X) + w$ where $w$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
+\item Let $S_0 = \{1,...,s_0\}$ denote the relevant variables where $s_0 \leq p$, i.e.,
+  $f_0(X) = f_0(X_{S_0})$.
 \end{packed_enum}
+
+Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Define $\mathcal{C}^{p}$ as the set of convex additive function
+$\mathcal{C}^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
+   f_k \in \mathcal{C}^1 \} $
+Let $f^*(x) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk minimizer:
+$f^* \equiv \arg\min_{f \in \mathcal{C}^p} \E\big(f_0(X) - f^*(X) \big)^2$.\\
+
+Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and let 
+$g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X) - g_k(X_k) \big)^2$. \\
+
+We let $S = \{ k = 1,...,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
 
@@
 \begin{packed_enum}
-\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
-\item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
-  twice-differentiable, and $L$-Lipschitz.
-\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
-\item[A4:] For all $k=1,...,s$, $\E(f^*_s(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
+\item[A1:] $X_S, X_{S^c}$ are independent. 
+\item[A2:] $f_0$ is convex and twice-differentiable. 
+\item[A3:] $|\partial_{x_k} f_0 | \leq L$ for all $k$
+\item[A4:] $w$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
 \end{packed_enum}
+By assumption A1, $f^*_k$ is must be zero for $k\notin \{1,...,s\}$.
 
-We will use assumptions A1, A2, A3 to control the probability of false
-positives and the stronger assumptions A1', A2', A3, A4 to control the
-probability of false negatives.  Assumption A4 can be
-weakened so that the relevant functions satisfy
-$\E(f^*_s(X_k))^2 \geq \alpha_n$ for $\alpha_n$ decaying to zero 
-at an appropriate rate.
+We define $\alpha_f, \alpha_g$ as a measure of the signal strength of the weakest variable:
+\begin{align*}
+\alpha_f &= \inf_{f \in \mathcal{C}^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
+        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
+\alpha_g &=   \min_{k \in S \,:\, g^*_k \neq 0}
+      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
+    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}
+\end{align*}
+
+Intuitively, if $\alpha_f$ is smaller, then it is easier to make a false omission in the additive convex stage of the procedure.
+If $\alpha_g$ is smaller, then it is easier to make a false omission in the decoupled concave stage of the procedure.
 
@@
   very weak assumptions on the true regression function $f_0$ in
-  A2. In particular, we do not assume that $f_0$ is additive. Relaxing
-  these assumptions is an interesting direction for future work. 
+  A2. In particular, we do not assume that $f_0$ is additive. 
   %Strong assumptions on the covariates are not uncommon in nonparametric
@@
 
-\begin{remark}
-Assumption A4 ensures that the relevant variables are ``relevant enough''.
-Under A4, the population risk of an additive function with $s-1$ components is at least $\alpha$ larger than the population risk of the optimal additive function with $s$ components.
-See lemma~\ref{lem:minus_one_risk_increase} in section~\ref{sec:false_negative_proof} of the appendix.
-\end{remark}
+\begin{theorem} (Controlling false positives) \\
+\label{thm:false_positive}
+Suppose assumptions A1-A4 hold.
 
-\begin{theorem} (Controlling false positives) 
-\label{thm:false_positive}
-Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\eqref{opt:alternate_opt} with the $B$-boundness constraint. Let $c,C$ be absolute constants.
-Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n
-  \log (pn)}$.  Then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$, $\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|$.
-Therefore, any solution to the full regression (\ref{opt:alternate_opt}), with boundedness constraint, is zero on $S^c$. 
+Suppose $\lambda_n \geq \mathbf{c} s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
+\[
+\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
+\]
+
+And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\ref{opt:alternate_opt_concave} are zero.
+\\
 \end{theorem}
@@
 The proof of Theorem~\ref{thm:false_positive} exploits independence of
-$\hat{r}$ and $\Delta_{k,j}$ from A1, and then uses concentration of
-measure results to argue that $| \frac{1}{n} \hat{r}^\tran
-\Delta_{k,j}|$ concentrates around zero at a desired rate. The fact
-that $\hat{r}$ is a centered vector is crucial to our proof, and our
-theory thus further illustrates the importance of imposing the
-centering constraints in optimization \eqref{opt:alternate_opt}. Our
-proof uses the concentration of the average of
-data sampled \emph{without} replacement
-\cite{serfling1974probability}. The full proof of
+$\hat{r}$ and $X_k$ from A1; when $\hat{r}$ and $X_k$ are independent, $\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random coordinates of $\hat{r}$.
+We can then uses the concentration of measure result for sampling without replacement to argue that $| \frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high probability.
+The full proof of
 Theorem~\ref{thm:false_positive} is in
@@
 
-\begin{theorem} (Controlling false negatives)
+\begin{theorem} (Controlling false negatives) \\
 \label{thm:false_negative}
-Suppose assumptions A1', A2', A3, A4 hold.
-Let $\ds \hat{f} = \{ \hat{d}_k, \hat{c}_k\}_{k\in S}$ be any solution to the restricted regression with both the $B$-boundedness and $L$-Lipschitz constraint.
-Let $c,C$ be absolute constants.
-Suppose $s L \lambda_n \rightarrow 0$ and $Lb(sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.
-Then, for sufficiently large $n$, $\hat{f}_k = (\hat{d}_k, \hat{c}_k)
-\neq 0$ for all $k \in S$ with probability at least $1-\frac{C}{n}$.
+Suppose assumptions A1-A4 hold.
+Let $\hat{f}$ be any AC solution to the restricted regression with $L$-Lipschitz constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $L$-Lipschitz constraint.\\
+
+Suppose $\lambda \leq \mathbf{c} sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\
+
+Suppose 
+$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+
+Then, with probability at least $1 - \frac{1}{n}$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.
+
 \end{theorem}
@@
 Combining Theorem~\ref{thm:false_positive} and
-~\ref{thm:false_negative} and ignoring dependencies on $b,B,L,\sigma$,
+~\ref{thm:false_negative} 
 we have the following result.
 \begin{corollary}
-  Assume A1', A2', A3, A4. Let $\lambda_n = \Theta\left( \sqrt{
-  \frac{s^3}{n} \log n \log (pn)} \right)$. Suppose $s \lambda_n
-  \rightarrow 0$ and $\sqrt{\frac{s^5}{n^{4/5}} \log sn} \rightarrow
-  0$. Let $\hat{f_n}$ be a solution to (\ref{opt:alternate_opt}) with
-  boundedness and Lipschitz constraints. Then 
-  $\P( \trm{supp}(\hat{f_n}) = \trm{supp}(f_0) ) \rightarrow 1$.
+Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints, both with 
+$\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\
+
+Suppose 
+$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+
+Then, for all large enough $n$, we have that with probability at least $1-\frac{1}{n}$:
+\begin{align*}
+\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
+\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S
+\end{align*}
+
 \end{corollary}

### 2014-04-24 tex/scam/optimization.tex
experiment code

@@
 other variables fixed. We present the one-block optimization in matrix notation:
-\begin{align*}
+\begin{align}
 \min_{ \bds{f}_k, \bds{\beta}_k, \gamma_k}& \frac{1}{2n} \| \bds{r}_{\mh k} - \bds{f}_k \|_2^2 
-     + \lambda \gamma_k \\
- \textrm{s.t. } & P \bds{f}_k = \diag(P \bds{x}_k)  \bds{\beta}_k \\
+     + \lambda \gamma_k \label{opt:1d_compact} \\
+ \textrm{s.t. } & P \bds{f}_k = \diag(P \bds{x}_k)  \bds{\beta}_k \nonumber \\
    & D \bds{\beta}_k \leq 0 ,
    \quad -\gamma_k \mathbf{1}_n \leq \bds{f}_k \leq \gamma_k \mathbf{1}_n,
-   \quad \mathbf{1}_n^\tran \bds{f}_k = 0
-\end{align*}
+   \quad \mathbf{1}_n^\tran \bds{f}_k = 0 \nonumber
+\end{align}
 
@@
 
-\begin{equation}
-\label{eqn:opt_1d}
-\begin{split}
-       \min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} &
-             \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}
-                -\sum_{r\neq{k}}f_{ri})-f_{ki}\Bigr)^{2} 
-                      + \lambda\gamma_{k} \\
-        \textrm{such that} & \ f_{k(i+1)} = f_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}),\\
-        &\ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq f_{ki}\leq\gamma_{k}\\
-        &\  \sum_{i=1}^{n}f_{ki}=0, \ (\forall i).
-\end{split}
-\end{equation}
+% \begin{equation}
+% \label{eqn:opt_1d}
+% \begin{split}
+%        \min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} &
+%              \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((Y_{i}-\bar{Y}
+%                 -\sum_{r\neq{k}}f_{ri})-f_{ki}\Bigr)^{2} 
+%                       + \lambda\gamma_{k} \\
+%         \textrm{such that} & \ f_{k(i+1)} = f_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}),\\
+%         &\ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq f_{ki}\leq\gamma_{k}\\
+%         &\  \sum_{i=1}^{n}f_{ki}=0, \ (\forall i).
+% \end{split}
+% \end{equation}
 The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
@@
 \nonumber
-      f(\bds{x}_j) & = \sum_{k=1}^{p}f_k(x_{kj})+\mu \\ 
-    & = \sum_{k=1}^{p}\max_{i} \{f_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} +
+      f(\bds{x}_j) & = \sum_{k=1}^{p}f_k(x_{kj})+\mu 
+= \sum_{k=1}^{p}\max_{i} \{f_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} +
       \mu.
@@
 
-The univariate concave function estimation is a straightforward modification of optimization~\ref{eqn:opt_1d}.
+The univariate concave function estimation is a straightforward modification of optimization~\ref{opt:1d_compact}.
 We need only modify one linear inequality constraint to enforce that the subgradients must be non-increasing: $\beta_{k(i+1)} \leq \beta_{k(i)}$.
@@
 \end{array} \right] 
-+ c_k \equiv \Delta_k d_k + c_k
++ \mu_k \equiv \Delta_k d_k + \mu_k
 \end{split}
@@
 
-Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = |x_{ki} - x_{k(j)}|_+$, $d_k = (d_{k(1)} ,..., d_{k(n-1)})$, and $c_k = f_k(x_{k1})$.
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = |x_{ki} - x_{k(j)}|_+$, $d_k = (d_{k(1)} ,..., d_{k(n-1)})$, and $\mu_k = f_k(x_{k1})$.
 
-Because $f_k$ has to be centered, $c_k = - \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k$, therefore:
+Because $f_k$ has to be centered, $\mu_k = - \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k$, therefore:
 \[
-\Delta_k d_k + c_k \mathbf{1}_n = 
+\Delta_k d_k + \mu_k \mathbf{1}_n = 
    \Delta_k d_k - \frac{1}{n} \mathbf{1}_n \mathbf{1}_n^\tran \Delta_k d_k = 
@@
 \textrm{for all}&\textrm{ $k$ such that $\hat{d}_k = 0$: }  \nonumber \\
-  \min_{d_k} & 
-      \frac{1}{2n} \Bigl \| \hat{r} - \bar{\Delta}_k d_k \Bigr \|_2^2
-      + \lambda_n \| \bar{\Delta}_k d_k \|_\infty 
+  \min_{c_k} & 
+      \frac{1}{2n} \Bigl \| \hat{r} - \Delta_k c_k \Bigr \|_2^2
+      + \lambda_n \| \Delta_k c_k \|_\infty 
       \label{opt:alternate_opt_concave}\\
- \trm{s.t.} & d_{k(2)}, \ldots, d_{k(n-1)} \leq 0 \qquad \trm{(concavity)} \nonumber
+ \trm{s.t.} & c_{k(2)}, \ldots, c_{k(n-1)} \leq 0 \qquad \trm{(concavity)} \nonumber
 \end{align}
 
-\textbf{Note:} in sparsistency analysis, we assume that an upper bound $L$ to the Lipschitz smoothness of the true function $f_0$ is known and that we constrain our estimate $\hat{f}$ to obey the same Lipschitz condition, that is, each $\hat{f}_k$ must be $L$-Lipschitz.
+We can use either the off-centered $\Delta_k$ matrix or the centered $\bar{\Delta}_k$ matrix because the concave estimations are decoupled and hence suffer no identifiability problems.\\
+
+\begin{remark}
+in sparsistency analysis, we assume that $L$, an upper bound to the coordinate-wise Lipschitz smoothness of the true function $f_0$, is known and that we constrain our estimate $\hat{f}$ to obey the same Lipschitz condition, that is, each $\hat{f}_k$ must be $L$-Lipschitz.
 This Lipschitz constraint can be easily added to our optimization program.
-In optimization~\ref{opt:alternate_opt}, we can enforce the Lipschitz condition by adding two constraints: $d_{k(1)} \geq - L$ and $\sum_{j=2}^{n-1} d_{k(j)} \leq L$.
+In optimization~\ref{opt:alternate_opt}, we can enforce the Lipschitz condition by adding two constraints: $d_{k(1)} \geq - L$ and $\sum_{j=2}^{n-1} d_{k(j)} \leq L$ (similarly for optimization~\ref{opt:alternate_opt_concave}).
 We emphasize that we use the Lipschitz constraint only in our theoretical analysis; all of our experiments do not impose any Lipschitz condition.
+\end{remark}
 

### 2014-04-24 tex/scam/sparsistency.tex
experiment code

@@
 
-We divide our analysis into two parts. We first establish a sufficient
-\emph{deterministic} condition for sparsistency.  We then consider the
+We divide our analysis into two parts. We first establish a sufficient deterministic condition for sparsistency.  We then consider the
 stochastic setting and argue that the deterministic conditions hold with high probability.
@@
 
-We follow \cite{Wain:09a} and define the \emph{restricted regression} purely for theoretical purposes.
+We construct an additive convex solution $\{\hat{d}_k\}_{k=1,...,p}$ that is zero for $k \in S^c$ and show that it satisfies the KKT conditions for optimality of optimization~\ref{opt:alternate_opt}.
+We define $\hat{d}_k$ for $k \in S$ to be a solution to the restricted regression (defined below).
+We will then also show that $\hat{c}_k = 0$ satisfies the optimality condition of optimization~\ref{opt:alternate_opt_concave} for all $k \in S^c$.
+
 \begin{definition}
+\label{def:restricted_regression}
 In \emph{restricted regression}, we restrict the indices $k$ in
-optimization (\ref{opt:alternate_opt}) to lie in the support $S$ instead of ranging from $1,...,p$. 
+optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$. 
 \end{definition}
@@
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
-\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
+\item For all $k \in S^c$, the solution $\hat{c}_k$ to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
 \end{enumerate}

### 2014-04-24 code/paper_exp/C.m

@@ -1,0 +1,83 @@
+function C(version)
+% Diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 100; v = 0.0;
+    case 01, n = 100; v = 0.0;
+    case 02, n = 200; v = 0.0;
+    case 03, n = 300; v = 0.0;
+    case 04, n = 400; v = 0.0;
+    case 05, n = 500; v = 0.0;
+    case 06, n = 600; v = 0.0;
+    case 07, n = 700; v = 0.0;
+    case 08, n = 800; v = 0.0;
+    case 09, n = 900; v = 0.0;
+    case 10, n =1000; v = 0.0;
+        
+    case 11, n = 100; v = 0.2;
+    case 12, n = 200; v = 0.2;
+    case 13, n = 300; v = 0.2;
+    case 14, n = 400; v = 0.2;
+    case 15, n = 500; v = 0.2;
+    case 16, n = 600; v = 0.2;
+    case 17, n = 700; v = 0.2;
+    case 18, n = 800; v = 0.2;
+    case 19, n = 900; v = 0.2;
+    case 20, n =1000; v = 0.2;
+        
+    case 21, n = 100; v = 0.5;
+    case 22, n = 200; v = 0.5;
+    case 23, n = 300; v = 0.5;
+    case 24, n = 400; v = 0.5;
+    case 25, n = 500; v = 0.5;
+    case 26, n = 600; v = 0.5;
+    case 27, n = 700; v = 0.5;
+    case 28, n = 800; v = 0.5;
+    case 29, n = 900; v = 0.5;
+    case 30, n =1000; v = 0.5;
+  
+    case 31, n = 100; v = 0.9;
+    case 32, n = 200; v = 0.9;
+    case 33, n = 300; v = 0.9;
+    case 34, n = 400; v = 0.9;
+    case 35, n = 500; v = 0.9;
+    case 36, n = 600; v = 0.9;
+    case 37, n = 700; v = 0.9;
+    case 38, n = 800; v = 0.9;
+    case 39, n = 900; v = 0.9;
+    case 40, n =1000; v = 0.9;
+    otherwise, return
+end
+
+p = 128; k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6;
+nrun = 200; J = ones(p,nrun)==0; Ln = zeros(p,nrun); Q = eye(k);
+
[…]

### 2014-04-24 code/paper_exp/C1.m

@@ -1,0 +1,66 @@
+function C1(version)
+% Non-diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 500; v = 0.8;
+    case 01, n = 100; v = 0.2;
+    case 02, n = 200; v = 0.2;
+    case 03, n = 300; v = 0.2;
+    case 04, n = 400; v = 0.2;
+    case 05, n = 500; v = 0.2;
+    case 06, n = 600; v = 0.2;
+    case 07, n = 700; v = 0.2;
+    case 08, n = 800; v = 0.2;
+    case 09, n = 900; v = 0.2;
+    case 10, n =1000; v = 0.2;
+        
+    case 11, n = 100; v = 0.4;
+    case 12, n = 200; v = 0.4;
+    case 13, n = 300; v = 0.4;
+    case 14, n = 400; v = 0.4;
+    case 15, n = 500; v = 0.4;
+    case 16, n = 600; v = 0.4;
+    case 17, n = 700; v = 0.4;
+    case 18, n = 800; v = 0.4;
+    case 19, n = 900; v = 0.4;
+    case 20, n =1000; v = 0.4;
+        
+    case 21, n = 100; v = 0.6;
+    case 22, n = 200; v = 0.6;
+    case 23, n = 300; v = 0.6;
+    case 24, n = 400; v = 0.6;
+    case 25, n = 500; v = 0.6;
+    case 26, n = 600; v = 0.6;
+    case 27, n = 700; v = 0.6;
+    case 28, n = 800; v = 0.6;
+    case 29, n = 900; v = 0.6;
+    case 30, n =1000; v = 0.6;
+        
+    case 31, n = 100; v = 0.8;
+    case 32, n = 200; v = 0.8;
+    case 33, n = 300; v = 0.8;
+    case 34, n = 400; v = 0.8;
+    case 35, n = 500; v = 0.8;
+    case 36, n = 600; v = 0.8;
+    case 37, n = 700; v = 0.8;
+    case 38, n = 800; v = 0.8;
+    case 39, n = 900; v = 0.8;
+    case 40, n =1000; v = 0.8;
+    otherwise, return
+end
+
+p = 128; k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6;
[…]

### 2014-04-24 code/paper_exp/Midway.m

@@ -1,0 +1,16 @@
+function submit = Midway(core,mode)
+submit =['module load matlab; '];
+for i = 0:mode
+    submit = [submit 'sbatch ' core '_' num2str(i) '.sbatch; '];
+    fid = fopen([core '_' num2str(i) '.sbatch'],'W');
+    fprintf(fid,'#!/bin/bash\n');
+    fprintf(fid,'#SBATCH --output=%s\n',[core '_' num2str(i) '.txt']);
+    fprintf(fid,'#SBATCH --job-name=%s\n',[core '_' num2str(i)]);
+    fprintf(fid,'#SBATCH --partition=bigmem\n');
+    % fprintf(fid,'cd $Home/rcchelp/software/matlab.rcc-docs');
+    fprintf(fid,'module load matlab\n');
+    fprintf(fid,'matlab -nodisplay  -r "%s(%d)"\n', core,i);
+    fclose(fid);
+end
+disp(submit);
+return

### 2014-04-24 code/paper_exp/R.m

@@ -1,0 +1,124 @@
+function R(version)
+% Non-diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 100; alpha = 0.2;
+    case 01, n = 100; alpha = 0.0;
+    case 02, n = 200; alpha = 0.0;
+    case 03, n = 300; alpha = 0.0;
+    case 04, n = 400; alpha = 0.0;
+    case 05, n = 500; alpha = 0.0;
+    case 06, n = 600; alpha = 0.0;
+    case 07, n = 700; alpha = 0.0;
+    case 08, n = 800; alpha = 0.0;
+    case 09, n = 900; alpha = 0.0;
+    case 10, n =1000; alpha = 0.0;
+        
+    case 11, n = 100; alpha = 0.2;
+    case 12, n = 200; alpha = 0.2;
+    case 13, n = 300; alpha = 0.2;
+    case 14, n = 400; alpha = 0.2;
+    case 15, n = 500; alpha = 0.2;
+    case 16, n = 600; alpha = 0.2;
+    case 17, n = 700; alpha = 0.2;
+    case 18, n = 800; alpha = 0.2;
+    case 19, n = 900; alpha = 0.2;
+    case 20, n =1000; alpha = 0.2;
+        
+    case 21, n = 100; alpha = 0.5;
+    case 22, n = 200; alpha = 0.5;
+    case 23, n = 300; alpha = 0.5;
+    case 24, n = 400; alpha = 0.5;
+    case 25, n = 500; alpha = 0.5;
+    case 26, n = 600; alpha = 0.5;
+    case 27, n = 700; alpha = 0.5;
+    case 28, n = 800; alpha = 0.5;
+    case 29, n = 900; alpha = 0.5;
+    case 30, n =1000; alpha = 0.5;
+        
+    case 31, n = 100; alpha = 1.0;
+    case 32, n = 200; alpha = 1.0;
+    case 33, n = 300; alpha = 1.0;
+    case 34, n = 400; alpha = 1.0;
+    case 35, n = 500; alpha = 1.0;
+    case 36, n = 600; alpha = 1.0;
+    case 37, n = 700; alpha = 1.0;
+    case 38, n = 800; alpha = 1.0;
+    case 39, n = 900; alpha = 1.0;
+    case 40, n =1000; alpha = 1.0;
+    otherwise, return
+end
+
[…]

### 2014-04-24 code/paper_exp/SCAM.m

@@ -1,0 +1,49 @@
+% Run SCAM on Boston housing data. 
+% Use 5-fold CV and plot prediction error
+
+function SCAM(version)
+clc; close all; format long; randn('state',0); rand('state',0);
+lambda0 = {[0.00 .005 0.01 .015 0.02 0.04 0.06 ...
+            0.07 0.08 0.09 0.10 0.12 0.20 0.30 0.40],...
+           };
+nd = size(lambda0,2); nv = zeros(1,nd); 
+
+for i = 1:nd, nv(i) = length(lambda0{i}); end
+
+data = sum(version>cumsum(nv)) + 1; 
+lambda = lambda0{data}(version - sum(nv(1:data-1)));
+
+switch data
+    case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
+    % case 2, 
+    otherwise, return
+end
+
+[p,n] = size(X); mrun = 10; b = 5; m = fix(n/b); % 5-fold CV
+err = zeros(2,mrun); num = zeros(1,mrun);
+
+for run = 1:mrun
+    ord = randperm(n);
+    for i = 1:b
+        ndx = ones(n,1)==0;
+        if i<b, ndx(ord((i-1)*m+1:i*m))=1==1; else ndx(ord((i-1)*m+1:end))=1==1; end
+        [erri,numi] = SCAM_Main(X,y,ndx,lambda);
+        err(:,run) = err(:,run) + erri./[b-1; 1]; num(run) = num(run) + numi/b;
+        disp(['run=' num2str(run) ' cv=' num2str(i)]);
+    end
+end
+
+out = [mean(num) mean(err,2)' std(err,1,2)']
+save(['SCAM/SCAM_' num2str(version) '.mat'],'out');
+return
+
+function [err,num,yo] = SCAM_Main(X,y,ndx,lambda)
+[p,n] = size(X); [X1,X2] = SCAM_Unit(X,ndx);
+y1 = y(~ndx); ym = mean(y1); y2 = y(ndx); maxit = 20; tol = 10^-6;
+[beta0,h0,obj0,Ln0] = SCAM_QP(X1,y1-ym,lambda,maxit,tol);
+active = find(abs(Ln0)>10^-8); num = length(active);
+[beta1,h1,obj1,Ln1] = SCAM_QP(X1(active,:),y1-ym,0,maxit,tol);
[…]

### 2014-04-24 code/paper_exp/SCAM_MOSEK_f.m

@@ -1,0 +1,67 @@
+
+%
+% performs SCAM_MOSEK with L1 penalty on function value
+% 
+% minimize over {f, beta, gamma}
+
+function [beta,z,Ln] = SCAM_MOSEK_f(y,x,lambda)
+n = length(x); [Xd,ord] = sort(x'); dX = Xd(2:n)-Xd(1:n-1);
+Hi = 1:2*n; Hj = 1:2*n; Hs = [ones(1,n)/n,10^-6*ones(1,n)];
+
+% Use 10^-6 instead of 0 to make this QP strictly convex.
+H = sparse(Hi,Hj,Hs,2*n,2*n); f = [-y/n; zeros(n-1,1); lambda];
+Ai = []; Aj = []; As = []; row = 0; ndx = 0;
+
+%variable ordering:
+% function values: 1:n
+% beta: (n+1):(2*n-1)
+% gamma: 2*n
+
+valmat = [ones(n-2,1) -ones(n-2,1)];
+rowmat = [(1:(n-2))' (1:(n-2))'] + row;
+colmat = [((n+1):(2*n-2))' ((n+2):(2*n-1))'];
+rg = (ndx+1):(ndx+2*(n-2)); row = row + (n-2); ndx = ndx + 2*(n-2);
+Ai(rg) = rowmat(:); Aj(rg) = colmat(:); As(rg) = valmat(:);
+
+
+
+
+% gamma inequalities
+%valmat = [ones(n-1,1) -ones(n-1,1) -ones(n-1,1) -ones(n-1,1)];
+valmat = [ones(n,1), -ones(n,1), -ones(n,1), -ones(n,1)];
+%rowmat = [(1:(n-1))' (1:(n-1))' (n:(2*n-2))' (n:(2*n-2))'] + row;
+rowmat = [(1:n)' (1:n)' ((n+1):(2*n))' ((n+1):(2*n))'] + row;
+%colmat = [((n+1):(2*n-1))' 2*n*ones(n-1,1) ...
+%          ((n+1):(2*n-1))' 2*n*ones(n-1,1)];
+colmat = [(1:n)' 2*n*ones(n, 1) ...
+          (1:n)' 2*n*ones(n, 1)];
+%rg = (ndx+1):(ndx+4*(n-1)); row = row + 2*(n-1); ...
+%      ndx = ndx + 4*(n-1);
+rg = (ndx+1):(ndx+4*n); 
[…]

### 2014-04-24 code/paper_exp/T.m

@@ -1,0 +1,82 @@
+function T(version)
+% Diagonal quadratic with noise.
+clc; close all; format long; randn('state',0); rand('state',0); 
+switch version
+    case 00, n = 100; p = 064;
+    case 01, n = 100; p = 064;
+    case 02, n = 200; p = 064;
+    case 03, n = 300; p = 064;
+    case 04, n = 400; p = 064;
+    case 05, n = 500; p = 064;
+    case 06, n = 600; p = 064;
+    case 07, n = 700; p = 064;
+    case 08, n = 800; p = 064;
+    case 09, n = 900; p = 064;
+    case 10, n =1000; p = 064;
+        
+    case 11, n = 100; p = 128;
+    case 12, n = 200; p = 128;
+    case 13, n = 300; p = 128;
+    case 14, n = 400; p = 128;
+    case 15, n = 500; p = 128;
+    case 16, n = 600; p = 128;
+    case 17, n = 700; p = 128;
+    case 18, n = 800; p = 128;
+    case 19, n = 900; p = 128;
+    case 20, n =1000; p = 128;
+        
+    case 21, n = 100; p = 256;
+    case 22, n = 200; p = 256;
+    case 23, n = 300; p = 256;
+    case 24, n = 400; p = 256;
+    case 25, n = 500; p = 256;
+    case 26, n = 600; p = 256;
+    case 27, n = 700; p = 256;
+    case 28, n = 800; p = 256;
+    case 29, n = 900; p = 256;
+    case 30, n =1000; p = 256;
+  
+    case 31, n = 100; p = 512;
+    case 32, n = 200; p = 512;
+    case 33, n = 300; p = 512;
+    case 34, n = 400; p = 512;
+    case 35, n = 500; p = 512;
+    case 36, n = 600; p = 512;
+    case 37, n = 700; p = 512;
+    case 38, n = 800; p = 512;
+    case 39, n = 900; p = 512;
+    case 40, n =1000; p = 512;
+    otherwise, return
+end
+
+k = 5; lambda = 4*sqrt(log(n*p)/n); maxit = 20; tol = 10^-6;
+nrun = 200; J = ones(p,nrun)==0; Ln = zeros(p,nrun); Q = eye(k);
+
+for run = 1:nrun
+    ord = randperm(p); J(ord(1:k),run) = 1==1; X = randn(p,n); 
[…]

### 2014-04-24 code/paper_exp/acdc_QP.m

@@ -1,0 +1,55 @@
+% 
+
+function [beta,z,obj,Ln] = acdc_QP(X,y,lambda,maxit,tol)
+[p,n] = size(X); z = zeros(p,n); beta = zeros(p,n-1);
+
+Ln = zeros(p,1); 
+Ln2 = zeros(p,1);
+
+res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
+obj = zeros(maxit,1);
+
+%SCAM
+while iter < maxit && change > tol
+    iter = iter + 1;
+    
+    for d = 1:p
+        res = res + z(d,:)';
+        [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK_f(res,X(d,:),lambda);
+        res = res - z(d,:)';
+    end
+    
+    obj(iter) = 0.5/n*sum(res.^2) + lambda*sum(Ln);
+    
+    if iter>1
+        change = abs(obj(iter-1)-obj(iter))/obj(iter-1); 
+    end
+    
+    if mod(iter,10)==0
+        disp(['   SCAM_QP:    Iteration ' num2str(iter) ...
+              ' Objective ' num2str(obj(iter))]);
+        
+        figure(9); subplot(2,1,1); 
+        plot(1:n,y,'ko',1:n,sum(z,1)','r+'); 
+        title('Response');
+        
+        subplot(2,1,2); plot(1:p,Ln,'r.'); 
+        title('L\infty norm'); drawnow;
+    end
+end
+
+%postprocessing
+for d=1:p
+    if Ln(d) > 1e-5
+        continue
+    end
+    res = res + z(d,:)';
+    [~, ~, Ln2(d)] = SCAM_MOSEK_f(-res, X(d,:), lambda);
+    res = res - z(d,:)';
+end
+
+Ln = max(Ln, Ln2);
+
+
+return
+

### 2014-04-24 code/paper_exp/acdc_test.m

@@ -1,0 +1,54 @@
+n = 500;
+alpha = 0.5;
+v = 0.3;
+
+p = 64; 
+k = 4; 
+
+lambda = 0.5*sqrt(1/n)*log(n*p); 
+maxit = 20; tol = 10^-6;
+
+nrun = 5; 
+
+J = ones(p,nrun)==0; 
+Ln = zeros(p,nrun);
+
+
+if alpha<10^-16
+    Q = eye(k); 
+else
+    Q = 0.5*eye(k); 
+    B0 = rand(k,k) < alpha;
+    for i = 1:k
+        for j = 1:i
+            if B0(i,j) && i~=j
+                Q(i,j) = 0.5; 
+            end; 
+        end; 
+    end; Q = Q + Q';
+end
+
+for run = 1:nrun
+    %ord = randperm(p); 
+    ord = 1:p;
+    J(ord(1:k),run) = 1==1; 
+    
+    %X = randn(p,n); 
+    X = mvnrnd(zeros(1,p), toeplitz(v.^(0:p-1)), n)';
+    
+    y = sum(X(J(:,run),:).*(Q*X(J(:,run),:)),1)' + randn(n,1);
+    % main function call
+    [beta,h,obj,Ln(:,run)] = acdc_QP(X, y-mean(y), lambda, maxit, tol);
+    %[beta,h,obj,Ln(:,run)] = SCAM_QP(X,y-mean(y),lambda,maxit,tol);
+    disp(['version=' num2str(version) ' run=' num2str(run)]);
+end
+
+prob = 0; epsil = 10^-7;
+
+nrun = size(Ln,2); suc = 0;
+for run = 1:nrun
+    if max(Ln(~J(:,run),run)) < epsil && min(Ln(J(:,run),run)) > epsil
+        suc = suc + 1;
+    end
+end
+prob = suc/nrun;

### 2014-05-05 tex/scam/appendix.tex
paper modifications

@@
 
-Suppose $\lambda_n \geq \mathbf{c} s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
+Suppose $\lambda_n \geq c s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
 \[
@@
 
-Because $w_i$ is subgaussian, $|w_i| \leq \mathbf{c} \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
-By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.
+Because $w_i$ is subgaussian, $|w_i| \leq c \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq c \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.
 
@@
 \begin{align*}
-\| \hat{r} \|_\infty &\leq \mathbf{c} (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
-      &\leq \mathbf{c} sLb \sigma \sqrt{\log \frac{2}{\delta}}
+\| \hat{r} \|_\infty &\leq c (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
+      &\leq c sLb \sigma \sqrt{\log \frac{2}{\delta}}
 \end{align*}
@@
 | \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
-  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
+  &\leq c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
 \end{align*}
@@
 \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
-  \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
+  c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
 \end{align*}
@@
 \label{thm:convex_consistent}
-Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq \mathbf{c} sLb\sqrt{ \frac{1}{n} \log^2 np}$.
+Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sLb\sqrt{ \frac{1}{n} \log^2 np}$.
 
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq \mathbf{c} (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
+&\leq c (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
 \end{align}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + c(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
 \end{align}
@@
 
-According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma \mathbf{c} \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
+According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
 \[
 P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
-  4 \exp \Big( - \frac{ n \epsilon^2}{ \mathbf{c} R^2 \sigma^2} \Big)
+  4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
 \]
@@
 \sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
-   \mathbf{c} R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
+   c R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
       \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
-       \mathbf{c} \sigma \sqrt{\frac{1}{n}} 
+       c \sigma \sqrt{\frac{1}{n}} 
 \]
@@
  &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
- &= \sqrt{C s^{1.5} b L} \, \mathbf{c} (sLb)^{3/4} \\
- &\leq \mathbf{c} (s b L)^2
+ &= \sqrt{C s^{1.5} b L} \, c (sLb)^{3/4} \\
+ &\leq c (s b L)^2
 \end{align*}
@@
 \sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
-    \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
-    \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
- &\leq \mathbf{c} (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
+   c sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
+    c (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
+ &\leq c (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
 \end{align*}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
-   + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
+   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+   + \lambda 4 s L b + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
    + \lambda 4 s L b    \label{eqn:second_step_inequality}
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
- +\lambda 4 s L b + \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
+ +\lambda 4 s L b + c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
+&\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
 \end{align}
 
-Substituting in $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
+Substituting in $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
 
@@
 \label{thm:concave_consistent}
-Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$.\\
+Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$.\\
 
@@
 \[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  \mathbf{c}(Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c (Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
 \]
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
+  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
-  \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
- &\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
+  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
+  c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
+ &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
+\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
     2Lb \sqrt{\frac{1}{n} \log^2 np}\\
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
+\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
 \end{align*}
@@
    + 2 \langle f_0 - f^*, g^*_k \rangle \\
- &\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
+ &\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
     2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
- &\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+ &\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
     2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
-&\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
-   \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+&\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+   c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                    \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
-&\leq  \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+&\leq  c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                    \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
@@
 \| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
-   \mathbf{c}(Lb)^{2.5} \sigma^{0.5} 
+   c (Lb)^{2.5} \sigma^{0.5} 
      \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
@@
 \sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
-   \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+   c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
 \end{align*}
@@
      + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
-  &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+  &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
 \end{align*}
@@
 \Big | \| f_0 - f^* \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 \Big| \leq
-    \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
+    c (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
 \]
@@
 \begin{align*}
-| \bar{f}^* | | \bar{f}_0 | &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
-\bar{f}^{*2} &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+| \bar{f}^* | | \bar{f}_0 | &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
+\bar{f}^{*2} &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
 \end{align*}
@@
 \[
-\|f_0 - f^*\|_n^2 - \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
+\|f_0 - f^*\|_n^2 - c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
     \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
-\|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+\|f_0 - f^*\|_n^2 + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
 \]

### 2014-05-05 tex/scam/paper.tex
paper update
paper modifications

@@
 \usepackage{authblk}
+
+\usepackage{yhmath}
 
@@
 \begin{document}
+
+% min's macros
+\mathchardef\mh="2D
 
@@
 \begin{abstract}
-  We consider the problem of estimating a sparse convex function of
-  many variables.  In constrast to classical nonparametric
-  regression with smoothness constraints, we show that convexity is
-  additively faithful---it suffices to estimate a convex additive
-  model for variable selection.  We develop algorithms for estimating
-  sparse convex additive models, including an approach using iterative
-  quadratic programming.  Supporting experiments and statistical
-  theory are presented, showing variable selection consistency in
-  dimensions that can scale exponentially in the sample size.  An
-  attractive feature of this framework is the lack of tuning parameters
-  for smoothness.
+We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points. 
 \end{abstract}
@@
 \input{additive_faithful}
+\input{estimation}
 \input{optimization}

### 2014-05-05 tex/scam/sparsistency.tex
paper modifications

@@
 stochastic setting and argue that the deterministic conditions hold with high probability.
+In all of our results and analysis, we let $c, C$ represent absolute constants; the actual values of $c,C$ could change from line to line.
 
@@
 \label{def:restricted_regression}
-In \emph{restricted regression}, we restrict the indices $k$ in
-optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$. 
+We define as \emph{restricted regression} where we restrict the indices $k$ in
+optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$:
+\[
+\min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
+   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, ..., d_{k,n-1} \geq 0
+\]
 \end{definition}
-
-Our analysis then differs from the now-standard ``primal-dual witness
-technique''~\cite{Wain:09a}.
-Primal-dual witness explicitly solves all the dual variables, but because our optimization program is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.
 
@@
 \label{thm:deterministic}
-Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
+Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression as defined above.
 Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\
@@
 rates and false positive rates separately. To control false positives,
-we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression.
+we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression. \\
+
+The proof of theorem~\ref{thm:deterministic} looks at KKT conditions of optimization~\ref{opt:alternate_opt}, similar to the now standard \emph{primal-dual witness} technique~\cite{wainwright2009sharp}.
+We cannot derive analogous \emph{mutual incoherence} conditions because the estimation is nonparametric -- even the low dimensional restricted regression has $s(n-1)$ variables.
+The details of the proof are in section~\ref{sec:deterministic_proof} of the Appendix.
 
@@
 
-Suppose $\lambda \leq \mathbf{c} sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\
+Suppose $\lambda \leq c sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
 
@@
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
 

### 2014-05-05 code/paper_exp/R.m

@@ -113,7 +113,7 @@ for v = 1:length(alpha)
 end
 
 
-prob = zeros(1,40); epsil = 10^-7;
+prob = zeros(1,40); epsil = 10^-6;
 for version = 1:40
     load(['R_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0;

### 2014-05-05 code/paper_exp/T.m

@@ -86,7 +86,7 @@ return
 
 %% Reading the result:
 clc; clear all; close all; 
-prob = zeros(1,40); epsil = 10^-7;
+prob = zeros(1,40); epsil = 10^-6;
 for version = 1:40
     load(['T_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 

### 2014-05-15 tex/scam/additive_faithful.tex
acdc screen

@@
 \begin{remark} 
-It is difficult to prove the opposite direction of additive faithfulness, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
-Consider as a conceptual example a 3D distribution over $(X_1, X_2, X_3)$; suppose $X_1, X_2$ are independent, and $f$ is only a function of $X_1, X_2$.
-We can then let $X_3 = f(X_1, X_2) - f^*_1(X_1) - f^*_2(X_2)$, that is, we let $X_3$ exactly capture the additive approximation error, then the best additive approximation of $f$ would have a component $f^*_3(X_3) = X_3$ even though $f$ does not depend on $X_3$.
+It remains difficult to find conditions under which the opposite direction of additive faithfulness holds, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
+As a conceptual example, suppose that $f$ is only a function of $X_1, X_2$, and that $(X_1, X_2, X_3)$ follows a degenerate 3-dimensional distribution where $X_3 = f(X_1, X_2) - f^*(X_1) - f^*_2(X_2)$, that is, we let $X_3$ exactly capture the additive approximation error.
+In this case, the best additive approximation of $f$ would have a component $f^*_3(X_3) = X_3$ even though $f$ does not depend on $X_3$.
 \end{remark}
+
+It is possible to get a similar result for distributions with unbounded support, by using a limit condition $\lim_{|x_k| \rightarrow \infty} \frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k} = 0$ instead of the boundary condition.
+Such a limit condition is too strong however, it is not obeyed by the multivariate Gaussian distribution.
+\\
+
+In fact, not all convex functions are additively faithful under certain multivariate Gaussian distributions.
+
+\begin{example}
+\label{examp:gaussian_counterexample}
+Consider a quadratic form $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c^\tran \mathbf{x}$ and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma_{jj} = 1$ for all $j$.
+
+Then we have a closed form for the additive approximation, which we prove in [TODO:appendix reference].
+\begin{itemize}
+\item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
+\item If $f$ depends on $x_j$, then
+\[
+f^*_j(x_j) = H_j^\tran \Sigma_j x_j^2 + c_j x_j
+\]
+where $H_j, \Sigma_j$ are the $j$-th row of $H_j, \Sigma_j$ respectively. 
+\end{itemize}
+Let $H = [1, 2; 2,5]$ and let $\Sigma = [1, -\alpha; -\alpha, 1]$.
+It is easy to check then that if $\alpha=0.5$, then $f^*_1 = 0$ and additive faithfulness is violated, and if $\alpha > 0.5$, then $f^*_1$ is a concave function.
+\end{example}
 
@@
 
-Although convex functions are additively faithful, it is difficult to estimate the optimal additive functions $f^*_k$'s (as defined in equation~\ref{eqn:unconstrained_additive}) because $f^*_k$ need not be a convex function.
+Although convex functions are additively faithful, it is difficult to estimate the optimal additive functions $f^*_k$'s (as defined in equation~\ref{eqn:unconstrained_additive}) because $f^*_k$ need not be a convex function, as example~\ref{examp:gaussian_counterexample} shows.
+$f^*_k$ can be shown to be smooth but it is preferable to use shape-constraints whenever possible to avoid the introduction of the additional smoothing bandwidth.
 
-Because the true regression function $f$ is convex, it is natural to consider an convex additive model:
+Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model:
 \begin{equation}
@@
 
-The convex functions $f^*_k$'s are not additively faithful by themselves but faithfulness can be restored by coupling the $f^*_k$'s with a set of concave functions:
+The convex functions $f^*_k$'s are not additively faithful by themselves unfortunately. But, faithfulness can be restored by coupling the $f^*_k$'s with a set of concave functions:
 \begin{equation}

### 2014-05-15 tex/scam/appendix.tex
acdc screen

@@
     \lambda \sum_{k=1}^p \| \bar{\Delta}_k d_k \|_\infty -
-    \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki} 
+    \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki} 
 \end{equation}
@@
 
+We have thus proven that there exist one solution $\{ \hat{d}_k \}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in S^c$.
+Furthermore, we have shown that the subgradient variables $\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.
+We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as well.
+\\
+
+%% prove uniqueness of sparsity pattern.
+
+We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k = \sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$.
+If this were not true, then a convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly lower objective on the quadratic term.
+More precisely, let $\zeta \in [0,1]$.
+If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k \big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is strongly convex as a function of $\nu$.
+Thus, it cannot be that $\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective and we have reached a contradiction.\\
+
+Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$ and $\{ \hat{d}'_k \}$.
+Let $\mathbf{u}_k \in \partial \| \bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k \in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets of subgradients.
+Let $\{ \nu_{ki} \}_{k=1,..,p,\, i=1,...n-1}$ and $\{ \nu'_{ki} \}$ be the two sets of positivity dual variables.
+\footnote{since there is no positivity constraint on $d_{k1}$, we let $\nu_{k1} = 0$ always.}
+
+Let us define $\bar{\Delta}$, a $n \times p(n-1)$ matrix, to denote the column-wise concatenation of $\{ \bar{\Delta}_k \}_k$ and $\hat{d}$, a $p(n-1)$ dimensional vector, to denote the concatenation of $\{ \hat{d}_k \}_k$.
+With this notation, we can express $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k = \bar{\Delta} \hat{d}$.
+
+Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}', \mathbf{u}', \nu')$ must satisfy the stationarity condition, we have that:
+\[
+\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
+   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}_k - \nu = 
+\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
+   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0
+\] 
+We multiply both sides of the above equation by $\hat{d}'$:
+\[
+\hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
+    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
+    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'
+\]
+Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that:
+\[
+\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty
+\]
+On one hand, $\hat{d}'$ is a feasible solution so $\hat{d}'^\tran \nu \geq 0$ and so 
+\[
+\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k \geq \sum_{k=1}^p \| \hat{f}'_k \|_\infty .
+\]
+
+On the other hand, by Holder's inequality:
+\begin{align*}
+\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
+   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 
+\end{align*}
+
+Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$.
+We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.\\
+
 The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way.
@@
   \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
-  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=1}^{n-1} \nu_{ki} d_{ki}
+  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
 \]

### 2014-05-15 code/paper_exp/acdc_QP.m

@@ -9,13 +9,53 @@ Ln2 = zeros(p,1);
 res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
 obj = zeros(maxit,1);
 
+counter = [0,0];
 %SCAM
 while iter < maxit && change > tol
     iter = iter + 1;
     
     for d = 1:p
         res = res + z(d,:)';
-        [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK_f(res,X(d,:),lambda);
+        
+        
+        % screening one
+        xcol = reshape(X(d,:), n, 1);
+        [Xd, ord] = sort(X(d,:), 'ascend');
+        Xdrow = reshape(Xd(1:(n-1)), 1, n-1);
+        pieceI = repmat(xcol, 1, n-1);
+        pieceJ = repmat(Xdrow, n, 1);
+        Delta_matrix = max(pieceI - pieceJ, 0);
+        Delta2_matrix = Delta_matrix - (1/n)*repmat(sum(Delta_matrix, 1), n, 1);
+
+        res_vec = (0.5/n)*res'*Delta_matrix;
+        
+        lambda_vec1 = lambda*(1/n)*ones(1,n)*Delta_matrix;
+        
+        uvec = abs(res'); uvec = uvec/sum(uvec);
+        lambda_vec2 = lambda*uvec*Delta_matrix;
+        
+        screen_one_flag = sum(lambda_vec1 >= res_vec) == n-1 || ...
+            sum(lambda_vec2 >= res_vec) == n-1 ;
+        
+        
+   
+        
+        if (screen_one_flag)
+            disp('good')
+            counter(1) = counter(1) +1;
+            %[beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK_f(res,X(d,:),lambda);
+            %if (max(abs(z(d,:))) > 1e-6)
+            %    disp('err!!!!!!!!')
+            %end
+            
+            
+        else
+            disp('bad')
+            counter(2) = counter(2) + 1;
+            [beta(d,:),z(d,:),Ln(d)] = SCAM_MOSEK_f(res,X(d,:),lambda);
+        end
+        
+        
         res = res - z(d,:)';
     end
     
@@ -26,7 +66,7 @@ while iter < maxit && change > tol
     end
     
     if mod(iter,10)==0
[…]

### 2014-05-15 code/paper_exp/acdc_test.m

@@ -1,14 +1,15 @@
-n = 500;
-alpha = 0.5;
-v = 0.3;
+n = 1000;
+alpha = 0;
+%v = 0.3;
+v = 0;
 
-p = 64; 
+p = 512; 
 k = 4; 
 
 lambda = 0.5*sqrt(1/n)*log(n*p); 
 maxit = 20; tol = 10^-6;
 
-nrun = 5; 
+nrun = 1; 
 
 J = ones(p,nrun)==0; 
 Ln = zeros(p,nrun);
@@ -40,10 +41,10 @@ for run = 1:nrun
     % main function call
     [beta,h,obj,Ln(:,run)] = acdc_QP(X, y-mean(y), lambda, maxit, tol);
     %[beta,h,obj,Ln(:,run)] = SCAM_QP(X,y-mean(y),lambda,maxit,tol);
-    disp(['version=' num2str(version) ' run=' num2str(run)]);
+    %disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
 
-prob = 0; epsil = 10^-7;
+prob = 0; epsil = 10^-6;
 
 nrun = size(Ln,2); suc = 0;
 for run = 1:nrun

### 2014-06-22 tex/scam/paper.tex
minor updates

@@
 
-\title{Variable Selection in Convex Function Estimation}
+\title{Faithful Variable Screening for High-Dimensional Convex Regression}
 
@@
 We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points.
+Convex function estimation is subject to the curse of dimensionality where the sample size necessary for consistent estimation increases exponentially with the dimensionality of the observed variables $p$.
+However, if the function is sparse, with $s << p$ relevant variables, then one could achieve consistency in the high-dimensional setting by first identifying the $s$ variables.
+We develop a faithful screening procedure to compute a set $S$ that contains the $s$ relevant variables.
+Our approach is a two-stage method that estimates a sum of $p$ one-dimensional convex functions, followed by one-dimensional concave regression fits on the residuals.
+The method is based on quadratic programming, and in contrast to standard sparse additive models, requires no tuning parameters for smoothness.
+Under appropriate assumptions, we prove that the procedure is faithful in the population setting, yielding no false negatives, and we give a finite sample statistical analysis.
+In addition, we introduce algorithms for efficiently carrying out the required quadratic programs.
+The approach leads to significant computational and statistical advantages over fitting a full model, and provides an effective, practical approach to variable screening in convex regression.
+
 \end{abstract}

### 2014-06-22 code/paper_exp/C.m

@@ -90,7 +90,7 @@ return
 %% Reading the result:
 clc; clear all; close all; 
 prob = zeros(1,40); 
-epsil = 10^-7;
+epsil = 1e-6;
 for version = 1:40
     load(['C_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 

### 2014-06-22 code/paper_exp/acdc_test.m

@@ -1,5 +1,5 @@
 n = 1000;
-alpha = 0;
+alpha = 0.5;
 %v = 0.3;
 v = 0;
 

### 2014-06-27 tex/scam/faithful.tex
added faithful.tex as main file in aos format

--- 2014-06-22 tex/scam/paper.tex
@@
-\documentclass{article}
+\documentclass[12pt,pdftex,aos]{imsart}
+
+\RequirePackage[OT1]{fontenc}
 \usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
+\RequirePackage{hypernat}
+\usepackage[ruled,section]{algorithm}
+\usepackage[noend]{algorithmic}
+\usepackage{graphicx}
 \usepackage[hscale=0.7,vscale=0.8]{geometry}
@@
 \usepackage{hyperref}
-\usepackage{authblk}
-
 \usepackage{yhmath}
 
-\bibliographystyle{plainnat}
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+\DeclareMathOperator{\rank}{rank}
+\DeclareMathOperator{\diag}{diag}
+\DeclareMathOperator{\trace}{trace}
+\DeclareMathOperator{\pr}{Prob}
+\DeclareMathOperator{\cov}{Cov}
+\newcommand{\EE}[1]{\mathbb{E}({#1})}
+\def\interleave{|\kern-.25ex|\kern-.25ex|}
+\def\interleavesub{|\kern-.15ex|\kern-.15ex|}
+\newcommand{\nnorm}[1]{\interleave {#1} \interleave}
+\newcommand{\nnormsub}[1]{\interleavesub {#1} \interleavesub}
+\newcommand{\nNorm}[1]{\left|\kern-.25ex\left|\kern-.25ex\left| {#1}\right|\kern-.25ex\right|\kern-.25ex\right|}
+\newcommand{\norm}[1]{\left\|{#1}\right\|}
+%\newcommand{\trnorm}[1]{\norm{{#1}}_{\mathrm{tr}}}
+\newcommand{\trnorm}[1]{\norm{{#1}}_{*}}
+\newcommand{\spnorm}[1]{\norm{{#1}}_{\mathrm{sp}}}
+\newcommand{\frnorm}[1]{\norm{{#1}}_{\mathrm{F}}}
+%\newcommand{\trnnorm}[1]{\nnorm{{#1}}_{\mathrm{tr}}}
+\newcommand{\trnnorm}[1]{\nnorm{{#1}}_{*}}
+\newcommand{\spnnorm}[1]{\nnorm{{#1}}_{\mathrm{sp}}}
+\newcommand{\spnnormsub}[1]{\nnormsub{{#1}}_{\mathrm{sp}}}
+\newcommand{\frnnorm}[1]{\nnorm{{#1}}_{\mathrm{F}}}
+\newcommand{\Norm}[1]{\left\|{#1}\right\|}
+%\newcommand{\Trnorm}[1]{\Norm{{#1}}_{\mathrm{tr}}}
+\newcommand{\Trnorm}[1]{\Norm{{#1}}_{*}}
+\newcommand{\Spnorm}[1]{\Norm{{#1}}_{\mathrm{sp}}}
+\newcommand{\Frnorm}[1]{\Norm{{#1}}_{\mathrm{F}}}
+%\newcommand{\Trnnorm}[1]{\nNorm{{#1}}_{\mathrm{tr}}}
+\newcommand{\Trnnorm}[1]{\nNorm{{#1}}_{*}}
+\newcommand{\Spnnorm}[1]{\nNorm{{#1}}_{\mathrm{sp}}}
+\newcommand{\Frnnorm}[1]{\nNorm{{#1}}_{\mathrm{F}}}
+\newcommand{\colspan}[1]{\mathrm{colspan}\left({#1}\right)}
+\def\myllangle{\langle\mspace{-4mu}\langle\mspace{1mu}}
+\def\myrrangle{\mspace{1mu}\rangle\mspace{-4mu}\rangle}
 
-\title{Faithful Variable Screening for High-Dimensional Convex Regression}
-
-%\author{
-%Min Xu, Minhua Chen, John Lafferty
-%}
-
-\author[1]{Min Xu}
-\author[2,3]{Minhua Chen}
-\author[2,3]{John Lafferty}
-
-\affil[1]{Machine Learning Department, Carnegie Mellon University}
-\affil[2]{Department of Statistics, University of Chicago}
-\affil[3]{Department of Computer Science, University of Chicago}
-
-% ENVIRONMENTS
 \numberwithin{equation}{section}
@@
 
-\begin{document}
+\renewcommand{\baselinestretch}{1.1}
+%\parskip12pt
+%\parindent0pt
+\setcounter{tocdepth}{2}
 
@@
 \def\reals{{\mathbb R}}
+\def\R{\reals}
 \def\P{{\mathbb P}}
@@
 
-\maketitle
+\begin{document}
+
+\begin{frontmatter}
+\title{Faithful Variable Screening for High-Dimensional Convex Regression}
+\runtitle{Faithful Variable Screening for Convex Regression}
+
+\begin{aug}
+\vskip10pt
+\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
+\comma 
+\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
+\and
+\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{
+\begin{tabular}{ccc}
+\\[10pt]
+Machine Learning Department & Department of Statistics & Department of Statistics\\
+Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
+& & University of Chicago
+\end{tabular}
+\\[20pt]
+\printead{e1,e2,e3}}
+\end{aug}
 
 \begin{abstract}
-We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points.
-Convex function estimation is subject to the curse of dimensionality where the sample size necessary for consistent estimation increases exponentially with the dimensionality of the observed variables $p$.
-However, if the function is sparse, with $s << p$ relevant variables, then one could achieve consistency in the high-dimensional setting by first identifying the $s$ variables.
-We develop a faithful screening procedure to compute a set $S$ that contains the $s$ relevant variables.
-Our approach is a two-stage method that estimates a sum of $p$ one-dimensional convex functions, followed by one-dimensional concave regression fits on the residuals.
-The method is based on quadratic programming, and in contrast to standard sparse additive models, requires no tuning parameters for smoothness.
-Under appropriate assumptions, we prove that the procedure is faithful in the population setting, yielding no false negatives, and we give a finite sample statistical analysis.
-In addition, we introduce algorithms for efficiently carrying out the required quadratic programs.
-The approach leads to significant computational and statistical advantages over fitting a full model, and provides an effective, practical approach to variable screening in convex regression.
+  We consider the problem of variable selection in convex nonparametric
+  regression.  Under the assumption that the true regression
+  function is sparse and convex, we
+  develop a faithful screening procedure to compute a set $S$ that
+  contains the $s$ relevant variables. Our approach is a two-stage
+  method that estimates a sum of $p$ one-dimensional convex functions,
+  followed by one-dimensional concave regression fits on the
+  residuals. The method is based on quadratic programming, and in
+  contrast to standard sparse additive models, requires no tuning
+  parameters for smoothness. Under appropriate assumptions, we prove
+  that the procedure is faithful in the population setting, yielding
+  no false negatives, and we give a finite sample statistical
+  analysis. In addition, we introduce algorithms for efficiently
+  carrying out the required quadratic programs. The approach leads to
+  significant computational and statistical advantages over fitting a
+  full model, and provides an effective, practical approach to
+  variable screening in convex regression.
+\end{abstract}
 
-\end{abstract}
+\begin{keyword}
+\kwd{nonparametric regression}
+\kwd{convex regression}
+\kwd{variable selection}
+\kwd{quadratic programming}
+\kwd{additive model}
+\end{keyword}
+
+%\tableofcontents
+\vskip20pt
+\end{frontmatter}
+
+\maketitle
 \vskip10pt
@@
 
-%\bibliographystyle{plain}
-\bibliography{local}
-
 \newpage
@@
 
+\section*{Acknowledgements}
+Research supported in part by NSF grants IIS-1116730, 
+AFOSR grant FA9550-09-1-0373, ONR grant
+N000141210762, and an Amazon AWS in Education Machine Learning
+Research grant.
+
+\bibliographystyle{imsart-nameyear}
+\bibliography{local}
+
 \end{document}

### 2014-06-29 tex/scam/abstract.tex
added abstract.tex

--- 2014-05-05 tex/scam/paper.tex
@@
-\documentclass{article}
-\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
-\usepackage[hscale=0.7,vscale=0.8]{geometry}
+\begin{abstract}
+  We study the problem of variable selection in convex nonparametric
+  regression.  Under the assumption that the true regression function
+  is convex and sparse, we develop a screening procedure to select a
+  subset of variables that contains the relevant variables. Our
+  approach is a two-stage quadratic programming method that estimates
+  a sum of one-dimensional convex functions, followed by
+  one-dimensional concave regression fits on the residuals.  In
+  contrast to previous methods for sparse additive models, the
+  optimization is finite dimensional and requires no tuning parameters
+  for smoothness. Under appropriate assumptions, we prove that the
+  procedure is faithful in the population setting, yielding no false
+  negatives, and we give a finite sample statistical analysis. In
+  addition, we introduce algorithms for efficiently carrying out the
+  required quadratic programs. The approach leads to significant
+  computational and statistical advantages over fitting a full model,
+  and provides an effective, practical approach to variable screening
+  in convex regression.
+\end{abstract}
 
-\usepackage{subfigure}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{authblk}
-
-\usepackage{yhmath}
-
-\bibliographystyle{plainnat}
-
-\title{Variable Selection in Convex Function Estimation}
-
-%\author{
-%Min Xu, Minhua Chen, John Lafferty
-%}
-
-\author[1]{Min Xu}
-\author[2,3]{Minhua Chen}
-\author[2,3]{John Lafferty}
-
-\affil[1]{Machine Learning Department, Carnegie Mellon University}
-\affil[2]{Department of Statistics, University of Chicago}
-\affil[3]{Department of Computer Science, University of Chicago}
-
-% ENVIRONMENTS
-\numberwithin{equation}{section}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheoremstyle{remark}{\topsep}{\topsep}%
-     {\normalfont}% Body font
-     {}           % Indent amount (empty = no indent, \parindent = para indent)
-     {\bfseries}  % Thm head font
-     {.}          % Punctuation after thm head
-     {.5em}       % Space after thm head (\newline = linebreak)
-     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{assumption}{Assumption}[section]
-\newtheorem{definition}{Definition}[section]
-
-\begin{document}
-
-% min's macros
-\mathchardef\mh="2D
-
-% John's macros
-\def\X{\mathcal{X}}
-\def\comma{\unskip,~}
-\def\truep{p^*}
-\def\div{\|\,}
-\long\def\comment#1{}
-\def\reals{{\mathbb R}}
-\def\P{{\mathbb P}}
-\def\E{{\mathbb E}}
-\def\Cov{\mathop{\text{Cov}}}
-\def\supp{\mathop{\text{supp}\kern.2ex}}
-\def\argmin{\mathop{\text{\rm arg\,min}}}
-\def\arginf{\mathop{\text{\rm arg\,inf}}}
-\def\argmax{\mathop{\text{\rm arg\,max}}}
-\let\tilde\widetilde
-\def\csd{${}^*$}
-\def\mld{${}^\dag$}
-\def\dos{${}^\ddag$}
-\def\W{\widetilde Y}
-\def\Z{\widetilde X}
-\let\hat\widehat
-\let\tilde\widetilde
-\def\given{{\,|\,}}
-\def\ds{\displaystyle}
-\def\bs{\backslash}
-\def\1{{(1)}}
-\def\2{{(2)}}
-\def\pn{{(n)}}
-\def\ip{{(i)}}
-\def\Xbar{\overline{X}}
-\def\except{\backslash}
-\def\npn{\mathop{\textit{NPN\,}}}
-\def\i{{(i)}}
-\def\cE{{\mathcal{C}}}
-\def\cM{{\mathcal{M}}}
-\def\cF{{\mathcal{F}}}
-\def\cP{{\mathcal{P}}}
-\def\cG{{\mathcal{G}}}
-\def\tr{\mathop{\text{tr}}}
-\long\def\comment#1{}
-\def\ti#1{#1}
-\def\titi#1{\textit{#1}}
-\def\cram{{\sc cram}}
-\def\spam{{\small\sc SpAM}}
-\def\diag{\mathop{\rm diag}}
-\def\ones{\mathbf{1}}
-\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
-\def\fatnorm#1{\threebars #1 \threebars}
-\def\rank{\mathop{\rm rank}}
-\def\S{\mathcal{S}}
-\def\H{\mathcal{H}}
-\def\K{{K}}
-\def\rank{\mathop{\rm rank}}
-\def\half{{1/2}}
-\def\Y{\mathbb{Y}}
-\def\M{\mathbb{M}}
-\def\F{\mathbb{F}}
-\def\pinv{{-1}}
-%\def\ones{\mathds{1}}
-%\def\ones{1}
-\def\Res{Z}
-\def\Proj{P}
-\def\cN{{\mathcal N}}
-\def\cT{{\mathcal H}}
-\def\coloneqq{:=}
-\def\mathbf#1{\mbox{\boldmath $#1$}} 
-\def\bar#1{\overline{#1}}
-
-\maketitle
-
-\begin{abstract}
-We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points. 
-\end{abstract}
-\vskip10pt
-
-% \tableofcontents
-
-\input{introduction}
-\input{related_work}
-\input{summary}
-\input{additive_faithful}
-\input{estimation}
-\input{optimization}
-\input{sparsistency}
-\input{experiments}
-\input{discussion}
-
-\clearpage
-
-%\bibliographystyle{plain}
-\bibliography{local}
-
-\newpage
-\input{appendix}
-%\newpage
-%\input{notes}
-
-\end{document}
+\begin{keyword}
+\kwd{nonparametric regression}
+\kwd{convex regression}
+\kwd{variable selection}
+\kwd{quadratic programming}
+\kwd{additive model}
+\end{keyword}

### 2014-06-29 tex/scam/faithful.tex
test

@@
 \documentclass[12pt,pdftex,aos]{imsart}
+%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
 
@@
 \end{tabular}
-\\[20pt]
-\printead{e1,e2,e3}}
+%\\[20pt]
+%\printead{e1,e2,e3}
+}
 \end{aug}
 
-\begin{abstract}
-  We consider the problem of variable selection in convex nonparametric
-  regression.  Under the assumption that the true regression
-  function is sparse and convex, we
-  develop a faithful screening procedure to compute a set $S$ that
-  contains the $s$ relevant variables. Our approach is a two-stage
-  method that estimates a sum of $p$ one-dimensional convex functions,
-  followed by one-dimensional concave regression fits on the
-  residuals. The method is based on quadratic programming, and in
-  contrast to standard sparse additive models, requires no tuning
-  parameters for smoothness. Under appropriate assumptions, we prove
-  that the procedure is faithful in the population setting, yielding
-  no false negatives, and we give a finite sample statistical
-  analysis. In addition, we introduce algorithms for efficiently
-  carrying out the required quadratic programs. The approach leads to
-  significant computational and statistical advantages over fitting a
-  full model, and provides an effective, practical approach to
-  variable screening in convex regression.
-\end{abstract}
-
-\begin{keyword}
-\kwd{nonparametric regression}
-\kwd{convex regression}
-\kwd{variable selection}
-\kwd{quadratic programming}
-\kwd{additive model}
-\end{keyword}
-
+\input{abstract}
 %\tableofcontents

### 2014-06-29 tex/scam/introduction.tex
minor updates
test

--- 2013-11-01 tex/scam/icml14/introduction_icml.tex
@@
 
-We consider the problem of estimating a convex function of several
-variables from noisy values of the function at a finite sample of
-input points.  Recent work \cite{Guntu:12,Guntu:13} shows that the
-minimax rate for convex function estimation in $p$ dimensions is
-$n^{-4/(4+p)}$.  Loosely speaking, this shows that the
-geometric convexity constraint is statistically equivalent to
-requiring two derivatives of the function, and thus is
-subject to the same curse of dimensionality.
-However, if the function is sparse, with $s\ll p$ relevant variables,
-then the faster rate $n^{-4/(4+s)}$ may be achievable if the $s$
-variables can be identified.  To determine the relevant variables, we
+Shape restrictions such as monotonicity, convexity, and concavity
+provide a natural way of limiting the complexity of many statistical
+estimation problem.  Shape-constrained estimation is not as well
+understood as more traditional nonparametric estimation involving
+smoothness constraints.  For instance, as of this writing the minimax
+rate of convergence for multivariate convex regression has yet to be
+rigorously established in full generality.  Even the one-dimensional
+case is challenging, and has been of recent interest
+\citep{guntusen:13}.
+
+In this paper we study the problem of variable selection
+in convex regression.   Assuming that the regression
+function is convex and sparse, in order to select the
+relevant variables we 
 show that it suffices to estimate a sum of $p$ one-dimensional convex
 functions, leading to significant computational and statistical
-advantages.  In addition, we introduce algorithms and supporting
+advantages .  In addition, we introduce algorithms and supporting
 statistical theory for a practical, effective approach to this
@@
 \def\mathbf#1{\mbox{\boldmath $#1$}}
+
+% DO NOT CHANGE; RefTex variables -minx
+
+%%% Local Variables: ***
+%%% mode:latex ***
+%%% TeX-master: "paper.tex" ***
+%%% End: ***

### 2014-06-30 tex/scam/introduction.tex
minor additions

@@
 understood as more traditional nonparametric estimation involving
-smoothness constraints.  For instance, as of this writing the minimax
+smoothness constraints.  For instance, as of this writing, the minimax
 rate of convergence for multivariate convex regression has yet to be
@@
 
-In this paper we study the problem of variable selection
-in convex regression.   Assuming that the regression
-function is convex and sparse, in order to select the
-relevant variables we 
-show that it suffices to estimate a sum of $p$ one-dimensional convex
-functions, leading to significant computational and statistical
-advantages .  In addition, we introduce algorithms and supporting
-statistical theory for a practical, effective approach to this
-variable selection problem.
+In this paper we study the problem of variable selection in convex
+regression.  Assuming that the regression function is convex and
+sparse, our goal is to identify the relevant variables.  We show that
+it suffices to estimate a sum of $p$ one-dimensional convex functions,
+leading to significant computational and statistical advantages.  This
+is in contrast to general nonparametric regression, where fitting an
+additive model can result in false negatives.  Our approach is based
+on a two-stage quadratic programming procedure.  In the first stage,
+we fit an convex additive model, imposing a sparsity penalty.  In the
+second stage, we fit a concave function on the residual for each
+variable.  As we demonstrate, this perhaps non-intuity second stage is
+in general necessary.  Our first result is that this procedure is
+faithful in the population setting, meaning that it results in no
+false negatives, under mild assumptions on the density of the
+covariates.  Our second result is a finite-sample statistical analysis
+of the procedure, where we upper bound the statistical rate of
+convergence.  Each stage of the method requires quadratic programming.
+An additional contribution is to show how these quadratic programs can
+be forumlated to be more scalable.  Simulations demonstrate the method
+performs in a manner that is consistent with our analysis.
 
-The general sparse nonparametric regression problem is considered in \cite{lafferty2008rodeo}, where it is shown that computationally efficient, near minimax-optimal estimation is possible, but in ambient
-dimensions that scale only as $p = O(\log n)$ instead of $p=O\bigl(e^{n^c}\bigr)$ as enjoyed by sparse linear models.
-\citet{dalalyan:12} do achieve exponential scaling $p=O(e^n)$ under certain Fourier smoothness conditions but they show that variable selection is still hard in that the number of relevant variables $s$ must be less than $\log n$.
+Variable selection for nonparametric
+regression under smoothness constraints is difficult without
+making additional strong assumptions. 
+\cite{lafferty2008rodeo} show that computationally
+efficient, near minimax-optimal estimation is possible, but in ambient
+dimensions that scale only as $p = O(\log n)$; see also \cite{BertinLecue}.  This is in contrast
+to the $p=O\bigl(e^{n^c}\bigr)$ scaling enjoyed by sparse linear
+models \cite{Wain:09a}. \citet{dalalyan:12} achieve exponential scaling $p=O(e^n)$
+under certain Fourier smoothness conditions, but require
+that the number of relevant variables $s$ must be less than $\log n$.
 
-% The general sparse nonparametric regression problem is considered in
-% \cite{lafferty2008rodeo}, where it is shown that computationally
-% efficient, near minimax-optimal estimation is possible, but in ambient
-% dimensions that scale only as $p = O(\log n)$.  This is in stark
-% contrast to the exponential scaling $p = O\bigl(e^{n^c}\bigr)$ enjoyed
-% by sparse linear models \cite{Wain:09a}.
-
-Approximating the regression function by a sum of one-dimensional functions, known as sparse additive models, \cite{Ravikumar:09} is a practical alternative to fully
-nonparametric function estimation.  But the additive assumption is
-limited.  In particular, the natural idea of first selecting the
-single variable effects, then the pairwise effects, and so on, does
-not in general lead to consistent variable selection.  In other words,
-the general nonparametric model is not additively faithful.
-Remarkably, the additional assumption of convexity does lead to
-consistent variable selection, as we show here. In addition, we show that
-the scaling $p = O(\log n)$ and $n = O\big(\textrm{poly}(s)\big)$ is achievable for sparse convex additive models. Thus, the geometric convexity constraint is quite different from the
-smoothness constraints imposed in traditional nonparametric
-regression.
+Approximating the regression function by a sum of one-dimensional
+functions, known as sparse additive models \citep{Ravikumar:09}, is a
+practical alternative to fully nonparametric function estimation.  
+Sparse additive models have been further studied in by \cite{Meier09},
+and by \cite{Raskutti:12}.  But 
+the additive assumption is limited.  In particular, the natural idea
+of first selecting the single variable effects, then the pairwise
+effects, and so on, does not in general lead to consistent variable
+selection.  In other words, the general nonparametric model is not
+additively faithful.  Remarkably, the additional assumption of
+convexity does lead to consistent variable selection, as we show
+here. In addition, we show that the high dimensional scaling $n =
+O\big(\textrm{poly}(s) \log p\big)$ is achievable for sparse convex
+additive models. Thus, with respect to variable selection, the
+geometric convexity constraint is quite different from the smoothness
+constraints imposed in traditional nonparametric regression.
 

### 2014-07-01 tex/scam/introduction.tex
restructured related work

@@
 
-Variable selection for nonparametric
-regression under smoothness constraints is difficult without
-making additional strong assumptions. 
-\cite{lafferty2008rodeo} show that computationally
-efficient, near minimax-optimal estimation is possible, but in ambient
-dimensions that scale only as $p = O(\log n)$; see also \cite{BertinLecue}.  This is in contrast
-to the $p=O\bigl(e^{n^c}\bigr)$ scaling enjoyed by sparse linear
-models \cite{Wain:09a}. \citet{dalalyan:12} achieve exponential scaling $p=O(e^n)$
-under certain Fourier smoothness conditions, but require
-that the number of relevant variables $s$ must be less than $\log n$.
+Estimation of convex functions arises naturally in several
+applications.  Examples include geometric programming \citep{Boyd04},
+computed tomography \citep{Prince:90}, target reconstruction
+\citep{Lele:92}, image analysis \citep{Golden:06} and circuit design
+\citep{Hannah:12}.  Other applications include queuing theory
+\citep{Chen:01} and economics, where it is of interest to estimate
+concave utility functions \citep{Pratt:68}.  See \cite{Lim:12} for
+other applications.  
+Beyond cases where the assumption of convexity is
+natural, the convexity assumption can be attractive as a
+tractable, nonparamametric relaxation of the linear model.
 
-Approximating the regression function by a sum of one-dimensional
-functions, known as sparse additive models \citep{Ravikumar:09}, is a
-practical alternative to fully nonparametric function estimation.  
-Sparse additive models have been further studied in by \cite{Meier09},
-and by \cite{Raskutti:12}.  But 
-the additive assumption is limited.  In particular, the natural idea
-of first selecting the single variable effects, then the pairwise
-effects, and so on, does not in general lead to consistent variable
-selection.  In other words, the general nonparametric model is not
-additively faithful.  Remarkably, the additional assumption of
-convexity does lead to consistent variable selection, as we show
-here. In addition, we show that the high dimensional scaling $n =
-O\big(\textrm{poly}(s) \log p\big)$ is achievable for sparse convex
-additive models. Thus, with respect to variable selection, the
-geometric convexity constraint is quite different from the smoothness
-constraints imposed in traditional nonparametric regression.
+Variable selection in general nonparametric regression or function
+estimation is a notoriously difficult problem. \citet{lafferty2008rodeo} develop a greedy procedure for
+adjusting bandwidths in a local linear regression estimator,
+and show that the procedure achieves the minimax rate
+as if the relevant variables were isolated in advance.
+But the method only provably scales to dimensions $p$ that 
+grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  Note that this
+is the opposite of the high dimensional scaling behavior
+known to hold for sparsity selection in linear models
+using $\ell_1$ penalization, where the sample size $n$
+is logarithmic in the dimension $p$. \citet{bertin:08}
+develop an optimization-based approach in
+the nonparametric setting, applying the lasso
+in a local linear model at each test point.  Here again,
+however, the method only scales as $p = O(\log n)$,
+the low-dimensional regime.
+An approximation theory approach to the same
+problem is presented in \cite{devore:11}, 
+using techniques based on hierarchical hashing schemes,
+similar to those used for ``junta'' problems \cite{mossel:04}.
+Here it is shown that the sample complexity scales as $n > \log p$ 
+if one adaptively selects the points on
+which the high-dimensional function is evaluated.
 
-A key to our approach is the observation that least squares
-nonparametric estimation under convexity constraints is equivalent to
-a finite dimensional quadratic program.  Specifically, the infinite
-dimensional optimization 
-\begin{align}
-\begin{split}
-\text{minimize} & \quad \sum_{i=1}^n (Y_i - m(x_i))^2 \\
-\text{subject to} &  \quad m:\reals^p\rightarrow\reals\ \text{is
-  convex}
-\end{split}
-\end{align}
-is precisely equivalent to the finite dimensional quadratic
-program 
-\begin{align}
-\begin{split}
-\label{eq:outer}
-\text{minimize}_{h, \beta} & \;\; \sum_{i=1}^n (Y_i - h_i)^2 \\
-\text{subject to} & \;\; h_j \geq h_i + \beta_i^T (x_j-x_i),\; \text{for
-    all $i,j$}.
-\end{split}
-\end{align}
-%\end{equation}
-%See \cite{Boyd04}, Section 6.5.5.
-Here $h_i$ is the estimated function value $m(x_i)$, and the vectors
-$\beta_i \in \reals^d$ represent supporting hyperplanes to the
-epigraph of $m$.  Importantly, this finite dimensional quadratic program does
-not have tuning parameters for smoothing the function. Such parameters are the bane
-of nonparametric estimation.
+\citet{dalalyan:12} show that the exponential scaling $p=O(\log n)$ is achievable if the underlying function is assumed to be smooth with respect to a Fourier basis. They also give
+support for the intrinsic difficulty of variable
+selection in nonparametric regression, giving lower bounds 
+showing that sparsistency is not possible if $n < \log p$ or if $n <
+\exp s$, where $s$ is the number of relevant variables.
+Variable selection over kernel classes is studied
+by \citet{Kolch:10}.
 
-Estimation of convex functions arises naturally in several
-applications.  Examples include geometric programming \cite{Boyd04},
-computed tomography \cite{Prince:90}, target reconstruction
-\cite{Lele:92}, image analysis \cite{Golden:06} and circuit design
-\cite{Hannah:12}.  Other applications include queuing theory
-\cite{Chen:01} and economics, where it is of interest to estimate
-concave utility functions \cite{Pratt:68}.  See \cite{Lim:12} for
-other applications.
+Perhaps most closely related to the present work, is the framework
+studied by \cite{Raskutti:12} for sparse additive models, where sparse
+regression is considered under an additive assumption, with each
+component function belonging to an RKHS.  An advantage of working over
+an RKHS, in contrast to the other papers mentioned above, is that
+nonparametric regression with a sparsity-inducing regularization penalty can be
+formulated as a finite dimensional convex cone optimization.
+On the other hand, 
+smoothing parameters for the component Hilbert spaces
+must be chosen, leading to extra tuning parameters
+that are difficult to select in practice.  In addition, 
+the additive model must be assumed to
+be correct for sparsistent variable selection.
 
-Beyond cases where the assumption of convexity is
-natural, we offer that the convexity assumption is attractive as a
-tractable, nonparamametric relaxation of the linear model.  In
-addition to the lack of tuning parameters, other than the
-regularization parameter $\lambda$ to control the level of sparsity,
-the global convexity assumption leads to effective, scalable algorithms.  We
-demonstrate use of our approach on experiments with standard
-regression data sets, in a comparison with sparse linear models
-(lasso).
+An attraction of the convex function estimation framework we consider
+in this paper is that the additive model can be used for convenience,
+without assuming it to actually hold.  While nonparametric, the
+problem is naturally formulated using finite dimensional convex
+optimization, but with no additional tuning parameters.  As we show
+below, our method scales to high dimensions, with a dependence on the
+intrinsic dimension $s$ that scales polynomially, rather than
+exponentially as in the general case analyzed in \cite{dalalyan:12}.
 
-%In the following section we give a high-level summary of our technical
-%results, including additive faithfulness, variable selection 
-%consistency, and high dimensional scaling.  In Section~X...
+%* Laetitia Comminges, Arnak S. Dalalyan 
+%Tight conditions for consistency of variable selection 
+%In the context of high dimensionality. 
+%Ann. Statist, 40(5), 2667-2696, 2012 
+%
+%Comment: They estimate the coefficient of the regression function with respect to a Fourier basis and then threshold the estimated coefficients.
+They prove that sparsistency is achievable so long as $n > log p$ and $n > exp(s)$.
+They assume that the functions are smooth with respect to the Fourier basis.
+The fourier coefficients however seem difficult to estimate; it appears that the knowledge of the true density is required.
+They also provide
+%
+%
+%* Bertin, K. and Lecu´e, G. (2008). Selection of variables 
+%and dimension reduction in high-dimensional non-parametric 
+%regression. Electron. J. Stat. 2 1224–1241 
+%
+%Comment: They assume Holder smoothness and use multiple L1 regularized local polynomial smoothing to detect the sparsity pattern. They require that $p < log n$.
+%
+%
+%* "Approximation of Functions of Few Variables in High Dimensions" 
+%by DeVore, Petrova and Wojtaszczyk. 
+%
+%Comment: They show that variable selection under a scaling of
+%
 
-\def\mathbf#1{\mbox{\boldmath $#1$}}
+%Variable selection for nonparametric
+%regression under smoothness constraints is difficult without
+%making additional strong assumptions. 
+%\cite{lafferty2008rodeo} show that computationally
+%efficient, near minimax-optimal estimation is possible, but in ambient
+%dimensions that scale only as $p = O(\log n)$; see also \cite{BertinLecue}.  This is in contrast
+%to the $p=O\bigl(e^{n^c}\bigr)$ scaling enjoyed by sparse linear
+%models \cite{Wain:09a}. \citet{dalalyan:12} achieve exponential scaling $p=O(e^n)$
+%under certain Fourier smoothness conditions, but require
+%that the number of relevant variables $s$ must be less than $\log n$.
+%
+%Approximating the regression function by a sum of one-dimensional
+%functions, known as sparse additive models \citep{Ravikumar:09}, is a
+%practical alternative to fully nonparametric function estimation.  
+%Sparse additive models have been further studied in by \cite{Meier09},
+%and by \cite{Raskutti:12}.  But 
+%the additive assumption is limited.  In particular, the natural idea
+%of first selecting the single variable effects, then the pairwise
+%effects, and so on, does not in general lead to consistent variable
+%selection.  In other words, the general nonparametric model is not
+%additively faithful.  Remarkably, the additional assumption of
+%convexity does lead to consistent variable selection, as we show
+%here. In addition, we show that the high dimensional scaling $n =
+%O\big(\textrm{poly}(s) \log p\big)$ is achievable for sparse convex
+%additive models. Thus, with respect to variable selection, the
+%geometric convexity constraint is quite different from the smoothness
+%constraints imposed in traditional nonparametric regression.
+%
+
+In the following section we give a high-level summary of our technical
+results, including additive faithfulness, variable selection 
+consistency, and high dimensional scaling.  In Section~X...
 

### 2014-07-01 tex/scam/summary.tex
restructured summary and intro

--- 2013-10-01 tex/scam/icml14/introduction_icml.tex
@@
-\section{Introduction}
+\section{Overview of Results}
 
-We consider the problem of estimating a convex function of several
-variables from noisy values of the function at a finite sample of
-input points.  Recent work \cite{Guntu:12,Guntu:13} shows that the
-minimax rate for convex function estimation in $p$ dimensions is
-$n^{-4/(4+p)}$.  Loosely speaking, this shows that the
-geometric convexity constraint is statistically equivalent to
-requiring two derivatives of the function, and thus is
-subject to the same curse of dimensionality.
-However, if the function is sparse, with $s\ll p$ relevant variables,
-then the faster rate $n^{-4/(4+s)}$ may be achievable if the $s$
-variables can be identified.  To determine the relevant variables, we
-show that it suffices to estimate a sum of $p$ one-dimensional convex
-functions, leading to significant computational and statistical
-advantages.  In addition, we introduce algorithms and supporting
-statistical theory for a practical, effective approach to this
-variable selection problem.
-
-The general sparse nonparametric regression problem is considered in
-\cite{lafferty2008rodeo}, where it is shown that computationally
-efficient, near minimax-optimal estimation is possible, but in ambient
-dimensions that scale only as $p = O(\log n)$.  This is in stark
-contrast to the exponential scaling $p = O\bigl(e^{n^c}\bigr)$ enjoyed
-by sparse linear models \cite{Wain:09a}.  Sparse additive models
-\cite{Ravikumar:09} provide a practical alternative to fully
-nonparametric function estimation.  But the additive assumption is
-limited.  In particular, the natural idea of first selecting the
-single variable effects, then the pairwise effects, and so on, does
-not in general lead to consistent variable selection.  In other words,
-the general nonparametric model is not additively faithful.
-Remarkably, the additional assumption of convexity does lead to
-additive faithfulness, as we show here.  In addition, we show that
-exponential scaling is achievable for sparse convex additive models.
-Thus, the geometric convexity constraint is quite different from the
-smoothness constraints imposed in traditional nonparametric
-regression.
-
-A key to our approach is the observation that least squares
+The starting point for our approach is the observation that least squares
 nonparametric estimation under convexity constraints is equivalent to
@@
 
-Estimation of convex functions arises naturally in several
-applications.  Examples include geometric programming \cite{Boyd04},
-computed tomography \cite{Prince:90}, target reconstruction
-\cite{Lele:92}, image analysis \cite{Golden:06} and circuit design
-\cite{Hannah:12}.  Other applications include queuing theory
-\cite{Chen:01} and economics, where it is of interest to estimate
-concave utility functions \cite{Pratt:68}.  See \cite{Lim:12} for
-other applications.  Beyond cases where the assumption of convexity is
-natural, we offer that the convexity assumption is attractive as a
-tractable, nonparamametric relaxation of the linear model.  In
-addition to the lack of tuning parameters, other than the
-regularization parameter $\lambda$ to control the level of sparsity,
-the global convexity assumption leads to effective, scalable algorithms.  We
-demonstrate use of our approach on experiments with standard
-regression data sets, in a comparison with sparse linear models
-(lasso).
-
-%In the following section we give a high-level summary of our technical
-%results, including additive faithfulness, variable selection 
-%consistency, and high dimensional scaling.  In Section~X...
-
-\def\mathbf#1{\mbox{\boldmath $#1$}}
-
 \textbf{Notation.} If
@@
 the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
-$\bar{X}$ to denote the empirical average.
+$\bar{X}$ to denote the empirical average. Given a random variable $X_k$ and a scalar $x_k$, we use $\E[\cdot \given x_k]$ as a shorthand for $\E[ \cdot \given X_k = x_k]$.

### 2014-07-07 tex/scam/summary.tex
major edits

@@
+\def\x{\mathbf{x}}
+
 \section{Overview of Results}
+
+In this section we provide a high-level description of our technical
+results.  Our presentation is intended to give the reader
+an overview of our results and their significance.  The 
+full technical details, the precise statement of the results,
+and their detailed proofs are provided in following sections.
+
+Our results address three problems.  The first is to develop
+a procedure based on an additive approximation for identifying
+relevant variables in convex regression.  To this end,
+we prove a result that shows when and how the additive approximation
+be used without introducing false negatives in the population setting.  The
+second result concerns the efficient implementation of
+the quadratic programs required by the procedure.  
+Finally, the third problem we consider is the finite-sample
+behavior of our proposed method.
+
+We first establish some notation, to be used throughout the remainder 
+of the paper.
+If $\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
+vector with the $k$-th coordinate removed. If $\mathbf{v} \in \R^n$, then
+$v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
+magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
+is the all ones vector. If $X \in \R^p$ and $S \subset
+\{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
+the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
+$\bar{X}$ to denote the empirical average. Given a random variable
+$X_k$ and a scalar $x_k$, we use $\E[\cdot \given x_k]$ as a shorthand
+for $\E[ \cdot \given X_k = x_k]$.
+
+\subsection{Additive faithfulness}
 
@@
 \begin{split}
-\text{minimize} & \quad \sum_{i=1}^n (Y_i - m(x_i))^2 \\
-\text{subject to} &  \quad m:\reals^p\rightarrow\reals\ \text{is
+\text{minimize} & \quad \sum_{i=1}^n (Y_i - f(\x_i))^2 \\
+\text{subject to} &  \quad f:\reals^p\rightarrow\reals\ \text{is
   convex}
@@
 \end{align}
-is precisely equivalent to the finite dimensional quadratic
+is equivalent to the finite dimensional quadratic
 program 
@@
 \begin{split}
-\label{eq:outer}
-\text{minimize}_{h, \beta} & \;\; \sum_{i=1}^n (Y_i - h_i)^2 \\
-\text{subject to} & \;\; h_j \geq h_i + \beta_i^T (x_j-x_i),\; \text{for
+\text{minimize}_{f, \beta} & \;\; \sum_{i=1}^n (Y_i - f_i)^2 \\
+\text{subject to} & \;\; f_j \geq f_i + \beta_i^T (\x_j-\x_i),\; \text{for
     all $i,j$}.
@@
 \end{align}
-%\end{equation}
-%See \cite{Boyd04}, Section 6.5.5.
-Here $h_i$ is the estimated function value $m(x_i)$, and the vectors
+See \cite{Boyd04}, Section 6.5.5.
+Here $f_i$ is the estimated function value $f(\x_i)$, and the vectors
 $\beta_i \in \reals^d$ represent supporting hyperplanes to the
-epigraph of $m$.  Importantly, this finite dimensional quadratic program does
-not have tuning parameters for smoothing the function. Such parameters are the bane
-of nonparametric estimation.
+epigraph of $f$.  Importantly, this finite dimensional quadratic program does
+not have tuning parameters for smoothing the function.
 
-\textbf{Notation.} If
-$\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
-vector with the $k$-th coordinate removed. If $\mathbf{v} \in \R^n$, then
-$v_{(1)}$ denotes the smallest coordinate of $\mathbf{v}$ in
-magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
-is the all ones vector. If $X \in \R^p$ and $S \subset
-\{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
-the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
-$\bar{X}$ to denote the empirical average. Given a random variable $X_k$ and a scalar $x_k$, we use $\E[\cdot \given x_k]$ as a shorthand for $\E[ \cdot \given X_k = x_k]$.
+For general regression, using an additive approximation for variable
+selection may make errors.  In particular, the nonlinearities in the
+regression function may result in an additive component being wrongly
+zeroed out.  Surprisingly, this will not happen for convex regression
+under appropriate conditions.
+
+A differential function $f$ depends on variable $x_k$ if
+$\partial_{x_k} f \neq 0$ with probability greater than zero.  An additive approximation is given by
+\begin{equation}
+\{f_k^*\}, \mu^* \coloneqq \argmin_{f_1,\ldots, f_p, \mu} \Bigl\{ 
+             \E ( f(X) - \mu - \sum_{k=1}^p f_k(X_k))^2 
+         \,:\, \E f_k(X_k) = 0 \Bigr\}.
+\end{equation}
+We say that $f$ is \textit{additively faithful} in case $f^*_k = 0$
+implies that $f$ does not depend on coordinate $k$.
+% We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
+% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^s$, then $f$
+% is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.
+Additive faithfulness is a desireable property,
+since it implies that an additive approximation may allow us to 
+screen out irrelevant variables.
+
+Our first result shows that convex multivariate functions are
+additively faithful
+under the following assumption on the distribution of the data.
+\begin{definition}
+  Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.  Then $p$
+  satisfies the \emph{boundary-points condition} if, for all $j$, and
+  for all $\mathbf{x}_{-j}$:
+\[
+\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
+\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
+\quad \trm{at $x_j = 0$ and $x_j = 1$}.
+\]
+\end{definition}
+
+As discussed in Section~\ref{sec:additivefaithful}, this is a relatively weak condition. 
+Our first result is that this condition suffices in the population
+setting of convex regression.
+
+\begin{theorem}
+  Let $p$ be a positive density supported on $C=[0,1]^s$ that
+  satisfies the boundary-points property. If $f$ is convex and twice
+  differentiable, then $f$ is additively faithful under $p$.
+\end{theorem}
+
+% We give the full proof in Section~\ref{sec:faithful_proof} of the
+% Appendix, but pause here to provide some intuition.
+
+Intuitively, an additive approximation zeroes out variable $k$ when, fixing $x_k$, every
+``slice'' of $f$ integrates to zero. We prove this result
+by showing that ``slices'' of convex
+functions that integrate to zero cannot be ``glued together'' while
+still maintaining convexity.
+
+While this shows that convex functions are additively faithful, it is difficult to
+estimate the optimal additive functions $f^*_k$'s.  The difficulty
+is that $f^*_k$ need not be
+a convex function, as we show through a counterexample
+in Section~\ref{sec:additivefaithful}.   
+Since the true regression function $f$ is convex, it is natural to ask
+when it is sufficient to estimate an convex additive model.  
+Unfortunately, a convex additive approximation is not generally
+faithful.  In other words, it could be that $f^*_k\equiv 0$
+even for a relevant variable $x_k$.  But our next result
+shows that this type of error can be detected by fitting 
+a \textit{concave} function to the residual.  If the
+concave fit to the residual is zero, we can then safely
+mark $x_k$ as an irrelevant variable.
+
+\begin{theorem}
+Suppose $p(\mathbf{x})$ is a positive
+density on $C=[0,1]^p$ and satisfies the boundary-points
+condition. Suppose that $f$ is convex and twice-differentiable.
+and that $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k}
+\given x_k )$, and $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$
+are all continuous as functions on $C$.\\
+Define
+\begin{equation}
+\{ f^*_k \}_{k=1}^p,\mu^* = \arg\min \Big \{
+\E\big( f(X) - \mu - \sum_{k=1}^s f_k(X_k) \big)^2 \,:\, f_k \in
+\mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
+\end{equation} where $\mathcal{C}^1$ is the set of univariate convex
+functions, and
+\begin{equation}
+g^*_k = \arg\min \Big\{ \E\big( f(X) -
+\sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 \,:\, g_k \in \mh
+\mathcal{C}^1, \E g_k(X_k) = 0 \Big\},
+\end{equation}
+with $\mh{}\mathcal{C}^1$ denoting the set of univariate concave
+function.  Then, $f^*_k = 0$ and $g^*_k = 0$ implies that $f$ does not
+depend on $x_k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ with
+probability one.
+\end{theorem}
+
+This result suggests a two-stage screening
+procedure for variable selection. In the first stage we fit a sparse \emph{convex}
+additive model.  In the second stage we
+fit a concave function $\hat g_k$ to the residual for each variable
+having a zero convex component $\hat f_k$.  If both $\hat f_k = 0$ and
+$\hat g_k = 0$, we remove variable $x_k$.  
+Our next results concern the optimizations involved, and their finite
+sample statistical performance.
+
+\subsection{Optimization}
+
+\subsection{Finite-sample analysis}

### 2014-07-08 tex/scam/summary.tex
added optimization subsection

@@
 
-\subsection{Additive faithfulness}
+\subsection{Faithful screening}
 
@@
 \begin{align}
+\label{eq:convreg}
 \begin{split}
@@
 with $\mh{}\mathcal{C}^1$ denoting the set of univariate concave
-function.  Then, $f^*_k = 0$ and $g^*_k = 0$ implies that $f$ does not
+functions.  Then $f^*_k = 0$ and $g^*_k = 0$ implies that $f$ does not
 depend on $x_k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ with
@@
 
-This result suggests a two-stage screening
-procedure for variable selection. In the first stage we fit a sparse \emph{convex}
+This result naturally suggests a two-stage screening
+procedure for variable selection. In the first stage we fit a sparse convex
 additive model.  In the second stage we
@@
 having a zero convex component $\hat f_k$.  If both $\hat f_k = 0$ and
-$\hat g_k = 0$, we remove variable $x_k$.  
-Our next results concern the optimizations involved, and their finite
+$\hat g_k = 0$, we can safely discard variable $x_k$.  
+Our next results concern the required optimizations, and their finite
 sample statistical performance.
@@
 
+In Section~\ref{sec:optimization} we present optimization algorithms for the additive convex regression stage.
+The convex constraints for the additive functions, analogous to 
+the multivariate constraints \eqref{eq:convreg},
+are  that each component $f_{k}(\cdot)$ 
+can be represented by its supporting hyperplanes, i.e.,
+\begin{equation}
+      f_{ki'} \geq f_{ki} + \beta_{ki}(x_{ki'}-x_{ki}) \quad \text{for
+        all $i,i'$}
+\end{equation}
+where $f_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
+subgradient at point $x_{ki}$. While this apparently requires $O(n^2
+p)$ equations to impose the supporting hyperplane constraints, 
+in fact, only $O(np)$ constraints suffice.  This is because univariate convex functions are
+characterized by the condition that the subgradient, which is a scalar, must
+increase monotonically. This observation leads to a reduced quadratic
+program with $O(np)$ variables and $O(np)$ constraints.
+
+Directly applying a QP solver to this optimization is still computationally
+expensive for relatively large
+$n$ and $p$.  We thus develop a block
+coordinate descent method, where in each step we solve a sparse
+QP involving $O(n)$ variables and $O(n)$ constraints.  This 
+is efficiently solved using optimization packages 
+such as {\sc mosek}.  The details of these optimizations
+are given in Section~\ref{sec:optimization}.
+
 \subsection{Finite-sample analysis}

### 2014-07-11 tex/scam/summary.tex
added section on finite sample analysis

@@
 the quadratic programs required by the procedure.  
-Finally, the third problem we consider is the finite-sample
+Finally, the third problem we consider is the finite sample
 behavior of our proposed method.
@@
 \given x_k )$, and $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$
-are all continuous as functions on $C$.\\
+are all continuous as functions on $C$.
 Define
@@
 
-\subsection{Finite-sample analysis}
+\subsection{Finite sample analysis}
+
+In Section~\ref{sec:finitesample} 
+we analyze the finite sample variable selection consistency of convex
+additive modeling, without making the assumption that the true
+regression function is additive.  Our analysis first establishes
+a sufficient deterministic condition for variable selection 
+consistency, and then considers a stochastic setting.
+Our proof technique decomposes the KKT conditions for the optimization
+in a manner that is similar to the now standard \emph{primal-dual
+  witness} method~\cite{wainwright2009sharp}.
+
+We prove separate results that allow us to analyze false negative
+rates and false positive rates.  To control false positives,
+we analyze when the condition on $\lambda_n$ is fulfilled for all $j$
+and all $k \in S^c$, where $S\subset \{1,\ldots, p\}$ is the set of
+relevant variables. 
+To control false negatives, we analyze the restricted regression
+where the variables in $S^c$ are zeroed out, following the primal-dual
+strategy.
+
+Each of our theorems uses a subset of the following assumptions:
+\begin{packed_enum}
+\item[A1:] $X_S, X_{S^c}$ are independent. 
+\item[A2:] $f_0$ is convex and twice-differentiable. 
+\item[A3:] $|\partial_{x_k} f_0 | \leq L$ for all $k$
+\item[A4:] The noise $w$ is mean-zero sub-Gaussian, independent of $X$
+\end{packed_enum}
+
+We define $\alpha_f, \alpha_g$ as a measure of the signal strength of the weakest variable:
+\begin{align*}
+\alpha_f &= \inf_{f \in \mathcal{C}^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
+        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
+\alpha_g &=   \min_{k \in S \,:\, g^*_k \neq 0}
+      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
+    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}
+\end{align*}
+
+Intuitively, if $\alpha_f$ is smaller, then it is easier to make a
+false omission in the additive convex stage of the procedure. If
+$\alpha_g$ is smaller, then it is easier to make a false omission in
+the decoupled concave stage of the procedure.
+
+We make strong assumptions on the covariates in A1 in order to make
+very weak assumptions on the true regression function $f_0$ in
+A2; in particular, we do not assume that $f_0$ is additive.
+
+We also include an extra
+Lipschitz constraint so that we can use existing covering number
+results \cite{Bronshtein:76}. Recent work
+\cite{Guntu:13} shows that the Lipschitz constraint
+is not required with more advanced empirical process theory
+techniques; we leave the incorporation of this development as future work.
+
+Our main result is the following.
+\begin{theorem}
+Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and
+$\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints,
+both with  regularization parameter $\lambda$ scaling as
+$\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
+Suppose in addition that
+\begin{gather}
+\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2
+  np}\\
+\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}}
+  \log^2 2np}.
+\end{gather}
+Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$:
+\begin{align*}
+\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
+\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S.
+\end{align*}
+
+\end{theorem}
+
+This shows that variable selection consistency is achievable at the
+same exponential scaling of the ambient dimension $p = O(\exp(n^c)),
+c<1$ rate,  as for linear models. The cost of nonparametric modeling is
+reflected in the scaling with respect to $s$, which can only scale at
+$o(n^{4/25})$.
+
+We remark that \citet{dalalyan:12} show that under tradtional smoothness
+constraints, variable selection is achievable only if $n > O(e^s)$. 
+Here we demonstrate that convexity yields the scaling $n =
+O(\textrm{poly}(s))$.

### 2014-07-11 tex/scam/appendix.tex
some changes

@@
 Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_L\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
-Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
 
-According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
-\[
-P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
-  4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
-\]
-where $R = 4sLb$ for our purpose.
+% Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
 
-Restated, we have that, with probablity at least $1-\delta$,
-\[
-\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
-   c R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
-      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
-       c \sigma \sqrt{\frac{1}{n}} 
-\]
+% According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
+% \[
+% P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
+%   4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
+% \]
+% where $R = 4sLb$ for our purpose.
 
-Now we evaluate the integral. Since $N_{\|\cdot\|_n}(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.
+% Restated, we have that, with probablity at least $1-\delta$,
+% \[
+% \sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
+%    c R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
+%       \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
+%        c \sigma \sqrt{\frac{1}{n}} 
+% \]
 
-\begin{align*}
-\int_0^R \sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} dt &\leq 
-      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
- &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
- &= \sqrt{C s^{1.5} b L} \, c (sLb)^{3/4} \\
- &\leq c (s b L)^2
-\end{align*}
+% Now we evaluate the integral. Since $N_{\|\cdot\|_n}(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.
 
-Coming back, we have, with probability at least $1-\delta$,
-\begin{align*}
-\sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
-   c sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
-    c (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
- &\leq c (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
-\end{align*}
+% \begin{align*}
+% \int_0^R \sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} dt &\leq 
+%       \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
+%  &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
+%  &= \sqrt{C s^{1.5} b L} \, c (sLb)^{3/4} \\
+%  &\leq c (s b L)^2
+% \end{align*}
+
+% Coming back, we have, with probability at least $1-\delta$,
+% \begin{align*}
+% \sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
+%    c sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
+%     c (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
+%  &\leq c (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
+% \end{align*}
 
@@
 
-For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-cover of $\mathcal{G}$ closest to $h$.
+By Corollary~\ref{cor:convexbracket_ln}, there exists a bracketing $\mathcal{G}_\epsilon$ of $\mathcal{G}$ which has sized bounded by [TODO:...], which is an $\epsilon$-bracketing with respect to the $L_2(P)$ norm, and which is also an $(\epsilon + \epsilon_{n,\delta})$-bracketing with respect to the $L_n$ norm with probability at least $1-\delta$.
+
+For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$.
 It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\
@@
 
-\subsubsection{Covering Number for Lipschitz Convex Functions}
+\subsubsection{Bracketing Number for Convex Functions}
 
 \begin{definition}
-$\{ f_1,..., f_N\} \subset \mathcal{C}[b,B,L]$ is an $\epsilon$-covering of $\mathcal{C}[b,B,L]$ if for all $f \in \mathcal{C}[b,B,L]$, there exist $f_i$ such that $\| f - f_i \|_\infty \leq \epsilon$.
+% upper, lower, epsilon room
+% metric
+% function space
+Let $\mathcal{C}$ be a set of functions.
+For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f^L, f^U) \}$ satisfying (1) $\rho( f^L, f^U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f^L, f^U)$ where $f^U \geq f \geq f^L$.
 
-We define $N_\infty( \epsilon, \mathcal{C}[b,B,L])$ as the size of the minimum covering.
+We let $N_{[]}(\epsilon, \mathbf{C}, \rho)$ denote the size of the smallest bracketing of $\mathcal{C}$
 \end{definition}
 
-\begin{lemma} (Bronshtein 1974)
+\begin{proposition} (Proposition 16 in \cite{kim2014global})\\
+\label{prop:convexbracket}
+Let $\mathcal{C}$ be the set of convex functions supported on $[-b, b]^d$ and uniformly bounded by $B$. Then there exist constants $\epsilon_3$ and $K^{**}$, dependent on $d$, such that
 \[
-\log N_\infty (\epsilon, \mathcal{C}[b,B,L]) \leq C\left( \frac{bBL}{\epsilon} \right)^{1/2}
+\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
 \]
-For some absolute constant $C$.
-\end{lemma}
+for all $\epsilon \in (0, B \epsilon_3]$.
+\end{proposition}
 
-\begin{lemma}
+It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for a distribution $P$ with an uniformly upper bounded density.
+
+\begin{corollary}
+\label{cor:convexbracket_lp}
+Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
 \[
-\log N_\infty( \epsilon, \mathcal{C}^s[b,B,L])  \leq C s \left(\frac{bBLs}{\epsilon}\right)^{1/2}
+\log N_{[]} (2\epsilon, \mathcal{C}, L_2(P)) \leq K^{**} \left( \frac{2bB c_u}{\epsilon} \right)^{d/2}
 \]
-For some absolute constant $C$.
-\end{lemma}
+\end{corollary}
+
+Given samples $X_1,..., X_n \in \R^p$, we define $L_n$-norm as $\| f \|^2_n \equiv \frac{1}{n}\sum_{i=1}^n f(X_i)^2$.
+The following result follows from Corollary~\ref{cor:convexbracket_lp} directly by an union bound.
+
+\begin{corollary}
+\label{cor:convexbracket_ln}
+Let $X_1,...,X_n$ be random samples from a distribution $P$.
+Let $1 > \delta > 0$.
+Let $\mathcal{C}_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}$ with respect to the $L_2(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}, L_2(P))$.
+\\
+
+Then, with probability at least $1-\delta$, for all pairs $(f^L, f^U) \in \mathcal{C}_\epsilon$, $\frac{1}{n} \sum_{i=1}^n ( f^L(X_i) - f^U(X_i)^2 \leq \epsilon + \epsilon_{n, \delta}$, where 
+$\epsilon_{n,\delta} \equiv 
+B^2 \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
+B^2 \sqrt{ \frac{K^{**} (2bBc_u)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
+\end{corollary}
 
 \begin{proof}
-Let $f = \sum_{k=1}^s f_k$ be a convex additive function. Let $\{ f'_k \}_{k=1,..,s}$ be $k$ functions from a $\frac{\epsilon}{s}$ $L_\infty$ covering of $\mathcal{C}[b,B,L]$.
-
-Let $f' \coloneqq \sum_{k=1}^s f'_k$, then 
-\[
-\| f' - f \|_{\infty} \leq \sum_{k=1}^s \| f_k - f'_k \|_\infty \leq s \frac{\epsilon}{s} \leq \epsilon
-\]
-
-Therefore, a product of $s$ $\frac{\epsilon}{s}$-coverings of univariate functions induces an $\epsilon$-covering of the additive functions.
+$(f^L(X_i) - f^U(X_i))^2$ is at most $B^2$.
+There are $N_{[]}(2\epsilon, \mathcal{C}, L_2(P))$ pairs $(f^L, f^U)$.
+The corollary follows from a direct application of union bound and Hoeffding Inequality.
 \end{proof}
 
-In our proofs, we will use the Dudley's chaining: [TODO:cite van de geer]
+% \subsubsection{Covering Number for Lipschitz Convex Functions}
 
-\begin{theorem} (Dudley's Chaining) \\
-\label{thm:chaining}
-Let $\mathcal{G} = \{ g : \| g \|_n \leq R \}$.
+% \begin{definition}
+% $\{ f_1,..., f_N\} \subset \mathcal{C}[b,B,L]$ is an $\epsilon$-covering of $\mathcal{C}[b,B,L]$ if for all $f \in \mathcal{C}[b,B,L]$, there exist $f_i$ such that $\| f - f_i \|_\infty \leq \epsilon$.
+
+% We define $N_\infty( \epsilon, \mathcal{C}[b,B,L])$ as the size of the minimum covering.
+% \end{definition}
+
+% \begin{lemma} (Bronshtein 1974)
+% \[
+% \log N_\infty (\epsilon, \mathcal{C}[b,B,L]) \leq C\left( \frac{bBL}{\epsilon} \right)^{1/2}
+% \]
+% For some absolute constant $C$.
+% \end{lemma}
+
+% \begin{lemma}
+% \[
+% \log N_\infty( \epsilon, \mathcal{C}^s[b,B,L])  \leq C s \left(\frac{bBLs}{\epsilon}\right)^{1/2}
+% \]
+% For some absolute constant $C$.
+% \end{lemma}
+
+% \begin{proof}
+% Let $f = \sum_{k=1}^s f_k$ be a convex additive function. Let $\{ f'_k \}_{k=1,..,s}$ be $k$ functions from a $\frac{\epsilon}{s}$ $L_\infty$ covering of $\mathcal{C}[b,B,L]$.
+
+% Let $f' \coloneqq \sum_{k=1}^s f'_k$, then 
+% \[
+% \| f' - f \|_{\infty} \leq \sum_{k=1}^s \| f_k - f'_k \|_\infty \leq s \frac{\epsilon}{s} \leq \epsilon
+% \]
+
+% Therefore, a product of $s$ $\frac{\epsilon}{s}$-coverings of univariate functions induces an $\epsilon$-covering of the additive functions.
+% \end{proof}
+
+% In our proofs, we will use the Dudley's chaining: [TODO:cite van de geer]
+
+% \begin{theorem} (Dudley's Chaining) \\
+% \label{thm:chaining}
+% Let $\mathcal{G} = \{ g : \| g \|_n \leq R \}$.
 Let $M( \epsilon, R)$ be the size of the minimal $\epsilon$-covering of $\mathcal{G}$ with respect to the $\| \cdot \|_n$ norm.
@@
 
-Suppose $\delta > 0$ is such that
-\[
-\sqrt{n} \delta \geq \sigma \Big( 
-   14 \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
-      \Big)\vee 70 \log 2 R
-\]
-Then we have that 
-\[
-P\Big( \sup_{g \in \mathcal{G}} \langle w, g \rangle_n \geq \delta \Big) \leq
-  4 \exp \Big( - \frac{n \delta^2}{(70R)^2\sigma^2} \Big)
-\]
-\end{theorem}
+% Suppose $\delta > 0$ is such that
+% \[
+% \sqrt{n} \delta \geq \sigma \Big( 
+%    14 \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
+%       \Big)\vee 70 \log 2 R
+% \]
+% Then we have that 
+% \[
+% P\Big( \sup_{g \in \mathcal{G}} \langle w, g \rangle_n \geq \delta \Big) \leq
+%   4 \exp \Big( - \frac{n \delta^2}{(70R)^2\sigma^2} \Big)
+% \]
+% \end{theorem}
 
-For convenience, we can upper bound the metric-entropy sum with an integral: \\
-$\ds \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
-  \leq \int_0^R \sqrt{\log M(t, \mathcal{G}) } dt
-$
+% For convenience, we can upper bound the metric-entropy sum with an integral: \\
+% $\ds \sum_{s=0}^\infty 2^{-s} \sqrt{ \log M( 2^{-s} R, \mathcal{G})} 
+%   \leq \int_0^R \sqrt{\log M(t, \mathcal{G}) } dt
+% $
 

### 2014-07-11 tex/scam/introduction.tex
some changes

--- 2014-06-29 tex/scam/introduction.tex
@@
 
-Shape restrictions such as monotonicity, convexity, and concavity
-provide a natural way of limiting the complexity of many statistical
-estimation problem.  Shape-constrained estimation is not as well
-understood as more traditional nonparametric estimation involving
-smoothness constraints.  For instance, as of this writing the minimax
-rate of convergence for multivariate convex regression has yet to be
-rigorously established in full generality.  Even the one-dimensional
-case is challenging, and has been of recent interest
-\citep{guntusen:13}.
+We consider the problem of estimating a convex function of several
+variables from noisy values of the function at a finite sample of
+input points.
 
-In this paper we study the problem of variable selection
-in convex regression.   Assuming that the regression
-function is convex and sparse, in order to select the
-relevant variables we 
+Recent work \cite{Guntu:12,Guntu:13} shows that the
+minimax rate for convex function estimation in $p$ dimensions is
+$n^{-4/(4+p)}$.  Loosely speaking, this shows that the
+geometric convexity constraint is statistically equivalent to
+requiring two derivatives of the function, and thus is
+subject to the same curse of dimensionality.
+
+However, if the function is sparse, with $s\ll p$ relevant variables,
+then the faster rate $n^{-4/(4+s)}$ may be achievable if the $s$
+variables can be identified.  To determine the relevant variables, we
 show that it suffices to estimate a sum of $p$ one-dimensional convex
 functions, leading to significant computational and statistical
-advantages .  In addition, we introduce algorithms and supporting
+advantages.  In addition, we introduce algorithms and supporting
 statistical theory for a practical, effective approach to this

### 2014-07-11 tex/scam/abstract.tex

@@
   procedure is faithful in the population setting, yielding no false
-  negatives, and we give a finite sample statistical analysis. In
-  addition, we introduce algorithms for efficiently carrying out the
-  required quadratic programs. The approach leads to significant
-  computational and statistical advantages over fitting a full model,
-  and provides an effective, practical approach to variable screening
-  in convex regression.
+  negatives.  We give a finite sample statistical analysis, and introduce
+  algorithms for efficiently carrying out the required quadratic
+  programs. The approach leads to significant computational and
+  statistical advantages over fitting a full model, and provides an
+  effective, practical approach to variable screening in convex
+  regression.
 \end{abstract}

### 2014-07-11 tex/scam/faithful.tex

@@
 \usepackage[hscale=0.7,vscale=0.8]{geometry}
-
 \usepackage{subfigure}
@@
 \usepackage{yhmath}
-
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-\DeclareMathOperator{\rank}{rank}
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\trace}{trace}
-\DeclareMathOperator{\pr}{Prob}
-\DeclareMathOperator{\cov}{Cov}
-\newcommand{\EE}[1]{\mathbb{E}({#1})}
-\def\interleave{|\kern-.25ex|\kern-.25ex|}
-\def\interleavesub{|\kern-.15ex|\kern-.15ex|}
-\newcommand{\nnorm}[1]{\interleave {#1} \interleave}
-\newcommand{\nnormsub}[1]{\interleavesub {#1} \interleavesub}
-\newcommand{\nNorm}[1]{\left|\kern-.25ex\left|\kern-.25ex\left| {#1}\right|\kern-.25ex\right|\kern-.25ex\right|}
-\newcommand{\norm}[1]{\left\|{#1}\right\|}
-%\newcommand{\trnorm}[1]{\norm{{#1}}_{\mathrm{tr}}}
-\newcommand{\trnorm}[1]{\norm{{#1}}_{*}}
-\newcommand{\spnorm}[1]{\norm{{#1}}_{\mathrm{sp}}}
-\newcommand{\frnorm}[1]{\norm{{#1}}_{\mathrm{F}}}
-%\newcommand{\trnnorm}[1]{\nnorm{{#1}}_{\mathrm{tr}}}
-\newcommand{\trnnorm}[1]{\nnorm{{#1}}_{*}}
-\newcommand{\spnnorm}[1]{\nnorm{{#1}}_{\mathrm{sp}}}
-\newcommand{\spnnormsub}[1]{\nnormsub{{#1}}_{\mathrm{sp}}}
-\newcommand{\frnnorm}[1]{\nnorm{{#1}}_{\mathrm{F}}}
-\newcommand{\Norm}[1]{\left\|{#1}\right\|}
-%\newcommand{\Trnorm}[1]{\Norm{{#1}}_{\mathrm{tr}}}
-\newcommand{\Trnorm}[1]{\Norm{{#1}}_{*}}
-\newcommand{\Spnorm}[1]{\Norm{{#1}}_{\mathrm{sp}}}
-\newcommand{\Frnorm}[1]{\Norm{{#1}}_{\mathrm{F}}}
-%\newcommand{\Trnnorm}[1]{\nNorm{{#1}}_{\mathrm{tr}}}
-\newcommand{\Trnnorm}[1]{\nNorm{{#1}}_{*}}
-\newcommand{\Spnnorm}[1]{\nNorm{{#1}}_{\mathrm{sp}}}
-\newcommand{\Frnnorm}[1]{\nNorm{{#1}}_{\mathrm{F}}}
-\newcommand{\colspan}[1]{\mathrm{colspan}\left({#1}\right)}
-\def\myllangle{\langle\mspace{-4mu}\langle\mspace{1mu}}
-\def\myrrangle{\mspace{1mu}\rangle\mspace{-4mu}\rangle}
-
-\numberwithin{equation}{section}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheoremstyle{remark}{\topsep}{\topsep}%
-     {\normalfont}% Body font
-     {}           % Indent amount (empty = no indent, \parindent = para indent)
-     {\bfseries}  % Thm head font
-     {.}          % Punctuation after thm head
-     {.5em}       % Space after thm head (\newline = linebreak)
-     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{assumption}{Assumption}[section]
-\newtheorem{definition}{Definition}[section]
 
@@
 
-% min's macros
-\mathchardef\mh="2D
-
-% John's macros
-\def\X{\mathcal{X}}
-\def\comma{\unskip,~}
-\def\truep{p^*}
-\def\div{\|\,}
-\long\def\comment#1{}
-\def\reals{{\mathbb R}}
-\def\R{\reals}
-\def\P{{\mathbb P}}
-\def\E{{\mathbb E}}
-\def\Cov{\mathop{\text{Cov}}}
-\def\supp{\mathop{\text{supp}\kern.2ex}}
-\def\argmin{\mathop{\text{\rm arg\,min}}}
-\def\arginf{\mathop{\text{\rm arg\,inf}}}
-\def\argmax{\mathop{\text{\rm arg\,max}}}
-\let\tilde\widetilde
-\def\csd{${}^*$}
-\def\mld{${}^\dag$}
-\def\dos{${}^\ddag$}
-\def\W{\widetilde Y}
-\def\Z{\widetilde X}
-\let\hat\widehat
-\let\tilde\widetilde
-\def\given{{\,|\,}}
-\def\ds{\displaystyle}
-\def\bs{\backslash}
-\def\1{{(1)}}
-\def\2{{(2)}}
-\def\pn{{(n)}}
-\def\ip{{(i)}}
-\def\Xbar{\overline{X}}
-\def\except{\backslash}
-\def\npn{\mathop{\textit{NPN\,}}}
-\def\i{{(i)}}
-\def\cE{{\mathcal{C}}}
-\def\cM{{\mathcal{M}}}
-\def\cF{{\mathcal{F}}}
-\def\cP{{\mathcal{P}}}
-\def\cG{{\mathcal{G}}}
-\def\tr{\mathop{\text{tr}}}
-\long\def\comment#1{}
-\def\ti#1{#1}
-\def\titi#1{\textit{#1}}
-\def\cram{{\sc cram}}
-\def\spam{{\small\sc SpAM}}
-\def\diag{\mathop{\rm diag}}
-\def\ones{\mathbf{1}}
-\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
-\def\fatnorm#1{\threebars #1 \threebars}
-\def\rank{\mathop{\rm rank}}
-\def\S{\mathcal{S}}
-\def\H{\mathcal{H}}
-\def\K{{K}}
-\def\rank{\mathop{\rm rank}}
-\def\half{{1/2}}
-\def\Y{\mathbb{Y}}
-\def\M{\mathbb{M}}
-\def\F{\mathbb{F}}
-\def\pinv{{-1}}
-%\def\ones{\mathds{1}}
-%\def\ones{1}
-\def\Res{Z}
-\def\Proj{P}
-\def\cN{{\mathcal N}}
-\def\cT{{\mathcal H}}
-\def\coloneqq{:=}
-\def\mathbf#1{\mbox{\boldmath $#1$}} 
-\def\bar#1{\overline{#1}}
+\input{macros}
 
@@
 
-% \tableofcontents
+%\tableofcontents
 
 \input{introduction}
-\input{related_work}
 \input{summary}

### 2014-07-12 tex/scam/introduction.tex
made a pass over the entire intro

--- 2014-07-01 tex/scam/introduction.tex
@@
 provide a natural way of limiting the complexity of many statistical
-estimation problem.  Shape-constrained estimation is not as well
+estimation problems.  Shape-constrained estimation is not as well
 understood as more traditional nonparametric estimation involving
@@
 
-In this paper we study the problem of variable selection in convex
-regression.  Assuming that the regression function is convex and
+In this paper we study the problem of variable selection in
+multivariate convex regression.  Assuming that the regression function is convex and
 sparse, our goal is to identify the relevant variables.  We show that
@@
 second stage, we fit a concave function on the residual for each
-variable.  As we demonstrate, this perhaps non-intuity second stage is
+variable.  As we demonstrate, this non-intuitive second stage is
 in general necessary.  Our first result is that this procedure is
@@
 false negatives, under mild assumptions on the density of the
-covariates.  Our second result is a finite-sample statistical analysis
+covariates.  Our second result is a finite sample statistical analysis
 of the procedure, where we upper bound the statistical rate of
@@
 An additional contribution is to show how these quadratic programs can
-be forumlated to be more scalable.  Simulations demonstrate the method
-performs in a manner that is consistent with our analysis.
+be formulated to be more scalable.  We give simulations that
+demonstrate our method, showing that it performs in a manner that is consistent with our analysis.
 
@@
 But the method only provably scales to dimensions $p$ that 
-grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  Note that this
-is the opposite of the high dimensional scaling behavior
+grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  This
+is in contrast to the high dimensional scaling behavior
 known to hold for sparsity selection in linear models
@@
 using techniques based on hierarchical hashing schemes,
-similar to those used for ``junta'' problems \cite{mossel:04}.
+similar to those used for ``junta'' problems \citep{mossel:04}.
 Here it is shown that the sample complexity scales as $n > \log p$ 
@@
 
-\citet{dalalyan:12} show that the exponential scaling $p=O(\log n)$ is achievable if the underlying function is assumed to be smooth with respect to a Fourier basis. They also give
-support for the intrinsic difficulty of variable
-selection in nonparametric regression, giving lower bounds 
-showing that sparsistency is not possible if $n < \log p$ or if $n <
-\exp s$, where $s$ is the number of relevant variables.
-Variable selection over kernel classes is studied
-by \citet{Kolch:10}.
+\citet{dalalyan:12} show that the exponential scaling $n=O(\log p)$ is
+achievable if the underlying function is assumed to be smooth with
+respect to a Fourier basis. They also give support for the intrinsic
+difficulty of variable selection in nonparametric regression, giving
+lower bounds showing that consistent variable selection is not
+possible if $n < \log p$ or if $n < \exp s$, where $s$ is the number
+of relevant variables.  Variable selection over kernel classes is
+studied by \citet{Kolch:10}.
 
@@
 component function belonging to an RKHS.  An advantage of working over
-an RKHS, in contrast to the other papers mentioned above, is that
-nonparametric regression with a sparsity-inducing regularization penalty can be
-formulated as a finite dimensional convex cone optimization.
-On the other hand, 
-smoothing parameters for the component Hilbert spaces
-must be chosen, leading to extra tuning parameters
-that are difficult to select in practice.  In addition, 
-the additive model must be assumed to
-be correct for sparsistent variable selection.
+an RKHS is that nonparametric regression with a sparsity-inducing
+regularization penalty can be formulated as a finite dimensional
+convex cone optimization.  On the other hand, smoothing parameters for
+the component Hilbert spaces must be chosen, leading to extra tuning
+parameters that are difficult to select in practice.  In addition, the
+additive model must be assumed to be correct for consistent variable
+selection.
 
@@
 problem is naturally formulated using finite dimensional convex
-optimization, but with no additional tuning parameters.  As we show
-below, our method scales to high dimensions, with a dependence on the
+optimization, with no additional tuning parameters.  As we demonstrate,
+our method scales to high dimensions, with a dependence on the
 intrinsic dimension $s$ that scales polynomially, rather than
@@
 results, including additive faithfulness, variable selection 
-consistency, and high dimensional scaling.  In Section~X...
+consistency, and high dimensional scaling.  In
+Section~\ref{sec:additivefaithful} we give a detailed account
+of our method and the conditions under which we can guarantee
+consistent variable selection.  In Section~\ref{sec:optimization}
+we show how the required quadratic programs can be reformulated
+to be more efficient and scalable.  In Section~\ref{sec:finitesample}
+we give the details of our finite sample analysis, showing
+the scaling $n = O\big(\textrm{poly}(s) \log p\big)$
+is sufficient for variable selection.  In Section~\ref{sec:thesims}
+we report the results of simulations that illustrate our methods
+and theory.  The full proofs of are
+given in a technical appendix.
 

### 2014-07-13 tex/scam/abstract.tex
typo

@@
   procedure is faithful in the population setting, yielding no false
-  negatives.  We give a finite sample statistical analysis, and introduce
-  algorithms for efficiently carrying out the required quadratic
-  programs. The approach leads to significant computational and
+  negatives.  We give a finite sample statistical analysis, and
+  introduce algorithms for efficiently carrying out the required
+  quadratic programs. The approach leads to computational and
   statistical advantages over fitting a full model, and provides an

### 2014-07-13 tex/scam/introduction.tex
got rid of some useless words

@@
 understood as more traditional nonparametric estimation involving
-smoothness constraints.  For instance, as of this writing, the minimax
-rate of convergence for multivariate convex regression has yet to be
-rigorously established in full generality.  Even the one-dimensional
-case is challenging, and has been of recent interest
-\citep{guntusen:13}.
+smoothness constraints.  For instance, the minimax rate of convergence
+for multivariate convex regression has yet to be rigorously
+established in full generality.  Even the one-dimensional case is
+challenging, and has been of recent interest \citep{guntusen:13}.
 
 In this paper we study the problem of variable selection in
-multivariate convex regression.  Assuming that the regression function is convex and
-sparse, our goal is to identify the relevant variables.  We show that
-it suffices to estimate a sum of $p$ one-dimensional convex functions,
-leading to significant computational and statistical advantages.  This
-is in contrast to general nonparametric regression, where fitting an
-additive model can result in false negatives.  Our approach is based
-on a two-stage quadratic programming procedure.  In the first stage,
-we fit an convex additive model, imposing a sparsity penalty.  In the
-second stage, we fit a concave function on the residual for each
-variable.  As we demonstrate, this non-intuitive second stage is
-in general necessary.  Our first result is that this procedure is
-faithful in the population setting, meaning that it results in no
-false negatives, under mild assumptions on the density of the
-covariates.  Our second result is a finite sample statistical analysis
-of the procedure, where we upper bound the statistical rate of
-convergence.  Each stage of the method requires quadratic programming.
-An additional contribution is to show how these quadratic programs can
-be formulated to be more scalable.  We give simulations that
-demonstrate our method, showing that it performs in a manner that is consistent with our analysis.
+multivariate convex regression.  Assuming that the regression function
+is convex and sparse, our goal is to identify the relevant variables.
+We show that it suffices to estimate a sum of one-dimensional convex
+functions, leading to significant computational and statistical
+advantages.  This is in contrast to general nonparametric regression,
+where fitting an additive model can result in false negatives.  Our
+approach is based on a two-stage quadratic programming procedure.  In
+the first stage, we fit an convex additive model, imposing a sparsity
+penalty.  In the second stage, we fit a concave function on the
+residual for each variable.  As we show, this non-intuitive second
+stage is in general necessary.  Our first result is that this
+procedure is faithful in the population setting, meaning that it
+results in no false negatives, under mild assumptions on the density
+of the covariates.  Our second result is a finite sample statistical
+analysis of the procedure, where we upper bound the statistical rate
+of convergence.  An additional contribution is to show how the
+required quadratic programs can be formulated to be more scalable.  We
+give simulations to illustrate our method, showing that it performs in
+a manner that is consistent with our analysis.
 
@@
 
-Perhaps most closely related to the present work, is the framework
+Perhaps most closely related to the present work is the framework
 studied by \cite{Raskutti:12} for sparse additive models, where sparse
@@
 
-An attraction of the convex function estimation framework we consider
-in this paper is that the additive model can be used for convenience,
-without assuming it to actually hold.  While nonparametric, the
-problem is naturally formulated using finite dimensional convex
-optimization, with no additional tuning parameters.  As we demonstrate,
-our method scales to high dimensions, with a dependence on the
-intrinsic dimension $s$ that scales polynomially, rather than
-exponentially as in the general case analyzed in \cite{dalalyan:12}.
+While nonparametric, the convex regression problem is naturally
+formulated using finite dimensional convex optimization, with no
+additional tuning parameters.  The convex additive model can be used
+for convenience, without assuming it to actually hold, for the purpose
+of variable selection.  As we show, our method scales to high
+dimensions, with a dependence on the intrinsic dimension $s$ that
+scales polynomially, rather than exponentially as in the general case
+analyzed in \cite{dalalyan:12}.
 
@@
 we give the details of our finite sample analysis, showing
-the scaling $n = O\big(\textrm{poly}(s) \log p\big)$
+that a sample size growing as $n = O\big(\textrm{poly}(s) \log p\big)$
 is sufficient for variable selection.  In Section~\ref{sec:thesims}
 we report the results of simulations that illustrate our methods
-and theory.  The full proofs of are
+and theory.  The full proofs are
 given in a technical appendix.

### 2014-07-13 tex/scam/summary.tex
tightened up the writing

@@
 In this section we provide a high-level description of our technical
-results.  Our presentation is intended to give the reader
-an overview of our results and their significance.  The 
-full technical details, the precise statement of the results,
-and their detailed proofs are provided in following sections.
+results.  The full technical details, the precise statement of the
+results, and their detailed proofs are provided in following sections.
 
-Our results address three problems.  The first is to develop
-a procedure based on an additive approximation for identifying
-relevant variables in convex regression.  To this end,
-we prove a result that shows when and how the additive approximation
-be used without introducing false negatives in the population setting.  The
-second result concerns the efficient implementation of
+Our main contribution is an analysis of an additive approximation for identifying
+relevant variables in convex regression.  
+We prove a result that shows when and how the additive approximation
+can be used without introducing false negatives in the population
+setting.  In addition, we develop algorithms for the efficient implementation of
 the quadratic programs required by the procedure.
-Finally, the third problem we consider is the finite sample
-behavior of our proposed method.
 
-We first establish some notation, to be used throughout the remainder 
-of the paper.
+We first establish some notation, to be used throughout the  paper.
 If $\mathbf{x}$ is a vector, we use $\mathbf{x}_{-k}$ to denote the
@@
 magnitude, and $v_{(j)}$ denotes the $j$-th smallest; $\mathbf{1}_n \in \R^n$
-is the all ones vector. If $X \in \R^p$ and $S \subset
+is the all ones vector. If $X \in \R^p$ is a random variable and $S \subset
 \{1,...,p\}$, then $X_S$ is the subvector of $X$ restricted to
 the coordinates in $S$. Given $n$ samples $X^{(1)},...,X^{(n)}$, we use
-$\bar{X}$ to denote the empirical average. Given a random variable
-$X_k$ and a scalar $x_k$, we use $\E[\cdot \given x_k]$ as a shorthand
-for $\E[ \cdot \given X_k = x_k]$.
+$\bar{X}$ to denote the sample mean. Given a random variable
+$X_k$ and a scalar $x_k$, we use $\E[\,\cdot \given x_k]$ as a shorthand
+for $\E[\, \cdot \given X_k = x_k]$.
 
@@
 regression function may result in an additive component being wrongly
-zeroed out.  Surprisingly, this will not happen for convex regression
+zeroed out.  We show that this will not happen for convex regression
 under appropriate conditions.
 
-A differential function $f$ depends on variable $x_k$ if
+We say that a differentiable function $f$ depends on variable $x_k$ if
 $\partial_{x_k} f \neq 0$ with probability greater than zero.  An additive approximation is given by
@@
 \{f_k^*\}, \mu^* \coloneqq \argmin_{f_1,\ldots, f_p, \mu} \Bigl\{ 
-             \E ( f(X) - \mu - \sum_{k=1}^p f_k(X_k))^2 
+             \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 
          \,:\, \E f_k(X_k) = 0 \Bigr\}.
@@
 % is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.
-Additive faithfulness is a desireable property,
+Additive faithfulness is a desireable property
 since it implies that an additive approximation may allow us to 
@@
   Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.  Then $p$
-  satisfies the \emph{boundary-points condition} if, for all $j$, and
-  for all $\mathbf{x}_{-j}$:
+  satisfies the \emph{boundary points condition} if for all $j$, and
+  for all $\mathbf{x}_{-j}$,
 \[
@@
 
-\begin{theorem}
-  Let $p$ be a positive density supported on $C=[0,1]^s$ that
-  satisfies the boundary-points property. If $f$ is convex and twice
+\begin{stheorem}
+  Let $p$ be a positive density supported on $C=[0,1]^p$ that
+  satisfies the boundary points property. If $f$ is convex and twice
   differentiable, then $f$ is additively faithful under $p$.
-\end{theorem}
+\end{stheorem}
 
@@
 While this shows that convex functions are additively faithful, it is difficult to
-estimate the optimal additive functions $f^*_k$'s.  The difficulty
+estimate the optimal additive functions.  The difficulty
 is that $f^*_k$ need not be
@@
 Since the true regression function $f$ is convex, it is natural to ask
-when it is sufficient to estimate an convex additive model.  
+when it is sufficient to estimate a convex additive model.  
 Unfortunately, a convex additive approximation is not generally
@@
 shows that this type of error can be detected by fitting 
-a \textit{concave} function to the residual.  If the
-concave fit to the residual is zero, we can then safely
+a \textit{concave} function to the residual.  If this
+concave function is zero, we can then safely
 mark $x_k$ as an irrelevant variable.
 
-\begin{theorem}
+\begin{stheorem}
 Suppose $p(\mathbf{x})$ is a positive
-density on $C=[0,1]^p$ and satisfies the boundary-points
+density on $C=[0,1]^p$ that satisfies the boundary points
 condition. Suppose that $f$ is convex and twice-differentiable.
@@
 \begin{equation}
-\{ f^*_k \}_{k=1}^p,\mu^* = \arg\min \Big \{
-\E\big( f(X) - \mu - \sum_{k=1}^s f_k(X_k) \big)^2 \,:\, f_k \in
+\{ f^*_k \}_{k=1}^p,\mu^* = \arg\min_{\{f_k\},\mu} \Big \{
+\E\Bigl( f(X) - \mu - \sum_{k=1}^s f_k(X_k) \Bigr)^2 \,:\, f_k \in
 \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
@@
 \begin{equation}
-g^*_k = \arg\min \Big\{ \E\big( f(X) -
-\sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 \,:\, g_k \in \mh
+g^*_k = \arg\min_{g_k} \Big\{ \E\Bigl( f(X) - \mu^* - 
+\sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \Bigr)^2 \,:\, g_k \in \mh
 \mathcal{C}^1, \E g_k(X_k) = 0 \Big\},
@@
 probability one.
-\end{theorem}
+\end{stheorem}
 
@@
 procedure for variable selection. In the first stage we fit a sparse convex
-additive model.  In the second stage we
+additive model $\{\hat f_k\}$.  In the second stage we
 fit a concave function $\hat g_k$ to the residual for each variable
@@
 $\hat g_k = 0$, we can safely discard variable $x_k$.  
+As a shorthand, we refer to this two-stage procedure as AC/DC.  In 
+the AC stage we fit an additive convex model.  In the DC 
+stage we fit decoupled concave functions on the residuals.  The
+decoupled nature of the DC stage allows all of the fits to
+be carried out in parallel.
 Our next results concern the required optimizations, and their finite
@@
 Our main result is the following.
-\begin{theorem}
+\begin{stheorem}
 Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and
-$\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints,
-both with  regularization parameter $\lambda$ scaling as
+$\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints
+and with regularization parameter $\lambda$ scaling as
 $\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
@@
 
-\end{theorem}
+\end{stheorem}
 

### 2014-07-14 tex/scam/summary.tex
minor edits to the finite sample subsection

@@
 coordinate descent method, where in each step we solve a sparse
-QP involving $O(n)$ variables and $O(n)$ constraints.  This 
+quadratic program involving $O(n)$ variables and $O(n)$ constraints.  This 
 is efficiently solved using optimization packages 
@@
 additive modeling, without making the assumption that the true
-regression function is additive.  Our analysis first establishes
+regression function $f_0$ is additive.  Our analysis first establishes
 a sufficient deterministic condition for variable selection 
@@
 in a manner that is similar to the now standard \emph{primal-dual
-  witness} method~\cite{wainwright2009sharp}.
+  witness} method~\citep{wainwright2009sharp}.
 
@@
 rates and false positive rates.  To control false positives,
-we analyze when the condition on $\lambda_n$ is fulfilled for all $j$
-and all $k \in S^c$, where $S\subset \{1,\ldots, p\}$ is the set of
+we analyze scaling conditions on the regularization parameter
+$\lambda_n$ for 
+group sparsity needed to zero out irrelevant variables
+$k \in S^c$, where $S\subset \{1,\ldots, p\}$ is the set of
 relevant variables. 
@@
 \item[A3:] $|\partial_{x_k} f_0 | \leq L$ for all $k$
-\item[A4:] The noise $w$ is mean-zero sub-Gaussian, independent of $X$
+\item[A4:] The noise is mean-zero sub-Gaussian, independent of $X$.
 \end{packed_enum}
 
-We define $\alpha_f, \alpha_g$ as a measure of the signal strength of the weakest variable:
+Our analysis involves parameters $\alpha_f$ and $\alpha_g$,
+which are measures of the signal strength of the weakest variable:
 \begin{align*}
@@
       \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
-    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}
+    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}.
 \end{align*}
 
-Intuitively, if $\alpha_f$ is smaller, then it is easier to make a
+Intuitively, if $\alpha_f$ is small, then it is easier to make a
 false omission in the additive convex stage of the procedure. If
-$\alpha_g$ is smaller, then it is easier to make a false omission in
+$\alpha_g$ is small, then it is easier to make a false omission in
 the decoupled concave stage of the procedure.
@@
 A2; in particular, we do not assume that $f_0$ is additive. 
-
+Relaxing this condition is an important direction for future work.
 We also include an extra
 Lipschitz constraint so that we can use existing covering number
-results \cite{Bronshtein:76}. Recent work
+results \citep{Bronshtein:76}. Recent work
 \cite{Guntu:13} shows that the Lipschitz constraint
@@
 \begin{stheorem}
-Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and
-$\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints
-and with regularization parameter $\lambda$ scaling as
+Suppose assumptions A1-A4 hold. Let $\{\hat{f}_i\}$ be any AC solution and
+let $\{\hat{g}_k\}$ be any DC solution, both estimated with 
+regularization parameter $\lambda$ scaling as
 $\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
@@
 
-This shows that variable selection consistency is achievable at the
-same exponential scaling of the ambient dimension $p = O(\exp(n^c)),
-c<1$ rate,  as for linear models. The cost of nonparametric modeling is
-reflected in the scaling with respect to $s$, which can only scale at
-$o(n^{4/25})$.
+This shows that variable selection consistency is achievable under
+exponential scaling of the ambient dimension, $p = O(\exp(n^c))
+for c<1$, as for linear models. The cost of nonparametric estimation is
+reflected in the scaling with respect to $s=|S|$, which can grow only
+as $o(n^{4/25})$.
 
-We remark that \citet{dalalyan:12} show that under tradtional smoothness
+We remark that \citet{dalalyan:12} show that under traditional smoothness
 constraints, variable selection is achievable only if $n > O(e^s)$. 

### 2014-07-15 tex/scam/additive_faithful.tex
made a pass up to sec 3.1

@@
 \section{Additive Faithfulness}
+\label{sec:additivefaithful}
 
-For general regression, additive approximation may result in a
+For general regression, an additive approximation may result in a
 relevant variable being incorrectly marked as irrelevant. Such
-mistakes are inherent to the approximation and may persist even with
-infinite samples.  In this section we give
+mistakes are inherent to the approximation and may persist even in
+the population setting.  In this section we give
 examples of this phenomenon, and then show how the convexity
@@
 \label{lem:general_int_reduction}
-Let $F$ be a distribution on $C=[0,1]^s$ with a positive density function $p$. Let $f: C \rightarrow \R$ be an integrable function。
-
-Let $\ds f^*_1,...,f^*_s, \mu^* \coloneqq 
-\arg\min \{ \E \big( f(X) - \sum_{k=1}^s f_k(X_k) - mu \big)^2 \,:\, \forall k, \E f_k(X_k) = 0\}$
-
-Then 
-$$ f^*_k(x_k) = \E[ f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) \given x_k] - \E f(X) $$
- and $\mu^* = \E f(X)$ and this solution is unique.
+Let $F$ be a distribution on $C=[0,1]^p$ with a positive density
+function $p$. Let $f: C \rightarrow \R$ be an integrable function,
+and define 
+\begin{equation}
+f^*_1,...,f^*_s, \mu^* \coloneqq 
+\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
+\E f_k(X_k) = 0,\; \forall k=1,\ldots, p \right\}.
+\end{equation}
+Then $\mu^* = \E f(X)$,
+\begin{equation}
+\label{eq:backfit}
+f^*_k(x_k) = \E\Bigl[ f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) \given
+x_k\Bigr] - \E f(X) 
+\end{equation}
+and this solution is unique.
 \end{lemma}
@@
 Lemma~\ref{lem:general_int_reduction} follows from the stationarity
-conditions of the optimal solution.
+conditions of the optimal solution.   This result is known, and
+criterion \eqref{eq:backfit} is used in the backfitting
+algorithm for fitting additive models.   We include 
+a proof of the result as our results build on it.
+% perhaps include this in an appendix??
 
 \begin{proof}
-Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.
+  Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.  We first
+  show that the optimal $\mu$ is $\mu^* = \E f(X)$ for any $f_1, ...,
+  f_k$ such that $\E f_k(X_k) = 0$. This follows from the stationarity
+  condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] =
+  \E[ f(X) ]$. Uniqueness is apparent because the second derivative is
+  strictly larger than zero and strong convexity is guaranteed.
 
-We first show that the optimal $\mu^* = \E f(X)$ for any $f_1, ..., f_k$ such that $\E f_k(X_k) = 0$.
-This follows from the stationarity condition, which states that $\mu^* = \E[ f(X) - \sum_k f_k(X_k)] = \E[ f(X) ]$.
-Uniqueness is apparent because the second derivative is strictly larger than 0 and strong convexity is guaranteed.
-
-We now turn our attention toward the $f^*_k$'s.
-
-It must be that $f^*_k$ minimizes $\Big\{ \E \big( f(X) - \mu^* - \sum_{k' \neq k} f^*_{k'} (X_{k'}) - f_k (X_k) \big)^2 \,:\, \E f_k(X_k) = 0 \Big\}$.
-
-Fix $x_k$, we will show that the value 
-$\E[ f(X) - \sum_{k' \neq k} f_{k'}(X_{k'}) \given x_k] - \mu^*$, for all $x_k$,  
+  We now turn our attention toward the $f^*_k$s.  It must be that
+  $f^*_k$ minimizes 
+\begin{equation}
+\E\Bigl[ \big( f(X) - \mu^* - \sum_{k' \neq k}
+  f^*_{k'} (X_{k'}) - f_k (X_k) \big)^2\Bigr]
+\end{equation}
+subject to $\E f_k(X_k) = 0$.
+Fixing $x_k$, we will show that the value 
+\begin{equation}
+\E[ f(X) - \sum_{k' \neq k}
+f_{k'}(X_{k'}) \given x_k] - \mu^*
+\end{equation} 
 uniquely minimizes
-\[
+\begin{equation}
 \min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(\mathbf{x}) 
@@
                  d \mathbf{x}_{-k}.
-\]
-It easily follows then that the function $x_k \mapsto \E[ f(X) - \sum_{k'} f_{k'} (X_{k'}) \given x_k] - \mu^*$ is the unique $f^*_k$ that minimizes the expected square error.We focus our attention on $f^*_K$, and fix $x_k$.
-
-The first-order optimality condition gives us:
-
-\begin{align*}
+\end{equation}
+The first-order optimality condition gives us
+\begin{align}
 \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= 
@@
      (f(\mathbf{x}) - \sum_{k'\neq k} f_{k'} (x_{k'})  -\mu^*) d \mathbf{x}_{-k} 
- \end{align*}
-
-The square error objective is strongly convex.
-The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
+ \end{align}
+The square error objective is strongly convex,
+and the second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
 Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.
-
-Now, we note that as a function of $x_k$, $\E[ f(X) -\sum_{k'\neq k} f_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero and we thus finish the proof.
+Noting that $\E[ f(X) -\sum_{k'\neq k} f_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero as a function of $x_k$
+completes the proof.
 \end{proof}
 
-In the case that the distribution in Lemma~\ref{lem:general_int_reduction} is a product distribution, we get particularly clean expressions for the additive components.
+In the case that the distribution in
+Lemma~\ref{lem:general_int_reduction} is a product distribution, 
+the additive components take on a simple form.
 
@@
 \label{cor:product_int_reduction}
-Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let $\mu^*, f^*_k(x_k)$ be defined as in Lemma~\ref{lem:general_int_reduction}.
+Let $F$ be a product distribution on $C=[0,1]^p$ with density function
+$p$ which is positive on $C$. 
+Let $\mu^*, f^*_k(x_k)$ be defined as in Lemma~\ref{lem:general_int_reduction}.
 Then $\mu^* = \E f(X)$ and $f^*_k(x_k) = \E[ f(X) \given x_k] - \E f(X)$ and this solution is unique.
@@
 If $F$ is the uniform distribution,
-then $f^*_k(x_k) = \int f(x_k, \mathbf{x}_{-k})
+then $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k})
 d\mathbf{x}_{-k}$.
 
-\begin{example} Using Corollary~\ref{cor:product_int_reduction}, we give two examples of \emph{additive unfaithfulness} under
-  the uniform distribution, that is, examples where relevant variables are erroneously marked as irrelevant under an additive approximation. First, consider the following function:
+\begin{example} Using Corollary~\ref{cor:product_int_reduction}, we
+  give two examples of \emph{additively unfaithfulness} under the
+  uniform distribution---where relevant variables are
+  erroneously marked as irrelevant under an additive
+  approximation. First, consider the following function:
 \[
-\trm{(egg carton)} \quad f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)
+f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)\quad
+\trm{(egg carton)} 
 \]
 defined for $(x_1, x_2) \in [0,1]^2$.  Then
-$\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
-$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
+$\displaystyle\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
+$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
 would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
 \[
-\trm{(tilting slope)} \quad f(x_1, x_2) = x_1 x_2
+f(x_1, x_2) = x_1 x_2 \quad \trm{(tilting slope)} 
 \]
 defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
-$\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation.
+$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation.
 This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
@@
 
-In order to exploit additive models, it is important to understand when the
+In order to exploit additive models in variable selection, it is important to understand when the
 additive approximation accurately captures all of the relevant variables.
-We call this property \textbf{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{depends on} a coordinate $x_k$.
+We call this property \textit{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{depends on} a coordinate $x_k$.
 
 \begin{definition}
-  Let $F$ be a distribution on $\mathbf{C}=[0,1]^s$, and $f:\mathbf{C}\rightarrow \R$.
-
-We say that $f$ \textbf{depends on} coordinate $k$ if, for all $x_k \in [0,1]$, the set 
+  Let $F$ be a distribution on $C=[0,1]^p$, and $f:C \rightarrow \R$. 
+We say that $f$ \textit{depends on coordinate $k$} if, for all $x_k \in [0,1]$, the set 
 $\big\{ x'_k \in [0, 1] \,:\, f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k}) 
 \trm{ for almost all  $\mathbf{x}_{-k}$} \big\}$ 
-has probability strictly less than 1.\\
+has probability strictly less than one.
+If $f$ is differentiable, then $f$ depends on $k$ if $\partial_{x_k} f \neq 0$ with probability greater than zero.
 
-If $f$ is differentiable, then $f$ depends on $k$ if $\partial_{x_k} f \neq 0$ with probability greater than 0.\\
-
-Suppose we have the additive approximation:
+Suppose we have the additive approximation
 \begin{equation}
@@
 f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
-             \E ( f(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 
+             \E \Bigl[\bigl( f(X) - \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \Bigr]
          \,:\, \E f_k(X_k) = 0 \Bigr\}.
 \end{equation}
+We say that $f$ is \textit{additively faithful} under $F$ in case
+$f^*_k = 0$ implies that $f$ does not depend on coordinate $k$.
+\end{definition}
 
-We say that $f$ is \textbf{additively faithful} under $F$ in case $f^*_k = 0 \Rightarrow \trm{$f$ does not depend on coordinate $k$}$.
-
-\end{definition}
 % We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
@@
 
-Additive faithfulness is an attractive property because it implies that, in the population setting, the additive approximation yields consistent variable selection.
+Additive faithfulness is an attractive property because it implies
+that, in the population setting, the additive approximation yields
+consistent variable selection.
 
@@
 
-\subsection{Convex Additive Model}
+\subsection{Convex Additive Models}
 

### 2014-07-17 tex/scam/additive_faithful.tex
made a pass over sec 3.1

@@
 algorithm for fitting additive models.   We include 
-a proof of the result as our results build on it.
+a proof as our results build on it.
 % perhaps include this in an appendix??
@@
 
-If $F$ is the uniform distribution,
+In particular, if $F$ is the uniform distribution,
 then $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k})
@@
   approximation. First, consider the following function:
-\[
+\begin{equation}
 f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)\quad
 \trm{(egg carton)} 
-\]
+\end{equation}
 defined for $(x_1, x_2) \in [0,1]^2$.  Then
@@
 would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
-\[
+\begin{equation}
 f(x_1, x_2) = x_1 x_2 \quad \trm{(tilting slope)} 
-\]
+\end{equation}
 defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
@@
 f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
-             \E \Bigl[\bigl( f(X) - \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \Bigr]
+             \E \Bigl[\Bigl( f(X) - \sum_{k=1}^p f_k(X_k) -\mu \Bigr)^2 \Bigr]
          \,:\, \E f_k(X_k) = 0 \Bigr\}.
@@
 % We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
-% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^s$, then $f$
+% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^p$, then $f$
 % is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.
@@
 
-Remarkably, under a general class of distributions which we characterize below, convex multivariate functions are additively faithful.
+We now show that under a general class of distributions which we
+characterize below, convex multivariate functions are additively
+faithful.
 
@@
 \label{defn:boundary-point}
-Let $p(\mathbf{x})$ be a density supported on $[0,1]^s$, $p$ satisfies the \emph{boundary-points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
+A density $p(\mathbf{x})$ be a density supported on $[0,1]^p$ satisfies
+the \emph{boundary points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
 
-\[
+\begin{equation}
 \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
@@
 \quad \trm{at } x_k = 0, x_k = 1
-\]
+\end{equation}
 
@@
 
-The boundary-points condition is a weak condition.
-For instance, it is satisfied when the density is flat at the boundary of support, more precisely, when the \emph{joint density} satisfies the properties that $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =  \frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at points $x_j = 0, x_j=1$.
-The boundary-points property is also trivially satisfied when $p$ is the density of any product distributions.
+The boundary points condition is a weak condition. For instance, it is
+satisfied when the density is flat at the boundary of support---more
+precisely, when the joint density satisfies the property that
+$\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =
+\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at
+points $x_j = 0, x_j=1$. The boundary points property is also
+trivially satisfied when $p$ is a product density.
 
@@
 \label{thm:convex_faithful}
-Let $p$ be a positive density supported on $C=[0,1]^s$ that satisfies the boundary-points property (definition~\ref{defn:boundary-point}).
-If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $p$.
+Let $p$ be a positive density supported on $C=[0,1]^p$ that satisfies
+the boundary points property. 
+If $f$ is convex and twice differentiable, then $f$ is additively faithful under $p$.
 \end{theorem}
@@
 
-We pause to give some intuition before we present the full proof: 
-suppose the underlying distribution is a product distribution for a second, 
-then we know from lemma~\ref{lem:general_int_reduction} that the
+We pause to give some intuition before we presenting the full proof.
+Suppose that the the underlying distribution has a product density.
+Then we know from Lemma~\ref{lem:general_int_reduction} that the
 additive approximation zeroes out $k$ when, fixing $x_k$, every
@@
 
-\begin{proof} (of Theorem~\ref{thm:convex_faithful})\\
-Fix $k$.
-Using the result of Lemma~\ref{lem:general_int_reduction}, we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ implies that $f$ does not depend on coordinate $k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ for all $\mathbf{x}$.\\
+\begin{proof}
 
-Let us then use the shorthand notation that $r(\mathbf{x}_{-k}) = \sum_{k' \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that $\mu = 0$. We then assume that for all $x_k$,
+Fixing $k$ and using the result of
+Lemma~\ref{lem:general_int_reduction}, 
+we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'}
+f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ 
+implies that $f$ does not depend on coordinate $k$, i.e., 
+$\partial_{x_k} f(\mathbf{x}) = 0$ for all $\mathbf{x}$.
 
-\[
+Let us use the shorthand notation that $r(\mathbf{x}_{-k}) = \sum_{k'
+  \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that
+$\mu = 0$. We then assume that for all $x_k$,
+\begin{equation}
  \E[ f(X) - r(X_{-k})  \given x_k] \equiv 
  \int_{\mathbf{x}_{-k}}  p(\mathbf{x}_{-k} \given x_k ) 
- \big(f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) = 0
-\]
-
+ \big(f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) = 0.
+\end{equation}
 We let $p'(\mathbf{x}_{-k} \given x_k)$ denote 
@@
 $p''(\mathbf{x}_{-k} \given x_k)$ denote 
-$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k, \mathbf{x}_{-k})$.
-We then differentiate under the integral, which is valid because all functions are bounded.
-
-\begin{align}
-& \int_{\mathbf{x}_{-k}} p'(\mathbf{x}_{-k} \given x_k) 
+$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and
+likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k,
+\mathbf{x}_{-k})$. We then differentiate under the integral, valid
+because all functions are bounded, and obtain
+\begin{gather}
+\int_{\mathbf{x}_{-k}} p'(\mathbf{x}_{-k} \given x_k) 
 \big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) + 
@@
 \label{eqn:integral1a} \\
-& \int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
-\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 
-2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
-p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 
-\end{align}
+\int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
+\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
+p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 .
+\end{gather}
 
-By the boundary-points condition, we have that $p''(\mathbf{x}_{-k} \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k = x_k^0 \equiv 0$.
-The integral equations reduce to the following then:
+By the boundary points condition, we have that $p''(\mathbf{x}_{-k}
+\given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k =
+x_k^0 \equiv 0$. The integral equations then reduce to the following:
 \begin{align}
 & \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f'(x^0_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}= 0 \label{eqn:integral1b} \\
-& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f''(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} = 0
+& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f''(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} = 0.
 \end{align}
+Because $f$ is convex, $f(x_k, \mathbf{x}_{-k})$ must be a convex
+function of 
+$x_k$ for all $\mathbf{x}_{-k}$. Therefore, for all $\mathbf{x}_{-k}$,
+$f''(x^0_k, \mathbf{x}_{-k}) \geq 0$. Since $p(\mathbf{x}_{-k} \given
+x^0_k) > 0$ by the assumption that $p$ is a positive density, 
+we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.
 
-Because $f$ is convex, $f(x_k, \mathbf{x}_{-k})$ must be a convex function of $x_k$ for all $\mathbf{x}_{-k}$.
-Therefore, for all $\mathbf{x}_{-k}$, $f''(x^0_k, \mathbf{x}_{-k}) \geq 0$.
-Since $p(\mathbf{x}_{-k} \given x^0_k) > 0$ by assumption that $p$ is a positive density, we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.\\
+The Hessian of $f$ at $(x^0_k, \mathbf{x}_{-k})$ then has a zero at
+the $k$-th main diagonal entry. A positive semidefinite matrix with a
+zero on the $k$-th main diagonal entry must have only zeros on the
+$k$-th row and column; see proposition 7.1.10 of
+\citet{HJ90}.  Thus, at all $\mathbf{x}_{-k}$, the
+gradient of $f'(x^0_k, \mathbf{x}_{-k})$ with respect to
+$\mathbf{x}_{-k}$ must be zero.
+Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be constant for all
+$\mathbf{x}_{-k}$. By equation~\ref{eqn:integral1b}, we conclude 
+that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$. We
+can use the same reasoning for the case where $x_k = x_k^1$ and deduce
+that $f'(x^1_k, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
 
-The Hessian of $f$ at $(x^0_k, \mathbf{x}_{-k})$ then has a zero at the $k$-th main diagonal entry.
-A positive semidefinite matrix with a zero on the $k$-th main diagonal entry must have only zeros on the $k$-th row and column \footnote{ See proposition 7.1.10 of \citet{HJ90}}, which means that \emph{at all $\mathbf{x}_{-k}$, the gradient of $f'(x^0_k, \mathbf{x}_{-k})$ with respect to $\mathbf{x}_{-k}$ must be zero}.
-
-Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be constant for all $\mathbf{x}_{-k}$.
-By equation~\ref{eqn:integral1b}, we conclude then that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
-We can use the same reasoning for the case where $x_k = x_k^1$ and deduce that $f'(x^1_k, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.
-\\
-
-Because $f(x_k, \mathbf{x}_{-k})$ as a function of $x_k$ is convex, it must be that, for all $x_k \in (0,1)$ and for all $\mathbf{x}_{-k}$:
-\[
+Because $f(x_k, \mathbf{x}_{-k})$ as a function of $x_k$ is convex, it must be that, for all $x_k \in (0,1)$ and for all $\mathbf{x}_{-k}$,
+\begin{equation}
 0 = f'(x_k^0, \mathbf{x}_{-k}) \leq f'(x_k, \mathbf{x}_{-k}) \leq 
     f'(x_k^1, \mathbf{x}_{-k}) = 0
-\]
-
-$f$ thus does not depend on $x_k$.
+\end{equation}
+Therefore $f$ does not depend on $x_k$.
 % Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:
@@
 Theorem~\ref{thm:convex_faithful} plays an important role in our
-sparsistency analysis, where we show that the additive
+finite sample analysis, where we show that the additive
 approximation is variable selection consistent (or ``sparsistent''), even when the true function is not
@@
 \item If $f$ depends on $x_j$, then
-\[
+\begin{equation}
 f^*_j(x_j) = H_j^\tran \Sigma_j x_j^2 + c_j x_j
-\]
+\end{equation}
 where $H_j, \Sigma_j$ are the $j$-th row of $H_j, \Sigma_j$ respectively. 
@@
 \label{eqn:convex_additive}
-\{ f^*_k \}_{k=1}^s = \arg\min \Big \{ 
-    \E\big( f(X) - \sum_{k=1}^s f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
+\{ f^*_k \}_{k=1}^p = \arg\min \Big \{ 
+    \E\big( f(X) - \sum_{k=1}^p f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
 \end{equation}
@@
 \label{thm:acdc_faithful}
-Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary-points condition. Suppose that $f$ is convex and twice-differentiable.
+Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary points condition. Suppose that $f$ is convex and twice-differentiable.
 
@@
 \label{cor:faithfulness_extension}
-Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary-points condition.
+Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary points condition.
 
@@
 Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
-\[
+\begin{equation}
 \arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
-\]
+\end{equation}
 Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
@@
 Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
-\[
+\begin{equation}
 \arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
        - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
-\]
+\end{equation}
 Again, $c^* = \frac{\mathbb{E}[g(X)\big( 

### 2014-07-19 tex/scam/additive_faithful.tex
edits through 3.2

@@
   We assume twice differentiability in
-  Theorems~\ref{thm:convex_faithful} to simplify the proof. 
-  We believe
-  this smoothness condition is not necessary because every non-smooth
-  convex function can be approximated arbitrarily well by a smooth
-  one.  
+  Theorems~\ref{thm:convex_faithful} to simplify the proof.  We
+  expect, however, that this this smoothness condition is not
+  necessary---every convex function can be approximated arbitrarily
+  well by a smooth convex function.
 \end{remark}
@@
 \begin{remark} 
-It remains difficult to find conditions under which the opposite direction of additive faithfulness holds, that is, if $f$ does not depend on coordinate $k$, then $f_k^*$ will be zero in the additive approximation.
-As a conceptual example, suppose that $f$ is only a function of $X_1, X_2$, and that $(X_1, X_2, X_3)$ follows a degenerate 3-dimensional distribution where $X_3 = f(X_1, X_2) - f^*(X_1) - f^*_2(X_2)$, that is, we let $X_3$ exactly capture the additive approximation error.
-In this case, the best additive approximation of $f$ would have a component $f^*_3(X_3) = X_3$ even though $f$ does not depend on $X_3$.
+  We have not found natural conditions under which the opposite
+  direction of additive faithfulness holds---conditions implying that if $f$ does not
+  depend on coordinate $k$, then $f_k^*$ will be zero in the additive
+  approximation.  Suppose, for example, that $f$ is only a
+  function of $X_1, X_2$, and that $(X_1, X_2, X_3)$ follows a
+  degenerate 3-dimensional distribution where $X_3 = f(X_1, X_2) -
+  f^*(X_1) - f^*_2(X_2)$.  In this case $X_3$ exactly captures the
+  additive approximation error.  The best additive
+  approximation of $f$ would have a component $f^*_3(x_3) = x_3$ even
+  though $f$ does not depend on $x_3$.
 \end{remark}
 
-It is possible to get a similar result for distributions with unbounded support, by using a limit condition $\lim_{|x_k| \rightarrow \infty} \frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k} = 0$ instead of the boundary condition.
-Such a limit condition is too strong however, it is not obeyed by the multivariate Gaussian distribution.
-\\
+\begin{remark}
+It is possible to get a similar result for distributions with
+unbounded support, by using a limit condition $\lim_{|x_k| \rightarrow
+  \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}
+= 0$.  Such a limit condition is too
+strong however, as it is not obeyed by the multivariate Gaussian
+distribution. 
+\end{remark}
 
-In fact, not all convex functions are additively faithful under certain multivariate Gaussian distributions.
+The following example shows that not all convex functions are
+additively faithful under multivariate Gaussian distributions.
 
@@
 Consider a quadratic form $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c^\tran \mathbf{x}$ and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma_{jj} = 1$ for all $j$.
-
-Then we have a closed form for the additive approximation, which we prove in [TODO:appendix reference].
-\begin{itemize}
+As we show in the appendix, the additive approximation has the
+following closed form.
+\begin{enumerate}
 \item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
@@
 \end{equation}
-where $H_j, \Sigma_j$ are the $j$-th row of $H_j, \Sigma_j$ respectively. 
-\end{itemize}
-Let $H = [1, 2; 2,5]$ and let $\Sigma = [1, -\alpha; -\alpha, 1]$.
-It is easy to check then that if $\alpha=0.5$, then $f^*_1 = 0$ and additive faithfulness is violated, and if $\alpha > 0.5$, then $f^*_1$ is a concave function.
+where $H_j, \Sigma_j$ are the $j$-th rows of $H_j, \Sigma_j$, respectively. 
+\end{enumerate}
+Let $H = \begin{pmatrix}1 & 2 \\ 2 & 5\end{pmatrix}$ and let $\Sigma
+= \begin{pmatrix}1 & -\alpha \\ -\alpha & 1\end{pmatrix}$. 
+It can be checked that if if $\alpha=\frac{1}{2}$, then $f^*_1 = 0$
+and additive faithfulness is violated.  Moreover, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
 \end{example}

### 2014-07-21 tex/scam/additive_faithful.tex
edited through end of section.  important: commented out proposition 3.1, as it looks like an old version of the theorem?

@@
 \end{equation}
-where $H_j, \Sigma_j$ are the $j$-th rows of $H_j, \Sigma_j$, respectively. 
+where $H_j$ and $\Sigma_j$ are the $j$th rows of $H_j$ and $\Sigma_j$, respectively. 
 \end{enumerate}
@@
 = \begin{pmatrix}1 & -\alpha \\ -\alpha & 1\end{pmatrix}$. 
-It can be checked that if if $\alpha=\frac{1}{2}$, then $f^*_1 = 0$
+It can be checked that if $\alpha=\frac{1}{2}$, then $f^*_1 = 0$
 and additive faithfulness is violated.  Moreover, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
@@
 
-Although convex functions are additively faithful, it is difficult to estimate the optimal additive functions $f^*_k$'s (as defined in equation~\ref{eqn:unconstrained_additive}) because $f^*_k$ need not be a convex function, as example~\ref{examp:gaussian_counterexample} shows.
-$f^*_k$ can be shown to be smooth but it is preferable to use shape-constraints whenever possible to avoid the introduction of the additional smoothing bandwidth.
-
-Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model:
+Although convex functions are additively faithful---under appropriate conditions---it is difficult to
+estimate the optimal additive functions $f^*_k$s as defined in
+equation~\eqref{eqn:unconstrained_additive}.  The reason is that $f^*_k$ need not be
+a convex function, as example~\ref{examp:gaussian_counterexample}
+shows. 
+%The function $f^*_k$ can be shown to be smooth but it is preferable to use
+%shape-constraints whenever possible to avoid the introduction of the
+%additional smoothing bandwidth.
+Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model
 \begin{equation}
@@
 \{ f^*_k \}_{k=1}^p = \arg\min \Big \{ 
-    \E\big( f(X) - \sum_{k=1}^p f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
+    \E\Bigl( f(X) - \sum_{k=1}^p f_k(X_k) \Bigr)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
 \end{equation}
 where $\mathcal{C}^1$ is the set of univariate convex functions.
-
-The convex functions $f^*_k$'s are not additively faithful by themselves unfortunately. But, faithfulness can be restored by coupling the $f^*_k$'s with a set of concave functions:
+While the convex functions $\{f^*_k\}$ are not additively faithful by
+themselves, faithfulness can be restored by coupling the $f^*_k$s with a set of concave functions:
 \begin{equation}
@@
 g^*_k = \arg\min \Big\{
-   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 
+   \E\Bigl( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \Bigr)^2
     \,:\, g_k \in \mh \mathcal{C}^1, \E g_k(X_k) = 0 
-  \Big\}
+  \Big\}.
 \end{equation}
@@
 \label{thm:acdc_faithful}
-Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary points condition. Suppose that $f$ is convex and twice-differentiable.
-
-Suppose that $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$ are all continuous as functions on $C$.\\
-
-Then, $f^*_k = 0$ and $g^*_k = 0$ (as defined in equation~\ref{eqn:convex_additive} and equation~\ref{eqn:concave_postprocess}) implies that $f$ does not depend on $x_k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ with probability 1.
+Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ that
+satisfies the boundary points condition. Suppose that $f$ is convex
+and twice-differentiable, and that that $\partial_{x_k} f$,
+$\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
+$\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$ are all continuous
+as functions on $C$.  Let $f^*_k$ and $g^*_k$ be as defined in equations
+\eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}.  Then
+$f^*_k = 0$ and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x})
+= 0$ with probability one,
+so that $f$ does not depend on~$x_k$.
 \end{theorem}
 
-Theorem~\ref{thm:acdc_faithful} suggests a two-stage screening procedure for variable selection.
-We first fit a sparse \emph{convex} additive model and then, for every variable marked as irrelevant in the first stage, we allow ourself to change our mind by fitting an univariate \emph{concave} function.
-We refer to this procedure as AC/DC (additive convex / decoupled concave) and describe it in more details in section~\ref{sec:acdc}.
+This theorem naturally suggests a two-stage screening procedure for
+variable selection.  In the first stage we fit a sparse convex additive model.
+In the second stage, for every variable marked as irrelevant in the first stage,
+we fit a univariate \emph{concave} function on the residual for
+that variable. We refer to this procedure as AC/DC (additive
+convex / decoupled concave) and describe it in more detail in
+Section~\ref{sec:acdc}.
 
-\begin{proof} (of theorem~\ref{thm:acdc_faithful}) \\
-Fix $k$. Let $f^*_k, g^*_k$'s be defined as equation~\ref{eqn:convex_additive} and equation~\ref{eqn:concave_postprocess}.
+\begin{lemma}
+\label{cor:faithfulness_extension}
+Suppose $p(x)$ is a positive density on $[0,1]^p$ satisfying the boundary points condition.
+For any function $\phi(X_{-k})$ that does not depend on $X_k$,
+ \begin{align}
+f^*_k = \arg\min_{f_k} \mathbb{E} \Bigl[\bigl( f(X) 
+           - \phi(X_{-k}) - f_k(X_k) \bigr)^2\Bigr]
+\end{align}
+is given by $f^*_k(x_k) = \mathbb{E}\bigl[ f(X) - \phi(X_{-k}) \,|\, x_k\bigr]$,
+and $ f^*_k = 0$ implies that $\partial_{x_k} f(x) = 0$.
+\end{lemma}
 
-By definition of $f^*_k$ and $g^*_k$, we have that:
+\begin{proof}
+  In the proof of Theorem~\ref{thm:convex_faithful}, the only property
+  of $r(\mathbf{x}_{-k})$ we used was the fact that $\partial_{x_k}
+  r(\mathbf{x}_{-k}) = 0$. Therefore, the proof here is identical to
+  that of Theorem~\ref{thm:convex_faithful} except that we let
+  $\phi(\mathbf{x}_{-k})= r(\mathbf{x}_{-k}).$
+\end{proof}
+
+\begin{proof}[Proof of theorem~\ref{thm:acdc_faithful}]
+Fix $k$. Let $f^*_k$ and $g^*_k$'s be defined as in
+equation~\ref{eqn:convex_additive} and
+equation~\ref{eqn:concave_postprocess}.  Then
+we have that
 \begin{align*}
 f^*_k &= \arg\min_{f_k} \Big\{
-   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \big)^2 
+   \E\big( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - f_k \big)^2 
     \,:\, f_k \in  \mathcal{C}^1,\, \E f_k(X_k) = 0 
@@
 \end{align*}
-
-Therefore, $f^*_k = 0$ and $f^*_k = 0$ implies that $\E[ f(X) - \sum_{k'\neq k} f^*_{k'}(X_{k'}) \given x_k] = 0$.
-
-Now we use corollary~\ref{cor:faithfulness_extension}. We let $\phi(\mathbf{x}_{-k}) = f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that $f$ does not depend on $x_k$. 
+Therefore, $f^*_k = 0$ and $g^*_k = 0$ implies that $\E[ f(X) -
+\sum_{k'\neq k} f^*_{k'}(X_{k'}) \given x_k] = 0$.  Now we use
+Lemma~\ref{cor:faithfulness_extension} with $\phi(\mathbf{x}_{-k}) =
+f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that
+$f^*_k = 0$ and $g^*_k = 0$ together imply that $f$ does not depend on $x_k$.
 \end{proof}
 
-\begin{corollary} 
-\label{cor:faithfulness_extension}
-Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary points condition.
-
-For any function $\phi(X_{-k})$ that does not depend on $X_k$:
- \begin{align*}
-f^*_k(x_k) &= \arg\min_{f_k} \mathbb{E} \Big( f(X) 
-           - \phi(X_{-k}) - f_k(X_k) \Big)^2 
-      = \mathbb{E}\Big[ f(X) - \phi(X_{-k}) \,|\, x_k\Big] 
-\end{align*}
-We have that $ f^*_k = 0 \Rightarrow \partial_{x_k} f(x) = 0$.
-\end{corollary}
-
-\begin{proof}
-In the proof of theorem~\ref{thm:convex_faithful}, the only property of $r(\mathbf{x}_{-k})$ we used was the fact that $\partial_{x_k} r(\mathbf{x}_{-k}) = 0$.
-Therefore, the proof here is identical to that of theorem~\ref{thm:convex_faithful} except we let $\phi(\mathbf{x}_{-k})= r(\mathbf{x}_{-k}).$
-\end{proof}
-
-\begin{proposition}
-\label{prop:shape_approx_univariate}
-Let $C \subset \R^p$ be a compact set and let $h : C \rightarrow \R$.
+%%% JL:  I'm commenting out this proposition.  I don't see that it
+%% serves any particular role in the rest of the paper.  Am I missing
+%% something??
+%%
+%%\begin{proposition}
+%%\label{prop:shape_approx_univariate}
+%%Let $C \subset \R^p$ be a compact set and let $h : C \rightarrow \R$.
 Let $p(x)$ be a positive density on $C$ and suppose $\E h(X) = 0$.
@@
 Suppose that $\partial^2_{x_k} h(x) \geq 0$.
-
-Let 
-\begin{align*}
-f^*_k(x_k) &= \arg\min_{f_k} \Big\{
-   \E \Big( h(X) - f_k(X_k) \Big)^2 \,:\, f_k \in \mathcal{C}^1,\, \E f_k = 0 \Big\} \\
-g^*_k(x_k) &= \arg\min_{g_k} \Big \{
-   \E \Big( h(X) - g_k(X_k) \Big)^2 \,:\, g_k \in \mh \mathcal{C}^1 ,\, \E g_k = 0 \Big\}
-\end{align*}
-be the best convex and concave univariate approximation respectively.\\
-
-Then, $f^*_k = 0$ and $g^*_k = 0$ iff $h^*_k(x_k) \equiv \E[ h(X) \given x_k ] = 0$.
-\end{proposition}
-
-\begin{proof}
-
-First, we will establish that $h^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded.
-
-\begin{align*}
-h^*_k(x_k) &= \E[ h(X) \given x_k] \\
-  &= \int_{x_{-k}} h(x) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
-\partial^2_{x_k} h^*_k(x_k) 
-  &= \int_{\mathbf{x}_{-k}} h''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) +
-  2 h'(x) p'(\mathbf{x}_{-k} \given x_k) + h(x) p''(\mathbf{x}_{-k} \given x_k) 
-  d\mathbf{x}_{-k} 
-\end{align*}
-
-The first term $h''(x) p(\mathbf{x}_{-k} \given x_k)$ is strictly positive.
+%%
+%%
+%%Let 
+%%\begin{align*}
+%%f^*_k(x_k) &= \arg\min_{f_k} \Big\{
+%%   \E \Big( h(X) - f_k(X_k) \Big)^2 \,:\, f_k \in \mathcal{C}^1,\, \E f_k = 0 \Big\} \\
+%%g^*_k(x_k) &= \arg\min_{g_k} \Big \{
+%%   \E \Big( h(X) - g_k(X_k) \Big)^2 \,:\, g_k \in \mh \mathcal{C}^1 ,\, \E g_k = 0 \Big\}
+%%\end{align*}
+%%be the best convex and concave univariate approximation respectively.\\
+%%
+%%Then, $f^*_k = 0$ and $g^*_k = 0$ iff $h^*_k(x_k) \equiv \E[ h(X) \given x_k ] = 0$.
+%%\end{proposition}
+%%
+%%\begin{proof}
+%%
+%%
+%%First, we will establish that $h^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded. 
+%%
+%%\begin{align*}
+%%h^*_k(x_k) &= \E[ h(X) \given x_k] \\
+%%  &= \int_{x_{-k}} h(x) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
+%%\partial^2_{x_k} h^*_k(x_k) 
+%%  &= \int_{\mathbf{x}_{-k}} h''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) +
+%%  2 h'(x) p'(\mathbf{x}_{-k} \given x_k) + h(x) p''(\mathbf{x}_{-k} \given x_k) 
+%%  d\mathbf{x}_{-k} 
+%%\end{align*}
+%%
+%%The first term $h''(x) p(\mathbf{x}_{-k} \given x_k)$ is strictly positive.
 By assumption, the remaining terms are continuous and hence bounded on a compact set.
@@
 Before proceeding, we also note that because $\E h(X) = 0$, it must be that $\E h^*_k(X_k) = 0$.
-
-Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
-\begin{equation}
-\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
-\end{equation}
-Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
-we know $\mathbb{E} [ h(X) X_k^2 ] = 
-\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
-
-Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
-\begin{equation}
-\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
-       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
-\end{equation}
-Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
-            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
-        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
-\begin{align*}
-\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
-\mathbb{E}[ h(X) h^*_k(X_k) ] \\
-& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
-& = \mathbb{E} h^*_k(X_k)^2 = 0
-\end{align*}
-Therefore, $h^*_k(x_k) = 0$.
-
-\end{proof}
+%%
+%%Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
+%%\begin{equation}
+%%\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
+%%\end{equation}
+%%Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
+%%we know $\mathbb{E} [ h(X) X_k^2 ] = 
+%%\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
+%%
+%%Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
+%%\begin{equation}
+%%\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
+%%       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
+%%\end{equation}
+%%Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
+%%            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
+%%        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
+%%\begin{align*}
+%%\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
+%%\mathbb{E}[ h(X) h^*_k(X_k) ] \\
+%%& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
+%%& = \mathbb{E} h^*_k(X_k)^2 = 0
+%%\end{align*}
+%%Therefore, $h^*_k(x_k) = 0$.
+%%
+%%\end{proof}
+%%
 

### 2014-07-22 tex/scam/additive_faithful.tex
minor edits

@@
 % Let $F$ be a product distribution on $\mathbf{C}=[0,1]^s$ with density function $p$ which is positive on $\mathbf{C}$. Let
-% $X=(X_1,...,X_s) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
+% $X=(X_1,...,X_p) \sim F$. Let $f: \mathbf{C} \rightarrow \R$ be an
 % integrable function.
@@
 % \begin{equation}
-% f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ \E \bigl( f(X)  -
+% f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_p, \mu} \Bigl\{ \E \bigl( f(X)  -
 %  \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 
@@
 \begin{equation}
-f^*_1,...,f^*_s, \mu^* \coloneqq 
+f^*_1,...,f^*_p, \mu^* \coloneqq 
 \arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
@@
 \begin{proof}
-  Let $f^*_1,...,f^*_s, \mu^*$ be the minimizers as defined.  We first
+  Let $f^*_1,...,f^*_p, \mu^*$ be the minimizers as defined.  We first
   show that the optimal $\mu$ is $\mu^* = \E f(X)$ for any $f_1, ...,
@@
 \label{eqn:unconstrained_additive}
-f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
+f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_p, \mu} \Bigl\{ 
              \E \Bigl[\Bigl( f(X) - \sum_{k=1}^p f_k(X_k) -\mu \Bigr)^2 \Bigr]
@@
   \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that
-$\mu = 0$. We then assume that for all $x_k$,
+$\mu^* = E[f(X)] = 0$. We then assume that for all $x_k$,
 \begin{equation}
@@
 
-This theorem naturally suggests a two-stage screening procedure for
-variable selection.  In the first stage we fit a sparse convex additive model.
-In the second stage, for every variable marked as irrelevant in the first stage,
-we fit a univariate \emph{concave} function on the residual for
-that variable. We refer to this procedure as AC/DC (additive
-convex / decoupled concave) and describe it in more detail in
-Section~\ref{sec:acdc}.
-
 \begin{lemma}
@@
 \begin{proof}[Proof of theorem~\ref{thm:acdc_faithful}]
-Fix $k$. Let $f^*_k$ and $g^*_k$'s be defined as in
+Fix $k$. Let $f^*_k$ and $g^*_k$ be defined as in
 equation~\ref{eqn:convex_additive} and

### 2014-07-22 tex/scam/estimation.tex
redoing section as subsection of additive_faithful, expanding on algo description

@@
-\section{Estimation Procedure}
+\subsection{Estimation Procedure}
 \label{sec:acdc}
 
-Theorem~\ref{thm:acdc_faithful} suggest a two stage procedure for variable selection in convex regression--first learning a sparse convex additive model and then, on the residual, separately learning an univariate concave function for each of the dimensions.
+Theorem~\ref{thm:acdc_faithful} naturally suggests a two-stage screening procedure for
+variable selection.  In the first stage we fit a sparse convex additive model.
+In the second stage, for every variable marked as irrelevant in the first stage,
+we fit a univariate \emph{concave} function separately on the residual for
+that variable. We refer to this procedure as AC/DC (additive
+convex/decoupled concave).
 
-More precisely, given samples $(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, we perform the following procedure, which we refer to as AC/DC (additively convex / decoupled concave):
+More precisely, given samples  
+$(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, 
+we perform the following procedure, which we refer to as AC/DC (additively convex / decoupled concave):
 \begin{enumerate}
-\item Compute: 
+\item {\it AC Stage}: Estimate an additive convex model
 \begin{equation}
 \label{eqn:scam}
-\hat{f}_1, ..., \hat{f}_p = \argmin_{f_1,...,f_p \in \mathcal{C}^1} 
-   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \sum_{k=1}^p f_k(x_{ki}) \Big)^2 
-       + \lambda \sum_{k=1}^p \| f_k \|_\infty
+\hat{f}_1, ..., \hat{f}_p, \hat \mu  = \argmin_{f_1,...,f_p \in
+  \mathcal{C}^1, \mu\in\reals} 
+   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \mu - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
+       + \lambda \sum_{k=1}^p \| f_k \|_\infty.
 \end{equation}
-\item Compute, for each $k$ such that $\| \hat{f}_k \| = 0$:
+\item {\it DC Stage}: For each $k$ such that $\| \hat{f}_k \| = 0$, estimate
+  a concave function on the residual:
 \begin{equation}
@@
 \hat{g}_k = \argmin_{g_k \in \mathcal{C}^1} 
-   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \sum_{k'} \hat{f}_{k'}(x_{k'i}) 
-    - g_k(x_{ki})\Big)^2 
+   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \hat \mu - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
+    - g_k(x_{ik})\Big)^2 
+      + \lambda \| g_k \|_\infty.
+\end{equation}
+\item Output as the set of relevant variables
+$\hat S = \{ k \,:\, \| \hat{f}_k \|_\infty > 0 
+  \textrm{ or } \| \hat{g}_k \|_\infty > 0 \}$. 
+\end{enumerate}
+
+We use an $\ell_\infty/\ell_1$ penalty in equation~\eqref{eqn:scam}
+and an $\ell_\infty$ penalty in equation~\eqref{eqn:dc} to encourage
+sparsity.  Other penalties can also produce
+sparse estimates, such as a penalty on the derivative of each of the
+component functions.  The $\|\cdot\|_\infty$ norm convenient for both
+theoretical analysis and implementation.
+
+The optimization in 
+\begin{align}
+\label{eq:convreg}
+\begin{split}
+\text{minimize}_{f, \beta} & \;\; \sum_{i=1}^n (Y_i - f_i)^2 \\
+\text{subject to} & \;\; f_j \geq f_i + \beta_i^T (\x_j-\x_i),\; \text{for
+    all $i,j$}.
+\end{split}
+\end{align}
+See \cite{Boyd04}, Section 6.5.5.
+Here $f_i$ is the estimated function value $f(\x_i)$, and the vectors
+$\beta_i \in \reals^d$ represent supporting hyperplanes to the
+epigraph of $f$.  Importantly, this finite dimensional quadratic program does
+not have tuning parameters for smoothing the function.
+
+\begin{figure}[t]
+{\sc AC/DC Algorithm for Variable Selection in Convex Regression\hfill}
+\vskip5pt
+\begin{center}
+\hrule
+\vskip7pt
+\normalsize
+\begin{enumerate}
+\item[] \textit{Input}:  $(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, regularization parameter $\lambda$.
+\vskip5pt
+\item[] \textit{AC Stage}:  Estimate a sparse additive convex model:
+\begin{equation}
+\label{eqn:scam2}
+\hat{f}_1, ..., \hat{f}_p = \argmin_{f_1,...,f_p \in \mathcal{C}^1} 
+   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
+       + \lambda \sum_{k=1}^p \| f_k \|_\infty
+\end{equation}
+\vskip5pt
+\item[] \textit{DC Stage}:  Estimate decoupled concave functions
+ for each $k$ such that $\| \hat{f}_k \| = 0$:
+\begin{equation}
+\label{eqn:dc2}
+\hat{g}_k = \argmin_{g_k \in \mathcal{C}^1} 
+   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
+    - g_k(x_{ik})\Big)^2 
       + \lambda \| g_k \|_\infty
 \end{equation}
-\item Output as the set of relevant variables: 
-$\{ k \,:\, \| \hat{f}_k \|_\infty > 0 
-  \textrm{ or } \| \hat{g}_k \|_\infty > 0 \}$ 
+\item[] \textit{Output}: Component functions $\{\hat f_k\}$ and 
+relevant variables $\hat S$ where
+\begin{equation}
+\hat S^c = \bigl\{k : \| \hat{f}_k \| =
+0 \; \mathrm{and}\; \|\hat{g}_k \|=0\bigr\}.
+\end{equation}
 \end{enumerate}
-
-We added an $\ell_\infty/\ell_1$ penalty in equation~\ref{eqn:scam} and the $\ell_\infty$ penalty in equation~\ref{eqn:dc} to encourage sparsisty.
-There are other forms of penalty that can also produce sparse estimates such as a penalty on the derivative of each of the component functions; we find the form we use to be convenient both for theoretical analysis and implementation.
+\vskip3pt
+\hrule
+\end{center}
+\vskip0pt
+\caption{The AC/DC algorithm for variable selection in convex
+  regression.  The AC stage fits a sparse additive convex regression
+  model, using a quadratic program that imposes an group sparsity
+  penalty for each component function.  The DC stage fits
+  decoupled concave functions on the residuals, for each 
+  component that is zeroed out in the AC stage.}
+\label{fig:backfitting:algo}
+\end{figure}
 

### 2014-07-23 tex/scam/estimation.tex
mods to description of ac/dc algo

@@
+\def\C{\mathcal{C}}
+
 \subsection{Estimation Procedure}
@@
 $(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, 
-we perform the following procedure, which we refer to as AC/DC (additively convex / decoupled concave):
+we perform the following steps.
 \begin{enumerate}
@@
 \hat{f}_1, ..., \hat{f}_p, \hat \mu  = \argmin_{f_1,...,f_p \in
-  \mathcal{C}^1, \mu\in\reals} 
+  \C^1_0, \,\mu\in\reals} 
    \frac{1}{n} \sum_{i=1}^n \Big(y_i - \mu - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
@@
 \end{equation}
-\item {\it DC Stage}: For each $k$ such that $\| \hat{f}_k \| = 0$, estimate
+\item {\it DC Stage}: For each $k$ such that $\| \hat{f}_k \|_\infty = 0$, estimate
   a concave function on the residual:
@@
 \label{eqn:dc}
-\hat{g}_k = \argmin_{g_k \in \mathcal{C}^1} 
+\hat{g}_k = \argmin_{g_k \in \mh{}\C^1_0} 
    \frac{1}{n} \sum_{i=1}^n \Big( y_i - \hat \mu - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
@@
 sparse estimates, such as a penalty on the derivative of each of the
-component functions.  The $\|\cdot\|_\infty$ norm convenient for both
+component functions.  The $\|\cdot\|_\infty$ norm is convenient for both
 theoretical analysis and implementation.
+For identifiability, we impose the constraint $\sum_{i=1}^n f_k(x_{ik}) =
+0$ for each $k$.  The set of 1-dimensional convex (concave) functions
+satisfying this mean zero constraint is denoted $\C^1_0$ ($\mh{}\C^1_0$).
 
-The optimization in 
-\begin{align}
-\label{eq:convreg}
-\begin{split}
-\text{minimize}_{f, \beta} & \;\; \sum_{i=1}^n (Y_i - f_i)^2 \\
-\text{subject to} & \;\; f_j \geq f_i + \beta_i^T (\x_j-\x_i),\; \text{for
-    all $i,j$}.
-\end{split}
-\end{align}
-See \cite{Boyd04}, Section 6.5.5.
-Here $f_i$ is the estimated function value $f(\x_i)$, and the vectors
-$\beta_i \in \reals^d$ represent supporting hyperplanes to the
-epigraph of $f$.  Importantly, this finite dimensional quadratic program does
-not have tuning parameters for smoothing the function.
+The optimization in \eqref{eqn:scam} appears to be infinite
+dimensional, but it is equivalent to a finite dimensional quadratic
+program.  In the following section, we give the details
+of this optimization, and show how it can be reformulated
+to be more computationally efficient.
+
+%%For a simple proof of this fact, see \cite{Boyd04}, Section 6.5.5.
+%%In more detail, we first set $\hat\mu = \frac{1}{n}\sum_{i=1}^n y_i$.  
+%%For identifiability, we impose the constraint $\sum_{i=1}^n f_{ik} =
+%%0$ for each $k$, where $f_{ik} = f_k(x_{ik})$ are the function values,
+%%which are the program variables.  Then, we write the optimization as
+%%\begin{align}
+%%\label{eqn:scamqp}
+%%\min_{f, \beta} \quad
+%% &  \frac{1}{n} \sum_{i=1}^n \Big(y_i - \hat\mu - \sum_{k=1}^p f_{ik} \Big)^2 
+%%       + \lambda \sum_{k=1}^p \| f_k \|_\infty \\
+%%\nonumber
+%%\text{such that} \quad & \textrm{for all $k=1,\ldots, p$:} \\
+%% & \mathbf{1}^T f_k = 0, \; k=1,\ldots, p \\
+%% & f_{i'k} \geq f_{ik} + \beta_{ik}(x_{i'k} - x_{ik}), \; \textrm{for
+%%   all $i', i = 1,\ldots, n$}.
+%%\end{align}
+%%Likewise, the optimization in \eqref{eqn:dc} is implemented as
+%%\begin{align}
+%%\label{eqn:dcqp}
+%%\min_{g_k, \gamma_k} \quad
+%% &  \frac{1}{n} \sum_{i=1}^n \Big(y_i - \hat\mu - \sum_{k'=1}^p
+%% f_{ik'} - g_{ik}\Big)^2 
+%%       + \lambda \sum_{k=1}^p \| g_k \|_\infty \\
+%%\nonumber
+%%\text{such that} \quad &  \mathbf{1}^T g_k = 0, \\
+%% & g_{i'k} \leq g_{ik} + \gamma_{ik}(x_{i'k} - x_{ik}), \; \textrm{for
+%%   all $i', i = 1,\ldots, n$}.
+%%\end{align}
 
@@
 \label{eqn:scam2}
-\hat{f}_1, ..., \hat{f}_p = \argmin_{f_1,...,f_p \in \mathcal{C}^1} 
-   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
+\hat{f}_1, ..., \hat{f}_p, \hat\mu = \argmin_{f_1,...,f_p \in \C^1_0} 
+   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \mu-\sum_{k=1}^p f_k(x_{ik}) \Big)^2 
        + \lambda \sum_{k=1}^p \| f_k \|_\infty
@@
 \vskip5pt
-\item[] \textit{DC Stage}:  Estimate decoupled concave functions
- for each $k$ such that $\| \hat{f}_k \| = 0$:
+\item[] \textit{DC Stage}:  Estimate concave functions
+ for each $k$ such that $\| \hat{f}_k \|_\infty = 0$:
 \begin{equation}
 \label{eqn:dc2}
-\hat{g}_k = \argmin_{g_k \in \mathcal{C}^1} 
-   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
+\hat{g}_k = \argmin_{g_k \in \mh{}\C^1_0} 
+   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \hat \mu - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
     - g_k(x_{ik})\Big)^2 

### 2014-07-23 tex/scam/additive_faithful.tex
scriptstyle

@@
 We let $p'(\mathbf{x}_{-k} \given x_k)$ denote 
-$\frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k}$ and 
+$\frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}$ and 
 $p''(\mathbf{x}_{-k} \given x_k)$ denote 
-$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and
+$\frac{\partial^2 p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k^2}$ and
 likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k,

### 2014-07-24 tex/scam/optimization.tex
minor edits

@@
+\def\uds#1{#1}
+
 \section{Optimization}
+\label{sec:optimization}
 
-We describe in detail the optimization algorithm for the additive convex regression stage, the second decoupled concave regression stage follows almost identical procedure.
+We now describe in detail the optimization algorithm for the additive
+convex regression stage.  The second decoupled concave regression stage
+follows a very similar procedure.
 
-We let $\bds{x}_{i}\in\mathbb{R}^{p}$ be the covariate, $Y_{i}$ be the
-response and $\epsilon_{i}$ be the mean zero noise. The regression function $f(\cdot)$ we estimate is the summation of 
+Let $\bds{x}_{i}\in\mathbb{R}^{p}$ be the covariate, let $y_{i}$ be the
+response and let $\epsilon_{i}$ be the mean zero noise. The regression function $f(\cdot)$ we estimate is the summation of 
 functions $f_{k}(\cdot)$ in each variable dimension and a scalar offset $\mu$.  
@@
 \begin{equation}\label{hyper}
-      f_{kj} \geq f_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
+      f_{i'k} \geq f_{ik} + \beta_{ik}(x_{i'k}-x_{ik}) \quad
+      \textrm{for all $i,i' = 1,\ldots, n$,}
 \end{equation}
-where $f_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
-subgradient at point $x_{ki}$. We apparently need $O(n^2 p)$ constraints to
-impose the supporting hyperplane constraints, which is computationally
-expensive for large scale problems.  In fact, only $O(np)$
+where $f_{ik}\coloneqq f_{k}(x_{ik})$ and $\beta_{ik}$ is the
+subgradient at point $x_{ik}$. We apparently need $O(n^2 p)$ constraints to
+impose the supporting hyperplane constraints.
+In fact, only $O(np)$
 constraints suffice, since univariate convex functions are
 characterized by the condition that the subgradient, which is a scalar, must
-increase monotonically. This observation leads to our optimization
-program:
+increase monotonically. This observation leads to the  optimization
 \begin{equation}
 \begin{split}
-       \min_{\bds{h},\bds{\beta},\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
-                     \Bigl( Y_{i}-\sum_{k=1}^{p}f_{ki} - \mu \Bigr)^{2} 
-                         + \lambda\sum_{k=1}^{p}\|\bds{f}_{k\cdot}\|_{\infty} \\
-       \textrm{subject to} &\;\; f_{k(i+1)} = f_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \\
-                     & \;\; \sum_{i=1}^{n}f_{ki}=0,\\
-                     & \;\; \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
+       \min_{f,\beta,\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
+                     \Bigl( y_{i}-\mu - \sum_{k=1}^{p}f_{ik}\Bigr)^{2} 
+                         + \lambda\sum_{k=1}^{p}\|f_k\|_{\infty} \\
+       \textrm{subject to} &\;\; \textrm{for all $k=1,\ldots, p$:}\\
+       & \;\; f_{(i+1)_k k} = f_{(i)_k k} +
+       \beta_{(i)_k k}(x_{(i+1)_k k}-x_{(i)_k k}),\;\textrm{for $i=1,\ldots, n-1$}\\
+       & \;\; \sum_{i=1}^{n}f_{ik}=0,\\
+       & \;\; \beta_{(i+1)_k k} \geq \beta_{(i)_k k}\;\textrm{for $i=1,\ldots, n-1$}.
 \end{split}
@@
 \end{equation}
-Here $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.
+Here $f_k$ denotes the vector $f_k = (f_{1k}, f_{2_k}\ldots, f_{nk})^T\in\reals^n$
+and $\{(1)_k,(2)_k,\ldots,(n)_k\}$ is a reordering of $\{1,2,\ldots,n\}$
+such that 
+\begin{equation}
+x_{(1)_k k} \leq{} x_{(2)_k k} \leq \cdots \leq{} x_{(n)_k k}.
+\end{equation}
 
-We can solve for $\mu$ explicitly, as  
-$\mu = \frac{1}{n} \sum_{i=1}^n Y_i = \bar{Y}$ which follows from the
+We can solve for $\mu$ explicitly as  
+$\mu = \frac{1}{n} \sum_{i=1}^n y_i = \bar{y}$.  This follows from the
 KKT conditions
 and the constraints $\sum_i f_{ki} = 0$.
-It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
-\begin{align*}
-  \forall & j\geq i, \; f_{k(j)}-f_{k(i)}  = \sum\limits_{t=i}^{j-1}(f_{k(t+1)}-f_{k(t)}) \\
-   &= \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})
-   \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) 
-  = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
-  \forall & j<i,\;  f_{k(j)}-f_{k(i)} =
+It is easy to verify that the constraints in (\ref{np}) satisfy the
+supporting hyperplane constraints, since
+for all $j > i$
+\begin{align}
+  f_{(j)_kk}-f_{(i)_kk}  & = \sum\limits_{t=i}^{j-1}(f_{(t+1)_kk}-f_{(t)_kk}) \\
+   &= \sum\limits_{t=i}^{j-1}\beta_{(t)_kk}(x_{(t+1)_kk}-x_{(t)_kk}) \\
+   &\geq \beta_{(i)_kk}\sum\limits_{t=i}^{j-1}(x_{(t+1)_kk}-x_{(t)_kk}) \\
+  & = \beta_{(i)_kk}(x_{(j)_kk}-x_{(i)_kk}) 
+\end{align}
+and for all $j < i$
+\begin{align}
+f_{k(j)}-f_{k(i)} & =
     \sum\limits_{t=j}^{i-1}(f_{k(t)}-f_{k(t+1)}) \\
-     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) 
-     \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
-\end{align*}
+     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\
+     &\geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) \\
+     & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
+\end{align}
 
@@
 
-The sparse convex additive model optimization in (\ref{np}) is a quadratic program (QP) with
+The sparse convex additive model optimization in (\ref{np}) is a quadratic program with
 $O(np)$ variables and $O(np)$ constraints. 
-Directly applying a QP solver for $\bds{h},
-\bds{\beta}$ would be computationally expensive for relatively large
+Directly applying a QP solver for $f$ and $\beta$
+would be computationally expensive for relatively large
 $n$ and $p$. However, notice that variables in different feature
 dimensions are only coupled in the term
-$(Y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block
+$(Y_{i}-\mu - \sum_{k=1}^{p}f_{ik})^{2}$. Hence, we can apply the block
 coordinate descent method, where in each step we solve the following
-QP subproblem for $\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the
-other variables fixed. We present the one-block optimization in matrix notation:
+QP subproblem for $\{f_k, \beta_k\}$ with the
+other variables fixed. In matrix notation, the optimization is
 \begin{align}
-\min_{ \bds{f}_k, \bds{\beta}_k, \gamma_k}& \frac{1}{2n} \| \bds{r}_{\mh k} - \bds{f}_k \|_2^2 
+\begin{split}
+\min_{ f_k, \beta_k, \gamma_k} \;\;& \frac{1}{2n} \| \uds{r}_k - \uds{f}_k \|_2^2 
      + \lambda \gamma_k \label{opt:1d_compact} \\
- \textrm{s.t. } & P \bds{f}_k = \diag(P \bds{x}_k)  \bds{\beta}_k \nonumber \\
-   & D \bds{\beta}_k \leq 0 ,
-   \quad -\gamma_k \mathbf{1}_n \leq \bds{f}_k \leq \gamma_k \mathbf{1}_n,
-   \quad \mathbf{1}_n^\tran \bds{f}_k = 0 \nonumber
+ \textrm{such that } & P \uds{f}_k = \diag(P \bds{x}_k)  \uds{\beta}_k \\
+   & D \uds{\beta}_k \leq 0 \\
+   & -\gamma_k \mathbf{1}_n \leq \uds{f}_k \leq \gamma_k \mathbf{1}_n   \\
+   & \mathbf{1}_n^\tran \uds{f}_k = 0 
+\end{split}
 \end{align}
-
-where $\bds{f}_k \in \R^n$ and equals $(f_{k1}, ..., f_{kn})$, $\bds{\beta}_k \in \R^{n-1}$ and equals $(\beta_{k1}, ..., \beta_{k(n-1)})$.
-$\bds{r}_{\mh k} \in \R^n$ is the residual vector: $\bds{r}_{\mh k}(i) = Y_i - \bar{Y} - \sum_{k' \neq k} f_{k' i}$.
-$\bds{x}_k \in \R^n$ and equals $(x_{k1}, ..., x_{kn})$.
-\\
-
-$P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i'$-th row $P_{i' \cdot}$ is all zero except $-1$ at the $(i')$-th smallest coordinate of $\bds{x}_k$ and $1$ at the $(i'+1)$-th smallest coordinate of $\bds{x}_k$.
-$D \in \R^{(n-2) \times (n-1)}$ is another permutation matrix where the $i'$-th row is all zero except $1$ at position $i'$ and $-1$ at position $i'+1$.
-$\diag( v )$ for a vector $v$ is a diagonal matrix whose diagonal entries are $v$.
+where $\uds{\beta}_k \in \R^{n-1}$ is the vector $\uds{\beta}_k =
+(\beta_{1k}, \ldots, \beta_{(n-1)k})^T$, and
+$\uds{r}_{k} \in \R^n$ is the residual vector $\uds{r}_{k} = (y_i -
+\hat\mu - \sum_{k' \neq k} f_{ik'})^T$.
+In addition, 
+$P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i$-th
+row  is all zero except $-1$ at in position $(i)_k$ and $1$ in
+position $(i+1)_k$, and $D \in \R^{(n-2) \times (n-1)}$ is another
+permutation matrix  where the $i$-th row is all zero except for a $1$ 
+at position $i$ and $-1$ at position $i+1$.  We denote by
+$\diag( v )$ the diagonal matrix whose diagonal entries are $v$.
 

### 2014-07-24 tex/scam/appendix.tex
bracketing number results

@@
 \end{align*}
-where the difference is a term that decreases with $n$.
+where the estimation error is a term that decreases with $n$.
 
@@
 \label{thm:convex_consistent}
-Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sLb\sqrt{ \frac{1}{n} \log^2 np}$.
+Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sB \sqrt{ \frac{1}{n} \log^2 np}$.
 
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq c (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
+&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
 \end{align}
@@
 
-The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4Lb$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.
+The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.
 
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b 
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B 
 \end{align*}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + c(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}
 \end{align}
 
-[TOOD: at this point, we still have to choose a value for $\lambda$]\\
+%[TOOD: at this point, we still have to choose a value for $\lambda$]\\
 
@@
 
-\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with theorem~\ref{thm:chaining}.\\
+\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with bracketing entropy.
 
-Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_L\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
+Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
+
+By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_2(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
+
+By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h^U, h^L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
+$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
+)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.
+
+For each $h \in \mathcal{G}$, there exists a pair $(h_U, h_L)$ such that $h_U(X_i) - h_L(X_i) \geq h(X_i) - h_L(X_i) \geq 0$.
+Therefore, with probability at least $1-\delta$, uniformly for all $h \in \mathcal{G}$:
+
+$$
+\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
+$$.
+
+We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
+Therefore,  
+\[
+|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
+  \sigma \sqrt{\log \frac{n}{\delta}} \left( \epsilon + \epsilon_{n,\delta} \right)
+\]
+For the last inequality, we used the fact that $w$ is a vector of independent subgaussian($\sigma$) random variables and hence, by union bound, with probability at least $1-\delta$, $\| w \|_\infty \leq \sigma \sqrt{\log \frac{n}{\delta}}$.
+
+By another property of subgaussian random variables, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{1}{cn} \log \frac{1}{\delta} }$.
+Applying an union bound, we have that
+$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{\log N_{[]}}{n} \log \frac{1}{\delta}}$.
+
+Putting this together, we have that
+\begin{align*}
+|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
+|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
+     | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log 1/\delta}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
+   \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
+   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
+   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
+\end{align*}
+
+The two terms are balanced when one sets $\epsilon = \sqrt{ \frac{((sB)^2 s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.
+
+This is only valid if $n$ is large enough so that $\epsilon \in (0, sB \epsilon_3]$.
+
+We upper bound some terms to simplify the presentations again and end up with the following result:
+
+\[
+|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
+   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+\]
 
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
-   + \lambda 4 s L b + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
+   &\leq c sB \sigma \sqrt{ 
+   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+   + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
-   + \lambda 4 s L b    \label{eqn:second_step_inequality}
+   &\leq sB \sigma \sqrt{ 
+   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+   + \lambda 4 s B \nonumber\\   
+   &\leq cB \sigma 
+    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log \frac{C}{\delta}} + \lambda 4 sB
+\label{eqn:second_step_inequality}
 \end{align}
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
- +\lambda 4 s L b + c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+   &\leq cB^2 \sigma 
+    \sqrt{ \frac{s^5 (b c_u)^{2/5}}{n^{4/5}} \log \frac{C}{\delta}}
+ +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
+&\leq c B^3 \sigma \sqrt{ \frac{s^5(bc_u)^{2/5}}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sB
 \end{align}
 
-Substituting in $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
+Substituting in $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
 
@@
 \begin{proof}
-The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same covering number.
+The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
 
@@
 
-Using the chaining result (theorem~\ref{thm:chaining}), setting $s=1$, we have, with probability at least $1-\delta$,
+Using identical analysis as Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
+  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 Lb
 \end{align*}
@@
 \sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
-   c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+   c B^2 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
 \end{align*}
@@
 \begin{proof}
-Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_L - f_0$.
-Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s b L$.\\
+Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$.
+Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.\\
 
-By Corollary~\ref{cor:convexbracket_ln}, there exists a bracketing $\mathcal{G}_\epsilon$ of $\mathcal{G}$ which has sized bounded by [TODO:...], which is an $\epsilon$-bracketing with respect to the $L_2(P)$ norm, and which is also an $(\epsilon + \epsilon_{n,\delta})$-bracketing with respect to the $L_n$ norm with probability at least $1-\delta$.
+There exists an $\epsilon$-bracketing of $\mathcal{G}$.
 
-For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$.
+%For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$.
+
+By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
+By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\| h_U - h_L \|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{2 \epsilon^{1/2} n}}$.
+
+For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
+\[
+\psi_L^2 \leq h^2 \leq \psi_U^2
+\]
+
+We can then bound the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$.
+\begin{align*}
+\int (\psi_U^2(x) - \psi_L^2(x)) p(x)dx  &\leq  \int | h_U^2(x) - h_L^2(x)| p(x) dx \\
+   &\leq \int | h_U(x) - h_L(x) | \, |h_U(x) + h_L(x)| p(x) dx \\
+   &\leq 2sB \epsilon
+\end{align*}
+
+% And, with probability at least $1-\delta$, for all $\psi_U, \psi_L$:
+% \begin{align*}
+% \frac{1}{n} \sum_{i=1}^n ( \psi_U^2(X_i) - \psi_L^2(X_i)) &\leq 
+%          \frac{1}{n} \sum_{i=1}^n | h_U^2(X_i) - h_L^2(X_i)| \\
+%   &\leq \frac{1}{n}\sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \, |h_U(X_i) + h_L(X_i)| \\
+%   &\leq 2sB(\epsilon + \epsilon_{n,\delta})
+% \end{align*}
+
+Now we can bound $\| h \|_n^2 - \| h \|_P^2$.
+
+\begin{align}
+\frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - \E \psi_U(X)^2  \leq
+    \| h \|_n^2 - \| h \|_P^2 \leq
+  \frac{1}{n} \sum_{i=1}^n \psi_U(X_i)^2 - \E \psi_L(X)^2  \label{eqn:hpsi_bound}
+\end{align}
+
+$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$.
+By uniform convergence, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
+\[
+\left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
+   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+\]
+
+Plugging this into equation~\ref{eqn:hpsi_bound} above, we have that:
+\begin{align*}
+& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \\
+ & \leq 
+ \| h \|_n^2 - \| h \|_P^2 \leq
+\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+\end{align*}
+
+Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have:
+\begin{align*}
+-sB\epsilon - 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \leq 
+ \| h \|_n^2 - \| h \|_P^2 \leq
+sB\epsilon + 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+\end{align*}
+
+We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.
+
+We have then that, with probability at least $1-\delta$,
+\begin{align*}
+\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
+  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{1}{\delta}}{n^{4/5}}}
+\end{align*}
+
+%For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$.
 It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\
 
-Because $\| h \|_n = \| h - h_\epsilon + h_\epsilon \|_n$, we have that
-\begin{align*}
-\|h_\epsilon \|_n - \| h - h_\epsilon \|_n &\leq 
-    \| h \|_n \leq \|h_\epsilon \|_n + \| h - h_\epsilon \|_n \\
-\|h_\epsilon \|_n - \epsilon &\leq 
-    \| h \|_n \leq \|h_\epsilon \|_n + \epsilon  \\
-\| h_\epsilon \|^2_n - 8 \epsilon (s L b)  &\leq \| h  \|^2_n  \leq
-   \| h_\epsilon \|_n^2 + 8 \epsilon (s L b) 
-\end{align*}
-where we used the fact that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$ and $ \| h_\epsilon \|_n \leq \| h_\epsilon \|_\infty \leq 4 s L b$.
+% Because $\| h \|_n = \| h - h^L + h^L \|_n$, we have that
+% \begin{align*}
+% \|h^L \|_n - \| h - h^L \|_n &\leq 
+%     \| h \|_n \leq \|h^L \|_n + \| h - h^L \|_n \\
+% \|h^L \|_n - \epsilon - \epsilon_{n,\delta} &\leq 
+%     \| h \|_n \leq \|h^L \|_n + \epsilon + \epsilon_{n,\delta}  \\
+% \| h^L \|^2_n - 8 \epsilon (sB)  &\leq \| h  \|^2_n  \leq
+%    \| h^L \|_n^2 + 8 \epsilon (sB) 
+% \end{align*}
+% where we used the fact that $\| h - h^L \|_n \leq \| h - h^L \|_\infty \leq \epsilon$ and $ \| h^L \|_n \leq \| h^L \|_\infty \leq 4 s L b$.
 
-And likewise:
-\begin{align*}
-\| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
-   \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
-\end{align*}
+% And likewise:
+% \begin{align*}
+% \| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
+%    \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
+% \end{align*}
 
-Therefore, 
-\begin{align*}
-\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
-\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
-        + \epsilon (16 sLb)
-\end{align*}
+% Therefore, 
+% \begin{align*}
+% \sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
+% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+%         + \epsilon (16 sLb)
+% \end{align*}
 
-Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
-\begin{align*}
-\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
-  (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
-        + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
-&\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
-        + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
-\end{align*}
+% Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
+% \begin{align*}
+% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+%   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+%         + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
+% &\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+%         + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
+% \end{align*}
 
-We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
-Therefore:
-\begin{align*}
-\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
-   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
-        + s n^{1/5}  \big) } \\
-  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
-\end{align*}
-And
-\begin{align*}
-\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
-\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
-        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
-  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
-     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
-  &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
-\end{align*}
+% We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
+% Therefore:
+% \begin{align*}
+% \sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
+%    (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
+%         + s n^{1/5}  \big) } \\
+%   &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
+% \end{align*}
+% And
+% \begin{align*}
+% \sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
+% \sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
+%         + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
+%   &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
+%      + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
+%   &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+% \end{align*}
 
@@
 Let $\mathcal{C}$ be a set of functions.
-For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f^L, f^U) \}$ satisfying (1) $\rho( f^L, f^U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f^L, f^U)$ where $f^U \geq f \geq f^L$.
+For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f^U \geq f \geq f^L$.
 
@@
 
-It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for a distribution $P$ with an uniformly upper bounded density.
+It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for an absolutely continuous distribution $P$.
+
+\begin{proposition}
+\label{prop:convexbracket_lp}
+Let $P$ be a distribution with a density $p$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
+\[
+\log N_{[]} (2\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
+\]
+For all $\epsilon \in (0, B\epsilon_3]$.
+\end{proposition}
+
+\begin{proof}
+Let $\mathcal{C}_\epsilon$ be the bracketing the satisfies the size bound in Proposition~\ref{prop:convexbracket_lp}.
+
+Let $(f_L, f_U) \in \mathcal{C}_\epsilon$. Then we have that:
+\begin{align*}
+\| f_L - f_U \|_{L_1(P)} &= \int | f_L(x) - f_U(x)| p(x) dx \\
+   &\leq \left( \int | f_L(x) - f_U(x) |^2 dx \right)^{1/2}
+      \left( \int p(x)^2 dx \right)^{1/2} \\
+  &\leq \left( \int | f_L(x) - f_U(x)|^2 dx \right)^{1/2}\\
+ &\leq \| f_L - f_U \|_{L_2} \leq \epsilon
+\end{align*}
+On the third line, we used the fact that $\int p(x)^2 dx \leq \left( \int p(x) dx \right)^2 \leq 1$.
+\end{proof}
+
+It is also simple to extend the bracketing number result to additive convex functions. As before, let $\mathcal{C}^s$ be the set of additive convex functions with $s$ components.
 
 \begin{corollary}
-\label{cor:convexbracket_lp}
-Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
+\label{cor:convexadditive_lp}
+Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
 \[
-\log N_{[]} (2\epsilon, \mathcal{C}, L_2(P)) \leq K^{**} \left( \frac{2bB c_u}{\epsilon} \right)^{d/2}
+\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**} 
+    \left( \frac{2sbB}{\epsilon} \right)^{1/2}
 \]
+For all $\epsilon \in (0, s B \epsilon_3]$.
 \end{corollary}
 
-Given samples $X_1,..., X_n \in \R^p$, we define $L_n$-norm as $\| f \|^2_n \equiv \frac{1}{n}\sum_{i=1}^n f(X_i)^2$.
-The following result follows from Corollary~\ref{cor:convexbracket_lp} directly by an union bound.
+\begin{proof}
+Let $f \in \mathcal{C}^s$. We can construct an $\epsilon$-bracketing for $f$ through $\epsilon/s$-bracketings for each of the components $\{ f_k \}_{k=1,...,s}$:
+\[f_U = \sum_{k=1}^s f_{Uk}  \qquad f_L = \sum_{k=1}^s f_{Lk} \]
+It is clear that $f_U \geq f \geq f_L$. It is also clear that $\| f_U - f_L \|_{L_1(P)} \leq \sum_{k=1}^s \| f_{Uk} - f_{Lk} \|_{L_1(P)} \leq \epsilon$.
+\end{proof}
+
+The following result follows from Corollary~\ref{prop:convexbracket_lp} directly by an union bound.
 
@@
 Let $1 > \delta > 0$.
-Let $\mathcal{C}_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}$ with respect to the $L_2(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}, L_2(P))$.
-\\
+Let $\mathcal{C}^s_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}^s$ with respect to the $L_1(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}^s, L_1(P))$.
+Let $\epsilon \in (0, s B \epsilon_3]$.
 
-Then, with probability at least $1-\delta$, for all pairs $(f^L, f^U) \in \mathcal{C}_\epsilon$, $\frac{1}{n} \sum_{i=1}^n ( f^L(X_i) - f^U(X_i)^2 \leq \epsilon + \epsilon_{n, \delta}$, where 
+Then, with probability at least $1-\delta$, for all pairs $(f_L, f_U) \in \mathcal{C}^s_\epsilon$, we have that
+
+\begin{align*}
+\frac{1}{n} \sum_{i=1}^n |f_L(X_i) - f_U(X_i)| &\leq \epsilon + \epsilon_{n, \delta}
+\end{align*}
+
+where 
 $\epsilon_{n,\delta} \equiv 
-B^2 \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
-B^2 \sqrt{ \frac{K^{**} (2bBc_u)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
+sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
+sB \sqrt{ \frac{sK^{**} (2sbB)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
 \end{corollary}
@@
 \begin{proof}
-$(f^L(X_i) - f^U(X_i))^2$ is at most $B^2$.
-There are $N_{[]}(2\epsilon, \mathcal{C}, L_2(P))$ pairs $(f^L, f^U)$.
-The corollary follows from a direct application of union bound and Hoeffding Inequality.
+$|f_L(X_i) - f_U(X_i)|$ is at most $sB$.
+There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$.
+The inequality follows from a direct application of union bound and Hoeffding Inequality.\\
 \end{proof}
-
 % \subsubsection{Covering Number for Lipschitz Convex Functions}

### 2014-07-25 tex/scam/optimization.tex
edits on qp formulation

@@
 where $f_{ik}\coloneqq f_{k}(x_{ik})$ and $\beta_{ik}$ is the
-subgradient at point $x_{ik}$. We apparently need $O(n^2 p)$ constraints to
+subgradient at point $x_{ik}$. This apparently requires $O(n^2 p)$ constraints to
 impose the supporting hyperplane constraints.
@@
 Here $f_k$ denotes the vector $f_k = (f_{1k}, f_{2_k}\ldots, f_{nk})^T\in\reals^n$
-and $\{(1)_k,(2)_k,\ldots,(n)_k\}$ is a reordering of $\{1,2,\ldots,n\}$
-such that 
+and $\{(1)_k,(2)_k,\ldots,(n)_k\}$ are the indices in the sorted ordering
+of the values of coordinate $k$:
 \begin{equation}
@@
 Directly applying a QP solver for $f$ and $\beta$
-would be computationally expensive for relatively large
+is computationally expensive for relatively large
 $n$ and $p$. However, notice that variables in different feature
-dimensions are only coupled in the term
-$(Y_{i}-\mu - \sum_{k=1}^{p}f_{ik})^{2}$. Hence, we can apply the block
+dimensions are only coupled in the squared error term
+$(y_{i}-\mu - \sum_{k=1}^{p}f_{ik})^{2}$. Hence, we can apply the block
 coordinate descent method, where in each step we solve the following
@@
 $P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i$-th
-row  is all zero except $-1$ at in position $(i)_k$ and $1$ in
+row  is all zeros except for a $-1$ in position $(i)_k$ and a $1$ in
 position $(i+1)_k$, and $D \in \R^{(n-2) \times (n-1)}$ is another
-permutation matrix  where the $i$-th row is all zero except for a $1$ 
-at position $i$ and $-1$ at position $i+1$.  We denote by
-$\diag( v )$ the diagonal matrix whose diagonal entries are $v$.
+permutation matrix  where the $i$-th row is all zeros except for a $1$ 
+in position $i$ and a $-1$ in position $i+1$.  We denote by
+$\diag( v )$ the diagonal matrix with diagonal entries $v$.
+The extra variable $\gamma_{k}$ is introduced to impose the
+regularization penalty involving the $\ell_{\infty}$ norm.
 
@@
 % \end{equation}
-The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
-which can be solved efficiently using optimization packages (e.g., MOSEK: \verb+http://www.mosek.com/+).
-We cycle through all feature dimensions ($k$) from $1$ to $p$ multiple times until convergence.
-Empirically, we observe that the algorithm converges in only a few cycles. We also implemented an ADMM solver for (\ref{np}), but found that it is not as efficient as this QP solver.
 
-After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
+This QP
+subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse
+structure, which can be solved efficiently using optimization
+packages. In our experiments we use {\sc mosek} (\href{http://www.mosek.com/}{www.mosek.com}).  We cycle through
+all covariates $k$ from $1$ to $p$ multiple times until convergence.
+Empirically, we observe that the algorithm converges in only a few
+cycles. We also implemented an ADMM solver for (\ref{np})
+\citep{Boyd:admm}, but found
+that it is not as efficient as this QP solver.
+
+After optimization, the function estimates for an input vector $\bds{x}$ is, according to (\ref{hyper}),
 \begin{equation}
 \begin{split}
-\nonumber
-      f(\bds{x}_j) & = \sum_{k=1}^{p}f_k(x_{kj})+\mu 
-= \sum_{k=1}^{p}\max_{i} \{f_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} +
-      \mu.
+      \hat f(\bds{x}) & = \sum_{k=1}^{p} \hat f_k(x_{j})+ \hat \mu 
+= \sum_{k=1}^{p}\max_{i} \bigl\{\hat f_{ik}+ \hat \beta_{ik}(x_{k}-x_{ik})\bigr\} +
+      \hat \mu.
 \end{split}
@@
 
-The univariate concave function estimation is a straightforward modification of optimization~\ref{opt:1d_compact}.
-We need only modify one linear inequality constraint to enforce that the subgradients must be non-increasing: $\beta_{k(i+1)} \leq \beta_{k(i)}$.
+The univariate concave function estimation is a straightforward
+modification of optimization~\ref{opt:1d_compact}. It is only
+necessary to modify the linear inequality constraints so that the subgradients are
+non-increasing: $\beta_{(i+1)_kk} \leq \beta_{(i)_kk}$.
 

### 2014-07-31 tex/scam/appendix.tex
results update

@@
 \label{thm:convex_consistent}
-Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sB \sqrt{ \frac{1}{n} \log^2 np}$.
+Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq sB \sqrt{ \frac{1}{n} \log^2 np}$.
+
+Suppose $n \geq c_1 \max(\sqrt{sB}, B)$ and $B, \sigma \geq c_2$ for some constant $c_1, c_2$.
 
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
+&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
 \end{align}
+Where $c, C$ are constants, dependent on $c_1, c_2$.
 
@@
 
-The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.
+The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$.
 
@@
 
-By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_2(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
-
-By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h^U, h^L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
+By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
+
+By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
 $\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
@@
 $$
-\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
+\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
 $$.
-
-We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
+Where we assumed that condition~\ref{cond:simplify_covering_number} holds.
+
+We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
 Therefore,  
@@
      | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log 1/\delta}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
+   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log \frac{1}{\delta}}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
    \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
-   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
-   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
-\end{align*}
-
-The two terms are balanced when one sets $\epsilon = \sqrt{ \frac{((sB)^2 s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.
+   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
+   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
+   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{n}{\delta}}{cn \epsilon^{1/2}}} \\
+\end{align*}
+
+The two terms are balanced when one sets $\epsilon = sB \sqrt{ \frac{(s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.
 
@@
 
+Also, to ensure that conditions~\ref{cond:simplify_covering_number} hold, we need that $\log n \geq 2$ and $n \geq c B$ where $c$ is some constant dependent only on $K^{**}$ and $b$.
+
 We upper bound some terms to simplify the presentations again and end up with the following result:
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{c n^{4/5}}}
 \]
@@
    &\leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{n^{4/5}}}
    + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
+   &\leq c sB \sigma \sqrt{ 
+   \frac{s b^{1/2} \log^2 \frac{nC}{\delta}}{n^{4/5}}}
    + \lambda 4 s B \nonumber\\   
-   &\leq cB \sigma 
-    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log \frac{C}{\delta}} + \lambda 4 sB
+   &\leq c B \sigma 
+    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log^2 \frac{n}{\delta}} + \lambda 4 sB
 \label{eqn:second_step_inequality}
@@
    &\leq cB^2 \sigma 
-    \sqrt{ \frac{s^5 (b c_u)^{2/5}}{n^{4/5}} \log \frac{C}{\delta}}
+    \sqrt{ \frac{s^3 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
  +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^3 \sigma \sqrt{ \frac{s^5(bc_u)^{2/5}}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sB
+&\leq c B^3 \sigma \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 4 sB \nonumber
 \end{align}
+Where for the second inequality, we used the assumption that there is some large constant $c$ such that $B \geq \frac{\sigma}{c\sigma + 1}$.
 
@@
 \label{thm:concave_consistent}
-Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$.\\
-
-Suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\
+Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$.\\
+
+Suppose $n$ is large enough such that $B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\
 
@@
    \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
-\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2 Lb \\
+\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2B \\
  &\\
 \| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
-   +\lambda 2 Lb \\
+   +\lambda 2 B \\
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
-   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2Lb
+   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2B
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 Lb
+  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 B
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
-  c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
+  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
+  c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
  &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
+\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
     2Lb \sqrt{\frac{1}{n} \log^2 np}\\
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
+\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
 \end{align*}
@@
    + 2 \langle f_0 - f^*, g^*_k \rangle \\
- &\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
+ &\leq c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
     2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
- &\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+ &\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
     2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
-&\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
-   c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+&\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+   c B \sqrt{B^3\sigma \sqrt{ 
                    \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
-&\leq  c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
+&\leq  cB \sqrt{B^3\sigma \sqrt{ 
                    \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
@@
 \| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
-   c (Lb)^{2.5} \sigma^{0.5} 
+   c B^{2.5} \sigma^{0.5} 
      \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
@@
 \end{align*}
-
 \end{lemma}
@@
 By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
-By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\| h_U - h_L \|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{2 \epsilon^{1/2} n}}$.
+By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
 
@@
 $\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$.
-By uniform convergence, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
+By Hoeffding's inequality and union bound, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
 \[
 \left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
-   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
 \]
@@
 & \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \\
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
  & \leq 
@@
 \E \psi_U(X)^2 - \E \psi_L(X)^2 + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
 \end{align*}
@@
 -sB\epsilon - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \leq 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
  \| h \|_n^2 - \| h \|_P^2 \leq
 sB\epsilon + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
 \end{align*}
@@
 \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
-  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{1}{\delta}}{n^{4/5}}}
+  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
 \end{align*}
@@
 \begin{align*}
-| \bar{f}^* | | \bar{f}_0 | &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
-\bar{f}^{*2} &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+| \bar{f}^* | | \bar{f}_0 | &\leq c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \\
+\bar{f}^{*2} &\leq c (sB)^2 \frac{1}{n} \log \frac{2}{\delta}
 \end{align*}
@@
 \[
-\|f_0 - f^*\|_n^2 - c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
+\|f_0 - f^*\|_n^2 - c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
     \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
-\|f_0 - f^*\|_n^2 + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
+\|f_0 - f^*\|_n^2 + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta}
 \]
@@
 $\epsilon_{n,\delta} \equiv 
-sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
-sB \sqrt{ \frac{sK^{**} (2sbB)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
+sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} 
+= \sqrt{ \frac{ sK^{**}(sBb)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}$
 \end{corollary}
@@
 \end{proof}
+
+To make the expression in this corollary easier to work with, we derive an upper bound for $\epsilon_{n, \delta}$. Suppose 
+\begin{align}
+\epsilon^{1/2} \leq 2sK^{**} (sBb)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2. \label{cond:simplify_covering_number}
+\end{align}
+
+Then we have that
+\begin{align*}
+\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}
+\end{align*}
+
 % \subsubsection{Covering Number for Lipschitz Convex Functions}
@@
 %%% mode:latex ***
-%%% TeX-master: "paper.tex" ***
+%%% TeX-master: "faithful.tex" ***
 %%% End: ***

### 2014-07-31 tex/scam/paper.tex
results update

@@
 % ENVIRONMENTS
-\numberwithin{equation}{section}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheoremstyle{remark}{\topsep}{\topsep}%
-     {\normalfont}% Body font
-     {}           % Indent amount (empty = no indent, \parindent = para indent)
-     {\bfseries}  % Thm head font
-     {.}          % Punctuation after thm head
-     {.5em}       % Space after thm head (\newline = linebreak)
-     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{assumption}{Assumption}[section]
-\newtheorem{definition}{Definition}[section]
+% \numberwithin{equation}{section}
+% \theoremstyle{plain}
+% \newtheorem{theorem}{Theorem}[section]
+% \newtheorem{corollary}{Corollary}[section]
+% \newtheorem{proposition}{Proposition}[section]
+% \newtheorem{lemma}{Lemma}[section]
+% \newtheoremstyle{remark}{\topsep}{\topsep}%
+%      {\normalfont}% Body font
+%      {}           % Indent amount (empty = no indent, \parindent = para indent)
+%      {\bfseries}  % Thm head font
+%      {.}          % Punctuation after thm head
+%      {.5em}       % Space after thm head (\newline = linebreak)
+%      {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
+% \theoremstyle{remark}
+% \newtheorem{remark}{Remark}[section]
+% \newtheorem{example}{Example}[section]
+% \newtheorem{assumption}{Assumption}[section]
+% \newtheorem{definition}{Definition}[section]
+
+\input{macros}
 
@@
 % John's macros
-\def\X{\mathcal{X}}
-\def\comma{\unskip,~}
-\def\truep{p^*}
-\def\div{\|\,}
-\long\def\comment#1{}
-\def\reals{{\mathbb R}}
-\def\P{{\mathbb P}}
-\def\E{{\mathbb E}}
-\def\Cov{\mathop{\text{Cov}}}
-\def\supp{\mathop{\text{supp}\kern.2ex}}
-\def\argmin{\mathop{\text{\rm arg\,min}}}
-\def\arginf{\mathop{\text{\rm arg\,inf}}}
-\def\argmax{\mathop{\text{\rm arg\,max}}}
-\let\tilde\widetilde
-\def\csd{${}^*$}
-\def\mld{${}^\dag$}
-\def\dos{${}^\ddag$}
-\def\W{\widetilde Y}
-\def\Z{\widetilde X}
-\let\hat\widehat
-\let\tilde\widetilde
-\def\given{{\,|\,}}
-\def\ds{\displaystyle}
-\def\bs{\backslash}
-\def\1{{(1)}}
-\def\2{{(2)}}
-\def\pn{{(n)}}
-\def\ip{{(i)}}
-\def\Xbar{\overline{X}}
-\def\except{\backslash}
-\def\npn{\mathop{\textit{NPN\,}}}
-\def\i{{(i)}}
-\def\cE{{\mathcal{C}}}
-\def\cM{{\mathcal{M}}}
-\def\cF{{\mathcal{F}}}
-\def\cP{{\mathcal{P}}}
-\def\cG{{\mathcal{G}}}
-\def\tr{\mathop{\text{tr}}}
-\long\def\comment#1{}
-\def\ti#1{#1}
-\def\titi#1{\textit{#1}}
-\def\cram{{\sc cram}}
-\def\spam{{\small\sc SpAM}}
-\def\diag{\mathop{\rm diag}}
-\def\ones{\mathbf{1}}
-\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
-\def\fatnorm#1{\threebars #1 \threebars}
-\def\rank{\mathop{\rm rank}}
-\def\S{\mathcal{S}}
-\def\H{\mathcal{H}}
-\def\K{{K}}
-\def\rank{\mathop{\rm rank}}
-\def\half{{1/2}}
-\def\Y{\mathbb{Y}}
-\def\M{\mathbb{M}}
-\def\F{\mathbb{F}}
-\def\pinv{{-1}}
-%\def\ones{\mathds{1}}
-%\def\ones{1}
-\def\Res{Z}
-\def\Proj{P}
-\def\cN{{\mathcal N}}
-\def\cT{{\mathcal H}}
-\def\coloneqq{:=}
-\def\mathbf#1{\mbox{\boldmath $#1$}} 
-\def\bar#1{\overline{#1}}
+% \def\X{\mathcal{X}}
+% \def\comma{\unskip,~}
+% \def\truep{p^*}
+% \def\div{\|\,}
+% \long\def\comment#1{}
+% \def\reals{{\mathbb R}}
+% \def\P{{\mathbb P}}
+% \def\E{{\mathbb E}}
+% \def\Cov{\mathop{\text{Cov}}}
+% \def\supp{\mathop{\text{supp}\kern.2ex}}
+% \def\argmin{\mathop{\text{\rm arg\,min}}}
+% \def\arginf{\mathop{\text{\rm arg\,inf}}}
+% \def\argmax{\mathop{\text{\rm arg\,max}}}
+% \let\tilde\widetilde
+% \def\csd{${}^*$}
+% \def\mld{${}^\dag$}
+% \def\dos{${}^\ddag$}
+% \def\W{\widetilde Y}
+% \def\Z{\widetilde X}
+% \let\hat\widehat
+% \let\tilde\widetilde
+% \def\given{{\,|\,}}
+% \def\ds{\displaystyle}
+% \def\bs{\backslash}
+% \def\1{{(1)}}
+% \def\2{{(2)}}
+% \def\pn{{(n)}}
+% \def\ip{{(i)}}
+% \def\Xbar{\overline{X}}
+% \def\except{\backslash}
+% \def\npn{\mathop{\textit{NPN\,}}}
+% \def\i{{(i)}}
+% \def\cE{{\mathcal{C}}}
+% \def\cM{{\mathcal{M}}}
+% \def\cF{{\mathcal{F}}}
+% \def\cP{{\mathcal{P}}}
+% \def\cG{{\mathcal{G}}}
+% \def\tr{\mathop{\text{tr}}}
+% \long\def\comment#1{}
+% \def\ti#1{#1}
+% \def\titi#1{\textit{#1}}
+% \def\cram{{\sc cram}}
+% \def\spam{{\small\sc SpAM}}
+% \def\diag{\mathop{\rm diag}}
+% \def\ones{\mathbf{1}}
+% \def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
+% \def\fatnorm#1{\threebars #1 \threebars}
+% \def\rank{\mathop{\rm rank}}
+% \def\S{\mathcal{S}}
+% \def\H{\mathcal{H}}
+% \def\K{{K}}
+% \def\rank{\mathop{\rm rank}}
+% \def\half{{1/2}}
+% \def\Y{\mathbb{Y}}
+% \def\M{\mathbb{M}}
+% \def\F{\mathbb{F}}
+% \def\pinv{{-1}}
+% %\def\ones{\mathds{1}}
+% %\def\ones{1}
+% \def\Res{Z}
+% \def\Proj{P}
+% \def\cN{{\mathcal N}}
+% \def\cT{{\mathcal H}}
+% \def\coloneqq{:=}
+% \def\mathbf#1{\mbox{\boldmath $#1$}} 
+% \def\bar#1{\overline{#1}}
 

### 2014-07-31 tex/scam/sparsistency.tex
minor typo
results update

@@
 \section{Analysis of Variable Selection Consistency}
+\label{sec:finitesample}
 
@@
 
-This result holds regardless of whether we impose the Lipschitz conditions in optimization~\ref{opt:alternate_opt} and~\ref{opt:alternate_opt_concave} or not.
+This result holds regardless of whether we impose the boundedness conditions in optimization~\ref{opt:alternate_opt} and~\ref{opt:alternate_opt_concave} or not.
 The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.\\
@@
 \item[A2:] $f_0$ is convex and twice-differentiable. 
-\item[A3:] $|\partial_{x_k} f_0 | \leq L$ for all $k$
+\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
 \item[A4:] $w$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
@@
 
-Suppose $\lambda_n \geq c s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
+Suppose $\lambda_n \geq c s B \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
 \[
@@
 Suppose assumptions A1-A4 hold.
-Let $\hat{f}$ be any AC solution to the restricted regression with $L$-Lipschitz constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $L$-Lipschitz constraint.\\
+Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.\\
 
-Suppose $\lambda \leq c sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\
+Suppose $\lambda \leq c sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
 
@@
 result, Theorem~\ref{thm:convex_faithful}. We also include an extra
-Lipschitz constraint so that we can use existing covering number
-results \cite{Bronshtein:76}. Recent work
-\cite{Guntu:13} shows that the Lipschitz constraint
-is not required with more advanced empirical process theory
-techniques; we leave the incorporation of this development as future work. 
-We give the full proof of Theorem~\ref{thm:false_negative}
-in Section~\ref{sec:false_negative_proof} of the Appendix.
+boundedness constraint so that we can use recent bracketing number
+results \cite{kim2014global}.
 
@@
 \begin{corollary}
-Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $L$-Lipschitz constraints, both with 
-$\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\
+Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
+$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
 
@@
 \begin{remark}
-\citet{dalalyan:12} have shown that under tradtional smoothness constraints, variable selection is achievable only if $n > O(e^s)$.
+\citet{dalalyan:12} have shown that under tradtional smoothness constraints, even with a product distribution, variable selection is achievable only if $n > O(e^s)$.
 It is interesting to observe that because of additive faithfulness, the convexity assumption enables a much better scaling of $n = O(\textrm{poly}(s))$, demonstrating that geometric constraints can be quite different from the previously studied smoothness conditions.

### 2014-07-31 tex/scam/summary.tex
results update

@@
 \item[A2:] $f_0$ is convex and twice-differentiable. 
-\item[A3:] $|\partial_{x_k} f_0 | \leq L$ for all $k$
+\item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \| \leq B$ for all $k$.
 \item[A4:] The noise is mean-zero sub-Gaussian, independent of $X$.
 \end{packed_enum}
+In Assumption A3, $f^*=\sum_k f^*_k$ denotes the population optimal additive projection of $f_0$.
 
@@
 We also include an extra
-Lipschitz constraint so that we can use existing covering number
-results \citep{Bronshtein:76}. Recent work
-\cite{Guntu:13} shows that the Lipschitz constraint
-is not required with more advanced empirical process theory
-techniques; we leave the incorporation of this development as future work.
+boundedness constraint so that we can use new bracketing number
+results \citep{kim2014global}.
 
@@
 regularization parameter $\lambda$ scaling as
-$\lambda = \Theta \Big( sLb \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
+$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
 Suppose in addition that
 \begin{gather}
-\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2
+\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2
   np}\\
-\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}}
+\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}}
   \log^2 2np}.
@@
 
-We remark that \citet{dalalyan:12} show that under traditional smoothness
+We remark that \citet{dalalyan:12} show that, even with the product distribution,
+ under traditional smoothness
 constraints, variable selection is achievable only if $n > O(e^s)$. 

### 2014-07-31 tex/scam/optimization.tex
boundedness

@@
 \begin{remark}
-in sparsistency analysis, we assume that $L$, an upper bound to the coordinate-wise Lipschitz smoothness of the true function $f_0$, is known and that we constrain our estimate $\hat{f}$ to obey the same Lipschitz condition, that is, each $\hat{f}_k$ must be $L$-Lipschitz.
-This Lipschitz constraint can be easily added to our optimization program.
-In optimization~\ref{opt:alternate_opt}, we can enforce the Lipschitz condition by adding two constraints: $d_{k(1)} \geq - L$ and $\sum_{j=2}^{n-1} d_{k(j)} \leq L$ (similarly for optimization~\ref{opt:alternate_opt_concave}).
-We emphasize that we use the Lipschitz constraint only in our theoretical analysis; all of our experiments do not impose any Lipschitz condition.
+in sparsistency analysis, we assume that $B$, an upper bound to $\| f^*_k \|_\infty$, is known and that we constrain our estimate $\hat{f}$ to obey the same boundedness condition, that is, for each $k$, we require that $\|\hat{f}_k\|_\infty \leq B$.
+This boundedness constraint can be easily added to our optimization program.
+In optimization~\ref{opt:alternate_opt}, we can enforce the boundedness condition by adding $p$ constraints: $\| \bar{\Delta}_k d_k \|_\infty \leq B$ for $k=1,...,p$.
+(similarly for optimization~\ref{opt:alternate_opt_concave}).
+We emphasize that we use the boundedness constraint only in our theoretical analysis; all of our experiments do not impose any boundedness condition.
 \end{remark}

### 2014-07-31 tex/scam/sparsistency.tex
boundedness

@@
 
-Suppose $\lambda \leq c sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.
+Suppose $\lambda \leq c_1 sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.
+Suppose also that $\sigma \geq c_2$ for an arbitrarily small constant $c_2 > 0$.
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$, where $c$ is a constant dependent only on $b, c_1, c_2$.\\
 
@@
 Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
-$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\
+$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. Suppose $\sigma \geq c_2$ for an arbitrarily small constant $c_2 > 0$.\\
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$ where $c$ is some constant dependent only on $b, c_2$.\\
 

### 2014-08-01 tex/scam/additive_faithful.tex
minor edits

@@
 We pause to give some intuition before we presenting the full proof.
-Suppose that the the underlying distribution has a product density.
+Suppose that the underlying distribution has a product density.
 Then we know from Lemma~\ref{lem:general_int_reduction} that the
@@
 Theorem~\ref{thm:convex_faithful} by showing that ``slices'' of convex
-functions that integrate to zero cannot be ``glued'' together while
+functions that integrate to zero cannot be ``glued together'' while
 still maintaining convexity.
@@
 satisfies the boundary points condition. Suppose that $f$ is convex
-and twice-differentiable, and that that $\partial_{x_k} f$,
+and twice differentiable, and that $\partial_{x_k} f$,
 $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
@@
 we have that
-\begin{align*}
+\begin{align}
 f^*_k &= \arg\min_{f_k} \Big\{
@@
   \Big\}
-\end{align*}
+\end{align}
 Therefore, $f^*_k = 0$ and $g^*_k = 0$ implies that $\E[ f(X) -

### 2014-08-12 tex/scam/appendix.tex
boundedness
proof update

@@
 \begin{theorem} 
-Suppose assumptions A1-A4 hold.
-
-Suppose $\lambda_n \geq c s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
-\[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
+Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$. Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+
+Suppose $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$, then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
+\[
+\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|
 \]
@@
 Fix $j$ and $i$.
-$\hat{r}^\tran \mathbf{1}_{(i':n)}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$.
+$\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$.
 We will then use Serfling's theorem on the concentration of measure of sampling without replacement.
@@
 
-Both $f_0(x_i)$ and $\hat{f}(x_i)$ are coordinate-wise $L$-Lipschitz and therefore are bounded by $2 sLb$.
-
-Because $w_i$ is subgaussian, $|w_i| \leq c \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
-By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq c \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.
-
-We now put this together and take another union bound across all $j$ and all $i'$:
-\begin{align*}
-\| \hat{r} \|_\infty &\leq c (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
-      &\leq c sLb \sigma \sqrt{\log \frac{2}{\delta}}
-\end{align*}
-with probability at least $1 - n^2 p \delta$. We supposed that both $sLb \geq 2$ and $\sigma\sqrt{\log \frac{2}{\delta}} \geq 2$.
+Both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $sB$.
+
+Because $w_i$ is subgaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at most $1 - \delta$.
+
+We now put this together: 
+%and take another union bound across all $j$ and all $i'$:
+\begin{align}
+\| \hat{r} \|_\infty &\leq 2sB + \sigma \sqrt{ 2\log \frac{2n}{\delta}}) \nonumber \\
+      &\leq 4 s \tilde{\sigma} \sqrt{\log \frac{2n}{\delta}} \label{eqn:stepone_rhat}
+\end{align}
+with probability at least $1 - \delta$.
+We define $\tilde{\sigma} = \max(\sigma, B)$.
+We also supposed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$, which is acceptable since $\delta \leq 1$ and the theorem presupposes that $\sqrt{ \log 2np } \geq 1$.
 
@@
 
-Because $|f_0(x_i)| \leq sLb$, the first term $| \frac{1}{n} \sum_{i=1}^n f_0(x_i)|$ is at most $2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$ by Hoeffding Inequality.
-
-Because $w_i$ is subgaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $2 \sigma \sqrt{ \frac{1}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+Because $|f_0(x_i)| \leq sB$, the first term $| \frac{1}{n} \sum_{i=1}^n f_0(x_i)|$ is at most $sB \sqrt{\frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$ by Hoeffding Inequality.
+
+Because $w_i$ is subgaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $\sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
 
@@
 
-\begin{align*}
-| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
-  &\leq c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
-\end{align*}
-with probability at least $1-2\delta$.\\
+\begin{align}
+| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq sB \sqrt{\frac{2}{n} \log \frac{4}{\delta}} +  \sigma \sqrt{\frac{2}{n} \log \frac{4}{\delta}} \nonumber \\
+  &\leq 4 s \tilde{\sigma} \sqrt{\frac{1}{n} \log \frac{4}{\delta}} \label{eqn:steptwo_rhat}
+\end{align}
+with probability at least $1-\delta$.\\
 
@@
 
-Serfling's theorem states that with probability at least $1 - \delta$:
-\[
+For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$:
+\begin{align*}
 \Big
-|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)}\Big| \leq
+|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| \leq
    2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
    \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
-\]
-
-Taking an union bound across previous events, we have that with probability at least $1 - 3n^2 p \delta$, for all $j \in S^c$, for all $i'=1,...,n$:
-\begin{align*}
-\Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
-  c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
-\end{align*}
-Setting $\delta = \frac{1}{n^3 p}$ gives the desired result.
+\end{align*}
+
+We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' = 1,...,n$.
+We also need the events that $\|\hat{r}\|_\infty$ and $| \frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold.
+The following follows from a union bound.
+With probability at least $1-\delta$, for all $k,i'$,
+\begin{align*}
+\Big
+|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| &\leq
+   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
+   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
+  &\leq 4s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
+  &\leq 8 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
+\end{align*}
+
+In the second inequality, we used equation~\ref{eqn:stepone_rhat} and equation~\ref{eqn:steptwo_rhat} from step 1 and 2 respectively. Setting $\delta = \frac{12}{n}$ gives the desired result.
 
@@
 Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
-Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions.
+Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions.
 \\
 
-Define $\mathcal{C}^s$ as the set of convex additive functions and $\mathcal{C}^s_L$ likewise as the set of $L$-Lipschitz convex additive functions.
+Define $\mathcal{C}^s$ as the set of convex additive functions and $\mathcal{C}^s_B$ likewise as the set of convex additive functions whose components are $B$-bounded.
 \begin{align*}
@@
    f_k \in \mathcal{C}^1 \} \\
-\mathcal{C}^s_L &\equiv \{ f \in \mathcal{C}^s \,:\, 
-f = \sum_{k=1}^s f_k, \, \| \partial f_k \|_\infty \leq L \}
+\mathcal{C}^s_B &\equiv \{ f \in \mathcal{C}^s \,:\, 
+f = \sum_{k=1}^s f_k, \, \| f_k \|_\infty \leq B \}
 \end{align*}
@@
 
-We let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.
-Since $f_0, f^*$ are supported on $[-b, b]^s$, it follows that $\| f_0 \|_\infty, \|f^* \|_\infty \leq s L b$.
+We let $sB$ be an upper bound on $\| f_0 \|_\infty$ and $B$ be an upper bound on $\| f^*_k \|_\infty$. It follows that $\|f^* \|_\infty \leq s B$.
 
@@
 \hat{f} = \arg\min \Big \{ \| y - f \|_n^2 + \lambda \sum_{k=1}^s \| f_k \|_\infty 
-    \,:\, f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0 \Big \}
+    \,:\, f \in \mathcal{C}^s_B,\, \mathbf{1}_n^\tran f_k = 0 \Big \}
 \]
@@
 \[
-\hat{g}_k \equiv \argmin \Big\{ \| f_0 - \hat{f} - g_k \|_n^2 \,:\, g_k \in \mh \mathcal{C}^1_L \,, \mathbf{1}_n^\tran g_k = 0 \Big\}
+\hat{g}_k \equiv \argmin \Big\{ \| f_0 - \hat{f} - g_k \|_n^2 \,:\, g_k \in \mh \mathcal{C}^1_B \,, \mathbf{1}_n^\tran g_k = 0 \Big\}
 \]
@@
 \label{thm:convex_consistent}
-Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq sB \sqrt{ \frac{1}{n} \log^2 np}$.
-
-Suppose $n \geq c_1 \max(\sqrt{sB}, B)$ and $B, \sigma \geq c_2$ for some constant $c_1, c_2$.
-
-Then, with probability at least $1-\delta$,
+Let $\tilde{\sigma} \equiv \max(\sigma, B)$. Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq 9 s \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
+
+Suppose $n \geq c_1 \max(\sqrt{sB}, B)$.
+
+Then, with probability at least $1-\frac{C}{n}$,
 \begin{align}
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np}
 \end{align}
-Where $c, C$ are constants, dependent on $c_1, c_2$.
+Where $c, C$ are constants, possibly dependent on $c_1, b$.
 
@@
 
-The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$.
+The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.
 
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B 
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B 
 \end{align*}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}
 \end{align}
@@
 
-Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s\}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
+Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_B \}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
 
@@
 $\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
-)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.
+)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$, where we assumed that condition~\ref{cond:simplify_covering_number} holds.
 
@@
 $$.
-Where we assumed that condition~\ref{cond:simplify_covering_number} holds.
-
-We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
-Therefore,  
+
+We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. \\
+
+As proved before, the event $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$ has probability at most $1-\delta$.
+We take an union bound between this event and the event that for all $h$, $\frac{1}{n}\sum_{i=1}^n | h(X_i) - h_L(X_i)|$ is small:
 \[
 |\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
-  \sigma \sqrt{\log \frac{n}{\delta}} \left( \epsilon + \epsilon_{n,\delta} \right)
-\]
-For the last inequality, we used the fact that $w$ is a vector of independent subgaussian($\sigma$) random variables and hence, by union bound, with probability at least $1-\delta$, $\| w \|_\infty \leq \sigma \sqrt{\log \frac{n}{\delta}}$.
-
-By another property of subgaussian random variables, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{1}{cn} \log \frac{1}{\delta} }$.
-Applying an union bound, we have that
-$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{\log N_{[]}}{n} \log \frac{1}{\delta}}$.
+  \sigma \sqrt{2 \log \frac{4n}{\delta}} \left( \epsilon + \epsilon_{n,2\delta} \right)
+\]
+
+By another property of subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
+Union bound again, we have that
+$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$.
 
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
-     | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log \frac{1}{\delta}}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
-   \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
-   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
-   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
-   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{n}{\delta}}{cn \epsilon^{1/2}}} \\
-\end{align*}
-
-The two terms are balanced when one sets $\epsilon = sB \sqrt{ \frac{(s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.
-
-This is only valid if $n$ is large enough so that $\epsilon \in (0, sB \epsilon_3]$.
-
-Also, to ensure that conditions~\ref{cond:simplify_covering_number} hold, we need that $\log n \geq 2$ and $n \geq c B$ where $c$ is some constant dependent only on $K^{**}$ and $b$.
-
-We upper bound some terms to simplify the presentations again and end up with the following result:
-
-\[
-|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{c n^{4/5}}}
-\]
+     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, 2\delta}) \\
+   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   \sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
+   &\leq \sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
+\end{align*}
+
+We need that $n$ is large enough so that $\epsilon \in (0, sB \epsilon_3]$ and to ensure that conditions~\ref{cond:simplify_covering_number} hold, we need that $\log n \geq 2$ and $n \geq c B$ where $c$ is some constant dependent only on $K^{**}$ and $b$.
+
+The conditions needed are satisfied if we set $\epsilon = sB \sqrt{ \frac{(s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$ and use the $n \geq c_1 \max( \sqrt{sB}, B)$ assumption in the statement of the theorem.
+Setting $\epsilon$ thus also balances the two terms.
+
+We upper bound some terms to simplify the presentations again and end up with the following result, with probability at least $1-\delta$:
+
+\[
+|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
+   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+\]
+where we absorbed $K^{**}$ into the constants $c$ and the union bound multipliers into the constant $C$.
 
@@
    &\leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{n^{4/5}}}
-   + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
+   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   + \lambda 2 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
    &\leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{nC}{\delta}}{n^{4/5}}}
-   + \lambda 4 s B \nonumber\\   
+   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   + \lambda 2 s B \nonumber\\   
    &\leq c B \sigma 
-    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log^2 \frac{n}{\delta}} + \lambda 4 sB
+    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
 \label{eqn:second_step_inequality}
@@
     \sqrt{ \frac{s^3 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
- +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+ +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^3 \sigma \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 4 sB \nonumber
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
 \end{align}
-Where for the second inequality, we used the assumption that there is some large constant $c$ such that $B \geq \frac{\sigma}{c\sigma + 1}$.
-
-Substituting in $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.
+Where for the second inequality, we define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+
+Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $\delta = \frac{C}{n}$ we get the desired result.
 
@@
 \label{thm:concave_consistent}
-Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$.\\
-
-Suppose $n$ is large enough such that $B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\
-
-Then, with probability at least $1- s\delta$, for all $k=1,...,s$:\\
-\[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c (Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
+Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+
+Suppose $n$ is large enough such that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np } \leq 1$.\\
+
+Then, with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$:\\
+\[
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np} 
 \]
@@
 
-Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
+Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-\delta$:
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
+  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda 2 B +
   c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
- &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
-\end{align*}
-
-Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
+ &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda 2B
+\end{align*}
+
+Plugging in $\lambda \leq 9 s \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$:
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
-    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ 
+    2s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
-\end{align*}
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}} \\
+\end{align*}
+with probability at least $1-\delta$.
 
@@
    + 2 \langle f_0 - f^*, g^*_k \rangle \\
- &\leq c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
+ &\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} + 
     2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
- &\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
+ &\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} +
     2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
-&\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
-   c B \sqrt{B^3\sigma \sqrt{ 
-                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
-&\leq  cB \sqrt{B^3\sigma \sqrt{ 
-                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
-\end{align*}
+&\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} +
+   c B \sqrt{B^2 \tilde{\sigma} \sqrt{ 
+                   \frac{s^5}{n^{4/5}} \log^2 np} }\\
+&\leq  cB \sqrt{B^2 \tilde{\sigma} \sqrt{ 
+                   \frac{s^5}{n^{4/5}} \log^2 np} }\\
+\end{align*}
+with probability at least $1-\frac{C}{n}$, by theorem~\ref{thm:convex_consistent}.
 
@@
 \| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
-   c B^{2.5} \sigma^{0.5} 
+   c B^2 \sigma^{1/2} 
      \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
@@
 \sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
-   c B^2 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
+   c B^3 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
 \end{align*}
@@
 
-$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$.
+$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $(sB)^2$.
 By Hoeffding's inequality and union bound, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
@@
 \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
-  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
+  c B^3 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
 \end{align*}
@@
 \Big | \| f_0 - f^* \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 \Big| \leq
-    c (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
+    c (sB)^2 \frac{1}{n} \log \frac{4}{\delta}
 \]
@@
 
-$\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 s L b \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.
+$\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 sB \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.
 
@@
 %%% mode:latex ***
-%%% TeX-master: "faithful.tex" ***
+%%% TeX-master: "paper.tex" ***
 %%% End: ***

### 2014-08-12 tex/scam/sparsistency.tex
proof update

--- 2014-07-31 tex/scam/sparsistency.tex
@@
 \label{thm:false_positive}
-Suppose assumptions A1-A4 hold.
+Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
 
-Suppose $\lambda_n \geq c s B \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
+Suppose $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{12}{np}$, for all $k \in S^c$, and for all $i'=1,...,n$:
 \[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
+\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|
 \]
@@
 Suppose assumptions A1-A4 hold.
-Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.\\
+Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.
+Let $\tilde{\sigma}$ denote $\max(\sigma, B)$.\\
 
-Suppose $\lambda \leq c sB  \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that$\frac{n^{4/5}}{\log^2 np} \geq B^3 \sigma s^{2.5}$.
+Suppose $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^2 \tilde{\sigma} s^{5/2}$.
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$, where $c$ is a constant dependent only on $b, c_1$.\\
 
-Then, with probability at least $1 - \frac{1}{n}$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.
+Then, with probability at least $1 - \frac{C}{n}$ for some constant $C$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.
 
@@
 Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
-$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. \\
+$\lambda = \Theta\big( s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np} \big) $. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
 
 Suppose 
-$\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
+$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^4 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$.
 
-Then, for all large enough $n$, we have that with probability at least $1-\frac{1}{n}$:
+Then, for all large enough $n$, we have that with probability at least $1-\frac{C}{n}$:
 \begin{align*}
@@
 \end{align*}
+
+where $c,C$ are constants, possibly dependent on $b, c_1$.
 

### 2014-08-12 tex/scam/summary.tex
boundedness
proof update

@@
 \begin{gather}
-\frac{\alpha_f}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2
+\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2
   np}\\
-\frac{\alpha_g^2}{\sigma} \geq c B^3 \sqrt{\frac{s^5}{n^{4/5}}
+\alpha_g^2/\tilde{\sigma} \geq c B^4 \sqrt{\frac{s^5}{n^{4/5}}
   \log^2 2np}.
 \end{gather} 
+where $\tilde{\sigma} \equiv \max(\sigma, B)$ and $c$ is a constant dependent only on $b, c_1$.
+
 Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$:
@@
 This shows that variable selection consistency is achievable under
-exponential scaling of the ambient dimension, $p = O(\exp(n^c))
-for c<1$, as for linear models. The cost of nonparametric estimation is
+exponential scaling of the ambient dimension, $p = O(\exp(n^c))$
+for $c<1$, as for linear models. The cost of nonparametric estimation is
 reflected in the scaling with respect to $s=|S|$, which can grow only

### 2014-09-10 tex/scam/appendix.tex
new plots

@@
 
-The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.
+The middle term can be bounded with the assumption that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.
 
@@
 
-By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
+Let us suppose condition~\ref{cond:simplify_covering_number} holds, then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$,
 $\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
-)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$, where we assumed that condition~\ref{cond:simplify_covering_number} holds.
+)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the end of the proof that condition~\ref{cond:simplify_covering_number} indeed holds.
 
@@
 
-We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. \\
-
-As proved before, the event $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$ has probability at most $1-\delta$.
-We take an union bound between this event and the event that for all $h$, $\frac{1}{n}\sum_{i=1}^n | h(X_i) - h_L(X_i)|$ is small:
+We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.
+Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$.
+$\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.\\
+
+Let $\mathcal{E}_{\|w\|_\infty}$ denote the event that $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$; $\mathcal{E}_{\|w\|_\infty}$ has probability at most $1-\delta$.
+We take an union bound between $\mathcal{E}_{\|w\|_\infty}$ and $\mathcal{E}_{[\,]}$ and get that, with probability at most $1-2\delta$, for all $h$:
 \[
@@
 
-By another property of subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
-Union bound again, we have that
-$\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$.
+Because $w$ is a subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
+Using union bound again, we have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has probability at most $1-\delta$.
 
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
-     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, 2\delta}) \\
-   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta}) \\
+   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
    &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
    &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   \sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
-   &\leq \sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
+   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
+   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
 \end{align*}

### 2014-09-10 code/paper_exp/C.m

@@ -107,3 +107,22 @@ plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
 legend('v=0.0','v=0.2','v=0.5','v=0.9');
 xlabel('Number of Samples'); ylabel('Probability of Recovery');
 title('Probability of Recovery');
+%set(gca, 'LooseInset', get(gca, 'TightInset'));
+
+tightInset = get(gca, 'TightInset');
+position(1) = tightInset(1);
+position(2) = tightInset(2);
+position(3) = 1 - tightInset(1) - tightInset(3);
+position(4) = 1 - tightInset(2) - tightInset(4);
+set(gca, 'Position', position);
+set(gca,'units','centimeters')
+pos = get(gca,'Position');
+
+ti = get(gca,'TightInset');
+set(gcf, 'PaperUnits','centimeters');
+set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+set(gcf, 'PaperPositionMode', 'manual');
+set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+
+h = gcf;
+%saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/Curve4.pdf');

### 2014-09-10 code/paper_exp/R.m

@@ -130,3 +130,22 @@ plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
 legend('\alpha=0.0','\alpha=0.2','\alpha=0.5','\alpha=1.0');
 xlabel('Number of samples'); ylabel('Probability of recovery');
 title('Probability of support recovery');
+
+
+tightInset = get(gca, 'TightInset');
+position(1) = tightInset(1);
+position(2) = tightInset(2);
+position(3) = 1 - tightInset(1) - tightInset(3);
+position(4) = 1 - tightInset(2) - tightInset(4);
+set(gca, 'Position', position);
+set(gca,'units','centimeters')
+pos = get(gca,'Position');
+
+ti = get(gca,'TightInset');
+set(gcf, 'PaperUnits','centimeters');
+set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+set(gcf, 'PaperPositionMode', 'manual');
+set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+
+h = gcf;
+saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/Curve2.pdf')

### 2014-09-10 code/paper_exp/T.m

@@ -1,6 +1,7 @@
 function T(version)
 % p changes
-% Diagonal quadratic with noise.
+% function Diagonal quadratic with noise.
+% covariance correlated alpha=0.5
 
 clc; close all; format long; randn('state',0); rand('state',0); 
 switch version
@@ -103,3 +104,22 @@ plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
 legend('p=64','p=128','p=256','p=512');
 xlabel('Number of Samples'); ylabel('Probability of Recovery');
 title('Probability of Recovery');
+
+
+tightInset = get(gca, 'TightInset');
+position(1) = tightInset(1);
+position(2) = tightInset(2);
+position(3) = 1 - tightInset(1) - tightInset(3);
+position(4) = 1 - tightInset(2) - tightInset(4);
+set(gca, 'Position', position);
+set(gca,'units','centimeters')
+pos = get(gca,'Position');
+
+ti = get(gca,'TightInset');
+set(gcf, 'PaperUnits','centimeters');
+set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+set(gcf, 'PaperPositionMode', 'manual');
+set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+
+h = gcf;
+saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/Curve1.pdf')

### 2014-09-10 tex/scam/appendix.tex
analysis update

@@
 
-Suppose $n$ is large enough such that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np } \leq 1$.\\
+Suppose $n$ is large enough such that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.\\
 
@@
 \begin{proof}
-The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
-
-\textbf{Step 1.} We start from the definition of $\hat{g}_k$:
+
+Because we fit $\hat{g}_k$ against $f_0 - \hat{f}$ instead of $f_0 - f^*$, we need the following decomposition:
+\begin{align}
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 = & \underbrace{\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \| f_0 - \hat{f} - g^*_k \|_P^2}_{\trm{term 1}} + \nonumber \\
+   & \underbrace{\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - \hat{f} - \hat{g}_k \|_P^2}_{\trm{term 2}} + \nonumber \\
+   & \underbrace{\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2}_{\trm{term 3}}  \label{eqn:concave_init_decomposition}
+\end{align}
+
+We now bound each of the terms. The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
+
+\textbf{Step 1.} We bound term 2. We start from the definition of $\hat{g}_k$:
 \begin{align*}
@@
 
-\textbf{Step 2.} The goal is to bound the quality of approximation between $\| f_0 - \hat{f} - g^*_k \|_P^2$ and $\| f_0 - f^* - g^*_k \|_P^2$ and likewise for $\hat{g}_k$.
+\textbf{Step 2.} We bound term 2 and 3.
 
@@
 \| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
-    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
-   + 2 \langle f_0 - f^*, g^*_k \rangle \\
+    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle_P
+   + 2 \langle f_0 - f^*, g^*_k \rangle_P \\
  &\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} + 
-    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
+    2 | \langle \hat{f} - f^*, g^*_k \rangle_P |  \\
  &\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} +
@@
                    \frac{s^5}{n^{4/5}} \log^2 np} }\\
-&\leq  cB \sqrt{B^2 \tilde{\sigma} \sqrt{ 
-                   \frac{s^5}{n^{4/5}} \log^2 np} }\\
+&\leq  cB^2 \tilde{\sigma}^{1/2} \sqrt[4]{ 
+                   \frac{s^5}{n^{4/5}} \log^2 np} 
 \end{align*}
 with probability at least $1-\frac{C}{n}$, by theorem~\ref{thm:convex_consistent}.
-
-The same bound likewise holds for $\hat{g}_k$.
-
-\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
+To get the fourth inequality, we used the fact that $\| \hat{f} - f^* \|^2 \leq \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2$, which is true because $f^*$ is the projection of $f_0$ onto the set of additive convex functions and the set of additive convex functions is convex itself.
+
+The last inequality holds because under the condition of the theorem that $n$ is large enough, $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
+
+The same bound likewise holds for term 2.
+
+\textbf{Step 3.} Collecting the results and plugging them into equation~\ref{eqn:concave_init_decomposition}, we have, with probability at least $1-2\delta$:
 \begin{align*}
 \| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
-   c B^2 \sigma^{1/2} 
+   c B^2 \tilde{\sigma}^{1/2} 
      \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 

### 2014-09-10 tex/scam/optimization.tex
analysis update

@@
 for all $j > i$
-\begin{align}
+\begin{align*}
   f_{(j)_kk}-f_{(i)_kk}  & = \sum\limits_{t=i}^{j-1}(f_{(t+1)_kk}-f_{(t)_kk}) \\
@@
   & = \beta_{(i)_kk}(x_{(j)_kk}-x_{(i)_kk}) 
-\end{align}
+\end{align*}
 and for all $j < i$
-\begin{align}
+\begin{align*}
 f_{k(j)}-f_{k(i)} & =
@@
      & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
-\end{align}
+\end{align*}
 

### 2014-09-10 tex/scam/sparsistency.tex
analysis update

@@
 
-Suppose $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^2 \tilde{\sigma} s^{5/2}$.
+Suppose $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that $\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s^5$.
 
 Suppose 
-$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$, where $c$ is a constant dependent only on $b, c_1$.\\
+$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ where $c$ is a constant.
 
@@
 
-Then, for all large enough $n$, we have that with probability at least $1-\frac{C}{n}$:
+Then, for all large enough $n$ such that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$, we have that with probability at least $1-\frac{C}{n}$:
 \begin{align*}
@@
 
-where $c,C$ are constants, possibly dependent on $b, c_1$.
+where $c,C$ are constants.
 

### 2014-09-10 tex/scam/summary.tex
analysis update

@@
 % is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.
-Additive faithfulness is a desireable property
+Additive faithfulness is a desirable property
 since it implies that an additive approximation may allow us to 
@@
 \end{packed_enum}
-In Assumption A3, $f^*=\sum_k f^*_k$ denotes the population optimal additive projection of $f_0$.
+In Assumption A3, $f^*=\sum_k f^*_k$ denotes the optimal additive projection of $f_0$ in the population setting.
 
@@
 We also include an extra
-boundedness constraint so that we can use new bracketing number
+boundedness constraint to use new bracketing number
 results \citep{kim2014global}.

### 2014-09-11 tex/scam/optimization.tex
minor edits

@@
 
-Let $\bds{x}_{i}\in\mathbb{R}^{p}$ be the covariate, let $y_{i}$ be the
-response and let $\epsilon_{i}$ be the mean zero noise. The regression function $f(\cdot)$ we estimate is the summation of 
-functions $f_{k}(\cdot)$ in each variable dimension and a scalar offset $\mu$.  
-We impose an additional constraint that each $f_{k}(\cdot)$ is 
-an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
+Let $\bds{x}_{i}\in\mathbb{R}^{p}$ be the covariate, let $y_{i}$ be
+the response and let $\epsilon_{i}$ be the mean zero noise. The
+regression function $f(\cdot)$ we estimate is the sum of
+univariate functions $f_{k}(\cdot)$ in each variable dimension and a scalar
+offset $\mu$.  We impose additional constraints that each
+function $f_{k}(\cdot)$ is convex function, which can be
+represented by its supporting hyperplanes, i.e.,
 \begin{equation}\label{hyper}

### 2014-09-11 tex/scam/optimization.tex
modified the order statistic notation

@@
 \def\uds#1{#1}
+\def\perm#1{\pi_k(#1)}
 
@@
 offset $\mu$.  We impose additional constraints that each
-function $f_{k}(\cdot)$ is convex function, which can be
+function $f_{k}(\cdot)$ is convex, which can be
 represented by its supporting hyperplanes, i.e.,
@@
 \end{equation}
-where $f_{ik}\coloneqq f_{k}(x_{ik})$ and $\beta_{ik}$ is the
-subgradient at point $x_{ik}$. This apparently requires $O(n^2 p)$ constraints to
+where $f_{ik}\coloneqq f_{k}(x_{ik})$ is the function value and $\beta_{ik}$ is a
+subgradient at point $x_{ik}$. This ostensibly requires $O(n^2 p)$ constraints to
 impose the supporting hyperplane constraints.
@@
        \textrm{subject to} &\;\; \textrm{for all $k=1,\ldots, p$:}\\
-       & \;\; f_{(i+1)_k k} = f_{(i)_k k} +
-       \beta_{(i)_k k}(x_{(i+1)_k k}-x_{(i)_k k}),\;\textrm{for $i=1,\ldots, n-1$}\\
+       & \;\; f_{\perm{i+1} k} = f_{\perm{i} k} +
+       \beta_{\perm{i} k}(x_{\perm{i+1} k}-x_{\perm{i} k}),\;\textrm{for $i=1,\ldots, n-1$}\\
        & \;\; \sum_{i=1}^{n}f_{ik}=0,\\
-       & \;\; \beta_{(i+1)_k k} \geq \beta_{(i)_k k}\;\textrm{for $i=1,\ldots, n-1$}.
+       & \;\; \beta_{\perm{i+1} k} \geq \beta_{\perm{i} k}\;\textrm{for $i=1,\ldots, n-1$}.
 \end{split}
@@
 Here $f_k$ denotes the vector $f_k = (f_{1k}, f_{2_k}\ldots, f_{nk})^T\in\reals^n$
-and $\{(1)_k,(2)_k,\ldots,(n)_k\}$ are the indices in the sorted ordering
+and $\{\perm{1},\perm{2},\ldots,\perm{n}\}$ are the indices in the sorted ordering
 of the values of coordinate $k$:
 \begin{equation}
-x_{(1)_k k} \leq{} x_{(2)_k k} \leq \cdots \leq{} x_{(n)_k k}.
+x_{\perm{1} k} \leq{} x_{\perm{2} k} \leq \cdots \leq{} x_{\perm{n} k}.
 \end{equation}
@@
 \begin{align*}
-  f_{(j)_kk}-f_{(i)_kk}  & = \sum\limits_{t=i}^{j-1}(f_{(t+1)_kk}-f_{(t)_kk}) \\
-   &= \sum\limits_{t=i}^{j-1}\beta_{(t)_kk}(x_{(t+1)_kk}-x_{(t)_kk}) \\
-   &\geq \beta_{(i)_kk}\sum\limits_{t=i}^{j-1}(x_{(t+1)_kk}-x_{(t)_kk}) \\
-  & = \beta_{(i)_kk}(x_{(j)_kk}-x_{(i)_kk}) 
+  f_{\perm{j}k}-f_{\perm{i}k}  & = \sum\limits_{t=i}^{j-1}(f_{\perm{t+1}k}-f_{\perm{t}k}) \\
+   &= \sum\limits_{t=i}^{j-1}\beta_{\perm{t}k}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
+   &\geq \beta_{\perm{i}k}\sum\limits_{t=i}^{j-1}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
+  & = \beta_{\perm{i}k}(x_{\perm{j}k}-x_{\perm{i}k}) 
 \end{align*}
@@
 $P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i$-th
-row  is all zeros except for a $-1$ in position $(i)_k$ and a $1$ in
-position $(i+1)_k$, and $D \in \R^{(n-2) \times (n-1)}$ is another
+row  is all zeros except for a $-1$ in position $\perm{i}$ and a $1$ in
+position $\perm{i+1}$, and $D \in \R^{(n-2) \times (n-1)}$ is another
 permutation matrix  where the $i$-th row is all zeros except for a $1$ 
@@
 necessary to modify the linear inequality constraints so that the subgradients are
-non-increasing: $\beta_{(i+1)_kk} \leq \beta_{(i)_kk}$.
+non-increasing: $\beta_{\perm{i+1}k} \leq \beta_{\perm{i}k}$.
 

### 2014-09-11 tex/scam/optimization.tex
modified the order statistic notation

@@
      + \lambda \gamma_k \label{opt:1d_compact} \\
- \textrm{such that } & P \uds{f}_k = \diag(P \bds{x}_k)  \uds{\beta}_k \\
+ \textrm{such that } & P_k \uds{f}_k = \diag(P_k \bds{x}_k)  \uds{\beta}_k \\
    & D \uds{\beta}_k \leq 0 \\
@@
 In addition, 
-$P \in \R^{(n-1) \times n}$ is a permutation matrix where the $i$-th
-row  is all zeros except for a $-1$ in position $\perm{i}$ and a $1$ in
+$P_k \in \R^{(n-1) \times n}$ is a permutation matrix where the $i$-th
+row  is all zeros except for the value $-1$ in position $\perm{i}$ and
+the value $1$ in
 position $\perm{i+1}$, and $D \in \R^{(n-2) \times (n-1)}$ is another

### 2014-09-11 tex/scam/optimization.tex
modified the order statistic notation

@@
 position $\perm{i+1}$, and $D \in \R^{(n-2) \times (n-1)}$ is another
-permutation matrix  where the $i$-th row is all zeros except for a $1$ 
-in position $i$ and a $-1$ in position $i+1$.  We denote by
+permutation matrix  where the $i$-th row is all zeros except for a
+value $1$  in position $\perm{i}$ and a value $-1$ in position $\perm{i+1}$.  We denote by
 $\diag( v )$ the diagonal matrix with diagonal entries $v$.
@@
 \citep{Boyd:admm}, but found
-that it is not as efficient as this QP solver.
+that it is not as efficient as this blockwise QP solver.
 
-After optimization, the function estimates for an input vector $\bds{x}$ is, according to (\ref{hyper}),
+After optimization, the function estimate for an input vector $\bds{x}$ is, according to (\ref{hyper}),
 \begin{equation}
@@
 
-The univariate concave function estimation is a straightforward
-modification of optimization~\ref{opt:1d_compact}. It is only
+The univariate concave function estimation required in the DC stage is a straightforward
+modification of optimization~\eqref{opt:1d_compact}. It is only
 necessary to modify the linear inequality constraints so that the subgradients are

### 2014-09-11 tex/scam/optimization.tex
modified the order statistic notation

@@
  \textrm{such that } & P_k \uds{f}_k = \diag(P_k \bds{x}_k)  \uds{\beta}_k \\
-   & D \uds{\beta}_k \leq 0 \\
+   & D_k \uds{\beta}_k \leq 0 \\
    & -\gamma_k \mathbf{1}_n \leq \uds{f}_k \leq \gamma_k \mathbf{1}_n   \\
@@
 the value $1$ in
-position $\perm{i+1}$, and $D \in \R^{(n-2) \times (n-1)}$ is another
+position $\perm{i+1}$, and $D_k \in \R^{(n-2) \times (n-1)}$ is another
 permutation matrix  where the $i$-th row is all zeros except for a
@@
       \hat f(\bds{x}) & = \sum_{k=1}^{p} \hat f_k(x_{j})+ \hat \mu 
-= \sum_{k=1}^{p}\max_{i} \bigl\{\hat f_{ik}+ \hat \beta_{ik}(x_{k}-x_{ik})\bigr\} +
+= \sum_{k=1}^{p}\max_{i} \Bigl\{\hat f_{ik}+ \hat \beta_{ik}(x_{k}-x_{ik})\Bigr\} +
       \hat \mu.
@@
 \subsection{Alternative Formulation}
-Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives, a form which we analyze in our theoretical analysis. The alternative formulation replaces the ordering
-constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity
-constraints, which simplifies theoretical analysis.
-Define $d_{k(i)}$ as the second derivative:
-$d_{k(1)} = \beta_{k(1)}$, and $d_{k(2)} =
-\beta_{k(2)} - \beta_{k(1)}$. The convexity constraint is
-equivalent to the constraint that $d_{k(i)} \geq 0$ for all $i >
-1$.
+Optimization (\ref{np}) can be reformulated in terms of the second
+derivatives.  We exploit this form in our theoretical analysis.
 
-It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(j)}$ and 
+The alternative formulation replaces the order constraints
+$\beta_{\perm{i+1}k} \geq \beta_{\perm{i}k}$ with positivity constraints, which
+simplifies the analysis.  Define $d_{\perm{i}k}$ as the second
+derivative: $d_{\perm{1}k} = \beta_{\perm{1}k}$, and $d_{\perm{i}k} = \beta_{\perm{i}k} -
+\beta_{\perm{i-1}k}$ for $i > 1$. The convexity constraint is equivalent to the
+constraint that $d_{\perm{i}k} \geq 0$ for all $i > 1$.
+
+It is easy to verify that $\beta_{\perm{i}k} = \sum_{j \leq i} d_{\perm{j}k}$ and 
 \begin{align*}
-f_k(x_{k(i)}) = & f_k(x_{k(i-1)}) + \beta_{k(i-1)}(x_{k(i)} - x_{k(i-1)}) \\
- =& f_k(x_{k1}) + \sum_{j < i} \beta_{k(j)} (x_{k(j)} - x_{k(j-1)}) \\
- =& f_k(x_{k1}) + \sum_{j < i} \sum_{j' \leq j} d_{k(j')} (x_{k(j)} - x_{k(j-1)})\\
- =& f_k(x_{k1}) + \sum_{j' < i} d_{k(j')} \sum_{i > j \geq j'} (x_{k(j)} - x_{k(j-1)}) \\
- =& f_k(x_{k1}) + \sum_{j' < i} d_{k(j')} (x_{k(i)} - x_{k(j')})
+f_k(x_{\perm{i}k}) = & f_k(x_{\perm{i-1}k}) + \beta_{\perm{i-1}k}(x_{\perm{i}k} - x_{\perm{i-1}k}) \\
+ =& f_k(x_{\perm{1}k}) + \sum_{j < i} \beta_{\perm{j}k} (x_{\perm{j}k} - x_{\perm{j-1}k}) \\
+ =& f_k(x_{\perm{1}k}) + \sum_{j < i} \sum_{j' \leq j} d_{\perm{j'}k} (x_{\perm{j}k} - x_{\perm{j-1}k})\\
+ =& f_k(x_{\perm{1}k}) + \sum_{j' < i} d_{\perm{j'}k} \sum_{i > j \geq j'} (x_{\perm{j}k} - x_{\perm{j-1}k}) \\
+ =& f_k(x_{\perm{1}k}) + \sum_{j' < i} d_{\perm{j'}k} (x_{\perm{i}k} - x_{\perm{j'}k}).
 \end{align*}
-We can write this more compactly in matrix notations.
+We can write this more compactly in matrix notation as
 \begin{equation*}
@@
 \left[ \begin{array}{c}
-f_k(x_{k1}) \\
-... \\
-f_k(x_{kn}) 
+f_k(x_{\perm{1}k}) \\
+\ldots \\
+f_k(x_{\perm{n}k})
 \end{array} \right] =
 \left[ \begin{array}{ccc}
-    |x_{k1} - x_{k(1)}|_+ & ... & |x_{k1} - x_{k(n-1)}|_+ \\
-    ... & & \\
-    |x_{kn} - x_{k(1)}|_+ & ... & |x_{kn} - x_{k(n-1)}|_+ 
+    |x_{k1} - x_{\perm{1}k}|_+ & \cdots & |x_{k1} - x_{\perm{n-1}k}|_+ \\
+    \cdots & & \\
+    |x_{kn} - x_{\perm{1}k}|_+ & \cdots & |x_{kn} - x_{\perm{n-1}k}|_+ 
 \end{array} \right]
 \left[ \begin{array}{c}
-    d_{k(1)} \\
-    ... \\
-    d_{k(n-1)}
+    d_{\perm{1}k} \\
+    \cdots \\
+    d_{\perm{n-1}k}
 \end{array} \right] 
@@
 
-Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) = |x_{ki} - x_{k(j)}|_+$, $d_k = (d_{k(1)} ,..., d_{k(n-1)})$, and $\mu_k = f_k(x_{k1})$.
+Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) =
+|x_{\perm{i}k} - x_{\perm{j}k}|_+$, $d_k = (d_{\perm{1}k} ,\ldots,
+d_{\perm{n-1}k})$, and $\mu_k = f_k(x_{\perm{1}k})$.
 
@@
      \label{opt:alternate_opt} \\
-\trm{s.t. }  & d_{k(2)}, \ldots , d_{k(n-1)} \geq 0  	
+\trm{s.t. }  & d_{\perm{2}k}, \ldots , d_{\perm{n-1}k} \geq 0  	
                \qquad \trm{(convexity)} \nonumber 
@@
       \label{opt:alternate_opt_concave}\\
- \trm{s.t.} & c_{k(2)}, \ldots, c_{k(n-1)} \leq 0 \qquad \trm{(concavity)} \nonumber
+ \trm{s.t.} & c_{\perm{2}k}, \ldots, c_{\perm{n-1}k} \leq 0 \qquad \trm{(concavity)} \nonumber
 \end{align}
@@
 This boundedness constraint can be easily added to our optimization program.
-In optimization~\ref{opt:alternate_opt}, we can enforce the boundedness condition by adding $p$ constraints: $\| \bar{\Delta}_k d_k \|_\infty \leq B$ for $k=1,...,p$.
+In optimization~\ref{opt:alternate_opt}, we can enforce the boundedness condition by adding $p$ constraints: $\| \bar{\Delta}_k d_k \|_\infty \leq B$ for $k=1,\ldots,p$.
 (similarly for optimization~\ref{opt:alternate_opt_concave}).

### 2014-09-11 tex/scam/optimization.tex
modified the order statistic notation

@@
 and the constraints $\sum_i f_{ki} = 0$.
-It is easy to verify that the constraints in (\ref{np}) satisfy the
+It is easy to verify that the constraints in \eqref{np} satisfy the
 supporting hyperplane constraints, since
@@
 
-The sparse convex additive model optimization in (\ref{np}) is a quadratic program with
+The sparse convex additive model optimization in \eqref{np} is a quadratic program with
 $O(np)$ variables and $O(np)$ constraints. 
@@
 Empirically, we observe that the algorithm converges in only a few
-cycles. We also implemented an ADMM solver for (\ref{np})
+cycles. We also implemented an ADMM solver for \eqref{np}
 \citep{Boyd:admm}, but found
@@
 
-After optimization, the function estimate for an input vector $\bds{x}$ is, according to (\ref{hyper}),
+After optimization, the function estimate for an input vector $\bds{x}$ is, according to \eqref{hyper},
 \begin{equation}
@@
 \subsection{Alternative Formulation}
-Optimization (\ref{np}) can be reformulated in terms of the second
+Optimization \eqref{np} can be reformulated in terms of the second
 derivatives.  We exploit this form in our theoretical analysis.
@@
 We can write this more compactly in matrix notation as
-\begin{equation*}
-\begin{split}
+\begin{align}
+\nonumber
 \left[ \begin{array}{c}
 f_k(x_{\perm{1}k}) \\
-\ldots \\
+f_k(x_{\perm{2}k}) \\
+\vdots \\
 f_k(x_{\perm{n}k})
-\end{array} \right] =
+\end{array} \right] &=
 \left[ \begin{array}{ccc}
-    |x_{k1} - x_{\perm{1}k}|_+ & \cdots & |x_{k1} - x_{\perm{n-1}k}|_+ \\
+    (x_{k1} - x_{\perm{1}k})_+ & \cdots & (x_{k1} - x_{\perm{n-1}k})_+ \\
     \cdots & & \\
-    |x_{kn} - x_{\perm{1}k}|_+ & \cdots & |x_{kn} - x_{\perm{n-1}k}|_+ 
+    (x_{kn} - x_{\perm{1}k})_+ & \cdots & (x_{kn} - x_{\perm{n-1}k})_+ 
 \end{array} \right]
@@
     d_{\perm{n-1}k}
-\end{array} \right] 
-+ \mu_k \equiv \Delta_k d_k + \mu_k
-\end{split}
-\end{equation*}
-
-Where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) =
-|x_{\perm{i}k} - x_{\perm{j}k}|_+$, $d_k = (d_{\perm{1}k} ,\ldots,
-d_{\perm{n-1}k})$, and $\mu_k = f_k(x_{\perm{1}k})$.
-
-Because $f_k$ has to be centered, $\mu_k = - \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k$, therefore:
+\end{array} \right] + \mu_k \\[10pt]
+& \equiv \Delta_k d_k + \mu_k
+\end{align}
+where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) =
+(x_{\perm{i}k} - x_{\perm{j}k})_+$, $d_k = (d_{\perm{1}k} ,\ldots,
+d_{\perm{n-1}k})$, and $\mu_k = f_k(x_{\perm{1}k}) \mathbf{1}_n$.
+Because $f_k$ has to be centered, $\mu_k = - \frac{1}{n}
+\mathbf{1}_n^\tran \Delta_k d_k$, and therefore
 \[
@@
 
-We can now reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
+We can now reformulate \eqref{np} as an equivalent optimization program with only centering and positivity constraints:
 \begin{align}
-\min_{d_k}& \frac{1}{2n} 
+\min_{d_k}\;\; & \frac{1}{2n} 
        \Bigl\| Y - \sum_{k=1}^p 
@@
      \label{opt:alternate_opt} \\
-\trm{s.t. }  & d_{\perm{2}k}, \ldots , d_{\perm{n-1}k} \geq 0  	
-               \qquad \trm{(convexity)} \nonumber 
+\trm{such that}\;\;  & d_{\perm{2}k}, \ldots , d_{\perm{n-1}k} \geq 0  	
+               \qquad \trm{(convexity).} \nonumber 
 \end{align}
 
-The decoupled concave postprocessing stage optimization is again similar.
-Suppose $\hat{d}_k$'s are the output of optimization~\ref{opt:alternate_opt}, define $\hat{r} = Y - \sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$.
+The decoupled concave postprocessing stage optimization is again
+similar. Specifically, suppose $\hat{d}_k$ is the output of
+optimization~\eqref{opt:alternate_opt}, and define the residual vector
+$\hat{r} = Y -
+\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$.  Then 
+for all $k$ such that $\hat{d}_k = 0$, the DC stage optimization is
+formulated as
 \begin{align}
-\textrm{for all}&\textrm{ $k$ such that $\hat{d}_k = 0$: }  \nonumber \\
-  \min_{c_k} & 
+  \min_{c_k}\;\; & 
       \frac{1}{2n} \Bigl \| \hat{r} - \Delta_k c_k \Bigr \|_2^2
@@
       \label{opt:alternate_opt_concave}\\
- \trm{s.t.} & c_{\perm{2}k}, \ldots, c_{\perm{n-1}k} \leq 0 \qquad \trm{(concavity)} \nonumber
+ \trm{such that }\;\; & c_{\perm{2}k}, \ldots, c_{\perm{n-1}k} \leq 0 \qquad \trm{(concavity).} \nonumber
 \end{align}
 
-We can use either the off-centered $\Delta_k$ matrix or the centered $\bar{\Delta}_k$ matrix because the concave estimations are decoupled and hence suffer no identifiability problems.\\
+We can use either the off-centered $\Delta_k$ matrix or the centered
+$\bar{\Delta}_k$ matrix because the concave estimations are decoupled
+and hence do not suffer identifiability under additive constants.
 
 \begin{remark}
-in sparsistency analysis, we assume that $B$, an upper bound to $\| f^*_k \|_\infty$, is known and that we constrain our estimate $\hat{f}$ to obey the same boundedness condition, that is, for each $k$, we require that $\|\hat{f}_k\|_\infty \leq B$.
-This boundedness constraint can be easily added to our optimization program.
-In optimization~\ref{opt:alternate_opt}, we can enforce the boundedness condition by adding $p$ constraints: $\| \bar{\Delta}_k d_k \|_\infty \leq B$ for $k=1,\ldots,p$.
-(similarly for optimization~\ref{opt:alternate_opt_concave}).
-We emphasize that we use the boundedness constraint only in our theoretical analysis; all of our experiments do not impose any boundedness condition.
+  In our sparsistency analysis, we assume that an upper bound $B$ to
+  $\| f^*_k \|_\infty$ is known, and that we constrain our estimate
+  $\hat{f}$ to obey the same boundedness condition.  That is, for each
+  $k$, we require that $\|\hat{f}_k\|_\infty \leq B$. This boundedness
+  constraint can be easily added to our optimization program. In
+  optimization~\eqref{opt:alternate_opt}, we can enforce the boundedness
+  condition by adding $p$ constraints $\| \bar{\Delta}_k d_k
+  \|_\infty \leq B$ for $k=1,\ldots,p$ (and similarly for
+  optimization~\eqref{opt:alternate_opt_concave}). We emphasize that we
+  use the boundedness constraint only in our theoretical analysis; 
+  our experiments do not impose any such condition.
 \end{remark}

### 2014-09-11 tex/scam/optimization.tex
minor edits

@@
 $\bar{\Delta}_k$ matrix because the concave estimations are decoupled
-and hence do not suffer identifiability under additive constants.
+and hence are not subject to non-identifiability under additive constants.
 

### 2014-09-11 tex/scam/sparsistency.tex
minor edits

@@
 
-We divide our analysis into two parts. We first establish a sufficient deterministic condition for sparsistency.  We then consider the
-stochastic setting and argue that the deterministic conditions hold with high probability.
-In all of our results and analysis, we let $c, C$ represent absolute constants; the actual values of $c,C$ could change from line to line.
+We divide our analysis into two parts. We first establish a sufficient
+deterministic condition for consistency of the sparsity pattern
+selection procedure---a property sometimes called \textit{sparsistency}.
+We then consider the
+stochastic setting and argue that the deterministic conditions hold
+with high probability. Note that in all of our results and analysis, we let $c,
+C$ represent absolute constants; the actual values of $c,C$ may change from line to line.
 
@@
 
-We construct an additive convex solution $\{\hat{d}_k\}_{k=1,...,p}$ that is zero for $k \in S^c$ and show that it satisfies the KKT conditions for optimality of optimization~\ref{opt:alternate_opt}.
-We define $\hat{d}_k$ for $k \in S$ to be a solution to the restricted regression (defined below).
-We will then also show that $\hat{c}_k = 0$ satisfies the optimality condition of optimization~\ref{opt:alternate_opt_concave} for all $k \in S^c$.
+We construct an additive convex solution $\{\hat{d}_k\}_{k=1,...,p}$
+that is zero for $k \in S^c$, where $S$ is the set of relevant
+variables, and show that it satisfies the KKT
+conditions for optimality of optimization~\eqref{opt:alternate_opt}. We
+define $\hat{d}_k$ for $k \in S$ to be a solution to the restricted
+regression (defined below). We also show that $\hat{c}_k =
+0$ satisfies the optimality condition of
+optimization~\eqref{opt:alternate_opt_concave} for all $k \in S^c$.
 
@@
 \label{def:restricted_regression}
-We define as \emph{restricted regression} where we restrict the indices $k$ in
-optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$:
+We define the \emph{restricted regression} problem 
 \[
@@
 \]
+where we restrict the indices $k$ in
+optimization \eqref{opt:alternate_opt} to lie in the set $S$ of true
+relevant variables.
 \end{definition}
 
-\begin{theorem} (Deterministic setting)
+\begin{theorem}[Deterministic setting]
 \label{thm:deterministic}
 Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression as defined above.
-Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\
-
+Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. 
 Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
-\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\
-
-Then the following are true:
+\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on
+the coordinates of the 
+$i$-th largest to the $n$-th largest entries of $X_k$ and 0
+elsewhere.  Then the following two statements hold.
 \begin{enumerate}
-\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}.
-Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
-\item For all $k \in S^c$, the solution $\hat{c}_k$ to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
+\item Let $\hat{d}_k = 0$ for $k \in S^c$.  Then
+  \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to
+  optimization~\eqref{opt:alternate_opt}. Furthermore, any solution to
+  the optimization program \eqref{opt:alternate_opt} must be zero on
+  $S^c$.
+\item For all $k \in S^c$, the solution $\hat{c}_k$ to optimization~\eqref{opt:alternate_opt_concave} must be zero.
 \end{enumerate}
@@
 
-This result holds regardless of whether we impose the boundedness conditions in optimization~\ref{opt:alternate_opt} and~\ref{opt:alternate_opt_concave} or not.
-The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.\\
+This result holds regardless of whether or not we impose the boundedness conditions in optimization~\eqref{opt:alternate_opt} and~\eqref{opt:alternate_opt_concave}.
+The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.
 
-Theorem~\ref{thm:deterministic} allows us to analyze false negative
-rates and false positive rates separately. To control false positives,
-we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression. \\
+Theorem~\ref{thm:deterministic} allows us to separately analyze the false negative
+rates and false positive rates. To control false positives,
+we analyze the condition on $\lambda_n$ for $k \in S^c$. To control
+false negatives, we analyze the restricted regression.
 
-The proof of theorem~\ref{thm:deterministic} looks at KKT conditions of optimization~\ref{opt:alternate_opt}, similar to the now standard \emph{primal-dual witness} technique~\cite{wainwright2009sharp}.
-We cannot derive analogous \emph{mutual incoherence} conditions because the estimation is nonparametric -- even the low dimensional restricted regression has $s(n-1)$ variables.
-The details of the proof are in section~\ref{sec:deterministic_proof} of the Appendix.
+The proof of Theorem~\ref{thm:deterministic} analyses the KKT
+conditions of optimization~\eqref{opt:alternate_opt}.  This parallels
+the now standard \emph{primal-dual witness}
+technique~\cite{wainwright2009sharp}. However, we cannot derive analogous
+\emph{mutual incoherence} conditions because the estimation is
+nonparametric---even the low dimensional restricted regression has
+$s(n-1)$ variables. The details of the proof are given in
+Section~\ref{sec:deterministic_proof} of the Appendix.
 
@@
 
-We let $S = \{ k = 1,...,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
+We let $S = \{ k = 1,...,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
 
@@
 
-And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\ref{opt:alternate_opt_concave} are zero.
-\\
+And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\eqref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\eqref{opt:alternate_opt_concave} are zero.
 \end{theorem}
@@
 
-\begin{theorem} (Controlling false negatives) \\
+\begin{theorem} (Controlling false negatives) 
 \label{thm:false_negative}
@@
 Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.
-Let $\tilde{\sigma}$ denote $\max(\sigma, B)$.\\
+Let $\tilde{\sigma}$ denote $\max(\sigma, B)$.
 

### 2014-09-11 tex/scam/optimization.tex
minor edits

@@
 \begin{remark}
-  In our sparsistency analysis, we assume that an upper bound $B$ to
+  In our analysis, we assume that an upper bound $B$ to
   $\| f^*_k \|_\infty$ is known, and that we constrain our estimate

### 2014-09-12 tex/scam/appendix.tex
minor edits

@@
 
-Because $w_i$ is subgaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
 By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at most $1 - \delta$.
@@
 
-Because $w_i$ is subgaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $\sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
+Because $w_i$ is sub-Gaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $\sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
 
@@
 
-Because $w$ is a subgaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
+Because $w$ is a sub-Gaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
 Using union bound again, we have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has probability at most $1-\delta$.
@@
 
-\textbf{Sub-Exponential} random variable is the square of a subgaussian random variable\cite{vershynin2010introduction}.
+\textbf{Sub-Exponential} random variable is the square of a sub-Gaussian random variable\cite{vershynin2010introduction}.
 
@@
 \begin{corollary}
-Let $w_1,...,w_n$ be $n$ independent subgaussian random variables with subgaussian scale $\sigma$.
+Let $w_1,...,w_n$ be $n$ independent sub-Gaussian random variables with sub-Gaussian scale $\sigma$.
 
@@
 Suppose $w = (w_1, ..., w_n)$ is a vector of i.i.d.
-subgaussian random variables with scale $\sigma$.\\
+sub-Gaussian random variables with scale $\sigma$.\\
 

### 2014-09-12 tex/scam/sparsistency.tex
minor edits

@@
 the now standard \emph{primal-dual witness}
-technique~\cite{wainwright2009sharp}. However, we cannot derive analogous
+technique~\citep{wainwright2009sharp}. However, we cannot derive analogous
 \emph{mutual incoherence} conditions because the estimation is
@@
 
-We use the following statistical setting:
+In the probabilistic setting we treat the covariates as random.  We
+adopt the following standard setup:
 
-\begin{packed_enum}
-\item Let $F$ be a distribution supported and positive on $\mathcal{X}=[-b,b]^p$. Let $X^{(1)},..., X^{(n)} \sim F$ be iid.
-\item Let $Y = f_0(X) + w$ where $w$ is zero-mean noise. Let $Y^{(1)},...,Y^{(n)}$ be iid.
-\item Let $S_0 = \{1,...,s_0\}$ denote the relevant variables where $s_0 \leq p$, i.e.,
-  $f_0(X) = f_0(X_{S_0})$.
-\end{packed_enum}
+\begin{enumerate}
+\item The data $X^{(1)},..., X^{(n)} \sim F$ are iid from
+a distribution $F$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$. 
+\item The response is $Y = f_0(X) + W$ where $W$ is
+  independent, zero-mean noise; thus $Y^{(i)} = f_0(X^{(i)}) + W^{(i)}$.
+\item The regression function $f_0$ satisfies
+$f_0(X) = f_0(X_{S_0})$, where $S_0 = \{1,...,s_0\}$ is the set of
+relevant variables.
+\end{enumerate}
 
-Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Define $\mathcal{C}^{p}$ as the set of convex additive function
-$\mathcal{C}^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
-   f_k \in \mathcal{C}^1 \} $
-Let $f^*(x) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk minimizer:
-$f^* \equiv \arg\min_{f \in \mathcal{C}^p} \E\big(f_0(X) - f^*(X) \big)^2$.\\
-
-Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and let 
-$g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X) - g_k(X_k) \big)^2$. \\
-
+Let $\mathcal{C}^1$ denote the set of univariate convex functions
+supported on $[-b,b]$, 
+and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
+$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
+   f_k \in \mathcal{C}^1 \} $.  
+Let $f^*(x) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
+minimizer in $\mathcal{C}_1^p$, 
+\begin{equation}
+f^* \equiv \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
+\big)^2.
+\end{equation}
+Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
+\begin{equation}
+g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
+- g_k(X_k) \big)^2.
+\end{equation}
 We let $S = \{ k = 1,...,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
@@
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
-\item[A4:] $w$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
+\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
 \end{packed_enum}
@@
 \begin{align*}
-\alpha_f &= \inf_{f \in \mathcal{C}^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+\alpha_f &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
@@
 
-\begin{theorem} (Controlling false positives) \\
+\begin{theorem}[Controlling false positives]
 \label{thm:false_positive}

### 2014-09-12 tex/scam/optimization.tex
minor edits

@@
 optimization~\eqref{opt:alternate_opt}, and define the residual vector
-$\hat{r} = Y -
-\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$.  Then 
-for all $k$ such that $\hat{d}_k = 0$, the DC stage optimization is
+\begin{equation}
+\hat{r} = Y -
+\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k.
+\label{eq:residual}
+\end{equation}  
+Then  for all $k$ such that $\hat{d}_k = 0$, the DC stage optimization is
 formulated as

### 2014-09-12 tex/scam/sparsistency.tex
minor edits

@@
 
-We construct an additive convex solution $\{\hat{d}_k\}_{k=1,...,p}$
+We construct an additive convex solution $\{\hat{d}_k\}_{k=1,\ldots,p}$
 that is zero for $k \in S^c$, where $S$ is the set of relevant
@@
 \min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
-   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, ..., d_{k,n-1} \geq 0
+   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, \ldots, d_{k,n-1} \geq 0
 \]
@@
 Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. 
-Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
+Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > | \frac{1}{2n}
 \hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on
@@
 \item Let $\hat{d}_k = 0$ for $k \in S^c$.  Then
-  \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to
+  \{$\hat{d}_k\}_{k=1,\ldots,p}$ is an optimal solution to
   optimization~\eqref{opt:alternate_opt}. Furthermore, any solution to
@@
 \begin{enumerate}
-\item The data $X^{(1)},..., X^{(n)} \sim F$ are iid from
+\item The data $X^{(1)},\ldots, X^{(n)} \sim F$ are iid from
 a distribution $F$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$. 
@@
 \item The regression function $f_0$ satisfies
-$f_0(X) = f_0(X_{S_0})$, where $S_0 = \{1,...,s_0\}$ is the set of
+$f_0(X) = f_0(X_{S_0})$, where $S_0 = \{1,\ldots,s_0\}$ is the set of
 relevant variables.
@@
 \end{equation}
-We let $S = \{ k = 1,...,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
+We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$.
 
@@
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
-\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$, i.e. for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
+\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
 \end{packed_enum}
-By assumption A1, $f^*_k$ is must be zero for $k\notin \{1,...,s\}$.
-
+By assumption A1, $f^*_k$ is must be zero for $k\notin S$.
 We define $\alpha_f, \alpha_g$ as a measure of the signal strength of the weakest variable:
@@
 \end{align*}
-
-Intuitively, if $\alpha_f$ is smaller, then it is easier to make a false omission in the additive convex stage of the procedure.
-If $\alpha_g$ is smaller, then it is easier to make a false omission in the decoupled concave stage of the procedure.
+These play the role of the absolute value of the smallest nonzero
+coefficient in the true linear model in lasso theory.  Intuitively, if
+$\alpha_f$ is small, then it is easier to make a false omission in the
+additive convex stage of the procedure. If $\alpha_g$ is small, then
+it is easier to make a false omission in the decoupled concave stage
+of the procedure.
 
@@
 \label{thm:false_positive}
-Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-Suppose $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{12}{np}$, for all $k \in S^c$, and for all $i'=1,...,n$:
-\[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|
-\]
-
-And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\eqref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\eqref{opt:alternate_opt_concave} are zero.
+Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
+and suppose 
+\begin{equation}
+\lambda_n \geq 8 s_0 \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
+\end{equation}  
+Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
+S^c$, and for all $i'=1,\ldots, n$,
+\begin{equation}
+\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
+\end{equation}
+and for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\eqref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\eqref{opt:alternate_opt_concave} are zero. 
 \end{theorem}
@@
 The proof of Theorem~\ref{thm:false_positive} exploits independence of
-$\hat{r}$ and $X_k$ from A1; when $\hat{r}$ and $X_k$ are independent, $\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random coordinates of $\hat{r}$.
-We can then uses the concentration of measure result for sampling without replacement to argue that $| \frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high probability.
-The full proof of
-Theorem~\ref{thm:false_positive} is in
+$\hat{r}$ and $X_k$ from A1; when $\hat{r}$ and $X_k$ are independent,
+$\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random
+coordinates of $\hat{r}$.  We can then use concentration of
+measure results for sampling without replacement to argue that $|
+\frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high
+probability. The full proof of Theorem~\ref{thm:false_positive} is in
 Section~\ref{sec:false_positive_proof} of the Appendix.

### 2014-09-12 tex/scam/sparsistency.tex
minor edits

@@
 \end{equation}
-and for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\eqref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\eqref{opt:alternate_opt_concave} are zero. 
+and for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero. 
 \end{theorem}

### 2014-09-15 tex/scam/sparsistency.tex
minor edits

@@
 We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$. 
-
 Each of our theorems will use a subset of the following assumptions:
@@
 By assumption A1, $f^*_k$ is must be zero for $k\notin S$.
-We define $\alpha_f, \alpha_g$ as a measure of the signal strength of the weakest variable:
+We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
 \begin{align*}
-\alpha_f &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
         \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
-\alpha_g &=   \min_{k \in S \,:\, g^*_k \neq 0}
+\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
       \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
@@
 \end{align*}
-These play the role of the absolute value of the smallest nonzero
+These quantities play the role of the absolute value of the smallest nonzero
 coefficient in the true linear model in lasso theory.  Intuitively, if
-$\alpha_f$ is small, then it is easier to make a false omission in the
-additive convex stage of the procedure. If $\alpha_g$ is small, then
+$\alpha_{+}$ is small, then it is easier to make a false omission in the
+additive convex stage of the procedure. If $\alpha_{-}$ is small, then
 it is easier to make a false omission in the decoupled concave stage
@@
   very weak assumptions on the true regression function $f_0$ in
-  A2. In particular, we do not assume that $f_0$ is additive. 
+  A2. In particular, we do not assume that $f_0$ is additive. In
+  important direction for future work is to weaken this assumption.
+  Our simulation experiments indicate that the procedure can be
+  effective even when the relevant and irrelevant variables are correlated.
   %Strong assumptions on the covariates are not uncommon in nonparametric
@@
 \frac{1}{n} \hat{r}^\tran\mathbf{1}_{(i':n)}|$ is small with high
-probability. The full proof of Theorem~\ref{thm:false_positive} is in
+probability. The result of Theorem~\ref{thm:deterministic} is then
+used. The full proof of Theorem~\ref{thm:false_positive} is in
 Section~\ref{sec:false_positive_proof} of the Appendix.
 
-\begin{theorem} (Controlling false negatives) 
+\begin{theorem}[Controlling false negatives]
 \label{thm:false_negative}
-Suppose assumptions A1-A4 hold.
-Let $\hat{f}$ be any AC solution to the restricted regression with $B$-boundedness constraint and let $\hat{g}_k$'s be any DC solution to the restricted regression with $B$-boundedness constraint.
-Let $\tilde{\sigma}$ denote $\max(\sigma, B)$.
-
-Suppose $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $n$ is large enough such that $\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s^5$.
-
-Suppose 
-$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ where $c$ is a constant.
-
-Then, with probability at least $1 - \frac{C}{n}$ for some constant $C$, we have that for all $k \in S$, $\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$.
-
+Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to
+the restricted regression with $B$-boundedness constraint, and let
+$\hat{g}_k$ be any DC solution to the restricted regression with
+$B$-boundedness constraint. Let $\tilde{\sigma}$ denote $\max(\sigma,
+B)$.  Suppose 
+\begin{equation}
+\lambda_n \leq 9 s_0 \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
+\end{equation}
+and that $n$ is sufficiently large so that 
+\begin{equation}
+\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s_0^5.
+\end{equation}
+Assume that the signal-to-noise ratio satisfies
+\begin{align}
+\frac{\alpha_{+}}{\tilde{\sigma}} & \geq c B^2
+\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}\\
+\frac{\alpha_{-}^2}{\tilde{\sigma}} &\geq c B^2
+\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}
+\end{align}
+where $c$ is a constant.  Then with probability at least $1 -
+\frac{C}{n}$ for some constant $C$, 
+$\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$ 
+for all $k \in S$.
 \end{theorem}
@@
 
-Combining Theorem~\ref{thm:false_positive} and
+Combining Theorems~\ref{thm:false_positive} and
 ~\ref{thm:false_negative} 
-we have the following result.
+we obtain the following result.
 \begin{corollary}
-Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution and $\hat{g}_k$'s be any DC solution, both with $B$-boundedness constraints, both with 
-$\lambda = \Theta\big( s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np} \big) $. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-Suppose 
-$\alpha_f/\tilde{\sigma} \geq c B^2 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\alpha_g^2/\tilde{\sigma} \geq c B^4 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$.
-
-Then, for all large enough $n$ such that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$, we have that with probability at least $1-\frac{C}{n}$:
-\begin{align*}
-\hat{f}_k \neq 0 \trm{ or } \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
-\hat{f}_k = 0 \trm{ and } \hat{g}_k = 0 & \trm{ for all } k \notin S
-\end{align*}
-
+  Suppose the assumptions of Theorem~\ref{thm:false_positive} and
+  Theorem~\ref{thm:false_negative} hold.  
+Then with probability at least $1-\frac{C}{n}$
+\begin{align}
+\hat{f}_k \neq 0 \trm{ or }\; \hat{g}_k \neq 0 &\trm{ for all } k \in S\\
+\hat{f}_k = 0 \trm{ and }\; \hat{g}_k = 0 & \trm{ for all } k \notin S
+\end{align}
 where $c,C$ are constants.
@@
 \end{corollary}
-The above corollary implies that sparsistency is achievable at the same exponential scaling of the ambient dimension $p = O(\exp(n^c)), c<1$ rate as parametric models.
-The cost of nonparametric modeling is reflected in the scaling with respect to $s$, which can only scale at $o(n^{4/25})$.
+The above corollary implies that sparsistency is achievable at the
+same exponential scaling of the ambient dimension scaling attained
+with parametric models, $p = O(\exp(n^c))$ for $c<1$.  The cost of
+nonparametric modeling through shape constraints 
+is reflected in the scaling with respect to
+the number of relevant variables, which can scale as $s_0 = o(n^{4/25})$.
 
 \begin{remark}
-\citet{dalalyan:12} have shown that under tradtional smoothness constraints, even with a product distribution, variable selection is achievable only if $n > O(e^s)$.
-It is interesting to observe that because of additive faithfulness, the convexity assumption enables a much better scaling of $n = O(\textrm{poly}(s))$, demonstrating that geometric constraints can be quite different from the previously studied smoothness conditions.
+  \citet{dalalyan:12} have shown that under tradtional smoothness
+  constraints, even with a product distribution, variable selection is
+  achievable only if $n > O(e^{s_0})$. It is interesting to observe that
+  because of additive faithfulness, the convexity assumption enables a
+  much better scaling of $n = O(\textrm{poly}(s_0))$, demonstrating that
+  geometric constraints can be quite different from the previously
+  studied smoothness conditions.
 \end{remark}

### 2014-09-15 tex/scam/paper.tex
minor edits

--- 2014-05-05 tex/scam/paper.tex
@@
-\documentclass{article}
+\documentclass[12pt,pdftex,aos]{imsart}
+%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
+
+\RequirePackage[OT1]{fontenc}
 \usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
+\RequirePackage{hypernat}
+\usepackage[ruled,section]{algorithm}
+\usepackage[noend]{algorithmic}
+\usepackage{graphicx}
 \usepackage[hscale=0.7,vscale=0.8]{geometry}
-
 \usepackage{subfigure}
@@
 \usepackage{hyperref}
-\usepackage{authblk}
-
 \usepackage{yhmath}
 
-\bibliographystyle{plainnat}
+\renewcommand{\baselinestretch}{1.1}
+%\parskip12pt
+%\parindent0pt
+\setcounter{tocdepth}{2}
 
-\title{Variable Selection in Convex Function Estimation}
-
-%\author{
-%Min Xu, Minhua Chen, John Lafferty
-%}
-
-\author[1]{Min Xu}
-\author[2,3]{Minhua Chen}
-\author[2,3]{John Lafferty}
-
-\affil[1]{Machine Learning Department, Carnegie Mellon University}
-\affil[2]{Department of Statistics, University of Chicago}
-\affil[3]{Department of Computer Science, University of Chicago}
-
-% ENVIRONMENTS
-\numberwithin{equation}{section}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheoremstyle{remark}{\topsep}{\topsep}%
-     {\normalfont}% Body font
-     {}           % Indent amount (empty = no indent, \parindent = para indent)
-     {\bfseries}  % Thm head font
-     {.}          % Punctuation after thm head
-     {.5em}       % Space after thm head (\newline = linebreak)
-     {\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}% Thm head spec
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{assumption}{Assumption}[section]
-\newtheorem{definition}{Definition}[section]
+\input{macros}
 
@@
 
-% min's macros
-\mathchardef\mh="2D
+\begin{frontmatter}
+\title{Faithful Variable Screening for\\ High-Dimensional Convex Regression}
+\runtitle{Faithful Variable Screening for Convex Regression}
 
-% John's macros
-\def\X{\mathcal{X}}
-\def\comma{\unskip,~}
-\def\truep{p^*}
-\def\div{\|\,}
-\long\def\comment#1{}
-\def\reals{{\mathbb R}}
-\def\P{{\mathbb P}}
-\def\E{{\mathbb E}}
-\def\Cov{\mathop{\text{Cov}}}
-\def\supp{\mathop{\text{supp}\kern.2ex}}
-\def\argmin{\mathop{\text{\rm arg\,min}}}
-\def\arginf{\mathop{\text{\rm arg\,inf}}}
-\def\argmax{\mathop{\text{\rm arg\,max}}}
-\let\tilde\widetilde
-\def\csd{${}^*$}
-\def\mld{${}^\dag$}
-\def\dos{${}^\ddag$}
-\def\W{\widetilde Y}
-\def\Z{\widetilde X}
-\let\hat\widehat
-\let\tilde\widetilde
-\def\given{{\,|\,}}
-\def\ds{\displaystyle}
-\def\bs{\backslash}
-\def\1{{(1)}}
-\def\2{{(2)}}
-\def\pn{{(n)}}
-\def\ip{{(i)}}
-\def\Xbar{\overline{X}}
-\def\except{\backslash}
-\def\npn{\mathop{\textit{NPN\,}}}
-\def\i{{(i)}}
-\def\cE{{\mathcal{C}}}
-\def\cM{{\mathcal{M}}}
-\def\cF{{\mathcal{F}}}
-\def\cP{{\mathcal{P}}}
-\def\cG{{\mathcal{G}}}
-\def\tr{\mathop{\text{tr}}}
-\long\def\comment#1{}
-\def\ti#1{#1}
-\def\titi#1{\textit{#1}}
-\def\cram{{\sc cram}}
-\def\spam{{\small\sc SpAM}}
-\def\diag{\mathop{\rm diag}}
-\def\ones{\mathbf{1}}
-\def\threebars{\mbox{$|\kern-.25ex|\kern-.25ex|$}}
-\def\fatnorm#1{\threebars #1 \threebars}
-\def\rank{\mathop{\rm rank}}
-\def\S{\mathcal{S}}
-\def\H{\mathcal{H}}
-\def\K{{K}}
-\def\rank{\mathop{\rm rank}}
-\def\half{{1/2}}
-\def\Y{\mathbb{Y}}
-\def\M{\mathbb{M}}
-\def\F{\mathbb{F}}
-\def\pinv{{-1}}
-%\def\ones{\mathds{1}}
-%\def\ones{1}
-\def\Res{Z}
-\def\Proj{P}
-\def\cN{{\mathcal N}}
-\def\cT{{\mathcal H}}
-\def\coloneqq{:=}
-\def\mathbf#1{\mbox{\boldmath $#1$}} 
-\def\bar#1{\overline{#1}}
+\begin{aug}
+\vskip10pt
+\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
+\comma 
+\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
+\and
+\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{
+\begin{tabular}{ccc}
+\\[10pt]
+Machine Learning Department & Department of Statistics & Department of Statistics\\
+Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
+& & University of Chicago
+\end{tabular}
+%\\[20pt]
+%\printead{e1,e2,e3}
+}
+\end{aug}
+
+\input{abstract}
+%\tableofcontents
+\vskip20pt
+\end{frontmatter}
 
 \maketitle
-
-\begin{abstract}
-We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points. 
-\end{abstract}
 \vskip10pt
 
-% \tableofcontents
+%\tableofcontents
 
 \input{introduction}
-\input{related_work}
 \input{summary}

### 2014-09-16 tex/scam/experiments.tex
added section label
new plots
minor edits

@@
+\def\x{x}
+\def\Q{Q}
+\def\bds#1{#1}
+
 \section{Experiments}
+\label{sec:thesims}
 %\subsection{Simulations}
-We first illustrate our methods using a simulation of the following regression problem
+We first illustrate our methods using a simulation of the model
 \begin{equation}\nonumber
-         y_i = \bds{x}_{iS}^{\top}\bds{Q}\bds{x}_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
+         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
 \end{equation}
-Here $\bds{x}_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0},\bds{I}_{p})$, 
-$\bds{x}_{iS}$ is a subset of $\bds{x}_i$ with dimension $|S|=5$, where $S$ represents the active feature set, and 
-$\epsilon_i$ is the additive noise drawn from $\mathcal{N}(0,1)$. 
-$\bds{Q}$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
-Notice that if $\bds{Q}$ is diagonal, then the true function is convex additive; otherwise the true function is convex but not additive.
-For all the simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.
+Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0},\bds{I}_{p})$, 
+$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
+represents the relevant variable set, and 
+$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
+The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
+Note that if $\Q$ is diagonal, then the true function is convex
+additive; 
+otherwise the true function is convex but not additive.
+For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.
 
-In the first simulation, we set $\bds{Q}=\bds{I}_{|S|}$ (the additive
+In the first simulation, we set $\Q=\bds{I}_{|S|}$ (the additive
 case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256,512$.
@@
 In the second simulation, we study the case in which the true function
-is convex but not additive. We generate four $\bds{Q}$ matrices
+is convex but not additive. We generate four $\Q$ matrices
 plotted in Figure \ref{Support}(b), where the diagonal elements are all $1$ and
@@
 In the third simulation, we study the case of correlated design, where
-$\bds{x}_{i}$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
+$\x_{i}$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
 instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
-$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\bds{Q}$ with
+$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$ with
 $\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=02, 0.4,
@@
 %                \includegraphics[width=\textwidth]{figs/Q}
-%                \caption{Four $\bds{Q}$ matrices.}
+%                \caption{Four $\Q$ matrices.}
 %                \label{Q}
@@
 %\includegraphics[width=.27\textwidth]{figs/Curve3}  \\
-%(a) additive model & (b) four $\bds{Q}$ matrices &
+%(a) additive model & (b) four $\Q$ matrices &
 %(c) non-additive models & (d) correlated design
@@
 \begin{tabular}{cccc}
-\hskip-20pt
-\includegraphics[width=.29\textwidth]{figs/Curve1} &
-\hskip-20pt
-\includegraphics[width=.29\textwidth]{figs/Q} &
-\hskip-20pt
-\includegraphics[width=.29\textwidth]{figs/Curve2} &
-\hskip-20pt
-\includegraphics[width=.29\textwidth]{figs/Curve3}  \\
+\hskip-10pt
+\includegraphics[width=.26\textwidth]{figs/Curve1} &
+\hskip-10pt
+\includegraphics[width=.26\textwidth]{figs/Q} &
+\hskip-10pt
+\includegraphics[width=.26\textwidth]{figs/Curve2} &
+\hskip-10pt
+\includegraphics[width=.26\textwidth]{figs/Curve4}  \\
 \hskip-10pt (a) additive model & 
-\hskip-10pt (b) four $\bds{Q}$ matrices &
+\hskip-10pt (b) four $\Q$ matrices &
 \hskip-10pt (c) non-additive models & 

### 2014-09-17 tex/scam/experiments.tex
minor edits

@@
 \def\bds#1{#1}
+\def\tts#1{\texttt{\small #1}}
 
@@
 In the first simulation, we set $\Q=\bds{I}_{|S|}$ (the additive
-case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256,512$.
+case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
 For each $(n,p)$ combination, we generate $200$ independent data
-sets. For each data set we use SCAM to infer the model parameterized
-by $\bds{h}$ and $\bds{\beta}$; see equation \eqref{np}. If
-$\|\bds{\beta}_{k\cdot}\|_{\infty}<10^{-8}\ (\forall k\not\in{}S)$ and
-$\|\bds{\beta}_{k\cdot}\|_{\infty}>10^{-8}\ (\forall k\in{}S)$, then
-we declare correct support recovery. We then plot the probability of
+sets. For each data set we use the AC/DC algorithm to estimate the model support.
+We plot the probability of
 support recovery over the $200$ data sets in Figure \ref{Support}(a).  We
-observe that SCAM performs consistent variable selection when the true
-function is convex additive.  
-To give the reader a
-sense of the running speed, the code runs in about $2$ minutes on one
-data set with $n=1000$ and $p=512$, on a MacBook with 2.3 GHz Intel
-Core i5 CPU and 4 GB memory.
+observe that the algorithm performs consistent variable selection when the true
+function is convex additive.    To give the reader a
+sense of the running speed, for a 
+data set with $n=1000$ and $p=512$, the code runs in roughly two 
+minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.
 
@@
 is convex but not additive. We generate four $\Q$ matrices
-plotted in Figure \ref{Support}(b), where the diagonal elements are all $1$ and
-the off-diagonal elements are $0.5$ with probability $\alpha$
+plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
+the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
 ($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We again run the SCAM optimization on $200$
+$n=100,200,\ldots,1000$. We again run the AC/DC optimization on $200$
 independently generated data sets and plot the probability of recovery
-in Figure \ref{Support}(c). The results demonstrate that SCAM performs
+in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
 consistent variable selection even if the true function is not additive (but
@@
 
-In the third simulation, we study the case of correlated design, where
-$\x_{i}$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
+In the third simulation, we study the case of a correlated design, where
+$\x_i$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
 instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
 $\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$ with
-$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=02, 0.4,
-0.6, 0.8$ are depicted in Figure \ref{Support}(d). As can be seen, for
-design of moderate correlation, SCAM can still select relevant
+$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
+0.6, 0.8$ are shown in Figure \ref{Support}(d). As can be seen, for
+design of moderate correlation, AC/DC can still select relevant
 variables well.
@@
 indicating housing values in suburbs of Boston. The data and detailed description
-can be found on the UCI Machine Learning Repository website~\footnote{\texttt{http://archive.ics.uci.edu/ml/datasets/Housing}}.
+can be found on the UCI Machine Learning Repository website\footnote{\url{http://archive.ics.uci.edu/ml/datasets/Housing}}.
 
-We first use all $n=506$ samples (with normalization) to train SCAM, using
-a set of candidate $\{\lambda^{(t)}\}$ with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
-we obtain a subgradient matrix $\bds{\beta}^{(t)}$ with $p=13$ rows. The non-zero
-rows in this matrix indicate the variables selected using $\lambda^{(t)}$. 
-We plot $\|\bds{\beta}^{(t)}\|_{\infty}$ and the row-wise mean of $\bds{\beta}^{(t)}$ versus the normalized
-norm $\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$ in Figures \ref{Boston}(a) and \ref{Boston}(b).
-As a comparison we plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
-From the figures we observe that the first three variables selected by SCAM
-and LASSO are the same: LSTAT, RM and PTRATIO, which is consistent with previous findings~\cite{SpAM:07}.
-The fourth variable selected by SCAM is TAX (with $\lambda^{(t)}=0.09$).
-We then refit SCAM with only these four variables without regularization, and plot the inferred additive
-functions in Figure \ref{Boston}(e). As can be seen, these functions contain clear nonlinear effects which cannot be captured
-by LASSO. The shapes of these functions are in agreement with those obtained by SpAM~\cite{SpAM:07}.
+We first use all $n=506$ samples (with normalization) to fit AC/DC,
+using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
+with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
+we obtain a subgradient matrix $\bds{\beta}^{(t)}$ with $p=13$
+rows. The non-zero rows in this matrix indicate the variables selected
+using $\lambda^{(t)}$.  We plot $\|\bds{\beta}^{(t)}\|_{\infty}$ and
+the row-wise mean of $\bds{\beta}^{(t)}$ versus the normalized norm
+$\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$
+in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
+plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
+From the figures we observe that the first three variables selected by
+AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
+consistent with previous findings~\citep{SpAM:07}.  The fourth
+variable selected by AC/DC is \tts{TAX} (with $\lambda^{(t)}=0.09$).
+We then refit AC/DC with only these four variables without
+regularization, and plot the estimated additive functions in Figure
+\ref{Boston}(e). As can be seen, these functions contain clear
+nonlinear effects which cannot be captured by LASSO. The shapes of
+these functions are in agreement with those obtained by
+SpAM~\citep{SpAM:07}.
 
-Next, in order to quantitatively study the predictive performance, we run 10 times 5-fold cross validation, following
-the same procedure described above (training, variable selection and
-refitting).  A plot of the mean and standard
-deviation of the predictive Mean Squared Error (MSE) in in Figure \ref{Boston}(d). Since for SCAM the same $\lambda^{(t)}$ may lead to
-slightly different number of selected features in different folds and runs, the values on the x-axis (average number of selected features)
-for SCAM are not necessarily integers. Nevertheless, the figure clearly shows that SCAM has a much lower predictive MSE than LASSO. 
-We also compared the performance of SCAM with that of Additive Forward Regression (AFR) presented in~\cite{Xi:09}, and found that they are similar.
-The main advantages of SCAM compared with AFR and SpAM are 1) there are no other tuning parameters (such as bandwidth)
-besides $\lambda$; 2) SCAM is formulated as a convex program, which guarantees a global optimum.
+Next, in order to quantitatively study the predictive performance, we
+run 10 times 5-fold cross validation, following the same procedure
+described above---training, variable selection and refitting.  A plot
+of the mean and standard deviation of the predictive mean squared
+error (MSE) is shown in Figure \ref{Boston}(d). Since for AC/DC the same
+regularization level $\lambda^{(t)}$ may lead to a slightly different number of selected
+variables in different folds and runs, the values on the $x$-axis
+for AC/DC are not necessarily integers. The figure clearly shows that AC/DC has a 
+lower predictive MSE than LASSO.  We also compared the performance of
+AC/DC with that of Additive Forward Regression (AFR) presented
+in~\cite{Xi:09}, and found that they are similar.  The main advantages
+of AC/DC compared with AFR and SpAM are that there are no smoothing
+parameters required, and the optimization is formulated
+as a convex program, guaranteeing a global optimum.
 
@@
 %                \includegraphics[width=\textwidth]{figs/Additive}
-%                 \caption{Variable selection result using SCAM.}
-%                \label{SCAM}
+%                 \caption{Variable selection result using AC/DC.}
+%                \label{AC/DC}
 %        \end{subfigure}
@@
 %                \includegraphics[width=\textwidth]{figs/Additive1}
-%                 \caption{Variable selection result using SCAM.}
-%                \label{SCAM1}
+%                 \caption{Variable selection result using AC/DC.}
+%                \label{AC/DC1}
 %        \end{subfigure}\\
@@
 %                \includegraphics[width=\textwidth]{figs/MSE}
-%                 \caption{Predictive MSE of SCAM and LASSO.}
+%                 \caption{Predictive MSE of AC/DC and LASSO.}
 %                 \label{MSE}
@@
 %                \includegraphics[width=\textwidth]{figs/Convex}
-%                \caption{Inferred additive convex functions by SCAM.}
+%                \caption{Inferred additive convex functions by AC/DC.}
 %                \label{Convex}
@@
 \hskip-10pt 
-SCAM $\|\beta_k\|_\infty$ paths & 
+AC/DC $\|\beta_k\|_\infty$ paths & 
 \hskip-25pt 
-SCAM $\text{mean}(\beta_k)$ paths &
+AC/DC $\text{mean}(\beta_k)$ paths &
 \hskip-25pt
@@
 \\
-predictive MSE & inferred functions from SCAM
+predictive MSE & estimated functions from AC/DC
 \end{tabular}

### 2014-09-21 tex/scam/additive_faithful.tex
analysis update
new examples

@@
 and define 
-\begin{equation}
-f^*_1,...,f^*_p, \mu^* \coloneqq 
-\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
+\begin{align*}
+f^*_1,...,&f^*_p, \mu^* \coloneqq  \\
+&\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
 \E f_k(X_k) = 0,\; \forall k=1,\ldots, p \right\}.
-\end{equation}
+\end{align*}
 Then $\mu^* = \E f(X)$, 
@@
 f^*_k(x_k) = \E\Bigl[ f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) \given
-x_k\Bigr] - \E f(X) 
+x_k\Bigr] - \E f(X), 
 \end{equation}
@@
 \int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
-\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
+\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) 
+    + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
 p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 .
@@
   \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}
-= 0$.  Such a limit condition is too
-strong however, as it is not obeyed by the multivariate Gaussian
-distribution. 
+= 0$.  Such a limit condition however is not obeyed by many common distributions such as the multivariate Gaussian distribution. 
 \end{remark}
@@
 \label{examp:gaussian_counterexample}
-Consider a quadratic form $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c^\tran \mathbf{x}$ and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma_{jj} = 1$ for all $j$.
-As we show in the appendix, the additive approximation has the
+Consider a two dimensional quadratic function $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c$ where $H = \begin{pmatrix} H_{11} & H_{12} \\ H_{12} & H_{22}\end{pmatrix}$ is positive definite and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma = \begin{pmatrix}1 & \alpha \\ \alpha & 1 \end{pmatrix}$.
+As we show in Section~\ref{sec:gaussian_example} of the Appendix, the additive approximation has the
 following closed form.
-\begin{enumerate}
-\item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
-\item If $f$ depends on $x_j$, then
-\begin{equation}
-f^*_j(x_j) = H_j^\tran \Sigma_j x_j^2 + c_j x_j
-\end{equation}
-where $H_j$ and $\Sigma_j$ are the $j$th rows of $H_j$ and $\Sigma_j$, respectively. 
-\end{enumerate}
-Let $H = \begin{pmatrix}1 & 2 \\ 2 & 5\end{pmatrix}$ and let $\Sigma
-= \begin{pmatrix}1 & -\alpha \\ -\alpha & 1\end{pmatrix}$. 
-It can be checked that if $\alpha=\frac{1}{2}$, then $f^*_1 = 0$
-and additive faithfulness is violated.  Moreover, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
+\begin{align*}
+f^*_1(x_1) &= \left( \frac{T_1 - T_2 \alpha^2}{1 - \alpha^4} \right) x_1^2 + c_1\\
+f^*_2(x_2) &= \left( \frac{T_2 - T_1 \alpha^2}{1 - \alpha^4} \right) x_2^2 + c_2
+\end{align*}
+Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$.
+Let $H = \begin{pmatrix} 1.6 & 2 \\ 2 & 5\end{pmatrix}$, then it is easy to check that if $\alpha = - \frac{1}{2}$, then $f^*_1 = 0$
+and additive faithfulness is violated, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
+We take the setting where $\alpha=-1/2$, compute the optimal additive functions via numerical simulation, and show the results in Figure~\ref{fig:gaussian_example}--$f^*_1$ is zero as expected.
 \end{example}
+
+Interestingly, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary-points conditions.
+
+\begin{example} 
+\label{examp:boundaryflat_example}
+ Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$.
+The uniform distribution is supported over a slightly larger square to satisfy the boundary-points conditions.
+
+When $b$ is large, $\epsilon$ is small, and $\lambda$ is small, the mixture closely approximates the Gaussian distribution but is still additively faithful for all convex functions.
+Figure~\ref{fig:boundaryflat_example} shows the optimal additive function under the mixture distribution, computed by numerical simulation with $b=5, \epsilon=0.3, \lambda=0.0001$.
+We note that $f^*_1$, which is zero under the Gaussian distribution, is nonzero under the mixture distribution.
+Although $f^*_1$ is non-zero, $\E f^*_1(X_1)^2$ is small however, around $10^{-8}$ in our example.
+\end{example}
+
+\begin{figure*}[htp]
+\vskip-10pt
+	\centering
+	\subfigure[Gaussian distribution]{
+          \label{fig:gaussian_example}
+		\centering
+		{\includegraphics[width=0.4\textwidth]{figs/gaussian_example}}
+	}
+	\subfigure[Mixture approximation]{
+          \label{fig:boundaryflat_example}
+		\centering
+		{\includegraphics[width=0.4\textwidth]{figs/boundaryflat_example}}
+	}
+\caption{Optimal additive projection of the quadratic function described in Example~\ref{examp:gaussian_counterexample} under both the Gaussian distribution described in Example~\ref{examp:gaussian_counterexample} and under the approximately Gaussian mixture distribution described in Example~\ref{examp:boundaryflat_example}.
+For the mixture approximation, we used $b=5, \epsilon=0.3, \lambda=0.0001$ where the parameters are defined in Example~\ref{examp:boundaryflat_example}.
+This example shows the effect and the importance of the boundary-points conditions.}
+\vskip-10pt
+\end{figure*}
 

### 2014-09-21 tex/scam/appendix.tex
new examples

@@
 
+\section{Gaussian Example}
+\label{sec:gaussian_example}
+
+Let $H$ be a positive definite matrix and let $f(x_1, x_2) = H_{11} x_1^2 + 2H_{12} x_1x_2 + H_{22} x_2^2 + c$ be a quadratic form where $c$ is a constant such that $\E[f(X)] = 0$.
+Let $X \sim N(0, \Sigma)$ be a random bivariate Gaussian vector with covariance $\Sigma = [1, \alpha; \alpha, 1]$
+
+\begin{proposition}
+Let $f^*_1(x_1) + f^*_2(x_2)$ be the additive projection of $f$ under the bivariate Gaussian distribution. That is,
+\begin{align*} 
+f^*_1, f^*_2 \equiv \argmin_{f_1, f_2} \Big\{ \E \left(f(X) - f_1(X_1) - f_2(X_2)\right)^2 \,:\, \E[f_1(X_1)] = \E[f_2(X_2)] = 0 \Big\}
+\end{align*}
+
+Then, we have that 
+\begin{align*}
+f^*_1(x_1) &= \left( \frac{T_1 - T_2 \alpha^2}{1 - \alpha^4} \right) x_1^2 + c_1 \\
+f^*_2(x_2) &= \left( \frac{T_2 - T_1\alpha^2}{1 - \alpha^4} \right) x_2^2 + c_2
+\end{align*}
+Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$ and $c_1,c_2$ are constants such that $\E[f_1^*(X_1)] = \E[f_2^*(X_2)] = 0$.
+
+\end{proposition}
+
+\begin{proof}
+By Lemma~\ref{lem:general_int_reduction}, we need only verify that $f^*_1, f^*_2$ satisfy
+\begin{align*}
+f^*_1(x_1) &= \E[ f(X) - f_2^*(X_2) \given x_1] \\
+f^*_2(x_2) &= \E[ f(X) - f_1^*(X_1) \given x_2 ] 
+\end{align*}
+
+Let us guess that $f^*_1, f^*_2$ are quadratic forms $f^*_1(x_1) = a_1 x_1^2 + c_1$, $f^*_2(x_2) = a_2 x_2^2 + c_2$ and verify that there exist $a_1, a_2$ to satisfy the above equations.
+Since we are not interested in constants, we define $\simeq$ to be equality up to a constant.
+
+Then, 
+\begin{align*}
+&\E[ f(X) - f_2^*(X_2) \given x_1]\\
+& \simeq \E[ H_{11} X_1^2 + 2H_{12}X_1 X_2 + H_{22}X_2^2 - a_2 X_2^2 \given x_1 ] \\ 
+    &\simeq H_{11} x_1^2 + 2 H_{12} x_1 \E[X_2 \given x_1] + H_{22} \E[X_2^2 \given x_1] - a_2\E[X_2^2 \given x_1] \\
+   &\simeq H_{11} x_1^2 + 2H_{12} \alpha x_1^2 + H_{22} \alpha^2 x_1^2 - a_2 \alpha^2 x_1^2\\
+   &\simeq (H_{11} + 2 H_{12} \alpha + H_{22} \alpha^2 - a_2 \alpha^2) x_1^2
+\end{align*}
+
+Likewise, we have that
+\[
+\E[ f(X) - f_1^2(X_1) \given x_2] \simeq (H_{22} + 2H_{12}\alpha + H_{22}\alpha^2 - a_1 \alpha^2) x_2^2
+\]
+
+Thus, $a_1, a_2$ need only satisfy the linear system:
+\begin{align*}
+T_1 - a_2 \alpha^2 &= a_1 \\
+T_2 - a_1 \alpha^2 &= a_2 
+\end{align*}
+where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$.
+
+It is then trivial to solve the system and verify that $a_1, a_2$ are as specified.
+
+\end{proof}
+
 % \subsubsection{Covering Number for Lipschitz Convex Functions}

### 2014-09-28 tex/scam/additive_faithful.tex
fix concave postprocess proof

@@
 satisfies the boundary points condition. Suppose that $f$ is convex
-and twice differentiable, and that $\partial_{x_k} f$,
-$\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
+and twice differentiable, and that $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
 $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$ are all continuous
-as functions on $C$.  Let $f^*_k$ and $g^*_k$ be as defined in equations
+as functions of $x_k$.  Let $f^*_k$ and $g^*_k$ be as defined in equations
 \eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}.  Then
 $f^*_k = 0$ and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x})
-= 0$ with probability one,
-so that $f$ does not depend on~$x_k$.
+= 0$, that is, $f$ does not depend on~$x_k$.
 \end{theorem}
@@
 \label{cor:faithfulness_extension}
-Suppose $p(x)$ is a positive density on $[0,1]^p$ satisfying the boundary points condition.
-For any function $\phi(X_{-k})$ that does not depend on $X_k$,
+Suppose $p(x)$ is a positive density on $C=[0,1]^p$ satisfying the boundary points condition.
+Let $f(\mathbf{x})$ be a convex twice differentiable function on $C$.
+Let $\phi(\mathbf{x}_{-k})$ be any function that does not depend on $x_k$.
+Then, we have that the unconstrained univariate function
  \begin{align}
-f^*_k = \arg\min_{f_k} \mathbb{E} \Bigl[\bigl( f(X) 
-           - \phi(X_{-k}) - f_k(X_k) \bigr)^2\Bigr]
+h^*_k = \arg\min_{f_k} \mathbb{E} \Bigl[\bigl( f(X) 
+           - \phi(X_{-k}) - h_k(X_k) \bigr)^2\Bigr]
 \end{align}
-is given by $f^*_k(x_k) = \mathbb{E}\bigl[ f(X) - \phi(X_{-k}) \,|\, x_k\bigr]$,
-and $ f^*_k = 0$ implies that $\partial_{x_k} f(x) = 0$.
+is given by $h^*_k(x_k) = \mathbb{E}\bigl[ f(X) - \phi(X_{-k}) \,|\, x_k\bigr]$,
+and $ h^*_k = 0$ implies that $\partial_{x_k} f(x) = 0$.
 \end{lemma}
@@
   r(\mathbf{x}_{-k}) = 0$. Therefore, the proof here is identical to
-  that of Theorem~\ref{thm:convex_faithful} except that we let
-  $\phi(\mathbf{x}_{-k})= r(\mathbf{x}_{-k}).$
+  that of Theorem~\ref{thm:convex_faithful} except that we replace $r(\mathbf{x}_{-k})$ with $\phi(\mathbf{x}_{-k})$.
 \end{proof}
@@
 \begin{proof}[Proof of theorem~\ref{thm:acdc_faithful}]
+
 Fix $k$. Let $f^*_k$ and $g^*_k$ be defined as in
 equation~\ref{eqn:convex_additive} and
-equation~\ref{eqn:concave_postprocess}.  Then
-we have that
+equation~\ref{eqn:concave_postprocess}. Let $\phi(\mathbf{x}_{-k}) \equiv \sum_{k' \neq k} f^*_{k'}(x_{k'})$.
+
+Then we have that
 \begin{align}
@@
 \end{align}
-Therefore, $f^*_k = 0$ and $g^*_k = 0$ implies that $\E[ f(X) -
-\sum_{k'\neq k} f^*_{k'}(X_{k'}) \given x_k] = 0$.  Now we use
+
+Let us suppose that $f^*_k = g^*_k = 0$. It must be then that
+\begin{align*}
+\argmin_{c \in \R} \E \left( f(X) - \phi(X_{-k}) - c (X_k^2 - m_k^2) \right)^2 = 0
+\end{align*}
+where $m_k^2 \equiv \E X_k^2$; this is because $c(x_k^2 - m_k^2)$ is either convex or concave in $x_k$ and it is centered, i.e.
+$\E[ X_k^2 - m_k^2] = 0$.
+Since the optimum has a closed form $c^* = \frac{\E\big[(f(X) -\phi(X_{-k}))(X_k^2 - m^2_k)\big]}{\E X_k^2}$, we deduce that
+\begin{align*}
+\E \big[ (f(X) - \phi(X_{-k})) &(X_k^2 - m_k^2) \big] \\
+   &= \E[ (f(X) - \phi(X_{-k})) X^2_k] = 
+ \E[ \E[ f(X) - \phi(X_{-k}) \given X_k] X^2_k] = 0
+\end{align*}
+
+We denote $h^*_k(x_k) = \E[ f(X) - \phi(X_{-k}) \given x_k]$.
+
+Under the derivative continuity conditions in the theorem, we apply Lemma~\ref{lem:acdc_derivative_bound} and know that $h^*_k(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$.
+Therefore, for a large enough positive scalar $\alpha$, $h^*_k(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second derivative and is thus convex.
+
+Because we assumed $f^* = g^* = 0$, it must be that
+\[
+\argmin_{c \in \R} 
+\E\Big( f(X) - \phi(X_{-k}) - c\big( h^*_k(X_k) + \alpha(X_k^2 - m_k^2)\big) \Big)^2 = 0
+\]
+This is because $c\big( h^*_k(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered function.
+
+Again, $c^* = \frac{\mathbb{E}[(f(X)-\phi(X_{-k}))\big( 
+           h^*_k(X_k) + \alpha (X_k^2 - m_k^2) \big)]}{\mathbb{E}
+       \big( h^*_k(X_k) + \alpha (X_k^2 - m_k^2) \big)^2} = 0$, so
+\begin{align*}
+\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( h^*_k(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
+\mathbb{E}[ (f(X) - \phi(X_{-k})) h^*_k(X_k) ] \\
+& = \mathbb{E}\Big[ \mathbb{E}[ f(X) - \phi(X_{-k}) \given X_k]  h^*_k(X_k) \Big] \\
+& = \mathbb{E} h^*_k(X_k)^2 = 0
+\end{align*}
+where the first equality follows because $\E[ (f(X) - \phi(X_{-k})) (X_k^2 - m_k^2)] = 0$. Therefore, we get that $h^*_k = 0$. Now we use
 Lemma~\ref{cor:faithfulness_extension} with $\phi(\mathbf{x}_{-k}) =
@@
 %%
-%%\begin{proposition}
-%%\label{prop:shape_approx_univariate}
-%%Let $C \subset \R^p$ be a compact set and let $h : C \rightarrow \R$.
-Let $p(x)$ be a positive density on $C$ and suppose $\E h(X) = 0$.
+
+% \begin{lemma}
+% \label{lem:shape_approx_univariate}
+% Let $C \subset \R^p$ be a compact set and let $h : C \rightarrow \R$.
+Let $p(x)$ be a positive density supported on $C$ and suppose $\E h(X) = 0$.
 Suppose that $\partial_{x_k} h(x)$, $\partial_{x_k} p( x \given x_k)$, and $\partial^2_{x_k} p( x \given x_k )$ are all continuous as functions on $C$.
 Suppose that $\partial^2_{x_k} h(x) \geq 0$.
-%%
-%%
-%%Let 
-%%\begin{align*}
-%%f^*_k(x_k) &= \arg\min_{f_k} \Big\{
-%%   \E \Big( h(X) - f_k(X_k) \Big)^2 \,:\, f_k \in \mathcal{C}^1,\, \E f_k = 0 \Big\} \\
-%%g^*_k(x_k) &= \arg\min_{g_k} \Big \{
-%%   \E \Big( h(X) - g_k(X_k) \Big)^2 \,:\, g_k \in \mh \mathcal{C}^1 ,\, \E g_k = 0 \Big\}
-%%\end{align*}
-%%be the best convex and concave univariate approximation respectively.\\
-%%
-%%Then, $f^*_k = 0$ and $g^*_k = 0$ iff $h^*_k(x_k) \equiv \E[ h(X) \given x_k ] = 0$.
-%%\end{proposition}
-%%
-%%\begin{proof}
-%%
-%%
-%%First, we will establish that $h^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded. 
-%%
-%%\begin{align*}
-%%h^*_k(x_k) &= \E[ h(X) \given x_k] \\
-%%  &= \int_{x_{-k}} h(x) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
-%%\partial^2_{x_k} h^*_k(x_k) 
-%%  &= \int_{\mathbf{x}_{-k}} h''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) +
-%%  2 h'(x) p'(\mathbf{x}_{-k} \given x_k) + h(x) p''(\mathbf{x}_{-k} \given x_k) 
-%%  d\mathbf{x}_{-k} 
-%%\end{align*}
-%%
-%%The first term $h''(x) p(\mathbf{x}_{-k} \given x_k)$ is strictly positive.
+
+% Let 
+% \begin{align*}
+% f^*_k(x_k) &= \arg\min_{f_k} \Big\{
+%   \E \Big( h(X) - f_k(X_k) \Big)^2 \,:\, f_k \in \mathcal{C}^1,\, \E f_k = 0 \Big\} \\
+% g^*_k(x_k) &= \arg\min_{g_k} \Big \{
+%   \E \Big( h(X) - g_k(X_k) \Big)^2 \,:\, g_k \in \mh \mathcal{C}^1 ,\, \E g_k = 0 \Big\}
+% \end{align*}
+% be the best convex and concave univariate approximation respectively.\\
+
+% Then, $f^*_k = 0$ and $g^*_k = 0$ iff $h^*_k(x_k) \equiv \E[ h(X) \given x_k ] = 0$.
+% \end{lemma}
+
+% \begin{proof}
+
+% First, we establish that $h^*_k(x_k)$ is twice differentiable and that $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded.
+
+% \begin{align*}
+% h^*_k(x_k) &= \E[ h(X) \given x_k] \\
+%  &= \int_{x_{-k}} h(x) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
+% \partial^2_{x_k} h^*_k(x_k) 
+%  &= \int_{\mathbf{x}_{-k}} h''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) +
+%  2 h'(x) p'(\mathbf{x}_{-k} \given x_k) + h(x) p''(\mathbf{x}_{-k} \given x_k) 
+%  d\mathbf{x}_{-k} 
+% \end{align*}
+
+% The first term $h''(x) p(\mathbf{x}_{-k} \given x_k)$ is strictly positive.
 By assumption, the remaining terms are continuous and hence bounded on a compact set.
@@
 Before proceeding, we also note that because $\E h(X) = 0$, it must be that $\E h^*_k(X_k) = 0$.
-%%
-%%Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
-%%\begin{equation}
-%%\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
-%%\end{equation}
-%%Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
-%%we know $\mathbb{E} [ h(X) X_k^2 ] = 
-%%\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
-%%
-%%Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
-%%\begin{equation}
-%%\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
-%%       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
-%%\end{equation}
-%%Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
-%%            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
-%%        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
-%%\begin{align*}
-%%\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
-%%\mathbb{E}[ h(X) h^*_k(X_k) ] \\
-%%& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
-%%& = \mathbb{E} h^*_k(X_k)^2 = 0
-%%\end{align*}
-%%Therefore, $h^*_k(x_k) = 0$.
-%%
-%%\end{proof}
+
+% Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
+% \begin{equation}
+% \arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
+% \end{equation}
+% Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
+% we know $\mathbb{E} [ h(X) X_k^2 ] = 
+% \mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\
+
+% Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
+% \begin{equation}
+% \arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
+%       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
+% \end{equation}
+% Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
+%            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
+%        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
+% \begin{align*}
+% \mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
+% \mathbb{E}[ h(X) h^*_k(X_k) ] \\
+% & = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
+% & = \mathbb{E} h^*_k(X_k)^2 = 0
+% \end{align*}
+% Therefore, $h^*_k(x_k) = 0$.
+
+% \end{proof}
 %%

### 2014-09-28 tex/scam/appendix.tex
fix concave postprocess proof

@@
 
+\subsubsection{Supporting Lemma for Theorem~\ref{thm:acdc_faithful}}
+
+\begin{lemma}
+\label{lem:acdc_derivative_bound}
+Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function.
+Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$.
+Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.\\
+
+Then, $h^*_k(x_k) \equiv \E[ f(X) - \phi(X_{-k}) \given x_k]$ is twice differentiable and has a second derivative lower bounded, that is, bounded away from $-\infty$.
+\end{lemma}
+
+\begin{proof}
+
+\[
+h^*_k(x_k) = \int_{\mathbf{x}_{-k}} \big(f(\mathbf{x}) - \phi(\mathbf{x}_{-k})\big) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
+\]
+
+The integrand is bounded because it is a sum-product of continuous functions over a compact set. Therefore, we can differentiate under the integral and derive that
+\begin{align*}
+\partial_{x_k} h^*_k(x_k) &= 
+    \int_{\mathbf{x}_{-k}} f'(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p'(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
+\partial_{x_k}^2 h^*_k(x_k) &= 
+    \int_{\mathbf{x}_{-k}} f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + 2f'(\mathbf{x}) p'(\mathbf{x}_{-k} \given x_k)  + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p''(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
+\end{align*}
+
+We used the shorthand $f'(\mathbf{x}), p'(\mathbf{x}_{-k} \given x_k), etc$ to denote $\partial_{x_k} f(\mathbf{x})$, $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$, etc.
+
+This proves that $h^*_k(x_k)$ is twice-differentiable.
+To see that the second derivative is lower bounded, we note that $f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k)$ is non-negative and the other terms in the second-derivative are all continuous functions on a compact set and thus bounded.
+
+\end{proof}
+
  \subsubsection{Concentration of Measure}

### 2014-09-29 tex/scam/additive_faithful.tex
boundary flatness name change

@@
 A density $p(\mathbf{x})$ be a density supported on $[0,1]^p$ satisfies
-the \emph{boundary points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
+the \emph{boundary flatness condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
 
@@
 
-The boundary points condition is a weak condition. For instance, it is
+The boundary flatness condition is a weak condition. For instance, it is
 satisfied when the density is flat at the boundary of support---more
@@
 \frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at
-points $x_j = 0, x_j=1$. The boundary points property is also
+points $x_j = 0, x_j=1$. The boundary flatness property is also
 trivially satisfied when $p$ is a product density.
@@
 Let $p$ be a positive density supported on $C=[0,1]^p$ that satisfies
-the boundary points property. 
+the boundary flatness property. 
 If $f$ is convex and twice differentiable, then $f$ is additively faithful under $p$.
@@
 
-By the boundary points condition, we have that $p''(\mathbf{x}_{-k}
+By the boundary flatness condition, we have that $p''(\mathbf{x}_{-k}
 \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k =
@@
 
-Interestingly, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary-points conditions.
+Interestingly, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary flatness conditions.
 
@@
  Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$.
-The uniform distribution is supported over a slightly larger square to satisfy the boundary-points conditions.
+The uniform distribution is supported over a slightly larger square to satisfy the boundary flatness conditions.
 
@@
 For the mixture approximation, we used $b=5, \epsilon=0.3, \lambda=0.0001$ where the parameters are defined in Example~\ref{examp:boundaryflat_example}.
-This example shows the effect and the importance of the boundary-points conditions.}
+This example shows the effect and the importance of the boundary flatness conditions.}
 \vskip-10pt
@@
 Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ that
-satisfies the boundary points condition. Suppose that $f$ is convex
+satisfies the boundary flatness condition. Suppose that $f$ is convex
 and twice differentiable, and that $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
@@
 \label{cor:faithfulness_extension}
-Suppose $p(x)$ is a positive density on $C=[0,1]^p$ satisfying the boundary points condition.
+Suppose $p(x)$ is a positive density on $C=[0,1]^p$ satisfying the boundary flatness condition.
 Let $f(\mathbf{x})$ be a convex twice differentiable function on $C$.

### 2014-09-29 tex/scam/summary.tex
added comment on sufficiently large n
boundary flatness name change

@@
   Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.  Then $p$
-  satisfies the \emph{boundary points condition} if for all $j$, and
+  satisfies the \emph{boundary flatness condition} if for all $j$, and
   for all $\mathbf{x}_{-j}$,
@@
   Let $p$ be a positive density supported on $C=[0,1]^p$ that
-  satisfies the boundary points property. If $f$ is convex and twice
+  satisfies the boundary flatness property. If $f$ is convex and twice
   differentiable, then $f$ is additively faithful under $p$.
@@
 Suppose $p(\mathbf{x})$ is a positive
-density on $C=[0,1]^p$ that satisfies the boundary points
+density on $C=[0,1]^p$ that satisfies the boundary flatness
 condition. Suppose that $f$ is convex and twice-differentiable.
@@
 
+%% this statement "for sufficiently large n" should be changed.  the
+%% result is stronger than this, since we get a sample complexity.
+
 \end{stheorem}

### 2014-10-01 tex/scam/additive_faithful.tex
new linear example

@@
 \begin{remark}
+In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components.
+The additive approximations may not be faithful if we use parametric components.
+For example, suppose we approximate a convex function $f(X)$ by a linear form $X \beta$.
+The optimal linear function in the population setting is $\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$.
+Suppose the $X$'s are independent and follow a symmetric distribution and suppose $f(\mathbf{x}) = x_1^2 - \E[X_1^2]$, then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 - X_1 \E[X_1^2]] = 0$.
+\end{remark}
+
+\begin{remark}
 It is possible to get a similar result for distributions with
@@
 \label{examp:boundaryflat_example}
- Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$.
+ Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$ and $U[-(b+\epsilon), b+\epsilon]^2$ is the uniform distribution over a square.
 The uniform distribution is supported over a slightly larger square to satisfy the boundary flatness conditions.
@@
 is given by $h^*_k(x_k) = \mathbb{E}\bigl[ f(X) - \phi(X_{-k}) \,|\, x_k\bigr]$,
-and $ h^*_k = 0$ implies that $\partial_{x_k} f(x) = 0$.
+and $ h^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x}) = 0$.
 \end{lemma}

### 2014-10-01 tex/scam/sparsistency.tex
minor edits
new linear example

@@
 where we restrict the indices $k$ in
-optimization \eqref{opt:alternate_opt} to lie in the set $S$ of true
+optimization \eqref{opt:alternate_opt} to lie in some set $S$ which contains the true
 relevant variables.
@@
 The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.
+We allow $S$ in Theorem~\ref{thm:deterministic} to be any set containing the relevant variables; in Lasso analysis, $S$ is taken to be the set of relevant variables; we will take $S$ to be the set of variables chosen by the additive convex and decoupled concave procedure in the population setting, which is guaranteed to contain the relevant variables because of additive faithfulness.
 
@@
    f_k \in \mathcal{C}^1 \} $.  
-Let $f^*(x) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
+Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
 minimizer in $\mathcal{C}_1^p$, 
@@
   We make strong assumptions on the covariates in A1 in order to make
-  very weak assumptions on the true regression function $f_0$ in
+  weak assumptions on the true regression function $f_0$ in
   A2. In particular, we do not assume that $f_0$ is additive. In
-  important direction for future work is to weaken this assumption.
+  important direction for future work is to weaken assumption A1.
   Our simulation experiments indicate that the procedure can be
@@
 \end{align}
-where $c,C$ are constants.
+for some constant $C$.
 

### 2014-10-17 tex/scam/appendix.tex
new plots

@@
 
-By additive faithfulness of the ACDC procedure, it is necessary that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\
-
-Intuitively, we would like to show the following:
-\begin{align*}
-\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
-\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P 
+By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\
+
+Intuitively, we would like to show that the risks of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risks of the population optimal functions $f^*, g^*$:
+\begin{align*}
+\| f_0 - \hat{f} \|^2_P & = \| f_0 - f^* \|^2_P + \trm{err}_+(n) \\
+\| f_0 - f^* - \hat{g}_k \|^2_P &=  \| f_0 - f^* - g^*_k \|^2_P + \trm{err}_-(n) 
        \quad \trm{for all $k \in S$ where $f^*_k = 0$}
 \end{align*}
-where the estimation error is a term that decreases with $n$.
-
-Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough, there must exist a contradiction because the population risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger than the population risk of the best approximation whose $k$-th component is constrained to be zero.
+where the estimation errors $\trm{err}_+(n), \trm{err}_-(n)$ decrease with $n$ at some rate.
+
+Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough such that $\trm{err}_+(n)$ and $\trm{err}_-(n)$ are smaller than $\alpha_+, \alpha_-$ (defined in equation~\ref{eqn:signal_level_defn}), there must exist a contradiction because the risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger by $\alpha_+$ than the risk of the best approximation whose $k$-th component is constrained to be zero.
 
 Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction. \\
+
+Theorem~\ref{thm:convex_consistent} and theorem~\ref{thm:concave_consistent} characterize $\trm{err}_+(n)$ and $\trm{err}_-(n)$ respectively.
 

### 2014-10-17 tex/scam/experiments.tex
new plots

@@
 \end{equation}
-Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0},\bds{I}_{p})$, 
+Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0}, \Sigma)$, 
 $\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
@@
 
-In the first simulation, we set $\Q=\bds{I}_{|S|}$ (the additive
-case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
-For each $(n,p)$ combination, we generate $200$ independent data
+In the first simulation, we vary the ambient dimension $p$.
+We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
+We use independent design by setting $\Sigma = Id$.
+For each $(n,p)$ combination, we generate $100$ independent data
 sets. For each data set we use the AC/DC algorithm to estimate the model support.
 We plot the probability of
-support recovery over the $200$ data sets in Figure \ref{Support}(a).  We
-observe that the algorithm performs consistent variable selection when the true
-function is convex additive.    To give the reader a
+support recovery over the $100$ data sets in Figure \ref{Support}(a).  We
+observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
 sense of the running speed, for a 
@@
 
-In the second simulation, we study the case in which the true function
-is convex but not additive. We generate four $\Q$ matrices
+In the second simulation, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
 plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
@@
 ($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We again run the AC/DC optimization on $200$
+$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = Id$. We again run the AC/DC optimization on $100$
 independently generated data sets and plot the probability of recovery
@@
 
-In the third simulation, we study the case of a correlated design, where
-$\x_i$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
+In the third simulation, we use correlated design and vary the correlation. We let
+$\x_i$ be drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
 instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
@@
 with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
-we obtain a subgradient matrix $\bds{\beta}^{(t)}$ with $p=13$
+we obtain a function value matrix $\bds{h}^{(t)}$ with $p=13$
 rows. The non-zero rows in this matrix indicate the variables selected
-using $\lambda^{(t)}$.  We plot $\|\bds{\beta}^{(t)}\|_{\infty}$ and
-the row-wise mean of $\bds{\beta}^{(t)}$ versus the normalized norm
-$\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$
+using $\lambda^{(t)}$.  We plot $\|\bds{h}^{(t)}\|_{\infty}$ and
+the row-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
+$\frac{\|\bds{h}^{(t)}\|_{\infty,1}}{\|\bds{h}^{(1)}\|_{\infty,1}}$
 in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
@@
 consistent with previous findings~\citep{SpAM:07}.  The fourth
-variable selected by AC/DC is \tts{TAX} (with $\lambda^{(t)}=0.09$).
+variable selected by AC/DC is \tts{INDUS} (with $\lambda^{(t)}=0.7$).
 We then refit AC/DC with only these four variables without
@@
 \begin{center}
-\begin{tabular}{ccc}
-\hskip-10pt
-  \includegraphics[width=.35\textwidth]{figs/Additive} &
-\hskip-25pt
-  \includegraphics[width=.35\textwidth]{figs/Additive1} &
-\hskip-25pt
-  \includegraphics[width=.35\textwidth]{figs/LASSO} 
+\begin{tabular}{cc}
+%\hskip-10pt
+  \includegraphics[width=.37\textwidth]{figs/acdc_path} &
+%\hskip-25pt
+  \includegraphics[width=.37\textwidth]{figs/lasso_path} 
 \\
-\hskip-10pt 
-AC/DC $\|\beta_k\|_\infty$ paths & 
-\hskip-25pt 
-AC/DC $\text{mean}(\beta_k)$ paths &
-\hskip-25pt
-LASSO $\beta_k$ paths
-\end{tabular}
-\begin{tabular}{cc}
-  \includegraphics[width=.37\textwidth]{figs/MSE} &
-  \includegraphics[width=.43\textwidth]{figs/Convex}
+%\hskip-10pt 
+AC/DC $\|f_k\|_\infty$ paths & 
+%\hskip-25pt
+LASSO $|\beta_k|$ paths \\
+%\end{tabular}
+%\begin{tabular}{cc}
+  \includegraphics[width=.37\textwidth]{figs/MSEacdc} &
+  \includegraphics[width=.43\textwidth]{figs/acdc_functs}
 \\

### 2014-10-17 tex/scam/sparsistency.tex
new plots

@@
 we analyze the condition on $\lambda_n$ for $k \in S^c$. To control
-false negatives, we analyze the restricted regression.
+false negatives, we need only analyze the restricted regression with only $|S|$ variables.
 
@@
 \end{equation}
-We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$. 
+We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$.
+By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$.
+In some cases such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
 Each of our theorems will use a subset of the following assumptions:
@@
 We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
-\begin{align*}
+\begin{align}
 \alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
-        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
+        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
 \alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
       \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
-    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}
-\end{align*}
+    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
+\end{align}
 These quantities play the role of the absolute value of the smallest nonzero
@@
 \begin{equation}
-\lambda_n \geq 8 s_0 \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
+\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
 \end{equation}  
@@
 \begin{equation}
-\lambda_n \leq 9 s_0 \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
+\lambda_n \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
 \end{equation}
@@
 \begin{equation}
-\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s_0^5.
+\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s^5.
 \end{equation}
@@
 \frac{\alpha_{+}}{\tilde{\sigma}} & \geq c B^2
-\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}\\
+\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}\\
 \frac{\alpha_{-}^2}{\tilde{\sigma}} &\geq c B^2
-\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}
+\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}
 \end{align}
@@
 boundedness constraint so that we can use recent bracketing number
-results \cite{kim2014global}.
+results \cite{kim2014global}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.
 
@@
 is reflected in the scaling with respect to
-the number of relevant variables, which can scale as $s_0 = o(n^{4/25})$.
+the number of relevant variables, which can scale as $s = o(n^{4/25})$.
 

### 2014-10-17 code/paper_exp/C.m

@@ -79,7 +79,8 @@ for run = 1:nrun
     
     y = sum(X(J(:,run),:).*(Q*X(J(:,run),:)),1)' + randn(n,1);
     % MODIFY
-    [beta,h,obj,Ln(:,run)] = acdc_QP(X,y-mean(y),lambda,maxit,tol); 
+    [beta,h,obj,Lnvex,Lncave] = acdc_QP(X,y-mean(y),lambda,maxit,tol); 
+    Ln(:,run) = max(Lnvex, Lncave);
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
 save(['C_' num2str(version) '.mat'],'J','Ln');

### 2014-10-17 code/paper_exp/LASSO.m

@@ -1,34 +1,58 @@
 function LASSO(data)
 clc; close all; format long; randn('state',0); rand('state',0);
+
 switch data
-    case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
-            [p,n] = size(X); q = p; 
+    case 1, load housing.data; 
+        X = housing(:,1:end-1)'; 
+        y = housing(:,end);
+        [p,n] = size(X); 
+        q = p; 
     case 2, load diabetes; X = diabetes.x'; y = diabetes.y; [p,n] = size(X); q = p;
     otherwise, return
 end
-mrun = 10; b = 5; m = fix(n/b); err = zeros(2,q+1,mrun);
+
+mrun = 10; 
+b = 5; 
+m = fix(n/b); 
+err = zeros(2,q+1,mrun);
+
 for run = 1:mrun
     ord = randperm(n); 
     for i = 1:b
         ndx = ones(n,1)==0; 
-        if i<b, ndx(ord((i-1)*m+1:i*m))=1==1; else ndx(ord((i-1)*m+1:end))=1==1; end
+        if i<b, 
+            ndx(ord((i-1)*m+1:i*m))=1==1; 
+        else
+            ndx(ord((i-1)*m+1:end))=1==1; 
+        end
         erri = LASSO_Main(X,y,ndx,q); 
+        
         err(:,:,run) = err(:,:,run) + erri./([b-1; 1]*ones(1,q+1));
     end
 end
+
 out = [(0:q)' mean(err,3)' std(err,1,3)']
-save(['SCAM/LASSO_' num2str(data) '.mat'],'out');
+save(['acdc_boston/lasso_' num2str(data) '.mat'],'out');
 return
 
 function [err,yo] = LASSO_Main(X,y,ndx,q)
-[p,n] = size(X); [X1,X2] = SCAM_Unit(X,ndx);
-y1 = y(~ndx); ym = mean(y1); y2 = y(ndx);
+[p,n] = size(X); 
+
+[X1,X2] = cv_standardize(X,ndx);
+
+y1 = y(~ndx); 
+ym = mean(y1); 
+y2 = y(ndx);
 beta0 = lars(X1',y1-ym,'lasso',0,0,[],0); 
-num = sum(abs(beta0)>10^-8,2); err = zeros(2,q+1); yo = zeros(n,q+1);
[…]

### 2014-10-17 code/paper_exp/R.m

@@ -78,7 +78,9 @@ for run = 1:nrun
     X = randn(p,n); 
     y = sum(X(J(:,run),:).*(Q*X(J(:,run),:)),1)' + randn(n,1);
     % main function call
-    [beta,h,obj,Ln(:,run)] = acdc_QP(X, y-mean(y), lambda, maxit, tol);
+    [beta,h,obj,Lnvex,Lncave] = acdc_QP(X, y-mean(y), lambda, maxit, tol);
+    
+    Ln(:,run) = max(Lnvex,Lncave);
     %[beta,h,obj,Ln(:,run)] = SCAM_QP(X,y-mean(y),lambda,maxit,tol);
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end

### 2014-10-17 code/paper_exp/SCAM.m

@@ -6,7 +6,8 @@ clc; close all; format long; randn('state',0); rand('state',0);
 lambda0 = {[0.00 .005 0.01 .015 0.02 0.04 0.06 ...
             0.07 0.08 0.09 0.10 0.12 0.20 0.30 0.40],...
            };
-nd = size(lambda0,2); nv = zeros(1,nd); 
+nd = size(lambda0,2); 
+nv = zeros(1,nd); 
 
 for i = 1:nd, nv(i) = length(lambda0{i}); end
 
@@ -19,16 +20,29 @@ switch data
     otherwise, return
 end
 
-[p,n] = size(X); mrun = 10; b = 5; m = fix(n/b); % 5-fold CV
-err = zeros(2,mrun); num = zeros(1,mrun);
+[p,n] = size(X); 
+mrun = 10; 
+b = 5; 
+m = fix(n/b); % 5-fold CV
+
+err = zeros(2,mrun); 
+num = zeros(1,mrun);
 
 for run = 1:mrun
     ord = randperm(n);
     for i = 1:b
-        ndx = ones(n,1)==0;
-        if i<b, ndx(ord((i-1)*m+1:i*m))=1==1; else ndx(ord((i-1)*m+1:end))=1==1; end
+        ndx = zeros(n,1);
+        if i<b
+            ndx(ord((i-1)*m+1:i*m))= 1; 
+        else
+            ndx(ord((i-1)*m+1:end))= 1; 
+        end
+        
         [erri,numi] = SCAM_Main(X,y,ndx,lambda);
-        err(:,run) = err(:,run) + erri./[b-1; 1]; num(run) = num(run) + numi/b;
+        
+        err(:,run) = err(:,run) + erri./[b-1; 1]; 
+        num(run) = num(run) + numi/b;
+        
         disp(['run=' num2str(run) ' cv=' num2str(i)]);
     end
 end
@@ -38,12 +52,27 @@ save(['SCAM/SCAM_' num2str(version) '.mat'],'out');
 return
 
 function [err,num,yo] = SCAM_Main(X,y,ndx,lambda)
-[p,n] = size(X); [X1,X2] = SCAM_Unit(X,ndx);
[…]

### 2014-10-17 code/paper_exp/SCAM_Eval.m

@@ -1,8 +1,24 @@
+% IN:
+%  "Xt" -- (p--by--nt) test data
+
+% OUT:
+%   "ht" -- (p--by--nt) predictive components for each test data
+
+% Formula:
+% for a single x_test
+% f_test = max_i  h_ik + beta_ik*(x_testk - x_ik)
+
 function ht = SCAM_Eval(Xt,X,beta,h)
-[p,n] = size(X); nt = size(Xt,2); ht = zeros(p,nt);
+[p,n] = size(X); 
+nt = size(Xt,2); 
+ht = zeros(p,nt);
+
 for d = 1:p
     [vv,ss] = sort(X(d,:)); 
     ht(d,:) = max(repmat(h(d,ss(1:n-1)),[nt,1]) + repmat(beta(d,:),[nt,1]) ...
-        .*(repmat(Xt(d,:)',[1,n-1])-repmat(X(d,ss(1:n-1)),[nt,1])),[],2);
+        .*(repmat(Xt(d,:)',[1,n-1]) - repmat(X(d,ss(1:n-1)),[nt,1])),[],2);
 end
+
+
 return
+

### 2014-10-17 code/paper_exp/SCAM_MOSEK_f.m

@@ -1,67 +1,0 @@
-
-%
-% performs SCAM_MOSEK with L1 penalty on function value
-% 
-% minimize over {f, beta, gamma}
-
-function [beta,z,Ln] = SCAM_MOSEK_f(y,x,lambda)
-n = length(x); [Xd,ord] = sort(x'); dX = Xd(2:n)-Xd(1:n-1);
-Hi = 1:2*n; Hj = 1:2*n; Hs = [ones(1,n)/n,10^-6*ones(1,n)];
-
-% Use 10^-6 instead of 0 to make this QP strictly convex.
-H = sparse(Hi,Hj,Hs,2*n,2*n); f = [-y/n; zeros(n-1,1); lambda];
-Ai = []; Aj = []; As = []; row = 0; ndx = 0;
-
-%variable ordering:
-% function values: 1:n
-% beta: (n+1):(2*n-1)
-% gamma: 2*n
-
-valmat = [ones(n-2,1) -ones(n-2,1)];
-rowmat = [(1:(n-2))' (1:(n-2))'] + row;
-colmat = [((n+1):(2*n-2))' ((n+2):(2*n-1))'];
-rg = (ndx+1):(ndx+2*(n-2)); row = row + (n-2); ndx = ndx + 2*(n-2);
-Ai(rg) = rowmat(:); Aj(rg) = colmat(:); As(rg) = valmat(:);
-
-
-
-
-% gamma inequalities
-%valmat = [ones(n-1,1) -ones(n-1,1) -ones(n-1,1) -ones(n-1,1)];
-valmat = [ones(n,1), -ones(n,1), -ones(n,1), -ones(n,1)];
-%rowmat = [(1:(n-1))' (1:(n-1))' (n:(2*n-2))' (n:(2*n-2))'] + row;
-rowmat = [(1:n)' (1:n)' ((n+1):(2*n))' ((n+1):(2*n))'] + row;
-%colmat = [((n+1):(2*n-1))' 2*n*ones(n-1,1) ...
-%          ((n+1):(2*n-1))' 2*n*ones(n-1,1)];
-colmat = [(1:n)' 2*n*ones(n, 1) ...
-          (1:n)' 2*n*ones(n, 1)];
-%rg = (ndx+1):(ndx+4*(n-1)); row = row + 2*(n-1); ...
-%      ndx = ndx + 4*(n-1);
-rg = (ndx+1):(ndx+4*n); 
[…]

### 2014-10-17 code/paper_exp/SCAM_Unit.m

@@ -1,5 +1,24 @@
+
+% OUT:
+% "X1 = transformed X(:,ndx) "
+% "X2 = transformed X(:,~ndx)"
+
+% standardizes X1, transform X2 accordingly
+
+% a predictor trained on standardized X1 can
+% be used on the returned X2
+
 function [X1,X2,Xm,Xstd] = SCAM_Unit(X,ndx)
-[p,n] = size(X); n1 = sum(~ndx); X1 = X(:,~ndx); Xm = mean(X1,2);
-X1 = X1 - Xm*ones(1,n1); Xstd = sqrt(sum(X1.^2,2))+eps; X1 = X1./(Xstd*ones(1,n1)); 
+
+[p,n] = size(X); 
+n1 = sum(~ndx); 
+
+X1 = X(:,~ndx); 
+Xm = mean(X1,2);
+
+X1 = X1 - Xm*ones(1,n1); 
+Xstd = sqrt(sum(X1.^2,2))+eps; 
+X1 = X1./(Xstd*ones(1,n1)); 
+
 X2 = (X(:,ndx) - Xm*ones(1,n-n1))./(Xstd*ones(1,n-n1));
 return

### 2014-10-17 code/paper_exp/SCAM_View.m

@@ -1,46 +1,80 @@
 data = 1;
 clc; close all; format long; randn('state',0); rand('state',0);
+
 lambda0 = {[0.00 .005 0.01 .015 0.02 0.04 0.06 0.07 0.08 0.09 0.10 0.12 0.20 0.30 0.40],...
            };
-nd = size(lambda0,2); nv = zeros(1,nd); for i = 1:nd, nv(i) = length(lambda0{i}); end
+
+       nd = size(lambda0,2); 
+nv = zeros(1,nd); 
+
+for i = 1:nd, nv(i) = length(lambda0{i}); end
+
+
 switch data
     case 1, load housing.data; X = housing(:,1:end-1)'; y = housing(:,end);
     % case 2, 
     otherwise, return
 end
 
-[p,n] = size(X); output = zeros(nv(data),5);
+[p,n] = size(X); 
+output = zeros(nv(data),5);
+
 for version = sum(nv(1:data-1))+1:sum(nv(1:data))
-    load(['SCAM/SCAM_' num2str(version) '.mat']); output(version-sum(nv(1:data-1)),:) = out;
+    load(['ACDC/ACDC_' num2str(version) '.mat']); 
+    output(version-sum(nv(1:data-1)),:) = out;
 end
-load(['SCAM/LASSO_' num2str(data) '.mat']);
+
+load(['ACDC/LASSO_' num2str(data) '.mat']);
 figure(1); set(gca,'FontSize',14);
+
 errorbar(out(:,1),out(:,3),out(:,5),'g--','LineWidth',2); hold on
+
 errorbar(output(:,1),output(:,3),output(:,5),'k:','LineWidth',2); hold off
-legend('LASSO','SCAM'); xlim([-1 out(end,1)+1])
-xlabel('Average number of seleted features'); ylabel('Testing Mean Squared Error')
+
+legend('LASSO','ACDC'); 
+xlim([-1 out(end,1)+1])
+xlabel('Average number of seleted features'); 
+ylabel('Testing Mean Squared Error')
 title('Testing errors for LASSO and SCAM');
+
 
 % Analysis using all the data.
 names = {{'CRIM','ZN','INDUS','CHAS','NOX','RM','AGE','DIS','RAD','TAX','PTRATIO','B','LSTAT'},...
[…]

### 2014-10-17 code/paper_exp/T.m

@@ -1,7 +1,7 @@
 function T(version)
 % p changes
 % function Diagonal quadratic with noise.
-% covariance correlated alpha=0.5
+% independent gaussian
 
 clc; close all; format long; randn('state',0); rand('state',0); 
 switch version
@@ -79,7 +79,8 @@ for run = 1:nrun
     
     y = sum(X(J(:,run),:).*(Q*X(J(:,run),:)),1)' + randn(n,1);
     
-    [beta,h,obj,Ln(:,run)] = acdc_QP(X,y-mean(y),lambda,maxit,tol);
+    [beta,h,obj,Lnvex,Lncave] = acdc_QP(X,y-mean(y),lambda,maxit,tol);
+    Ln(:,run) = max(Lnvex, Lncave);
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
 save(['T_' num2str(version) '.mat'],'J','Ln');

### 2014-10-17 code/paper_exp/acdc_QP.m

@@ -1,24 +1,30 @@
-% 
+% OUT:
+%   beta -- "p--by--(n-1)"
+%   z -- "p--by--n"
+%   Lnvex, Lncave -- "p" length
 
-function [beta,z,obj,Ln] = acdc_QP(X,y,lambda,maxit,tol)
-[p,n] = size(X); z = zeros(p,n); beta = zeros(p,n-1);
+function [beta,z, obj, Lnvex, Lncave] = acdc_QP(X,y,lambda,maxit,tol)
 
-Ln = zeros(p,1); 
-Ln2 = zeros(p,1);
+[p,n] = size(X); 
+z = zeros(p,n); 
+beta = zeros(p,n-1);
+
+Lnvex = zeros(p,1); 
+Lncave = zeros(p,1);
 
 res = y - sum(z,1)'; iter = 0; obj = []; change = 1;
 obj = zeros(maxit,1);
 
+% counts how many times screening was used
 counter = [0,0];
-%SCAM
+
 while iter < maxit && change > tol
     iter = iter + 1;
     
     for d = 1:p
         res = res + z(d,:)';
         
-        
-        % screening one
+        % screening for AC 
         xcol = reshape(X(d,:), n, 1);
         [Xd, ord] = sort(X(d,:), 'ascend');
         Xdrow = reshape(Xd(1:(n-1)), 1, n-1);
@@ -26,40 +32,33 @@ while iter < maxit && change > tol
         pieceJ = repmat(Xdrow, n, 1);
         Delta_matrix = max(pieceI - pieceJ, 0);
         Delta2_matrix = Delta_matrix - (1/n)*repmat(sum(Delta_matrix, 1), n, 1);
-
-        res_vec = (0.5/n)*res'*Delta_matrix;
         
+        res_vec = (0.5/n)*res'*Delta_matrix;
+        res_vec(1) = abs(res_vec(1));
         lambda_vec1 = lambda*(1/n)*ones(1,n)*Delta_matrix;
+        lambda_vec1(1) = abs(lambda_vec1(1));
         
         uvec = abs(res'); uvec = uvec/sum(uvec);
         lambda_vec2 = lambda*uvec*Delta_matrix;
+        lambda_vec2(1) = abs(lambda_vec2(1));
+        
         
         screen_one_flag = sum(lambda_vec1 >= res_vec) == n-1 || ...
             sum(lambda_vec2 >= res_vec) == n-1 ;
         
         
-   
-        
[…]

### 2014-10-17 tex/scam/experiments.tex
refit description

@@
 regularization, and plot the estimated additive functions in Figure
-\ref{Boston}(e). As can be seen, these functions contain clear
+\ref{Boston}(e).
+When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave only if it is non-zero in the DC stage.
+As can be seen, these functions contain clear
 nonlinear effects which cannot be captured by LASSO. The shapes of
-these functions are in agreement with those obtained by
+these functions, including the concave shape of the \tts{PTRATIO} function, are in agreement with those obtained by
 SpAM~\citep{SpAM:07}.

### 2014-10-21 tex/scam/additive_faithful.tex
new plots
minor edits

@@
   \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}
-= 0$.  Such a limit condition however is not obeyed by many common distributions such as the multivariate Gaussian distribution. 
+= 0$.
+Such a limit condition however is not obeyed by many common distributions such as the multivariate Gaussian distribution.
+The next example shows that certain convex functions are not additive faithful under certain multivariate Gaussian distributions.
 \end{remark}
-
-The following example shows that not all convex functions are
-additively faithful under multivariate Gaussian distributions.
 
@@
 \end{align*}
-Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$.
+Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$, $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$, $c_1, c_2$ are constants such that $f^*_1$ and $f^*_2$ both have mean zero.
 Let $H = \begin{pmatrix} 1.6 & 2 \\ 2 & 5\end{pmatrix}$, then it is easy to check that if $\alpha = - \frac{1}{2}$, then $f^*_1 = 0$
 and additive faithfulness is violated, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
-We take the setting where $\alpha=-1/2$, compute the optimal additive functions via numerical simulation, and show the results in Figure~\ref{fig:gaussian_example}--$f^*_1$ is zero as expected.
+We take the setting where $\alpha=-0.5$, compute the optimal additive functions via numerical simulation, and show the results in Figure~\ref{fig:gaussian_example}--$f^*_1$ is zero as expected.
 \end{example}
 
-Interestingly, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary flatness conditions.
+Although the Gaussian distribution does not satisfy the boundary flatness condition, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary flatness conditions.
 
@@
 \label{examp:boundaryflat_example}
+Let $\Sigma$ be as in Example~\ref{examp:gaussian_counterexample} with $\alpha = -0.5$ so that $f^*_1 = 0$.
 Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$ and $U[-(b+\epsilon), b+\epsilon]^2$ is the uniform distribution over a square.
@@
 
-When $b$ is large, $\epsilon$ is small, and $\lambda$ is small, the mixture closely approximates the Gaussian distribution but is still additively faithful for all convex functions.
-Figure~\ref{fig:boundaryflat_example} shows the optimal additive function under the mixture distribution, computed by numerical simulation with $b=5, \epsilon=0.3, \lambda=0.0001$.
-We note that $f^*_1$, which is zero under the Gaussian distribution, is nonzero under the mixture distribution.
-Although $f^*_1$ is non-zero, $\E f^*_1(X_1)^2$ is small however, around $10^{-8}$ in our example.
+When $b$ is large, $\epsilon$ is small, and $\lambda$ is small, the mixture closely approximates the Gaussian distribution but is still additively faithful for convex functions.
+Figure~\ref{fig:boundaryflat_example} shows the optimal additive components under the mixture distribution, computed by numerical integration with $b=5, \epsilon=0.3, \lambda=0.0001$.
+True to our theory, $f^*_1$, which is zero under the Gaussian distribution, is nonzero under the mixture approximation to the Gaussian distribution.
+We note that the magnitude $\E f^*_1(X_1)^2$, although non-zero, is very small, consistent with the fact that the mixture distribution closely approximates the Gaussian distribution.
 \end{example}
@@
 a convex function, as example~\ref{examp:gaussian_counterexample}
-shows. 
+shows. It may be possible to estimate $f^*_k$ via smoothing, but we prefer an approach that is free of smoothing parameters. 
 %The function $f^*_k$ can be shown to be smooth but it is preferable to use
@@
 %additional smoothing bandwidth.
-Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model
+Since the true regression function $f$ is convex, we approximate the additive model with a \emph{convex} additive model.
+We abuse notation and, for the rest of the paper, use the notation $f^*_k$ to represent convex additive fits:
+%it is natural to ask when it is sufficient to estimate an convex additive model
 \begin{equation}
@@
 where $\mathcal{C}^1$ is the set of univariate convex functions. 
-While the convex functions $\{f^*_k\}$ are not additively faithful by
-themselves, faithfulness can be restored by coupling the $f^*_k$s with a set of concave functions:
+The convex functions $\{f^*_k\}$ are not additively faithful by
+themselves, i.e., it could be that $f$ depends on variable $k$ but $f^*_k = 0$. But, faithfulness can be restored by coupling the $f^*_k$'s with a set of concave fits on the \emph{residual} $f - f^*$:
 \begin{equation}
@@
 as functions of $x_k$.  Let $f^*_k$ and $g^*_k$ be as defined in equations
-\eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}.  Then
+\eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, 
 $f^*_k = 0$ and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x})
@@
 \end{theorem}
+
+Uniqueness of $f^*_k$ and $g^*_k$ follows from the fact that $p(\mathbf{x})$ is a positive density and thus the objective is strongly convex (see proof of Lemma~\ref{lem:general_int_reduction}).
+Before we can prove the rest of the theorem however, we need a lemma that generalizes Theorem~\ref{thm:convex_faithful}.
 

### 2014-10-21 tex/scam/experiments.tex
minor edits

@@
 We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
-We use independent design by setting $\Sigma = Id$.
+We use independent design by setting $\Sigma = \textrm{I}_p$.
 For each $(n,p)$ combination, we generate $100$ independent data
-sets. For each data set we use the AC/DC algorithm to estimate the model support.
-We plot the probability of
+sets.
+For each data set we use the AC/DC algorithm and mark feature $j$ as irrelevant if both the AC estimate $\| \hat{f}_j \|_\infty$ and the DC estimate $\| \hat{g}_k \|_\infty$ are smaller than $10^{-6}$.
+We plot the probability of exact
 support recovery over the $100$ data sets in Figure \ref{Support}(a).  We
@@
 ($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = Id$. We again run the AC/DC optimization on $100$
+$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
 independently generated data sets and plot the probability of recovery
@@
 instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
-$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$ with
-$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
+$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$, same as in the second experiment, with $\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
 0.6, 0.8$ are shown in Figure \ref{Support}(d). As can be seen, for
@@
 
-We first use all $n=506$ samples (with normalization) to fit AC/DC,
+We first use all $n=506$ samples (with standardization) in the AC/DC algorithm,
 using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
-with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
+ranging from $\lambda^{(1)} = 0$ (no regularization) to $2$. For each $\lambda^{(t)}$
 we obtain a function value matrix $\bds{h}^{(t)}$ with $p=13$
-rows. The non-zero rows in this matrix indicate the variables selected
+columns. The non-zero columns in this matrix indicate the variables selected
 using $\lambda^{(t)}$.  We plot $\|\bds{h}^{(t)}\|_{\infty}$ and
-the row-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
+the column-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
 $\frac{\|\bds{h}^{(t)}\|_{\infty,1}}{\|\bds{h}^{(1)}\|_{\infty,1}}$
@@
 regularization, and plot the estimated additive functions in Figure
-\ref{Boston}(e).
-When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave only if it is non-zero in the DC stage.
-As can be seen, these functions contain clear
+\ref{Boston}(e). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
 nonlinear effects which cannot be captured by LASSO. The shapes of
@@
 Next, in order to quantitatively study the predictive performance, we
-run 10 times 5-fold cross validation, following the same procedure
+run 3 times 5-fold cross validation, following the same procedure
 described above---training, variable selection and refitting.  A plot
@@
 %\hskip-10pt
-  \includegraphics[width=.37\textwidth]{figs/acdc_path} &
+  \includegraphics[width=.38\textwidth]{figs/acdc_path} &
 %\hskip-25pt
-  \includegraphics[width=.37\textwidth]{figs/lasso_path} 
+  \includegraphics[width=.38\textwidth]{figs/lasso_path} 
 \\
@@
 %\begin{tabular}{cc}
-  \includegraphics[width=.37\textwidth]{figs/MSEacdc} &
-  \includegraphics[width=.43\textwidth]{figs/acdc_functs}
+  \includegraphics[width=.38\textwidth]{figs/MSEacdc} &
+%\hskip 5pt
+  \includegraphics[width=.45\textwidth]{figs/acdc_functs}
 \\

### 2014-10-21 tex/scam/sparsistency.tex
minor edits

@@
 \item The data $X^{(1)},\ldots, X^{(n)} \sim F$ are iid from
-a distribution $F$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$. 
+a distribution $F$ with a density $p$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$. 
 \item The response is $Y = f_0(X) + W$ where $W$ is
@@
 \begin{equation}
-f^* \equiv \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
+f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
 \big)^2.
 \end{equation}
+$f^*$ is the unique minimizer since the density is positive and thus the objective is strongly convex on $\mathcal{X}$.
 Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
@@
 \end{equation}
+The set $\{\hat{g}_k\}$ is the unique minimizer as well.
 We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$.
@@
 \begin{align}
-\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
@@
 \end{align}
-These quantities play the role of the absolute value of the smallest nonzero
-coefficient in the true linear model in lasso theory.  Intuitively, if
+$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$; $\alpha_+ > 0$ since $f^*$ is the unique risk minimizer.
+Likewise, $\alpha_-$ lower bounds the excess risk of any decoupled concave fit of the residual $f_0 - f^*$ that is strictly more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$; $\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well.
+These quantities play the role of the absolute value of the smallest nonzero coefficient in the true linear model in lasso theory.
+Intuitively, if
 $\alpha_{+}$ is small, then it is easier to make a false omission in the

### 2014-10-21 tex/scam/summary.tex
minor edits

@@
 in Section~\ref{sec:additivefaithful}.
-Since the true regression function $f$ is convex, it is natural to ask
-when it is sufficient to estimate a convex additive model.  
-Unfortunately, a convex additive approximation is not generally
-faithful.  In other words, it could be that $f^*_k\equiv 0$
-even for a relevant variable $x_k$.  But our next result
-shows that this type of error can be detected by fitting 
-a \textit{concave} function to the residual.  If this
-concave function is zero, we can then safely
-mark $x_k$ as an irrelevant variable.
+It may be possible to estimate $f^*_k$ with smoothing parameters, but, for the purpose of variable screening, it is sufficient in fact to approximate $f^*_k$ by a \emph{convex} additive model.
+
+Our next result states that a convex additive fit, combined with a series of univariate concave fits, is faithful.
+We abuse notation in Theorem~\ref{thm:summary_acdc_population} and let the notation $f^*_k$ represent convex additive components.
+%Since the true regression function $f$ is convex, it is natural to ask
+%when it is sufficient to estimate a convex additive model.  
+%Unfortunately, a convex additive approximation is not generally
+%faithful.  In other words, it could be that $f^*_k\equiv 0$
+%even for a relevant variable $x_k$.  But our next result
+%shows that this type of error can be detected by fitting 
+%a \textit{concave} function to the residual.  If this
+%concave function is zero, we can then safely
+%mark $x_k$ as an irrelevant variable.
 
 \begin{stheorem}
+\label{thm:summary_acdc_population}
 Suppose $p(\mathbf{x})$ is a positive
@@
 \end{equation} where $\mathcal{C}^1$ is the set of univariate convex
-functions, and
+functions, and, with respective to $f^*_k$'s from above, define
 \begin{equation}
@@
 decoupled nature of the DC stage allows all of the fits to
-be carried out in parallel.
+be carried out in parallel. The entire process involves no smoothing parameters.
 Our next results concern the required optimizations, and their finite
@@
 
-Our analysis involves parameters $\alpha_f$ and $\alpha_g$,
+Our analysis involves parameters $\alpha_+$ and $\alpha_-$,
 which are measures of the signal strength of the weakest variable:
 \begin{align*}
-\alpha_f &= \inf_{f \in \mathcal{C}^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
+\alpha_+ &= \inf_{f \in \mathcal{C}^p \,:\, \textrm{supp}(f)\subsetneq \textrm{supp}(f^*)} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
         \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
-\alpha_g &=   \min_{k \in S \,:\, g^*_k \neq 0}
+\alpha_- &=   \min_{k \in S \,:\, g^*_k \neq 0}
       \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
@@
 
-Intuitively, if $\alpha_f$ is small, then it is easier to make a
+ Intuitively, if $\alpha_+$ is small, then it is easier to make a
 false omission in the additive convex stage of the procedure. If
-$\alpha_g$ is small, then it is easier to make a false omission in
+$\alpha_-$ is small, then it is easier to make a false omission in
 the decoupled concave stage of the procedure.

### 2014-10-21 code/paper_exp/C.m

@@ -58,7 +58,7 @@ lambda = 0.5*sqrt(1/n)*log(n*p); % MODIFY
 alpha = 0.5;
 
 maxit = 20; tol = 10^-6;
-nrun = 100; % MODIFY
+nrun = 1; % MODIFY
 J = ones(p,nrun)==0; Ln = zeros(p,nrun); 
 
 
@@ -83,7 +83,7 @@ for run = 1:nrun
     Ln(:,run) = max(Lnvex, Lncave);
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
-save(['C_' num2str(version) '.mat'],'J','Ln');
+%save(['C_' num2str(version) '.mat'],'J','Ln');
 return
 
 

### 2014-10-24 tex/scam/estimation.tex
minor edits
acdc population, new prop for alt form

@@
 
-Theorem~\ref{thm:acdc_faithful} naturally suggests a two-stage screening procedure for
-variable selection.  In the first stage we fit a sparse convex additive model.
+Theorem~\ref{thm:acdc_faithful} naturally suggests 
+a two-stage screening procedure for variable selection in the population setting:
+
+\begin{enumerate}
+\item[] \textit{First Stage (AC)}:  Estimate an additive convex model:
+\begin{equation}
+\label{eqn:scam2_pop}
+f^*_1, ..., f^*_p = \argmin_{f_1,...,f_p \in \C^1_0} 
+   \E \Big( f(X)  - \sum_{k=1}^p f_k(X_k) \Big)^2 
+\end{equation}
+\item[] \textit{Second Stage (DC)}:  Estimate concave functions
+ for each $k$ such that $ f^*_k = 0$:
+\begin{equation}
+\label{eqn:dc2}
+g^*_k = \argmin_{g_k \in \mh{}\C^1_0} 
+   \E \Big( f(X) - \sum_{k'} f^*_{k'}(X_{k'}) 
+    - g_k(X_{k})\Big)^2 
+\end{equation}
+\item[] \textit{Output}: Component functions $\{f^*_k, g^*_k\}$ and 
+relevant variables $S$ where
+\begin{equation}
+S^c = \bigl\{k : f^*_k =
+0 \; \mathrm{and}\; g^*_k =0\bigr\}.
+\end{equation}
+\end{enumerate}
+Here we denote $\C^1_0$ ($\mh{}\C^1_0$) as the set of one-dimensional convex (resp. concave) functions with population mean zero.
+
+In the first stage we fit a convex additive model.
 In the second stage, for every variable marked as irrelevant in the first stage,
@@
 that variable. We refer to this procedure as AC/DC (additive
-convex/decoupled concave).
+convex/decoupled concave). Theorem~\ref{thm:acdc_faithful} guarantees that the set of relevant variables $S_0 \subset S$.
 
-More precisely, given samples  
-$(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, 
-we perform the following steps.
-\begin{enumerate}
-\item {\it AC Stage}: Estimate an additive convex model
-\begin{equation}
-\label{eqn:scam}
-\hat{f}_1, ..., \hat{f}_p, \hat \mu  = \argmin_{f_1,...,f_p \in
-  \C^1_0, \,\mu\in\reals} 
-   \frac{1}{n} \sum_{i=1}^n \Big(y_i - \mu - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
-       + \lambda \sum_{k=1}^p \| f_k \|_\infty.
-\end{equation}
-\item {\it DC Stage}: For each $k$ such that $\| \hat{f}_k \|_\infty = 0$, estimate
-  a concave function on the residual:
-\begin{equation}
-\label{eqn:dc}
-\hat{g}_k = \argmin_{g_k \in \mh{}\C^1_0} 
-   \frac{1}{n} \sum_{i=1}^n \Big( y_i - \hat \mu - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
-    - g_k(x_{ik})\Big)^2 
-      + \lambda \| g_k \|_\infty.
-\end{equation}
-\item Output as the set of relevant variables
-$\hat S = \{ k \,:\, \| \hat{f}_k \|_\infty > 0 
-  \textrm{ or } \| \hat{g}_k \|_\infty > 0 \}$. 
-\end{enumerate}
+% More precisely, given samples  
+% $(\mathbf{x}_1, y_1), ..., (\mathbf{x}_n, y_n)$, 
+% we perform the following steps.
+% \begin{enumerate}
+% \item {\it AC Stage}: Estimate an additive convex model
+% \begin{equation}
+% \label{eqn:scam}
+% \hat{f}_1, ..., \hat{f}_p, \hat \mu  = \argmin_{f_1,...,f_p \in
+%   \C^1_0, \,\mu\in\reals} 
+%    \frac{1}{n} \sum_{i=1}^n \Big(y_i - \mu - \sum_{k=1}^p f_k(x_{ik}) \Big)^2 
+%        + \lambda \sum_{k=1}^p \| f_k \|_\infty.
+% \end{equation}
+% \item {\it DC Stage}: For each $k$ such that $\| \hat{f}_k \|_\infty = 0$, estimate
+%   a concave function on the residual:
+% \begin{equation}
+% \label{eqn:dc}
+% \hat{g}_k = \argmin_{g_k \in \mh{}\C^1_0} 
+%    \frac{1}{n} \sum_{i=1}^n \Big( y_i - \hat \mu - \sum_{k'} \hat{f}_{k'}(x_{ik'}) 
+%     - g_k(x_{ik})\Big)^2 
+%       + \lambda \| g_k \|_\infty.
+% \end{equation}
+% \item Output as the set of relevant variables
+% $\hat S = \{ k \,:\, \| \hat{f}_k \|_\infty > 0 
+%   \textrm{ or } \| \hat{g}_k \|_\infty > 0 \}$. 
+% \end{enumerate}
 
-We use an $\ell_\infty/\ell_1$ penalty in equation~\eqref{eqn:scam}
-and an $\ell_\infty$ penalty in equation~\eqref{eqn:dc} to encourage
+%For identifiability, we impose the constraint $\sum_{i=1}^n f_k(x_{ik}) =
+%0$ for each $k$.  
+It is now straightforward to construct a finite sample variable screening procedure, which we present in Figure~\ref{fig:backfitting:algo}.
+We use an $\ell_\infty/\ell_1$ penalty in equation~\eqref{eqn:scam2}
+and an $\ell_\infty$ penalty in equation~\eqref{eqn:dc2} to encourage
 sparsity.  Other penalties can also produce
@@
 theoretical analysis and implementation.
-For identifiability, we impose the constraint $\sum_{i=1}^n f_k(x_{ik}) =
-0$ for each $k$.  The set of 1-dimensional convex (concave) functions
-satisfying this mean zero constraint is denoted $\C^1_0$ ($\mh{}\C^1_0$).
 
-The optimization in \eqref{eqn:scam} appears to be infinite
+The optimization in \eqref{eqn:scam2} appears to be infinite
 dimensional, but it is equivalent to a finite dimensional quadratic

### 2014-10-24 tex/scam/optimization.tex
new linear example
new plots
minor edits
acdc population, new prop for alt form

@@
 \begin{split}
-       \min_{f,\beta,\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
+       \min_{\{f_k,\beta_k\},\mu} & \;\; \frac{1}{2n}\sum_{i=1}^{n}
                      \Bigl( y_{i}-\mu - \sum_{k=1}^{p}f_{ik}\Bigr)^{2} 
@@
 and the constraints $\sum_i f_{ki} = 0$.
-It is easy to verify that the constraints in \eqref{np} satisfy the
-supporting hyperplane constraints, since
-for all $j > i$
-\begin{align*}
-  f_{\perm{j}k}-f_{\perm{i}k}  & = \sum\limits_{t=i}^{j-1}(f_{\perm{t+1}k}-f_{\perm{t}k}) \\
-   &= \sum\limits_{t=i}^{j-1}\beta_{\perm{t}k}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
-   &\geq \beta_{\perm{i}k}\sum\limits_{t=i}^{j-1}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
-  & = \beta_{\perm{i}k}(x_{\perm{j}k}-x_{\perm{i}k}) 
-\end{align*}
-and for all $j < i$
-\begin{align*}
-f_{k(j)}-f_{k(i)} & =
-    \sum\limits_{t=j}^{i-1}(f_{k(t)}-f_{k(t+1)}) \\
-     & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\
-     &\geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) \\
-     & = \beta_{k(i)}(x_{k(j)}-x_{k(i)}).
-\end{align*}
+% It is easy to verify that the constraints in \eqref{np} satisfy the
+% supporting hyperplane constraints, since
+% for all $j > i$
+% \begin{align*}
+%   f_{\perm{j}k}-f_{\perm{i}k}  & = \sum\limits_{t=i}^{j-1}(f_{\perm{t+1}k}-f_{\perm{t}k}) \\
+%    &= \sum\limits_{t=i}^{j-1}\beta_{\perm{t}k}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
+%    &\geq \beta_{\perm{i}k}\sum\limits_{t=i}^{j-1}(x_{\perm{t+1}k}-x_{\perm{t}k}) \\
+%   & = \beta_{\perm{i}k}(x_{\perm{j}k}-x_{\perm{i}k}) 
+% \end{align*}
+% and for all $j < i$
+% \begin{align*}
+% f_{k(j)}-f_{k(i)} & =
+%     \sum\limits_{t=j}^{i-1}(f_{k(t)}-f_{k(t+1)}) \\
+%      & = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{\perm{t}k}-x_{\perm{t+1}k}) \\
+%      &\geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{\perm{t}k}-x_{\perm{t+1}k}) \\
+%      & = \beta_{k(i)}(x_{\perm{j}k}-x_{\perm{i}k}).
+% \end{align*}
 
@@
 \begin{split}
-      \hat f(\bds{x}) & = \sum_{k=1}^{p} \hat f_k(x_{j})+ \hat \mu 
+      \hat f(\bds{x}) & = \sum_{k=1}^{p} \hat f_k(x_{k})+ \hat \mu 
 = \sum_{k=1}^{p}\max_{i} \Bigl\{\hat f_{ik}+ \hat \beta_{ik}(x_{k}-x_{ik})\Bigr\} +
@@
 Optimization \eqref{np} can be reformulated in terms of the second
-derivatives.  We exploit this form in our theoretical analysis.
+derivatives. The alternative formulation replaces the order constraints
+$\beta_{\perm{i+1}k} \geq \beta_{\perm{i}k}$ with positivity constraints, which
+simplifies the analysis.
 
-The alternative formulation replaces the order constraints
-$\beta_{\perm{i+1}k} \geq \beta_{\perm{i}k}$ with positivity constraints, which
-simplifies the analysis.  Define $d_{\perm{i}k}$ as the second
+%Let $\{\hat{f}_k, \hat{\beta}_k\}$ be a solution to optimization 4.2 (ref).
+
+% Let $\hat{d}_k$ be defined as beta difference, then \hat{d}_k is the minimizer of ...
+
+Define $d_{\perm{i}k}$ as the second
 derivative: $d_{\perm{1}k} = \beta_{\perm{1}k}$, and $d_{\perm{i}k} = \beta_{\perm{i}k} -
@@
 \mathbf{1}_n^\tran \Delta_k d_k$, and therefore
-\[
+\begin{equation}
 \Delta_k d_k + \mu_k \mathbf{1}_n = 
@@
    \bar{\Delta}_k d_k 
-\]
+\label{eq:deltabar_defn}
+\end{equation}
 where $\bar{\Delta}_k \equiv \Delta_k - \frac{1}{n} \mathbf{1}_n \mathbf{1}_n^\tran \Delta_k$ is $\Delta_k$ with the mean of each column subtracted.
 
-We can now reformulate \eqref{np} as an equivalent optimization program with only centering and positivity constraints:
+The above derivations prove the following proposition, which states that \eqref{np} has an alternative formulation.
+
+\begin{proposition}
+
+Let $\{\hat{f}_k, \hat{\beta}_k\}_{k=1,...,p}$ be an optimal solution to \eqref{np} and suppose $\bar{Y} = 0$.
+Define vectors $\hat{d}_k \in \R^{n-1}$ such that $\hat{d}_{\pi_k(1)k} = \hat{\beta}_{\pi_k(1)k}$ and $\hat{d}_{\pi_k(i)k} = \hat{\beta}_{\pi_k(i)k} - \hat{\beta}_{\pi_k(i-1)k}$ for $i > 1$.
+Then $\hat{f}_k = \bar{\Delta}_k \hat{d}_k$ and $\hat{d}_k$ is an optimal solution to the following optimization:
 \begin{align}
-\min_{d_k}\;\; & \frac{1}{2n} 
+\min_{\{d_k \in \R^{n-1}\}_{k=1,...p}}\;\; & \frac{1}{2n} 
        \Bigl\| Y - \sum_{k=1}^p 
@@
 \end{align}
+Likewise, suppose $\{\hat{d}_k\}_{k=1,...p}$ is a solution to \eqref{opt:alternate_opt}, define $\hat{\beta}_{\pi_k(i)k} = \sum_{j\leq i} \hat{d}_{\pi_k(j)k}$ and $\hat{f}_k = \bar{\Delta}_k \hat{d}_k$.
+Then $\{\hat{f}_k, \hat{\beta}_k\}_{k=1,...,p}$ is an optimal solution to \eqref{np}.
+$\bar{\Delta}$ is a $n$ by $n-1$ matrix defined by \eqref{eq:deltabar_defn}.
+
+\end{proposition}
 

### 2014-10-25 tex/scam/sparsistency.tex
acdc population, new prop for alt form
minor fix

@@
 
+%Our goal is to show that, as $n \rightarrow \infty$ and $p$ scales as $exp(-n^c)$, we have that the set of variables outputted by  $\hat{S}$
+
 We divide our analysis into two parts. We first establish a sufficient
 deterministic condition for consistency of the sparsity pattern
-selection procedure---a property sometimes called \textit{sparsistency}.
-We then consider the
+screening procedure.  We then consider the
 stochastic setting and argue that the deterministic conditions hold
@@
 \end{corollary}
-The above corollary implies that sparsistency is achievable at the
-same exponential scaling of the ambient dimension scaling attained
-with parametric models, $p = O(\exp(n^c))$ for $c<1$.  The cost of
-nonparametric modeling through shape constraints 
-is reflected in the scaling with respect to
-the number of relevant variables, which can scale as $s = o(n^{4/25})$.
+The above corollary implies that consistent variable selection is
+achievable at the same exponential scaling of the ambient dimension
+scaling attained with parametric models, $p = O(\exp(n^c))$ for $c<1$.
+The cost of nonparametric modeling through shape constraints is
+reflected in the scaling with respect to the number of relevant
+variables, which can scale as $s = o(n^{4/25})$.
 

### 2014-10-25 tex/scam/summary.tex
minor edits

@@
 $k \in S^c$, where $S\subset \{1,\ldots, p\}$ is the set of
-relevant variables. 
+variables selected by the AC/DC algorithm in the population setting.
 To control false negatives, we analyze the restricted regression

### 2014-10-25 tex/scam/summary.tex
tried to fix the abrupt changes

@@
 \end{align}
-See \cite{Boyd04}, Section 6.5.5.
 Here $f_i$ is the estimated function value $f(\x_i)$, and the vectors
 $\beta_i \in \reals^d$ represent supporting hyperplanes to the
-epigraph of $f$.  Importantly, this finite dimensional quadratic program does
+epigraph of $f$.  See \cite{Boyd04}, Section 6.5.5.
+Importantly, this finite dimensional quadratic program does
 not have tuning parameters for smoothing the function.
 
+This formulation of convex regression is subject to the curse
+of dimensionality.  Moreover, attempting to select variables
+by regularizing the subgradient vectors $\beta_i$ with
+a group sparsity penality is not effective.  Intuitively, the reason
+is that all $p$ components of the subgradient $\beta_i$
+appear in every convexity constraint 
+$ f_j \geq f_i + \beta_i^T (\x_j-\x_i)$; small changes to the 
+subgradients may not violate the constraints.  Experimentally,
+we find that regularization with a group sparsity penality
+will make the subgradients of irrelevant variables 
+small, but may not zero them out completely.
+
+This motivates us to consider an additive approximation. 
+Under a convex additive model, each component of the subgradient
+appears only in the convexity constraint for
+the corresponding variable:
+\begin{equation}
+f_{ki'} \geq f_{ki} + \beta_{ki}(x_{ki'}-x_{ki}) 
+\end{equation}
+where $f_{ki} = f_{k}(x_{ki})$ and $\beta_{ki}$ is the
+subgradient at point $x_{ki}$.   As we show, this leads to
+an effective variable selection procedure.  The
+shape constraints play an essential role.
 For general regression, using an additive approximation for variable
@@
 regression function may result in an additive component being wrongly
-zeroed out.  We show that this will not happen for convex regression
+zeroed out.  We show that this cannot happen for convex regression
 under appropriate conditions.

### 2014-10-25 tex/scam/estimation.tex
theory section add

@@
 Theorem~\ref{thm:acdc_faithful} naturally suggests 
-a two-stage screening procedure for variable selection in the population setting:
-
-\begin{enumerate}
-\item[] \textit{First Stage (AC)}:  Estimate an additive convex model:
+a two-stage screening procedure for variable selection in the population setting. In the first stage, we fit a convex additive model. 
 \begin{equation}
@@
 \end{equation}
-\item[] \textit{Second Stage (DC)}:  Estimate concave functions
+where we denote $\C^1_0$ ($\mh{}\C^1_0$) as the set of one-dimensional convex (resp.
+concave) functions with population mean zero.
+In the second stage, for every variable marked as irrelevant in the first stage, we fit a univariate \emph{concave} function separately on the residual for that variable.
  for each $k$ such that $ f^*_k = 0$:
@@
 \end{equation}
-\item[] \textit{Output}: Component functions $\{f^*_k, g^*_k\}$ and 
-relevant variables $S$ where
+We screen out $S^C$, any variable $k$ that is zero after the second stage, and output $S$.
 \begin{equation}
+\label{eqn:acdc_vars_pop}
 S^c = \bigl\{k : f^*_k =
@@
 \end{equation}
-\end{enumerate}
-Here we denote $\C^1_0$ ($\mh{}\C^1_0$) as the set of one-dimensional convex (resp. concave) functions with population mean zero.
 
-In the first stage we fit a convex additive model.
-In the second stage, for every variable marked as irrelevant in the first stage,
-we fit a univariate \emph{concave} function separately on the residual for
-that variable. We refer to this procedure as AC/DC (additive
-convex/decoupled concave). Theorem~\ref{thm:acdc_faithful} guarantees that the set of relevant variables $S_0 \subset S$.
+We refer to this procedure as AC/DC (additive
+convex/decoupled concave). Theorem~\ref{thm:acdc_faithful} guarantees that the true set of relevant variables $S_0$ must be a subset of $S$.
 
@@
 %0$ for each $k$.  
-It is now straightforward to construct a finite sample variable screening procedure, which we present in Figure~\ref{fig:backfitting:algo}.
+It is straightforward to construct a finite sample variable screening procedure, which we describe in Figure~\ref{fig:backfitting:algo}.
 We use an $\ell_\infty/\ell_1$ penalty in equation~\eqref{eqn:scam2}

### 2014-10-25 tex/scam/optimization.tex
theory section add

@@
 \begin{proposition} 
-
+\label{prop:alt_opt_form}
 Let $\{\hat{f}_k, \hat{\beta}_k\}_{k=1,...,p}$ be an optimal solution to \eqref{np} and suppose $\bar{Y} = 0$.
@@
 Then $\{\hat{f}_k, \hat{\beta}_k\}_{k=1,...,p}$ is an optimal solution to \eqref{np}.
-$\bar{\Delta}$ is a $n$ by $n-1$ matrix defined by \eqref{eq:deltabar_defn}.
+$\bar{\Delta}$ is the $n$ by $n-1$ matrix defined by \eqref{eq:deltabar_defn}.
 
@@
 
-\begin{remark}
-  In our analysis, we assume that an upper bound $B$ to
-  $\| f^*_k \|_\infty$ is known, and that we constrain our estimate
-  $\hat{f}$ to obey the same boundedness condition.  That is, for each
-  $k$, we require that $\|\hat{f}_k\|_\infty \leq B$. This boundedness
-  constraint can be easily added to our optimization program. In
-  optimization~\eqref{opt:alternate_opt}, we can enforce the boundedness
-  condition by adding $p$ constraints $\| \bar{\Delta}_k d_k
-  \|_\infty \leq B$ for $k=1,\ldots,p$ (and similarly for
-  optimization~\eqref{opt:alternate_opt_concave}). We emphasize that we
-  use the boundedness constraint only in our theoretical analysis; 
-  our experiments do not impose any such condition.
-\end{remark}
-
 % DO NOT CHANGE; RefTex variables -minx

### 2014-10-25 tex/scam/sparsistency.tex
theory section add

--- 2014-10-21 tex/scam/sparsistency.tex
@@
-\section{Analysis of Variable Selection Consistency}
+\section{Analysis of Variable Screening Consistency}
 \label{sec:finitesample}
 
+Our goal is to show that variable screening consistency.
+That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Algorithm~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.
+
 We divide our analysis into two parts. We first establish a sufficient
-deterministic condition for consistency of the sparsity pattern
-selection procedure---a property sometimes called \textit{sparsistency}.
-We then consider the
+deterministic condition that $\hat{S} = S$ and we then consider the
 stochastic setting and argue that the deterministic conditions hold
@@
 C$ represent absolute constants; the actual values of $c,C$ may change from line to line.
+We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$.
+Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis without further stating their relationships.
+
+In our analysis, we assume that an upper bound $B$ to $\| \hat{f}_k \|_\infty$ 
+is imposed in the optimization procedure, where $B \geq \| f^*_k \|_\infty$.
+This $B$-boundedness constraint is added so that we may use the convex function bracketing results from~\cite{kim2014global} to establish uniform convergence between the empirical risk and the population risk.
+We emphasize that this constraint is not needed in practice and we do not use it for any of our simulations.
 
@@
 
-We construct an additive convex solution $\{\hat{d}_k\}_{k=1,\ldots,p}$
+We analyze Optimization~\ref{opt:alternate_opt} and construct an additive convex solution $\{\hat{d}_k\}_{k=1,\ldots,p}$
 that is zero for $k \in S^c$, where $S$ is the set of relevant

### 2014-10-25 tex/scam/sparsistency.tex

@@
 We divide our analysis into two parts. We first establish a sufficient
-deterministic condition that $\hat{S} = S$ and we then consider the
-stochastic setting and argue that the deterministic conditions hold
-with high probability. Note that in all of our results and analysis, we let $c,
+deterministic condition for consistency of the sparsity pattern
+screening procedure.  We then consider the stochastic setting and argue that the 
+deterministic conditions hold with high probability. Note that in all of our results 
+and analysis, we let $c,
 C$ represent absolute constants; the actual values of $c,C$ may change from line to line.

### 2014-10-27 tex/scam/additive_faithful.tex
more citations

@@
 additive approximation accurately captures all of the relevant variables.
-We call this property \textit{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{depends on} a coordinate $x_k$.
+We call this property \textit{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{does not depends on} a coordinate $x_k$.
 
 \begin{definition}
-  Let $F$ be a distribution on $C=[0,1]^p$, and $f:C \rightarrow \R$. 
-We say that $f$ \textit{depends on coordinate $k$} if, for all $x_k \in [0,1]$, the set 
-$\big\{ x'_k \in [0, 1] \,:\, f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k}) 
-\trm{ for almost all  $\mathbf{x}_{-k}$} \big\}$ 
-has probability strictly less than one.
-If $f$ is differentiable, then $f$ depends on $k$ if $\partial_{x_k} f \neq 0$ with probability greater than zero.
+%   Let $F$ be a distribution on $C=[0,1]^p$, and $f:C \rightarrow \R$. 
+% We say that $f$ \textit{depends on coordinate $k$} if, for all $x_k \in [0,1]$, the set 
+% $\big\{ x'_k \in [0, 1] \,:\, f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k}) 
+% \trm{ for almost all  $\mathbf{x}_{-k}$} \big\}$ 
+% has probability strictly less than one.
+% If $f$ is differentiable, then $f$ depends on $k$ if $\partial_{x_k} f \neq 0$ with probability greater than zero.
+Let $C = [0,1]^p$ and let $f: C \rightarrow \R$.
+We say that $f$ \textit{does not depends on coordinate $k$} if for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a constant as a function of $x_k$.
+If $f$ is differentiable, then $f$ does not depend on $k$ if $\partial_{x_k} f(x_k, \mathbf{x}_{-k})$ is 0 for all $\mathbf{x}_{-k}$.
 
-Suppose we have the additive approximation
+In addition, suppose we have a distribution over $C$ and the additive approximation
 \begin{equation}
@@
 \end{equation}
-We say that $f$ is \textit{additively faithful} under $F$ in case
+We say that $f$ is \textit{additively faithful} under $F$ if
 $f^*_k = 0$ implies that $f$ does not depend on coordinate $k$.
@@
 $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =
-\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at
+\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at boundary
 points $x_j = 0, x_j=1$. The boundary flatness property is also
@@
 The convex functions $\{f^*_k\}$ are not additively faithful by
-themselves, i.e., it could be that $f$ depends on variable $k$ but $f^*_k = 0$. But, faithfulness can be restored by coupling the $f^*_k$'s with a set of concave fits on the \emph{residual} $f - f^*$:
+themselves, i.e., it could be that the true function $f$ depends on variable $k$ but $f^*_k = 0$.
+However, faithfulness can be restored by coupling the $f^*_k$'s with a set of univariate concave fits on the \emph{residual} $f - f^*$:
 \begin{equation}
@@
 
-Uniqueness of $f^*_k$ and $g^*_k$ follows from the fact that $p(\mathbf{x})$ is a positive density and thus the objective is strongly convex (see proof of Lemma~\ref{lem:general_int_reduction}).
-Before we can prove the rest of the theorem however, we need a lemma that generalizes Theorem~\ref{thm:convex_faithful}.
+Before we can prove the theorem, we need a lemma that generalizes Theorem~\ref{thm:convex_faithful}.
 
@@
 
-Under the derivative continuity conditions in the theorem, we apply Lemma~\ref{lem:acdc_derivative_bound} and know that $h^*_k(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$.
+Under the derivative continuity conditions in the theorem, we apply Lemma~\ref{lem:acdc_derivative_bound} in the appendix and know that $h^*_k(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$.
 Therefore, for a large enough positive scalar $\alpha$, $h^*_k(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second derivative and is thus convex.
@@
 f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that
-$f^*_k = 0$ and $g^*_k = 0$ together imply that $f$ does not depend on $x_k$.
+$f^*_k = 0$ and $g^*_k = 0$ together imply that $f$ does not depend on $x_k$.\\
+
+Now we turn to uniqueness.
+Suppose for sake of contradiction that $f^*$ and $f'$ are optimal solutions to (\ref{eqn:convex_additive}) and $\E (f'-f^*)^2 > 0$.
+$f^* + \lambda ( f' - f^*)$ for any $\lambda \in [0,1]$ must then also be an optimal solution by convexity of the objective and constraint.
+However, the second derivative of the objective $\E( f - f^* - \lambda(f' - f^*))^2$ with respect to $\lambda$ is $2 \E( f' - f^*)^2 > 0$.
+The objective is thus strongly convex and $f^*, f'$ cannot both be optimal.
+The uniqueness of $g^*$ is proved similarly.
 \end{proof}

### 2014-10-27 tex/scam/appendix.tex
minor typo
more citations

@@
 
-The Lagrangian form of the optimization, in term of just $d_k$, is
+The Lagrangian form of the optimization, in terms of just $d_k$, is
 \[
@@
 \begin{proof}
-
-\textbf{Step 1.} We start from the definition.
+\textbf{Step 1.} $\hat{f}$ minimizes the penalized empricial risk by definition.
+We would thus like to say that the penalized empirical risk of $\hat{f}$ is no larger than that of $f^*$.
+We cannot do a direct comparison because the empirical mean $\frac{1}{n} \sum_i f^*_k(x_{ik})$ is close to but not exactly zero.
+We thus have to work first with the function $f^* - \bar{f}^*$.
 
@@
 \| y - \hat{f} \|_n^2 + \lambda \sum_{k=1}^s \| \hat{f}_k \|_\infty &\leq
-  \| y - f^* + \bar{f}^* \|_n^2 + \lambda \sum_{k=1}^s \| f^*_k - \bar{f}^* \|_\infty 
+  \| y - f^* + \bar{f}^* \|_n^2 + \lambda \sum_{k=1}^s \| f^*_k - \bar{f}^*_k \|_\infty 
 \end{align*}

### 2014-10-27 tex/scam/introduction.tex
test
more citations

@@
 analysis of the procedure, where we upper bound the statistical rate
-of convergence.  An additional contribution is to show how the
+of variable screening consistency.  An additional contribution is to show how the
 required quadratic programs can be formulated to be more scalable.  We
@@
 tractable, nonparamametric relaxation of the linear model.
+
+Recently, there has been a flurry of research activity on shape-constrained estimation.
+\cite{seijo2011nonparametric} and \cite{Lim:12} independently established the consistency of multivariate convex regression, though without an explicit rate.
+\cite{Cule:10} and \cite{kim2014global} analyzed log-concave density estimation and showed consistency of the MLE with a rate of [TODO:find rate].
+Additive shape-constrained modeled were studied by \cite{chen2014generalised} and \cite{pya2014shape}.
+To the best of our knowledge however, there has been no work on variable selection for shape-constrained estimation.
 
@@
 
-Perhaps most closely related to the present work is the framework
+Perhaps more closely related to the present work is the framework
 studied by \cite{Raskutti:12} for sparse additive models, where sparse

### 2014-10-27 tex/scam/sparsistency.tex
more citations

@@
 We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$.
-Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis without further stating their relationships.
+Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis.
 
@@
 \end{equation}
-$f^*$ is the unique minimizer since the density is positive and thus the objective is strongly convex on $\mathcal{X}$.
-Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
+$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
 \begin{equation}
@@
 \end{equation}
-The set $\{\hat{g}_k\}$ is the unique minimizer as well.
+The $\hat{g}_k$'s are unique minimizers as well.
 We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$.
 By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$.
-In some cases such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
+In some cases, such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
 Each of our theorems will use a subset of the following assumptions:
@@
 Theorem~\ref{thm:false_negative} to use our additive faithfulness
-result, Theorem~\ref{thm:convex_faithful}. We also include an extra
-boundedness constraint so that we can use recent bracketing number
-results \cite{kim2014global}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.
+result, Theorem~\ref{thm:convex_faithful}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.
 

### 2014-10-27 tex/scam/introduction.tex
citation edit

@@
 
-Recently, there has been a flurry of research activity on shape-constrained estimation.
-\cite{seijo2011nonparametric} and \cite{Lim:12} independently established the consistency of multivariate convex regression, though without an explicit rate.
-\cite{Cule:10} and \cite{kim2014global} analyzed log-concave density estimation and showed consistency of the MLE with a rate of [TODO:find rate].
-Additive shape-constrained modeled were studied by \cite{chen2014generalised} and \cite{pya2014shape}.
-To the best of our knowledge however, there has been no work on variable selection for shape-constrained estimation.
+Recently, there has been increased research activity on shape-constrained estimation.
+\cite{guntusen:13} analyze univariate convex regression and show surprisingly that the risk of the MLE is adaptive to the complexity of the true function.
+\cite{seijo2011nonparametric} and \cite{Lim:12} study maximum likelihood estimation of multivariate convex regression and independently establish its consistency.
+\cite{Cule:10} and \cite{kim2014global} analyze log-concave density estimation and prove consistency of the MLE; the latter further show that log-concave density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$ for $d \geq 2$, refuting a common notion that the condition of convexity is equivalent, in estimation difficulty, to the condition of having two bounded derivatives.
+\cite{pya2014shape} and then \cite{chen2014generalised} both look at additive shape-constrained models.
+To the best of our knowledge though, there has not yet been any work on variable selection and high-dimensional estimation of convex functions.
 
@@
 But the method only provably scales to dimensions $p$ that 
-grow logarithmically in the sample size $n$, so that $p = O(\log n)$.  This
+grow logarithmically in the sample size $n$, i.e., $p = O(\log n)$.  This
 is in contrast to the high dimensional scaling behavior
 known to hold for sparsity selection in linear models
-using $\ell_1$ penalization, where the sample size $n$
+using $\ell_1$ penalization, where $n$
 is logarithmic in the dimension $p$. \citet{bertin:08}

### 2014-10-28 tex/scam/introduction.tex
new citation

@@
 \cite{Cule:10} and \cite{kim2014global} analyze log-concave density estimation and prove consistency of the MLE; the latter further show that log-concave density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$ for $d \geq 2$, refuting a common notion that the condition of convexity is equivalent, in estimation difficulty, to the condition of having two bounded derivatives.
-\cite{pya2014shape} and then \cite{chen2014generalised} both look at additive shape-constrained models.
-To the best of our knowledge though, there has not yet been any work on variable selection and high-dimensional estimation of convex functions.
+Additive shape-constrained estimation has also been studied; \cite{pya2014shape} propose a penalized B-spline estimator while \cite{chen2014generalised} show the consistency of the MLE.
+To the best of our knowledge however, there has been no work on variable selection and high-dimensional estimation of convex functions.
 
@@
 the component Hilbert spaces must be chosen, leading to extra tuning
-parameters that are difficult to select in practice.  In addition, the
-additive model must be assumed to be correct for consistent variable
-selection.
+parameters that are difficult to select in practice. \cite{huang2010variable} 
+too formulate sparse additive spline fitting as a convex optimization but
+their procedure too requires a smoothing parameter in the form of 
+a truncation level for the spline basis.
 

### 2014-11-02 tex/scam/appendix.tex
edited through 8.2

@@
 We restate Theorem~\ref{thm:deterministic} first for convenience. 
+The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.
 
 \begin{theorem} 
-The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.
-
 Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
-Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\
-
-Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
-\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\
-
+Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual.
+
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
+\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.
 Then the following are true:
@@
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
-\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
+\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and must be unique.
 \end{enumerate}
@@
 \begin{proof} 
-We will omit the Lipschitz constraint in our proof here. It is easy to add that in and check that the result of the theorem still holds.\\
-
-We first consider the first item in the conclusion of the theorem.
-
-We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.\\
+We will omit the Lipschitz constraint in our proof here. It can be
+added in and easily verified that the result of the theorem still holds.
+
+We begin by considering the first item in the conclusion of the theorem.
+We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we
+can set the dual variables to satisfy the 
+complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.
 
@@
 We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$. 
-
 The Lagrangian form of the optimization, in terms of just $d_k$, is
@@
 
-The derivative of the Lagrangian is:
+The derivative of the Lagrangian is
 \begin{align*}
@@
 
-We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.
-
+We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to zero,
 \begin{align*}
@@
 where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$.
-It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ hwere the inequality is element-wise.
-
-Let us reorder the samples so that the $i$-th sample is the $i$-smallest sample. \\
-
-We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for some $0 < a < 1/2$. (coordinates of $\mathbf{u}$ correspond to the new sample ordering) We then just need to show that
+It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ where the inequality is element-wise.
+
+Let us reorder the samples so that the $i$-th sample is the $i$-th smallest sample. 
+We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for
+some $0 < a < 1/2$, where the coordinates of $\mathbf{u}$ correspond
+to the new sample ordering. 
+We then just need to show that
 \begin{align*}
@@
 \end{align*}
-where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that:
-
+where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that
 \begin{align*}
@@
 - \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
-- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0
-\end{align*}
-
-We have thus proven that there exist one solution $\{ \hat{d}_k \}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in S^c$.
-Furthermore, we have shown that the subgradient variables $\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.
-We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as well.
-\\
-
-%% prove uniqueness of sparsity pattern.
-
-We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k = \sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$.
-If this were not true, then a convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly lower objective on the quadratic term.
-More precisely, let $\zeta \in [0,1]$.
-If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k \big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is strongly convex as a function of $\nu$.
-Thus, it cannot be that $\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective and we have reached a contradiction.\\
-
-Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$ and $\{ \hat{d}'_k \}$.
-Let $\mathbf{u}_k \in \partial \| \bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k \in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets of subgradients.
-Let $\{ \nu_{ki} \}_{k=1,..,p,\, i=1,...n-1}$ and $\{ \nu'_{ki} \}$ be the two sets of positivity dual variables.
-\footnote{since there is no positivity constraint on $d_{k1}$, we let $\nu_{k1} = 0$ always.}
+- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0.
+\end{align*}
+We have thus proven that there exists one solution $\{ \hat{d}_k
+\}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in
+S^c$. Furthermore, we have shown that the subgradient variables
+$\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such
+that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.
+
+We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another
+solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as
+well.  We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k =
+\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$. If this were not true, then a
+convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly
+lower objective on the quadratic term. More precisely, let $\zeta \in
+[0,1]$. If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p
+\bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k
+\big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is
+strongly convex as a function of $\nu$. Thus, it cannot be that
+$\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective, and we
+have reached a contradiction.
+
+Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$
+and $\{ \hat{d}'_k \}$. Let $\mathbf{u}_k \in \partial \|
+\bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k
+\in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets
+of subgradients. Let $\{ \nu_{ki} \}$ and $\{
+\nu'_{ki} \}$ be the two sets of positivity dual
+variables, for $k=1,..,p$ and $i=1,...n-1$.  Note that since there is no positivity constraint on
+$d_{k1}$, we let $\nu_{k1} = 0$ always.
 
@@
 
-Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}', \mathbf{u}', \nu')$ must satisfy the stationarity condition, we have that:
+Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}',
+\mathbf{u}', \nu')$ must satisfy the stationarity condition, we have
+that
 \[
@@
 \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
-   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0
-\] 
-We multiply both sides of the above equation by $\hat{d}'$:
+   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0.
+\] 
+Multiplying both sides of the above equation by $\hat{d}'$,
 \[
@@
     + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
-    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'
-\]
-Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that:
-\[
-\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty
+    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'.
+\]
+Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
+\[
+\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty.
 \]
@@
 \]
-
-On the other hand, by Holder's inequality:
+On the other hand, by H\"older's inequality,
 \begin{align*}
 \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
-   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 
-\end{align*}
-
+   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 .
+\end{align*}
 Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$.
-We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.\\
+We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.
 
 The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way. 
-
-The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is:
+The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is
 \[
@@
   \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
-  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
-\]
-
-The exact same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
-
+  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}.
+\]
+The same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
 \end{proof}
@@
 We will then use Serfling's theorem on the concentration of measure of sampling without replacement.
-(corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.\\
+(corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.
 
@@
 Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions.
-\\
 
@@
 
-By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\
+By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$.
 
@@
 
-Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction. \\
+Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction.
 
@@
 Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$.
-$\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.\\
+$\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.
 
@@
 Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$.
-Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.\\
+Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.
 
@@
 %For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$.
-It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\
+It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.
 
@@
 Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$.
-Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.\\
+Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.
 
@@
 
-\begin{proposition} (Proposition 16 in \cite{kim2014global})\\
+\begin{proposition} (Proposition 16 in \cite{kim2014global})
 \label{prop:convexbracket}
@@
 There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$.
-The inequality follows from a direct application of union bound and Hoeffding Inequality.\\
+The inequality follows from a direct application of union bound and Hoeffding Inequality.
 \end{proof}

### 2014-11-02 tex/scam/appendix.tex
edited up to 8.3

@@
 
-\textbf{Note:} the symbols $c,C$ represent absolute constants.
-We will often abuse notation and ``absorb'' new absolute constants into $c, C$; the actual value of $c, C$ could thus vary from line to line.
-
+ We note that in the following analysis the symbols $c,C$ represent
+ absolute constants. We will often abuse notation and ``absorb'' new
+ absolute constants into $c, C$; the actual value of $c, C$ could thus
+ vary from line to line.
 We first restate the theorem for convenience.
@@
 \begin{theorem} 
-Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$. Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-Suppose $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$, then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
-\[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|
-\]
-
-And therefore，for all $k \in S^c$, both the AC solution $\hat{f}_k$, from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$, from optimization~\ref{opt:alternate_opt_concave} are zero.
+Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+
+If $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
+\[
+\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|.
+\]
+Therefore, for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$ from optimization~\ref{opt:alternate_opt_concave} are zero. 
 \end{theorem}
@@
 
-Fix $j$ and $i$.
-$\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$.
-We will then use Serfling's theorem on the concentration of measure of sampling without replacement.
-(corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.
-
-\textbf{Step 1}: Bounding $\| \hat{r} \|_\infty$.
-
-$\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where $\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex additive function outputted by the restricted regression.
-
-Both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $sB$.
-
+Fix $j$ and $i$. Then $\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is the sum
+of $n-i'+1$ random coordinates of $\hat{r}$. We will use
+Serfling's theorem on the concentration of measure of sampling without
+replacement (Corollary~\ref{cor:serfling}). We must first bound $\|
+\hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we
+can use Serfling's results however.
+
+\vskip5pt
+\textbf{Step 1}: {\it Bounding $\| \hat{r} \|_\infty$.} We have $\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where
+$\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex
+additive function outputted by the restricted regression. Note that
+both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $sB$. 
 Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
@@
 
-We now put this together: 
+Putting these observations together,
 %and take another union bound across all $j$ and all $i'$:
@@
 \end{align}
-with probability at least $1 - \delta$.
-We define $\tilde{\sigma} = \max(\sigma, B)$.
-We also supposed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$, which is acceptable since $\delta \leq 1$ and the theorem presupposes that $\sqrt{ \log 2np } \geq 1$.
-
-\textbf{Step 2}: Bounding $| \frac{1}{n} \hat{r}^\tran \mathbf{1} |$.
-
+with probability at least $1 - \delta$, where we have defined
+$\tilde{\sigma} = \max(\sigma, B)$,
+and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$, which is acceptable since $\delta \leq 1$ and the theorem presupposes that $\sqrt{ \log 2np } \geq 1$.
+
+\vskip5pt
+\textbf{Step 2}: {\it Bounding $| \frac{1}{n} \hat{r}^\tran \mathbf{1}
+  |$.}  We have that 
 \begin{align*}
@@
     \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i - \hat{f}(x_i) \\
-  &= \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i \quad \trm{ ($\hat{f}$ is centered)}
-\end{align*}
-
-Because $|f_0(x_i)| \leq sB$, the first term $| \frac{1}{n} \sum_{i=1}^n f_0(x_i)|$ is at most $sB \sqrt{\frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$ by Hoeffding Inequality.
-
-Because $w_i$ is sub-Gaussian, the second term $|\frac{1}{n} \sum_{i=1}^n w_i|$ is at most $\sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta}}$ with probability at most $1-\delta$.
-
-Taking an union bound, we have that
-
+  &= \frac{1}{n} \sum_{i=1}^n f_0(x_i) + w_i \quad \trm{ ($\hat{f}$ is centered)}.
+\end{align*}
+Since $|f_0(x_i)| \leq sB$, the first term $| \frac{1}{n} \sum_{i=1}^n
+f_0(x_i)|$ is at most $sB \sqrt{\frac{2}{n} \log \frac{2}{\delta}}$
+with probability at most $1-\delta$ by Hoeffding's inequality. Since
+$w_i$ is sub-Gaussian, the second term $|\frac{1}{n} \sum_{i=1}^n
+w_i|$ is at most $\sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta}}$
+with probability at most $1-\delta$.  
+Taking a union bound, we have that 
 \begin{align}
@@
 \end{align}
-with probability at least $1-\delta$.\\
-
-\textbf{Step 3}: We now apply Serfling's theorem.
-
-For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$:
+with probability at least $1-\delta$.
+
+\vskip5pt
+\textbf{Step 3}: {\it Apply Serfling's theorem.}  
+For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$
 \begin{align*}
@@
 \end{align*}
-
-We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' = 1,...,n$.
-We also need the events that $\|\hat{r}\|_\infty$ and $| \frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold.
-The following follows from a union bound.
-With probability at least $1-\delta$, for all $k,i'$,
+We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' =
+1,...,n$. We also need the events that $\|\hat{r}\|_\infty$ and $|
+\frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold. Using a
+union bound, with probability at least $1-\delta$, for all $k,i'$,
 \begin{align*}
@@
 \end{align*}
-
-In the second inequality, we used equation~\ref{eqn:stepone_rhat} and equation~\ref{eqn:steptwo_rhat} from step 1 and 2 respectively. Setting $\delta = \frac{12}{n}$ gives the desired result.
-
+In the second inequality, we used equation~\eqref{eqn:stepone_rhat}
+and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
+respectively. Setting $\delta = \frac{12}{n}$ gives the desired
+result.
 \end{proof}
@@
  \label{sec:false_negative_proof}
-
-\textbf{Note:} the symbols $c,C$ represent absolute constants.
-We will often abuse notation and ``absorb'' new absolute constants into $c, C$; the actual value of $c, C$ could thus vary from line to line.
-
- We first introduce notations.
+ We begin by introducing some notation.
  \subsubsection{Notation} 

### 2014-11-02 tex/scam/appendix.tex
edited up to 8.3

@@
 \label{sec:false_negative_proof_notations}
-
-Let $f : \mathbb{R}^s \rightarrow \R$, we denote $\| f \|_P \equiv \E f(X)^2$. \\
-Given samples $X_1,...,X_n$, we denote $\| f \|_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i)^2$ and $\langle f, g \rangle_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i) g(X_i)$. \\
+If $f : \mathbb{R}^s \rightarrow \R$, we define $\| f \|_P \equiv \E f(X)^2$. 
+Given samples $X_1,...,X_n$, we denote $\| f \|_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i)^2$ and $\langle f, g \rangle_n \equiv \frac{1}{n} \sum_{i=1}^n f(X_i) g(X_i)$.
 
@@
 Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions.
-
-Define $\mathcal{C}^s$ as the set of convex additive functions and $\mathcal{C}^s_B$ likewise as the set of convex additive functions whose components are $B$-bounded.
+Define $\mathcal{C}^s$ as the set of convex additive functions and
+$\mathcal{C}^s_B$ likewise as the set of convex additive functions
+whose components are $B$-bounded:
 \begin{align*}
@@
 \mathcal{C}^s_B &\equiv \{ f \in \mathcal{C}^s \,:\, 
-f = \sum_{k=1}^s f_k, \, \| f_k \|_\infty \leq B \}
-\end{align*}
-
+f = \sum_{k=1}^s f_k, \, \| f_k \|_\infty \leq B \}.
+\end{align*}
 Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
@@
 \]
-
-We let $sB$ be an upper bound on $\| f_0 \|_\infty$ and $B$ be an upper bound on $\| f^*_k \|_\infty$. It follows that $\|f^* \|_\infty \leq s B$.
+We let $sB$ be an upper bound on $\| f_0 \|_\infty$ and $B$ be an
+upper bound on $\| f^*_k \|_\infty$. 
+It follows that $\|f^* \|_\infty \leq s B$.
 
@@
 \]
-
-For $k \in \{1,...,s\}$, define $g^*_k$ to be decoupled concave population risk minimizer
-\[
-g^*_k \equiv \argmin_{g_k \in \mh \mathcal{C}^1} \| f_0 - f^* - g_k \|_P^2 
-\]
-In our proof, we will analyze $g^*_k$ for $k$'s such that $f^*_k = 0$. Likewise, we define the empirical version:
-\[
-\hat{g}_k \equiv \argmin \Big\{ \| f_0 - \hat{f} - g_k \|_n^2 \,:\, g_k \in \mh \mathcal{C}^1_B \,, \mathbf{1}_n^\tran g_k = 0 \Big\}
-\]
-By the definition of the ACDC procedure, $\hat{g}_k$ exist only for $k$ that have zero in their convex additive approximation.
+For $k \in \{1,...,s\}$, define $g^*_k$ to be the decoupled concave population risk minimizer
+\[
+g^*_k \equiv \argmin_{g_k \in \mh \mathcal{C}^1} \| f_0 - f^* - g_k \|_P^2 .
+\]
+In our proof, we will analyze $g^*_k$ for each $k$ such that $f^*_k = 0$. Likewise, we define the empirical version:
+\[
+\hat{g}_k \equiv \argmin \Big\{ \| f_0 - \hat{f} - g_k \|_n^2 \,:\, g_k \in \mh \mathcal{C}^1_B \,, \mathbf{1}_n^\tran g_k = 0 \Big\}.
+\]
+By the definition of the AC/DC procedure, $\hat{g}_k$ is defined only
+for an index $k$ that has zero as the convex additive approximation.
 
@@
 By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. 
-
 Intuitively, we would like to show that the risks of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risks of the population optimal functions $f^*, g^*$:

### 2014-11-02 tex/scam/appendix.tex
edited up to 8.3

@@
 By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. 
-Intuitively, we would like to show that the risks of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risks of the population optimal functions $f^*, g^*$:
+Intuitively, we would like to show that the risk of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risk of the population optimal functions $f^*, g^*$:
 \begin{align*}
@@
 \| f_0 - f^* - \hat{g}_k \|^2_P &=  \| f_0 - f^* - g^*_k \|^2_P + \trm{err}_-(n) 
-       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
-\end{align*}
-where the estimation errors $\trm{err}_+(n), \trm{err}_-(n)$ decrease with $n$ at some rate.
+       \quad \trm{for all $k \in S$ where $f^*_k = 0$},
+\end{align*}
+where the estimation errors $\trm{err}_+(n)$ and $\trm{err}_-(n)$ decrease with $n$ at some rate.
 

### 2014-11-03 tex/scam/appendix.tex
edited up to Theorem 8.4

@@
 By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. 
-Intuitively, we would like to show that the risk of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risk of the population optimal functions $f^*, g^*$:
+Our argument will be to show that the risk of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risk of the population optimal functions $f^*, g^*$:
 \begin{align*}
@@
 
-Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough such that $\trm{err}_+(n)$ and $\trm{err}_-(n)$ are smaller than $\alpha_+, \alpha_-$ (defined in equation~\ref{eqn:signal_level_defn}), there must exist a contradiction because the risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger by $\alpha_+$ than the risk of the best approximation whose $k$-th component is constrained to be zero.
-
-Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction.
-
-Theorem~\ref{thm:convex_consistent} and theorem~\ref{thm:concave_consistent} characterize $\trm{err}_+(n)$ and $\trm{err}_-(n)$ respectively.
+Assuming this, suppose that $\hat{f}_k = 0$ and $f^*_k \neq 0$. Then when $n$ is large
+enough such that $\trm{err}_+(n)$ and $\trm{err}_-(n)$ are smaller
+than $\alpha_+$ and $\alpha_-$ defined in
+equation~\eqref{eqn:signal_level_defn}, we reach a contradiction.
+This is because the risk $\| f_0 - f^* \|_P$ of $f^*$ is
+strictly larger by $\alpha_+$ than the risk of the best approximation
+whose $k$-th component is constrained to be zero.
+Similarly, suppose $f^*_k = 0$ and $g^*_k \neq 0$. Then when $n$ is large
+enough, $\hat{g}_k$ must not be zero.
+
+Theorem~\ref{thm:convex_consistent} and
+Theorem~\ref{thm:concave_consistent} characterize $\trm{err}_+(n)$ and
+$\trm{err}_-(n)$ respectively.
 
@@
 \label{thm:convex_consistent}
-Let $\tilde{\sigma} \equiv \max(\sigma, B)$. Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq 9 s \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
-
+Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
+minimizer of the restricted regression with $\lambda \leq 9 s
+\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
 Suppose $n \geq c_1 \max(\sqrt{sB}, B)$.
-
-Then, with probability at least $1-\frac{C}{n}$,
+Then with probability at least $1-\frac{C}{n}$,
 \begin{align}
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np}
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
 \end{align}
-Where $c, C$ are constants, possibly dependent on $c_1, b$.
-
+where $c, C$ are constants, possibly dependent on $c_1, b$.
 \end{theorem}
@@
 \begin{proof}
-\textbf{Step 1.} $\hat{f}$ minimizes the penalized empricial risk by definition.
-We would thus like to say that the penalized empirical risk of $\hat{f}$ is no larger than that of $f^*$.
-We cannot do a direct comparison because the empirical mean $\frac{1}{n} \sum_i f^*_k(x_{ik})$ is close to but not exactly zero.
-We thus have to work first with the function $f^* - \bar{f}^*$.
-
+Our proof proceeds in three steps.  First, we bound
+the difference of empirical risks $\|f_0 - \hat{f} \|_n^2 - \| f_0 -
+f^* \|_n^2$.  Second, we bound the cross-term in the bound using
+a bracketing entropy argument for convex function classes.  Finally, 
+we combine the previous two steps to complete the argument.
+
+\textbf{Step 1.} The function $\hat{f}$ minimizes the penalized
+empricial risk by definition. We would thus like to say that the
+penalized empirical risk of $\hat{f}$ is no larger than that of
+$f^*$. We cannot do a direct comparison, however, because the empirical mean
+$\frac{1}{n} \sum_i f^*_k(x_{ik})$ is close to, but not exactly
+zero. We thus have to work first with the function $f^* - \bar{f}^*$.
+We have that
 \begin{align*}
@@
 \end{align*}
-We plug in $y = f_0 + w$:
+Plugging in $y = f_0 + w$, we obtain
 \begin{align*}
@@
      +\lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - \|f^*_k -\bar{f}^*_k\|_\infty \Big) 
-    &\leq \| f_0 - f^* + \bar{f}^* \|_n^2 + 
+    &\\
+\leq \| f_0 - f^* + \bar{f}^* \|_n^2 + 
     2 \langle w, f_0 - f^* + \bar{f}^* \rangle \\
@@
     \lambda \sum_{k=1}^s \Big( \| \hat{f}_k \|_\infty - 
- \| f^*_k - \bar{f}^*_k \|_\infty \Big) &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle
-\end{align*}
-
-The middle term can be bounded with the assumption that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 2B$.
-
+ \| f^*_k - \bar{f}^*_k \|_\infty \Big) &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle.
+\end{align*}
+The middle term can be bounded under the assumption that $\|f^*_k -
+\bar{f}^*_k \|_\infty \leq 2B$; thus,
 \begin{align*}
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B 
-\end{align*}
-
-Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B .
+\end{align*}
+Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from
+the lefthand side. Thus with probability at least $1 - \delta$,
 \begin{align}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}.
 \end{align}
@@
 
-\textbf{Step 2.} We upper bound $2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle$ with bracketing entropy.
-
-Define $\mathcal{G}$ as $\{ f - f^* + \bar{f}^* \,:\, f \in \mathcal{C}^s_B \}$ as the set of convex additive functions centered around the function $f^* - \bar{f}^*$.
-
+\textbf{Step 2.} We now upper bound the cross term $2 \langle w,
+\hat{f} - f^* + \bar{f}^* \rangle$ using bracketing entropy.
+
+Define $\mathcal{G} =\{ f - f^* + \bar{f}^* \,:\, f \in
+\mathcal{C}^s_B \}$ 
+as the set of convex additive functions centered around the function $f^* - \bar{f}^*$. 
 By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
-
-Let us suppose condition~\ref{cond:simplify_covering_number} holds, then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$,
+Let us suppose condition~\ref{cond:simplify_covering_number} holds.
+Then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$,
 $\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
-)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the end of the proof that condition~\ref{cond:simplify_covering_number} indeed holds.
+)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the
+end of the proof that 
+condition~\ref{cond:simplify_covering_number} indeed holds.
 
@@
 Therefore, with probability at least $1-\delta$, uniformly for all $h \in \mathcal{G}$:
-
 $$
-\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
-$$.
-
-We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.
-Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$.
+\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
+$$
+We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{
+  \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
+    n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h
+\in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such
+that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. Then
 $\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.
 
-Let $\mathcal{E}_{\|w\|_\infty}$ denote the event that $\| w \|_\infty \leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$; $\mathcal{E}_{\|w\|_\infty}$ has probability at most $1-\delta$.
-We take an union bound between $\mathcal{E}_{\|w\|_\infty}$ and $\mathcal{E}_{[\,]}$ and get that, with probability at most $1-2\delta$, for all $h$:
+Let $\mathcal{E}_{\|w\|_\infty}$ denote the event that $\| w \|_\infty
+\leq \sigma \sqrt{ 2\log \frac{2n}{\delta}}$.  Then
+$\mathcal{E}_{\|w\|_\infty}$ has probability at most $1-\delta$. We
+now take an union bound over $\mathcal{E}_{\|w\|_\infty}$ and
+$\mathcal{E}_{[\,]}$ and get that, with probability at most
+$1-2\delta$, for all $h$
 \[
 |\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
-  \sigma \sqrt{2 \log \frac{4n}{\delta}} \left( \epsilon + \epsilon_{n,2\delta} \right)
-\]
-
-Because $w$ is a sub-Gaussian random variables, for any fixed vector $h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$, $|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{ \frac{2}{n} \log \frac{2}{\delta} }$.
-Using union bound again, we have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB \sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has probability at most $1-\delta$.
+  \sigma \sqrt{2 \log \frac{4n}{\delta}} \left( \epsilon + \epsilon_{n,2\delta} \right).
+\]
+Because $w$ is a sub-Gaussian random variable, we have that for any fixed vector
+$h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$,
+$|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{
+  \frac{2}{n} \log \frac{2}{\delta} }$. Using another union bound, we
+have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB
+\sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has
+probability at most $1-\delta$.
 
@@
 \begin{align*}
-|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
-|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
-     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta}) \\
+\lefteqn{|\langle w, h \rangle_n | \leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|}\\
+\lefteqn{|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| \leq 
+     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta})} \\
    &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
@@
    2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
-   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}} \\
-\end{align*}
-
-We need that $n$ is large enough so that $\epsilon \in (0, sB \epsilon_3]$ and to ensure that conditions~\ref{cond:simplify_covering_number} hold, we need that $\log n \geq 2$ and $n \geq c B$ where $c$ is some constant dependent only on $K^{**}$ and $b$.
-
-The conditions needed are satisfied if we set $\epsilon = sB \sqrt{ \frac{(s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$ and use the $n \geq c_1 \max( \sqrt{sB}, B)$ assumption in the statement of the theorem.
-Setting $\epsilon$ thus also balances the two terms.
-
-We upper bound some terms to simplify the presentations again and end up with the following result, with probability at least $1-\delta$:
-
+   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
+\end{align*}
+We require that $n$ is large enough so that $\epsilon \in (0, sB
+\epsilon_3]$, and to ensure that
+conditions~\eqref{cond:simplify_covering_number} hold, we need that
+$\log n \geq 2$ and $n \geq c B$ where $c$ is a constant dependent
+only on $K^{**}$ and $b$.
+The conditions are satisfied if we set $\epsilon = sB \sqrt{ \frac{(s
+    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$ and assume 
+$n \geq c_1 \max( \sqrt{sB}, B)$, as stated in the theorem. 
+%% ?? Setting $\epsilon$ in this way thus also balances the two terms.
+
+In summary, we have that probability at least $1-\delta$,
 \[
@@
 where we absorbed $K^{**}$ into the constants $c$ and the union bound multipliers into the constant $C$.
-
 % Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
-
 % According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
@@
 % \]
-
 % Now we evaluate the integral. Since $N_{\|\cdot\|_n}(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.
-
 % \begin{align*}
@@
 % \end{align*}
-
-Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
+Plugging this result into equation~\eqref{eqn:first_step_inequality}
+we get that, with probability at least $1 - 2\delta$,
 \begin{align}
@@
 
-\textbf{Step 3.} We continue from equation~\ref{eqn:second_step_inequality}, use lemma~\ref{lem:uniform_convergence}, use another union bound, with probability at least $1-3\delta$,
-
+\textbf{Step 3.} Continuing from
+equation~\eqref{eqn:second_step_inequality}, we use
+Lemma~\ref{lem:uniform_convergence} and another union bound to obtain
+that, with probability at least $1-3\delta$,
 \begin{align}
@@
 \end{align}
-Where for the second inequality, we define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$ and $\delta = \frac{C}{n}$ we get the desired result.
-
+Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n}
+  \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
+the theorem.
 \end{proof}
@@
 
-We now bound each of the terms. The proof proceeds almost identically to that of theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
+We now bound each of the terms. The proof proceeds almost identically to that of Theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
 
@@
 \end{align*}
-with probability at least $1-\frac{C}{n}$, by theorem~\ref{thm:convex_consistent}.
+with probability at least $1-\frac{C}{n}$, by Theorem~\ref{thm:convex_consistent}.
 To get the fourth inequality, we used the fact that $\| \hat{f} - f^* \|^2 \leq \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2$, which is true because $f^*$ is the projection of $f_0$ onto the set of additive convex functions and the set of additive convex functions is convex itself.
@@
 
-\textbf{Step 3.} Collecting the results and plugging them into equation~\ref{eqn:concave_init_decomposition}, we have, with probability at least $1-2\delta$:
+\textbf{Step 3.} Collecting the results and plugging them into equation~\eqref{eqn:concave_init_decomposition}, we have, with probability at least $1-2\delta$:
 \begin{align*}
@@
 
-Plugging this into equation~\ref{eqn:hpsi_bound} above, we have that:
+Plugging this into equation~\eqref{eqn:hpsi_bound} above, we have that:
 \begin{align*}

### 2014-11-04 tex/scam/appendix.tex
edited up to supporting lemmata

@@
 \]
-where we absorbed $K^{**}$ into the constants $c$ and the union bound multipliers into the constant $C$.
+where we absorbed $K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
 % Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
@@
 \label{thm:concave_consistent}
-Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-Suppose $n$ is large enough such that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.\\
-
-Then, with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$:\\
-\[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np} 
+Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
+step with $\lambda_n \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.
+Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
+\[
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
 \]
@@
    & \underbrace{\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - \hat{f} - \hat{g}_k \|_P^2}_{\trm{term 2}} + \nonumber \\
-   & \underbrace{\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2}_{\trm{term 3}}  \label{eqn:concave_init_decomposition}
+   & \underbrace{\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2}_{\trm{term 3}}  \label{eqn:concave_init_decomposition}.
 \end{align}
-
-We now bound each of the terms. The proof proceeds almost identically to that of Theorem~\ref{thm:convex_consistent} because convex and concave functions have the same bracketing number.
-
-\textbf{Step 1.} We bound term 2. We start from the definition of $\hat{g}_k$:
-\begin{align*}
-\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
-   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
-\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2B \\
- &\\
+We now bound each of the terms. The proof proceeds almost identically to that of Theorem~\ref{thm:convex_consistent}, because convex and concave functions have the same bracketing number.
+
+\textbf{Step 1.} To bound term 2, we start from the definition of
+$\hat{g}_k$ and obtain
+\begin{align*}
+\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g} \|_\infty &\leq
+   \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n \| g^* \|_\infty \\
+\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n 2B \\[10pt]
 \| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
-   +\lambda 2 B \\
+   +\lambda_n 2 B \\
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
-   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2B
-\end{align*}
-
-Using identical analysis as Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
+   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda_n 2B.
+\end{align*}
+Using the same analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 B
-\end{align*}
-
-Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-\delta$:
+  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
+\end{align*}
+Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda 2 B +
+  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n 2 B +
   c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
- &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda 2B
-\end{align*}
-
-Plugging in $\lambda \leq 9 s \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$:
+ &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n 2B
+\end{align*}
+Finally, plugging in $\lambda_n \leq 9 s \tilde{\sigma} \sqrt{
+  \frac{1}{n} \log^2 np}$, we obtain
 \begin{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}} \\
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
 \end{align*}
@@
 
-\textbf{Step 2.} We bound term 2 and 3.
-
+\textbf{Step 2.} To bound terms 2 and 3 we derive
 \begin{align*}
@@
 \end{align*}
-with probability at least $1-\frac{C}{n}$, by Theorem~\ref{thm:convex_consistent}.
-To get the fourth inequality, we used the fact that $\| \hat{f} - f^* \|^2 \leq \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2$, which is true because $f^*$ is the projection of $f_0$ onto the set of additive convex functions and the set of additive convex functions is convex itself.
-
-The last inequality holds because under the condition of the theorem that $n$ is large enough, $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
-
+with probability at least $1-\frac{C}{n}$, by
+Theorem~\ref{thm:convex_consistent}. To obtain the fourth inequality,
+we used the fact that $\| \hat{f} - f^* \|^2 \leq \| f_0 - \hat{f}
+\|_P^2 - \|f_0 - f^*\|_P^2$, which follows from the fact that $f^*$ is the
+projection of $f_0$ onto the set of additive convex functions and the
+set of additive convex functions is convex itself.
+The last inequality holds due to the condition of the theorem that $n$
+is large enough so that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
 The same bound likewise holds for term 2.
@@
 \end{align*}
-
-Taking an union bound across $k=1,...,s$ dimensions completes the result.
-
+Taking a union bound across the $s$ dimensions completes the result.
 \end{proof}

### 2014-11-06 tex/scam/appendix.tex
edits after 8.3

@@
 Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.
-
-There exists an $\epsilon$-bracketing of $\mathcal{G}$.
-
+There exists an $\epsilon$-bracketing of $\mathcal{G}$, and
 %For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$. 
-
-By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
+by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
 By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
-
 For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
 \[
-\psi_L^2 \leq h^2 \leq \psi_U^2
-\]
-
-We can then bound the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$.
+\psi_L^2 \leq h^2 \leq \psi_U^2.
+\]
+We can then bound the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ as
 \begin{align*}
@@
 % \end{align*}
-
-Now we can bound $\| h \|_n^2 - \| h \|_P^2$.
-
+Now we can bound $\| h \|_n^2 - \| h \|_P^2$ as
 \begin{align}
@@
 \end{align}
-
-$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $(sB)^2$.
-By Hoeffding's inequality and union bound, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
+Since 
+$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with
+upper bound $(sB)^2$, Hoeffding's inequality and union bound give that,
+with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$)
 \[
@@
 \E \psi_U(X)^2 - \E \psi_L(X)^2 + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
-\end{align*}
-
-Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have:
+(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
+\end{align*}
+Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have
 \begin{align*}
@@
 We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.
-
 We have then that, with probability at least $1-\delta$,
@@
 \label{lem:remove_centering}
-
-Let $f_0, f^*$ be defined as in section~\ref{sec:false_negative_proof_notations}. Define $\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$.
-
+Let $f_0$ and $f^*$ be defined as in Section~\ref{sec:false_negative_proof_notations}. Define $\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$.
 Then, with probability at least $1 - 2\delta$,
@@
 
-\begin{proof} (of lemma~\ref{lem:remove_centering})
+\begin{proof}
+We decompose the empirical norm as
 \begin{align*}
@@
     \bar{f}^{*2} \\
-  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \bar{f}_0 - \bar{f}^{*2}
-\end{align*}
-
+  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \bar{f}_0 - \bar{f}^{*2}.
+\end{align*}
+Now
 $\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 sB \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.
-
 The same reasoning likewise applies to $\bar{f}_0 = \frac{1}{n} \sum_{i=1}^n f_0(X_i)$.
@@
 Taking a union bound and we have that, with probability at least $1- 2\delta$, 
-
 \begin{align*}
@@
 \end{align*}
-
 Therefore, with probability at least $1 - 2\delta$,
@@
 \]
-
 \end{proof}
@@
 
- \subsection{Supporting Technical Material}
+% \subsection{Supporting Technical Material}
 
@@
 
-Then, $h^*_k(x_k) \equiv \E[ f(X) - \phi(X_{-k}) \given x_k]$ is twice differentiable and has a second derivative lower bounded, that is, bounded away from $-\infty$.
+Then, $h^*_k(x_k) \equiv \E[ f(X) - \phi(X_{-k}) \given x_k]$ is twice
+differentiable and has a second derivative lower 
+bounded away from $-\infty$.
 \end{lemma}
@@
 \begin{proof}
-
+We can write
 \[
@@
 \]
-
 The integrand is bounded because it is a sum-product of continuous functions over a compact set. Therefore, we can differentiate under the integral and derive that
@@
 \end{align*}
-
-We used the shorthand $f'(\mathbf{x}), p'(\mathbf{x}_{-k} \given x_k), etc$ to denote $\partial_{x_k} f(\mathbf{x})$, $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$, etc.
+where we have used the shorthand $f'(\mathbf{x}), p'(\mathbf{x}_{-k}
+\given x_k)$ to denote $\partial_{x_k} f(\mathbf{x})$, $\partial_{x_k}
+p(\mathbf{x}_{-k} \given x_k)$, etc.
 
@@
 To see that the second derivative is lower bounded, we note that $f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k)$ is non-negative and the other terms in the second-derivative are all continuous functions on a compact set and thus bounded.
-
-\end{proof}
-
- \subsubsection{Concentration of Measure}
-
-\textbf{Sub-Exponential} random variable is the square of a sub-Gaussian random variable\cite{vershynin2010introduction}.
-
-\begin{proposition} (Subexponential Concentration \cite{vershynin2010introduction})
-Let $X_1,...,X_n$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
+\end{proof}
+
+subsubsection{Concentration of Measure}
+
+A sub-exponential random is the square of a sub-Gaussian random
+variable \cite{vershynin2010introduction}.
+
+\begin{proposition} (Subexponential Concentration
+  \cite{vershynin2010introduction})
+Let $X_1,...,X_n$ be zero-mean independent subexponential random
+variables with subexponential scale $K$. 
+Then
 \[
@@
 For uncentered subexponential random variables, we can use the following fact. If $X_i$ subexponential with scale $K$, then $X_i - \E[X_i]$ is also subexponential with scale at most $2K$.
-
-\textbf{Restating}. We can set
+Restating, we can set
 \[
@@
 \]
-Thus, with probability at least $1-\delta$, the deviation at most
-\[
-K \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}},  \frac{1}{cn} \log \frac{C}{\delta} \right)
+Thus, with probability at least $1-\delta$, the deviation is at most
+\[
+K \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}},  \frac{1}{cn} \log \frac{C}{\delta} \right).
 \]
@@
 \begin{corollary}
-Let $w_1,...,w_n$ be $n$ independent sub-Gaussian random variables with sub-Gaussian scale $\sigma$.
-
+Let $W_1,...,W_n$ be $n$ independent sub-Gaussian random variables with sub-Gaussian scale $\sigma$. 
 Then, for all $n > n_0$, with probability at least $1- \frac{1}{n}$,
 \[
-\frac{1}{n} \sum_{i=1}^n w_i^2 \leq c \sigma^2 
+\frac{1}{n} \sum_{i=1}^n W_i^2 \leq c \sigma^2 .
 \]
@@
 \[
-| \frac{1}{n} \sum_{i=1}^n w_i^2 - \E w^2 | \leq \sigma^2 \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}}, \frac{1}{cn}\log \frac{C}{\delta} \right)
+\left| \frac{1}{n} \sum_{i=1}^n W_i^2 - \E W^2\right| \leq \sigma^2 \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}}, \frac{1}{cn}\log \frac{C}{\delta} \right).
 \]
@@
 \begin{align*}
- \frac{1}{n} \sum_{i=1}^n w_i^2 &\leq c\sigma^2 \Big(1+\sqrt{\frac{1}{cn} \log Cn}\Big) \\
-		&\leq 2 c \sigma^2
- \end{align*}
-
+ \frac{1}{n} \sum_{i=1}^n W_i^2 &\leq c\sigma^2 \Big(1+\sqrt{\frac{1}{cn} \log Cn}\Big) \\
+		&\leq 2 c \sigma^2.
+ \end{align*}
 \end{proof}
@@
 
-\begin{lemma} (Serfling \cite{serfling1974probability}) 
+\begin{lemma} (\cite{serfling1974probability}) 
 Let $x_1,..., x_N$ be a finite list, $\bar{x} = \mu$. Let $X_1,...,X_n$ be sampled from $x$ without replacement.
@@
 \[
-P( S_n - n \mu \geq n \epsilon) \leq \exp( - 2 n \epsilon^2 \frac{1}{r_n (b-a)^2})
+\P( S_n - n \mu \geq n \epsilon) \leq \exp\left( - 2 n \epsilon^2 \frac{1}{r_n (b-a)^2}\right).
 \]
@@
 \[
-P( \frac{1}{N} S_n \geq \epsilon) \leq \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
-\]
-
+\P\left( \frac{1}{N} S_n \geq \epsilon\right) \leq \exp\left( -2 N \epsilon^2 \frac{1}{(b-a)^2}\right)
+\]
 And, by union bound, we have that
 \[
-P( | \frac{1}{N} S_n| \geq \epsilon) \leq 2 \exp( -2 N \epsilon^2 \frac{1}{(b-a)^2})
+\P\left( | \frac{1}{N} S_n| \geq \epsilon\right) \leq 2 \exp\left( -2 N \epsilon^2 \frac{1}{(b-a)^2}\right)
 \]
@@
 
-A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n|$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.
-
-\begin{proof}
-\[
-P( \frac{1}{N} S_n \geq \epsilon) = P( S_n \geq \frac{N}{n} n \epsilon) \leq \exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} ) 
-\]
-
-We note that $r_n \leq 1$ always, and $n \leq N$ always. 
-\[
-\exp( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} )  \leq \exp( - 2 N \epsilon^2 \frac{1}{(b-a)^2})
-\]
-This completes the proof.
-
+A simple restatement is that with probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n|$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.
+
+\begin{proof}
+\[
+\P\left( \frac{1}{N} S_n \geq \epsilon\right) = \P\left( S_n \geq \frac{N}{n} n \epsilon\right) \leq \exp\left( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} \right).
+\]
+We note that $r_n \leq 1$ always, and $n \leq N$ always.   Thus,
+\[
+\exp\left( - 2 n \frac{N^2}{n^2} \epsilon^2 \frac{1}{r_n (b-a)^2} \right)  \leq \exp\left( - 2 N \epsilon^2 \frac{1}{(b-a)^2}\right)
+\]
+completing the proof.
 \end{proof}
@@
 where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$.
-
-It is then trivial to solve the system and verify that $a_1, a_2$ are as specified.
-
+It is then simple to solve the system and verify that $a_1, a_2$ are as specified.
 \end{proof}

### 2014-11-06 tex/scam/appendix.tex
edits after 8.3

@@
 
-\subsubsection{Bracketing Number for Convex Functions}
+\subsubsection{Bracketing Numbers for Convex Functions}
 
@@
 Let $\mathcal{C}$ be a set of functions.
-For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textbf{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f^U \geq f \geq f^L$.
+For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textit{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f^U \geq f \geq f^L$.
 
@@
 
-It is trivial to extend Kim and Samworth's result to $L_2(P)$ norm for an absolutely continuous distribution $P$.
+It is trivial to extend Kim and Samworth's result to the $L_2(P)$ norm for an absolutely continuous distribution $P$.
 
@@
 \]
-For all $\epsilon \in (0, B\epsilon_3]$.
+for all $\epsilon \in (0, B\epsilon_3]$.
 \end{proposition}
@@
   &\leq \left( \int | f_L(x) - f_U(x)|^2 dx \right)^{1/2}\\
- &\leq \| f_L - f_U \|_{L_2} \leq \epsilon
+ &\leq \| f_L - f_U \|_{L_2} \leq \epsilon.
 \end{align*}
@@
 \]
-For all $\epsilon \in (0, s B \epsilon_3]$.
+for all $\epsilon \in (0, s B \epsilon_3]$.
 \end{corollary}
@@
 
-The following result follows from Corollary~\ref{prop:convexbracket_lp} directly by an union bound.
+The following result follows from Corollary~\ref{prop:convexbracket_lp} directly by a union bound.
 
@@
 Then, with probability at least $1-\delta$, for all pairs $(f_L, f_U) \in \mathcal{C}^s_\epsilon$, we have that
-
 \begin{align*}
@@
 \end{align*}
-
 where 
-$\epsilon_{n,\delta} \equiv 
+$$\epsilon_{n,\delta} \equiv 
 sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} 
-= \sqrt{ \frac{ sK^{**}(sBb)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}$
+= \sqrt{ \frac{ sK^{**}(sBb)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}.$$
 \end{corollary}
@@
 \begin{proof}
-$|f_L(X_i) - f_U(X_i)|$ is at most $sB$.
-There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$.
-The inequality follows from a direct application of union bound and Hoeffding Inequality.
+Noting that $|f_L(X_i) - f_U(X_i)|$ is at most $sB$ and there are
+$N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$, the
+inequality follows from a direct application of a union bound and Hoeffding's Inequality.
 \end{proof}
@@
 \begin{align}
-\epsilon^{1/2} \leq 2sK^{**} (sBb)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2. \label{cond:simplify_covering_number}
+\epsilon^{1/2} \leq 2sK^{**} (sBb)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2 \label{cond:simplify_covering_number}.
 \end{align}
-
 Then we have that
 \begin{align*}
-\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}
+\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}.
 \end{align*}
@@
 \end{align*}
-Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$ and $c_1,c_2$ are constants such that $\E[f_1^*(X_1)] = \E[f_2^*(X_2)] = 0$.
-
+where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$ and $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$ and $c_1,c_2$ are constants such that $\E[f_1^*(X_1)] = \E[f_2^*(X_2)] = 0$.
 \end{proposition}
@@
 f^*_1(x_1) &= \E[ f(X) - f_2^*(X_2) \given x_1] \\
-f^*_2(x_2) &= \E[ f(X) - f_1^*(X_1) \given x_2 ] 
-\end{align*}
-
+f^*_2(x_2) &= \E[ f(X) - f_1^*(X_1) \given x_2 ] .
+\end{align*}
 Let us guess that $f^*_1, f^*_2$ are quadratic forms $f^*_1(x_1) = a_1 x_1^2 + c_1$, $f^*_2(x_2) = a_2 x_2^2 + c_2$ and verify that there exist $a_1, a_2$ to satisfy the above equations.
 Since we are not interested in constants, we define $\simeq$ to be equality up to a constant.
-
 Then, 
@@
    &\simeq H_{11} x_1^2 + 2H_{12} \alpha x_1^2 + H_{22} \alpha^2 x_1^2 - a_2 \alpha^2 x_1^2\\
-   &\simeq (H_{11} + 2 H_{12} \alpha + H_{22} \alpha^2 - a_2 \alpha^2) x_1^2
-\end{align*}
-
+   &\simeq (H_{11} + 2 H_{12} \alpha + H_{22} \alpha^2 - a_2 \alpha^2) x_1^2.
+\end{align*}
 Likewise, we have that
 \[
-\E[ f(X) - f_1^2(X_1) \given x_2] \simeq (H_{22} + 2H_{12}\alpha + H_{22}\alpha^2 - a_1 \alpha^2) x_2^2
-\]
-
-Thus, $a_1, a_2$ need only satisfy the linear system:
+\E[ f(X) - f_1^2(X_1) \given x_2] \simeq (H_{22} + 2H_{12}\alpha + H_{22}\alpha^2 - a_1 \alpha^2) x_2^2.
+\]
+Thus, $a_1, a_2$ need only satisfy the linear system
 \begin{align*}

### 2014-11-07 tex/scam/introduction.tex
minor edits

@@
 Additive shape-constrained estimation has also been studied; \cite{pya2014shape} propose a penalized B-spline estimator while \cite{chen2014generalised} show the consistency of the MLE.
-To the best of our knowledge however, there has been no work on variable selection and high-dimensional estimation of convex functions.
+To the best of our knowledge however, there has been no work on variable selection and and estimation of high-dimensional convex functions.
 
@@
 the component Hilbert spaces must be chosen, leading to extra tuning
-parameters that are difficult to select in practice. \cite{huang2010variable} 
-too formulate sparse additive spline fitting as a convex optimization but
-their procedure too requires a smoothing parameter in the form of 
-a truncation level for the spline basis.
+parameters that are difficult to select in practice. There has also been
+work on estimating sparse additive models over a spline basis, for 
+instance the work of \cite{huang2010variable}, but these approaches too 
+require the tuning of smoothing parameters.
 

### 2014-11-09 tex/scam/coverletter.tex
initial commit

\documentclass[12pt]{article}
\input{letterhead}
\recommendee{}

\begin{document}
\thispagestyle{empty}
\myletterhead{}
\date{}
\vskip15pt

To the Editors:

We would like to submit the manuscript ``Faithful variable selection
for high dimensional convex regression'' for review and possible
publication in {\it The Annals of Statistics}.  This paper develops a
new procedure based on additive models for variable selection in high
dimensional convex regression, shows that the procedure yields no
false negatives in the population setting, and gives a finite sample
statistical analysis.

The manuscript is 29 pages including references, and we have
prepared a supplement with full proofs of all of the technical
results.  No version of this paper has been previously
published in any form.

As possible expert reviewers, we suggest Adityanand Guntuboyina
(Berkeley), Richard Samworth (Cambridge), Bodhisattva Sen (Columbia)
and Ming Yuan (Wisconsin).

\jdlucsig{}

\end{document}

### 2014-11-09 tex/scam/coverletter.tex
edit

@@
 
-We would like to submit the manuscript ``Faithful variable selection
-for high dimensional convex regression'' for review and possible
+We would like to submit the manuscript ``Faithful variable screening
+for high-dimensional convex regression'' for review and possible
 publication in {\it The Annals of Statistics}.  This paper develops a

### 2014-11-09 tex/scam/paper-submit.tex
initial commit

--- 2014-09-15 tex/scam/paper.tex
@@
-\documentclass[12pt,pdftex,aos]{imsart}
+\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
 %\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
@@
 \RequirePackage[OT1]{fontenc}
-\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
+\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
 \RequirePackage{hypernat}
@@
 
-\renewcommand{\baselinestretch}{1.1}
+\renewcommand{\baselinestretch}{1.05}
 %\parskip12pt
@@
 \and
-\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
-\address{
-\begin{tabular}{ccc}
-\\[10pt]
-Machine Learning Department & Department of Statistics & Department of Statistics\\
-Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
-& & University of Chicago
-\end{tabular}
-%\\[20pt]
-%\printead{e1,e2,e3}
-}
+\author{\fnms{John}
+  \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{Machine Learning Department, Carnegie Mellon University,
+  Pittsburgh PA 15213}
+\address{Department of Statistics, University of Chicago, Chicago IL 60637}
 \end{aug}
@@
 \input{discussion}
-
-\clearpage
-
-\newpage
-\input{appendix}
 %\newpage
@@
 
+\clearpage
+\input{supplement}
+
 \end{document}

### 2014-11-15 tex/scam/additive_faithful.tex
false positive edit

@@
 \label{defn:boundary-point}
-A density $p(\mathbf{x})$ be a density supported on $[0,1]^p$ satisfies
-the \emph{boundary flatness condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:
+Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. $p(\mathbf{x})$ satisfies
+the \emph{boundary flatness condition} if for all $j$, and for all $\mathbf{x}_{-j}$,
 
@@
 \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
-\quad \trm{at } x_k = 0, x_k = 1
+\quad \trm{at } x_j = 0, x_j = 1
 \end{equation}

### 2014-11-15 tex/scam/sparsistency.tex
false positive edit

@@
 In our analysis, we assume that an upper bound $B$ to $\| \hat{f}_k \|_\infty$ 
-is imposed in the optimization procedure, where $B \geq \| f^*_k \|_\infty$.
+is imposed in the optimization procedure, where $B$ is chosen to also upper bound $\| f^*_k \|_\infty$.
 This $B$-boundedness constraint is added so that we may use the convex function bracketing results from~\cite{kim2014global} to establish uniform convergence between the empirical risk and the population risk.
@@
 Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual.
-Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > | \frac{1}{2n}
-\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on
-the coordinates of the 
-$i$-th largest to the $n$-th largest entries of $X_k$ and 0
-elsewhere.  Then the following two statements hold.
+
+Let $\pi_k(i)$ be a reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry.
+Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
+Assume without loss of generality that $X_{k\pi_k(n)} - X_{k\pi_k(1)} \geq 1$.
+
+Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > (X_{k\pi_k(n)} - X_{k\pi_k(1)})| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$ and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \geq \frac{1}{16}$.
+
+Then the following two statements hold.
 \begin{enumerate}
@@
   $S^c$.
-\item For all $k \in S^c$, the solution $\hat{c}_k$ to optimization~\eqref{opt:alternate_opt_concave} must be zero.
+\item For all $k \in S^c$, the solution $\hat{c}_k$ to optimization~\eqref{opt:alternate_opt_concave} must be zero and unique.
 \end{enumerate}
@@
 \end{theorem}
+
+Theorem~\ref{thm:deterministic} states that the estimator produces no false positive so long as $\lambda_n$ upper bounds the partial sums of the residual $\hat{r}$ and that the maximum gap between ordered values of $X_k$ is small.
 
@@
 \item The data $X^{(1)},\ldots, X^{(n)} \sim F$ are iid from
-a distribution $F$ with a density $p$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$. 
+a distribution $F$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$.
 \item The response is $Y = f_0(X) + W$ where $W$ is
@@
 \item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
+\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition. (Definition~\ref{defn:boundary-point})
 \end{packed_enum}
-By assumption A1, $f^*_k$ is must be zero for $k\notin S$.
+By assumption A1, $f^*_k$ must be zero for $k\notin S$.
 We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
@@
 \label{thm:false_positive}
-Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
-and suppose 
+Suppose assumptions A1-A5 hold.
+Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $c, C$ dependent on $b$.
+Suppose also
 \begin{equation}
-\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
+\lambda_n \geq 512 b s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
 \end{equation}  
-Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
-S^c$, and for all $i'=1,\ldots, n$,
+Then with probability at least $ 1 - \frac{24}{n}$, for all $k \in
+S^c$, for all $i=1,\ldots,n$,
 \begin{equation}
-\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
+\lambda_n \geq (X_{k\pi_k(n)} - X_{k \pi_k(1)}) \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| ,
 \end{equation}
-and for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero. 
+$\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \leq \frac{1}{16}$, and both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero.
 \end{theorem}
@@
 The proof of Theorem~\ref{thm:false_positive} exploits independence of
-$\hat{r}$ and $X_k$ from A1; when $\hat{r}$ and $X_k$ are independent,
+$\hat{r}$ and $X_k$ under assumption A1; when $\hat{r}$ and $X_k$ are independent,
 $\hat{r}^\tran \mathbf{1}_{(i':n)}$ is the sum of $n - i' +1$ random
@@
 \label{thm:false_negative}
-Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to
+Suppose assumptions A1-A5 hold. Let $\hat{f}$ be any AC solution to
 the restricted regression with $B$-boundedness constraint, and let
@@
 \begin{equation}
-\lambda_n \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
+\lambda_n \leq 512 b s \tilde{\sigma} \sqrt{\frac{\log^2 np}{n}}
 \end{equation}
-and that $n$ is sufficiently large so that 
+and that $n$ is sufficiently large so that, for some constant $c' > 1$,
 \begin{equation}
-\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s^5.
+\frac{n^{4/5}}{\log np} \geq c' B^4 \tilde{\sigma}^2 s^5.
 \end{equation}
@@
 The above corollary implies that consistent variable selection is
-achievable at the same exponential scaling of the ambient dimension
-scaling attained with parametric models, $p = O(\exp(n^c))$ for $c<1$.
+achievable with an exponential scaling of the ambient dimension
+scaling, $p = O(\exp(n^c))$ for some $0<c<1$, just as in parametric models.
 The cost of nonparametric modeling through shape constraints is

### 2014-11-15 tex/scam/supplement.tex
initial commit
false positive edit

--- 2014-11-06 tex/scam/appendix.tex
@@
-\section{Appendix}
+\section{Supplement:  Proofs of Technical Results}
 
@@
 We restate Theorem~\ref{thm:deterministic} first for convenience. 
-The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.
+The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).
 
@@
 
-Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
-\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.
+Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry.
+Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
+
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$ and that $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \geq \frac{1}{16}$.
+
 Then the following are true:
@@
 \begin{proof} 
-We will omit the Lipschitz constraint in our proof here. It can be
-added in and easily verified that the result of the theorem still holds.
+We will omit the $B$-boundedness constraint in our proof here. It is easy to verify that the result of the theorem still holds with the constraint added in.
 
@@
 \]
-with the constraint that $v_i \geq 0$ for all $i$.
+with the constraint that $v_{ki} \geq 0$ for $i=2,...,n-1$.
 
@@
         + \lambda \bar{\Delta}_k^\tran \mathbf{u}
-      - \nu_k
-\end{align*}
-where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.
-
-We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to zero,
+      - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right)
+\end{align*}
+where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$.
+If $\bar{\Delta}_k d_k = 0$, then $\mathbf{u}$ can be any vector whose $L_1$ norm is less than or equal to $1$.
+$\nu_k \geq 0$ is a vector of Lagrangian multipliers.
+$\nu_{k1}$ does not exist because $d_{k1}$ is not constrained to be non-negative.
+
+We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the $\mathbf{u}, \nu_k$ dual variables can be set in a way to ensure that stationarity:
 \begin{align*}
 \partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
-           - \nu_k = 0 
+           - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right) = 0 
 \end{align*}
 where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$.
-It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ where the inequality is element-wise.
-
-Let us reorder the samples so that the $i$-th sample is the $i$-th smallest sample. 
-We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for
-some $0 < a < 1/2$, where the coordinates of $\mathbf{u}$ correspond
+It clear that to show stationarity, we only need to show that $[-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}]_j = 0$ for $j=1$ and $\geq 0$ for $j=2,...,n-1$.
+
+To ease notational burden, let us reorder the samples in ascending order so that the $i$-th sample is the $i$-th smallest sample. We will from here on write $X_{ki}$ to denote $X_{k \pi_k(i)}$.
+
+Define $i^*$ as the largest index such that $\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} \geq 1/2$. 
+We will construct $\mathbf{u} = (a - a', 0, ..., -a, 0,..., a')$ where
+$a,a'$ are positive scalars, where $-a$ lies at the $i^*$-th coordinate, and where the coordinates of $\mathbf{u}$ correspond
 to the new sample ordering.
-We then just need to show that
-\begin{align*}
-- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
-- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
-- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
-   \textrm{for each } j \\
-- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
-    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
-    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
-   + \lambda (X_{kn} - X_{kj})a &\geq 0 
-\end{align*}
-where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that
-\begin{align*}
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
-   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
-- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
-- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0.
-\end{align*}
+
+We define
+
+\begin{align*}
+\kappa &= \frac{1}{\lambda n} \big[ \Delta_k^\tran \hat{r} \big]_1 \\
+a' &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
+     \frac{X_{ki^*}-X_{k1}}{X_{kn} - X_{k i^*}} \frac{1}{8} \\
+a &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
+     \frac{X_{kn}-X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
+\end{align*}
+
+and we verify two facts: first that the KKT stationarity is satisfied and second, that $\| \mathbf{u} \|_1 < 1$ with high probability. Our claim is proved immediately by combining these two facts.
+
+Because $\hat{r}$ and $\mathbf{u}$ are both centered vectors, $\bar{\Delta}_k^\tran \hat{r} = \Delta_k^\tran \hat{r}$ and likewise for $\mathbf{u}$.
+Therefore, we need only show that for $j=1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j = \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$ and that for $j = 2,..., n-1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j \geq \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$.
+
+With our explicitly defined form of $\mathbf{u}$, we can characterize
+\begin{align}
+\big[ \Delta_k^\tran \mathbf{u} \big]_j = 
+  \left \{ \begin{array}{cc} 
+   (-a + a')(X_{k i^*} - X_{kj})+ a'(X_{kn} - X_{k i^*})
+   & \trm{ if } j \leq i^* \\
+   a'(X_{kn} - X_{kj}) & \trm{ if } j \geq i^* 
+     \end{array} \right.
+\end{align}
+
+It is straightforward to check that $\big[ \lambda \Delta_k^\tran \mathbf{u} \big]_1 = \lambda \kappa = \frac{1}{n} \big[ \Delta_k^\tran \hat{r} \big]_1$.
+
+To check that other rows of stationarity condition holds, we characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
+\begin{align*}
+[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i \\
+  & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
+ & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i \\
+ & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r} 
+\end{align*}
+where we denote $\mathsf{gap}_{i'} = X_{ki'} - X_{k(i'-1)}$.
+
+We pause for a second here to give a summary of our proof strategy.
+We leverage two critical observations: first, any two adjacent terms in the sequence $\frac{1}{n} \Delta_k^\tran \hat{r}$ cannot differ by too much.
+Second, we defined $a, a'$ such that $-a+a' = -\frac{1}{8}$ so that $\lambda \Delta_k^\tran \mathbf{u}$ is a sequence that strictly increases in the first half (for coordinates in $\{1,...,i^*\}$) and strictly decreases in the second half.
+
+We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate.
+We will show that the second sequence increases faster than the first sequence which will imply that the second sequence is larger than the first in the first half of the coordinates.
+We will then work similarly but backwards for the second half.
+
+Following our strategy, We first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.
+
+For $j = 1,..., i^*-1$, we have that
+\begin{align*}
+\lambda [ \Delta_k^\tran \mathbf{u}]_{j+1} - \lambda [ \Delta_k^\tran \mathbf{u}]_{j} &= \lambda (a - a') \mathsf{gap}_{j+1} \\
+ &\geq -\mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \\
+& = [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j+1} - [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j}
+\end{align*}
+
+The inequality follows because $a - a' = \frac{1}{8}$ and thus $\lambda (a - a') \geq \left| \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \right|$. Therefore, for all $j = 1,...,i^*$:
+\begin{align*}
+[ \lambda \Delta_k^\tran \mathbf{u}]_j &\geq [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_j
+\end{align*}
+
+For $j \geq i^*$, we start our comparison from $j=n-1$. First, we claim that $a' > \frac{1}{32}$. To prove this claim, note that
+\begin{align}
+|\kappa| &= \Big|\frac{1}{\lambda n} \sum_{i' > 1} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}\Big| \leq \frac{1}{X_{kn} - X_{k1}}\frac{1}{32} \sum_{i' > 1} \mathsf{gap}_{i'} 
+ = \frac{1}{32} 
+\end{align}
+and that
+\begin{align*}
+\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} &= \frac{X_{kn} - X_{k(i^*+1)} + X_{k(i^*+1)} - X_{ki^*}}{X_{kn} - X_{k1}} \leq \frac{1}{2} + \frac{1}{16}
+\end{align*}
+where the inequality follows because we had assumed that $\frac{X_{k(i+1)} - X_{ki}}{X_{k(n)} - X_{k(1)}} \leq \frac{1}{16}$ for all $i = 1,...,n-1$.
+
+So, we have 
+\begin{align*}
+a' &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \kappa 
+   + \frac{ X_{ki^*} - X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
+ &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
+  \kappa + \frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \frac{1}{8} \right) \\
+&\geq \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
+  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
+&\geq \frac{1}{1/2 + 1/16} \left(
+  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
+&\geq \frac{1}{32}
+\end{align*}
+In the first inequality of the above derivation, we used the fact that $\frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \leq \frac{1}{2} - \frac{1}{16}$.
+In the second inequality, we used the fact that the quantity inside the parentheses is positive and $\frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \geq \frac{1}{1/2 + 1/16}$.
+
+Now consider $j=n-1$. 
+\[
+[ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{n-1} = \frac{1}{n} \mathsf{gap}_n \hat{r}_n 
+ \leq \mathsf{gap}_n \frac{\lambda }{32} \leq \lambda \mathsf{gap}_n a' = \lambda [\Delta_k^\tran \mathbf{u}]_{n-1} 
+\]
+
+For $j = i^*, ..., n-2$, we have that 
+\begin{align*}
+\lambda [\Delta_k^\tran \mathbf{u} ]_j - \lambda [\Delta_k^\tran \mathbf{u}]_{j+1} &= 
+ \lambda a' \mathsf{gap}_{j+1}  \\
+ &\geq \mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r}  \\
+ &\geq  [\frac{1}{n} \Delta_k^\tran \hat{r}]_j - [\frac{1}{n} \Delta_k^\tran \hat{r}]_{j+1}
+\end{align*}
+
+Therefore, for $j = i^*,...,n-2$,
+\begin{align*}
+\lambda [\Delta_k^\tran \mathbf{u}]_j \geq \frac{1}{n} [ \Delta_k^\tran \hat{r}]_j
+\end{align*}
+
+We conclude then that $\lambda [\Delta_k^\tran \mathbf{u} ]_j \geq [\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for all $j = 2,...,n-1$.
+
+We have thus verified that the stationarity equations hold and now will bound $\| \mathbf{u} \|_1$.
+
+\begin{align*}
+\| \mathbf{u} \|_1 = | a - a'| + a + a' \leq \frac{1}{8} + 2 a \leq \frac{1}{8} + 4 |\kappa| + \frac{1}{2}  \leq \frac{1}{8} + \frac{1}{8} + \frac{1}{2} < 1
+\end{align*}
+In the third inequality, we used the fact that $|\kappa| \leq \frac{1}{32}$.
+
 We have thus proven that there exists one solution $\{ \hat{d}_k
@@
 \]
+with $\nu_{ki} \geq 0$.
 The same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
@@
 \begin{theorem} 
-Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-If $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
-\[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|.
-\]
+Suppose assumptions A1-A4 hold.
+Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose that $p \leq O\exp( c'' n)$ for some $c'' > 0$ and that $n \geq C''$ for some constant $C''$ possibly dependent on $b$.
+
+If $\lambda_n \geq (8 \cdot 32) 2 b s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
+\begin{align*}
+& \lambda_n > (X_{k\pi_k(n)} - X_{k\pi_k(1)}) \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
+\end{align*}
+and for all $k \in S^c$ and $i' = 1, ..., n-1$, $\frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \leq \frac{1}{16}$.
+
 Therefore, for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$ from optimization~\ref{opt:alternate_opt_concave} are zero. 
@@
 
-Fix $j$ and $i$. Then $\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is the sum
+Fix $j$ and $i$. Then $\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}$ is the sum
 of $n-i'+1$ random coordinates of $\hat{r}$. We will use
@@
 \Big
-|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| \leq
+|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| \leq
    2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
@@
 \Big
-|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| &\leq
+|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| &\leq
    2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
@@
 result.
+
+Finally, we note that $2b \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ by definition. This concludes the proof for the first part of the theorem.
+
+To prove the second claim, let the interval $[-b, b]$ be divided into $64$ non-overlapping segments each of length $b/32$.
+Because $X_k$ is drawn from a continuous density, the density has a lower bound $c_l > 0$ and the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{b}{32} c_l \right)^n$.
+Let $\mathcal{E}_k$ denote the event that every segment contains some samples.
+
+Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ where $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-b)$ and $\mathsf{gap}_{n} = b - X_{k\pi_k(n)}$.
+
+If any $\mathsf{gap}_i \geq \frac{b}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments.
+Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{b}{16}$ for all $i$.
+
+Thus, we have that, for all $i$:
+
+\[
+\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{X_{k\pi_k(n)} - X_{k \pi_k(1)}} \geq 
+\frac{ b/16 }{ 2b - b/8} \geq 1/16
+\]
+
+Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{b}{32} c_l \right)^n$.
+
+$64 \left( 1 - \frac{b}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $b, c_l$.
+Therefore, if $p \leq exp( c'' n)$ for some $c'' < c'$ and if $n$ is large enough, $C' p \exp( - c' n) \leq C' \exp( - (c' - c'') n) \leq \frac{12}{n}$.
+
+Taking an union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.
+
 \end{proof}
@@
 \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
-Suppose $n \geq c_1 \max(\sqrt{sB}, B)$.
+Suppose $n \geq c_1 s \sqrt{sB}$.
 Then with probability at least $1-\frac{C}{n}$,
@@
 \end{align}
-where $c, C$ are constants, possibly dependent on $c_1, b$.
+where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
 \end{theorem}
@@
 \end{align*}
-We require that $n$ is large enough so that $\epsilon \in (0, sB
-\epsilon_3]$, and to ensure that
-conditions~\eqref{cond:simplify_covering_number} hold, we need that
-$\log n \geq 2$ and $n \geq c B$ where $c$ is a constant dependent
-only on $K^{**}$ and $b$.
-The conditions are satisfied if we set $\epsilon = sB \sqrt{ \frac{(s
-    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$ and assume 
-$n \geq c_1 \max( \sqrt{sB}, B)$, as stated in the theorem. 
-%% ?? Setting $\epsilon$ in this way thus also balances the two terms.
+To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
+    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
+if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
+$\epsilon \in (0, sB \epsilon_3]$ for some absolute constant $\epsilon_3$ as required by the bracketing number results (Corollary~\ref{cor:convexadditive_lp}).
+Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.
 
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
-\]
-where we absorbed $K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
+   \frac{s^{6/5} B^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
+  c sB \sigma \sqrt{ 
+   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+\]
+where we absorbed $b, K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
 % Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
@@
    &\leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
    + \lambda 2 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
@@
    &\leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
    + \lambda 2 s B \nonumber\\   
    &\leq c B \sigma 
-    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
+    \sqrt{ \frac{s^4 B^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
 \label{eqn:second_step_inequality}
@@
    &\leq cB^2 \sigma 
-    \sqrt{ \frac{s^3 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
+    \sqrt{ \frac{s^4}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
  +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
 \end{align}
@@
 Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
-step with $\lambda_n \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.
+step with $\lambda_n \leq 9 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^4 \tilde{\sigma}^2 s^5$ where $c_1 \geq 1$ is an absolute constant.
 Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
 \[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
 \]
@@
 \begin{proof}
-
-Because we fit $\hat{g}_k$ against $f_0 - \hat{f}$ instead of $f_0 - f^*$, we need the following decomposition:
+This proof is similar to that of Theorem \ref{thm:convex_consistent}; it requires a few more steps because $\hat{g}_k$ is fitted against $f_0 - \hat{f}$ instead of $f_0 - f^*$.
+We start with the following decomposition:
 \begin{align}
@@
 
-\textbf{Step 1.} To bound term 2, we start from the definition of
+\textbf{Step 1.} To bound term 1, we start from the definition of
 $\hat{g}_k$ and obtain
@@
 \end{align*}
-Using the same analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
+Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
 \begin{align*}
@@
 \end{align*}
-Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
+The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
+We now integrate terms involving only $b$ into the constant $c$. Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
 \begin{align*}
@@
 \end{align*}
+
 Finally, plugging in $\lambda_n \leq 9 s \tilde{\sigma} \sqrt{
@@
 
-\textbf{Step 2.} To bound terms 2 and 3 we derive
+\textbf{Step 2.} We now bound term 3.
 \begin{align*}
@@
 set of additive convex functions is convex itself.
-The last inequality holds due to the condition of the theorem that $n$
-is large enough so that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
-The same bound likewise holds for term 2.
+The last inequality holds because there is a condition in the theorem which states $n$
+is large enough such that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
+The same derivation and the same bound likewise holds for term 2.
 
@@
 \label{lem:uniform_convergence}
-With probability at least $1-\delta$:
-\begin{align*}
-\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
-   c B^3 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
-\end{align*}
+Suppose $n \geq c_1 s\sqrt{sB}$ for some absolute constant $c_1$. Then, with probability at least $1-\delta$:
+\begin{align*}
+\sup_{f \in \mathcal{C}^s_B} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
+   c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+\end{align*}
+where $c_1$ is some absolute constant and $c,C$ are constants possibly dependent on $b$.
 \end{lemma}
@@
 by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
-By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
+By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
+Corollary~\ref{cor:convexbracket_ln} necessitates $\epsilon \in (0, sB\epsilon_3]$ for some absolute constant $\epsilon_3$; we will verify that this condition holds for large enough $n$ when we set the actual value of $\epsilon$.
 For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
@@
 We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.
+One can easily verify that $\epsilon \leq sB \epsilon_3$ condition needed by Corollary~\ref{cor:convexbracket_ln} is satisfied when $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$.
 We have then that, with probability at least $1-\delta$,
 \begin{align*}
-\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
+\sup_{h \in \mathcal{G}} \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
   c B^3 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
 \end{align*}
+
+We fold $b$ into the constant $c$ and the theorem follows.
 

### 2014-11-15 tex/scam/additive_faithful.tex
edits

@@
 
-For general regression, an additive approximation may result in a
+For a general regression function, an additive approximation may result in a
 relevant variable being incorrectly marked as irrelevant. Such
@@
 assumption
-changes the behavior of the additive approximation. We begin
+changes the behavior of the additive approximation. We work with $C=[0,1]^p$ as the support of the distribution in this section but all of our results apply to general hypercubes. We begin
 with a lemma that characterizes the components of the additive approximation under mild conditions.
@@
 However, the second derivative of the objective $\E( f - f^* - \lambda(f' - f^*))^2$ with respect to $\lambda$ is $2 \E( f' - f^*)^2 > 0$.
-The objective is thus strongly convex and $f^*, f'$ cannot both be optimal.
+The objective is thus strongly convex and $\E(f^* - f')^2 = 0$.
+We now apply Lemma~\ref{lem:additive_uniqueness} by letting $\phi_k = f^*_k - f'_k$.
+We conclude that $\E (f^*_k - f'_k)^2 = 0$ for all $k$.
 The uniqueness of $g^*$ is proved similarly.

### 2014-11-15 tex/scam/optimization.tex
edits

@@
 \left[ \begin{array}{ccc}
-    (x_{k1} - x_{\perm{1}k})_+ & \cdots & (x_{k1} - x_{\perm{n-1}k})_+ \\
+    (x_{1k} - x_{\perm{1}k})_+ & \cdots & (x_{1k} - x_{\perm{n-1}k})_+ \\
     \cdots & & \\
-    (x_{kn} - x_{\perm{1}k})_+ & \cdots & (x_{kn} - x_{\perm{n-1}k})_+ 
+    (x_{nk} - x_{\perm{1}k})_+ & \cdots & (x_{nk} - x_{\perm{n-1}k})_+ 
 \end{array} \right]
@@
 where $\Delta_k$ is a $n\times n-1$ matrix such that $\Delta_k(i,j) =
-(x_{\perm{i}k} - x_{\perm{j}k})_+$, $d_k = (d_{\perm{1}k} ,\ldots,
+(x_{ik} - x_{\perm{j}k})_+$, $d_k = (d_{\perm{1}k} ,\ldots,
 d_{\perm{n-1}k})$, and $\mu_k = f_k(x_{\perm{1}k}) \mathbf{1}_n$.

### 2014-11-15 tex/scam/sparsistency.tex
edits

@@
 Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
-Assume without loss of generality that $X_{k\pi_k(n)} - X_{k\pi_k(1)} \geq 1$.
+Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
 
-Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > (X_{k\pi_k(n)} - X_{k\pi_k(1)})| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$ and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \geq \frac{1}{16}$.
+Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > \mathsf{range}_k| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$.
+Suppose also that for all $k \in S^c$, $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
 
@@
 \item The data $X^{(1)},\ldots, X^{(n)} \sim F$ are iid from
-a distribution $F$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-b,b]^p$.
+a distribution $F$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-1,1]^p$.
 \item The response is $Y = f_0(X) + W$ where $W$ is
@@
 Let $\mathcal{C}^1$ denote the set of univariate convex functions
-supported on $[-b,b]$, 
+supported on $[-1,1]$, 
 and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
@@
 \end{equation}
-$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
+$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-1, 1]$ and define
 \begin{equation}
@@
 Suppose assumptions A1-A5 hold.
-Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Define $\tilde{\sigma} \equiv \max(\sigma, B)$ and define $\mathsf{range}_k = X_{k \pi_k(n)} - X_{k \pi_k(1)}$.
 Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $c, C$ dependent on $b$.
@@
 \begin{equation}
-\lambda_n \geq 512 b s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
+\lambda_n \geq 512 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
 \end{equation}  
@@
 \begin{equation}
-\lambda_n \geq (X_{k\pi_k(n)} - X_{k \pi_k(1)}) \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| ,
+\lambda_n \geq \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| ,
 \end{equation}
-$\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \leq \frac{1}{16}$, and both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero.
+$\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$, $\mathsf{range}_k \geq 1$, and both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero.
 \end{theorem}
@@
 \begin{equation}
-\lambda_n \leq 512 b s \tilde{\sigma} \sqrt{\frac{\log^2 np}{n}}
+\lambda_n \leq 512 s \tilde{\sigma} \sqrt{\frac{\log^2 np}{n}}
 \end{equation}

### 2014-11-15 tex/scam/summary.tex
edits

@@
 \item[A4:] The noise is mean-zero sub-Gaussian, independent of $X$.
+\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition.
 \end{packed_enum}
@@
 \begin{stheorem}
-Suppose assumptions A1-A4 hold. Let $\{\hat{f}_i\}$ be any AC solution and
+Suppose assumptions A1-A5 hold. Let $\{\hat{f}_i\}$ be any AC solution and
 let $\{\hat{g}_k\}$ be any DC solution, both estimated with 
@@
 exponential scaling of the ambient dimension, $p = O(\exp(n^c))$
-for $c<1$, as for linear models. The cost of nonparametric estimation is
+for some $0<c<1$, as for linear models. The cost of nonparametric estimation is
 reflected in the scaling with respect to $s=|S|$, which can grow only

### 2014-11-15 tex/scam/supplement.tex
edits

@@
 Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
-
-Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$ and that $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \geq \frac{1}{16}$.
+Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k \pi_k(1)}$.
+
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
 
@@
 Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
-\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and must be unique.
+\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and unique.
 \end{enumerate}
@@
 \begin{theorem} 
-Suppose assumptions A1-A4 hold.
-Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose that $p \leq O\exp( c'' n)$ for some $c'' > 0$ and that $n \geq C''$ for some constant $C''$ possibly dependent on $b$.
-
-If $\lambda_n \geq (8 \cdot 32) 2 b s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
-\begin{align*}
-& \lambda_n > (X_{k\pi_k(n)} - X_{k\pi_k(1)}) \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
-\end{align*}
-and for all $k \in S^c$ and $i' = 1, ..., n-1$, $\frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \leq \frac{1}{16}$.
+Suppose assumptions A1-A5 hold.
+Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $c,C$.
+Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
+
+If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
+\begin{align*}
+& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
+\end{align*}
+and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.
 
@@
 
-Finally, we note that $2b \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ by definition. This concludes the proof for the first part of the theorem.
-
-To prove the second claim, let the interval $[-b, b]$ be divided into $64$ non-overlapping segments each of length $b/32$.
-Because $X_k$ is drawn from a continuous density, the density has a lower bound $c_l > 0$ and the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{b}{32} c_l \right)^n$.
+Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.
+
+To prove the second and third claim, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$.
+Because $X_k$ is drawn from a density with a lower bound $c_l > 0$, the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{1}{32} c_l \right)^n$.
 Let $\mathcal{E}_k$ denote the event that every segment contains some samples.
 
-Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ where $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-b)$ and $\mathsf{gap}_{n} = b - X_{k\pi_k(n)}$.
-
-If any $\mathsf{gap}_i \geq \frac{b}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments.
-Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{b}{16}$ for all $i$.
-
-Thus, we have that, for all $i$:
-
-\[
-\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{X_{k\pi_k(n)} - X_{k \pi_k(1)}} \geq 
-\frac{ b/16 }{ 2b - b/8} \geq 1/16
-\]
-
-Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{b}{32} c_l \right)^n$.
-
-$64 \left( 1 - \frac{b}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $b, c_l$.
+Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.
+
+If any $\mathsf{gap}_i \geq \frac{1}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments.
+Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{1}{16}$ for all $i$.
+
+Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$:
+
+\[
+\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
+\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
+\]
+
+Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.
+
+$64 \left( 1 - \frac{1}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $c_l$.
 Therefore, if $p \leq exp( c'' n)$ for some $c'' < c'$ and if $n$ is large enough, $C' p \exp( - c' n) \leq C' \exp( - (c' - c'') n) \leq \frac{12}{n}$.
@@
 
-Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$.
+Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-1,1]$.
 Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions.
@@
 Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
-minimizer of the restricted regression with $\lambda \leq 9 s
+minimizer of the restricted regression with $\lambda \leq 512 s
 \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
@@
 as the set of convex additive functions centered around the function $f^* - \bar{f}^*$. 
-By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
+By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
 Let us suppose condition~\ref{cond:simplify_covering_number} holds.
 Then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$,
-$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
+$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sB
 )^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the
@@
 $$
-\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
+\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
 $$
 We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{
-  \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
+  \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
     n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h
@@
    &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
    \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
-   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
+   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
+   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
 \end{align*}
 To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
-    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
+    K^{**} (sB)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
 if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
@@
 \]
-where we absorbed $b, K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
+where we absorbed $K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
 % Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
@@
 \end{align}
-Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n}
+Substituting in $\lambda \leq 512 s \tilde{\sigma} \sqrt{\frac{1}{n}
   \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
@@
 Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
-step with $\lambda_n \leq 9 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^4 \tilde{\sigma}^2 s^5$ where $c_1 \geq 1$ is an absolute constant.
+step with $\lambda_n \leq 512 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
 Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
+  c B^2 \sigma \sqrt{ \frac{1}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
 \end{align*}
 The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
-We now integrate terms involving only $b$ into the constant $c$. Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
+Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
 \begin{align*}
@@
 %For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$. 
-by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
-By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
+by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sB}{\epsilon} \right)^{1/2}$.
+By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
 Corollary~\ref{cor:convexbracket_ln} necessitates $\epsilon \in (0, sB\epsilon_3]$ for some absolute constant $\epsilon_3$; we will verify that this condition holds for large enough $n$ when we set the actual value of $\epsilon$.
@@
 \left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
-   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
+   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
 \]
@@
 & \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
  & \leq 
@@
 \E \psi_U(X)^2 - \E \psi_L(X)^2 + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
 \end{align*}
@@
 -sB\epsilon - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
  \| h \|_n^2 - \| h \|_P^2 \leq
 sB\epsilon + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
-\end{align*}
-
-We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
+\end{align*}
+
+We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sB)^{1/2}}{n} \right)^{2/5}$.
 One can easily verify that $\epsilon \leq sB \epsilon_3$ condition needed by Corollary~\ref{cor:convexbracket_ln} is satisfied when $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$.
@@
 \sup_{h \in \mathcal{G}} \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
-  c B^3 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
+  c B^3 \sqrt{ \frac{s^5 \log \frac{2}{\delta}}{n^{4/5}}}
 \end{align*}
@@
 
-subsubsection{Concentration of Measure}
+\begin{lemma}
+\label{lem:additive_uniqueness}
+Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$. Let $\phi(\mathbf{x}) = \sum_{j=1}^p \phi_j(x_j)$ be an additive function.
+
+Suppose that for all $j$, $\phi_j(x_j)$ is bounded and $\E \phi_j(X_j) = 0$. Suppose for some $j$, $\E \phi_j(X_j)^2 > 0$, then it must be that $\E \phi(X)^2 > 0$. 
+\end{lemma}
+
+\begin{proof}
+
+Suppose, for sake of contradiction, that
+
+\begin{align*}
+\E \phi(X)^2 = \E \left( \phi_j(X_j) + \phi_{-j} (X_{-j}) \right)^2 = 0.
+\end{align*}
+
+Let $A_+ = \{ x_j \,:\, \phi_j(x_j) \geq 0 \}$. Since $\E \phi_j(X_j) = 0$, $\E \phi_j(X_j)^2 > 0$, and $\phi_j$ is bounded, it must be that both $A_+$ has probability greater than 0.
+
+Now, define $B_+ = \{ x_{-j} \,:\, \phi_{-j}(x_{-j}) \geq 0 \}$. $B_+$ then must have probability greater than 0 as well.
+
+Since $p(\mathbf{x})$ is a positive density, the set $A_+ \times B_+$ must have a positive probability. However, $\phi > 0$ on $A_+ \times B_+ \subset [0,1]^p$ which implies $\E \phi(X)^2 > 0$.
+
+\end{proof}
+
+\subsubsection{Concentration of Measure}
 
@@
 \label{prop:convexbracket}
-Let $\mathcal{C}$ be the set of convex functions supported on $[-b, b]^d$ and uniformly bounded by $B$. Then there exist constants $\epsilon_3$ and $K^{**}$, dependent on $d$, such that
-\[
-\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
+Let $\mathcal{C}$ be the set of convex functions supported on $[-1, 1]^d$ and uniformly bounded by $B$. Then there exist constants $\epsilon_3$ and $K^{**}$, dependent on $d$, such that
+\[
+\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2B}{\epsilon} \right)^{d/2}
 \]
@@
 \label{prop:convexbracket_lp}
-Let $P$ be a distribution with a density $p$. Let $\mathcal{C}, b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
-\[
-\log N_{[]} (2\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
+Let $P$ be a distribution with a density $p$. Let $\mathcal{C}, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
+\[
+\log N_{[]} (2\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{2B}{\epsilon} \right)^{d/2}
 \]
@@
 \label{cor:convexadditive_lp}
-Let $P$ be a distribution with a density $p$ upper bounded by $c_u$. Let $b, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
+Let $P$ be a distribution with a density $p$. Let $B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
 \[
 \log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**} 
-    \left( \frac{2sbB}{\epsilon} \right)^{1/2}
+    \left( \frac{2sB}{\epsilon} \right)^{1/2}
 \]
@@
 sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} 
-= \sqrt{ \frac{ sK^{**}(sBb)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}.$$
+= \sqrt{ \frac{ sK^{**}(sB)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}.$$
 \end{corollary}
@@
 \begin{align}
-\epsilon^{1/2} \leq 2sK^{**} (sBb)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2 \label{cond:simplify_covering_number}.
+\epsilon^{1/2} \leq 2sK^{**} (sB)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2 \label{cond:simplify_covering_number}.
 \end{align}
@@
 \begin{align*}
-\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}.
+\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}.
 \end{align*}

### 2014-11-17 tex/scam/additive_faithful.tex
minor edits

@@
 additive approximation accurately captures all of the relevant variables.
-We call this property \textit{additive faithfulness}. We first formalize the intuitive notion that a multivariate function $f$ \emph{does not depends on} a coordinate $x_k$.
+We call this property \textit{additive faithfulness}. We first formalize the concept that a multivariate function $f$ \emph{does not depend on} a coordinate $x_k$.
 
@@
 Let $C = [0,1]^p$ and let $f: C \rightarrow \R$.
-We say that $f$ \textit{does not depends on coordinate $k$} if for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a constant as a function of $x_k$.
+We say that $f$ \textit{does not depend on coordinate $k$} if for all $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a constant as a function of $x_k$.
 If $f$ is differentiable, then $f$ does not depend on $k$ if $\partial_{x_k} f(x_k, \mathbf{x}_{-k})$ is 0 for all $\mathbf{x}_{-k}$.
@@
 that, in the population setting, the additive approximation yields
-consistent variable selection.
+a consistent variable screening.
 
@@
 finite sample analysis, where we show that the additive
-approximation is variable selection consistent (or ``sparsistent''), even when the true function is not
+approximation is variable screening consistent, even when the true function is not
 additive.
@@
 In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components.
-The additive approximations may not be faithful if we use parametric components.
+The additive approximations may not be faithful if we assume a parametric form for each of the components.
 For example, suppose we approximate a convex function $f(X)$ by a linear form $X \beta$.
@@
 equation~\eqref{eqn:unconstrained_additive}.  The reason is that $f^*_k$ need not be
-a convex function, as example~\ref{examp:gaussian_counterexample}
-shows. It may be possible to estimate $f^*_k$ via smoothing, but we prefer an approach that is free of smoothing parameters. 
+a convex function, as example~\ref{examp:gaussian_counterexample} and example~\ref{examp:boundaryflat_example} 
+show. It may be possible to estimate $f^*_k$ via smoothing, but we prefer an approach that is free of smoothing parameters. 
 %The function $f^*_k$ can be shown to be smooth but it is preferable to use

### 2014-11-17 tex/scam/sparsistency.tex
minor edits

@@
 Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis.
+We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{mu}$ from our estimation procedure.
 
@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and twice-differentiable. 
+\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
@@
 Define $\tilde{\sigma} \equiv \max(\sigma, B)$ and define $\mathsf{range}_k = X_{k \pi_k(n)} - X_{k \pi_k(1)}$.
-Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $c, C$ dependent on $b$.
+Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $0 < c <1$ and $C$.
 Suppose also

### 2014-11-17 tex/scam/summary.tex
minor edits

@@
 be carried out in parallel. The entire process involves no smoothing parameters.
-Our next results concern the required optimizations, and their finite
+Our next result concerns the required optimizations, and their finite
 sample statistical performance.
@@
 we analyze the finite sample variable selection consistency of convex
-additive modeling, without making the assumption that the true
+additive modeling, without assuming that the true
 regression function $f_0$ is additive.  Our analysis first establishes
@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and twice-differentiable. 
+\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \| \leq B$ for all $k$.

### 2014-11-25 tex/scam/appendix.tex
mods for aos submission

@@
 
-Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
-\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.
+Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry.
+Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
+Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k \pi_k(1)}$.
+
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
+
 Then the following are true:
@@
         + \lambda \bar{\Delta}_k^\tran \mathbf{u}
-      - \nu_k
-\end{align*}
-where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.
-
-We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to zero,
+      - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right)
+\end{align*}
+where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$.
+If $\bar{\Delta}_k d_k = 0$, then $\mathbf{u}$ can be any vector whose $L_1$ norm is less than or equal to $1$.
+$\nu_k \geq 0$ is a vector of Lagrangian multipliers.
+$\nu_{k1}$ does not exist because $d_{k1}$ is not constrained to be non-negative.
+
+We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the $\mathbf{u}, \nu_k$ dual variables can be set in a way to ensure that stationarity:
 \begin{align*}
 \partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
-           - \nu_k = 0 
+           - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right) = 0 
 \end{align*}
 where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$.
-It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ where the inequality is element-wise.
-
-Let us reorder the samples so that the $i$-th sample is the $i$-th smallest sample. 
-We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for
-some $0 < a < 1/2$, where the coordinates of $\mathbf{u}$ correspond
+It clear that to show stationarity, we only need to show that $[-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}]_j = 0$ for $j=1$ and $\geq 0$ for $j=2,...,n-1$.
+
+To ease notational burden, let us reorder the samples in ascending order so that the $i$-th sample is the $i$-th smallest sample. We will from here on write $X_{ki}$ to denote $X_{k \pi_k(i)}$.
+
+Define $i^*$ as the largest index such that $\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} \geq 1/2$. 
+We will construct $\mathbf{u} = (a - a', 0, ..., -a, 0,..., a')$ where
+$a,a'$ are positive scalars, where $-a$ lies at the $i^*$-th coordinate, and where the coordinates of $\mathbf{u}$ correspond
 to the new sample ordering.
-We then just need to show that
-\begin{align*}
-- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
-- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
-- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
-   \textrm{for each } j \\
-- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
-    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
-    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
-   + \lambda (X_{kn} - X_{kj})a &\geq 0 
-\end{align*}
-where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that
-\begin{align*}
-- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
-   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
-- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
-- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0.
-\end{align*}
+
+We define
+
+\begin{align*}
+\kappa &= \frac{1}{\lambda n} \big[ \Delta_k^\tran \hat{r} \big]_1 \\
+a' &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
+     \frac{X_{ki^*}-X_{k1}}{X_{kn} - X_{k i^*}} \frac{1}{8} \\
+a &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
+     \frac{X_{kn}-X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
+\end{align*}
+
+and we verify two facts: first that the KKT stationarity is satisfied and second, that $\| \mathbf{u} \|_1 < 1$ with high probability. Our claim is proved immediately by combining these two facts.
+
+Because $\hat{r}$ and $\mathbf{u}$ are both centered vectors, $\bar{\Delta}_k^\tran \hat{r} = \Delta_k^\tran \hat{r}$ and likewise for $\mathbf{u}$.
+Therefore, we need only show that for $j=1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j = \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$ and that for $j = 2,..., n-1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j \geq \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$.
+
+With our explicitly defined form of $\mathbf{u}$, we can characterize
+\begin{align}
+\big[ \Delta_k^\tran \mathbf{u} \big]_j = 
+  \left \{ \begin{array}{cc} 
+   (-a + a')(X_{k i^*} - X_{kj})+ a'(X_{kn} - X_{k i^*})
+   & \trm{ if } j \leq i^* \\
+   a'(X_{kn} - X_{kj}) & \trm{ if } j \geq i^* 
+     \end{array} \right.
+\end{align}
+
+It is straightforward to check that $\big[ \lambda \Delta_k^\tran \mathbf{u} \big]_1 = \lambda \kappa = \frac{1}{n} \big[ \Delta_k^\tran \hat{r} \big]_1$.
+
+To check that other rows of stationarity condition holds, we characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
+\begin{align*}
+[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i \\
+  & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
+ & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i \\
+ & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r} 
+\end{align*}
+where we denote $\mathsf{gap}_{i'} = X_{ki'} - X_{k(i'-1)}$.
+
+We pause for a second here to give a summary of our proof strategy.
+We leverage two critical observations: first, any two adjacent coordinates in the vector $\frac{1}{n} \Delta_k^\tran \hat{r}$ cannot differ by too much.
+Second, we defined $a, a'$ such that $-a+a' = -\frac{1}{8}$ so that $\lambda \Delta_k^\tran \mathbf{u}$ is a sequence that strictly increases in the first half (for coordinates in $\{1,...,i^*\}$) and strictly decreases in the second half.
+
+We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate.
+We will show that the second sequence increases faster than the first sequence which will imply that the second sequence is larger than the first in the first half of the coordinates.
+We will then work similarly but backwards for the second half.
+
+Following our strategy, We first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.
+
+For $j = 1,..., i^*-1$, we have that
+\begin{align*}
+\lambda [ \Delta_k^\tran \mathbf{u}]_{j+1} - \lambda [ \Delta_k^\tran \mathbf{u}]_{j} &= \lambda (a - a') \mathsf{gap}_{j+1} \\
+ &\geq -\mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \\
+& = [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j+1} - [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j}
+\end{align*}
+
+The inequality follows because $a - a' = \frac{1}{8}$ and thus $\lambda (a - a') \geq \left| \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \right|$. Therefore, for all $j = 1,...,i^*$:
+\begin{align*}
+[ \lambda \Delta_k^\tran \mathbf{u}]_j &\geq [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_j
+\end{align*}
+
+For $j \geq i^*$, we start our comparison from $j=n-1$. First, we claim that $a' > \frac{1}{32}$. To prove this claim, note that
+\begin{align}
+|\kappa| &= \Big|\frac{1}{\lambda n} \sum_{i' > 1} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}\Big| \leq \frac{1}{X_{kn} - X_{k1}}\frac{1}{32} \sum_{i' > 1} \mathsf{gap}_{i'} 
+ = \frac{1}{32} 
+\end{align}
+and that
+\begin{align*}
+\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} &= \frac{X_{kn} - X_{k(i^*+1)} + X_{k(i^*+1)} - X_{ki^*}}{X_{kn} - X_{k1}} \leq \frac{1}{2} + \frac{1}{16}
+\end{align*}
+where the inequality follows because we had assumed that $\frac{X_{k(i+1)} - X_{ki}}{X_{k(n)} - X_{k(1)}} \leq \frac{1}{16}$ for all $i = 1,...,n-1$.
+
+So, we have 
+\begin{align*}
+a' &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \kappa 
+   + \frac{ X_{ki^*} - X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
+ &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
+  \kappa + \frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \frac{1}{8} \right) \\
+&\geq \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
+  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
+&\geq \frac{1}{1/2 + 1/16} \left(
+  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
+&\geq \frac{1}{32}
+\end{align*}
+In the first inequality of the above derivation, we used the fact that $\frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \leq \frac{1}{2} - \frac{1}{16}$.
+In the second inequality, we used the fact that the quantity inside the parentheses is positive and $\frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \geq \frac{1}{1/2 + 1/16}$.
+
+Now consider $j=n-1$. 
+\[
+[ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{n-1} = \frac{1}{n} \mathsf{gap}_n \hat{r}_n 
+ \leq \mathsf{gap}_n \frac{\lambda }{32} \leq \lambda \mathsf{gap}_n a' = \lambda [\Delta_k^\tran \mathbf{u}]_{n-1} 
+\]
+
+For $j = i^*, ..., n-2$, we have that 
+\begin{align*}
+\lambda [\Delta_k^\tran \mathbf{u} ]_j - \lambda [\Delta_k^\tran \mathbf{u}]_{j+1} &= 
+ \lambda a' \mathsf{gap}_{j+1}  \\
+ &\geq \mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r}  \\
+ &\geq  [\frac{1}{n} \Delta_k^\tran \hat{r}]_j - [\frac{1}{n} \Delta_k^\tran \hat{r}]_{j+1}
+\end{align*}
+
+Therefore, for $j = i^*,...,n-2$,
+\begin{align*}
+\lambda [\Delta_k^\tran \mathbf{u}]_j \geq \frac{1}{n} [ \Delta_k^\tran \hat{r}]_j
+\end{align*}
+
+We conclude then that $\lambda [\Delta_k^\tran \mathbf{u} ]_j \geq [\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for all $j = 2,...,n-1$.
+
+We have thus verified that the stationarity equations hold and now will bound $\| \mathbf{u} \|_1$.
+
+\begin{align*}
+\| \mathbf{u} \|_1 = | a - a'| + a + a' \leq \frac{1}{8} + 2 a \leq \frac{1}{8} + 4 |\kappa| + \frac{1}{2}  \leq \frac{1}{8} + \frac{1}{8} + \frac{1}{2} < 1
+\end{align*}
+In the third inequality, we used the fact that $|\kappa| \leq \frac{1}{32}$.
+
 We have thus proven that there exists one solution $\{ \hat{d}_k
@@
 \begin{theorem} 
-Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-
-If $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
-\[
-\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|.
-\]
+Suppose assumptions A1-A5 hold.
+Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$.
+Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
+
+If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
+\begin{align*}
+& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
+\end{align*}
+and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.
+
 Therefore, for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$ from optimization~\ref{opt:alternate_opt_concave} are zero. 
@@
 additive function outputted by the restricted regression. Note that
-both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $sB$. 
-Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$.
-By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at most $1 - \delta$.
+both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $2sB$. 
+Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at least $1-\delta$.
+By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at least $1 - \delta$.
 
@@
 $\tilde{\sigma} = \max(\sigma, B)$,
-and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$, which is acceptable since $\delta \leq 1$ and the theorem presupposes that $\sqrt{ \log 2np } \geq 1$.
+and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$.
+This assumption holds under the conditions in the theorem which state that $p \leq \exp( c n)$ and $n \geq C$ for some small constant $c$ and large constant $C$.
 
@@
 and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
-respectively. Setting $\delta = \frac{12}{n}$ gives the desired
-result.
+respectively. Setting $\delta = \frac{12}{n}$ gives the desired expression.
+
+Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.
+
+To prove the second and the third claims, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$.
+Because $X_k$ is drawn from a density with a lower bound $c_l > 0$, the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{1}{32} c_l \right)^n$.
+Let $\mathcal{E}_k$ denote the event that every segment contains some samples.
+
+Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.
+
+If any $\mathsf{gap}_i \geq \frac{1}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments.
+Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{1}{16}$ for all $i$.
+
+Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$,
+
+\[
+\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
+\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
+\]
+
+Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.
+
+$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$.
+Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c'') n) \leq \frac{12}{n}$.
+
+Taking an union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.
+
 \end{proof}
@@
 Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
-minimizer of the restricted regression with $\lambda \leq 9 s
+minimizer of the restricted regression with $\lambda \leq 512 s
 \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
-Suppose $n \geq c_1 \max(\sqrt{sB}, B)$.
+Suppose $n \geq c_1 s \sqrt{sB}$.
 Then with probability at least $1-\frac{C}{n}$,
@@
    &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
    \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
-   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
-\end{align*}
-We require that $n$ is large enough so that $\epsilon \in (0, sB
-\epsilon_3]$, and to ensure that
-conditions~\eqref{cond:simplify_covering_number} hold, we need that
-$\log n \geq 2$ and $n \geq c B$ where $c$ is a constant dependent
-only on $K^{**}$ and $b$.
-The conditions are satisfied if we set $\epsilon = sB \sqrt{ \frac{(s
-    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$ and assume 
-$n \geq c_1 \max( \sqrt{sB}, B)$, as stated in the theorem. 
-%% ?? Setting $\epsilon$ in this way thus also balances the two terms.
+   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
+   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
+\end{align*}
+To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
+    K^{**} (sB)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
+if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
+$\epsilon \in (0, sB \epsilon_3]$ for some absolute constant $\epsilon_3$ as required by the bracketing number results (Corollary~\ref{cor:convexadditive_lp}).
+Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.
 
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
-   \frac{s b^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   \frac{s^{6/5} B^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
+  c sB \sigma \sqrt{ 
+   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
 \]
@@
    &\leq cB^2 \sigma 
-    \sqrt{ \frac{s^3 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
+    \sqrt{ \frac{s^4}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
  +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
 \end{align}
-Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n}
+Substituting in $\lambda \leq 512 s \tilde{\sigma} \sqrt{\frac{1}{n}
   \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
@@
 Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
-step with $\lambda_n \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.
+step with $\lambda_n \leq 512 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
 Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
 \[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
 \]
@@
 \end{align*}
-Using the same analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
+Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
 \begin{align*}
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
-\end{align*}
+  c B^2 \sigma \sqrt{ \frac{1}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
+\end{align*}
+The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
 Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
@@
 %For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$. 
-by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$.
-By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
+by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sB}{\epsilon} \right)^{1/2}$.
+By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
+Corollary~\ref{cor:convexbracket_ln} necessitates $\epsilon \in (0, sB\epsilon_3]$ for some absolute constant $\epsilon_3$; we will verify that this condition holds for large enough $n$ when we set the actual value of $\epsilon$.
 For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
@@
 -sB\epsilon - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
  \| h \|_n^2 - \| h \|_P^2 \leq
 sB\epsilon + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
-\end{align*}
-
-We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBb)^{1/2}}{n} \right)^{2/5}$.
+(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
+\end{align*}
+
+We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sB)^{1/2}}{n} \right)^{2/5}$.
+One can easily verify that $\epsilon \leq sB \epsilon_3$ condition needed by Corollary~\ref{cor:convexbracket_ln} is satisfied when $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$.
 We have then that, with probability at least $1-\delta$,
 \begin{align*}
-\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
-  c B^3 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
-\end{align*}
+\sup_{h \in \mathcal{G}} \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
+  c B^3 \sqrt{ \frac{s^5 \log \frac{2}{\delta}}{n^{4/5}}}
+\end{align*}
+
+The theorem follows immediately.
 
@@
 Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function.
-Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$.
+Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are continuous as functions of $x_k$.
 Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.

### 2014-11-25 tex/scam/paper-submit.tex
false positive edit
mods for aos submission

@@
 \input{macros}
+\arxiv{1411.1805}
 
@@
 \vskip10pt
-\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
+\author{\fnms{Min} \snm{Xu${}^*$}\ead[label=e1]{minx@cs.cmu.edu}}
 \comma 
-\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
+\author{\fnms{Minhua} \snm{Chen${}^\dag$}\ead[label=e2]{minhua@galton.uchicago.edu}}
 \and
 \author{\fnms{John}
-  \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
-\address{Machine Learning Department, Carnegie Mellon University,
+  \snm{Lafferty${}^\dag$}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{${}^*$Machine Learning Department, Carnegie Mellon University,
   Pittsburgh PA 15213}
-\address{Department of Statistics, University of Chicago, Chicago IL 60637}
+\address{${}^\dag$Department of Statistics, University of Chicago, Chicago IL 60637}
 \end{aug}
@@
 \maketitle
+
 \vskip10pt
@@
 
+\clearpage
 \bibliographystyle{imsart-nameyear}

### 2014-11-25 tex/scam/summary.tex
minor

@@
 regularization parameter $\lambda$ scaling as
-$\lambda = \Theta \Big( sB \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
+$\lambda = \Theta \Big( s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np} \Big)$. 
 Suppose in addition that

### 2015-04-25 tex/scam/additive_faithful.tex
major paper revisions

@@
 Let $F$ be a distribution on $C=[0,1]^p$ with a positive density
-function $p$. Let $f: C \rightarrow \R$ be an integrable function,
-and define 
+function $p$. Let $f: C \rightarrow \R$ be in $L^2(F)$. Let
 \begin{align*}
@@
 &\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
-\E f_k(X_k) = 0,\; \forall k=1,\ldots, p \right\}.
+f_k \in L^2(F),\, \E f_k(X_k) = 0,\; k=1,\ldots, p \right\}.
 \end{align*}
-Then $\mu^* = \E f(X)$, 
+With $\mu^* = \E f(X)$, 
 \begin{equation}
@@
 \begin{proof}
-  Let $f^*_1,...,f^*_p, \mu^*$ be the minimizers as defined.  We first
+  Let $f^*_1,...,f^*_p, \mu^*$ be the minimizers as defined; they exist since the set of mean zero additive functions is a closed subspace of $L^2(F)$.  We first
   show that the optimal $\mu$ is $\mu^* = \E f(X)$ for any $f_1, ...,
@@
 \begin{equation}
-\E\Bigl[ \big( f(X) - \mu^* - \sum_{k' \neq k}
-  f^*_{k'} (X_{k'}) - f_k (X_k) \big)^2\Bigr]
+\min_{f_k} \E  \big( f(X) - \mu^* - \sum_{k' \neq k}
+  f^*_{k'} (X_{k'}) - f_k (X_k) \big)^2 
 \end{equation}
@@
 \E[ f(X) - \sum_{k' \neq k}
-f_{k'}(X_{k'}) \given x_k] - \mu^*
+f_{k'}^*(X_{k'}) \given x_k] - \mu^*
 \end{equation} 
@@
        p(\mathbf{x}_{-k} \given x_k ) 
-     (f(\mathbf{x}) - \sum_{k'\neq k} f_{k'} (x_{k'})  -\mu^*) d \mathbf{x}_{-k} 
+     (f(\mathbf{x}) - \sum_{k'\neq k} f^*_{k'} (x_{k'})  -\mu^*) d \mathbf{x}_{-k} 
  \end{align}
-The square error objective is strongly convex,
-and the second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive.
-Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ] - \E f(X)$ is unique.
-Noting that $\E[ f(X) -\sum_{k'\neq k} f_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero as a function of $x_k$
-completes the proof.
+
+To prove uniqueness, suppose $\tilde{f} = \sum_{j=1}^p \tilde{f}_j$ is another additive function that achieves the same square error.
+Let $\nu \in [0,1]$, consider $\E\left( f(X) - \mu^* - (f^* + \nu (\tilde{f} - f^*)) \right)^2$ as a function of $\nu$.
+The objective is strongly convex if $\E (\tilde{f} - f^*)^2$, and so $\E( \tilde{f} - f^*)^2 = 0$ by the assumption that $f^*$ and $\tilde{f}$ are both optimal solutions.
+By Lemma~\ref{lem:additive_uniqueness}, we conclude that $\E( f^*_j - \tilde{f}_j )^2 = 0$ as well and thus, $f^*_j = \tilde{f}_j$ almost everywhere.
+
+We note that $\E[ f(X) -\sum_{k'\neq k} f^*_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero as a function of $x_k$, which shows that $f^*_k$'s are feasible.
+
 \end{proof}
@@
 
-In particular, if $F$ is the uniform distribution,
-then $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k})
-d\mathbf{x}_{-k}$.
+In particular, under the uniform distribution, $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} - \int f(\mathbf{x}) d\mathbf{x}$.
 
 \begin{example} Using Corollary~\ref{cor:product_int_reduction}, we
-  give two examples of \emph{additively unfaithfulness} under the
+  give two examples of \emph{additive unfaithfulness} under the
   uniform distribution---where relevant variables are
@@
 Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. $p(\mathbf{x})$ satisfies
-the \emph{boundary flatness condition} if for all $j$, and for all $\mathbf{x}_{-j}$,
-
+the \emph{boundary flatness condition} if $0 < \inf_{\mathbf{x}} p(\mathbf{x}) \leq \sup_{\mathbf{x}} p(\mathbf{x}) < \infty$, and for all $j$, there exists some $\epsilon > 0$ such that for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
 \begin{equation}
@@
 
-The boundary flatness condition is a weak condition. For instance, it is
-satisfied when the density is flat at the boundary of support---more
-precisely, when the joint density satisfies the property that
-$\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =
-\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at boundary
-points $x_j = 0, x_j=1$. The boundary flatness property is also
-trivially satisfied when $p$ is a product density.
+The boundary flatness condition intuitively states that
+the conditional effect of $X_k$ weakens as $\mathbf{x}$ approaches the boundary.
+It is a weak condition because it affects only an $\epsilon$-small region around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from the boundary; it can induce arbitrary correlation structure (provided $p(\mathbf{x}) >0$) and need not be continuous.
+Before presenting the main theorem, let us see some examples of boundary flat distributions.
+
+\begin{example} The following densities satisfy boundary flatness.
+\begin{enumerate}
+\item If $\mathbf{p}$ is a product density, then boundary flatness is trivially
+satisfied.
+\item Let $p(\mathbf{x})$ be a joint density such that $0 < \inf_{\mathbf{x}} p(\mathbf{x}) \leq \sup_{\mathbf{x}} p(\mathbf{x}) < \infty$.
+Suppose $p(\mathbf{x})$ has a bounded second derivative for all $\mathbf{x}$.
+If, for all $j$,
+$\partial_{x_j} p(x_j,\mathbf{x}_{-j}) =
+\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0$ at $x_j = 0, 1$.
+Then it is possible to show that the two derivatives of $p(\mathbf{x}_{-j} \given x_j) = \frac{p(x_j, \mathbf{x}_{-j})}{p(x_j)}$ are 0 at $x_j = 0,1$; boundary flatness thus holds.
+\item Suppose $p(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
+Let $q(\mathbf{x})$ be a boundary flat density over $[0,1]^p$, take the uniform distribution for instance.
+Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
+Furthermore, $\epsilon$ and $\lambda$ can be made arbitrarily small and therefore, any bounded density over a hypercube can be approximated arbitrarily well by a boundary flat distribution.
+
+% $$
+% p'(\mathbf{x}_{-j} \given x_j) = \frac{ p(x_j, \mathbf{x}_{-j}) p'(x_j) - 
+%    p'(x_j, \mathbf{x}_{-j}) p(x_j)}{ p(x_j)^2 } = 0 
+% $$
+% \begin{align*}
+% p''(\mathbf{x}_{-j} \given x_j) = &
+%     \frac{ p(x_j)^2 \left( p(x_j, x_{-j}) p''(x_j) - p''(x_j, x_{-j}) p(x_j) \right) - 2p(x_j)p'(x_j) \left(p(x_j, x_{-j})p'(x_j) - p'(x_j, x_{-j}) p(x_j)  \right) }{p(x_j)^4}
+%  \end{align*}
+\end{enumerate}
+\end{example}
+
+% For instance, it is
+% satisfied when the density is flat at the boundary of support---more
+% precisely, when the joint density satisfies the property that
+% $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =
+% \frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at boundary
+% points $x_j = 0, x_j=1$. The boundary flatness property is also
+% trivially satisfied when $p$ is a product density.
 
@@
 the boundary flatness property. 
-If $f$ is convex and twice differentiable, then $f$ is additively faithful under $p$.
+If $f$ is convex and continuously twice differentiable, then $f$ is additively faithful under $p$.
 \end{theorem}
@@
 
-We pause to give some intuition before we presenting the full proof.
+We pause to give some intuition before we present the full proof.
 Suppose that the underlying distribution has a product density.
@@
 likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k,
-\mathbf{x}_{-k})$. We then differentiate under the integral, valid
-because all functions are bounded, and obtain
+\mathbf{x}_{-k})$. \\
+
+We differentiate with respect to $x_k$ at $x_k = 0,1$ under the integral.
+The detail necessary to verify the validity of this operation is technical and given in Section~\ref{sec:dominated_condition} of the supplementary material.
+
 \begin{gather}
@@
   Theorems~\ref{thm:convex_faithful} to simplify the proof.  We
-  expect, however, that this this smoothness condition is not
+  expect, however, that this smoothness condition is not
   necessary---every convex function can be approximated arbitrarily
@@
 \begin{remark}
-In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components.
-The additive approximations may not be faithful if we assume a parametric form for each of the components.
+In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components; the additive approximations may not be faithful if we take a parametric form.
 For example, suppose we approximate a convex function $f(X)$ by a linear form $X \beta$.
-The optimal linear function in the population setting is $\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$.
-Suppose the $X$'s are independent and follow a symmetric distribution and suppose $f(\mathbf{x}) = x_1^2 - \E[X_1^2]$, then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 - X_1 \E[X_1^2]] = 0$.
+The optimal linear function in the population setting is $\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma$ is the covariance matrix.
+Suppose the $X$'s are independent, follow a symmetric distribution, have unit variance, and suppose $f(\mathbf{x}) = x_1^2 - \E[X_1^2]$, then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 - X_1 \E[X_1^2]] = 0$.
 \end{remark}
@@
 Such a limit condition however is not obeyed by many common distributions such as the multivariate Gaussian distribution.
-The next example shows that certain convex functions are not additive faithful under certain multivariate Gaussian distributions.
+The next example shows that certain convex functions are not additively faithful under certain multivariate Gaussian distributions.
 \end{remark}
@@
 \label{examp:gaussian_counterexample}
-Consider a two dimensional quadratic function $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c$ where $H = \begin{pmatrix} H_{11} & H_{12} \\ H_{12} & H_{22}\end{pmatrix}$ is positive definite and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma = \begin{pmatrix}1 & \alpha \\ \alpha & 1 \end{pmatrix}$.
+Consider a two dimensional quadratic function $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c$ with zero mean where $H = \begin{pmatrix} H_{11} & H_{12} \\ H_{12} & H_{22}\end{pmatrix}$ is positive definite and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma = \begin{pmatrix}1 & \alpha \\ \alpha & 1 \end{pmatrix}$.
 As we show in Section~\ref{sec:gaussian_example} of the Appendix, the additive approximation has the
@@
 where $\mathcal{C}^1$ is the set of univariate convex functions.
-The convex functions $\{f^*_k\}$ are not additively faithful by
-themselves, i.e., it could be that the true function $f$ depends on variable $k$ but $f^*_k = 0$.
-However, faithfulness can be restored by coupling the $f^*_k$'s with a set of univariate concave fits on the \emph{residual} $f - f^*$:
+
+If $p(\mathbf{x})$ is a product density, then $\E[ f(X) \given x_k]$ is convex in $x_k$ and the additive projection is simultaneously the convex additive projection.
+Thus, in this case, additive faithfulness trivially holds for the convex additive projection.
+For a general boundary flat density $p(\mathbf{x})$ however, the additive projection need not be convex and we thus cannot say anything about additive faithfulness of the convex additive projection.
+
+Luckily, we can restore faithfulness by coupling the $f^*_k$'s with a set of univariate concave fits on the \emph{residual} $f - f^*$:
 \begin{equation}
@@
 g^*_k = \arg\min \Big\{
-   \E\Bigl( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \Bigr)^2
+   \E\Bigl( f(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k(X_k) \Bigr)^2
     \,:\, g_k \in \mh \mathcal{C}^1, \E g_k(X_k) = 0 
@@
 satisfies the boundary flatness condition. Suppose that $f$ is convex
-and twice differentiable, and that $\partial_{x_k} p( \mathbf{x}_{-k} \given x_k )$, and
-$\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$ are all continuous
-as functions of $x_k$.  Let $f^*_k$ and $g^*_k$ be as defined in equations
+and continuously twice differentiable. Let $f^*_k$ and $g^*_k$ be as defined in equations
 \eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, 
@@
 \label{cor:faithfulness_extension}
-Suppose $p(x)$ is a positive density on $C=[0,1]^p$ satisfying the boundary flatness condition.
-Let $f(\mathbf{x})$ be a convex twice differentiable function on $C$.
-Let $\phi(\mathbf{x}_{-k})$ be any function that does not depend on $x_k$.
+Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ satisfying the boundary flatness condition.
+Let $f(\mathbf{x})$ be a convex and continuously twice differentiable function on $C$.
+Let $\phi(\mathbf{x}_{-k})$ be a bounded function that does not depend on $x_k$.
 Then, we have that the unconstrained univariate function
@@
 equation~\ref{eqn:convex_additive} and
-equation~\ref{eqn:concave_postprocess}. Let $\phi(\mathbf{x}_{-k}) \equiv \sum_{k' \neq k} f^*_{k'}(x_{k'})$.
+equation~\ref{eqn:concave_postprocess}.
+Let $\phi(\mathbf{x}_{-k}) \equiv \sum_{k' \neq k} f^*_{k'}(x_{k'})$.
+Each $f^*_{k'}$ is convex and thus continuous on $(0,1)$.
+$f^*_{k'}(x_{k'})$ is defined at $x_{k'} = 0,1$; thus, $f^*_{k'}$ must be bounded and $\phi(\mathbf{x}_{-k})$ is bounded.
 
-Then we have that
+We have that
 \begin{align}
@@
 $\E[ X_k^2 - m_k^2] = 0$.
-Since the optimum has a closed form $c^* = \frac{\E\big[(f(X) -\phi(X_{-k}))(X_k^2 - m^2_k)\big]}{\E X_k^2}$, we deduce that
+Since the optimum has a closed form $c^* = \frac{\E\big[(f(X) -\phi(X_{-k}))(X_k^2 - m^2_k)\big]}{\E X_k^2 - m^2_k}$, we deduce that
 \begin{align*}
@@
 We denote $h^*_k(x_k) = \E[ f(X) - \phi(X_{-k}) \given x_k]$.
+$f(\mathbf{x})$ and $\phi(\mathbf{x}_{-k})$ are both bounded and so $h^*_k(x_k)$ is bounded as well.
+Therefore, $h^*_k$ is square integrable and there exists a fourier series $s_n(x_k)$ convergent to $h^*_k$ in $L_2$.
+Since $p(\mathbf{x})$ is bounded, $\lim_{n \rightarrow \infty} \E ( s_n(X_k) - h^*_k(X_k )^2 \rightarrow 0$ as well.
 
-Under the derivative continuity conditions in the theorem, we apply Lemma~\ref{lem:acdc_derivative_bound} in the appendix and know that $h^*_k(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$.
+%Under the derivative continuity conditions in the theorem, we apply Lemma~\ref{lem:acdc_derivative_bound} in the appendix and know that $h^*_k(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$.
 Therefore, for a large enough positive scalar $\alpha$, $h^*_k(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second derivative and is thus convex.
+
+If we can show that $\E h^*_k(X_k)^2 = 0$, we would apply Lemma~\ref{cor:faithfulness_extension} and finish the proof. So let us suppose for sake of contradiction that $\E h^*_k(X_k)^2 > 0$.\\
+
+Let $0 < \epsilon < 1$ be fixed and let $n$ be large enough such that $\E( s_n(X_k) - h^*_k(X_k))^2 \leq \epsilon \E h^*_k(X_k)^2 $.
+
+Since $s_n(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$, there exist some positive scalar $\alpha$ such that $s_n(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second derivative and is thus convex.
 
@@
 \argmin_{c \in \R} 
-\E\Big( f(X) - \phi(X_{-k}) - c\big( h^*_k(X_k) + \alpha(X_k^2 - m_k^2)\big) \Big)^2 = 0
+\E\Big( f(X) - \phi(X_{-k}) - c\big( s_n(X_k) + \alpha(X_k^2 - m_k^2)\big) \Big)^2 = 0
 \]
-This is because $c\big( h^*_k(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered function.
+This is because $c\big( s_n(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered function.
 
 Again, $c^* = \frac{\mathbb{E}[(f(X)-\phi(X_{-k}))\big( 
-           h^*_k(X_k) + \alpha (X_k^2 - m_k^2) \big)]}{\mathbb{E}
-       \big( h^*_k(X_k) + \alpha (X_k^2 - m_k^2) \big)^2} = 0$, so
+           s_n(X_k) + \alpha (X_k^2 - m_k^2) \big)]}{\mathbb{E}
+       \big( s_n(X_k) + \alpha (X_k^2 - m_k^2) \big)^2} = 0$, so
 \begin{align*}
-\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( h^*_k(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
-\mathbb{E}[ (f(X) - \phi(X_{-k})) h^*_k(X_k) ] \\
-& = \mathbb{E}\Big[ \mathbb{E}[ f(X) - \phi(X_{-k}) \given X_k]  h^*_k(X_k) \Big] \\
-& = \mathbb{E} h^*_k(X_k)^2 = 0
+\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( s_n(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
+\mathbb{E}[ (f(X) - \phi(X_{-k})) s_n(X_k) ] \\
+& = \mathbb{E}\Big[ \mathbb{E}[ f(X) - \phi(X_{-k}) \given X_k]  s_n(X_k) \Big] \\
+& = \mathbb{E} h^*_k(X_k) s_n(X_k)  = 0
 \end{align*}
-where the first equality follows because $\E[ (f(X) - \phi(X_{-k})) (X_k^2 - m_k^2)] = 0$. Therefore, we get that $h^*_k = 0$. Now we use
+where the first equality follows because $\E[ (f(X) - \phi(X_{-k})) (X_k^2 - m_k^2)] = 0$. \\
+
+We have chosen $s_n$ such that $\E(h^*_k(X_k) - s_n(X_k))^2 \leq \epsilon \E h^*_k(X_k)^2$ for some $\epsilon < 1$.
+But, $\E (h^*_k(X_k) - s_n(X_k))^2 = \E h^*_k(X_k)^2 - 2 \E h^*_k(X_k)s_n(X_k) + \E s_n(X_k)^2 \geq \E h^*_k(X_k)^2$.
+This is a contradiction and therefore, $\E h^*_k(X_k)^2 = 0$.\\
+
+Now we use
 Lemma~\ref{cor:faithfulness_extension} with $\phi(\mathbf{x}_{-k}) =
@@
 Now we turn to uniqueness.
-Suppose for sake of contradiction that $f^*$ and $f'$ are optimal solutions to (\ref{eqn:convex_additive}) and $\E (f'-f^*)^2 > 0$.
-$f^* + \lambda ( f' - f^*)$ for any $\lambda \in [0,1]$ must then also be an optimal solution by convexity of the objective and constraint.
-However, the second derivative of the objective $\E( f - f^* - \lambda(f' - f^*))^2$ with respect to $\lambda$ is $2 \E( f' - f^*)^2 > 0$.
-The objective is thus strongly convex and $\E(f^* - f')^2 = 0$.
-We now apply Lemma~\ref{lem:additive_uniqueness} by letting $\phi_k = f^*_k - f'_k$.
-We conclude that $\E (f^*_k - f'_k)^2 = 0$ for all $k$.
+Suppose for sake of contradiction that $f^*$ and $\tilde{f}$ are optimal solutions to (\ref{eqn:convex_additive}) and $\E (\tilde{f} - f^*)^2 > 0$.
+$f^* + \lambda ( \tilde{f}  - f^*)$ for any $\lambda \in [0,1]$ must then also be an optimal solution by convexity of the objective and constraint.
+However, the second derivative of the objective $\E( f - f^* - \lambda(\tilde{f} - f^*))^2$ with respect to $\lambda$ is $2 \E( \tilde{f} - f^*)^2 > 0$.
+The objective is thus strongly convex and $\E(f^* - \tilde{f})^2 = 0$.
+We now apply Lemma~\ref{lem:additive_uniqueness} by letting $\phi_k = f^*_k - \tilde{f}_k$.
+We conclude that $\E (f^*_k - \tilde{f}_k)^2 = 0$ for all $k$.
 The uniqueness of $g^*$ is proved similarly.
@@
 %%% mode:latex ***
-%%% TeX-master: "paper.tex" ***
+%%% TeX-master: "paper-submit.tex" ***
 %%% End: ***

### 2015-04-25 tex/scam/experiments.tex
major paper revisions

@@
 $\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
-represents the relevant variable set, and 
+represents the set of relevant variables, and 
 $\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
@@
 ($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
+$n=100,200,\ldots,1000$. We use independent design by setting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
 independently generated data sets and plot the probability of recovery
@@
 ranging from $\lambda^{(1)} = 0$ (no regularization) to $2$. For each $\lambda^{(t)}$
-we obtain a function value matrix $\bds{h}^{(t)}$ with $p=13$
-columns. The non-zero columns in this matrix indicate the variables selected
-using $\lambda^{(t)}$.  We plot $\|\bds{h}^{(t)}\|_{\infty}$ and
-the column-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
-$\frac{\|\bds{h}^{(t)}\|_{\infty,1}}{\|\bds{h}^{(1)}\|_{\infty,1}}$
-in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
-plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
+we obtain a function value matrix $\bds{f}^{(t)}$ with $p=13$
+columns and $n=506$ rows. The non-zero columns in this matrix indicate the variables selected using $\lambda^{(t)}$.
+
+In Figure~\ref{Boston}(a), we plot on the y-axis the norm $\|\bds{f}^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$.
+Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|\bds{f}^{(t)}_j\|_{\infty}}{\sum_j \|\bds{f}^{(1)}\|_{\infty}}$.
+Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.
+For comparison, we
+plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(b).
 From the figures we observe that the first three variables selected by
@@
 regularization, and plot the estimated additive functions in Figure
-\ref{Boston}(e). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
+\ref{Boston}(d). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
 nonlinear effects which cannot be captured by LASSO. The shapes of
@@
 of the mean and standard deviation of the predictive mean squared
-error (MSE) is shown in Figure \ref{Boston}(d). Since for AC/DC the same
+error (MSE) is shown in Figure \ref{Boston}(c). Since for AC/DC the same
 regularization level $\lambda^{(t)}$ may lead to a slightly different number of selected
@@
 %\hskip-10pt 
-AC/DC $\|f_k\|_\infty$ paths & 
+(a) AC/DC $\|f_k\|_\infty$ paths & 
 %\hskip-25pt
-LASSO $|\beta_k|$ paths \\
+(b) LASSO $|\beta_k|$ paths \\
 %\end{tabular}
@@
 \\
-predictive MSE & estimated functions from AC/DC
+(c) predictive MSE & (d) estimated functions from AC/DC
 \end{tabular}
@@
 \caption{Results on Boston housing data, showing regularization paths,
- MSE and fitted functions.}\label{Boston}
+ MSE and fitted functions.} \label{Boston}
 \end{figure*}

### 2015-04-25 tex/scam/sparsistency.tex
major paper revisions

@@
 Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis.
-We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{mu}$ from our estimation procedure.
+We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{\mu}$ from our estimation procedure.
 
@@
 \min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
-   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, \ldots, d_{k,n-1} \geq 0
+   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{\pi_k(2)k}, \ldots, d_{\pi_k(n-1)k} \geq 0
 \]
@@
 
-Let $\pi_k(i)$ be a reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry.
+Let $\pi_k(i)$ be a reordering of $X_k$ in ascending order so that $X_{\pi_k(n)k}$ is the largest entry.
 Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
-Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
+Define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.
 
 Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > \mathsf{range}_k| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$.
-Suppose also that for all $k \in S^c$, $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
+Suppose also that for all $k \in S^c$, $\max_{i=1,...,n-1} \frac{X_{\pi_k(i+1)k} - X_{\pi_k(i)k}}{\mathsf{range}_k} \leq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
 
@@
 \begin{equation}
-f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
+f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f(X)
 \big)^2.
@@
   weak assumptions on the true regression function $f_0$ in
-  A2. In particular, we do not assume that $f_0$ is additive. In
+  A2. In particular, we do not assume that $f_0$ is additive. An
   important direction for future work is to weaken assumption A1.
@@
 achievable with an exponential scaling of the ambient dimension
-scaling, $p = O(\exp(n^c))$ for some $0<c<1$, just as in parametric models.
+scaling, $p = O(\exp(cn))$ for some $0<c<1$, just as in parametric models.
 The cost of nonparametric modeling through shape constraints is

### 2015-04-25 tex/scam/supplement.tex
major paper revisions

@@
 We restate Theorem~\ref{thm:deterministic} first for convenience. 
-The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).
+The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at the beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).
 
@@
 
-Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry.
+Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{\pi_k(n)k}$ is the largest entry.
 Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.
-Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k \pi_k(1)}$.
-
-Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
+Define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.
+
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{\pi_k(i+1)k} - X_{\pi_k(i)k}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
 
@@
     \lambda \sum_{k=1}^p \| \bar{\Delta}_k d_k \|_\infty -
-    \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki} 
+    \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{\pi_k(i)k} d_{\pi_k(i)k} 
 \end{equation}
-with the constraint that $\nu_{ki} \geq 0$ for all $k,i$.
+with the constraint that $\nu_{\pi_k(i)k} \geq 0$ for all $k,i$.
 
@@
 We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$.
+
+To ease notational burden, let us reorder the samples $\{X_{ik}\}_{i=1,...,n}$ in ascending order so that the $i$-th sample is the $i$-th smallest sample.
+We will from here on write $X_{ik}$ to denote $X_{\pi_k(i)k}$, $d_{ik}$ to denote $d_{\pi_k(i)k}$, etc.
+
 The Lagrangian form of the optimization, in terms of just $d_k$, is
@@
    + \lambda \| \bar{\Delta}_k d_k\|_\infty
-  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
-\]
-with the constraint that $v_{ki} \geq 0$ for $i=2,...,n-1$.
+  - \sum_{i=2}^{n-1} \nu_{ik} d_{ik}
+\]
+with the constraint that $\nu_{ik} \geq 0$ for $i=2,...,n-1$.
 
@@
 
-We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the $\mathbf{u}, \nu_k$ dual variables can be set in a way to ensure that stationarity:
+We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S^c$, and $r = \hat{r}$ and show that the $\mathbf{u}, \nu_k$ dual variables can be set in a way to ensure that stationarity:
 \begin{align*}
@@
 \end{align*}
-where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$.
-It clear that to show stationarity, we only need to show that $[-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}]_j = 0$ for $j=1$ and $\geq 0$ for $j=2,...,n-1$.
-
-To ease notational burden, let us reorder the samples in ascending order so that the $i$-th sample is the $i$-th smallest sample. We will from here on write $X_{ki}$ to denote $X_{k \pi_k(i)}$.
-
-Define $i^*$ as the largest index such that $\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} \geq 1/2$. 
+where $\| \mathbf{u} \|_1 \leq 1$ and $\nu_k \geq 0$.
+It is clear that to show stationarity, we only need to show that $[-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}]_j = 0$ for $j=1$ and $\geq 0$ for $j=2,...,n-1$.
+
+Define $i^*$ as the largest index such that $\frac{X_{nk} - X_{i^*k}}{X_{nk} - X_{1k}} \geq 1/2$. 
 We will construct $\mathbf{u} = (a - a', 0, ..., -a, 0,..., a')$ where
@@
 \begin{align*}
-\kappa &= \frac{1}{\lambda n} \big[ \Delta_k^\tran \hat{r} \big]_1 \\
-a' &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
-     \frac{X_{ki^*}-X_{k1}}{X_{kn} - X_{k i^*}} \frac{1}{8} \\
-a &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
-     \frac{X_{kn}-X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
+\kappa &= \frac{1}{\lambda n (X_{nk} - X_{1k})} \big[ \Delta_k^\tran \hat{r} \big]_1 \\
+a' &= \frac{X_{nk} - X_{1k}}{X_{nk} -  X_{i^*k}} \kappa + 
+     \frac{X_{i^*k}-X_{1k}}{X_{nk} - X_{i^*k}} \frac{1}{8} \\
+a &= \frac{X_{nk} - X_{1k}}{X_{nk} -  X_{i^*k}} \kappa + 
+     \frac{X_{nk}-X_{1k}}{X_{nk} - X_{i^*k}} \frac{1}{8} \\
 \end{align*}
@@
 
-With our explicitly defined form of $\mathbf{u}$, we can characterize
+With our explicitly defined form of $\mathbf{u}$, we can characterize $\Delta_k^\tran \mathbf{u}$.
+Note that under sample reordering, the $j$-th column of $\Delta_k$ is $(0, ..., x_{(j+1)k} - x_{jk},\, x_{(j+2)k} - x_{jk},\, ...,\, x_{nk} - x_{jk} )$ where the first $j$-th entries are all 0.
+\begin{align*}
+\Delta_k^\tran \mathbf{u}]_j &= \sum_{i > j} (X_{ik} - X_{jk}) \mathbf{u}_i \\
+  &= \mathbf{u}_{i^*} (X_{i^*k} - X_{jk}) \delta_{i^* \geq j} + \mathbf{u}_n (X_{nk} - X_{jk})\\ 
+  &= -a (X_{i^*k} - X_{jk}) \delta_{i^* \geq j} + a' (X_{nk} - X_{jk}) \\
+\end{align*}
+Simple algebra shows then that
 \begin{align}
@@
   \left \{ \begin{array}{cc} 
-   (-a + a')(X_{k i^*} - X_{kj})+ a'(X_{kn} - X_{k i^*})
+   (-a + a')(X_{i^*k} - X_{jk})+ a'(X_{nk} - X_{ i^*k})
    & \trm{ if } j \leq i^* \\
-   a'(X_{kn} - X_{kj}) & \trm{ if } j \geq i^* 
+   a'(X_{nk} - X_{jk}) & \trm{ if } j \geq i^* 
      \end{array} \right.
@@
 
-It is straightforward to check that $\big[ \lambda \Delta_k^\tran \mathbf{u} \big]_1 = \lambda \kappa = \frac{1}{n} \big[ \Delta_k^\tran \hat{r} \big]_1$.
+It is straightforward to check that $\big[ \lambda \Delta_k^\tran \mathbf{u} \big]_1 = \lambda (X_{nk} - X_{1k}) \kappa = \frac{1}{n} \big[ \Delta_k^\tran \hat{r} \big]_1$.
 
@@
 \begin{align*}
-[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i \\
+[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ik} - X_{jk}) \hat{r}_i \\
   & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
@@
 \end{align*}
-where we denote $\mathsf{gap}_{i'} = X_{ki'} - X_{k(i'-1)}$.
+where we denote $\mathsf{gap}_{i'} = X_{i'k} - X_{(i'-1)k}$.
 
 We pause for a second here to give a summary of our proof strategy.
-We leverage two critical observations: first, any two adjacent terms in the sequence $\frac{1}{n} \Delta_k^\tran \hat{r}$ cannot differ by too much.
+We leverage two critical observations: first, any two adjacent coordinates in the vector $\frac{1}{n} \Delta_k^\tran \hat{r}$ cannot differ by too much.
 Second, we defined $a, a'$ such that $-a+a' = -\frac{1}{8}$ so that $\lambda \Delta_k^\tran \mathbf{u}$ is a sequence that strictly increases in the first half (for coordinates in $\{1,...,i^*\}$) and strictly decreases in the second half.
@@
 \begin{align}
-|\kappa| &= \Big|\frac{1}{\lambda n} \sum_{i' > 1} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}\Big| \leq \frac{1}{X_{kn} - X_{k1}}\frac{1}{32} \sum_{i' > 1} \mathsf{gap}_{i'} 
+|\kappa| &= \Big|\frac{1}{\lambda n} \sum_{i' > 1} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}\Big| \leq \frac{1}{(X_{kn} - X_{k1})^2}\frac{1}{32} \sum_{i' > 1} \mathsf{gap}_{i'} 
  = \frac{1}{32} 
 \end{align}
-and that
-\begin{align*}
-\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} &= \frac{X_{kn} - X_{k(i^*+1)} + X_{k(i^*+1)} - X_{ki^*}}{X_{kn} - X_{k1}} \leq \frac{1}{2} + \frac{1}{16}
-\end{align*}
-where the inequality follows because we had assumed that $\frac{X_{k(i+1)} - X_{ki}}{X_{k(n)} - X_{k(1)}} \leq \frac{1}{16}$ for all $i = 1,...,n-1$.
+because $\sum_{i'>1} \mathsf{gap}_{i'} = X_{nk} - X_{1k}$ by definition and $X_{nk} - X_{1k} \geq 1$ by assumption of the theorem. We note also that
+\begin{align*}
+\frac{X_{nk} - X_{i^*k}}{X_{nk} - X_{1k}} &= \frac{X_{nk} - X_{(i^*+1)k} + X_{(i^*+1)k} - X_{i^*}k}{X_{nk} - X_{1k}} \leq \frac{1}{2} + \frac{1}{16}
+\end{align*}
+where the inequality follows because we had assumed that $\frac{X_{(i+1)k} - X_{ik}}{X_{nk} - X_{1k}} \leq \frac{1}{16}$ for all $i = 1,...,n-1$.
 
@@
 \begin{align*}
-a' &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \kappa 
-   + \frac{ X_{ki^*} - X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
- &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
-  \kappa + \frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \frac{1}{8} \right) \\
-&\geq \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
+a' &= \frac{X_{nk} - X_{1k}}{X_{nk} - X_{i^*k}} \kappa 
+   + \frac{ X_{i^*k} - X_{1k}}{X_{nk} - X_{i^*k}} \frac{1}{8} \\
+ &= \frac{X_{nk} - X_{1k}}{X_{nk} - X_{i^*k}} \left(
+  \kappa + \frac{X_{i^*k} - X_{1k}}{X_{nk} - X_{1k}} \frac{1}{8} \right) \\
+&\geq \frac{X_{nk} - X_{1k}}{X_{nk} - X_{i^*k}} \left(
   -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
@@
 \end{align*}
-In the first inequality of the above derivation, we used the fact that $\frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \leq \frac{1}{2} - \frac{1}{16}$.
-In the second inequality, we used the fact that the quantity inside the parentheses is positive and $\frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \geq \frac{1}{1/2 + 1/16}$.
+In the first inequality of the above derivation, we used the fact that $\frac{X_{i^*k} - X_{1k}}{X_{nk} - X_{1k}} \leq \frac{1}{2} - \frac{1}{16}$.
+In the second inequality, we used the fact that the quantity inside the parentheses is positive and $\frac{X_{nk} - X_{1k}}{X_{nk} - X_{i^*k}} \geq \frac{1}{1/2 + 1/16}$.
 
@@
 Define $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $c,C$.
+Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$.
 Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
@@
 and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
-respectively. Setting $\delta = \frac{12}{n}$ gives the desired
-result.
+respectively. Setting $\delta = \frac{12}{n}$ gives the desired expression.
 
@@
 
-To prove the second and third claim, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$.
+To prove the second and the third claims, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$.
 Because $X_k$ is drawn from a density with a lower bound $c_l > 0$, the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{1}{32} c_l \right)^n$.
@@
 
-Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$:
+Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$,
 
@@
 
-$64 \left( 1 - \frac{1}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $c_l$.
-Therefore, if $p \leq exp( c'' n)$ for some $c'' < c'$ and if $n$ is large enough, $C' p \exp( - c' n) \leq C' \exp( - (c' - c'') n) \leq \frac{12}{n}$.
+$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$.
+Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c'') n) \leq \frac{12}{n}$.
 
@@
 
-We fold $b$ into the constant $c$ and the theorem follows.
+The theorem follows immediately.
 
@@
 % \subsection{Supporting Technical Material}
-
-\subsubsection{Supporting Lemma for Theorem~\ref{thm:acdc_faithful}}
-
-\begin{lemma}
-\label{lem:acdc_derivative_bound}
-Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function.
-Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$.
+\subsubsection{Detail for Proof of Theorem~\ref{thm:convex_faithful}} 
+\label{sec:dominated_condition}
+
+Let $p(\mathbf{x}_{-k} \given x_k), f(\mathbf{x}), r(\mathbf{x}_{-k})$ be defined as in the proof of Theorem~\ref{thm:convex_faithful}.
+
+We claim that 
+\[
+\partial_{x_k} \int_{\mathbf{x}_{-k}} 
+  p(\mathbf{x}_{-k} \given x_k)\left( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \right) d\mathbf{x}_{-k} 
+ = \int_{\mathbf{x}_{-k}} \partial_{x_k} \Big( p(\mathbf{x}_{-k} \given x_k)\left( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \right) \Big) d \mathbf{x}_{-k}
+\]
+And likewise for the second derivative.\\
+
+ The first derivative of the integrand is 
+$$
+p'(\mathbf{x}_{-k} \given x_k)\left( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \right) + p(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}).
+$$
+$f(\mathbf{x})$ is continuous and bounded and $p'(\mathbf{x}_{-k} \given x_k)$ is bounded for all $\mathbf{x}_{-k}$ and all $x_k \in [0,\epsilon) \cup (1-\epsilon, 1]$ by boundary flatness.
+Thus, $p'(\mathbf{x}_{-k} \given x_k) f(\mathbf{x})$ is bounded for all $\mathbf{x}_{-k}$ and all $x_k \in [0,\epsilon) \cup (1-\epsilon, 1]$.\\
+
+$r(\mathbf{x}_{-k}) p(\mathbf{x})$ is integrable, and since $\inf_{\mathbf{x}} p(\mathbf{x}) > 0$, $r(\mathbf{x}_{-k})$ is integrable.
+Since $p'(\mathbf{x}_{-k} \given x_k)$ is bounded, $r(\mathbf{x}_{-k}) p'(\mathbf{x}_{-k} \given x_k) \leq |r(\mathbf{x}_{-k})|M$ for some constant $M$ for all $\mathbf{x}_{-k}$ and $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$.
+\\
+
+$f'(x_k, \mathbf{x}_{-k})$ is continuous and thus bounded, therefore, $p(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k})$ is bounded for all $\mathbf{x}_{-k}$ and $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$.
+
+This verifies that, for all $\mathbf{x}_{-k}$ and for all $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$, the first derivative is less than $M |r(\mathbf{x}_{-k})| + C$, which is integrable.
+By dominated convergence theorem, we can thus exchange the derivative with the integral.
+\\
+
+The second derivative of the integrand is 
+$$
+p''(\mathbf{x}_{-k} \given x_k) \left( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \right) + 
+  2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) + p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k})
+$$
+
+We just need to remember that $p''(\mathbf{x}_{-k} \given x_k)$ is bounded for all $\mathbf{x}_{-k}$ and $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$ by boundary flatness, that $f''(x_k, \mathbf{x}_{-k})$ is a continuous function of $\mathbf{x}$, and the same argument applies.
+
+% \subsubsection{Supporting Lemma for Theorem~\ref{thm:acdc_faithful}}
+
+% \begin{lemma}
+% \label{lem:acdc_derivative_bound}
+% Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function.
+Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are continuous as functions of $x_k$.
 Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.
 
-Then, $h^*_k(x_k) \equiv \E[ f(X) - \phi(X_{-k}) \given x_k]$ is twice
-differentiable and has a second derivative lower 
-bounded away from $-\infty$.
-\end{lemma}
-
-\begin{proof}
-We can write
-\[
-h^*_k(x_k) = \int_{\mathbf{x}_{-k}} \big(f(\mathbf{x}) - \phi(\mathbf{x}_{-k})\big) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
-\]
-The integrand is bounded because it is a sum-product of continuous functions over a compact set. Therefore, we can differentiate under the integral and derive that
-\begin{align*}
-\partial_{x_k} h^*_k(x_k) &= 
-    \int_{\mathbf{x}_{-k}} f'(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p'(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
-\partial_{x_k}^2 h^*_k(x_k) &= 
-    \int_{\mathbf{x}_{-k}} f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + 2f'(\mathbf{x}) p'(\mathbf{x}_{-k} \given x_k)  + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p''(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
-\end{align*}
-where we have used the shorthand $f'(\mathbf{x}), p'(\mathbf{x}_{-k}
-\given x_k)$ to denote $\partial_{x_k} f(\mathbf{x})$, $\partial_{x_k}
-p(\mathbf{x}_{-k} \given x_k)$, etc.
-
-This proves that $h^*_k(x_k)$ is twice-differentiable.
+% Then, $h^*_k(x_k) \equiv \E[ f(X) - \phi(X_{-k}) \given x_k]$ is twice
+% differentiable and has a second derivative lower 
+% bounded away from $-\infty$.
+% \end{lemma}
+
+% \begin{proof}
+% We can write
+% \[
+% h^*_k(x_k) = \int_{\mathbf{x}_{-k}} \big(f(\mathbf{x}) - \phi(\mathbf{x}_{-k})\big) p(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
+% \]
+% The integrand is bounded because it is a sum-product of continuous functions over a compact set. Therefore, we can differentiate under the integral and derive that
+% \begin{align*}
+% \partial_{x_k} h^*_k(x_k) &= 
+%     \int_{\mathbf{x}_{-k}} f'(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p'(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}\\
+% \partial_{x_k}^2 h^*_k(x_k) &= 
+%     \int_{\mathbf{x}_{-k}} f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k) + 2f'(\mathbf{x}) p'(\mathbf{x}_{-k} \given x_k)  + (f(\mathbf{x}) - \phi(\mathbf{x}_{-k}) p''(\mathbf{x}_{-k} \given x_k) d \mathbf{x}_{-k}
+% \end{align*}
+% where we have used the shorthand $f'(\mathbf{x}), p'(\mathbf{x}_{-k}
+% \given x_k)$ to denote $\partial_{x_k} f(\mathbf{x})$, $\partial_{x_k}
+% p(\mathbf{x}_{-k} \given x_k)$, etc.
+
+% This proves that $h^*_k(x_k)$ is twice-differentiable.
 To see that the second derivative is lower bounded, we note that $f''(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k)$ is non-negative and the other terms in the second-derivative are all continuous functions on a compact set and thus bounded.
-\end{proof}
+% \end{proof}
 
@@
 \label{lem:additive_uniqueness}
-Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$. Let $\phi(\mathbf{x}) = \sum_{j=1}^p \phi_j(x_j)$ be an additive function.
-
-Suppose that for all $j$, $\phi_j(x_j)$ is bounded and $\E \phi_j(X_j) = 0$. Suppose for some $j$, $\E \phi_j(X_j)^2 > 0$, then it must be that $\E \phi(X)^2 > 0$. 
+Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$.
+Let $f(\mathbf{x}) = \sum_{j=1}^p f_j(x_j)$ and $h(\mathbf{x}) = \sum_{j=1}^d h_j(x_j)$ be two additive functions such that $\E( f(X) - h(X) )^2 = 0$.
+Suppose also that $\E f_j(X_j) = 0, \E h_j(X_j) = 0$ for all $j$.
+Then, it must be that $\E( f_j(X_j) - h_j(X_j))^2 = 0$ for all $j$.
 \end{lemma}
@@
 
-Suppose, for sake of contradiction, that
-
-\begin{align*}
-\E \phi(X)^2 = \E \left( \phi_j(X_j) + \phi_{-j} (X_{-j}) \right)^2 = 0.
-\end{align*}
-
-Let $A_+ = \{ x_j \,:\, \phi_j(x_j) \geq 0 \}$. Since $\E \phi_j(X_j) = 0$, $\E \phi_j(X_j)^2 > 0$, and $\phi_j$ is bounded, it must be that both $A_+$ has probability greater than 0.
-
-Now, define $B_+ = \{ x_{-j} \,:\, \phi_{-j}(x_{-j}) \geq 0 \}$. $B_+$ then must have probability greater than 0 as well.
-
-Since $p(\mathbf{x})$ is a positive density, the set $A_+ \times B_+$ must have a positive probability. However, $\phi > 0$ on $A_+ \times B_+ \subset [0,1]^p$ which implies $\E \phi(X)^2 > 0$.
+Let $\phi(\mathbf{x}) = f(\mathbf{x}) - g(\mathbf{x})$ and it is clear that $\phi(\mathbf{x}) = \sum_{j=1}^d \phi_j(x_j)$ with $\phi_j(x_j) = f_j(x_j) - h_j(x_j)$ and $\E \phi_j(X_j) = 0$.
+It is also immediate that $E \phi(X)^2 = 0$.
+\\
+
+Let $P$ be the probability measure induced by the density $p$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure.
+Since $p > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well.
+\\
+
+For sake of contradiction, let us assume that for some $j$, $\E \phi_j(X_j)^2 > 0$.
+Then, $P(A_j ) > 0$ where $A_j = \{ \mathbf{x} \in [0,1]^p \,:\, \phi_j(x_j) > 0 \}$.
+To see this, suppose that $\phi_j \leq 0$ almost surely.
+Then, $\E \phi_j = 0$ implies that $\phi_j = 0$ almost surely, contradicting the assumption that $\E \phi_j(X_j)^2 > 0$.\\
+
+For $j' \neq j$, define $B_{j'} = \{ \mathbf{x} \in [0,1]^p \,:\, \phi_{j'}(x_{j'}) \geq 0 \}$.
+$P( B_{j'} ) > 0$ because, if not, then $\phi_{j'} < 0$ almost surely and that contradicts the $\E \phi_{j'}(X_{j'}) = 0$ assumption.
+\\
+
+Since the probability measure $P$ is absolutely continuous with respect to the Lebesgue measure on $[0, 1]^p$, $\lambda (A_j) > 0$.
+Let $\lambda_1$ be the one dimensional Lebesgue measure on $[0,1]$ and let $A^1_j = \{ x_j \in [0,1] \,:\, \phi_j(x_j) > 0\}$.
+From the fact that $\lambda(A_j) > 0$, and that $A_j = A^1_j \times [0,1]^{p-1}$, $\lambda_1(A^1_j) > 0$.
+Same reasoning show that $\lambda_1(B^1_{j'}) > 0$ where $B^1_{j'}$ is similarly defined.\\
+
+$A_j \cap \left( \bigcap_{j'} B_{j'} \right) = A^1_j \times \prod_{j'} B^1_{j'}$.
+Therefore, $\lambda ( A_j \cap \left( \bigcap_{j'} B_{j'} \right) ) = \lambda_1(A^1_j)  \prod_{j'} \lambda_1 (B_{j'}) > 0$.
+Since the density of $P$ is positive, $P( A_j \cap \left( \bigcap_{j'} B_{j'} \right) ) > 0$ and since $\phi > 0$ on this event, we conclude that $\E \phi(X)^2 > 0$, thus giving us the desired contradiction.
 

### 2015-04-27 tex/scam/reviews-v1/response-v1.tex
initial commit

\documentclass[pdftex,12pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{graphicx,subfigure}
\usepackage[pdftex]{color}
\usepackage{epic,eepic,eepicemu}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{graphics}
\usepackage{psfrag,latexsym}
\usepackage{times}
\newcommand{\thetamin}{\ensuremath{\theta^*_{min}}}
\newcommand{\mutinc}{\ensuremath{\alpha}}
\bibliographystyle{abbrv}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\degmax{d}
\def\pdim{p}
\def\numobs{n}
\let\hat\widehat
\definecolor{blue}{rgb}{0.01,0.01,0.75}
\def\reviewercomment#1{{\it\textcolor{blue}{#1}}\smallskip}
\parindent0pt
\parskip12pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\vspace*{5pt}

We thank the reviewers for their helpful comments regarding our
submission. We have carefully addressed all these comments. The
following describes the revisions made to the manuscript in response
to the reviews.

\subsection*{Associate Editor}

\reviewercomment{Below I recapitulate a few
point of the reviewers', along with some questions/comments of my own.
These (as well as other points in the reviews) need to be thoroughly
addressed in the revised manuscript.}

\begin{enumerate}
\item \reviewercomment{Boundary flatness condition: much of the paper's analysis hinges on
this condition.  Reviewer 3 raises some concerns about when it holds,
especially for functions that are not necessarily supported on the
unit hypercube.  See also the point below.}

We have added commentary on this here and here.

\item \reviewercomment{Intuitively, variable selection is very closely related to
estimating a function (or possibly its partial derivatives) in the
sup-norm.  It is well-known that accurate estimation of functions
(whether in $L^2$ or the sup-norm) with bounded smoothness in dimension
$s$ requires a sample size that grows exponentially in $s$.  For this
reason, the past result of Comminges and Dalalyan (suggesting an
exponential growth for variable selection) is to be expected.
However, in terms of metric entropy, the class of convex functions
behaves roughly like the class of two-smooth functions (e.g., Dryanov
(2009)).  So at first glance, this makes the result of this paper
rather surprising---namely, that one can somehow side-step any
exponential growth in $s$, even though the metric entropy is still
scaling as badly as the case of 2-smooth functions.  I wondered if the
authors could comment and shed insight on this fact, which seems a
little counterintuitive.  What I suspect that it could mean is that
the additive faithfulness (AF) condition, or one of the sufficient
conditions for AF (namely boundary flatness) are somehow very
restrictive.  Could the authors comment on these issues?}

We have made these revisions.

\item \reviewercomment{Writing and proofs need to be tidied up in places to make it easier
to follow.  See various comments of referees, particularly the
detailed ones of R2.  Also, in Theorem 3, please remind the author of
when/where the AC/DC estimators were defined.  (I was forced to dig
back through.)}

We have tidied up.

\end{enumerate}

\subsection*{Reviewer 1}

\reviewercomment{Conceptually, I have a few questions for the authors to address:}

\begin{enumerate}[(1)]
\item \reviewercomment{If the true regression function $f_0$ can actually be written as a
sum of univariate convex functions (plus noise), are there natural
conditions that one can provide for when additive faithfulness will
hold? Similarly, is there a simpler version of Theorem 3 that can be
stated when $f_0$ is actually a sum of univariate convex functions? This
would seem to depend on an appropriate statement for Assumption (A3).}

\item \reviewercomment{If we actually wish to fit smooth convex univariate components, is
it easy to add this condition as a regularization term and incorporate
it into the analysis?}

\item \reviewercomment{Assuming model selection consistency, can one derive prediction
error bounds using the fitted $f_k$'s and $g_k$'s, as well? Prediction error
bounds seem quite relevant due to possible model misspecification when
$f_0$ is not actually a sum of univariate convex functions.}

\item \reviewercomment{In order to improve clarity, the authors should define the convex
additive model at the top of page 5: $f(x_i) = \sum_{k=1}^p f_k(x_{ik})$, where the
$f_k$'s are convex.  Otherwise, the notation in equation (2.3) is
initially a bit confusing.}

\item \reviewercomment{Another notational comment: the use of the
distribution function $F$ seems unnecessary (e.g., Lemma 3.1 and
Corollary 3.1), since everything is already defined in terms of the
joint density function $p(x)$. (An additional suggestion would be to use
a different letter to represent the joint density function, since $p$ is
already used to represent the dimensionality of the distribution.)}

\item \reviewercomment{I would suggest including the dependence on the positive-valued lower
bound on $p(x)$ (as assumed in (A5)) in the statement of Theorem 3. This
is a point worth commenting upon, since the earlier theorems only
require $p(x)$ to be strictly positive. Assumption (A5) seems like it
could also be interpreted as a sort of minimum signal strength
requirement for successful variable selection.}

\item \reviewercomment{It would be good to point to Assumption (A3) at the beginning of
Section 5 when discussing the $B$-boundedness condition. In the third
paragraph, the authors might note that the $B$-boundedness condition
arises from the analysis of Theorem 5.2. To clarify, the penultimate
paragraph on page 22 should state that Theorem 5.1 controls false
positives alone, whereas Theorem 5.3 (to follow) provides
finite-sample results controlling the false negative rate.}

\item \reviewercomment{At the top
of page 23, the remark regarding mutual incoherence conditions is a
bit confusing. Aren’t the conditions imposed in Theorem 5.1 on the
covariates essentially analogous to the mutual incoherence conditions
in this case? }

\item \reviewercomment{In the simulation section, the authors might consider comparing the
set of variables selected after the AC step only with the set of
variables selected via the entire AC/DC algorithm. This would help
illustrate the necessity of the concave fitting step in addition to
the convex additive fit alone.}

Minor typos:
\begin{enumerate}[(i)]
\item \reviewercomment{In Section 2.3, it would be good to actually state the regularized
objective function being analyzed, rather than waiting until Section
4.}
\item \reviewercomment{Assumption (A3) on page 7 is missing the subscript $\infty$.}
\item \reviewercomment{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
it seems to be the sub-Gaussian parameter of the additive noise.}
\item \reviewercomment{Perhaps Section 3 should be titled something other than ``Additive
faithfulness'' (maybe ``Population- level results''?).}
\item \reviewercomment{The first paragraph of Section 5 should read
  ``Figure 3'' rather than ``Algorithm 3.''}

\item \reviewercomment{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
\item \reviewercomment{The first sentence of Section 5.1 should read optimization (4.8).}
\end{enumerate}

\end{enumerate}

\subsection*{Reviewer 2}

\reviewercomment{I found many (unimportant) mistakes in the proofs (I
  did not mention them all in the minor comments), which need to be
  read again carefully.}

\begin{enumerate}
\item \reviewercomment{I have a problem with the assertion of
  uniqueness in Lemma 3.1 and Therorem 3.2. First, in Lemma 3.1, it is
  clear that $f^∗$ is unique. But $(f_1^∗, \ldots, f_p^∗)$ is not. What is
  shown is that, for $k$ fixed and given $(f_j^*)_{j\neq k}$, $f_k^*$ is unique. Next,
  in Theorem 3.2, the proof of uniqueness (bottom of page 16 and top
  of page 17) is not at all correct.
   Now, to see why I think that, with the assumtions made on $X$, there is
   not uniqueness, simply suppose for instance that $p = 2$ and $X_2 = g(X_1)$
   for a certain function $g$. Then if $(f_1^∗, f_2^∗)$ is a solution,
   $(f_1^∗ + f_2^ \circ g, 0)$ is also a solution.}

\end{enumerate}

\subsection*{Reviewer 3}

Major comments:

\begin{enumerate}
\item \reviewercomment{The basis of all the results seem to be the boundary flatness
condition. This condition seems to be an artifact of the analysis and
based on my reading, it is unclear how restrctive this assumption
is. The authors claim it is weak just after stating it and then
present several straightforward examples in which it doesn't hold
(e.g. $f(x_1,x_2)=x_1 x_2$) and multivariate Gaussian examples. Hence it is unclear to me how
likely a given function is likely to fit into this framework.}

\item \reviewercomment{Following on from the previous point, the simulation study also does
not add any further insight to this issue since the simulations are
for multivariate Gaussians where other parametric approaches that deal
with covariance seem more suitable. It is puzzling to me that the
authors did not consider non-parametric examples where the additive
model framework seems more suitable.}

\end{enumerate}

Minor comments:

\begin{enumerate}
\item \reviewercomment{I didn't think there was any need for Section 2
  since it feels very repetitive and slightly confusing that parts of
  the text are repeated almost verbatim. I would suggest removing this section.}

\item \reviewercomment{Page 2, second last paragraph `and and.'}
\end{enumerate}

\vspace*{10pt}

Sincerely,

Min Xu, Minhua Chen, and John Lafferty\\[1pt]
\today{}

\bibliography{local}
\end{document}

### 2015-04-27 tex/scam/supplement.tex
appendix edits

@@
 
-To check that other rows of stationarity condition holds, we characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
+To check that $\lambda [ \Delta_k^\tran \mathbf{u} ]_j \geq [ \frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j > 1$, we first characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
 \begin{align*}
@@
 We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate.
-We will show that the second sequence increases faster than the first sequence which will imply that the second sequence is larger than the first in the first half of the coordinates.
+We will show that the second sequence increases faster than the first sequence, which will imply that the second sequence is larger than the first in the first half of the coordinates.
 We will then work similarly but backwards for the second half.
 
-Following our strategy, We first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.
+Following our strategy, we first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.
 
@@
 \big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is
-strongly convex as a function of $\nu$. Thus, it cannot be that
+strongly convex as a function of $\zeta$. Thus, it cannot be that
 $\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective, and we
@@
 \in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets
-of subgradients. Let $\{ \nu_{ki} \}$ and $\{
-\nu'_{ki} \}$ be the two sets of positivity dual
+of subgradients. Let $\{ \nu_{ik} \}$ and $\{
+\nu'_{ik} \}$ be the two sets of positivity dual
 variables, for $k=1,..,p$ and $i=1,...n-1$.  Note that since there is no positivity constraint on
-$d_{k1}$, we let $\nu_{k1} = 0$ always.
+$d_{1k}$, we let $\nu_{1k} = 0$ always.
 
@@
 \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
-   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}_k - \nu = 
+   + \lambda \left( \begin{array}{c} 
+          \bar{\Delta}_1^\tran \mathbf{u}_1  
+          \\ ... \\ \bar{\Delta}_p^\tran \mathbf{u}_p \end{array} \right)
+    - \nu = 
 \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
-   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0.
+   + \lambda \left( \begin{array}{c} 
+          \bar{\Delta}_1^\tran \mathbf{u}'_1  
+          \\ ... \\ \bar{\Delta}_p^\tran \mathbf{u}'_p \end{array} \right)
+ - \nu' = 0.
 \] 
@@
 \]
-Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
+Since $\bar{\Delta} \hat{d}' = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
 \[
@@
 \[
-\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
-  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
-  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}.
-\]
-with $\nu_{ki} \geq 0$.
-The same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
+\mathcal{L}_{\trm{cave}}(c_k, \nu_k) = 
+  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k c_k \big \|_2^2 + 
+  \lambda \| \bar{\Delta}_k c_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ik} c_{ik}.
+\]
+with $\nu_{ik} \geq 0$.
+The same reasoning applies to show that $\hat{c}_k = 0$ for all $k\in S^c$ satisfies KKT conditions sufficient for optimality.
 \end{proof}
@@
 Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$.
-Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.
-
-If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
+Define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.
+
+If $\lambda_n \geq 2 (12 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
 \begin{align*}
@@
 \end{align*}
-and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.
+and $\max_{i'} \frac{X_{\pi_k(i'+1)k} - X_{\pi_k(i')k}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.
 
@@
 $\tilde{\sigma} = \max(\sigma, B)$,
-and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$.
-This assumption holds under the conditions in the theorem which state that $p \leq \exp( c n)$ and $n \geq C$ for some small constant $c$ and large constant $C$.
+and assumed that $\sqrt{\log \frac{2n}{\delta}} \geq 1$.
+We will eventually take $\delta = O(1/n)$ so this assumption holds under the condition in the theorem which state that $n \geq C$ for some large constant $C$.
 
@@
    \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
-  &\leq 4s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
-  &\leq 8 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
+  &\leq 8 s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
+  &\leq 12 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
 \end{align*}
@@
 
-Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.
+Finally, we note that $2 \geq (X_{\pi_k(n)k} - X_{\pi_k(1)k})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.
 
@@
 
-Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.
+Define $\mathsf{gap}_i = X_{\pi_k(i+1)k} - X_{\pi_k(i)k}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{\pi_k(1)k} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{\pi_k(n)k}$.
 
@@
 \[
-\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
-\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
-\]
-
-Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.
+\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \leq 
+\frac{ 1/16 }{ 2 - 1/8} \leq 1/16
+\]
+
+Taking a union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.
 
 $p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$.
-Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c'') n) \leq \frac{12}{n}$.
-
-Taking an union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.
+Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c) n) \leq \frac{12}{n}$.
+
+Taking a union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.
 
@@
 Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
-minimizer of the restricted regression with $\lambda \leq 512 s
+minimizer of the restricted regression with $\lambda \leq 768 s
 \tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
@@
 \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 Cnp},
 \end{align}
@@
 \textbf{Step 1.} The function $\hat{f}$ minimizes the penalized
-empricial risk by definition. We would thus like to say that the
+empirical risk by definition. We would thus like to say that the
 penalized empirical risk of $\hat{f}$ is no larger than that of
@@
 as the set of convex additive functions centered around the function $f^* - \bar{f}^*$. 
-By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
+By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose log-size is bounded by $\log N_{[]}( \epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{4sBc_u}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3c_u]$.
 Let us suppose condition~\ref{cond:simplify_covering_number} holds.
 Then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$,
-$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sB
-)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the
+$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq \epsilon + 2sB \sqrt{ \frac{sK^{**}(sBc_u)^{1/2} \log \frac{2}{\delta}}{\epsilon^{1/2} n}}$. We verify at the
 end of the proof that 
@@
 $$
-\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
+\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq \epsilon +  (2sB) \sqrt{ \frac{sK^{**}(sBc_u)^{1/2} \log \frac{2}{\delta}}{\epsilon^{1/2} n}}.
 $$
-We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{
-  \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
+We denote $\epsilon_{n,\delta} \equiv (2sB) \sqrt{
+  \frac{sK^{**}(sBc_u)^{1/2} \log \frac{2}{\delta}}{\epsilon^{1/2}
     n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h
 \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such
-that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. Then
+that $\|h-h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n, \delta}$. Then
 $\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.
@@
 \]
-Because $w$ is a sub-Gaussian random variable, we have that for any fixed vector
-$h_L = (h_L(X_1),...,h_L(X_n))$, with probability at least $1-\delta$,
-$|\langle w, h_L \rangle_n | \leq \| h_L \|_n \sigma \sqrt{
-  \frac{2}{n} \log \frac{2}{\delta} }$. Using another union bound, we
-have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq sB
-\sigma \sqrt{ \frac{2}{n}\log \frac{2 N_{[]}}{\delta}}$ has
+Because $w$ is a sub-Gaussian random variable, we have that the random variables $w_i h_L(X_i)$ are independent, centered, and sub-Gaussian with scale at most $2\sigma sB$. 
+Thus, with probability at least $1-\delta$,
+$|\langle w, h_L \rangle_n | \leq 2\sigma sB \sqrt{
+  \frac{1}{n} \log \frac{2}{\delta} }$. Using another union bound, we
+have that the event $\sup_{h_L} |\langle w, h_L \rangle| \leq 2\sigma sB
+\sqrt{ \frac{1}{n}\log \frac{2 N_{[]}}{\delta}}$ has
 probability at most $1-\delta$.
@@
 \lefteqn{|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| \leq 
-     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta})} \\
-   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
-   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
-   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
-   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
-\end{align*}
-To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
-    K^{**} (sB)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
+     | \sup_{h_L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, 2\delta})} \\
+   &\leq   2 sB \sigma \sqrt{ \frac{ \log N_{[]} + \log \frac{2}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq  2 sB \sigma \sqrt{ \frac{sK^{**} (4sBc_u)^{1/2} + \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
+   &\leq 2 sB \sigma \sqrt{ \frac{sK^{**} (4sBc_u)^{1/2} + \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
+   \sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + 2sB \sigma \sqrt{2 \frac{sK^{**} (sBc_u)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
+   &\leq \sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 8 sB \sigma \sqrt{ \frac{sK^{**} (sBc_u)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
+\end{align*}
+On the last line, we have assumed that conditions~\ref{cond:simplify_covering_number} hold so that $ \frac{sK^{**}(sBc_u)^{1/2}}{\epsilon^{1/2}} + \log 1/\delta \leq \frac{sK^{**} (sBc_u)^{1/2}}{\epsilon^{1/2}} \log 1/\delta$.
+
+We choose $\epsilon = \left( \frac{(sB)^2 (s
+    K^{**} (sBc_u)^{1/2})}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our results. It is easy to verify that
 if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
-$\epsilon \in (0, sB \epsilon_3]$ for some absolute constant $\epsilon_3$ as required by the bracketing number results (Corollary~\ref{cor:convexadditive_lp}).
+$\epsilon \in (0, sB \epsilon_3c_u]$ for some absolute constant $\epsilon_3$ as required by the bracketing number statement (Corollary~\ref{cor:convexadditive_lp}).
 Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.
@@
 |\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
-   \frac{s^{6/5} B^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
+   \frac{s^{6/5} (Bc_u)^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
   c sB \sigma \sqrt{ 
-   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   \frac{s (sBc_u)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
 \]
@@
    &\leq c sB \sigma \sqrt{ 
-   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   \frac{s (sBc_u)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
    + \lambda 2 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq c sB \sigma \sqrt{ 
-   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
+   &\leq c B^2 \sigma \sqrt{ 
+   \frac{s^4 c_u^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
    + \lambda 2 s B \nonumber\\   
-   &\leq c B \sigma 
-    \sqrt{ \frac{s^4 B^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
+   &\leq c B^2 \sigma 
+    \sqrt{ \frac{s^4 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
 \label{eqn:second_step_inequality}
@@
    &\leq cB^2 \sigma 
-    \sqrt{ \frac{s^4}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
- +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
+    \sqrt{ \frac{s^4c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
+ +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
 \end{align}
-Substituting in $\lambda \leq 512 s \tilde{\sigma} \sqrt{\frac{1}{n}
+Substituting in $\lambda \leq 768 s \tilde{\sigma} \sqrt{\frac{1}{n}
   \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
@@
 Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
-step with $\lambda_n \leq 512 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
+step with $\lambda_n \leq 768 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
 Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
@@
 \label{lem:uniform_convergence}
-Suppose $n \geq c_1 s\sqrt{sB}$ for some absolute constant $c_1$. Then, with probability at least $1-\delta$:
+Let $P$ be a distribution with a density $p(\mathbf{x})$ which is upper bounded by $c_u \geq 1$.
+Suppose $n \geq c_1 s\sqrt{sB}$ for some absolute constant $c_1$.
+Let $\delta$ be small enough such that $\log \frac{2}{\delta} \geq 2$.
+Then, with probability at least $1-\delta$:
 \begin{align*}
 \sup_{f \in \mathcal{C}^s_B} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
-   c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
-\end{align*}
-where $c_1$ is some absolute constant and $c,C$ are constants possibly dependent on $b$.
+   c B^3 \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
+\end{align*}
+where $c_1, c$ are some absolute constants.
 \end{lemma}
@@
 \begin{proof}
-Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$.
-Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.
+Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_B - f_0$.
+Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 2 s B$.
 There exists an $\epsilon$-bracketing of $\mathcal{G}$, and
-%For every $h \in \mathcal{G}$, there exists $h^L$ in the bracketing such that $\| h^U - h^L \|_{L_1(P)} \leq \epsilon$. 
-by Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sB}{\epsilon} \right)^{1/2}$.
-By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.
-Corollary~\ref{cor:convexbracket_ln} necessitates $\epsilon \in (0, sB\epsilon_3]$ for some absolute constant $\epsilon_3$; we will verify that this condition holds for large enough $n$ when we set the actual value of $\epsilon$.
-For a particular function $h \in \mathcal{G}$, we can construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
+by Corollary~\ref{cor:convexadditive_lp}, the bracketing has log-size at most $\log N_{[]}(\epsilon, \mathcal{C}^s_B, L_1(P)) \leq s K^{**}\left( \frac{4sBc_u}{\epsilon} \right)^{1/2}$ for all $\epsilon < \epsilon_3 s B c_u$, for some constant $\epsilon_3$.
+%By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = 2sB \sqrt{ \frac{K^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{\epsilon^{1/2} n}}$.
+Corollary~\ref{cor:convexbracket_ln} necessitates $\epsilon \in (0, sB\epsilon_3c_u]$ for some absolute constant $\epsilon_3$; we will verify that this condition holds for large enough $n$ when we set the actual value of $\epsilon$.
+
+For a particular function $h \in \mathcal{G}$, there exist an $\epsilon$-bracket $h_U, h_L$. We construct $\psi_L \equiv \min( |h_U|, |h_L|)$ and $\psi_U \equiv \max( |h_U|, |h_L| )$ so that
 \[
@@
 \]
+
+If $x$ is such that $h^2_U(x) \geq h^2_L(x)$, then $\psi_U^2(x) - \psi_L^2(x) = h^2_U(x) - h^2_L(x)$.
+If $x$ is such that $h^2_U(x) \leq h^2_L(x)$, then $\psi_U^2(x) - \psi_L^2(x) = h^2_L(x) - h_U^2(x)$.
 We can then bound the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ as
 \begin{align*}
-\int (\psi_U^2(x) - \psi_L^2(x)) p(x)dx  &\leq  \int | h_U^2(x) - h_L^2(x)| p(x) dx \\
+\int (\psi_U^2(x) - \psi_L^2(x)) p(x)dx  &=  \int | h_U^2(x) - h_L^2(x)| p(x) dx \\
    &\leq \int | h_U(x) - h_L(x) | \, |h_U(x) + h_L(x)| p(x) dx \\
-   &\leq 2sB \epsilon
+   &\leq 4sB \epsilon
 \end{align*}
@@
 $\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with
-upper bound $(sB)^2$, Hoeffding's inequality and union bound give that,
+upper bound $(2sB)^2$, Hoeffding's inequality and union bound give that,
 with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$)
-\[
+\begin{align*}
 \left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
-   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
-\]
+   \E \psi_L(X)^2 \right| &\leq (2sB)^2 \sqrt{ \frac{sK^{**} (4sBc_u)^{1/2}}{\epsilon^{1/2}2n} + \frac{\log\frac{2}{\delta}}{2n}} 
+\end{align*}
+To simplify the expression, we will suppose that $\frac{sK^{**} (4sBc_u)^{1/2}}{\epsilon^{1/2}} \geq 2$ and that $\log \frac{2}{\delta} \geq 2$.
+The second supposition holds by assumption in the theorem.
+Once we calculate the proper values of $\epsilon$, we will verify that these first supposition holds under the assumption of the theorem also.
+Under these two suppositions, we have
+\begin{align}
+\label{eqn:simplified_psi_concentration}
+\left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
+   \E \psi_L(X)^2 \right| &\leq (2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
+\end{align}
 
@@
 & \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
+(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
  & \leq 
@@
 \E \psi_U(X)^2 - \E \psi_L(X)^2 + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
-\end{align*}
-Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have
-\begin{align*}
--sB\epsilon - 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
+(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
+\end{align*}
+Using our bound on the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$, we have
+\begin{align*}
+-4sB\epsilon - 
+(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
  \| h \|_n^2 - \| h \|_P^2 \leq
-sB\epsilon + 
-(sB)^2 \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
-\end{align*}
-
-We balance the terms by choosing $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sB)^{1/2}}{n} \right)^{2/5}$.
-One can easily verify that $\epsilon \leq sB \epsilon_3$ condition needed by Corollary~\ref{cor:convexbracket_ln} is satisfied when $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$.
+4sB\epsilon + 
+(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
+\end{align*}
+
+We choose $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBc_u)^{1/2}}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our result.
+
+One can easily verify that $\epsilon \leq sB \epsilon_3 c_u$ when $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, thus, the $\epsilon$-bracketing number we used is valid.
+
+One can also verify that the condition above equation~\ref{eqn:simplified_psi_concentration} is satisfied.
+
 We have then that, with probability at least $1-\delta$,
@@
 \sup_{h \in \mathcal{G}} \big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
-  c B^3 \sqrt{ \frac{s^5 \log \frac{2}{\delta}}{n^{4/5}}}
+  c B^3 \sqrt{ \frac{s^5 c_u^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
 \end{align*}
@@
 
-Taking a union bound and we have that, with probability at least $1- 2\delta$, 
+We take a union bound and get that, with probability at least $1- 2\delta$, 
 \begin{align*}
@@
 
-A sub-exponential random is the square of a sub-Gaussian random
+A sub-exponential random variable is the square of a sub-Gaussian random
 variable \cite{vershynin2010introduction}.
@@
 Let $\mathcal{C}$ be a set of functions.
-For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define a \textit{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f^U \geq f \geq f^L$.
+For a given $\epsilon$ and metric $\rho$ (which we take to be $L_2$ or $L_2(P)$), we define an $\epsilon$-\textit{bracketing} of $\mathcal{C}$ to be a set of pairs of functions $\{ (f_L, f_U) \}$ satisfying (1) $\rho( f_L, f_U) \leq \epsilon$ and (2) for any $f \in \mathcal{C}$, there exist a pair $(f_L, f_U)$ where $f_U \geq f \geq f_L$.
 
@@
 \[
-\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2B}{\epsilon} \right)^{d/2}
+\log N_{[]} (\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{4B}{\epsilon} \right)^{d/2}
 \]
@@
 
-It is trivial to extend Kim and Samworth's result to the $L_2(P)$ norm for an absolutely continuous distribution $P$.
+It is easy to extend Kim and Samworth's result to the $L_1(P)$ norm for a distribution $P$ with a bounded density $p(x)$.
 
@@
 \label{prop:convexbracket_lp}
-Let $P$ be a distribution with a density $p$. Let $\mathcal{C}, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
-\[
-\log N_{[]} (2\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{2B}{\epsilon} \right)^{d/2}
-\]
-for all $\epsilon \in (0, B\epsilon_3]$.
+Let $P$ be a distribution with a density $p(x)$ and suppose $p(x) \leq c_u$ for some constant $c_u >0$.
+Let $\mathcal{C}, B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}.
+Then,
+\[
+\log N_{[]} (\epsilon, \mathcal{C}, L_1(P)) \leq K^{**} \left( \frac{4Bc_u}{\epsilon} \right)^{d/2}
+\]
+for all $\epsilon \in (0, B\epsilon_3 c_u]$.
 \end{proposition}
@@
 \begin{proof}
-Let $\mathcal{C}_\epsilon$ be the bracketing the satisfies the size bound in Proposition~\ref{prop:convexbracket_lp}.
-
-Let $(f_L, f_U) \in \mathcal{C}_\epsilon$. Then we have that:
+Let $\mathcal{C}_{\epsilon/c_u}$ be an $\epsilon/c_u$-bracketing with respect to the $L_2$ norm.
+Because $\epsilon \in (0, B \epsilon_3 c_u]$, it is clear that $\epsilon/c_u \in (0, B\epsilon]$.
+Then, the log-size of $\mathcal{C}_{\epsilon/c_u}$ is at most $K^{**} \left( \frac{4Bc_u}{\epsilon} \right)^{d/2}$ by Proposition~\ref{prop:convexbracket_lp}.
+
+Let $(f_L, f_U) \in \mathcal{C}_{\epsilon/c_u}$. Then we have that:
 \begin{align*}
@@
       \left( \int p(x)^2 dx \right)^{1/2} \\
-  &\leq \left( \int | f_L(x) - f_U(x)|^2 dx \right)^{1/2}\\
- &\leq \| f_L - f_U \|_{L_2} \leq \epsilon.
-\end{align*}
-On the third line, we used the fact that $\int p(x)^2 dx \leq \left( \int p(x) dx \right)^2 \leq 1$.
+  &\leq \left( \int | f_L(x) - f_U(x)|^2 dx \right)^{1/2} c_u\\
+ &\leq \| f_L - f_U \|_{L_2} c_u \leq \epsilon
+\end{align*}
+On the third line, we used the fact that $\left( \int p(x)^2 dx \right)^2 \leq c_u$.
 \end{proof}
 
-It is also simple to extend the bracketing number result to additive convex functions. As before, let $\mathcal{C}^s$ be the set of additive convex functions with $s$ components.
+It is also simple to extend the bracketing number result to additive convex functions.
+As before, let $\mathcal{C}^s_B$ be the set of additive convex functions with $s$ components, each component of which is bounded by $B$.
 
@@
 \label{cor:convexadditive_lp}
-Let $P$ be a distribution with a density $p$. Let $B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
-\[
-\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**} 
-    \left( \frac{2sB}{\epsilon} \right)^{1/2}
-\]
-for all $\epsilon \in (0, s B \epsilon_3]$.
+Let $P$ be a distribution with a density $p(x)$ and suppose $p(x) \leq c_u$. Let $B, \epsilon_3, K^{**}$ be defined as in Proposition~\ref{prop:convexbracket}. Then,
+\[
+\log N_{[]}(\epsilon, \mathcal{C}^s_B, L_1(P)) \leq s K^{**} 
+    \left( \frac{4sBc_u}{\epsilon} \right)^{1/2}
+\]
+for all $\epsilon \in (0, s B \epsilon_3c_u]$.
 \end{corollary}
@@
 \begin{proof}
-Let $f \in \mathcal{C}^s$. We can construct an $\epsilon$-bracketing for $f$ through $\epsilon/s$-bracketings for each of the components $\{ f_k \}_{k=1,...,s}$:
+Let $f \in \mathcal{C}^s$. We can construct an $\epsilon$-bracketing for $f$ through $\epsilon/s$-bracketings (with respect to the $L_1(P)$ norm) for each of the components $\{ f_k \}_{k=1,...,s}$:
 \[f_U = \sum_{k=1}^s f_{Uk}  \qquad f_L = \sum_{k=1}^s f_{Lk} \]
@@
 \label{cor:convexbracket_ln}
-Let $X_1,...,X_n$ be random samples from a distribution $P$.
+Let $X_1,...,X_n$ be random samples from a distribution $P$ and suppose $P$ has a density $p(x)$ bounded by $c_u$.
 Let $1 > \delta > 0$.
-Let $\mathcal{C}^s_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}^s$ with respect to the $L_1(P)$-norm whose size is at most $N_{[]}( 2\epsilon, \mathcal{C}^s, L_1(P))$.
-Let $\epsilon \in (0, s B \epsilon_3]$.
+Let $\mathcal{C}^s_\epsilon$ be an $\epsilon$-bracketing of $\mathcal{C}^s_B$ with respect to the $L_1(P)$-norm whose size is at most $N_{[]}(\epsilon, \mathcal{C}^s, L_1(P))$.
+Let $\epsilon \in (0, s B \epsilon_3c_u]$.
 
@@
 $$\epsilon_{n,\delta} \equiv 
-sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} 
-= \sqrt{ \frac{ sK^{**}(sB)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}.$$
+2sB \sqrt{ \frac{ \log N_{[]}(\epsilon, \mathcal{C}^s, L_1(P)) + \log \frac{2}{\delta}}{2n}} 
+= 2sB \sqrt{ \frac{ sK^{**}(4sBc_u)^{1/2}}{\epsilon^{1/2} 2n} + \frac{1}{2n} \log \frac{2}{\delta}}.$$
 \end{corollary}
@@
 \begin{proof}
-Noting that $|f_L(X_i) - f_U(X_i)|$ is at most $sB$ and there are
-$N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$, the
+Noting that $|f_L(X_i) - f_U(X_i)|$ is at most $2sB$ and that there are at most 
+$N_{[]}(\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$, the
 inequality follows from a direct application of a union bound and Hoeffding's Inequality.
@@
 \begin{align}
-\epsilon^{1/2} \leq 2sK^{**} (sB)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2 \label{cond:simplify_covering_number}.
+\frac{ sK^{**} (4sBc_u)^{1/2}}{\epsilon^{1/2}} \geq 2 \quad \trm{and} \quad \log \frac{2}{\delta} \geq 2 \label{cond:simplify_covering_number}.
 \end{align}
@@
 \begin{align*}
-\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sB)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}.
+\epsilon_{n,\delta} \leq 2sB \sqrt{ \frac{ sK^{**} (4 sBc_u)^{1/2} \log \frac{2}{\delta}}{2\epsilon^{1/2}n}} = 2sB \sqrt{ \frac{sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{\epsilon^{1/2} n}}
 \end{align*}

### 2015-04-28 tex/scam/reviews-v1/response-v1.tex
rev2

@@
 
+\item \reviewercomment{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
+write $g_k(X_k)$ in the sum instead of $g_k$.}
+
+\item \reviewercomment{On page 9, in the proof of Lemma 3.1, the star has been forgotten
+twice on $f_{k'}$ in (3.2) and (3.7).}
+
+\item \reviewercomment{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
+− \E f(X)$ is unique'', the term $−\sum_{k'\neq k} f_{k'}(X_{k'})$ has been forgotten.}
+
+\item \reviewercomment{On page 10, on line 14, ``In particular, if $F$ is the uniform
+distribution etc'', the term $− \int f$ has been forgotten.}
+
+\item \reviewercomment{On page 10, on line 16, ``additively'' should be replaced by
+``additive''.}
+
+\item \reviewercomment{On page 11, at the bottom of the page, ``before we presenting''}
+
+\item \reviewercomment{On page 11, after Deônition 3.2, it is written ``when the joint
+density satisfies the property that
+$\frac{\partial(x_{-j},x_j)}{\partial x_j} = \frac{\partial^2 p(x_{-j},
+  x_j)}{\partial x_j^2} = 0$ at boundary points''.
+I think the condition ``$p(x_{−j}, x_j ) = 0$ at the boundary points'' is
+missing.}
+
+\item \reviewercomment{On page 12, I did not understand why the functions 
+$\frac{\partial^2 p(x_{-j} |  x_j)}{\partial x_j^2}$
+and and 
+$\frac{\partial^2 f(x_{-j} |  x_j)}{\partial x_j^2}$
+are bounded (they are not supposed to be continuous)}
+
+\item \reviewercomment{On page 13, on line 6, ``this this''.}
+
 \end{enumerate}

### 2015-04-28 tex/scam/reviews-v1/response-v1.tex
a

@@
 $\frac{\partial^2 p(x_{-j} |  x_j)}{\partial x_j^2}$
-and and 
+and adn 
 $\frac{\partial^2 f(x_{-j} |  x_j)}{\partial x_j^2}$
@@
 \item \reviewercomment{On page 13, on line 6, ``this this''.}
+
+\item \reviewercomment{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
+is not speciôed that $Var(X_1) = 1$.}
+\item \reviewercomment{On page 13, on line 29, ``additive'' should be replaced by
+``additively''.}
+\item \reviewercomment{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
+parameter $\mu$ should be introduced as before.}
+\item \reviewercomment{On page 16, in the expresson of $c^∗$, the
+  denominator should be $\E X_k^2 −m_k^2$.}
+\item \reviewercomment{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
+lemma supposes that $\phi$ is continuous. Here I do not see why $\phi =
+\sum_{k'\neq k} f_{k'}*$ is continuous (it is convex then continuous on the interior of
+$[0,1]^p$. ).}
+\item \reviewercomment{On page 17, same problem as before with the absence of parameter $\mu$.}
+\item \reviewercomment{On page 17, on line 16 ``for that variable. for each''}
+\item \reviewercomment{On page 18, at the bottom of the page :
+  ``$\beta_{\pi_k(i+1)k} 
+\geq \beta_{\pi_k(i)k}$ for $i=1,\ldots, n-1$'' , $n−1$ must be replaced by $n−2$.}
+\item \reviewercomment{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
+  f_{ki}$.}
+\item \reviewercomment{On page 20, in the third paragraph, on the second, third and fourth
+lines, $j$ and $j − 1$ must be replaced by $j + 1$ and $j$ respectively in
+$x_{\pi_k(j)k}$ and $x_{\pi_k(j-1)k}$.}
 

### 2015-04-28 tex/scam/experiments.tex
various updates

@@
 \label{sec:thesims}
-%\subsection{Simulations}
+
+We perform both synthetic and real data experiments.
+
+\subsection{Simulations}
 We first illustrate our methods using a simulation of the model
@@
 
-%\begin{figure}[!htpb]
-%        \centering
-%        \begin{subfigure}[b]{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{figs/Curve1}
-%                 \caption{Additive model.}
-%                \label{Curve1}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{figs/Q}
-%                \caption{Four $\Q$ matrices.}
-%                \label{Q}
-%        \end{subfigure}\\
-%        \begin{subfigure}[b]{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{figs/Curve2}
-%                \caption{Additive and non-additive models.}
-%                \label{Curve2}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{figs/Curve3}
-%                \caption{Correlated design for non-additive model.}
-%                \label{Curve3}
-%        \end{subfigure}
-%        \caption{Result of support recovery.}\label{Support}
-%\end{figure}
+\begin{figure*}[!t]
+\begin{center}
+\begin{tabular}{cc}
+%\hskip-10pt
+\includegraphics[width=.42\textwidth]{figs/CurveT} &
+%\hskip-10pt
+\includegraphics[width=.42\textwidth]{figs/CurveR} \\
+(a) additive function & (b) non-additive function \\
+%\hskip-10pt
+\includegraphics[width=.42\textwidth]{figs/Q} &
+%\hskip-10pt
+\includegraphics[width=.42\textwidth]{figs/CurveC}  \\
+(c) four $\Q$ matrices & (d) correlated design \\
+\includegraphics[width=.42\textwidth]{figs/C_support_box} & 
+\includegraphics[width=.42\textwidth]{figs/CurveS}\\
+(e) recovered support size & (f) nonparametric function
+\end{tabular}
+\end{center}
+\caption{Support recovery results where the additive assumption is
+  correct (a), incorrect (b), (c), and with correlated design (d).}\label{Support}
+\vskip10pt
+\end{figure*}
 
-%\begin{figure}[ht]
-%\begin{center}
-%\begin{tabular}{cccc}
-%\hskip-20pt
-%\includegraphics[width=.27\textwidth]{figs/Curve1} &
-%\hskip-17pt
-%\includegraphics[width=.27\textwidth]{figs/Q} &
-%\hskip-17pt
-%\includegraphics[width=.27\textwidth]{figs/Curve2} &
-%\hskip-17pt
-%\includegraphics[width=.27\textwidth]{figs/Curve3}  \\
-%(a) additive model & (b) four $\Q$ matrices &
-%(c) non-additive models & (d) correlated design
-%\end{tabular}
-%\end{center}
-%\caption{Result of support recovery.}\label{Support}
-%\end{figure}
-
-%\subsection{Boston housing data}
+\subsection{Boston housing data}
 
@@
 
-\begin{figure*}[!t]
-\begin{center}
-\begin{tabular}{cccc}
-\hskip-10pt
-\includegraphics[width=.26\textwidth]{figs/Curve1} &
-\hskip-10pt
-\includegraphics[width=.26\textwidth]{figs/Q} &
-\hskip-10pt
-\includegraphics[width=.26\textwidth]{figs/Curve2} &
-\hskip-10pt
-\includegraphics[width=.26\textwidth]{figs/Curve4}  \\
-\hskip-10pt (a) additive model & 
-\hskip-10pt (b) four $\Q$ matrices &
-\hskip-10pt (c) non-additive models & 
-\hskip-10pt (d) correlated design
-\end{tabular}
-\end{center}
-\caption{Support recovery results where the additive assumption is
-  correct (a), incorrect (b), (c), and with correlated design (d).}\label{Support}
-\vskip10pt
-
+\begin{figure*}
 \begin{center}

### 2015-04-28 code/paper_exp/C.m

@@ -96,31 +96,43 @@ return
 
 
 %% Reading the result:
-clc; clear all; close all; 
+%clc; clear all; close all; 
+num_versions = 28;
 prob = zeros(1,num_versions); 
+supp = zeros(nrun, num_versions);
+
+success_supp = 20;
+
 epsil = 1e-6;
+
 for version = 1:num_versions
-    load(['C_' num2str(version) '.mat']);
+    load(['mat/C_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 
     for run = 1:nrun
-        if min(Ln(J(:,run), run)) > epsil && ...
-           sum(Ln(:,run) > epsil) < 11
+        cur_supp = sum(Ln(:,run) > 1e-5);
+        if min(Ln(J(:,run),run)) > epsil && ...
+            cur_supp < success_supp
             suc = suc + 1;
         end
+        supp(run,version) = cur_supp;
     end
     prob(version) = suc/nrun;
 end
 
+
+samples = 200:200:1400;
+
 % much of the figures still need to be edited
+figure(2); set(gca,'FontSize',14); 
+plot(samples,prob(1:7),'r.-',...
+     samples,prob(8:14),'b.-',...
+     samples,prob(15:21),'g.-',...
+     samples,prob(22:28),'k.-','LineWidth',2);
 
-figure(2); set(gca,'FontSize',12); 
-plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
-    100:100:1000,prob(21:30),'g.-',100:100:1000,prob(31:40),'k.-','LineWidth',2);
-
-legend('v=0.0','v=0.2','v=0.5','v=0.9');
+legend('v=0.0','v=0.2','v=0.5','v=0.9','Location','SouthEast');
 xlabel('Number of Samples'); 
-ylabel('Probability of Recovery');
-title('Probability of Recovery');
+ylabel('Probability of Screening');
+title('Probability of Screening');
 %set(gca, 'LooseInset', get(gca, 'TightInset'));
 
 tightInset = get(gca, 'TightInset');
@@ -139,4 +151,40 @@ set(gcf, 'PaperPositionMode', 'manual');
 set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
 
 h = gcf;
[…]

### 2015-04-28 code/paper_exp/K.m

@@ -1,4 +1,4 @@
-function S(version)
+function K(version)
 % p changes
 % softmax of affine with noise.
 % Correlated
@@ -12,39 +12,31 @@ clc;
 addpath('../simdata', '-end')
 
 switch version
-    case 01, n = 200; p = 128;
-    case 02, n = 500; p = 128;
-    case 03, n = 800; p = 128;
-    case 04, n = 1100; p = 128;
-    case 05, n = 1500; p = 128;
-    case 06, n = 2000; p = 128;
+    case 01, s = 2; p = 128;
+    case 02, s = 4; p = 128;
+    case 03, s = 8; p = 128;
+    case 04, s = 12; p = 128;
+    case 05, s = 16; p = 128;
         
-    case 07, n = 200; p = 256;
-    case 08, n = 500; p = 256;
-    case 09, n = 800; p = 256;
-    case 10, n = 1100; p = 256;
-    case 11, n = 1500; p = 256;
-    case 12, n = 2000; p = 256;
-        
-    case 13, n = 200; p = 512;
-    case 14, n = 500; p = 512;
-    case 15, n = 800; p = 512;
-    case 16, n = 1100; p = 512;
-    case 17, n = 1500; p = 512;
-    case 18, n = 2000; p = 512;
-        
+    case 06, s = 2; p = 256;
+    case 07, s = 4; p = 256;
+    case 08, s = 8; p = 256;
+    case 09, s = 12; p = 256;
+    case 010, s = 16; p = 256;
+
     otherwise, return
 end
 
-v = 0.5;
-k = 5; 
+n = 600;
+v = 0.2;
+k = s;
 K = 7;
 lambda = 0.5*sqrt(1/n)*log(n*p); % MODIFY
 SNR = 5;
 
 maxit = 20; tol = 10^-6;
 
-nrun = 15; % MODIFY
+nrun = 50; % MODIFY
 
 J = ones(p,nrun)==0; Ln = zeros(p,nrun); 
 
@@ -72,12 +64,12 @@ for run = 1:nrun
     
     epsil = 1e-6;
     succ1 = min(Ln(J(:,run),run)) > epsil
-    succ2 = sum(Ln(:,run) > epsil) < 11
+    succ2 = sum(Ln(:,run) > epsil) < 2*s
     
     
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
[…]

### 2015-04-28 code/paper_exp/R.m

@@ -122,7 +122,7 @@ end
 
 prob = zeros(1,40); epsil = 10^-6;
 for version = 1:40
-    load(['R_' num2str(version) '.mat']);
+    load(['mat/R_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0;
     for run = 1:nrun
         if max(Ln(~J(:,run),run)) < epsil && min(Ln(J(:,run),run)) > epsil
@@ -131,11 +131,11 @@ for version = 1:40
     end
     prob(version) = suc/nrun;
 end
-figure(2); set(gca,'FontSize',12); 
+figure(2); set(gca,'FontSize',14); 
 plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
     100:100:1000,prob(21:30),'g.-',100:100:1000,prob(31:40),'k.-','LineWidth',2);
 
-legend('\alpha=0.0','\alpha=0.2','\alpha=0.5','\alpha=1.0');
+legend('\alpha=0.0','\alpha=0.2','\alpha=0.5','\alpha=1.0','Location','SouthEast');
 xlabel('Number of samples'); 
 ylabel('Probability of recovery');
 title('Probability of support recovery');
@@ -157,4 +157,6 @@ set(gcf, 'PaperPositionMode', 'manual');
 set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
 
 h = gcf;
-saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/Curve2.pdf')
+saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/CurveR.pdf')
+
+

### 2015-04-28 code/paper_exp/T.m

@@ -83,14 +83,14 @@ for run = 1:nrun
     Ln(:,run) = max(Lnvex, Lncave);
     disp(['version=' num2str(version) ' run=' num2str(run)]);
 end
-save(['T_' num2str(version) '.mat'],'J','Ln');
+save(['mat/T_' num2str(version) '.mat'],'J','Ln');
 return
 
 %% Reading the result:
 clc; clear all; close all; 
 prob = zeros(1,40); epsil = 10^-6;
 for version = 1:40
-    load(['T_' num2str(version) '.mat']);
+    load(['mat/T_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 
     for run = 1:nrun
         if max(Ln(~J(:,run),run)) < epsil && min(Ln(J(:,run),run)) > epsil
@@ -100,10 +100,10 @@ for version = 1:40
     prob(version) = suc/nrun;
 end
 
-figure(2); set(gca,'FontSize',12); 
+figure(2); set(gca,'FontSize',14); 
 plot(100:100:1000,prob(1:10),'r.-',100:100:1000,prob(11:20),'b.-',...
     100:100:1000,prob(21:30),'g.-',100:100:1000,prob(31:40),'k.-','LineWidth',2);
-legend('p=64','p=128','p=256','p=512');
+legend('p=64','p=128','p=256','p=512','Location','SouthEast');
 xlabel('Number of Samples'); 
 ylabel('Probability of Recovery');
 title('Probability of Recovery');
@@ -125,4 +125,6 @@ set(gcf, 'PaperPositionMode', 'manual');
 set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
 
 h = gcf;
-saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/Curve1.pdf')
+saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/CurveT.pdf')
+
+

### 2015-04-28 code/simdata/simulateBoundedGaussCopula.m

@@ -5,9 +5,7 @@
 % OUTPUT: 
 %       X should be (p--by--n)
 %
-% mixture of uniform [-2, 2] and max-divided Gaussian
-% Gaussian is truncated at 2.4
-% then divided by maximum to sit between [-2.7, 2.7]
+% mixture of uniform [-2, 2] of Gaussian copula
 
 function [X] = simulateBoundedGaussCopula(p, n, unif_weight, Sigma)
 

### 2015-04-28 tex/scam/experiments.tex
new plots

@@
 \begin{equation}\nonumber
-         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
+         Y_i = f_o(\x_{iS}) + \epsilon_i \quad (i=1,2,\ldots,n).
 \end{equation}
-Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0}, \Sigma)$, 
-$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
+Here $\x_{i}$ denotes data sample $i$ drawn from some distribution $P$. 
+$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=s$, where $S$
 represents the set of relevant variables, and 
-$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
+$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,\sigma)$. For 
+all simulations, we set $\sigma$ such that the signal-to-noise ratio(SNR, $\frac{\trm{std}(Y)}{\sigma}$) is 5; we
+set $\lambda = \frac{1}{2} \sqrt{ \frac{\log^2(np)}{n} }$.
+
+For the first three simulations, we will use the quadratic form as our true regression function.
+\[
+f_0(x_{iS}) = x_{iS}^\tran \Q x_{iS}
+\]
+
 The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
@@
 otherwise the true function is convex but not additive.
-For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.
 
-In the first simulation, we vary the ambient dimension $p$.
+In the \textbf{first simulation}, we vary the ambient dimension $p$.
 We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
-We use independent design by setting $\Sigma = \textrm{I}_p$.
+We use independent $X$ and draw $X \sim N(0, I_p)$.
 For each $(n,p)$ combination, we generate $100$ independent data
@@
 We plot the probability of exact
-support recovery over the $100$ data sets in Figure \ref{Support}(a).  We
+support recovery over the $100$ independent trials in Figure \ref{Support}(a).  We
 observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
@@
 
-In the second simulation, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
-plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
+In the \textbf{second simulation}, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
+plotted in Figure \ref{Support}(c), where the diagonal elements are all one and
 the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
-($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We use independent design by setting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
-independently generated data sets and plot the probability of recovery
-in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
+($\alpha=0,0.2,0.5,1$ for the four cases). We show the 4 $\Q$ matrices we used in Figure~\ref{Support}(c).
+We fix $p=128$ and choose
+$n=100,200,\ldots,1000$. We use $X \sim N(0,I_p)$. We again run the AC/DC optimization on $100$
+independent trials and plot the probability of recovery
+in Figure \ref{Support}(b). The results demonstrate that AC/DC performs
 consistent variable selection even if the true function is not additive (but
@@
 
-In the third simulation, we use correlated design and vary the correlation. We let
-$\x_i$ be drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
-instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
-$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$, same as in the second experiment, with $\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
-0.6, 0.8$ are shown in Figure \ref{Support}(d). As can be seen, for
-design of moderate correlation, AC/DC can still select relevant
-variables well.
+In the third, fourth, and fifth simulations, we use correlated design and vary the correlation.
+We generate $X$ from a non-Gaussian correlated boundary flat distribution.
+The distribution we used is a mixture of a uniform distribution and a Gaussian Copula.
+\[
+X \sim \gamma U([-2, 2]^p) + (1-\gamma) \trm{Copula}(0, \Sigma, F)
+\]
+Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the covariance structure.
+Gaussian Copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each variable of Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new desired marginal distribution.
+In all our experiments, we set $\gamma = 0.05$ and set the marginal CDF $F$ so that marginal density of the Copula is bimodal and supported on $[-1.8, 1.8]$.
+The marginal density of the mixture is shown in Figure~\ref{fig:copula_marginal}.
+Notice that boundary flatness holds because the distribution is uniform in the boundary area $[-2,2]^p \backslash [-1.8, 1.8]^p$.
+
+\begin{figure*}
+\includegraphics[width=.4\textwidth]{figs/copula_marginal}
+\caption{Marginal density of the Gaussian Copula and Uniform Mixture}
+\label{fig:copula_marginal}
+\end{figure*}
+
+In the \textbf{third experiment}, we set $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
+We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128$.
+We measure success not through exact recovery but through approximate recovery.
+We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall.
+The probabilities of success are computed from 40 independent trials and plotted against various values of $\nu$ in Figure~\ref{Support}(d).
+Additionally, for $\nu = 0.5$, we show the number of selected variables versus the sample size as a Box-and-Whisker plot in Figure~\ref{Support}(e).
+As can be seen, AC/DC can successfully recover the relevant variables with only a small number of false positives.
+
+In the fourth, fifth, and sixth simulation, we use a softmax regression function
+\[
+f_0(x_{iS}) = \log \left( \sum_{k=1}^K \exp( \beta_k^\tran x_{iS} ) \right) - \mu
+\]
+where $\{\beta_k \in \R^s\}_{k=1,...,K}$ are random unit vectors. $\mu$ is chosen so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
+
+For the \textbf{fourth experiment}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution described earlier with correlation level $\nu = 0.5$.
+We use the same approximate recovery success criteria as the third experiment and plot probability of approximate recovery against the number of samples for $p=128, 256, 512$.
+The probabilities are computed over 30 independent trials.
+
+For the \textbf{fifth experiment}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with correlation level $\nu = 0.2$.
+
+For the \textbf{sixth experiment}, we compare the variables selected via the AC stage and the variables selected via the DC stage.
+We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with correlation level $\nu = -0.7$.
+We set $n=500, p=128$.
+We perform 30 independent trials and plot the frequency of variable selection in Figure~\ref{fig:ac_v_dc}.
+The true variables are $X_j$ for $j=5,6,7,8,9,10$.
+We plot the frequency of selection among only the first 20 variables, that is, $X_j$ for $j=1,...,20$.
+We do not plot selection frequencies for variables 21 to 128 because they are almost never selected by either AC or DC.
+As can be seen, the DC stage is slightly helpful in recovering the true variables but its effect is not significant.
+We thus believe that the DC stage, though important in theory, is not as important in practice; it may be omitted without significant detriment to the overall result.
 
@@
 \includegraphics[width=.42\textwidth]{figs/CurveR} \\
-(a) additive function & (b) non-additive function \\
+(a) quadratic $f_0$, independent $X$, varying $p$  & (b) quadratic $f_0$, independent $X$, varying $\Q$ \\
 %\hskip-10pt
@@
 \includegraphics[width=.42\textwidth]{figs/CurveC}  \\
-(c) four $\Q$ matrices & (d) correlated design \\
+(c) four $\Q$ matrices used in (b) & (d) quadratic $f_0$, correlated $X$, varying correlation $\nu$ \\
 \includegraphics[width=.42\textwidth]{figs/C_support_box} & 
 \includegraphics[width=.42\textwidth]{figs/CurveS}\\
-(e) recovered support size & (f) nonparametric function
+(e) recovered support size for $\nu=0.5$ in (d) & (f) softmax $f_0$, correlated $X$, varying $p$ \\
+\includegraphics[width=0.42\textwidth]{figs/S_support_box} & \\
+(g) recovered support size for $p=256$ in (f) & (h) softmax $f_0$, correlated $X$, varying $s$ 
 \end{tabular}
@@
 \vskip10pt
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.5\textwidth]{figs/ACvDC}
+\caption{Frequency of variable selection among the first 20 variables ($X_j$ for $j=1,...,20$) in the AC stage vs. in the DC stage. The true variables are [5,6,7,8,9,10].}
+\label{fig:ac_v_dc}
 \end{figure*}

### 2015-04-28 tex/scam/reviews-v1/response-v1.tex
added some response

@@
 
-We have made these revisions.
+The boundary flatness condition does not artificially make the variable selection problem easy.
+Comminges and Dalalyan showed that variable selection for general two-smooth functions is difficult even if the underlying distribution is a product distribution, and boundary flat distributions are much more general than product distributions.
 
@@
 
+If the true regression function is a convex additive function, then additive faithfulness holds trivially--the best additive approximation to an additive function is the function itself.
+The estimation procedure becomes simpler--the DC stage is no longer necessary and can be safely removed.
+
+In the finite sample analysis, the assumptions would not change except that A3 would be $\| f^*_k \|_\infty \leq B$ for all $k$ since $f_0 = f^*$ in this case.
+The signal strength definition can be made simpler: $\alpha^+ = \min_k \mathbb{E}( f^*_k(X_k)^2 )$.
+The rates would not improve.
+
 \item \reviewercomment{If we actually wish to fit smooth convex univariate components, is
@@
 it into the analysis?}
+
+Smoothness can be incorporated by using B-spline basis with uniformly spaced knots.
+The details are described in a paper by Pya and Wood which we cited.
+We chose not to discuss estimating smooth convex functions because it would introduce an additional tuning parameter, which negates some of the advantages of doing shape-constrained estimation.
 
@@
 
+We consider only densities with support in a hypercube.
+We have modified old experiments and added new experiments to use boundary flat distributions instead of the correlated multivariate Gaussian distribution.
+
 \end{enumerate}

### 2015-04-29 tex/scam/reviews-v1/response-v1.tex
a

@@
 \definecolor{blue}{rgb}{0.01,0.01,0.75}
-\def\reviewercomment#1{{\it\textcolor{blue}{#1}}\smallskip}
+\def\rc#1{{\it\textcolor{blue}{#1}}\smallskip}
 \parindent0pt
@@
 
-\reviewercomment{Below I recapitulate a few
+\rc{Below I recapitulate a few
 point of the reviewers', along with some questions/comments of my own.
@@
 \begin{enumerate}
-\item \reviewercomment{Boundary flatness condition: much of the paper's analysis hinges on
+\item \rc{Boundary flatness condition: much of the paper's analysis hinges on
 this condition.  Reviewer 3 raises some concerns about when it holds,
@@
 
-\item \reviewercomment{Intuitively, variable selection is very closely related to
+\item \rc{Intuitively, variable selection is very closely related to
 estimating a function (or possibly its partial derivatives) in the
@@
 
-\item \reviewercomment{Writing and proofs need to be tidied up in places to make it easier
+\item \rc{Writing and proofs need to be tidied up in places to make it easier
 to follow.  See various comments of referees, particularly the
@@
 
-\reviewercomment{Conceptually, I have a few questions for the authors to address:}
+\rc{Conceptually, I have a few questions for the authors to address:}
 
 \begin{enumerate}[(1)]
-\item \reviewercomment{If the true regression function $f_0$ can actually be written as a
+\item \rc{If the true regression function $f_0$ can actually be written as a
 sum of univariate convex functions (plus noise), are there natural
@@
 
-\item \reviewercomment{If we actually wish to fit smooth convex univariate components, is
+\item \rc{If we actually wish to fit smooth convex univariate components, is
 it easy to add this condition as a regularization term and incorporate
@@
 
-\item \reviewercomment{Assuming model selection consistency, can one derive prediction
+\item \rc{Assuming model selection consistency, can one derive prediction
 error bounds using the fitted $f_k$'s and $g_k$'s, as well? Prediction error
@@
 
-\item \reviewercomment{In order to improve clarity, the authors should define the convex
+\item \rc{In order to improve clarity, the authors should define the convex
 additive model at the top of page 5: $f(x_i) = \sum_{k=1}^p f_k(x_{ik})$, where the
@@
 
-\item \reviewercomment{Another notational comment: the use of the
+\item \rc{Another notational comment: the use of the
 distribution function $F$ seems unnecessary (e.g., Lemma 3.1 and
@@
 
-\item \reviewercomment{I would suggest including the dependence on the positive-valued lower
+\item \rc{I would suggest including the dependence on the positive-valued lower
 bound on $p(x)$ (as assumed in (A5)) in the statement of Theorem 3. This
@@
 
-\item \reviewercomment{It would be good to point to Assumption (A3) at the beginning of
+\item \rc{It would be good to point to Assumption (A3) at the beginning of
 Section 5 when discussing the $B$-boundedness condition. In the third
@@
 
-\item \reviewercomment{At the top
+\item \rc{At the top
 of page 23, the remark regarding mutual incoherence conditions is a
@@
 
-\item \reviewercomment{In the simulation section, the authors might consider comparing the
+\item \rc{In the simulation section, the authors might consider comparing the
 set of variables selected after the AC step only with the set of
@@
 \begin{enumerate}[(i)]
-\item \reviewercomment{In Section 2.3, it would be good to actually state the regularized
+\item \rc{In Section 2.3, it would be good to actually state the regularized
 objective function being analyzed, rather than waiting until Section
 4.}
-\item \reviewercomment{Assumption (A3) on page 7 is missing the subscript $\infty$.}
-\item \reviewercomment{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
+\item \rc{Assumption (A3) on page 7 is missing the subscript $\infty$.}
+\item \rc{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
 it seems to be the sub-Gaussian parameter of the additive noise.}
-\item \reviewercomment{Perhaps Section 3 should be titled something other than ``Additive
+\item \rc{Perhaps Section 3 should be titled something other than ``Additive
 faithfulness'' (maybe ``Population- level results''?).}
-\item \reviewercomment{The first paragraph of Section 5 should read
+\item \rc{The first paragraph of Section 5 should read
   ``Figure 3'' rather than ``Algorithm 3.''}
 
-\item \reviewercomment{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
-\item \reviewercomment{The first sentence of Section 5.1 should read optimization (4.8).}
+\item \rc{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
+\item \rc{The first sentence of Section 5.1 should read optimization (4.8).}
 \end{enumerate}
@@
 
-\reviewercomment{I found many (unimportant) mistakes in the proofs (I
+\rc{I found many (unimportant) mistakes in the proofs (I
   did not mention them all in the minor comments), which need to be
@@
 \begin{enumerate}
-\item \reviewercomment{I have a problem with the assertion of
+\item \rc{I have a problem with the assertion of
   uniqueness in Lemma 3.1 and Therorem 3.2. First, in Lemma 3.1, it is
@@
    for a certain function $g$. Then if $(f_1^∗, f_2^∗)$ is a solution,
-   $(f_1^∗ + f_2^ \circ g, 0)$ is also a solution.}
+   $(f_1^∗ + f_2^* \circ g, 0)$ is also a solution.}
 
-\item \reviewercomment{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
+\item \rc{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
 write $g_k(X_k)$ in the sum instead of $g_k$.}
 
-\item \reviewercomment{On page 9, in the proof of Lemma 3.1, the star has been forgotten
+\item \rc{On page 9, in the proof of Lemma 3.1, the star has been forgotten
 twice on $f_{k'}$ in (3.2) and (3.7).}
 
-\item \reviewercomment{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
+\item \rc{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
 − \E f(X)$ is unique'', the term $−\sum_{k'\neq k} f_{k'}(X_{k'})$ has been forgotten.}
 
-\item \reviewercomment{On page 10, on line 14, ``In particular, if $F$ is the uniform
+\item \rc{On page 10, on line 14, ``In particular, if $F$ is the uniform
 distribution etc'', the term $− \int f$ has been forgotten.}
 
-\item \reviewercomment{On page 10, on line 16, ``additively'' should be replaced by
+\item \rc{On page 10, on line 16, ``additively'' should be replaced by
 ``additive''.}
 
-\item \reviewercomment{On page 11, at the bottom of the page, ``before we presenting''}
+\item \rc{On page 11, at the bottom of the page, ``before we presenting''}
 
-\item \reviewercomment{On page 11, after Deônition 3.2, it is written ``when the joint
+\item \rc{On page 11, after Deônition 3.2, it is written ``when the joint
 density satisfies the property that
@@
 
-\item \reviewercomment{On page 12, I did not understand why the functions 
+\item \rc{On page 12, I did not understand why the functions 
 $\frac{\partial^2 p(x_{-j} |  x_j)}{\partial x_j^2}$
@@
 
-\item \reviewercomment{On page 13, on line 6, ``this this''.}
+\item \rc{On page 13, on line 6, ``this this''.}
 
-\item \reviewercomment{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
+\item \rc{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
 is not speciôed that $Var(X_1) = 1$.}
-\item \reviewercomment{On page 13, on line 29, ``additive'' should be replaced by
+\item \rc{On page 13, on line 29, ``additive'' should be replaced by
 ``additively''.}
-\item \reviewercomment{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
+\item \rc{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
 parameter $\mu$ should be introduced as before.}
-\item \reviewercomment{On page 16, in the expresson of $c^∗$, the
+\item \rc{On page 16, in the expresson of $c^∗$, the
   denominator should be $\E X_k^2 −m_k^2$.}
-\item \reviewercomment{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
+\item \rc{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
 lemma supposes that $\phi$ is continuous. Here I do not see why $\phi =
@@
 $[0,1]^p$. ).}
-\item \reviewercomment{On page 17, same problem as before with the absence of parameter $\mu$.}
-\item \reviewercomment{On page 17, on line 16 ``for that variable. for each''}
-\item \reviewercomment{On page 18, at the bottom of the page :
+\item \rc{On page 17, same problem as before with the absence of parameter $\mu$.}
+\item \rc{On page 17, on line 16 ``for that variable. for each''}
+\item \rc{On page 18, at the bottom of the page :
   ``$\beta_{\pi_k(i+1)k} 
 \geq \beta_{\pi_k(i)k}$ for $i=1,\ldots, n-1$'' , $n−1$ must be replaced by $n−2$.}
-\item \reviewercomment{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
+\item \rc{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
   f_{ki}$.}
-\item \reviewercomment{On page 20, in the third paragraph, on the second, third and fourth
+\item \rc{On page 20, in the third paragraph, on the second, third and fourth
 lines, $j$ and $j − 1$ must be replaced by $j + 1$ and $j$ respectively in
 $x_{\pi_k(j)k}$ and $x_{\pi_k(j-1)k}$.}
+
+\item \rc{On page 20, In the central matrix equation, the
+  first vector should be
+  $\left[\begin{matrix}f_k(x_{1k}\\ f_k(x_{2k}\\ \vdots\\f_k(x_{nk}\end{matrix}\right]$. Next
+  in ``$\mu_k = -\frac{1}{n} 1_n^T \Delta_k d_k$``, $1_n$ is missing.}
+\item \rc{On page 21, in Section 5, at the end of the
+  second paragraph, ``$m\hat{}u$ from
+our estimation procedure''.}
+
+\item \rc{On page 22, in Deônition 5.1, the inequalities
+  about $d_k$ must be replaced by the same inequalities as in Proposition 4.1.}
+
+\item \rc{On page 22 (and on page 31), in the statement of Theorem
+  5.1, in\\ $\max_{i=1,\ldots, n} \frac{X_{k\pi_k(i+1)}-
+    X_{k\pi_k(i)}}{\text{range}_k} \geq \frac{1}{16}$ the
+sign $\geq$ must be replaced by $\leq$ . Besides I think it
+is a bad idea to change notation : $X_{k\pi_k(i)}$ should
+be replaced by $X_{\pi_k(i)k}$ as before (page 19 for instance).}
+
+\item \rc{On page 23, in equation (5.1), in ``$f^∗(X)$'', the star must be
+removed.}
+
+\item \rc{On page 24, ``$\alpha_{+} > 0$ since $f$ is the unique risk minimizer'' : I do
+not understand this statement (there is an infimum, not a minimum in
+the definition of $\alpha_{+}$.)}
+\item \rc{On page 24, in Remark 5.1, ``In important direction''.}
+\item \rc{On page 25, in the statement of Theorem 5.3, the square must be
+removed on $\alpha_-$.}
 
@@
 \begin{enumerate}
-\item \reviewercomment{The basis of all the results seem to be the boundary flatness
+\item \rc{The basis of all the results seem to be the boundary flatness
 condition. This condition seems to be an artifact of the analysis and
@@
 
-\item \reviewercomment{Following on from the previous point, the simulation study also does
+\item \rc{Following on from the previous point, the simulation study also does
 not add any further insight to this issue since the simulations are
@@
 \begin{enumerate}
-\item \reviewercomment{I didn't think there was any need for Section 2
+\item \rc{I didn't think there was any need for Section 2
   since it feels very repetitive and slightly confusing that parts of
@@
 
-\item \reviewercomment{Page 2, second last paragraph `and and.'}
+\item \rc{Page 2, second last paragraph `and and.'}
 \end{enumerate}

### 2015-04-29 tex/scam/reviews-v1/response-v1.tex
added rev 2

@@
 
+\item \rc{On page 25, after the statement of Corollary 5.1 : I do not understand
+why ``$p = O(exp(n^c)$'' is written instead of ``$p = O(exp(cn)$.}
+\item \rc{On page 26, in the first paragraph ``the relevant variable set'' and
+in the third paragraph, ``seting''.}
+\item \rc{I really did not understand what was represented in figures 5(a) and
+5(b) (axis?). Besides it does not seem to correspond with what is
+described at the bottom of page 26 and at the top of page 27. The
+notation $\|\cdot\|_{\infty,1}$ is not defined.}
+\item \rc{On page 31, at the top of the page, ``see discussion at beginning of
+Section 5'' : I think it should be ``at the beginning''. In (8.1),
+same problem as before with the indices : ``$\nu_{ki} d_{ki}$ `` must be replaced
+with ``$\nu_{ik}d_{ik}$'' (see for instance page 20). At the bottom of the page,
+$v_{ki}$ must be replaced by $\nu_{ki}$.}
+\item \rc{On page 32, on the first line of the second paragraph, ``$d_k = 0 \mbox{for $k
+\in S$}$'', $S$ must be replaced by $S^c$ and $\|\mu\|$ by $\|\mu\|_1$ and ``It clear
+that''. Next, the third paragraph (``to ease notational ....'') should
+be placed at the beginning of the proof (it is used from the beginning
+of the proof, cf conditions on $d_k$).}
+\item \rc{On page 33, I find that $[\lambda\Delta_k^Tu]_1 = \lambda((X_{kn} −X_{k1})\kappa$. ( If $\kappa$ is be defined
+in the following way : $\kappa =
+\frac{1}{\lambda_n(X_{kn}-X_{k1})}[\Delta_k^T u]_1$, then everything
+goes well).}
+
+\item \rc{On page 33, on the second line, ``other rows of stationarity
+condition holds'' and in the third paragraph : ``following our strategy, We''.}
+\item \rc{On page 34, at the bottom of the page, the parentheses in the
+denominator of the fraction.}
+\item \rc{On page 35, in the third paragraph, ``as a function of $\nu$'' : it is
+$\zeta$, not $\nu$. In the fourth paragraph, $\nu$ is not defined. In the fifth
+paragraph, in the equation, remove the sum $\sum_{k=1}^p
+\bar\Delta_k^T u_k$  and replace
+it by the vector ̄ˆ with componen$(\bar\Delta_k^T u_k)_{k=1,\ldots, p}$ In the sixth paragraph,
+in $\bar\Delta \hat d_k = \bar\Delta\hat d$ replace $\hat d_k$ by
+$\hat d'$.}
+\item \rc{On page 36, maybe it would be better to replace $d$ by $c$ here. Add
+``for $k\in S^c$ after''to show that $\hat c_k =0$''.}
+\item \rc{On page 37, In the first paragraph, I do not understand why $p$ appears
+here. In the last paragraph, I find 4 instead of 2 on the first term of
+the second line (and then 12 instead of 8 on the third line) .}
+\item \rc{on page 38, In the sixth paragraph, in the inequality, the sign
+should be $\leq$. In the eighth paragraph, $c''$ must be replaced by $c$. In
+the ninth paragraph, ``Taking an union''.}
+\item \rc{On page 40, on the fifth line, ``empricial''. In the last paragraph,
+``whose size is bounded'' : it is the log of the size.}
+
 \end{enumerate}

### 2015-04-29 tex/scam/reviews-v1/response-v1.tex
added rev 2

@@
 
+\item \rc{I had a problem with the definition of an ε-bracketing. First, in the
+definition 8.1, on page 49, `` we define a bracketing'' should be
+replaced by `` we define a $\epsilon$-bracketing''. Then it is said that $\rho(f_L ,
+f_U ) \leq \epsilon$ and that the corresponding size is $N(\epsilon,C,\rho)$. But then, in
+Proposition 8.3 (and almost everywhere else), when $N(2\epsilon,L_2(P),\rho)$ is
+used, it is written $\|f_L − f_U \|_{L_2} \leq \epsilon$ (instead of $2\epsilon$. ) (same thing in
+Corollary 8.4 for instance : $\epsilon$-bracketing with a size $N(2\epsilon,...)$)}
+\item \rc{On page 41, problem with $\epsilon$ (same as the previous item).}
+\item \rc{On page 40, I think the functions in $G$ are bounded by $2sB$ (not $sB$.).}
+\item \rc{On page 49, in Definition 8.1, $f^U$ and $f^L$ must be replaced by $f_U$ and
+$f_L$. On the last line of the page, ``additive convex functions with $s$
+components'' : add ``components bounded by $B$''.}
+\item \rc{On page 49, ``$\int p(x)^2dx \leq (\int p(x)dx)^2$ ``??}
+\item \rc{On page 50, a constant 2 is missing in $\epsilon_n$.}
+\item \rc{On page 41, in the second paragraph, I think the bound on $\sup_{h_L} |⟨w,h_L⟩_n|$ is
+wrong. I would have used the fact that the variables $h_L(X_i) W_i$ are
+independent, centered and sub-Gaussian with a scale smaller than
+$2\sigma s B$. It gives a bound of order $sB\sigma \sqrt{\frac{\log\frac{2}{\delta}}{n}}$.}
+\item \rc{The term $\epsilon$ supposed to balance the two terms is not correct (for
+instance it does not contain $\delta$). There are many small mistakes in the
+calculations. In particular, the exponent in $s$ is not the right one.}
+\item \rc{In the proof of Theorem 8.4 : too many small mistakes in
+calculations, but the final result is OK.}
+\item \rc{On page 45, the term $\epsilon$ supposed to balance the terms is not correct
+(same remark about $\delta$). In the last equations, on the first line (bottom
+of the page) $n$ is missing in one of the scalar products.}
+\item \rc{On page 46: ``taking a union bound and we have that''}
+\item \rc{In Lemma 8.3, I do not see why the functions are continuous : the
+functions $x_{-k} \rightarrow p(x_{-k} | x_k)$ are not supposed to be continuous .}
+\item \rc{On page 47, in the proof of Lemma 8.4 : notation $\phi_{-j}$
+  has not been defined.
+In the definition of $A_+$, the sign should be $>$, not $\geq$. Remove ``both'' .}
+\item \rc{On page 47, ``a sub-exponential random is''.}
+
 \end{enumerate}

### 2015-04-29 tex/scam/reviews-v1/response-v1.tex
new exp

--- 2015-04-29 tex/scam/reviews-v1/response-v1.tex
@@
 \definecolor{blue}{rgb}{0.01,0.01,0.75}
-\def\rc#1{{\it\textcolor{blue}{#1}}\smallskip}
+\def\reviewercomment#1{{\it\textcolor{blue}{#1}}\smallskip}
 \parindent0pt
@@
 
-\rc{Below I recapitulate a few
+\reviewercomment{Below I recapitulate a few
 point of the reviewers', along with some questions/comments of my own.
@@
 \begin{enumerate}
-\item \rc{Boundary flatness condition: much of the paper's analysis hinges on
+\item \reviewercomment{Boundary flatness condition: much of the paper's analysis hinges on
 this condition.  Reviewer 3 raises some concerns about when it holds,
@@
 
-\item \rc{Intuitively, variable selection is very closely related to
+\item \reviewercomment{Intuitively, variable selection is very closely related to
 estimating a function (or possibly its partial derivatives) in the
@@
 
-\item \rc{Writing and proofs need to be tidied up in places to make it easier
+\item \reviewercomment{Writing and proofs need to be tidied up in places to make it easier
 to follow.  See various comments of referees, particularly the
@@
 
-\rc{Conceptually, I have a few questions for the authors to address:}
+\reviewercomment{Conceptually, I have a few questions for the authors to address:}
 
 \begin{enumerate}[(1)]
-\item \rc{If the true regression function $f_0$ can actually be written as a
+\item \reviewercomment{If the true regression function $f_0$ can actually be written as a
 sum of univariate convex functions (plus noise), are there natural
@@
 
-\item \rc{If we actually wish to fit smooth convex univariate components, is
+\item \reviewercomment{If we actually wish to fit smooth convex univariate components, is
 it easy to add this condition as a regularization term and incorporate
@@
 
-\item \rc{Assuming model selection consistency, can one derive prediction
+\item \reviewercomment{Assuming model selection consistency, can one derive prediction
 error bounds using the fitted $f_k$'s and $g_k$'s, as well? Prediction error
@@
 
-\item \rc{In order to improve clarity, the authors should define the convex
+\item \reviewercomment{In order to improve clarity, the authors should define the convex
 additive model at the top of page 5: $f(x_i) = \sum_{k=1}^p f_k(x_{ik})$, where the
@@
 
-\item \rc{Another notational comment: the use of the
+\item \reviewercomment{Another notational comment: the use of the
 distribution function $F$ seems unnecessary (e.g., Lemma 3.1 and
@@
 
-\item \rc{I would suggest including the dependence on the positive-valued lower
+\item \reviewercomment{I would suggest including the dependence on the positive-valued lower
 bound on $p(x)$ (as assumed in (A5)) in the statement of Theorem 3. This
@@
 
-\item \rc{It would be good to point to Assumption (A3) at the beginning of
+\item \reviewercomment{It would be good to point to Assumption (A3) at the beginning of
 Section 5 when discussing the $B$-boundedness condition. In the third
@@
 
-\item \rc{At the top
+\item \reviewercomment{At the top
 of page 23, the remark regarding mutual incoherence conditions is a
@@
 
-\item \rc{In the simulation section, the authors might consider comparing the
+\item \reviewercomment{In the simulation section, the authors might consider comparing the
 set of variables selected after the AC step only with the set of
@@
 \begin{enumerate}[(i)]
-\item \rc{In Section 2.3, it would be good to actually state the regularized
+\item \reviewercomment{In Section 2.3, it would be good to actually state the regularized
 objective function being analyzed, rather than waiting until Section
 4.}
-\item \rc{Assumption (A3) on page 7 is missing the subscript $\infty$.}
-\item \rc{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
+\item \reviewercomment{Assumption (A3) on page 7 is missing the subscript $\infty$.}
+\item \reviewercomment{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
 it seems to be the sub-Gaussian parameter of the additive noise.}
-\item \rc{Perhaps Section 3 should be titled something other than ``Additive
+\item \reviewercomment{Perhaps Section 3 should be titled something other than ``Additive
 faithfulness'' (maybe ``Population- level results''?).}
-\item \rc{The first paragraph of Section 5 should read
+\item \reviewercomment{The first paragraph of Section 5 should read
   ``Figure 3'' rather than ``Algorithm 3.''}
 
-\item \rc{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
-\item \rc{The first sentence of Section 5.1 should read optimization (4.8).}
+\item \reviewercomment{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
+\item \reviewercomment{The first sentence of Section 5.1 should read optimization (4.8).}
 \end{enumerate}
@@
 
-\rc{I found many (unimportant) mistakes in the proofs (I
+We are grateful to the reviewer for the detailed reading. We have corrected the mistakes found and further proof-read the paper. We discuss some of the issues raised.
+
+\reviewercomment{I found many (unimportant) mistakes in the proofs (I
   did not mention them all in the minor comments), which need to be
@@
 \begin{enumerate}
-\item \rc{I have a problem with the assertion of
+\item \reviewercomment{I have a problem with the assertion of
   uniqueness in Lemma 3.1 and Therorem 3.2. First, in Lemma 3.1, it is
@@
    for a certain function $g$. Then if $(f_1^∗, f_2^∗)$ is a solution,
-   $(f_1^∗ + f_2^* \circ g, 0)$ is also a solution.}
+   $(f_1^∗ + f_2^ \circ g, 0)$ is also a solution.}
 
-\item \rc{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
-write $g_k(X_k)$ in the sum instead of $g_k$.}
+We have corrected the proof of Lemma 3.1 and we have given a more rigorous proof that the components $f^*_k$'s are unique in a new Lemma 8.3 (old Lemma 8.3 was removed).
+Our result requires that the density $p(\mathbf{x}) > 0$ and thus, the $X_2 = g(X_1)$ example raised by the reviewer is ruled out.
 
-\item \rc{On page 9, in the proof of Lemma 3.1, the star has been forgotten
-twice on $f_{k'}$ in (3.2) and (3.7).}
-
-\item \rc{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
-− \E f(X)$ is unique'', the term $−\sum_{k'\neq k} f_{k'}(X_{k'})$ has been forgotten.}
-
-\item \rc{On page 10, on line 14, ``In particular, if $F$ is the uniform
-distribution etc'', the term $− \int f$ has been forgotten.}
-
-\item \rc{On page 10, on line 16, ``additively'' should be replaced by
-``additive''.}
-
-\item \rc{On page 11, at the bottom of the page, ``before we presenting''}
-
-\item \rc{On page 11, after Deônition 3.2, it is written ``when the joint
+\item \reviewercomment{On page 11, after Deônition 3.2, it is written ``when the joint
 density satisfies the property that
@@
 
-\item \rc{On page 12, I did not understand why the functions 
+It is not necessary that $p(\mathbf{x}_{-j}, x_j) = 0$ at $x_j = 0,1$; it is necessary that $p(\mathbf{x}_{-j}, x_j) > 0$.
+We have however, added an additional condition that $p(\mathbf{x})$ has a bounded second derivative.
+This condition ensures that the marginal density $p(x_j)$ is twice differentiable and $p'(x_j) = p''(x_j) = 0$ at $x_j = 0,1$.
+With this, it is valid to apply the quotient rule for differentiation to show that boundary flatness holds.
+Please see the second item in Example 3.2 for the relevant modifications.
+
+\item \reviewercomment{On page 12, I did not understand why the functions 
 $\frac{\partial^2 p(x_{-j} |  x_j)}{\partial x_j^2}$
@@
 
-\item \rc{On page 13, on line 6, ``this this''.}
+We have modified the definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$ is bounded and has a bounded first and second derivative for all $x_j$ in some open set around the boundary points and for all $\mathbf{x}_{-j}$.
+Dominated convergenc theorem holds without problems because we only exchange the derivative and the integral at $x_j = 0,1$.
+Just to make sure, we have verified in detail that the domination condition holds in the newly added Section 8.3.4.
 
-\item \rc{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
-is not speciôed that $Var(X_1) = 1$.}
-\item \rc{On page 13, on line 29, ``additive'' should be replaced by
-``additively''.}
-\item \rc{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
-parameter $\mu$ should be introduced as before.}
-\item \rc{On page 16, in the expresson of $c^∗$, the
-  denominator should be $\E X_k^2 −m_k^2$.}
-\item \rc{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
+%\item \reviewercomment{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
+%is not speciôed that $Var(X_1) = 1$.}
+
+%\item \reviewercomment{On page 13, on line 29, ``additive'' should be replaced by
+%``additively''.}
+
+%\item \reviewercomment{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
+%parameter $\mu$ should be introduced as before.}
+
+%\item \reviewercomment{On page 16, in the expresson of $c^∗$, the
+%  denominator should be $\E X_k^2 −m_k^2$.}
+
+\item \reviewercomment{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
 lemma supposes that $\phi$ is continuous. Here I do not see why $\phi =
@@
 $[0,1]^p$. ).}
-\item \rc{On page 17, same problem as before with the absence of parameter $\mu$.}
-\item \rc{On page 17, on line 16 ``for that variable. for each''}
-\item \rc{On page 18, at the bottom of the page :
+
+We have modified the conditions and the proof of Theorem 3.2 so that $\phi$ need only be bounded.
+The new proof does not require that $h^*_k$ is differentiable, only that it is in $L^2$.
+The old Lemma 8.3 has been removed.
+
+\item \reviewercomment{On page 17, same problem as before with the absence of parameter $\mu$.}
+\item \reviewercomment{On page 17, on line 16 ``for that variable. for each''}
+\item \reviewercomment{On page 18, at the bottom of the page :
   ``$\beta_{\pi_k(i+1)k} 
 \geq \beta_{\pi_k(i)k}$ for $i=1,\ldots, n-1$'' , $n−1$ must be replaced by $n−2$.}
-\item \rc{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
+\item \reviewercomment{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
   f_{ki}$.}
-\item \rc{On page 20, in the third paragraph, on the second, third and fourth
+\item \reviewercomment{On page 20, in the third paragraph, on the second, third and fourth
 lines, $j$ and $j − 1$ must be replaced by $j + 1$ and $j$ respectively in
 $x_{\pi_k(j)k}$ and $x_{\pi_k(j-1)k}$.}
-
-\item \rc{On page 20, In the central matrix equation, the
-  first vector should be
-  $\left[\begin{matrix}f_k(x_{1k}\\ f_k(x_{2k}\\ \vdots\\f_k(x_{nk}\end{matrix}\right]$. Next
-  in ``$\mu_k = -\frac{1}{n} 1_n^T \Delta_k d_k$``, $1_n$ is missing.}
-\item \rc{On page 21, in Section 5, at the end of the
-  second paragraph, ``$m\hat{}u$ from
-our estimation procedure''.}
-
-\item \rc{On page 22, in Deônition 5.1, the inequalities
-  about $d_k$ must be replaced by the same inequalities as in Proposition 4.1.}
-
-\item \rc{On page 22 (and on page 31), in the statement of Theorem
-  5.1, in\\ $\max_{i=1,\ldots, n} \frac{X_{k\pi_k(i+1)}-
-    X_{k\pi_k(i)}}{\text{range}_k} \geq \frac{1}{16}$ the
-sign $\geq$ must be replaced by $\leq$ . Besides I think it
-is a bad idea to change notation : $X_{k\pi_k(i)}$ should
-be replaced by $X_{\pi_k(i)k}$ as before (page 19 for instance).}
-
-\item \rc{On page 23, in equation (5.1), in ``$f^∗(X)$'', the star must be
-removed.}
-
-\item \rc{On page 24, ``$\alpha_{+} > 0$ since $f$ is the unique risk minimizer'' : I do
-not understand this statement (there is an infimum, not a minimum in
-the definition of $\alpha_{+}$.)}
-\item \rc{On page 24, in Remark 5.1, ``In important direction''.}
-\item \rc{On page 25, in the statement of Theorem 5.3, the square must be
-removed on $\alpha_-$.}
 
@@
 \begin{enumerate}
-\item \rc{The basis of all the results seem to be the boundary flatness
+\item \reviewercomment{The basis of all the results seem to be the boundary flatness
 condition. This condition seems to be an artifact of the analysis and
@@
 
-\item \rc{Following on from the previous point, the simulation study also does
+\item \reviewercomment{Following on from the previous point, the simulation study also does
 not add any further insight to this issue since the simulations are
@@
 \begin{enumerate}
-\item \rc{I didn't think there was any need for Section 2
+\item \reviewercomment{I didn't think there was any need for Section 2
   since it feels very repetitive and slightly confusing that parts of
@@
 
-\item \rc{Page 2, second last paragraph `and and.'}
+\item \reviewercomment{Page 2, second last paragraph `and and.'}
 \end{enumerate}

### 2015-04-29 code/paper_exp/K.m

@@ -12,22 +12,28 @@ clc;
 addpath('../simdata', '-end')
 
 switch version
-    case 01, s = 2; p = 128;
-    case 02, s = 4; p = 128;
-    case 03, s = 8; p = 128;
-    case 04, s = 12; p = 128;
-    case 05, s = 16; p = 128;
+    case 01, n = 200;   s = 4;
+    case 02, n = 400;   s = 4;
+    case 03, n = 600;   s = 4;
+    case 04, n = 800;   s = 4;
+    case 05, n = 1000;  s = 4;
         
-    case 06, s = 2; p = 256;
-    case 07, s = 4; p = 256;
-    case 08, s = 8; p = 256;
-    case 09, s = 12; p = 256;
-    case 10, s = 16; p = 256;
+    case 06, n = 200;   s = 8;
+    case 07, n = 400;   s = 8;
+    case 08, n = 600;   s = 8;
+    case 09, n = 800;   s = 8;
+    case 10, n = 1000;  s = 8;
+        
+    case 11, n = 200;   s = 12;
+    case 12, n = 400;   s = 12;
+    case 13, n = 600;   s = 12;
+    case 14, n = 800;   s = 12;
+    case 15, n = 1000;  s = 12;
 
     otherwise, return
 end
 
-n = 600;
+p = 128;
 v = 0.2;
 k = s;
 K = 7;

### 2015-04-29 tex/scam/reviews-v1/response-v1.tex

--- 2015-04-29 tex/scam/reviews-v1/response-v1.tex
@@
 
+We are grateful to the reviewer for the detailed reading. We have corrected the mistakes found and further proof-read the paper. We discuss some of the issues raised.
+
 \rc{I found many (unimportant) mistakes in the proofs (I
@@
 
-\item \rc{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
-write $g_k(X_k)$ in the sum instead of $g_k$.}
+We have corrected the proof of Lemma 3.1 and we have given a more rigorous proof that the components $f^*_k$'s are unique in a new Lemma 8.3 (old Lemma 8.3 was removed).
+Our result requires that the density $p(\mathbf{x}) > 0$ and thus, the $X_2 = g(X_1)$ example raised by the reviewer is ruled out.
 
-\item \rc{On page 9, in the proof of Lemma 3.1, the star has been forgotten
-twice on $f_{k'}$ in (3.2) and (3.7).}
+%\item \rc{In the definition of $g_k^∗$ on pages 6 and 15, it would be more precise to
+%write $g_k(X_k)$ in the sum instead of $g_k$.}
 
-\item \rc{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
-− \E f(X)$ is unique'', the term $−\sum_{k'\neq k} f_{k'}(X_{k'})$ has been forgotten.}
+%\item \rc{On page 9, in the proof of Lemma 3.1, the star has been forgotten
+%twice on $f_{k'}$ in (3.2) and (3.7).}
 
-\item \rc{On page 10, on line 14, ``In particular, if $F$ is the uniform
-distribution etc'', the term $− \int f$ has been forgotten.}
+%\item \rc{On page 10, on line 3, ``therefore the solution $f_k^∗(x_k) = \E[f(X)|x_k]
+%− \E f(X)$ is unique'', the term $−\sum_{k'\neq k} f_{k'}(X_{k'})$ has been forgotten.}
 
-\item \rc{On page 10, on line 16, ``additively'' should be replaced by
-``additive''.}
+%\item \rc{On page 10, on line 14, ``In particular, if $F$ is the uniform
+%distribution etc'', the term $− \int f$ has been forgotten.}
 
-\item \rc{On page 11, at the bottom of the page, ``before we presenting''}
+%\item \rc{On page 10, on line 16, ``additively'' should be replaced by
+%``additive''.}
+
+%\item \rc{On page 11, at the bottom of the page, ``before we presenting''}
 
@@
 
+It is not necessary that $p(\mathbf{x}_{-j}, x_j) = 0$ at $x_j = 0,1$; it is necessary that $p(\mathbf{x}_{-j}, x_j) > 0$.
+We have however, added an additional condition that $p(\mathbf{x})$ has a bounded second derivative.
+This condition ensures that the marginal density $p(x_j)$ is twice differentiable and $p'(x_j) = p''(x_j) = 0$ at $x_j = 0,1$.
+With this, it is valid to apply the quotient rule for differentiation to show that boundary flatness holds.
+Please see the second item in Example 3.2 for the relevant modifications.
+
 \item \rc{On page 12, I did not understand why the functions 
@@
 
-\item \rc{On page 13, on line 6, ``this this''.}
+We have modified the definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$ is bounded and has a bounded first and second derivative for all $x_j$ in some open set around the boundary points and for all $\mathbf{x}_{-j}$.
+Dominated convergenc theorem holds without problems because we only exchange the derivative and the integral at $x_j = 0,1$.
+Just to make sure, we have verified in detail that the domination condition holds in the newly added Section 8.3.4.
+
+%\item \reviewercomment{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
+%is not speciôed that $Var(X_1) = 1$.}
+
+%\item \reviewercomment{On page 13, on line 29, ``additive'' should be replaced by
+%``additively''.}
+
+%\item \reviewercomment{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
+%parameter $\mu$ should be introduced as before.}
+
+%\item \reviewercomment{On page 16, in the expresson of $c^∗$, the
+%  denominator should be $\E X_k^2 −m_k^2$.}
+
+%\item \rc{On page 13, on line 6, ``this this''.}
 
@@
 is not speciôed that $Var(X_1) = 1$.}
+
 \item \rc{On page 13, on line 29, ``additive'' should be replaced by
 ``additively''.}
+
 \item \rc{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
 parameter $\mu$ should be introduced as before.}
+
 \item \rc{On page 16, in the expresson of $c^∗$, the
   denominator should be $\E X_k^2 −m_k^2$.}
+
 \item \rc{On page 16, in the proof of Theorem 3.2, Lemma 8.3 is used. This
@@
 $[0,1]^p$. ).}
+
 \item \rc{On page 17, same problem as before with the absence of parameter $\mu$.}
 \item \rc{On page 17, on line 16 ``for that variable. for each''}
+
 \item \rc{On page 18, at the bottom of the page :

### 2015-04-29 tex/scam/experiments.tex
new exp
minor mod

@@
 \end{equation}
-Here $\x_{i}$ denotes data sample $i$ drawn from some distribution $P$. 
-$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=s$, where $S$
+Here $\x_{i}$ denotes data sample $i$ drawn from some distribution $P$. $f_0$ is the true regression function. $\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=s$, where $S$
 represents the set of relevant variables, and 
 $\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,\sigma)$. For 
-all simulations, we set $\sigma$ such that the signal-to-noise ratio(SNR, $\frac{\trm{std}(Y)}{\sigma}$) is 5; we
-set $\lambda = \frac{1}{2} \sqrt{ \frac{\log^2(np)}{n} }$.
+all simulations, we set $\sigma$ such that the signal-to-noise ratio(SNR, $\frac{\trm{std}(Y)}{\sigma}$) is 5.
+Also, for all simulations except the sixth, we choose the set of relevant variables $S$ uniformly at random among all variables $\{1,...,p\}$.
+
+The purpose of the simulations is to see how the probability of variable selection scales with the number of samples $n$, the ambient dimension $p$, and the sparsity level $s$.
+We study both the independent case where $P = N(0, I_p)$ and the correlated case where $P$ is a correlated Gaussian Copula modified slightly to satisfy boundary flatness.
+We measure the probability of exact selection in the independent case and the probability of screening in the correlated case.
+We also study both cases where the regression function is simple (quadratic) and cases where the regression function is complicated (softmax of random linear forms).
+In all our experiments, we mark a variable as selected if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate $\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$.
 
@@
 
-The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
+The matrix $\Q$ is a symmetric positive definite matrix of dimension $s \times{} s$. 
 Note that if $\Q$ is diagonal, then the true function is convex
@@
 We use independent $X$ and draw $X \sim N(0, I_p)$.
-For each $(n,p)$ combination, we generate $100$ independent data
-sets.
-For each data set we use the AC/DC algorithm and mark feature $j$ as irrelevant if both the AC estimate $\| \hat{f}_j \|_\infty$ and the DC estimate $\| \hat{g}_k \|_\infty$ are smaller than $10^{-6}$.
-We plot the probability of exact
-support recovery over the $100$ independent trials in Figure \ref{Support}(a).  We
-observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
+For each $(n,p)$ combination, we generate $100$ independent trials. 
+In Figure~\ref{Support}(a), we plot the probability of exact
+support recovery, that is, the probability that the set of the selected variables is exactly equal to the set of true variables.
+We observe that the algorithm performs consistent variable selection even if the dimensionality is large.
+To give the reader a
 sense of the running speed, for a 
 data set with $n=1000$ and $p=512$, the code runs in roughly two 
-minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.
+minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory. In this simulation, $s=5$ and we set $\lambda = \frac{1}{2} \sqrt{ \frac{\log^2(np)}{n} }$.
 
@@
 We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We use $X \sim N(0,I_p)$. We again run the AC/DC optimization on $100$
-independent trials and plot the probability of recovery
+$n=100,200,\ldots,1000$. We use $X \sim N(0,I_p)$, set $s=5$, and use the same $\lambda$ as before.  We again run the AC/DC optimization on $100$
+independent trials and plot the probability of exact recovery
 in Figure \ref{Support}(b). The results demonstrate that AC/DC performs
@@
 \]
-Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the covariance structure.
+Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the same covariance.
 Gaussian Copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each variable of Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new desired marginal distribution.
 In all our experiments, we set $\gamma = 0.05$ and set the marginal CDF $F$ so that marginal density of the Copula is bimodal and supported on $[-1.8, 1.8]$.
-The marginal density of the mixture is shown in Figure~\ref{fig:copula_marginal}.
+The resulting marginal density of the mixture is shown in Figure~\ref{fig:copula_marginal}.
 Notice that boundary flatness holds because the distribution is uniform in the boundary area $[-2,2]^p \backslash [-1.8, 1.8]^p$.
@@
 
-In the \textbf{third experiment}, we set $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
+In the \textbf{third simulation}, we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
 We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128$.
-We measure success not through exact recovery but through approximate recovery.
-We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall.
+We measure success not through exact recovery but through faithful recovery.
+We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall (true sparsisty $s=5$).
+We use the same $\lambda$ as before.
 The probabilities of success are computed from 40 independent trials and plotted against various values of $\nu$ in Figure~\ref{Support}(d).
-Additionally, for $\nu = 0.5$, we show the number of selected variables versus the sample size as a Box-and-Whisker plot in Figure~\ref{Support}(e).
-As can be seen, AC/DC can successfully recover the relevant variables with only a small number of false positives.
+Additionally, for $\nu = 0.5$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(e).
+As seen, for distributions with moderate to small correlations, AC/DC can successfully recover the relevant variables with only a small number of false positives.
 
@@
 
-For the \textbf{fourth experiment}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution described earlier with correlation level $\nu = 0.5$.
-We use the same approximate recovery success criteria as the third experiment and plot probability of approximate recovery against the number of samples for $p=128, 256, 512$.
+For the \textbf{fourth simulation}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance  $\Sigma_{ij}=\nu^{|i-j|}$ and $\nu = 0.5$.
+We set $s=5$ and use the same $\lambda$ as before.
+We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples for $p=128, 256, 512$.
 The probabilities are computed over 30 independent trials.
+Also, for $p=256$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(g).
+Not surprisingly, the softmax function is harder than the quadratic function; the softmax setting requires about $n > 1500$ to achieve the same success probability as the quadratic setting with $n=1000$.
+We see that increasing the ambient dimension $p$ does not signficantly affect the recovery probability however.
 
@@
 For the \textbf{sixth experiment}, we compare the variables selected via the AC stage and the variables selected via the DC stage.
-We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with correlation level $\nu = -0.7$.
+We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.
 We set $n=500, p=128$.

### 2015-04-29 code/paper_exp/K.m

@@ -13,22 +13,22 @@ addpath('../simdata', '-end')
 
 switch version
     case 01, n = 200;   s = 3;
-    case 02, n = 500;   s = 3;
-    case 03, n = 800;   s = 3;
-    case 04, n = 1100;   s = 3;
-    case 05, n = 1500;  s = 3;
+    case 02, n = 600;   s = 3;
+    case 03, n = 1000;   s = 3;
+    case 04, n = 1400;   s = 3;
+    case 05, n = 1800;  s = 3;
         
     case 06, n = 200;   s = 6;
-    case 07, n = 500;   s = 6;
-    case 08, n = 800;   s = 6;
-    case 09, n = 1100;   s = 6;
-    case 10, n = 1500;  s = 6;
+    case 07, n = 600;   s = 6;
+    case 08, n = 1000;   s = 6;
+    case 09, n = 1400;   s = 6;
+    case 10, n = 1800;  s = 6;
         
     case 11, n = 200;   s = 9;
-    case 12, n = 500;   s = 9;
-    case 13, n = 800;   s = 9;
-    case 14, n = 1100;   s = 9;
-    case 15, n = 1500;  s = 9;
+    case 12, n = 600;   s = 9;
+    case 13, n = 1000;   s = 9;
+    case 14, n = 1400;   s = 9;
+    case 15, n = 1800;  s = 9;
 
     otherwise, return
 end
@@ -37,7 +37,7 @@ p = 128;
 k = s;
 
 K = 7;
-lambda = s*0.05*sqrt(1/n)*log(n*p); % MODIFY
+lambda = s*0.03*sqrt(1/n)*log(n*p); % MODIFY
 SNR = 5;
 
 maxit = 20; tol = 10^-6;

### 2015-04-29 tex/scam/experiments.tex
update

@@
 We measure the probability of exact selection in the independent case and the probability of screening in the correlated case.
-We also study both cases where the regression function is simple (quadratic) and cases where the regression function is complicated (softmax of random linear forms).
+We also study both cases where the regression function is parametric (quadratic) and cases where the regression function is nonparametric (softmax of linear forms).
 In all our experiments, we mark a variable as selected if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate $\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$.
@@
 
-In the \textbf{first simulation}, we vary the ambient dimension $p$.
+In the \textbf{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$.
 We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
@@
 
-In the \textbf{second simulation}, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
+In the \textbf{second simulation} (Figure~\ref{Support}b,c), we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive.
+We generate four $\Q$ matrices
 plotted in Figure \ref{Support}(c), where the diagonal elements are all one and
@@
 
-In the third, fourth, and fifth simulations, we use correlated design and vary the correlation.
-We generate $X$ from a non-Gaussian correlated boundary flat distribution.
+In the third and fourth simulation, we use a correlated design.
+We generate $X$ from a non-Gaussian boundary flat distribution with covariance $\Sigma$.
 The distribution we used is a mixture of a uniform distribution and a Gaussian Copula.
@@
 \]
-Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the same covariance.
-Gaussian Copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each variable of Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new desired marginal distribution.
+The Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the same covariance.
+Gaussian Copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each of the variables of a Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new marginal distribution.
 In all our experiments, we set $\gamma = 0.05$ and set the marginal CDF $F$ so that marginal density of the Copula is bimodal and supported on $[-1.8, 1.8]$.
@@
 
-In the \textbf{third simulation}, we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
+In the \textbf{third simulation} (Figure~\ref{Support}d,e), we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
 We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128$.
@@
 
-In the fourth, fifth, and sixth simulation, we use a softmax regression function
+In the fourth, fifth, and sixth simulation, we use a softmax function as the ground truth
 \[
@@
 \]
-where $\{\beta_k \in \R^s\}_{k=1,...,K}$ are random unit vectors. $\mu$ is chosen so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
+We generate random unit vectors as $\{\beta_k \in \R^s\}_{k=1,...,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
 
-For the \textbf{fourth simulation}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance  $\Sigma_{ij}=\nu^{|i-j|}$ and $\nu = 0.5$.
+For the \textbf{fourth simulation} (Figure~\ref{Support}f,g), we let $f_0$ be the softmax function and let $X$ be drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$.
 We set $s=5$ and use the same $\lambda$ as before.
-We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples for $p=128, 256, 512$.
+We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples for $p=128, 256, 512$ in Figure~\ref{Support}(f).
 The probabilities are computed over 30 independent trials.
 Also, for $p=256$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(g).
-Not surprisingly, the softmax function is harder than the quadratic function; the softmax setting requires about $n > 1500$ to achieve the same success probability as the quadratic setting with $n=1000$.
-We see that increasing the ambient dimension $p$ does not signficantly affect the recovery probability however.
+The softmax function is more challenging to estimate than the quadratic function; the softmax function requires about $n > 1500$ to achieve the same success probability as the quadratic function with $n=1000$.
+Regardless, we see that increasing the ambient dimension $p$ does not signficantly affect the recovery probability.
 
-For the \textbf{fifth experiment}, we use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with correlation level $\nu = 0.2$.
+For the \textbf{fifth experiment} (Figure~\ref{Support}h), we vary the true sparsity level $s$.
+We let $f_0$ be the softmax function, $X \sim N(0, I)$, and set $p=128$.
+We set $\lambda = 0.1 s \sqrt{\frac{\log^2 np}{n}}$ for $s = 3,6,9$.
+We compute the probability of exact recovery over 40 independent trials and plot the results in Figure~\ref{Support}(h).
 
-For the \textbf{sixth experiment}, we compare the variables selected via the AC stage and the variables selected via the DC stage.
+For the \textbf{sixth experiment} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
 We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.

### 2015-04-29 code/paper_exp/K.m

@@ -12,23 +12,23 @@ clc;
 addpath('../simdata', '-end')
 
 switch version
-    case 01, n = 200;   s = 3;
-    case 02, n = 600;   s = 3;
-    case 03, n = 1000;   s = 3;
-    case 04, n = 1400;   s = 3;
-    case 05, n = 1800;  s = 3;
+    case 01, n = 400;   s = 3;
+    case 02, n = 800;   s = 3;
+    case 03, n = 1200;   s = 3;
+    case 04, n = 1600;   s = 3;
+    case 05, n = 2000;  s = 3;
         
-    case 06, n = 200;   s = 6;
-    case 07, n = 600;   s = 6;
-    case 08, n = 1000;   s = 6;
-    case 09, n = 1400;   s = 6;
-    case 10, n = 1800;  s = 6;
+    case 06, n = 400;   s = 6;
+    case 07, n = 800;   s = 6;
+    case 08, n = 1200;   s = 6;
+    case 09, n = 1600;   s = 6;
+    case 10, n = 2000;  s = 6;
         
-    case 11, n = 200;   s = 9;
-    case 12, n = 600;   s = 9;
-    case 13, n = 1000;   s = 9;
-    case 14, n = 1400;   s = 9;
-    case 15, n = 1800;  s = 9;
+    case 11, n = 400;   s = 9;
+    case 12, n = 800;   s = 9;
+    case 13, n = 1200;   s = 9;
+    case 14, n = 1600;   s = 9;
+    case 15, n = 2000;  s = 9;
 
     otherwise, return
 end
@@ -37,7 +37,7 @@ p = 128;
 k = s;
 
 K = 7;
-lambda = s*0.1*sqrt(1/n)*log(n*p); % MODIFY
+lambda = 0.5*sqrt(1/n)*log(n*p); % MODIFY
 SNR = 5;
 
 maxit = 20; tol = 10^-6;

### 2015-04-30 tex/scam/experiments.tex
k

@@
 In all our experiments, we mark a variable as selected if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate $\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$.
+We set $\lambda = 0.5 \sqrt{\frac{\log^2 np}{n}}$ for all the simulations.
 
@@
 In the \textbf{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$.
-We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
-We use independent $X$ and draw $X \sim N(0, I_p)$.
+We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$ and $512$.
+We draw $X \sim N(0, I_p)$.
 For each $(n,p)$ combination, we generate $100$ independent trials. 
 In Figure~\ref{Support}(a), we plot the probability of exact
-support recovery, that is, the probability that the set of the selected variables is exactly equal to the set of true variables.
-We observe that the algorithm performs consistent variable selection even if the dimensionality is large.
-To give the reader a
+support recovery. We observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
 sense of the running speed, for a 
 data set with $n=1000$ and $p=512$, the code runs in roughly two 
-minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory. In this simulation, $s=5$ and we set $\lambda = \frac{1}{2} \sqrt{ \frac{\log^2(np)}{n} }$.
+minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.
 
@@
 ($\alpha=0,0.2,0.5,1$ for the four cases). We show the 4 $\Q$ matrices we used in Figure~\ref{Support}(c).
-We fix $p=128$ and choose
-$n=100,200,\ldots,1000$. We use $X \sim N(0,I_p)$, set $s=5$, and use the same $\lambda$ as before.  We again run the AC/DC optimization on $100$
+We fix $p=128$, $s=5$, and $X \sim N(0,I_p)$.  We again run the AC/DC optimization on $100$
 independent trials and plot the probability of exact recovery
@@
 In the \textbf{third simulation} (Figure~\ref{Support}d,e), we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
-We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128$.
+We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128, s=5$.
 We measure success not through exact recovery but through faithful recovery.
@@
 Additionally, for $\nu = 0.5$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(e).
-As seen, for distributions with moderate to small correlations, AC/DC can successfully recover the relevant variables with only a small number of false positives.
+As seen, for small to moderate correlations, AC/DC can successfully recover the relevant variables with only a small number of false positives.
 
@@
 For the \textbf{fourth simulation} (Figure~\ref{Support}f,g), we let $f_0$ be the softmax function and let $X$ be drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$.
-We set $s=5$ and use the same $\lambda$ as before.
-We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples for $p=128, 256, 512$ in Figure~\ref{Support}(f).
+We set $s=5$ and vary $p=128,256,512$.
+We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples in Figure~\ref{Support}(f).
 The probabilities are computed over 30 independent trials.
@@
 We let $f_0$ be the softmax function, $X \sim N(0, I)$, and set $p=128$.
-We set $\lambda = 0.1 s \sqrt{\frac{\log^2 np}{n}}$ for $s = 3,6,9$.
 We compute the probability of exact recovery over 40 independent trials and plot the results in Figure~\ref{Support}(h).
@@
 We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.
-We set $n=500, p=128$.
+We set $s=5, n=500, p=128$.
 We perform 30 independent trials and plot the frequency of variable selection in Figure~\ref{fig:ac_v_dc}.

### 2015-04-30 code/paper_exp/K.m

@@ -12,23 +12,26 @@ clc;
 addpath('../simdata', '-end')
 
 switch version
-    case 01, n = 400;   s = 3;
-    case 02, n = 800;   s = 3;
-    case 03, n = 1200;   s = 3;
-    case 04, n = 1600;   s = 3;
-    case 05, n = 2000;  s = 3;
+    case 01, n = 100;   s = 3;
+    case 02, n = 300;   s = 3;
+    case 03, n = 600;   s = 3;
+    case 04, n = 900;   s = 3;
+    case 05, n = 1200;   s = 3;
+    case 06, n = 1500;  s = 3;
+    
+    case 07, n = 100;   s = 5;
+    case 08, n = 300;   s = 5;
+    case 09, n = 600;   s = 5;
+    case 10, n = 900;   s = 5;
+    case 11, n = 1200;   s = 5;
+    case 12, n = 1500;  s = 5;
         
-    case 06, n = 400;   s = 6;
-    case 07, n = 800;   s = 6;
-    case 08, n = 1200;   s = 6;
-    case 09, n = 1600;   s = 6;
-    case 10, n = 2000;  s = 6;
-        
-    case 11, n = 400;   s = 9;
-    case 12, n = 800;   s = 9;
-    case 13, n = 1200;   s = 9;
-    case 14, n = 1600;   s = 9;
-    case 15, n = 2000;  s = 9;
+    case 13, n = 100;  s = 7;
+    case 14, n = 300;   s = 7;
+    case 15, n = 600;   s = 7;
+    case 16, n = 900;   s = 7;
+    case 17, n = 1200;   s = 7;
+    case 18, n = 1500;  s = 7;
 
     otherwise, return
 end
@@ -37,7 +40,7 @@ p = 128;
 k = s;
 
 K = 7;
-lambda = 0.5*sqrt(1/n)*log(n*p); % MODIFY
+lambda = 0.3*sqrt(1/n)*log(n*p); % MODIFY
 SNR = 5;
 
 maxit = 20; tol = 10^-6;
@@ -70,8 +73,9 @@ for run = 1:nrun
     Ln(:,run) = max(Lnvex, Lncave);
     
     epsil = 1e-6;
-    succ1 = min(Ln(J(:,run),run)) > epsil
-    succ2 = sum(Ln(:,run) > epsil) <= k
+    succ1 = min(Ln(J(:,run),run)) > epsil;
+    succ2 = sum(Ln(:,run) > epsil) <= k;
[…]

### 2015-04-30 code/paper_exp/acdc_QP.m

@@ -21,7 +21,7 @@ counter = [0,0];
 while iter < maxit && change > tol
     iter = iter + 1;
     
-    for d = 1:p
+    for d = 1:p           
         res = res + z(d,:)';
         
         % screening for AC 

### 2015-04-30 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
-%\item \reviewercomment{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
-%is not speciôed that $Var(X_1) = 1$.}
-
-%\item \reviewercomment{On page 13, on line 29, ``additive'' should be replaced by
-%``additively''.}
-
-%\item \reviewercomment{On page 13, the assumption $\E f(X) = 0$ should be made, or else the
-%parameter $\mu$ should be introduced as before.}
-
-%\item \reviewercomment{On page 16, in the expresson of $c^∗$, the
-%  denominator should be $\E X_k^2 −m_k^2$.}
-
 %\item \rc{On page 13, on line 6, ``this this''.}
@@
 
-\item \rc{On page 13, on line 29, ``additive'' should be replaced by
-``additively''.}
+$\Sigma$ has been defined as the covariance matrix with diagonal entries equal to 1.
+
+%\item \rc{On page 13, on line 29, ``additive'' should be replaced by
+%``additively''.}
 
@@
 
-\item \rc{On page 16, in the expresson of $c^∗$, the
-  denominator should be $\E X_k^2 −m_k^2$.}
+We have added the $\E f(X) = 0$ assumption.
+
+%\item \rc{On page 16, in the expresson of $c^∗$, the
+%  denominator should be $\E X_k^2 −m_k^2$.}
 
@@
 
+We have updated the statement and the proof of Theorem 3.2 so that only boundedness is required of $\phi$.
+Furthermore, $h^*_k$ is no longer required to be twice differentiable; it need only be square-integrable.
+The old Lemma 8.3 is no longer necessary and has been removed.
+
 \item \rc{On page 17, same problem as before with the absence of parameter $\mu$.}
-\item \rc{On page 17, on line 16 ``for that variable. for each''}
 
-\item \rc{On page 18, at the bottom of the page :
-  ``$\beta_{\pi_k(i+1)k} 
-\geq \beta_{\pi_k(i)k}$ for $i=1,\ldots, n-1$'' , $n−1$ must be replaced by $n−2$.}
+$\mu$ has been added.
+
+%\item \rc{On page 17, on line 16 ``for that variable. for each''}
+
+%\item \rc{On page 18, at the bottom of the page :
+%  ``$\beta_{\pi_k(i+1)k} 
+%\geq \beta_{\pi_k(i)k}$ for $i=1,\ldots, n-1$'' , $n−1$ must be replaced by $n−2$.}
+
 \item \rc{On page 19, $\sum_{i} f_{ik}$ instead of $\sum_i
   f_{ki}$.}
-\item \rc{On page 20, in the third paragraph, on the second, third and fourth
-lines, $j$ and $j − 1$ must be replaced by $j + 1$ and $j$ respectively in
-$x_{\pi_k(j)k}$ and $x_{\pi_k(j-1)k}$.}
 
-\item \rc{On page 20, In the central matrix equation, the
-  first vector should be
-  $\left[\begin{matrix}f_k(x_{1k}\\ f_k(x_{2k}\\ \vdots\\f_k(x_{nk}\end{matrix}\right]$. Next
-  in ``$\mu_k = -\frac{1}{n} 1_n^T \Delta_k d_k$``, $1_n$ is missing.}
-\item \rc{On page 21, in Section 5, at the end of the
-  second paragraph, ``$m\hat{}u$ from
-our estimation procedure''.}
+This has been fixed. We have also gone through the paper and corrected all instances of the $f_{ik}, f_{ki}$ notation inconsistency so that $i$ always come before $k$.
 
-\item \rc{On page 22, in Deônition 5.1, the inequalities
-  about $d_k$ must be replaced by the same inequalities as in Proposition 4.1.}
+%\item \rc{On page 20, in the third paragraph, on the second, third and fourth
+%lines, $j$ and $j − 1$ must be replaced by $j + 1$ and $j$ respectively in
+%$x_{\pi_k(j)k}$ and $x_{\pi_k(j-1)k}$.}
+
+%\item \rc{On page 20, In the central matrix equation, the
+%  first vector should be
+%  $\left[\begin{matrix}f_k(x_{1k}\\ f_k(x_{2k}\\ \vdots\\f_k(x_{nk}\end{matrix}\right]$. N%ext
+%  in ``$\mu_k = -\frac{1}{n} 1_n^T \Delta_k d_k$``, $1_n$ is missing.}
+%\item \rc{On page 21, in Section 5, at the end of the
+%  second paragraph, ``$m\hat{}u$ from
+%our estimation procedure''.}
+
+%\item \rc{On page 22, in Deônition 5.1, the inequalities
+%  about $d_k$ must be replaced by the same inequalities as in Proposition 4.1.}
 
@@
 
-\item \rc{On page 23, in equation (5.1), in ``$f^∗(X)$'', the star must be
-removed.}
+We have corrected all instances of this notation inconsistency.
+
+%\item \rc{On page 23, in equation (5.1), in ``$f^∗(X)$'', the star must be
+%removed.}
 
@@
 the definition of $\alpha_{+}$.)}
-\item \rc{On page 24, in Remark 5.1, ``In important direction''.}
+
+TODO
+
+%\item \rc{On page 24, in Remark 5.1, ``In important direction''.}
+
 \item \rc{On page 25, in the statement of Theorem 5.3, the square must be
 removed on $\alpha_-$.}
+
+The square is not an error.
 

### 2015-04-30 tex/scam/reviews-v1/response-v1.tex
more response

@@
 
-TODO
+The infimum is achieved by some $f \neq f^*$ since the constraint set $\{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)\}$ is a finite union of closed convex sets.
+It is $\bigcup_k \{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) = \textrm{supp}(f^*) - \{k\}\}$.
+Therefore, the infimum is the minimum of a finite number of projections onto closed convex sets.
+We have changed the ``inf'' to ``min'' and added an explanation in the paper to remove the confusion.
 
@@
 The square is not an error.
+We have a stronger requirement on the signal strength for the DC stage.
+This is because the $\hat{g}_k$'s are fitted onto the finite sample residual and thus, we need $\hat{f}$ to be close to $f^*$ in order to be able to prove something about the $\hat{g}_k$'s.
 

### 2015-04-30 tex/scam/sparsistency.tex
more response

@@
 \begin{align}
-\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
+\alpha_{+} &= \min_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
        \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
@@
 \end{align}
-$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$; $\alpha_+ > 0$ since $f^*$ is the unique risk minimizer.
+$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$.
+$\alpha_+$ is achieved by some $f \neq f^*$ because the set $\{f\in \mathcal{C}_1^p\,:\, \trm{supp}(f) \subsetneq \textrm{supp}(f^*)\}$ is a finite union of closed convex sets.
+$\alpha_+ > 0$ since $f^*$ is the unique risk minimizer.
 Likewise, $\alpha_-$ lower bounds the excess risk of any decoupled concave fit of the residual $f_0 - f^*$ that is strictly more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$; $\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well.
@@
 it is easier to make a false omission in the decoupled concave stage
-of the procedure.
+of the procedure. If $X$ is independent, then $\alpha_+$ can be simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and $\alpha_-$ becomes unnecessary.
 

### 2015-04-30 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
+To minimize predictive error, we can refit a non-additive convex function after selecting a sparse model.
+Comparing the predictive accuracy of $f^*_k$'s and $g^*_k$'s against the non-additive true regression function $f_0$ is beyond the scope of our paper, but we do compare the finite sample estimate $\hat{f}_k$ and $\hat{g}_k$ against the population level $f^*_k$ and $g^*_k$.
+The analysis we do to control false negatives also shows that $\mathbb{E}\left(\sum_{k=1}^p (f^*_k(X_k) - \hat{f}_k(X_k))\right)^2 \rightarrow 0$ and likewise for the DC stage.
+
 \item \rc{In order to improve clarity, the authors should define the convex
@@
 
-We are grateful to the reviewer for the detailed reading. We have corrected the mistakes found and further proof-read the paper. We discuss some of the issues raised.
+We are grateful to the reviewer for the detailed reading. We have corrected the mistakes found and further proof-read the paper. We discuss the nontrivial issues here.
 
@@
 \item \rc{On page 25, after the statement of Corollary 5.1 : I do not understand
-why ``$p = O(exp(n^c)$'' is written instead of ``$p = O(exp(cn)$.}
-\item \rc{On page 26, in the first paragraph ``the relevant variable set'' and
-in the third paragraph, ``seting''.}
+why ``$p = O(exp(n^c)$'' is written instead of ``$p = O(exp(cn)$''.}
+
+We have changed it to $\exp(cn)$.
+
+%\item \rc{On page 26, in the first paragraph ``the relevant variable set'' and
+%in the third paragraph, ``seting''.}
+
 \item \rc{I really did not understand what was represented in figures 5(a) and
@@
 notation $\|\cdot\|_{\infty,1}$ is not defined.}
-\item \rc{On page 31, at the top of the page, ``see discussion at beginning of
-Section 5'' : I think it should be ``at the beginning''. In (8.1),
-same problem as before with the indices : ``$\nu_{ki} d_{ki}$ `` must be replaced
-with ``$\nu_{ik}d_{ik}$'' (see for instance page 20). At the bottom of the page,
-$v_{ki}$ must be replaced by $\nu_{ki}$.}
+
+We have further explained the old figure 5a and 5b (now figure 7a and 7b) in the experiment section. The following has been added to the paper:
+
+...
+we plot on the y-axis the norm $\|f^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$.
+Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|f^{(t)}_j\|_{\infty}}{\sum_j \|f^{(1)}\|_{\infty}}$.
+Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.
+
+%\item \rc{On page 31, at the top of the page, ``see discussion at beginning of
+%Section 5'' : I think it should be ``at the beginning''. In (8.1),
+%same problem as before with the indices : ``$\nu_{ki} d_{ki}$ '' must be replaced
+%with ``$\nu_{ik}d_{ik}$'' (see for instance page 20). At the bottom of the page,
+%$v_{ki}$ must be replaced by $\nu_{ki}$.}
+
 \item \rc{On page 32, on the first line of the second paragraph, ``$d_k = 0 \mbox{for $k
@@
 of the proof, cf conditions on $d_k$).}
+
+We cannot move the third paragraph to the beginning because it is not clear at that point that $k$ is fixed.
+We have corrected all the notations before the third paragraph so that the notations are consistent.
+
 \item \rc{On page 33, I find that $[\lambda\Delta_k^Tu]_1 = \lambda((X_{kn} −X_{k1})\kappa$. ( If $\kappa$ is be defined
-in the following way : $\kappa =
-\frac{1}{\lambda_n(X_{kn}-X_{k1})}[\Delta_k^T u]_1$, then everything
+in the following way : $\kappa = \frac{1}{\lambda_n(X_{kn}-X_{k1})}[\Delta_k^T u]_1$, then everything
 goes well).}
 
-\item \rc{On page 33, on the second line, ``other rows of stationarity
-condition holds'' and in the third paragraph : ``following our strategy, We''.}
-\item \rc{On page 34, at the bottom of the page, the parentheses in the
-denominator of the fraction.}
+We have redefined $\kappa$.
+
+%\item \rc{On page 33, on the second line, ``other rows of stationarity
+%condition holds'' and in the third paragraph : ``following our strategy, We''.}
+
+%\item \rc{On page 34, at the bottom of the page, the parentheses in the
+%denominator of the fraction.}
+
 \item \rc{On page 35, in the third paragraph, ``as a function of $\nu$'' : it is
@@
 $\hat d'$.}
+
+We have corrected the expression. The sum has been replaced by a vector.
+
 \item \rc{On page 36, maybe it would be better to replace $d$ by $c$ here. Add
 ``for $k\in S^c$ after''to show that $\hat c_k =0$''.}
+
+We have replaced $d$ by $c$.
+
 \item \rc{On page 37, In the first paragraph, I do not understand why $p$ appears
@@
 the second line (and then 12 instead of 8 on the third line) .}
-\item \rc{on page 38, In the sixth paragraph, in the inequality, the sign
-should be $\leq$. In the eighth paragraph, $c''$ must be replaced by $c$. In
-the ninth paragraph, ``Taking an union''.}
-\item \rc{On page 40, on the fifth line, ``empricial''. In the last paragraph,
-``whose size is bounded'' : it is the log of the size.}
+
+We have removed mentions of $p$ here and corrected the constants.
+
+%\item \rc{on page 38, In the sixth paragraph, in the inequality, the sign
+%should be $\leq$. In the eighth paragraph, $c''$ must be replaced by $c$. In
+%the ninth paragraph, ``Taking an union''.}
+%\item \rc{On page 40, on the fifth line, ``empricial''. In the last paragraph,
+%``whose size is bounded'' : it is the log of the size.}
 
@@
 Corollary 8.4 for instance : $\epsilon$-bracketing with a size $N(2\epsilon,...)$)}
+
 \item \rc{On page 41, problem with $\epsilon$ (same as the previous item).}

### 2015-04-30 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
+We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5 because everything there is discussed again on page 6.
+
 \item \rc{Another notational comment: the use of the
@@
 already used to represent the dimensionality of the distribution.)}
+
+We sometimes need a notation for the distribution because we want to write $L^2(P), L_2(P)$ to represent, respectively, the Hilbert space of square integrable functions and the $L_2$-norm with respect to the distribution $P$.
+We have removed any mention of the distribution where it is not necessary.
+
+We have changed all ``F'' to ``P'' to represent the distribution, and, to avoid confusing the density with the dimensionality, we now write $p(x)$ instead of just $p$ whenever we refer to the density.
+We believe that this change, along with the context, are enough to disambiguate the two quantities.
 

### 2015-04-30 tex/scam/additive_faithful.tex
more responses

@@
 \label{lem:general_int_reduction}
-Let $F$ be a distribution on $C=[0,1]^p$ with a positive density
-function $p$. Let $f: C \rightarrow \R$ be in $L^2(F)$. Let
+Let $P$ be a distribution on $C=[0,1]^p$ with a positive density
+function $p(\mathbf{x})$. Let $f: C \rightarrow \R$ be in $L^2(P)$. Let
 \begin{align*}
@@
 \label{cor:product_int_reduction}
-Let $F$ be a product distribution on $C=[0,1]^p$ with density function
-$p$ which is positive on $C$. 
+Let $p(\mathbf{x})$ be a positive density on $C=[0,1]^p$.
 Let $\mu^*, f^*_k(x_k)$ be defined as in Lemma~\ref{lem:general_int_reduction}.
@@
 
-In addition, suppose we have a distribution over $C$ and the additive approximation
+In addition, suppose we have a distribution $P$ over $C$ and the additive approximation
 \begin{equation}
@@
 \end{equation}
-We say that $f$ is \textit{additively faithful} under $F$ if
+We say that $f$ is \textit{additively faithful} under $P$ if
 $f^*_k = 0$ implies that $f$ does not depend on coordinate $k$.
@@
 \label{thm:convex_faithful}
-Let $p$ be a positive density supported on $C=[0,1]^p$ that satisfies
+Let $p(\mathbf{x})$ be a positive density supported on $C=[0,1]^p$ that satisfies
 the boundary flatness property. 
-If $f$ is convex and continuously twice differentiable, then $f$ is additively faithful under $p$.
+If $f$ is convex and continuously twice differentiable, then $f$ is additively faithful under $p(\mathbf{x})$.
 \end{theorem}
@@
 $f''(x^0_k, \mathbf{x}_{-k}) \geq 0$. Since $p(\mathbf{x}_{-k} \given
-x^0_k) > 0$ by the assumption that $p$ is a positive density, 
+x^0_k) > 0$ by the assumption that $p(\mathbf{x})$ is a positive density, 
 we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.
@@
 In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components; the additive approximations may not be faithful if we take a parametric form.
-For example, suppose we approximate a convex function $f(X)$ by a linear form $X \beta$.
+For example, suppose we approximate a mean-zero convex function $f(X)$ by a linear form $X \beta$.
 The optimal linear function in the population setting is $\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma$ is the covariance matrix.

### 2015-04-30 tex/scam/sparsistency.tex
more responses

@@
 \begin{enumerate}
-\item The data $X^{(1)},\ldots, X^{(n)} \sim F$ are iid from
-a distribution $F$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-1,1]^p$.
+\item The data $X^{(1)},\ldots, X^{(n)} \sim P$ are iid from
+a distribution $P$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-1,1]^p$.
 \item The response is $Y = f_0(X) + W$ where $W$ is
@@
 \begin{equation}
-\lambda_n \leq 512 s \tilde{\sigma} \sqrt{\frac{\log^2 np}{n}}
+\lambda_n \leq 768 s \tilde{\sigma} \sqrt{\frac{\log^2 np}{n}}
 \end{equation}

### 2015-04-30 tex/scam/summary.tex
major paper revisions
more responses

@@
 $X_k$ and a scalar $x_k$, we use $\E[\,\cdot \given x_k]$ as a shorthand
-for $\E[\, \cdot \given X_k = x_k]$.
+for $\E[\, \cdot \given X_k = x_k]$. If we say a function is integrable, we 
+mean it is Lebesgue integrable.
 
@@
 This motivates us to consider an additive approximation. 
-Under a convex additive model, each component of the subgradient
-appears only in the convexity constraint for
-the corresponding variable:
-\begin{equation}
-f_{ki'} \geq f_{ki} + \beta_{ki}(x_{ki'}-x_{ki}) 
-\end{equation}
-where $f_{ki} = f_{k}(x_{ki})$ and $\beta_{ki}$ is the
-subgradient at point $x_{ki}$.   As we show, this leads to
+%Under a convex additive model, each component of the subgradient
+%appears only in the convexity constraint for
+%the corresponding variable:
+%\begin{equation}
+%f_{ki'} \geq f_{ki} + \beta_{ki}(x_{ki'}-x_{ki}) 
+%\end{equation}
+%where $f_{ki} = f_{k}(x_{ki})$ and $\beta_{ki}$ is the
+%subgradient at point $x_{ki}$.   
+As we show, this leads to
 an effective variable selection procedure.  The
@@
 \begin{stheorem}
-  Let $p$ be a positive density supported on $C=[0,1]^p$ that
+  Let $p(\mathbf{x})$ be a positive density supported on $C=[0,1]^p$ that
   satisfies the boundary flatness property. If $f$ is convex and twice
@@
 g^*_k = \arg\min_{g_k} \Big\{ \E\Bigl( f(X) - \mu^* - 
-\sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k \Bigr)^2 \,:\, g_k \in \mh
+\sum_{k' \neq k} f^*_{k'}(X_{k'}) - g_k(X_k) \Bigr)^2 \,:\, g_k \in \mh
 \mathcal{C}^1, \E g_k(X_k) = 0 \Big\},

### 2015-04-30 tex/scam/supplement.tex
more responses

@@
 
-Let $P$ be the probability measure induced by the density $p$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure.
+Let $P$ be the probability measure induced by the density $p(\mathbf{x})$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure.
 Since $p > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well.

### 2015-05-01 tex/scam/reviews-v1/response-v1.tex
boundary flat

@@
 Smoothness can be incorporated by using B-spline basis with uniformly spaced knots.
-The details are described in a paper by Pya and Wood which we cited.
-We chose not to discuss estimating smooth convex functions because it would introduce an additional tuning parameter, which negates some of the advantages of doing shape-constrained estimation.
+The details are described in a 2014 paper by Pya and Wood which we have cited in the introduction.
+We chose not to discuss estimating smooth convex functions because it would introduce an additional tuning parameter.
+
+The analysis may require much more work if one uses a B-spline basis in the estimation.
+B-splines may significantly complicate the false positive analysis, which rely on the particular form of the optimization.
+The false negative analysis may not be affected much because it mainly uses bracketing entropy.
 
@@
 
+We have made the suggested modifications except for the one in the second sentence.
+The $B$-boundedness condition is used in both Theorem 5.2 and Theorem 5.3.
+It is relied upon critically in Theorem 5.3 and used for convenience in Theorem 5.2.
+
 \item \rc{At the top
@@
 in this case? }
+
+The conditions in Theorem 5.1 are indeed analogous and we have edited the remark accordingly. The conditions in Theorem 5.1 are much more strict than the mutual incoherence condition though.
 

### 2015-05-01 tex/scam/additive_faithful.tex
boundary flat

@@
 characterize below, convex multivariate functions are additively
-faithful.
+faithful. To simplify presentation, we restrict our attention to densities bounded away from $0/\infty$, that is, $p(\mathbf{x})$ such that $0 < \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) < \infty$.
 
@@
 \label{defn:boundary-point}
-Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. $p(\mathbf{x})$ satisfies
-the \emph{boundary flatness condition} if $0 < \inf_{\mathbf{x}} p(\mathbf{x}) \leq \sup_{\mathbf{x}} p(\mathbf{x}) < \infty$, and for all $j$, there exists some $\epsilon > 0$ such that for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
+Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.
+We say that $p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if for all $j$, there exists some $\epsilon > 0$ such that for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
 \begin{equation}
@@
 
-The boundary flatness condition intuitively states that
-the conditional effect of $X_k$ weakens as $\mathbf{x}$ approaches the boundary.
-It is a weak condition because it affects only an $\epsilon$-small region around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from the boundary; it can induce arbitrary correlation structure (provided $p(\mathbf{x}) >0$) and need not be continuous.
-Before presenting the main theorem, let us see some examples of boundary flat distributions.
-
-\begin{example} The following densities satisfy boundary flatness.
-\begin{enumerate}
-\item If $\mathbf{p}$ is a product density, then boundary flatness is trivially
-satisfied.
-\item Let $p(\mathbf{x})$ be a joint density such that $0 < \inf_{\mathbf{x}} p(\mathbf{x}) \leq \sup_{\mathbf{x}} p(\mathbf{x}) < \infty$.
-Suppose $p(\mathbf{x})$ has a bounded second derivative for all $\mathbf{x}$.
-If, for all $j$,
-$\partial_{x_j} p(x_j,\mathbf{x}_{-j}) =
-\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0$ at $x_j = 0, 1$.
-Then it is possible to show that the two derivatives of $p(\mathbf{x}_{-j} \given x_j) = \frac{p(x_j, \mathbf{x}_{-j})}{p(x_j)}$ are 0 at $x_j = 0,1$; boundary flatness thus holds.
-\item Suppose $p(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
-Let $q(\mathbf{x})$ be a boundary flat density over $[0,1]^p$, take the uniform distribution for instance.
-Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
-Furthermore, $\epsilon$ and $\lambda$ can be made arbitrarily small and therefore, any bounded density over a hypercube can be approximated arbitrarily well by a boundary flat distribution.
-
-% $$
-% p'(\mathbf{x}_{-j} \given x_j) = \frac{ p(x_j, \mathbf{x}_{-j}) p'(x_j) - 
-%    p'(x_j, \mathbf{x}_{-j}) p(x_j)}{ p(x_j)^2 } = 0 
-% $$
-% \begin{align*}
-% p''(\mathbf{x}_{-j} \given x_j) = &
-%     \frac{ p(x_j)^2 \left( p(x_j, x_{-j}) p''(x_j) - p''(x_j, x_{-j}) p(x_j) \right) - 2p(x_j)p'(x_j) \left(p(x_j, x_{-j})p'(x_j) - p'(x_j, x_{-j}) p(x_j)  \right) }{p(x_j)^4}
-%  \end{align*}
-\end{enumerate}
-\end{example}
+The boundary flatness condition intuitively states that two conditional densities $p(\mathbf{x}_{-j} \given x_j)$ and $p(\mathbf{x}_{-j} \given x_j')$ are similar when $x_j$ and $x_j'$ are both close to $0$ or both close to $1$.
+Product densities satisfy boundary flatness trivially.
+Boundary flatness is a weak condition because it affects only an $\epsilon$-small region around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from the boundary.
+Boundary flatness also allows arbitrary correlation structure between the variables (provided $p(\mathbf{x}) >0$).
+In Section~\ref{sec:boundary_flat}, we give a detailed discussion of the boundary flatness condition and show many examples of boundary flat distributions; in particular, we show that any distribution supported on a compact set can be approximated arbitrarily well by boundary flat distributions.
 
@@
 \label{thm:convex_faithful}
-Let $p(\mathbf{x})$ be a positive density supported on $C=[0,1]^p$ that satisfies
+Let $p(\mathbf{x})$ be a density supported on $C=[0,1]^p$ and bounded away from $0/\infty$ that satisfies
 the boundary flatness property. 
@@
 
-\begin{remark}
-It is possible to get a similar result for distributions with
+\subsection{Boundary Flatness Examples}
+\label{sec:boundary_flat}
+
+In this section, we give more examples of boundary flat densities (see Definition~\ref{defn:boundary-point}) and discuss extending the notion of boundary flatness to densities with a more general support.
+We first start with an sufficient condition on the \emph{joint density} that ensures boundary flatness.
+
+\begin{example}
+\label{ex:joint_density_flat}
+Boundary flatness is satisfied if the joint density becomes flat at the boundary.
+To be precise, let $p(\mathbf{x})$ be a joint density bounded away from $0/\infty$.
+Suppose, for all $j$,  $\partial_{x_j} p(x_j, \mathbf{x}_{-j})$ and $\partial^2_{x_j} p(x_j, \mathbf{x}_{-j})$ exist and are bounded for all $\mathbf{x}_{-j}$ and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$ for some $\epsilon >0$.
+
+Suppose also, for all $j$,
+$$
+\partial_{x_j} p(x_j,\mathbf{x}_{-j}) =
+\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0\quad  \trm{at $x_j = 0, 1$,}
+$$
+then it is straightforward to show that $\partial_{x_j} p(\mathbf{x}_{-j} \given x_j) = \partial_{x_j}^2 p(\mathbf{x}_{-j} \given x_j) = 0$ at $x_j = 0,1$ as well.
+One need only see that the derivatives of the marginal densities are zero at the boundary and apply the quotient rule.
+\end{example}
+
+The next example shows that any bounded density over a hypercube can be approximated arbitrarily well by some boundary flat distributions.
+
+\begin{example}
+\label{ex:mixture_approx}
+Suppose $p(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
+Let $q(\mathbf{x})$ be a boundary flat density over $[0,1]^p$.
+Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
+Furthermore, $\epsilon$ and $\lambda$ can be made arbitrarily small and therefore, $p(\mathbf{x})$ can be approximated arbitrarily well (in $L_1$ for example) by a boundary flat distribution.
+\end{example}
+
+The result in Example~\ref{ex:joint_density_flat} further shows that boundary flat densities can arise from monotone marginal transformations of more general random vectors.
+This gives another way of approximating general densities by boundary flat densities.
+
+\begin{example}
+Let $X = (X_1,...,X_p)$ be drawn from a density supported on $[0,1]^p$, bounded away from $0/\infty$, and with a bounded second derivative.
+Let $\phi : [0,1] \rightarrow [0,1]$ be a monotonically increasing transformation.
+We will show that under certain conditions on $\phi$, the density of $(\phi(X_1), ..., \phi(X_p))$ is boundary flat.
+
+Suppose $\phi^{-1}$ has a bounded third derivative on some neighborhood around the boundary, say $[0, \epsilon) \cup (1-\epsilon, 1]$ and suppose $\phi^{-1\prime}(z) = \phi^{-1\prime\prime}(z) = \phi^{-1\prime\prime\prime}(z) = 0$ at $z=0,1$.
+
+Then, the density $p(z_1,...,z_p)$ of the transformed variables $z_j = \phi(x_j)$ is 
+$$ 
+p(z_1,...,z_p) = p_X(\phi^{-1}(z_1), ..., \phi^{-1}(z_p)) \prod_{j=1}^p \phi^{-1\prime}(z_j),
+$$ where $p_X(\cdot,...,\cdot)$ is the density of $X$.
+One can use the product rule and the chain rule to differentiate $p(z_1,...,z_p)$ and verify that $\partial_{z_j} p(\mathbf{z}) = \partial^2_{z_j} p(\mathbf{z}) = 0$ at $z_j = 0,1$ and thus show that $p(z_1,...,z_p)$ satisfies boundary flatness by Example~\ref{ex:joint_density_flat}.
+
+As a concrete example, we can use the following transformation $\phi_\epsilon$, defined in term of its inverse:
+$$\phi_\epsilon^{-1}(z) = \left\{ \begin{array}{cc} z^4 & \trm{if $z \leq \epsilon$} \\ 
+                     \frac{1-2\epsilon^4}{1-2\epsilon} z - \frac{ \epsilon + \epsilon^4}{1-2\epsilon} & \trm{if $\epsilon \leq z \leq 1-\epsilon$} \\
+                      1-(1-z)^4 & \trm{if $z \geq 1-\epsilon$} \end{array} \right.$$
+for any $1/2 > \epsilon > 0$.
+As $\epsilon$ becomes small, $\phi_\epsilon$ becomes close to the identity and so $(\phi_\epsilon(X_1), ..., \phi_\epsilon(X_p))$ closely approximates the original random variable $(X_1,...,X_p)$.
+Intuitively, $\phi$ stretches $X$ near the boundary so that changes in the transformed variable $z$ near the boundary corresponds to much smaller change in original variable $x$.
+\end{example}
+
+In our discussion so far, we have restricted ourselves to densities supported and positive on the hypercube $[0,1]^p$ to minimize extraneous technical details.
+It may be possible to extend the analysis to densities whose support is a convex and compact set so long as the marginal density $p(x_j) > 0$ for all $x_j$ in the support.
+
+It may also possible to extend similar result to densities with an
 unbounded support, by using a limit condition $\lim_{|x_k| \rightarrow
   \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}
-= 0$.
-Such a limit condition however is not obeyed by many common distributions such as the multivariate Gaussian distribution.
+= 0$.  Such a limit condition however is not obeyed by a correlated multivariate Gaussian distribution. 
 The next example shows that certain convex functions are not additively faithful under certain multivariate Gaussian distributions.
-\end{remark}
 
@@
 Although the Gaussian distribution does not satisfy the boundary flatness condition, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary flatness conditions.
+We use the similar idea as that of Example~\ref{ex:mixture_approx}.
 
@@
 \label{thm:acdc_faithful}
-Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ that
+Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ that
 satisfies the boundary flatness condition. Suppose that $f$ is convex
@@
 \label{cor:faithfulness_extension}
-Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ satisfying the boundary flatness condition.
+Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ satisfying the boundary flatness condition.
 Let $f(\mathbf{x})$ be a convex and continuously twice differentiable function on $C$.

### 2015-05-01 tex/scam/experiments.tex
boundary flat

@@
 
-The purpose of the simulations is to see how the probability of variable selection scales with the number of samples $n$, the ambient dimension $p$, and the sparsity level $s$.
-We study both the independent case where $P = N(0, I_p)$ and the correlated case where $P$ is a correlated Gaussian Copula modified slightly to satisfy boundary flatness.
+We study both the independent case where $P = N(0, I_p)$ and the correlated case where $P$ is a correlated Gaussian Copula modified slightly to satisfy the boundary flatness condition.
 We measure the probability of exact selection in the independent case and the probability of screening in the correlated case.
@@
 
-In the third and fourth simulation, we use a correlated design.
+In the third, fourth, and fifth simulation, we use a correlated design.
 We generate $X$ from a non-Gaussian boundary flat distribution with covariance $\Sigma$.
@@
 
-In the fourth, fifth, and sixth simulation, we use a softmax function as the ground truth
-\[
+In the fourth and fifth simulation, we use a softmax function as the ground truth
+\begin{align}
 f_0(x_{iS}) = \log \left( \sum_{k=1}^K \exp( \beta_k^\tran x_{iS} ) \right) - \mu
-\]
+\end{align}
 We generate random unit vectors as $\{\beta_k \in \R^s\}_{k=1,...,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
@@
 
-For the \textbf{fifth experiment} (Figure~\ref{Support}h), we vary the true sparsity level $s$.
+%For the \textbf{fifth experiment} (Figure~\ref{Support}h), we vary the true sparsity level $s$.
 We let $f_0$ be the softmax function, $X \sim N(0, I)$, and set $p=128$.
@@
 
-For the \textbf{sixth experiment} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
+For the \textbf{fifth simulation} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
 We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.
@@
 (e) recovered support size for $\nu=0.5$ in (d) & (f) softmax $f_0$, correlated $X$, varying $p$ \\
-\includegraphics[width=0.42\textwidth]{figs/S_support_box} & \\
-(g) recovered support size for $p=256$ in (f) & (h) softmax $f_0$, correlated $X$, varying $s$ 
+%\includegraphics[width=0.42\textwidth]{figs/S_support_box} & \\
+%(g) recovered support size for $p=256$ in (f) & (h) softmax $f_0$, correlated $X$, varying $s$ 
 \end{tabular}
 \end{center}
-\caption{Support recovery results where the additive assumption is
-  correct (a), incorrect (b), (c), and with correlated design (d).}\label{Support}
+\caption{Support recovery results.}
+\label{Support}
 \vskip10pt

### 2015-05-01 tex/scam/sparsistency.tex
boundary flat

@@
 In our analysis, we assume that an upper bound $B$ to $\| \hat{f}_k \|_\infty$ 
-is imposed in the optimization procedure, where $B$ is chosen to also upper bound $\| f^*_k \|_\infty$.
+is imposed in the optimization procedure, where $B$ is chosen to also upper bound $\| f^*_k \|_\infty$ (same $B$ as in Assumption A3 in Section~\ref{sec:probabilistic_setting}).
 This $B$-boundedness constraint is added so that we may use the convex function bracketing results from~\cite{kim2014global} to establish uniform convergence between the empirical risk and the population risk.
@@
 rates and false positive rates. To control false positives,
-we analyze the condition on $\lambda_n$ for $k \in S^c$. To control
-false negatives, we need only analyze the restricted regression with only $|S|$ variables.
+Theorem~\ref{thm:false_positive} verifies that the conditions in Theorem~\ref{thm:deterministic} hold in a stochastic setting. To control
+false negatives, Theorem~\ref{thm:false_negative} analyzes the restricted regression with only $|S|$ variables.
 
@@
 the now standard \emph{primal-dual witness}
-technique~\citep{wainwright2009sharp}. However, we cannot derive analogous
-\emph{mutual incoherence} conditions because the estimation is
+technique~\citep{wainwright2009sharp}.
+The conditions in Theorem~\ref{thm:deterministic} is our analogue to the \emph{mutual incoherence} condition.
+Our conditions are much more strict however because the estimation is
 nonparametric---even the low dimensional restricted regression has
-$s(n-1)$ variables. The details of the proof are given in
+$s(n-1)$ variables.
+
+The details of the proof are given in
 Section~\ref{sec:deterministic_proof} of the Appendix.
@@
 \subsection{Probabilistic Setting}
+\label{sec:probabilistic_setting}
 
@@
 Suppose assumptions A1-A5 hold.
-Define $\tilde{\sigma} \equiv \max(\sigma, B)$ and define $\mathsf{range}_k = X_{k \pi_k(n)} - X_{k \pi_k(1)}$.
+Define $\tilde{\sigma} \equiv \max(\sigma, B)$ and define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.
 Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $0 < c <1$ and $C$.
@@
 \begin{equation}
-\lambda_n \geq 512 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
+\lambda_n \geq 768 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
 \end{equation}  
@@
 \end{equation}
-$\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$, $\mathsf{range}_k \geq 1$, and both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero.
+$\max_{i'} \frac{X_{\pi_k(i'+1)k} - X_{\pi_k(i')k}}{\mathsf{range}_k} \leq \frac{1}{16}$, $\mathsf{range}_k \geq 1$, and both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero.
 \end{theorem}

### 2015-05-01 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
+We have added an additional simulation comparing the variables selected via the AC stage and the DC stage.
+Please see the last paragraph in Section 6.1 as well as Figure 6.
+The DC stage is slightly helpful in recovering the true variables but its effect is insignificant.
+We believe that the DC stage is important in theory but not so in practice.
+
 Minor typos:
@@
 
+We indeed need a bounded condition here.
 We have modified the definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$ is bounded and has a bounded first and second derivative for all $x_j$ in some open set around the boundary points and for all $\mathbf{x}_{-j}$.
 Dominated convergenc theorem holds without problems because we only exchange the derivative and the integral at $x_j = 0,1$.
-Just to make sure, we have verified in detail that the domination condition holds in the newly added Section 8.3.4.
+We have verified in detail that the domination condition holds in the newly added Section 8.4.1.
 
@@
 
-\item \rc{On page 41, problem with $\epsilon$ (same as the previous item).}
+We have corrected this problem by replacing all instances of $N(2\epsilon,...)$ with $N(\epsilon, ...)$ and updating the bound for $\log N(...)$ accordingly.
+
+%\item \rc{On page 41, problem with $\epsilon$ (same as the previous item).}
 \item \rc{On page 40, I think the functions in $G$ are bounded by $2sB$ (not $sB$.).}
+
+This has been noted and corrected across the proofs.
+
 \item \rc{On page 49, in Definition 8.1, $f^U$ and $f^L$ must be replaced by $f_U$ and
@@
 components'' : add ``components bounded by $B$''.}
+
+We have corrected the instances in which we erroneously omitted ``... components bounded by $B$''.
+
 \item \rc{On page 49, ``$\int p(x)^2dx \leq (\int p(x)dx)^2$ ``??}
-\item \rc{On page 50, a constant 2 is missing in $\epsilon_n$.}
+
+We have corrected this mistake by placing an upper bound $c_u$ on the density $p(\mathbf{x})$ and incorporating that upper bound into this derivation.
+We now use the correct bound $\sqrt{ \int p(x)^2 dx } \leq c_u$.
+
+%\item \rc{On page 50, a constant 2 is missing in $\epsilon_n$.}
 \item \rc{On page 41, in the second paragraph, I think the bound on $\sup_{h_L} |⟨w,h_L⟩_n|$ is
@@
 $2\sigma s B$. It gives a bound of order $sB\sigma \sqrt{\frac{\log\frac{2}{\delta}}{n}}$.}
+
+We have updated this derivation.
+
 \item \rc{The term $\epsilon$ supposed to balance the two terms is not correct (for
@@
 calculations. In particular, the exponent in $s$ is not the right one.}
+
+The $\epsilon$ we choose is sufficient to get the bounds we want but it does not exactly balance the terms.
+We left dependence on $\delta$ out of the $\epsilon$ intentionally because we need to verify that $\epsilon$ satisfies certain conditions, see Equation (8.12) for instance.
+These conditions are much easier to verify if $\epsilon$ does not depend on $\delta$, which we set to be $1/n$ only at the end.
+We have updated the paper to clearly state that we use a suboptimal $\epsilon$.
+
 \item \rc{In the proof of Theorem 8.4 : too many small mistakes in
 calculations, but the final result is OK.}
+
+TODO
+
 \item \rc{On page 45, the term $\epsilon$ supposed to balance the terms is not correct
@@
 of the page) $n$ is missing in one of the scalar products.}
-\item \rc{On page 46: ``taking a union bound and we have that''}
+
+We also use a suboptimal $\epsilon$ here for convenience. We have updated the paper to clearly state that.
+
+%\item \rc{On page 46: ``taking a union bound and we have that''}
 \item \rc{In Lemma 8.3, I do not see why the functions are continuous : the
 functions $x_{-k} \rightarrow p(x_{-k} | x_k)$ are not supposed to be continuous .}
+
+The old Lemma 8.3 has been removed.
+We now just need $x_{-k} \rightarrow p(x_{-k} \,|\, x_k)$ to be bounded, which has been added as a condition.
+(We now assume for convenience that the joint density $p(\mathbf{x})$ be bounded away from 0 and $\infty$.)
+
 \item \rc{On page 47, in the proof of Lemma 8.4 : notation $\phi_{-j}$
@@
 In the definition of $A_+$, the sign should be $>$, not $\geq$. Remove ``both'' .}
-\item \rc{On page 47, ``a sub-exponential random is''.}
+
+The old Lemma 8.4 (now Lemma 8.3) has been updated.
+
+%\item \rc{On page 47, ``a sub-exponential random is''.}
 

### 2015-05-01 tex/scam/additive_faithful.tex
more responses

@@
 Boundary flatness also allows arbitrary correlation structure between the variables (provided $p(\mathbf{x}) >0$).
-In Section~\ref{sec:boundary_flat}, we give a detailed discussion of the boundary flatness condition and show many examples of boundary flat distributions; in particular, we show that any distribution supported on a compact set can be approximated arbitrarily well by boundary flat distributions.
+In Section~\ref{sec:boundary_flat}, we give a detailed discussion of the boundary flatness condition and show examples of boundary flat densities; in particular, we show that any density supported on a compact set can be approximated arbitrarily well by boundary flat densities.
 
@@
 \label{thm:convex_faithful}
-Let $p(\mathbf{x})$ be a density supported on $C=[0,1]^p$ and bounded away from $0/\infty$ that satisfies
-the boundary flatness property. 
-If $f$ is convex and continuously twice differentiable, then $f$ is additively faithful under $p(\mathbf{x})$.
+Let $p(\mathbf{x})$ be a density supported on $C=[0,1]^p$ and bounded away from $0/\infty$ that satisfies the boundary flatness property.
+
+Suppose $f$ is a convex and continuously twice differentiable on an open set containing $C$, then $f$ is additively faithful under $p(\mathbf{x})$.
 \end{theorem}
+
+We let the domain of $f$ be slightly larger than $C$ for a technical reason--it is so we can say in the proof that the Hessian of $f$ is positive semidefinite even at the boundary of $C$.
 
@@
 \label{ex:joint_density_flat}
-Boundary flatness is satisfied if the joint density becomes flat at the boundary.
-To be precise, let $p(\mathbf{x})$ be a joint density bounded away from $0/\infty$.
-Suppose, for all $j$,  $\partial_{x_j} p(x_j, \mathbf{x}_{-j})$ and $\partial^2_{x_j} p(x_j, \mathbf{x}_{-j})$ exist and are bounded for all $\mathbf{x}_{-j}$ and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$ for some $\epsilon >0$.
+Boundary flatness is satisfied if the joint density becomes flat at the boundary. To be precise, let $p(\mathbf{x})$ be a joint density bounded away from $0/\infty$ with a bounded second derivative.
 
@@
 \partial_{x_j} p(x_j,\mathbf{x}_{-j}) =
-\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0\quad  \trm{at $x_j = 0, 1$,}
+\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0\quad  \trm{at $x_j = 0, 1$,}.
 $$
-then it is straightforward to show that $\partial_{x_j} p(\mathbf{x}_{-j} \given x_j) = \partial_{x_j}^2 p(\mathbf{x}_{-j} \given x_j) = 0$ at $x_j = 0,1$ as well.
-One need only see that the derivatives of the marginal densities are zero at the boundary and apply the quotient rule.
+It is then straightforward to show boundary flatness.
+One can first verify that the derivatives of the marginal density $p(x_j)$ vanishes at $x_j = 0,1$ and then apply the quotient rule on $\frac{p(x_j,\mathbf{x}_{-j}}{p(x_j)}$ to show that $\partial_{x_j} p(\mathbf{x}_{-j} \given x_j) = \partial_{x_j}^2 p(\mathbf{x}_{-j} \given x_j) = 0$ at $x_j = 0,1$ as well.
 \end{example}
 
-The next example shows that any bounded density over a hypercube can be approximated arbitrarily well by some boundary flat distributions.
+The next example shows that any bounded density over a hypercube can be approximated arbitrarily well by boundary flat densities.
 
@@
 \label{ex:mixture_approx}
-Suppose $p(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
-Let $q(\mathbf{x})$ be a boundary flat density over $[0,1]^p$.
-Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
-Furthermore, $\epsilon$ and $\lambda$ can be made arbitrarily small and therefore, $p(\mathbf{x})$ can be approximated arbitrarily well (in $L_1$ for example) by a boundary flat distribution.
+Suppose $p_\epsilon(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
+Let $q(\mathbf{x})$ be an arbitrary boundary flat density over $[0,1]^p$ (one can take the uniform density for instance).
+Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p_\epsilon(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
+
+Now, let $p(\mathbf{x})$ be a bounded density over $[0,1]^p$.
+Let $p_\epsilon(\mathbf{x})$ be the density formed from truncating $p(\mathbf{x})$ in $[\epsilon, 1-\epsilon]^p$.
+The corresponding mixture $p_{\lambda,\epsilon}(\mathbf{x})$ then approximates $p(\mathbf{x})$ when $\lambda$ and $\epsilon$ are both small.
+
+Since $p_{\lambda,\epsilon}(\mathbf{x})$ remains boundary flat for arbitrarily small $\epsilon$ and $\lambda$, $p(\mathbf{x})$ can be approximated arbitrarily well (in $L_1$ for example) by boundary flat densities.
 \end{example}
 
-The result in Example~\ref{ex:joint_density_flat} further shows that boundary flat densities can arise from monotone marginal transformations of more general random vectors.
+% The result in Example~\ref{ex:joint_density_flat} further shows that boundary flat densities can arise from monotone marginal transformations of more general random vectors.
 This gives another way of approximating general densities by boundary flat densities.
 
-\begin{example}
-Let $X = (X_1,...,X_p)$ be drawn from a density supported on $[0,1]^p$, bounded away from $0/\infty$, and with a bounded second derivative.
+% \begin{example}
+% Let $X = (X_1,...,X_p)$ be drawn from a density supported on $[0,1]^p$, bounded away from $0/\infty$, and with a bounded second derivative.
 Let $\phi : [0,1] \rightarrow [0,1]$ be a monotonically increasing transformation.
@@
 
-Suppose $\phi^{-1}$ has a bounded third derivative on some neighborhood around the boundary, say $[0, \epsilon) \cup (1-\epsilon, 1]$ and suppose $\phi^{-1\prime}(z) = \phi^{-1\prime\prime}(z) = \phi^{-1\prime\prime\prime}(z) = 0$ at $z=0,1$.
+% Suppose $\phi^{-1}$ has a bounded third derivative on some neighborhood around the boundary, say $[0, \epsilon) \cup (1-\epsilon, 1]$ and suppose $\phi^{-1\prime}(z) = \phi^{-1\prime\prime}(z) = \phi^{-1\prime\prime\prime}(z) = 0$ at $z=0,1$.
 
-Then, the density $p(z_1,...,z_p)$ of the transformed variables $z_j = \phi(x_j)$ is 
-$$ 
-p(z_1,...,z_p) = p_X(\phi^{-1}(z_1), ..., \phi^{-1}(z_p)) \prod_{j=1}^p \phi^{-1\prime}(z_j),
-$$ where $p_X(\cdot,...,\cdot)$ is the density of $X$.
-One can use the product rule and the chain rule to differentiate $p(z_1,...,z_p)$ and verify that $\partial_{z_j} p(\mathbf{z}) = \partial^2_{z_j} p(\mathbf{z}) = 0$ at $z_j = 0,1$ and thus show that $p(z_1,...,z_p)$ satisfies boundary flatness by Example~\ref{ex:joint_density_flat}.
+% Then, the density $p(z_1,...,z_p)$ of the transformed variables $z_j = \phi(x_j)$ is 
+% $$ 
+% p(z_1,...,z_p) = p_X(\phi^{-1}(z_1), ..., \phi^{-1}(z_p)) \prod_{j=1}^p \phi^{-1\prime}(z_j),
+% $$ where $p_X(\cdot,...,\cdot)$ is the density of $X$.
+% One can use the product rule and the chain rule to differentiate $p(z_1,...,z_p)$ and verify that $\partial_{z_j} p(\mathbf{z}) = \partial^2_{z_j} p(\mathbf{z}) = 0$ at $z_j = 0,1$ and thus show that $p(z_1,...,z_p)$ satisfies boundary flatness by Example~\ref{ex:joint_density_flat}.
 
-As a concrete example, we can use the following transformation $\phi_\epsilon$, defined in term of its inverse:
-$$\phi_\epsilon^{-1}(z) = \left\{ \begin{array}{cc} z^4 & \trm{if $z \leq \epsilon$} \\ 
-                     \frac{1-2\epsilon^4}{1-2\epsilon} z - \frac{ \epsilon + \epsilon^4}{1-2\epsilon} & \trm{if $\epsilon \leq z \leq 1-\epsilon$} \\
-                      1-(1-z)^4 & \trm{if $z \geq 1-\epsilon$} \end{array} \right.$$
-for any $1/2 > \epsilon > 0$.
-As $\epsilon$ becomes small, $\phi_\epsilon$ becomes close to the identity and so $(\phi_\epsilon(X_1), ..., \phi_\epsilon(X_p))$ closely approximates the original random variable $(X_1,...,X_p)$.
-Intuitively, $\phi$ stretches $X$ near the boundary so that changes in the transformed variable $z$ near the boundary corresponds to much smaller change in original variable $x$.
-\end{example}
+% As a concrete example, we can use the following transformation $\phi_\epsilon$, defined in term of its inverse:
+% $$\phi_\epsilon^{-1}(z) = \left\{ \begin{array}{cc} z^4 & \trm{if $z \leq \epsilon$} \\ 
+%                      \frac{1-2\epsilon^4}{1-2\epsilon} z - \frac{ \epsilon + \epsilon^4}{1-2\epsilon} & \trm{if $\epsilon \leq z \leq 1-\epsilon$} \\
+%                       1-(1-z)^4 & \trm{if $z \geq 1-\epsilon$} \end{array} \right.$$
+% for any $1/2 > \epsilon > 0$.
+As $\epsilon$ becomes small, $\phi_\epsilon$ becomes close to the identity and so $(\phi_\epsilon(X_1), ..., \phi_\epsilon(X_p))$ closely approximates the original random variables $(X_1,...,X_p)$.
+Intuitively, $\phi$ stretches $X$ near the boundary so that a change in the transformed variable $z$ near the boundary corresponds to a much smaller change in original variable $x$.
+% \end{example}
 
@@
 Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ that
-satisfies the boundary flatness condition. Suppose that $f$ is convex
-and continuously twice differentiable. Let $f^*_k$ and $g^*_k$ be as defined in equations
+satisfies the boundary flatness condition. Suppose that $f$ is convex and continuously twice differentiable on an open set around $C$. Let $f^*_k$ and $g^*_k$ be as defined in equations
 \eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, 
@@
 Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ satisfying the boundary flatness condition.
-Let $f(\mathbf{x})$ be a convex and continuously twice differentiable function on $C$.
+Let $f(\mathbf{x})$ be a convex and continuously twice differentiable function on an open set around $C$.
 Let $\phi(\mathbf{x}_{-k})$ be a bounded function that does not depend on $x_k$.

### 2015-05-01 tex/scam/sparsistency.tex
more responses

@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
+\item[A2:] $f_0$ is convex and continuously twice-differentiable on an open set around $[-1,1]^p$. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
 \item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
-\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition. (Definition~\ref{defn:boundary-point})
+\item[A5:] The density $p(\mathbf{x})$ satisfies the boundary flatness condition (Definition~\ref{defn:boundary-point}), and $0 < c_l \leq \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) \leq c_u < \infty$ for two constants $c_l, c_u$.
 \end{packed_enum}
@@
 Define $\tilde{\sigma} \equiv \max(\sigma, B)$ and define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.
-Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $0 < c <1$ and $C$.
+Suppose $p \leq O\big( \exp(c n) \big)$ and $n \geq C$ for some positive constants $C$ and $0 < c < \frac{c_l}{32}$.
 Suppose also
@@
 \frac{\alpha_{+}}{\tilde{\sigma}} & \geq c B^2
-\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}\\
+\sqrt{\frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np}\\
 \frac{\alpha_{-}^2}{\tilde{\sigma}} &\geq c B^2
-\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}
+\sqrt{\frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np}
 \end{align}

### 2015-05-01 tex/scam/summary.tex
more responses

@@
   Let $p(\mathbf{x})$ be a positive density supported on $C=[0,1]^p$ that
-  satisfies the boundary flatness property. If $f$ is convex and twice
-  differentiable, then $f$ is additively faithful under $p$.
+  satisfies the boundary flatness property. If $f$ is convex and continuously twice
+  differentiable on an open set around $C$, then $f$ is additively faithful under $p$.
 \end{stheorem}
@@
 density on $C=[0,1]^p$ that satisfies the boundary flatness
-condition. Suppose that $f$ is convex and twice-differentiable.
+condition. Suppose that $f$ is convex and continuously twice-differentiable on an open set around $C$.
 and that $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k}
@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
+\item[A2:] $f_0$ is convex and continuously twice-differentiable. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \| \leq B$ for all $k$.

### 2015-05-01 tex/scam/supplement.tex
more responses

@@
 
-$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$.
-Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c) n) \leq \frac{12}{n}$.
+$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ where $c' = -\log(1-\frac{c_l}{32}) > \frac{c_l}{32}$ since $c_l < 1$.
+Therefore, if $p \leq exp( c n)$ for some $0<c < \frac{c_l}{32}$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c) n) \leq \frac{12}{n}$.
 
@@
 
-% \subsection{Supporting Technical Material}
+\subsection{Supporting Technical Material}
+
 \subsubsection{Detail for Proof of Theorem~\ref{thm:convex_faithful}} 
@@
 
+\subsubsection{Uniqueness of the Additive Components}
+
 \begin{lemma}

### 2015-05-02 tex/scam/summary.tex
more responses

@@
 
-In Section~\ref{sec:optimization} we present optimization algorithms for the additive convex regression stage.
+Given samples $(y_i, X_i)$, AC/DC becomes the following optimization.
+\begin{align*}
+\{\hat{f}_k\}_{k=1}^p &= \arg\min_{\{f_k \in \mathcal{C}^1\}} \frac{1}{n}\sum_{i=1}^n \left(
+        y_i - \bar{y} - \sum_{k=1}^p f_k(X_{ik}) \right)^2 + \lambda \sum_{k=1}^p \| f_k \|_\infty \\
+\forall k, \, \hat{g}_k &= \arg\min_{g_k \in \mathcal{C}^1} \frac{1}{n} \sum_{i=1}^n \left(
+    y_i - \bar{y} - \sum_{k' \neq k} \hat{f}_{k'}(X_{ik'}) - g_k(X_{ik}) \right)^2 + \lambda \| g_k \|_\infty
+\end{align*}
+where $\bar{y}$ is the empirical mean of $y$. Our estimate of the relevant variables is $\hat{S} = \{ k \,:\, \| \hat{f}_k \| > 0 \trm{ or } \| \hat{g}_k \| > 0\}$.
+
+We present the optimization algorithms in Section~\ref{sec:optimization}.
 The convex constraints for the additive functions, analogous to 
@@
 In Section~\ref{sec:finitesample} 
-we analyze the finite sample variable selection consistency of convex
-additive modeling, without assuming that the true
+we analyze the finite sample variable selection consistency of AC/DC, without assuming that the true
 regression function $f_0$ is additive. Our analysis first establishes
@@
 \item[A2:] $f_0$ is convex and continuously twice-differentiable. $\E f_0(X) = 0$.
-\item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \| \leq B$ for all $k$.
+\item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \|_\infty \leq B$ for all $k$.
 \item[A4:] The noise is mean-zero sub-Gaussian, independent of $X$.

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
+We have added the dependence on the lower bound $c_l$ of $p(x)$ in Theorem 5.2, where we require that $p \leq O(\exp(cn))$ for $c < \frac{c_l}{32}$.
+We have also added the dependence on the upper bound $c_u$ of the density in Theorem 5.3.
+The lower and upper bounds $c_l, c_u$ do not directly play the role of the signal level; they are used to simplify technicalities in the presentation and the proof of the theorems.
+For example, Theorem 5.2 should also go through if one assumes only that the marginal densities $p(x_j)$'s are positive on a sub-interval of $[-1,1]$.
+
 \item \rc{It would be good to point to Assumption (A3) at the beginning of
@@
 4.}
+
+We have added the objective function in Section 2.2 where we summarize the optimization algorithm.
+
 \item \rc{Assumption (A3) on page 7 is missing the subscript $\infty$.}
+
+The missing subscript is added.
+
 \item \rc{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
 it seems to be the sub-Gaussian parameter of the additive noise.}
+
+$\sigma$ has been defined in Section 2.3.
+
 \item \rc{Perhaps Section 3 should be titled something other than ``Additive
 faithfulness'' (maybe ``Population- level results''?).}
+
+TODO
+
 \item \rc{The first paragraph of Section 5 should read
@@
 
+Corrected.
+
 \item \rc{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}
+
+Corrected.
+
 \item \rc{The first sentence of Section 5.1 should read optimization (4.8).}
+
+Corrected.
+
 \end{enumerate}

### 2015-05-02 tex/scam/sparsistency.tex
more responses

@@
 Our goal is to show that variable screening consistency.
-That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Algorithm~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.
+That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Figure~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.
 

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
new response

@@
 
-%\item \rc{On page 31, at the top of the page, ``see discussion at beginning of
-%Section 5'' : I think it should be ``at the beginning''. In (8.1),
-%same problem as before with the indices : ``$\nu_{ki} d_{ki}$ '' must be replaced
-%with ``$\nu_{ik}d_{ik}$'' (see for instance page 20). At the bottom of the page,
-%$v_{ki}$ must be replaced by $\nu_{ki}$.}
+\item \rc{On page 31, at the top of the page, ``see discussion at beginning of
+Section 5'' : I think it should be ``at the beginning''. In (8.1),
+same problem as before with the indices : ``$\nu_{ki} d_{ki}$ '' must be replaced
+with ``$\nu_{ik}d_{ik}$'' (see for instance page 20). At the bottom of the page,
+$v_{ki}$ must be replaced by $\nu_{ki}$.}
+
+The typo and the index notation inconsistency have been corrected.
 
@@
 
-We have redefined $\kappa$.
+The original definition of $\kappa$ was indeed wrong; we forgot to update $\kappa$ when we edited the proof. We have corrected this in the paper.
 
@@
 %the ninth paragraph, ``Taking an union''.}
+
 %\item \rc{On page 40, on the fifth line, ``empricial''. In the last paragraph,
@@
 
-%\item \rc{On page 50, a constant 2 is missing in $\epsilon_n$.}
+\item \rc{On page 50, a constant 2 is missing in $\epsilon_n$.}
+
+This mistake has been corrected across the proofs.
+
 \item \rc{On page 41, in the second paragraph, I think the bound on $\sup_{h_L} |⟨w,h_L⟩_n|$ is
@@
 
+The boundary flatness condition is not restrictive in the sense that for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon > 0$, there exists a boundary flat density whose $L_1$ distance with $p(x)$ is at most $\epsilon$ (Please see the newly added Example 3.2).
+This is because boundary flatness places no restriction on what $p(x)$ looks like in the interior of the hypercube.
+Boundary flatness allows arbitrary correlation structure, provided that $p(x) > 0$.
+We have added Section 3.2 to the paper to give a more detailed discussion on boundary flatness.
+
+$f(x_1,x_2) = x_1 x_2$ is non-convex and it is an example of how non-convex functions may not be additively faithful under the uniform distribution; it is not an example in which boundary flatness doesn't hold.
+The multivariate Gaussian is a counterexample but it is to show that boundary flatness may not extend easily to densities with unbounded support.
+
+We acknowledge that many distributions are not boundary flat.
+We present boundary flatness as a significant generalization of the product density, under which nonparametric variable selection is already very difficult.
+
+Boundary flatness is not a contrived condition.
+We initially proved additive faithfulness only for product densities and then went back and gradually weakened the condition on the density over many iterations of refinement.
+
 \item \rc{Following on from the previous point, the simulation study also does

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
response
more responses

@@
 
-The boundary flatness condition does not artificially make the variable selection problem easy.
-Comminges and Dalalyan showed that variable selection for general two-smooth functions is difficult even if the underlying distribution is a product distribution, and boundary flat distributions are much more general than product distributions.
+The boundary flatness doesn't artificially make the variable selection easy.
+Boundary flatness is much more general than the product density and Comminges and Dalalyan showed that, even under a product density, variable selection for general two-smooth functions is hard.
+Any bounded density with compact support can be approximated arbitrary well by a boundary flat density (see the newly added Example 3.2).
+
+The intuition behind our result is the following: start with the fact that convex functions are additively faithful under a product density (see paragraphs below Theorem 3.1 for an intuition of this).
+The behavior of a convex function everywhere is constrained by its behavior at the boundary.
+Therefore, it is sufficient that the underlying density resembles a product density only at the boundary, which is exactly the notion that boundary flatness formalizes.
+
+What we think is that, for functions with shape-constraints such as convexity, the metric entropy alone does not determine the hardness of variable selection; the shape-constraint too plays a direct role.
 
@@
 
-This has been noted and corrected across the proofs.
+This has been noted and corrected across the paper.
 
@@
 
-This mistake has been corrected across the proofs.
+This mistake has been corrected across the paper.
 
@@
 
-We have updated this derivation.
+We have updated this part of the proof.
 

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
mods

@@
 Boundary flatness is not a contrived condition.
-We initially proved additive faithfulness only for product densities and then went back and gradually weakened the condition on the density over many iterations of refinement.
+We initially proved additive faithfulness only for product densities.
+But then, knowing that the behavior of a convex function everywhere is constrained by its behavior at the boundary, we conjectured that underlying density may only need to ``look like'' a product density at the boundary.
+Attempts to formalize this notion led us to the definition of boundary flatness.
 

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
mod

@@
 The behavior of a convex function everywhere is constrained by its behavior at the boundary.
-Therefore, it is sufficient that the underlying density resembles a product density only at the boundary, which is exactly the notion that boundary flatness formalizes.
+Therefore, we need only that the underlying density resembles a product density at the boundary, which is exactly the notion that boundary flatness formalizes.
 

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex
more response

@@
 Comparing the predictive accuracy of $f^*_k$'s and $g^*_k$'s against the non-additive true regression function $f_0$ is beyond the scope of our paper, but we do compare the finite sample estimate $\hat{f}_k$ and $\hat{g}_k$ against the population level $f^*_k$ and $g^*_k$.
-The analysis we do to control false negatives also shows that $\mathbb{E}\left(\sum_{k=1}^p (f^*_k(X_k) - \hat{f}_k(X_k))\right)^2 \rightarrow 0$ and likewise for the DC stage.
+The analysis we do to control false negatives also shows that $$\left| \mathbb{E}\left( f_0(X)  - \sum_{k=1}^p f^*_k(X_k) \right)^2 - \mathbb{E} \left( f_0(X) - \sum_{k=1}^p \hat{f}_k(X_k))\right)^2 \right| \rightarrow 0$$ and likewise for the $\hat{g}_k$'s.
+Please see Theorem 8.3 and 8.4 in the supplement.
 
@@
 
-We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5 because everything there is discussed again on page 6.
+We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5. Everything there is discussed on page 6, after AC/DC has been introduced.
 
@@
 
-TODO
+We have carefully proof-read and edited the proof of Theorem 8.4.
 
@@
 
+Section 2 is repetitive but we believe it has value in highlighting the big picture, which could otherwise be overwhelmed by the technical details.
+
 \item \rc{Page 2, second last paragraph `and and.'}
+
+We have corrected this.
+
 \end{enumerate}

### 2015-05-02 tex/scam/estimation.tex
minor edit
major paper revisions
more response

@@
 \label{eqn:scam2_pop}
-f^*_1, ..., f^*_p = \argmin_{f_1,...,f_p \in \C^1_0} 
-   \E \Big( f(X)  - \sum_{k=1}^p f_k(X_k) \Big)^2 
+f^*_1, ..., f^*_p = \argmin_{f_1,...,f_p \in \C^1_0, \mu} 
+   \E \Big( f(X) - \mu - \sum_{k=1}^p f_k(X_k) \Big)^2 
 \end{equation}
@@
 In the second stage, for every variable marked as irrelevant in the first stage, we fit a univariate \emph{concave} function separately on the residual for that variable.
- for each $k$ such that $ f^*_k = 0$:
+ For each $k$ such that $ f^*_k = 0$:
 \begin{equation}
@@
 g^*_k = \argmin_{g_k \in \mh{}\C^1_0} 
-   \E \Big( f(X) - \sum_{k'} f^*_{k'}(X_{k'}) 
+   \E \Big( f(X) - \mu^* - \sum_{k'} f^*_{k'}(X_{k'}) 
     - g_k(X_{k})\Big)^2 
@@
 theoretical analysis and implementation.
+
+After selecting the variable set $\hat{S}$, one can refit a low-dimensional non-additive convex function to build the best predictive model.
+If refitting is undesirable for whatever reason, the AC/DC outputs can also be used for prediction.
+Given a new sample $\mathbf{x}$, we let $\hat{y} = \sum_k \hat{f}_k(\mathbf{x}_k) + \sum_k \hat{g}_k(\mathbf{x}_k)$.
+Note that $\hat{g}_k = 0$ for $k$ such that $\hat{f}_k \neq 0$ in AC/DC.
+The next section describes how to compute this function evaluation.
 
@@
 \begin{equation}
-\label{eqn:dc2}
+\label{eqn:dc22}
 \hat{g}_k = \argmin_{g_k \in \mh{}\C^1_0} 

### 2015-05-02 tex/scam/supplement.tex
more response

@@
 \end{align*}
-The middle term can be bounded under the assumption that $\|f^*_k -
-\bar{f}^*_k \|_\infty \leq 2B$; thus,
+The middle term can be bounded since $\|f^*_k -
+\bar{f}^*_k \|_\infty \leq B$; thus,
 \begin{align*}
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B .
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda s B .
 \end{align*}
@@
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
-   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 2 s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}.
+   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda  s B + c(sB)^2 \frac{1}{n} \log \frac{2}{\delta}.
 \end{align}
@@
    \frac{s (sBc_u)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
-   + \lambda 2 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
+   + \lambda s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
 \|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
@@
    \frac{s^4 c_u^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
-   + \lambda 2 s B \nonumber\\   
+   + \lambda s B \nonumber\\   
    &\leq c B^2 \sigma 
-    \sqrt{ \frac{s^4 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB
+    \sqrt{ \frac{s^4 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda sB
 \label{eqn:second_step_inequality}
@@
     \sqrt{ \frac{s^4c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
- +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
+ +\lambda s B + c B^3 \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
     \nonumber \\
-&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
+&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda sB \nonumber
 \end{align}
@@
 step with $\lambda_n \leq 768 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
-Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
+Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5 c_u^{1/2}$ where $c' \geq 1$ is a constant.
 Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
 \[
-\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
+\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 np}.
 \]
@@
 \| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g} \|_\infty &\leq
-   \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n \| g^* \|_\infty \\
-\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n 2B \\[10pt]
-\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
-   +\lambda_n 2 B \\
-\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
-   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda_n 2B.
-\end{align*}
+   \| y - \hat{f} - (g^*_k - \bar{g}^*_k) \|_n^2 + \lambda_n \| (g^*-\bar{g}^*_k) \|_\infty \\
+\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - (g^*_k-\bar{g}^*_k) \|_n^2 + \lambda_n B \\[10pt]
+\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - (g^*_k-\bar{g}^*_k) + w \|_n^2 
+   +\lambda_n B \\
+\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - (g^*_k-\bar{g}^*_k) \|_n^2 &\leq
+   2 \langle w, \hat{g}_k - (g^*_k-\bar{g}^*_k) \rangle_n + \lambda_n B.
+\end{align*}
+$\bar{g}^*_k = \frac{1}{n} \sum_{i=1}^n g^*_k(X_{ik})$; we subtract it from $g^*_k$ again so that $g^*_k$ is empirically mean-zero.
+
 Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{1}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
+  c B^2 \sigma \sqrt{ \frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta} }+ \lambda_n B.
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n 2 B +
-  c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
- &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n 2B
-\end{align*}
-
-Finally, plugging in $\lambda_n \leq 9 s \tilde{\sigma} \sqrt{
+  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n B +
+  c B^3 \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta} } \\
+ &\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n B
+\end{align*}
+
+Finally, plugging in $\lambda_n \leq 768 s \tilde{\sigma} \sqrt{
   \frac{1}{n} \log^2 np}$, we obtain
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ 
-    2s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ 
+    c s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^2 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
 \end{align*}
@@
    + 2 \langle f_0 - f^*, g^*_k \rangle_P \\
- &\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} + 
+ &\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np} + 
     2 | \langle \hat{f} - f^*, g^*_k \rangle_P |  \\
- &\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} +
+ &\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np} +
     2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
-&\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} +
+&\leq  c B^2 \tilde{\sigma} \sqrt{ \frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np} +
    c B \sqrt{B^2 \tilde{\sigma} \sqrt{ 
-                   \frac{s^5}{n^{4/5}} \log^2 np} }\\
+                   \frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np} }\\
 &\leq  cB^2 \tilde{\sigma}^{1/2} \sqrt[4]{ 
-                   \frac{s^5}{n^{4/5}} \log^2 np} 
+                   \frac{s^5 c_u^{1/2}}{n^{4/5}} \log^2 np} 
 \end{align*}
@@
 Theorem~\ref{thm:convex_consistent}. To obtain the fourth inequality,
-we used the fact that $\| \hat{f} - f^* \|^2 \leq \| f_0 - \hat{f}
+we used the fact that $\| \hat{f} - f^* \|_P^2 \leq \| f_0 - \hat{f}
 \|_P^2 - \|f_0 - f^*\|_P^2$, which follows from the fact that $f^*$ is the
@@
 set of additive convex functions is convex itself.
-The last inequality holds because there is a condition in the theorem which states $n$
-is large enough such that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.
+The last inequality holds because the conditions of the theorem stipulate $n$
+is large enough such that $B^2 \tilde{\sigma} \sqrt{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 np} \leq 1$.
 The same derivation and the same bound likewise holds for term 2.
@@
    c B^2 \tilde{\sigma}^{1/2} 
-     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
+     \sqrt[4]{ \frac{s^5c_u^{1/2}}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
 \end{align*}

### 2015-05-03 tex/scam/reviews-v1/response-v1.tex
more responses

@@
 
-We have added commentary on this here and here.
+We have added a new Section 3.2 to the paper to further discuss the boundary flatness condition as well as giving more examples.
+The following paragraph has been added to briefly discuss extending the same additive faithfulness analysis to densities whose support is not a hypercube:
+
+``In our discussion so far, we have restricted ourselves to densities supported and positive on the hypercube $[0,1]^p$ to minimize extraneous technical details.
+It may be possible to extend the analysis to densities whose support is a convex and compact set so long as the marginal density $p(x_j) > 0$ for all $x_j$ in the support.
+A rigorous analysis of this however is beyond the scope of this paper.''
+
+The original paper also briefly discussed extending boundary flatness to densities with an unbounded support.
+
+The key ideas behind our analysis do not depend critically on the fact that the support is a hypercube. The hypercube assumption is made for convenience, to minimize technical details.
 
@@
 
+We have further expanded the paragraph discussing the intuition behind additive faithfulness in the paper--the second paragraph right below Theorem 3.1.
+
 \item \rc{Writing and proofs need to be tidied up in places to make it easier
@@
 
-We have tidied up.
+We have added a concise definition of AC/DC in Section 2.2, before Theorem 3.
+
+We have corrected all the minor mistakes found by the reviewers.
 
@@
 
+We have added a paragraph in Section 3.4 that discusses prediction.
+
 \item \rc{In order to improve clarity, the authors should define the convex
@@
 
-We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5. Everything there is discussed on page 6, after AC/DC has been introduced.
+We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5. Everything there is discussed now on page 6, after AC/DC has been introduced.
 
@@
 
-The conditions in Theorem 5.1 are indeed analogous and we have edited the remark accordingly. The conditions in Theorem 5.1 are much more strict than the mutual incoherence condition though.
+The conditions in Theorem 5.1 are indeed analogous and we have edited the remark in the paper accordingly.
+The conditions in Theorem 5.1 are much more strict than the mutual incoherence condition however.
 
@@
 
-TODO
+We have changed the title of Section 3 to the suggested one.
 
@@
 
-We consider only densities with support in a hypercube.
-We have modified old experiments and added new experiments to use boundary flat distributions instead of the correlated multivariate Gaussian distribution.
+We have removed old experiments that use correlated multivariate Gaussian and replaced them instead with new experiments that use boundary flat Gaussian Copula mixture distributions.
+Please see Section 6.1; Figure 4 in particular shows the bimodal marginal density of the new joint density that we use.
+Figure 5d, 5e, 5f show the result of simulations using the new non-Gaussian density.
+
+We have also added new experiments that use nonparametric true regression function instead of the quadratic form.
+We use a log-sum-exp (softmax) of linear forms (please see Equation 6.1).
+Figure 5f and 6 show the results of experiments using the softmax as the true regression function: AC/DC is still effective under the high-dimensional scaling.
 
@@
 
-Section 2 is repetitive but we believe it has value in highlighting the big picture, which could otherwise be overwhelmed by the technical details.
+Section 2 is repetitive but we believe it has value in highlighting the big picture, which could otherwise be drowned out by the technical details.
 

### 2015-05-03 tex/scam/additive_faithful.tex
more response
more responses

@@
-\section{Additive Faithfulness}
+\section{Population Level Analysis: Additive Faithfulness}
 \label{sec:additivefaithful}
@@
 &\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
-f_k \in L^2(F),\, \E f_k(X_k) = 0,\; k=1,\ldots, p \right\}.
+f_k \in L^2(P),\, \E f_k(X_k) = 0,\; k=1,\ldots, p \right\}.
 \end{align*}
@@
 \begin{proof}
-  Let $f^*_1,...,f^*_p, \mu^*$ be the minimizers as defined; they exist since the set of mean zero additive functions is a closed subspace of $L^2(F)$.  We first
+  Let $f^*_1,...,f^*_p, \mu^*$ be the minimizers as defined; they exist since the set of mean zero additive functions is a closed subspace of $L^2(P)$.  We first
   show that the optimal $\mu$ is $\mu^* = \E f(X)$ for any $f_1, ...,
@@
 characterize below, convex multivariate functions are additively
-faithful. To simplify presentation, we restrict our attention to densities bounded away from $0/\infty$, that is, $p(\mathbf{x})$ such that $0 < \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) < \infty$.
+faithful. To simplify presentation, we restrict our attention to densities bounded away from $0/\infty$, that is, $0 < \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) < \infty$.
 
@@
 Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.
-We say that $p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if for all $j$, there exists some $\epsilon > 0$ such that for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
+We say that $p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if for all $j$, for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$ for some arbitrarily small $\epsilon > 0$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
 \begin{equation}
@@
 
-The boundary flatness condition intuitively states that two conditional densities $p(\mathbf{x}_{-j} \given x_j)$ and $p(\mathbf{x}_{-j} \given x_j')$ are similar when $x_j$ and $x_j'$ are both close to $0$ or both close to $1$.
-Product densities satisfy boundary flatness trivially.
+The boundary flatness condition intuitively states that two conditional densities $p(\mathbf{x}_{-j} \given x_j)$ and $p(\mathbf{x}_{-j} \given x_j')$ are similar when $x_j$ and $x_j'$ are both close to the same boundary point.
+It is thus much more general than product densities.
 Boundary flatness is a weak condition because it affects only an $\epsilon$-small region around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from the boundary.
@@
 
-Suppose $f$ is a convex and continuously twice differentiable on an open set containing $C$, then $f$ is additively faithful under $p(\mathbf{x})$.
+Suppose $f$ is a convex with a bounded second derivative on an open set containing $C$, then $f$ is additively faithful under $p(\mathbf{x})$.
 \end{theorem}
@@
 We pause to give some intuition before we present the full proof.
-Suppose that the underlying distribution has a product density.
-Then we know from Lemma~\ref{lem:general_int_reduction} that the
+Suppose that the underlying density is a product density first.
+We know from Lemma~\ref{lem:general_int_reduction} that the
 additive approximation zeroes out $k$ when, fixing $x_k$, every
-``slice'' of $f$ integrates to zero. We prove
-Theorem~\ref{thm:convex_faithful} by showing that ``slices'' of convex
+``slice'' of $f$ integrates to zero, but ``slices'' of convex
 functions that integrate to zero cannot be ``glued together'' while
-still maintaining convexity.
+still maintaining convexity. Since the behavior of the whole convex function is constrained by its behavior at the boundary, 
+the same result holds even if the underlying density is not a product density but merely resembles a product density at the boundary, which is exactly the notion formalized by the boundary flatness condition.
 
@@
 It may be possible to extend the analysis to densities whose support is a convex and compact set so long as the marginal density $p(x_j) > 0$ for all $x_j$ in the support.
+A rigorous analysis of this however is beyond the scope of this paper.
 
@@
 Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ that
-satisfies the boundary flatness condition. Suppose that $f$ is convex and continuously twice differentiable on an open set around $C$. Let $f^*_k$ and $g^*_k$ be as defined in equations
+satisfies the boundary flatness condition. Suppose that $f$ is convex with a bounded second derivative on an open set around $C$. Let $f^*_k$ and $g^*_k$ be as defined in equations
 \eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, 
@@
 Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ satisfying the boundary flatness condition.
-Let $f(\mathbf{x})$ be a convex and continuously twice differentiable function on an open set around $C$.
+Let $f(\mathbf{x})$ be a convex function with a bounded second derivative on an open set around $C$.
 Let $\phi(\mathbf{x}_{-k})$ be a bounded function that does not depend on $x_k$.
@@
 Therefore, $h^*_k$ is square integrable and there exists a fourier series $s_n(x_k)$ convergent to $h^*_k$ in $L_2$.
-Since $p(\mathbf{x})$ is bounded, $\lim_{n \rightarrow \infty} \E ( s_n(X_k) - h^*_k(X_k )^2 \rightarrow 0$ as well.
+Since $p(\mathbf{x})$ is bounded, $$\lim_{n \rightarrow \infty} \E \left( s_n(X_k) - h^*_k(X_k ) \right)^2 \rightarrow 0$$ as well.
 

### 2015-05-03 tex/scam/sparsistency.tex
more responses

@@
 \item The data $X^{(1)},\ldots, X^{(n)} \sim P$ are iid from
-a distribution $P$ with a density $p(\mathbf{x})$ that is supported and strictly positive on $\mathcal{X}=[-1,1]^p$.
+a distribution $P$ with a density $p(\mathbf{x})$ that is supported on $\mathcal{X}=[-1,1]^p$.
 \item The response is $Y = f_0(X) + W$ where $W$ is
@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and continuously twice-differentiable on an open set around $[-1,1]^p$. $\E f_0(X) = 0$.
+\item[A2:] $f_0$ is convex with a bounded second derivative on an open set around $[-1,1]^p$. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.

### 2015-05-03 tex/scam/summary.tex
more responses

@@
   Let $p(\mathbf{x})$ be a positive density supported on $C=[0,1]^p$ that
-  satisfies the boundary flatness property. If $f$ is convex and continuously twice
-  differentiable on an open set around $C$, then $f$ is additively faithful under $p$.
+  satisfies the boundary flatness property. If $f$ is convex with a bounded second derivative on an open set around $C$, then $f$ is additively faithful under $p$.
 \end{stheorem}
@@
 \item[A1:] $X_S, X_{S^c}$ are independent. 
-\item[A2:] $f_0$ is convex and continuously twice-differentiable. $\E f_0(X) = 0$.
+\item[A2:] $f_0$ is convex with a bounded second derivative. $\E f_0(X) = 0$.
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\|f^*_k \|_\infty \leq B$ for all $k$.
-\item[A4:] The noise is mean-zero sub-Gaussian, independent of $X$.
-\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition.
+\item[A4:] The noise is mean-zero sub-Gaussian with scale $\sigma$, independent of $X$.
+\item[A5:] The density $p(\mathbf{x})$ is bounded away from $0/\infty$ and satisfies the boundary flatness condition.
 \end{packed_enum}
@@
 This shows that variable selection consistency is achievable under
-exponential scaling of the ambient dimension, $p = O(\exp(n^c))$
+exponential scaling of the ambient dimension, $p = O(\exp(cn))$
 for some $0<c<1$, as for linear models. The cost of nonparametric estimation is

### 2015-05-03 tex/scam/supplement.tex
more responses

@@
 
-We just need to remember that $p''(\mathbf{x}_{-k} \given x_k)$ is bounded for all $\mathbf{x}_{-k}$ and $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$ by boundary flatness, that $f''(x_k, \mathbf{x}_{-k})$ is a continuous function of $\mathbf{x}$, and the same argument applies.
+We just need to remember that $p''(\mathbf{x}_{-k} \given x_k)$ is bounded for all $\mathbf{x}_{-k}$ and $x_k \in [0, \epsilon) \cup (1-\epsilon, 1]$ by boundary flatness, that $f''(x_k, \mathbf{x}_{-k})$ is bounded, and the same argument applies.
 

### 2015-05-03 code/Piecewise_Infinity.m

@@ -1,6 +1,14 @@
 function [beta,h,obj] = Piecewise_Infinity(X,y,lambda,mu,maxit)
-[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
-M = zeros(p,n); iter = 0; obj = []; C = zeros(p,n);
+
+[p,n] = size(X); 
+beta = zeros(p,n); 
+S = zeros(n,n); 
+W = zeros(n,n); 
+
+M = zeros(p,n); 
+iter = 0; 
+obj = []; 
+C = zeros(p,n);
 
 num_lambda = length(lambda);
 if (num_lambda < p)
@@ -9,7 +17,9 @@ end
 
 while iter < maxit 
     iter = iter + 1;
-    for j = 1:p, C(j,:) = Piecewise_Inf(beta(j,:)-1/mu*M(j,:),lambda(j)/mu); end
+    for j = 1:p, 
+        C(j,:) = Piecewise_Inf(beta(j,:)-1/mu*M(j,:),lambda(j)/mu); 
+    end
     
     xb = sum(X.*beta,1); %a row of dimension n
     h = 1/mu*y-1/mu*(sum(W,2)-sum(W,1)')+sum(S,2)-sum(S,1)'+ ...
@@ -23,9 +33,13 @@ while iter < maxit
     
     for i = 1:n
         Xi = X - repmat(X(:,i),[1,n]); 
-        beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
-        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0); 
-        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); M(:,i) = M(:,i) + mu*(C(:,i)-beta(:,i)); 
+        beta(:,i) = (eye(p)+Xi*Xi')\ ...
+                    (C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-S(:,i)+1/mu*W(:,i)));
+        xbi = Xi'*beta(:,i); 
+        
+        S(:,i) = max(h-h(i)-xbi+1/mu*W(:,i),0); 
+        W(:,i) = W(:,i) + mu*(h-h(i)-xbi-S(:,i)); 
[…]

### 2015-05-03 code/Piecewise_TestInfinity.m

@@ -1,25 +1,35 @@
-clc; clear all; close all; randn('state',123); rand('state',0);
+%clc; clear all; close all; 
+%randn('state',123); rand('state',0);
+
+addpath('simdata');
+
 noise = 0.2; 
-n = 100; p = 80; s = 3; lambda = 2*noise*sqrt(s*log(p)/n)*n; maxit = 10000; mu = 0.01;
+n = 1000; 
+p = 30; 
+s = 3; 
+
+lambda = noise*sqrt(s*log(p)/n)*n; 
+
+maxit = 2000; 
+mu = 0.005;
+
 lambda = max(lambda,1e-3*n);
-prob = zeros(p,1); 
-%ord = randperm(p); 
-ord = 1:p;
-prob(ord(1:s)) = gamrnd(10*ones(s,1),1);
-prob(ord(1:s)) = prob(ord(1:s))/sum(prob(ord(1:s)));
-X = randn(p,n); 
-%X = X./(ones(p,1)*sqrt(sum(X.^2,1)));
-%X = 0.5*rand(p,n)+1;
 
-y = diag(X(1:s,:)'*eye(s)*X(1:s,:)) + noise*randn(n,1);
+X = 2*rand(p,n) - 1;
 
-%y = exp(X'*prob) + noise*randn(n,1);
-%y = log(sum(exp(X'*prob),2)) + noise*randn(n,1);
+K = 4;
+y = softmaxAffine(X', K, 1:s) + noise*randn(n,1);
+
 
 %[beta1,h1,obj1] = Piecewise_Convex(X,y,lambda,mu,maxit); % L-2-1 norm
-%[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda,mu,maxit); % L-infinity-1 norm
+[beta2,h2,obj2] = Piecewise_Infinity(X,y,lambda,mu,maxit); % L-infinity-1 norm
+
+
 
 %gamma = 1/sqrt(n);
-gamma = 1e7;
+%gamma = 1e7;
 
-[beta1,D,h1,obj1] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit); % L-2-1 norm
+
+%[beta1,D,h1,obj1] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit); % L-2-1 norm
+
+

### 2015-05-03 code/Quadratic_Infinity.m

@@ -1,6 +1,16 @@
+% ADMM
+
 function [beta,D,h,obj] = Quadratic_Infinity(X,y,lambda,gamma,mu,maxit)
-[p,n] = size(X); beta = zeros(p,n); S = zeros(n,n); W = zeros(n,n); 
-M = zeros(p,2*n); iter = 0; obj = []; C = zeros(p,2*n); D = zeros(p,n);
+
+[p,n] = size(X); 
+beta = zeros(p,n); 
+S = zeros(n,n); 
+
+W = zeros(n,n); 
+M = zeros(p,2*n); 
+iter = 0; obj = []; 
+C = zeros(p,2*n); 
+D = zeros(p,n);
 
 num_lambda = length(lambda);
 if (num_lambda < p)
@@ -14,7 +24,9 @@ end
 
 while iter < maxit 
     iter = iter + 1;
-    for j = 1:p, C(j,:) = Piecewise_Inf([beta(j,:),D(j,:)]-1/mu*M(j,:),lambda(j)/mu); end
+    for j = 1:p, 
+        C(j,:) = Piecewise_Inf([beta(j,:),D(j,:)]-1/mu*M(j,:),lambda(j)/mu); 
+    end
     
     Dexpand = permute(repmat(D,[1,1,n]),[1,3,2]);
     tmp = reshape(Delta.*Dexpand,[p,n*n]);
@@ -41,7 +53,9 @@ while iter < maxit
     for i = 1:n
         Xi = X - repmat(X(:,i),[1,n]); 
         beta(:,i) = (eye(p)+Xi*Xi')\(C(:,i)+1./mu*M(:,i)+Xi*(h-h(i)-DDelta(:,i)-S(:,i)+1/mu*W(:,i)));
-        xbi = Xi'*beta(:,i); S(:,i) = max(h-h(i)-xbi-DDelta(:,i)+1/mu*W(:,i)-gamma,0);
+        
+        xbi = Xi'*beta(:,i); 
+        S(:,i) = max(h-h(i)-xbi-DDelta(:,i)+1/mu*W(:,i)-gamma,0);
         %xbi is (n--by--1)
         
         %update for D
@@ -58,8 +72,10 @@ while iter < maxit
     if mod(iter,100)==0, 
         disp(['   Iter ' num2str(iter) ' Obj ' num2str(obj(iter)) ' sparsity: ' num2str(sum(max(abs(C),[],2) < 1e-6))]);
[…]

### 2015-05-03 code/paper_exp/K.m

@@ -110,20 +110,21 @@ return
 num_versions = 18;
 prob = zeros(1,num_versions); 
 supp = zeros(nrun, num_versions);
-epsil = 1e-6;
-
-success_supp = 20;
+epsil = 1e-5;
+%success_supp = 20;
 
 for version = 1:num_versions
-    load(['mat/S_' num2str(version) '.mat']);
+    if (version == 10 || version == 18)
+        continue
+    end
+    
+    load(['mat/K_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 
     for run = 1:nrun
-        cur_supp = sum(Ln(:,run) > 1e-5);
         if min(Ln(J(:,run),run)) > epsil && ...
-            cur_supp < success_supp
+           max(Ln(~J(:,run), run)) < epsil
             suc = suc + 1;
         end
-        supp(run,version) = cur_supp;
     end
     prob(version) = suc/nrun;
 end

### 2015-05-04 tex/scam/reviews-v1/response-v1.tex
more response

@@
 
-The intuition behind our result is the following: start with the fact that convex functions are additively faithful under a product density (see paragraphs below Theorem 3.1 for an intuition of this).
+The intuition behind our result is the following: start with the fact that convex functions are additively faithful under a product density.
 The behavior of a convex function everywhere is constrained by its behavior at the boundary.
@@
 The details are described in a 2014 paper by Pya and Wood which we have cited in the introduction.
-We chose not to discuss estimating smooth convex functions because it would introduce an additional tuning parameter.
+We chose not to add smoothness into the estimation because it would introduce an additional tuning parameter.
 
 The analysis may require much more work if one uses a B-spline basis in the estimation.
-B-splines may significantly complicate the false positive analysis, which rely on the particular form of the optimization.
+B-splines may complicate the false positive analysis, which rely on the particular form of the optimization objective.
 The false negative analysis may not be affected much because it mainly uses bracketing entropy.
@@
 
-It is not necessary that $p(\mathbf{x}_{-j}, x_j) = 0$ at $x_j = 0,1$; it is necessary that $p(\mathbf{x}_{-j}, x_j) > 0$.
-We have however, added an additional condition that $p(\mathbf{x})$ has a bounded second derivative.
+It is necessary that $p(\mathbf{x}_{-j}, x_j) > 0$.
+We have added an additional condition that $p(\mathbf{x})$ has a bounded second derivative.
 This condition ensures that the marginal density $p(x_j)$ is twice differentiable and $p'(x_j) = p''(x_j) = 0$ at $x_j = 0,1$.
 With this, it is valid to apply the quotient rule for differentiation to show that boundary flatness holds.
-Please see the second item in Example 3.2 for the relevant modifications.
+Please see Example 3.2 for the relevant edits.
 
@@
 
-We indeed need a bounded condition here.
+We do need a boundedness condition here.
 We have modified the definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$ is bounded and has a bounded first and second derivative for all $x_j$ in some open set around the boundary points and for all $\mathbf{x}_{-j}$.
@@
 
-...
+``...
 we plot on the y-axis the norm $\|f^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$.
 Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|f^{(t)}_j\|_{\infty}}{\sum_j \|f^{(1)}\|_{\infty}}$.
-Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.
+Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.''
 
@@
 
-The boundary flatness condition is not restrictive in the sense that for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon > 0$, there exists a boundary flat density whose $L_1$ distance with $p(x)$ is at most $\epsilon$ (Please see the newly added Example 3.2).
+The boundary flatness condition is not restrictive in the sense that for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon > 0$, there exists a boundary flat density whose $L_1$ distance with $p(x)$ is at most $\epsilon$ (Please see the newly added Example 3.3).
 This is because boundary flatness places no restriction on what $p(x)$ looks like in the interior of the hypercube.
@@
 We initially proved additive faithfulness only for product densities.
-But then, knowing that the behavior of a convex function everywhere is constrained by its behavior at the boundary, we conjectured that underlying density may only need to ``look like'' a product density at the boundary.
+Then, knowing that the behavior of a convex function everywhere is constrained by its behavior at the boundary, we conjectured that underlying density may only need to ``look like'' a product density at the boundary.
 Attempts to formalize this notion led us to the definition of boundary flatness.

### 2015-05-05 tex/scam/reviews-v1/response-v1.tex
shorten

@@
 We have added a new Section 3.2 to the paper to further discuss the boundary flatness condition as well as giving more examples.
-The following paragraph has been added to briefly discuss extending the same additive faithfulness analysis to densities whose support is not a hypercube:
-
-``In our discussion so far, we have restricted ourselves to densities supported and positive on the hypercube $[0,1]^p$ to minimize extraneous technical details.
-It may be possible to extend the analysis to densities whose support is a convex and compact set so long as the marginal density $p(x_j) > 0$ for all $x_j$ in the support.
-A rigorous analysis of this however is beyond the scope of this paper.''
-
-The original paper also briefly discussed extending boundary flatness to densities with an unbounded support.
-
-The key ideas behind our analysis do not depend critically on the fact that the support is a hypercube. The hypercube assumption is made for convenience, to minimize technical details.
+Extending our analysis to densities who support is not hypercube is beyond the scope of our paper although we think it is do-able.
+The key ideas behind our analysis do not depend critically on the fact that the support is a hypercube.
+The hypercube assumption is made for convenience, to minimize technical details.
 

### 2015-05-15 tex/scam/additive_faithful.tex
minor

@@
 
-The boundary flatness condition intuitively states that two conditional densities $p(\mathbf{x}_{-j} \given x_j)$ and $p(\mathbf{x}_{-j} \given x_j')$ are similar when $x_j$ and $x_j'$ are both close to the same boundary point.
-It is thus much more general than product densities.
-Boundary flatness is a weak condition because it affects only an $\epsilon$-small region around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from the boundary.
-Boundary flatness also allows arbitrary correlation structure between the variables (provided $p(\mathbf{x}) >0$).
-In Section~\ref{sec:boundary_flat}, we give a detailed discussion of the boundary flatness condition and show examples of boundary flat densities; in particular, we show that any density supported on a compact set can be approximated arbitrarily well by boundary flat densities.
+The boundary flatness condition intuitively states that two
+conditional densities $p(\mathbf{x}_{-j} \given x_j)$ and
+$p(\mathbf{x}_{-j} \given x_j')$ are similar when $x_j$ and $x_j'$ are
+both close to the same boundary point. It is thus much more general
+than product densities. Boundary flatness is a weak condition because
+it affects only an $\epsilon$-small region around the boundary;
+$p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from
+the boundary. Boundary flatness also allows arbitrary correlation
+structure between the variables (provided $p(\mathbf{x}) >0$). In
+Section~\ref{sec:boundary_flat}, we give a detailed discussion of the
+boundary flatness condition and show examples of boundary flat
+densities. In particular, we show that any density supported on a
+compact set can be approximated arbitrarily well by boundary flat
+densities.
 
@@
 \begin{remark}
-In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric form for the additive components; the additive approximations may not be faithful if we take a parametric form.
-For example, suppose we approximate a mean-zero convex function $f(X)$ by a linear form $X \beta$.
-The optimal linear function in the population setting is $\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma$ is the covariance matrix.
-Suppose the $X$'s are independent, follow a symmetric distribution, have unit variance, and suppose $f(\mathbf{x}) = x_1^2 - \E[X_1^2]$, then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 - X_1 \E[X_1^2]] = 0$.
+In Theorem~\ref{thm:convex_faithful}, we do not assume a parametric
+form for the additive components; the additive approximations may not
+be faithful if we take a parametric form. For example, suppose we
+approximate a mean-zero convex function $f(X)$ by a linear form $X
+\beta$. The optimal linear function in the population setting is
+$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma$ is the
+covariance matrix. Suppose the $X$s are independent, have a
+symmetric distribution with unit variance, and suppose $f(\mathbf{x})
+= x_1^2 - \E[X_1^2]$. Then $\beta^*_1 = \E[ X_1 f(X)] = \E[ X_1^3 -
+  X_1 \E[X_1^2]] = 0$.
 \end{remark}
@@
 
-In this section, we give more examples of boundary flat densities (see Definition~\ref{defn:boundary-point}) and discuss extending the notion of boundary flatness to densities with a more general support.
-We first start with an sufficient condition on the \emph{joint density} that ensures boundary flatness.
+In this section, we give more examples of boundary flat densities (see
+Definition~\ref{defn:boundary-point}) and discuss extending the notion
+of boundary flatness to densities with a more general support. We
+first start with a sufficient condition on the \emph{joint density}
+that ensures boundary flatness.
 
@@
 
-In our discussion so far, we have restricted ourselves to densities supported and positive on the hypercube $[0,1]^p$ to minimize extraneous technical details.
-It may be possible to extend the analysis to densities whose support is a convex and compact set so long as the marginal density $p(x_j) > 0$ for all $x_j$ in the support.
-A rigorous analysis of this however is beyond the scope of this paper.
+In the discussion so far, we have restricted our attention to
+densities supported and positive on the hypercube $[0,1]^p$ to
+minimize extraneous technical details. It may be possible to extend
+the analysis to densities whose support is a convex and compact set so
+long as the marginal density $p(x_j) > 0$ for all $x_j$ in the
+support. A rigorous analysis of this however is beyond the scope of
+this paper.
 
-It may also possible to extend similar result to densities with an
+It may also possible to formulate a similar result to densities with
 unbounded support, by using a limit condition $\lim_{|x_k| \rightarrow
-  \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given x_k)}{\partial x_k}
-= 0$.  Such a limit condition however is not obeyed by a correlated multivariate Gaussian distribution. 
-The next example shows that certain convex functions are not additively faithful under certain multivariate Gaussian distributions.
+  \infty} \frac{\partial p(\mathbf{\scriptstyle x}_{-k} \given
+  x_k)}{\partial x_k} = 0$.  Such a limit condition however is not
+obeyed by a correlated multivariate Gaussian distribution.  The next
+example shows that certain convex functions are not additively
+faithful under general multivariate Gaussian distributions.
 
@@
 \end{align*}
-Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$, $T_2 = H_{22} + 2H_{12} \alpha + H_{11} \alpha^2$, $c_1, c_2$ are constants such that $f^*_1$ and $f^*_2$ both have mean zero.
-Let $H = \begin{pmatrix} 1.6 & 2 \\ 2 & 5\end{pmatrix}$, then it is easy to check that if $\alpha = - \frac{1}{2}$, then $f^*_1 = 0$
-and additive faithfulness is violated, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave function.
-We take the setting where $\alpha=-0.5$, compute the optimal additive functions via numerical simulation, and show the results in Figure~\ref{fig:gaussian_example}--$f^*_1$ is zero as expected.
+Where $T_1 = H_{11} + 2H_{12} \alpha + H_{22} \alpha^2$, $T_2 = H_{22}
++ 2H_{12} \alpha + H_{11} \alpha^2$, $c_1, c_2$ are constants such
+that $f^*_1$ and $f^*_2$ both have mean zero. Let $H = \begin{pmatrix}
+  1.6 & 2 \\ 2 & 5\end{pmatrix}$, then it is easy to check that if
+  $\alpha = - \frac{1}{2}$, then $f^*_1 = 0$ and additive faithfulness
+  is violated, if $\alpha > \frac{1}{2}$, then $f^*_1$ is a concave
+  function. We take the setting where $\alpha=-0.5$, compute the
+  optimal additive functions via numerical simulation, and show the
+  results in Figure~\ref{fig:gaussian_example}.  Here $f^*_1$ is zero as
+  expected.
 \end{example}
 
-Although the Gaussian distribution does not satisfy the boundary flatness condition, it is possible to approximate the Gaussian distribution arbitrarily well with distributions that do satisfy the boundary flatness conditions.
-We use the similar idea as that of Example~\ref{ex:mixture_approx}.
+Although the Gaussian distribution does not satisfy the boundary
+flatness condition, it is possible to approximate the Gaussian
+distribution arbitrarily well with distributions that do satisfy the
+boundary flatness condition. We use an idea similar to that of
+Example~\ref{ex:mixture_approx}.
 
@@
 \label{examp:boundaryflat_example}
-Let $\Sigma$ be as in Example~\ref{examp:gaussian_counterexample} with $\alpha = -0.5$ so that $f^*_1 = 0$.
-Consider a mixture $\lambda U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where $N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate Gaussian bounded in $[-b, b]^2$ and $U[-(b+\epsilon), b+\epsilon]^2$ is the uniform distribution over a square.
-The uniform distribution is supported over a slightly larger square to satisfy the boundary flatness conditions.
+Let $\Sigma$ be as in Example~\ref{examp:gaussian_counterexample} with
+$\alpha = -0.5$ so that $f^*_1 = 0$. Consider a mixture $\lambda
+U[-(b+\epsilon), b+\epsilon]^2 + (1-\lambda) N_b(0, \Sigma)$ where
+$N_b(0,\Sigma)$ is the density of a \emph{truncated} bivariate
+Gaussian bounded in $[-b, b]^2$ and $U[-(b+\epsilon), b+\epsilon]^2$
+is the uniform distribution over a square. The uniform distribution is
+supported over a slightly larger square to satisfy the boundary
+flatness condition.
 
-When $b$ is large, $\epsilon$ is small, and $\lambda$ is small, the mixture closely approximates the Gaussian distribution but is still additively faithful for convex functions.
-Figure~\ref{fig:boundaryflat_example} shows the optimal additive components under the mixture distribution, computed by numerical integration with $b=5, \epsilon=0.3, \lambda=0.0001$.
-True to our theory, $f^*_1$, which is zero under the Gaussian distribution, is nonzero under the mixture approximation to the Gaussian distribution.
-We note that the magnitude $\E f^*_1(X_1)^2$, although non-zero, is very small, consistent with the fact that the mixture distribution closely approximates the Gaussian distribution.
+When $b$ is large, $\epsilon$ is small, and $\lambda$ is small, the
+mixture closely approximates the Gaussian distribution but is still
+additively faithful for convex
+functions. Figure~\ref{fig:boundaryflat_example} shows the optimal
+additive components under the mixture distribution, computed by
+numerical integration with $b=5, \epsilon=0.3, \lambda=0.0001$. True
+to our theory, $f^*_1$, which is zero under the Gaussian distribution,
+is nonzero under the mixture approximation to the Gaussian
+distribution. We note that the magnitude $\E f^*_1(X_1)^2$, although
+non-zero, is very small, consistent with the fact that the mixture
+distribution closely approximates the Gaussian distribution.
 \end{example}
@@
 	}
-\caption{Optimal additive projection of the quadratic function described in Example~\ref{examp:gaussian_counterexample} under both the Gaussian distribution described in Example~\ref{examp:gaussian_counterexample} and under the approximately Gaussian mixture distribution described in Example~\ref{examp:boundaryflat_example}.
-For the mixture approximation, we used $b=5, \epsilon=0.3, \lambda=0.0001$ where the parameters are defined in Example~\ref{examp:boundaryflat_example}.
-This example shows the effect and the importance of the boundary flatness conditions.}
+\caption{Optimal additive projection of the quadratic function
+  described in Example~\ref{examp:gaussian_counterexample} under both
+  the Gaussian distribution described in
+  Example~\ref{examp:gaussian_counterexample} and the
+  approximately Gaussian mixture distribution described in
+  Example~\ref{examp:boundaryflat_example}. For the mixture
+  approximation, we used $b=5, \epsilon=0.3, \lambda=0.0001$ where the
+  parameters are defined in
+  Example~\ref{examp:boundaryflat_example}. This example shows the
+  effect and the importance of the boundary flatness condition.}
 \vskip-10pt

### 2015-05-15 tex/scam/additive_faithful.tex
a

@@
 We pause to give some intuition before we present the full proof.
-Suppose that the underlying density is a product density first.
-We know from Lemma~\ref{lem:general_int_reduction} that the
-additive approximation zeroes out $k$ when, fixing $x_k$, every
-``slice'' of $f$ integrates to zero, but ``slices'' of convex
-functions that integrate to zero cannot be ``glued together'' while
-still maintaining convexity. Since the behavior of the whole convex function is constrained by its behavior at the boundary, 
-the same result holds even if the underlying density is not a product density but merely resembles a product density at the boundary, which is exactly the notion formalized by the boundary flatness condition.
+Suppose that the underlying density is a product density.  We know
+from Lemma~\ref{lem:general_int_reduction} that the additive
+approximation zeroes out $k$ when, fixing $x_k$, every ``slice'' of
+$f$ integrates to zero, but ``slices'' of convex functions that
+integrate to zero cannot be ``glued together'' while still maintaining
+convexity. Since the behavior of the whole convex function is
+constrained by its behavior at the boundary, the same result holds
+even if the underlying density is not a product density but merely
+resembles a product density at the boundary, which is exactly the
+notion formalized by the boundary flatness condition.
 
@@
 equation~\eqref{eqn:unconstrained_additive}.  The reason is that $f^*_k$ need not be
-a convex function, as example~\ref{examp:gaussian_counterexample} and example~\ref{examp:boundaryflat_example} 
+a convex function, as Example~\ref{examp:gaussian_counterexample} and Example~\ref{examp:boundaryflat_example} 
 show. It may be possible to estimate $f^*_k$ via smoothing, but we prefer an approach that is free of smoothing parameters. 
@@
 \label{thm:acdc_faithful}
-Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ that
-satisfies the boundary flatness condition. Suppose that $f$ is convex with a bounded second derivative on an open set around $C$. Let $f^*_k$ and $g^*_k$ be as defined in equations
-\eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, 
-$f^*_k = 0$ and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x})
-= 0$, that is, $f$ does not depend on~$x_k$. 
+Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from
+$0/\infty$ that satisfies the boundary flatness condition. Suppose
+that $f$ is convex with a bounded second derivative on an open set
+around $C$. Let $f^*_k$ and $g^*_k$ be as defined in equations
+\eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then
+the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, $f^*_k = 0$
+and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x}) = 0$, that
+is, $f$ does not depend on~$x_k$.
 \end{theorem}
@@
 \label{cor:faithfulness_extension}
-Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from $0/\infty$ satisfying the boundary flatness condition.
-Let $f(\mathbf{x})$ be a convex function with a bounded second derivative on an open set around $C$.
-Let $\phi(\mathbf{x}_{-k})$ be a bounded function that does not depend on $x_k$.
-Then, we have that the unconstrained univariate function
+Suppose $p(\mathbf{x})$ is a density on $C=[0,1]^p$ bounded away from
+$0$ and~$\infty$ satisfying the boundary flatness condition.  Let
+$f(\mathbf{x})$ be a convex function with a bounded second derivative
+on an open set around $C$. Let $\phi(\mathbf{x}_{-k})$ be a bounded
+function that does not depend on $x_k$. Then the
+unconstrained univariate function
  \begin{align}
@@
 equation~\ref{eqn:convex_additive} and
-equation~\ref{eqn:concave_postprocess}.
-Let $\phi(\mathbf{x}_{-k}) \equiv \sum_{k' \neq k} f^*_{k'}(x_{k'})$.
-Each $f^*_{k'}$ is convex and thus continuous on $(0,1)$.
-$f^*_{k'}(x_{k'})$ is defined at $x_{k'} = 0,1$; thus, $f^*_{k'}$ must be bounded and $\phi(\mathbf{x}_{-k})$ is bounded.
+equation~\ref{eqn:concave_postprocess}. Let $\phi(\mathbf{x}_{-k})
+\equiv \sum_{k' \neq k} f^*_{k'}(x_{k'})$. Each $f^*_{k'}$ is convex
+and thus continuous on $(0,1)$. The function $f^*_{k'}(x_{k'})$ is defined at
+$x_{k'} = 0,1$; thus, $f^*_{k'}$ must be bounded and
+$\phi(\mathbf{x}_{-k})$ is bounded.
 

### 2015-05-15 tex/scam/paper.tex
minor edits
removed clearpage
acdc population, new prop for alt form
a

@@
 \usepackage{yhmath}
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{shadecolor}{gray}{0.9}
+\definecolor{shadecolor}{gray}{0.9}
+\hypersetup{citecolor=MidnightBlue}
+\hypersetup{linkcolor=MidnightBlue}
+\hypersetup{urlcolor=MidnightBlue}
 
-\renewcommand{\baselinestretch}{1.1}
+\renewcommand{\baselinestretch}{1.05}
 %\parskip12pt
@@
 \vskip10pt
-\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
+\author{\fnms{Min} \snm{Xu${}^*$}\ead[label=e1]{minx@cs.cmu.edu}}
 \comma 
-\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
+\author{\fnms{Minhua} \snm{Chen${}^\dag$}\ead[label=e2]{minhua@galton.uchicago.edu}}
 \and
-\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
-\address{
-\begin{tabular}{ccc}
-\\[10pt]
-Machine Learning Department & Department of Statistics & Department of Statistics\\
-Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
-& & University of Chicago
-\end{tabular}
-%\\[20pt]
-%\printead{e1,e2,e3}
-}
+\author{\fnms{John}
+  \snm{Lafferty${}^\dag$}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{${}^*$Machine Learning Department, Carnegie Mellon University,
+  Pittsburgh PA 15213}
+\address{${}^\dag$Department of Statistics, University of Chicago, Chicago IL 60637}
 \end{aug}
@@
 
+%\clearpage
 \bibliographystyle{imsart-nameyear}
@@
 
+%\clearpage
+\input{supplement}
+
 \end{document}

### 2015-05-15 tex/scam/reviews-v1/response-v1.tex
a

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\renewcommand{\baselinestretch}{1.02}
 
@@
 
-We thank the reviewers for their helpful comments regarding our
-submission. We have carefully addressed all these comments. The
-following describes the revisions made to the manuscript in response
-to the reviews.
+We thank the reviewers for their careful reading of our paper and many
+helpful comments. We have carefully addressed all these comments. The
+following describes the revisions made to the manuscript, with 
+responses to each of the points made in the reviews.
 
@@
 
-We have added a new Section 3.2 to the paper to further discuss the boundary flatness condition as well as giving more examples.
-Extending our analysis to densities who support is not hypercube is beyond the scope of our paper although we think it is do-able.
-The key ideas behind our analysis do not depend critically on the fact that the support is a hypercube.
-The hypercube assumption is made for convenience, to minimize technical details.
+We have added a new Section 3.2 ``Boundary Flatness Examples'' to the
+paper to further discuss the boundary flatness condition.
+Extending our analysis to densities whose support
+is not a hypercube is beyond the scope of our paper, although we think it
+is possible. The key ideas behind our analysis do not depend critically
+on the fact that the support is a hypercube. The hypercube assumption
+is made only for convenience, to minimize technical details.
 
@@
 
-The boundary flatness doesn't artificially make the variable selection easy.
-Boundary flatness is much more general than the product density and Comminges and Dalalyan showed that, even under a product density, variable selection for general two-smooth functions is hard.
-Any bounded density with compact support can be approximated arbitrary well by a boundary flat density (see the newly added Example 3.2).
+Boundary flatness doesn't artificially make variable selection
+easy. Boundary flatness is much more general than the product density,
+and Comminges and Dalalyan showed that even under a product density
+variable selection for general two-smooth functions is hard. Any
+bounded density with compact support can be approximated arbitrary
+well by a boundary flat density (see the newly added Example 3.2).
 
-The intuition behind our result is the following: start with the fact that convex functions are additively faithful under a product density.
-The behavior of a convex function everywhere is constrained by its behavior at the boundary.
-Therefore, we need only that the underlying density resembles a product density at the boundary, which is exactly the notion that boundary flatness formalizes.
+The intuition behind our result is the following. Start with the fact
+that convex functions are additively faithful under a product
+density. Next observed that the behavior of a convex function is constrained
+by its behavior at the boundary; in particular, it is identically zero
+if it's zero on the boundary. Therefore, it is sufficient if the 
+underlying density resembles a product density at the boundary.  This is
+exactly the notion that boundary flatness formalizes.
 
-What we think is that, for functions with shape-constraints such as convexity, the metric entropy alone does not determine the hardness of variable selection; the shape-constraint too plays a direct role.
+At a high level, our results show that for functions with
+shape-constraints such as convexity, the metric entropy alone does not
+determine the hardness of variable selection.  The shape constraints
+also play a direct role.
 
-We have further expanded the paragraph discussing the intuition behind additive faithfulness in the paper--the second paragraph right below Theorem 3.1.
+We have expanded the paragraph discussing the intuition behind
+additive faithfulness in the paper. Please see the second paragraph
+after Theorem 3.1.
 
@@
 
+We have corrected all the minor mistakes found by the reviewers.
 We have added a concise definition of AC/DC in Section 2.2, before Theorem 3.
-
-We have corrected all the minor mistakes found by the reviewers.
 
@@
 
-If the true regression function is a convex additive function, then additive faithfulness holds trivially--the best additive approximation to an additive function is the function itself.
-The estimation procedure becomes simpler--the DC stage is no longer necessary and can be safely removed.
+If the true regression function is a convex additive function, then
+additive faithfulness holds----the best additive approximation
+to an additive function is the function itself. The estimation
+procedure becomes simpler.  In this case the DC stage is no longer necessary and can
+be safely removed.
 
@@
 
-Smoothness can be incorporated by using B-spline basis with uniformly spaced knots.
-The details are described in a 2014 paper by Pya and Wood which we have cited in the introduction.
-We chose not to add smoothness into the estimation because it would introduce an additional tuning parameter.
+Smoothness can be incorporated by using a B-spline basis with uniformly
+spaced knots. The details are described in a 2014 paper by Pya and
+Wood which we have cited in the introduction. We choose not to add
+smoothness into the estimation because it introduces 
+additional tuning parameters, which are difficult to set for
+additive models.
 
-The analysis may require much more work if one uses a B-spline basis in the estimation.
-B-splines may complicate the false positive analysis, which rely on the particular form of the optimization objective.
-The false negative analysis may not be affected much because it mainly uses bracketing entropy.
+The analysis would require much more work if one were to use a B-spline basis
+in the estimation. In particular, B-splines may complicate the false positive
+analysis, which relies on the particular form of the optimization
+objective. The false negative analysis may however not be affected much,
+because it is mainly based on bracketing entropy.
 
 \item \rc{Assuming model selection consistency, can one derive prediction
-error bounds using the fitted $f_k$'s and $g_k$'s, as well? Prediction error
+error bounds using the fitted $f_k$s and $g_k$s, as well? Prediction error
 bounds seem quite relevant due to possible model misspecification when
@@
 
-To minimize predictive error, we can refit a non-additive convex function after selecting a sparse model.
-Comparing the predictive accuracy of $f^*_k$'s and $g^*_k$'s against the non-additive true regression function $f_0$ is beyond the scope of our paper, but we do compare the finite sample estimate $\hat{f}_k$ and $\hat{g}_k$ against the population level $f^*_k$ and $g^*_k$.
-The analysis we do to control false negatives also shows that $$\left| \mathbb{E}\left( f_0(X)  - \sum_{k=1}^p f^*_k(X_k) \right)^2 - \mathbb{E} \left( f_0(X) - \sum_{k=1}^p \hat{f}_k(X_k))\right)^2 \right| \rightarrow 0$$ and likewise for the $\hat{g}_k$'s.
-Please see Theorem 8.3 and 8.4 in the supplement.
+To minimize predictive error, we can refit a non-additive convex
+function after selecting a sparse model. Comparing the predictive
+accuracy of the $f^*_k$s and $g^*_k$s against the non-additive true
+regression function $f_0$ is beyond the scope of our paper, but we do
+compare the finite sample estimate $\hat{f}_k$ and $\hat{g}_k$ against
+the population level $f^*_k$ and $g^*_k$. Our analysis to
+control false negatives also shows that $$\left| \mathbb{E}\left(
+f_0(X) - \sum_{k=1}^p f^*_k(X_k) \right)^2 - \mathbb{E} \left( f_0(X)
+- \sum_{k=1}^p \hat{f}_k(X_k))\right)^2 \right| \rightarrow 0$$ and
+likewise for the $\hat{g}_k$s. Please see Theorem 8.3 and 8.4 in the
+supplement.
 
@@
 additive model at the top of page 5: $f(x_i) = \sum_{k=1}^p f_k(x_{ik})$, where the
-$f_k$'s are convex.  Otherwise, the notation in equation (2.3) is
+$f_k$s are convex.  Otherwise, the notation in equation (2.3) is
 initially a bit confusing.}
 
-We have removed the old equation (2.3) and any discussion of convex additive model at the top of page 5. Everything there is discussed now on page 6, after AC/DC has been introduced.
+We have removed the old equation (2.3), and moved discussion of convex
+additive models to after AC/DC has been introduced, on page 6.
 
@@
 
-We sometimes need a notation for the distribution because we want to write $L^2(P), L_2(P)$ to represent, respectively, the Hilbert space of square integrable functions and the $L_2$-norm with respect to the distribution $P$.
-We have removed any mention of the distribution where it is not necessary.
+We sometimes prefer notation involving the distribution because we want to
+write, for example, $L^2(P)$ to represent the Hilbert space
+of square integrable functions with respect to the
+distribution $P$. We have removed any mention of the distribution
+where it is not necessary.
 
-We have changed all ``F'' to ``P'' to represent the distribution, and, to avoid confusing the density with the dimensionality, we now write $p(x)$ instead of just $p$ whenever we refer to the density.
-We believe that this change, along with the context, are enough to disambiguate the two quantities.
+We have changed all $F$ notation to $P$ notation to represent the
+distribution. To avoid confusing the density with the
+dimension, we now write $p(x)$ instead of just $p$ whenever we
+refer to the density. We believe that this change, along with the
+context, should be enough to disambiguate the two quantities.
 
@@
 
-We have added the dependence on the lower bound $c_l$ of $p(x)$ in Theorem 5.2, where we require that $p \leq O(\exp(cn))$ for $c < \frac{c_l}{32}$.
-We have also added the dependence on the upper bound $c_u$ of the density in Theorem 5.3.
-The lower and upper bounds $c_l, c_u$ do not directly play the role of the signal level; they are used to simplify technicalities in the presentation and the proof of the theorems.
-For example, Theorem 5.2 should also go through if one assumes only that the marginal densities $p(x_j)$'s are positive on a sub-interval of $[-1,1]$.
+We have added the dependence on the lower bound $c_l$ of $p(x)$ in
+Theorem 5.2, where we require that $p \leq O(\exp(cn))$ for $c <
+\frac{c_l}{32}$. We have also added the dependence on the upper bound
+$c_u$ of the density in Theorem 5.3. The lower and upper bounds $c_l,
+c_u$ do not directly play the role of the signal level; they are used
+to simplify technicalities in the presentation and the proof of the
+theorems. For example, Theorem 5.2 should also go through if one
+assumes only that the marginal densities $p(x_j)$ are positive on a
+sub-interval of $[-1,1]$.
 
@@
 
-We have added an additional simulation comparing the variables selected via the AC stage and the DC stage.
-Please see the last paragraph in Section 6.1 as well as Figure 6.
-The DC stage is slightly helpful in recovering the true variables but its effect is insignificant.
-We believe that the DC stage is important in theory but not so in practice.
+We have added an additional simulation comparing the variables
+selected via the AC stage and the DC stage. Please see the last
+paragraph in Section 6.1 as well as Figure 6. The DC stage is slightly
+helpful in recovering the true variables but its effect is
+insignificant. We believe that the DC stage is important in theory, but
+not in practice.
 
@@
 \item \rc{I have a problem with the assertion of
-  uniqueness in Lemma 3.1 and Therorem 3.2. First, in Lemma 3.1, it is
+  uniqueness in Lemma 3.1 and Theorem 3.2. First, in Lemma 3.1, it is
   clear that $f^∗$ is unique. But $(f_1^∗, \ldots, f_p^∗)$ is not. What is
@@
   of page 17) is not at all correct.
-   Now, to see why I think that, with the assumtions made on $X$, there is
+   Now, to see why I think that, with the assumptions made on $X$, there is
    not uniqueness, simply suppose for instance that $p = 2$ and $X_2 = g(X_1)$
@@
 
-We have corrected the proof of Lemma 3.1 and we have given a more rigorous proof that the components $f^*_k$'s are unique in a new Lemma 8.3 (old Lemma 8.3 was removed).
-Our result requires that the density $p(\mathbf{x}) > 0$ and thus, the $X_2 = g(X_1)$ example raised by the reviewer is ruled out.
+We have corrected the proof of Lemma 3.1 and we have given a more
+rigorous proof that the component $f^*_k$s are unique in a new Lemma
+8.3 (old Lemma 8.3 was removed). Our result requires that the density
+is strictly positive, and thus, the $X_2 = g(X_1)$ example raised by the
+reviewer is ruled out.
 
@@
 
-\item \rc{On page 11, after Deônition 3.2, it is written ``when the joint
+\item \rc{On page 11, after Definition 3.2, it is written ``when the joint
 density satisfies the property that
@@
 $\frac{\partial^2 p(x_{-j} |  x_j)}{\partial x_j^2}$
-and adn 
+and 
 $\frac{\partial^2 f(x_{-j} |  x_j)}{\partial x_j^2}$
@@
 
-We do need a boundedness condition here.
-We have modified the definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$ is bounded and has a bounded first and second derivative for all $x_j$ in some open set around the boundary points and for all $\mathbf{x}_{-j}$.
-Dominated convergenc theorem holds without problems because we only exchange the derivative and the integral at $x_j = 0,1$.
-We have verified in detail that the domination condition holds in the newly added Section 8.4.1.
+We do need a boundedness condition here. We have modified the
+definition of boundary flatness so that $p(\mathbf{x_{-j}} \,|\, x_j)$
+is bounded and has a bounded first and second derivative for all $x_j$
+in some open set around the boundary points and for all
+$\mathbf{x}_{-j}$. The dominated convergence theorem holds 
+because we only exchange the derivative and the integral at $x_j =
+0,1$. We have verified in detail that the domination condition holds
+in the newly added Section 8.4.1.
 
@@
 \item \rc{On page 13, on line 23, I do not think $\Sigma$ has been defined. Besides it
-is not speciôed that $Var(X_1) = 1$.}
+is not specified that $Var(X_1) = 1$.}
 
@@
 
-%\item \rc{On page 16, in the expresson of $c^∗$, the
+%\item \rc{On page 16, in the expression of $c^∗$, the
 %  denominator should be $\E X_k^2 −m_k^2$.}
@@
 
-This has been fixed. We have also gone through the paper and corrected all instances of the $f_{ik}, f_{ki}$ notation inconsistency so that $i$ always come before $k$.
+This has been fixed. We have also gone through the paper and corrected
+all instances of the $f_{ik}, f_{ki}$ notation inconsistency so that
+$i$ always comes before $k$.
 
@@
 
-%\item \rc{On page 22, in Deônition 5.1, the inequalities
+%\item \rc{On page 22, in Definition 5.1, the inequalities
 %  about $d_k$ must be replaced by the same inequalities as in Proposition 4.1.}
@@
 
-The infimum is achieved by some $f \neq f^*$ since the constraint set $\{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)\}$ is a finite union of closed convex sets.
-It is $\bigcup_k \{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) = \textrm{supp}(f^*) - \{k\}\}$.
-Therefore, the infimum is the minimum of a finite number of projections onto closed convex sets.
-We have changed the ``inf'' to ``min'' and added an explanation in the paper to remove the confusion.
+The infimum is achieved by some $f \neq f^*$ since the constraint set
+$\{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) \subsetneq
+\textrm{supp}(f^*)\}$ is a finite union of closed convex sets. It is
+$\bigcup_k \{ f \in \mathcal{C}^p_1 \,:\, \textrm{supp}(f) =
+\textrm{supp}(f^*) - \{k\}\}$. Therefore, the infimum is the minimum
+of a finite number of projections onto closed convex sets. We have
+changed the ``inf'' to ``min'' and added an explanation in the paper
+to remove the confusion.
 
@@
 
-The square is not an error.
-We have a stronger requirement on the signal strength for the DC stage.
-This is because the $\hat{g}_k$'s are fitted onto the finite sample residual and thus, we need $\hat{f}$ to be close to $f^*$ in order to be able to prove something about the $\hat{g}_k$'s.
+The square is not an error. We have a stronger requirement on the
+signal strength for the DC stage. This is because the $\hat{g}_k$s
+are fitted onto the finite sample residual and thus, we need $\hat{f}$
+to be close to $f^*$ in order to be able to prove something about the
+$\hat{g}_k$s.
 
@@
 
-We have further explained the old figure 5a and 5b (now figure 7a and 7b) in the experiment section. The following has been added to the paper:
+We have further explained the old Figures 5a and 5b (now Figure 7a and
+7b) in the experiment section. The following has been added to the
+paper:
 
-``...
-we plot on the y-axis the norm $\|f^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$.
-Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|f^{(t)}_j\|_{\infty}}{\sum_j \|f^{(1)}\|_{\infty}}$.
-Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.''
+``... we plot on the $y$-axis the norm $\|f^{(t)}_j\|_{\infty}$ of every
+column $j$ against the regularization strength
+$\lambda^{(t)}$. Instead of plotting the value of $\lambda^{(t)}$ on
+the $x$-axis however, we plot the total norm at $\lambda^{(t)}$
+normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j
+  \|f^{(t)}_j\|_{\infty}}{\sum_j \|f^{(1)}\|_{\infty}}$. Thus, as
+$x$ moves from 0 to 1, the regularization goes from strong to
+weak.''
 
@@
 
-We cannot move the third paragraph to the beginning because it is not clear at that point that $k$ is fixed.
-We have corrected all the notations before the third paragraph so that the notations are consistent.
+We cannot move the third paragraph to the beginning because it is not
+clear at that point that $k$ is fixed. We have corrected all of the
+notation before the third paragraph to be
+consistent.
 
@@
 
-We have corrected the instances in which we erroneously omitted ``... components bounded by $B$''.
+We have corrected the instances in which we erroneously omitted ``...components bounded by $B$''.
 
@@
 
-The $\epsilon$ we choose is sufficient to get the bounds we want but it does not exactly balance the terms.
-We left dependence on $\delta$ out of the $\epsilon$ intentionally because we need to verify that $\epsilon$ satisfies certain conditions, see Equation (8.12) for instance.
-These conditions are much easier to verify if $\epsilon$ does not depend on $\delta$, which we set to be $1/n$ only at the end.
-We have updated the paper to clearly state that we use a suboptimal $\epsilon$.
+The $\epsilon$ we choose is sufficient to get the bounds we want but
+it does not exactly balance the terms. We left dependence on $\delta$
+out of the $\epsilon$ intentionally because we need to verify that
+$\epsilon$ satisfies certain conditions; see Equation (8.12) for
+instance. These conditions are much easier to verify if $\epsilon$
+does not depend on $\delta$, which we set to be $1/n$ only at the
+end. We have updated the paper to clearly state that we use a
+suboptimal $\epsilon$.
 
@@
 
-We also use a suboptimal $\epsilon$ here for convenience. We have updated the paper to clearly state that.
+We also use a suboptimal $\epsilon$ here for convenience. We have updated the paper to clearly state this.
 
@@
 
-The old Lemma 8.3 has been removed.
-We now just need $x_{-k} \rightarrow p(x_{-k} \,|\, x_k)$ to be bounded, which has been added as a condition.
-(We now assume for convenience that the joint density $p(\mathbf{x})$ be bounded away from 0 and $\infty$.)
+The old Lemma 8.3 has been removed. We now just need $x_{-k}
+\rightarrow p(x_{-k} \,|\, x_k)$ to be bounded, which has been added
+as a condition. (We now assume for convenience that the joint density
+$p(\mathbf{x})$ is bounded away from 0 and $\infty$.)
 
@@
 condition. This condition seems to be an artifact of the analysis and
-based on my reading, it is unclear how restrctive this assumption
+based on my reading, it is unclear how restrictive this assumption
 is. The authors claim it is weak just after stating it and then
@@
 
-The boundary flatness condition is not restrictive in the sense that for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon > 0$, there exists a boundary flat density whose $L_1$ distance with $p(x)$ is at most $\epsilon$ (Please see the newly added Example 3.3).
-This is because boundary flatness places no restriction on what $p(x)$ looks like in the interior of the hypercube.
-Boundary flatness allows arbitrary correlation structure, provided that $p(x) > 0$.
-We have added Section 3.2 to the paper to give a more detailed discussion on boundary flatness.
+The boundary flatness condition is not restrictive in the sense that
+for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon >
+0$, there exists a boundary flat density whose $L_1$ distance with
+$p(x)$ is at most $\epsilon$. Please see the newly added Example
+3.3. This is because boundary flatness places no restriction on what
+$p(x)$ looks like in the interior of the hypercube. Boundary flatness
+allows arbitrary correlation structure, provided that $p(x) > 0$. We
+have added Section 3.2 to the paper to give a more detailed discussion
+of boundary flatness.
 
-$f(x_1,x_2) = x_1 x_2$ is non-convex and it is an example of how non-convex functions may not be additively faithful under the uniform distribution; it is not an example in which boundary flatness doesn't hold.
-The multivariate Gaussian is a counterexample but it is to show that boundary flatness may not extend easily to densities with unbounded support.
+$f(x_1,x_2) = x_1 x_2$ is non-convex and it is an example of how
+non-convex functions may not be additively faithful under the uniform
+distribution; it is not an example for which boundary flatness fails
+to hold. The multivariate Gaussian counterexample is used to show
+that boundary flatness may not extend easily to densities with
+unbounded support.
 
@@
 
-Boundary flatness is not a contrived condition.
-We initially proved additive faithfulness only for product densities.
-Then, knowing that the behavior of a convex function everywhere is constrained by its behavior at the boundary, we conjectured that underlying density may only need to ``look like'' a product density at the boundary.
-Attempts to formalize this notion led us to the definition of boundary flatness.
+Boundary flatness is not a contrived condition. We initially proved
+additive faithfulness only for product densities. Then, knowing that
+the behavior of a convex function everywhere is constrained by its
+behavior at the boundary, we conjectured that the underlying density may
+only need to ``look like'' a product density at the boundary. Attempts
+to formalize this notion led us to the definition of boundary
+flatness.
 
@@
 
-We have removed old experiments that use correlated multivariate Gaussian and replaced them instead with new experiments that use boundary flat Gaussian Copula mixture distributions.
-Please see Section 6.1; Figure 4 in particular shows the bimodal marginal density of the new joint density that we use.
-Figure 5d, 5e, 5f show the result of simulations using the new non-Gaussian density.
+We have replaced the experiments that use correlated multivariate
+Gaussians with new experiments that use
+boundary flat Gaussian Copula mixture distributions. Please see
+Section 6.1; Figure 4 in particular shows the bimodal marginal density
+of the new joint density that we use. Figures 5d, 5e, and 5f show the
+result of simulations using the new non-Gaussian density.
 
-We have also added new experiments that use nonparametric true regression function instead of the quadratic form.
-We use a log-sum-exp (softmax) of linear forms (please see Equation 6.1).
-Figure 5f and 6 show the results of experiments using the softmax as the true regression function: AC/DC is still effective under the high-dimensional scaling.
+We have also added new experiments that use nonparametric 
+regression functions instead of the quadratic form. We use a
+log-sum-exp (softmax) of linear forms (please see Equation
+6.1). Figures 5f and 6 show the results of experiments using the
+softmax as the true regression function: AC/DC is still effective
+under a high-dimensional scaling.
 
@@
 
-Section 2 is repetitive but we believe it has value in highlighting the big picture, which could otherwise be drowned out by the technical details.
+Section 2 is repetitive but we believe it has value in highlighting
+the big picture, which could otherwise be obscured by the technical
+details.
 

### 2015-05-15 tex/scam/experiments.tex
a

@@
 
-In Figure~\ref{Boston}(a), we plot on the y-axis the norm $\|\bds{f}^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$.
-Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|\bds{f}^{(t)}_j\|_{\infty}}{\sum_j \|\bds{f}^{(1)}\|_{\infty}}$.
-Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak.
-For comparison, we
-plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(b).
-From the figures we observe that the first three variables selected by
+In Figure~\ref{Boston}(a), we plot on the $y$-axis the norm
+$\|\bds{f}^{(t)}_j\|_{\infty}$ of every column $j$ against the
+regularization strength $\lambda^{(t)}$. Instead of plotting the value
+of $\lambda^{(t)}$ on the $x$-axis,  however, we plot the total norm at
+$\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$:
+$\frac{\sum_j \|\bds{f}^{(t)}_j\|_{\infty}}{\sum_j
+  \|\bds{f}^{(1)}\|_{\infty}}$. Thus, as $x$ moves from 0 to 1, the
+regularization goes from strong to weak. For comparison, we plot the
+LASSO/LARS result in a similar way in Figure \ref{Boston}(b).  From
+the figures we observe that the first three variables selected by
 AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
@@
 regularization, and plot the estimated additive functions in Figure
-\ref{Boston}(d). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
-nonlinear effects which cannot be captured by LASSO. The shapes of
-these functions, including the concave shape of the \tts{PTRATIO} function, are in agreement with those obtained by
-SpAM~\citep{SpAM:07}.
+\ref{Boston}(d). When refitting, we constrain a component to be convex
+if it is non-zero in the AC stage and concave if it is non-zero in the
+DC stage. As can be seen, these functions contain clear nonlinear
+effects which cannot be captured by LASSO. The shapes of these
+functions, including the concave shape of the \tts{PTRATIO} function,
+are in agreement with those obtained by SpAM~\citep{SpAM:07}.
 

### 2015-05-15 tex/scam/sparsistency.tex
a

@@
 the now standard \emph{primal-dual witness}
-technique~\citep{wainwright2009sharp}.
-The conditions in Theorem~\ref{thm:deterministic} is our analogue to the \emph{mutual incoherence} condition.
-Our conditions are much more strict however because the estimation is
-nonparametric---even the low dimensional restricted regression has
-$s(n-1)$ variables.
+technique~\citep{wainwright2009sharp}. The conditions in
+Theorem~\ref{thm:deterministic} are analogues of the \emph{mutual
+  incoherence} conditions. Our conditions are much more strict, however,
+because the estimation is nonparametric---even the low dimensional
+restricted regression has $s(n-1)$ variables.
 

### 2015-05-15 tex/scam/experiments.tex
a

@@
 We measure success not through exact recovery but through faithful recovery.
-We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall (true sparsisty $s=5$).
+We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall (true sparsity $s=5$).
 We use the same $\lambda$ as before.
@@
 The softmax function is more challenging to estimate than the quadratic function; the softmax function requires about $n > 1500$ to achieve the same success probability as the quadratic function with $n=1000$.
-Regardless, we see that increasing the ambient dimension $p$ does not signficantly affect the recovery probability.
+Regardless, we see that increasing the ambient dimension $p$ does not significantly affect the recovery probability.
 

### 2015-05-15 tex/scam/reviews-v1/response-v1.tex
a

@@
 
-Major comments:
+\begin{enumerate}
 
-\begin{enumerate}
+\item \rc{I don't see why one would use convex regression to do
+  variable screening when other parametric approaches seem more
+  appropriate (e.g. clean and screen methods by Ke et al. and
+  others). This method and others were compared with and so it again
+  raised the question of what class of interesting examples would this
+  method be useful for.}
+
+Our methods are appropriate in settings where one expects the
+regression function to be convex, for example in utility function
+estimation in economics. The power of our results is that
+using convex additive models results in consistent variable selection.
+In more general settings, without this shape constraint,
+approaches based on the lasso (``screen and clean'') or nonparametric 
+additive models do not have such guarantees.
+
+Also note that we have replaced the multivariate Gaussian examples with 
+nonparametric examples; please see point 3 below.
+
 \item \rc{The basis of all the results seem to be the boundary flatness

### 2015-05-15 tex/scam/reviews-v1/response-v1.tex
a

@@
 regression function to be convex, for example in utility function
-estimation in economics. The power of our results is that
-using convex additive models results in consistent variable selection.
+estimation in economics. The power of our framework and analysis is that
+using convex additive models leads to consistent variable selection.
 In more general settings, without this shape constraint,
@@
 
-We acknowledge that many distributions are not boundary flat.
-We present boundary flatness as a significant generalization of the product density, under which nonparametric variable selection is already very difficult.
+We acknowledge that many distributions are not boundary flat. We
+present boundary flatness as a significant generalization of the
+product density, under which nonparametric variable selection is
+already very difficult (Comminges and Dalalyan, 2012).
 

### 2015-05-15 tex/scam/summary.tex
defn change

@@
   Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. Then $p$
-  satisfies the \emph{boundary flatness condition} if for all $j$, and
+  satisfies the \emph{boundary flatness condition} if it satisfies certain regularity conditions (see precise statement in Definition~\ref{defn:boundary-point}) and if for all $j$, and
   for all $\mathbf{x}_{-j}$,

### 2015-05-15 tex/scam/additive_faithful.tex
a

@@
 \label{defn:boundary-point}
-Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.
-We say that $p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if for all $j$, for all $\mathbf{x}_{-j}$, and for all $x_j \in [0, \epsilon) \cup (1-\epsilon, 1]$ for some arbitrarily small $\epsilon > 0$, $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in $x_j$, that $p(\mathbf{x}_{-j} \given x_j), \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2 p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded, and that
+Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. We say that
+$p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if
+for all $j$, for all $\mathbf{x}_{-j}$, and for all $x_j \in [0,
+  \epsilon) \cup (1-\epsilon, 1]$ for some arbitrarily small $\epsilon
+> 0$, 
+\begin{enumerate}[(i)]
+\item $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in
+$x_j$,
+\item $p(\mathbf{x}_{-j} \given x_j), \frac{\partial
+  p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2
+  p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded,
+\item for $x_j=0$ and $x_j=1$,
 \begin{equation}
 \frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
-\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
-\quad \trm{at } x_j = 0, x_j = 1
+\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0.
 \end{equation}
+\end{enumerate}
 
@@
 $f(\mathbf{x})$ and $\phi(\mathbf{x}_{-k})$ are both bounded and so $h^*_k(x_k)$ is bounded as well.
-Therefore, $h^*_k$ is square integrable and there exists a fourier series $s_n(x_k)$ convergent to $h^*_k$ in $L_2$.
+Therefore, $h^*_k$ is square integrable and there exists a Fourier series $s_n(x_k)$ convergent to $h^*_k$ in $L_2$.
 Since $p(\mathbf{x})$ is bounded, $$\lim_{n \rightarrow \infty} \E \left( s_n(X_k) - h^*_k(X_k ) \right)^2 \rightarrow 0$$ as well.

### 2015-05-15 tex/scam/additive_faithful.tex
a

@@
 $p(\mathbf{x})$ satisfies the \emph{boundary flatness condition} if
-for all $j$, for all $\mathbf{x}_{-j}$, and for all $x_j \in [0,
-  \epsilon) \cup (1-\epsilon, 1]$ for some arbitrarily small $\epsilon
-> 0$, 
+for all $j$ and for all $\mathbf{x}_{-j}$, 
 \begin{enumerate}[(i)]
-\item $p(\mathbf{x}_{-j} \given x_j)$ is twice differentiable in
-$x_j$,
-\item $p(\mathbf{x}_{-j} \given x_j), \frac{\partial
+\item the derivatives $\frac{\partial
   p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}, \frac{\partial^2
-  p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ are bounded,
+  p(\mathbf{x}_{-j} \given x_j) }{\partial^2 x_j}$ exist and are bounded,
+for all $x_j \in [0,  \epsilon) \cup (1-\epsilon, 1]$ 
+with $\epsilon > 0$ arbitrarily small,
 \item for $x_j=0$ and $x_j=1$,
-\begin{equation}
-\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
-\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0.
-\end{equation}
+$\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
+\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0$.
 \end{enumerate}

### 2015-05-17 tex/scam/introduction.tex
more response
a

--- 2014-10-28 tex/scam/introduction.tex
@@
 understood as more traditional nonparametric estimation involving
-smoothness constraints.  For instance, the minimax rate of convergence
-for multivariate convex regression has yet to be rigorously
-established in full generality.  Even the one-dimensional case is
-challenging, and has been of recent interest \citep{guntusen:13}.
+smoothness constraints.  
+%For instance, the minimax rate of convergence
+%for multivariate convex regression has yet to be rigorously
+%established in full generality.  
+Even the one-dimensional case is
+interesting and challenging, and has been of recent interest \citep{guntusen:13}.
 
@@
 Beyond cases where the assumption of convexity is
-natural, the convexity assumption can be attractive as a
+natural, convexity can be attractive as a
 tractable, nonparamametric relaxation of the linear model.
@@
 Additive shape-constrained estimation has also been studied; \cite{pya2014shape} propose a penalized B-spline estimator while \cite{chen2014generalised} show the consistency of the MLE.
-To the best of our knowledge however, there has been no work on variable selection and high-dimensional estimation of convex functions.
+To the best of our knowledge however, there has been no work on variable selection and estimation of high-dimensional convex functions.
 
@@
 the component Hilbert spaces must be chosen, leading to extra tuning
-parameters that are difficult to select in practice. \cite{huang2010variable} 
-too formulate sparse additive spline fitting as a convex optimization but
-their procedure too requires a smoothing parameter in the form of 
-a truncation level for the spline basis.
+parameters that are difficult to select in practice. There has also been
+work on estimating sparse additive models over a spline basis, for 
+instance the work of \cite{huang2010variable}, but these approaches also
+require the tuning of smoothing parameters.
 

### 2015-05-17 tex/scam/summary.tex
a

--- 2015-05-03 tex/scam/summary.tex
@@
   Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. Then $p$
-  satisfies the \emph{boundary flatness condition} if for all $j$, and
-  for all $\mathbf{x}_{-j}$,
+  satisfies the \emph{boundary flatness condition} if it satisfies
+  certain regularity conditions (see the precise statement in
+  Definition~\ref{defn:boundary-point}) and if for all $j$, and for
+  all $\mathbf{x}_{-j}$,
 \[
@@
 density on $C=[0,1]^p$ that satisfies the boundary flatness
-condition. Suppose that $f$ is convex and continuously twice-differentiable on an open set around $C$.
-and that $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k}
+condition. Suppose that $f$ is convex and continuously twice-differentiable on an open set around $C$
+and that the derivatives $\partial_{x_k} f$, $\partial_{x_k} p( \mathbf{x}_{-k}
 \given x_k )$, and $\partial_{x_k}^2 p( \mathbf{x}_{-k} \given x_k)$
@@
 \end{equation} where $\mathcal{C}^1$ is the set of univariate convex
-functions, and, with respective to $f^*_k$'s from above, define
+functions.  Using the $f^*_k$s above, define
 \begin{equation}
@@
 
-Given samples $(y_i, X_i)$, AC/DC becomes the following optimization.
+Given samples $(y_i, X_i)$, AC/DC becomes the following optimization:
 \begin{align*}
@@
 where $\tilde{\sigma} \equiv \max(\sigma, B)$ and $c$ is a constant dependent only on $b, c_1$.
-
-Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$:
+Then, for sufficiently large $n$, with probability at least $1-\frac{1}{n}$,
 \begin{align*}
@@
 
-We remark that \citet{dalalyan:12} show that, even with the product distribution,
- under traditional smoothness
-constraints, variable selection is achievable only if $n > O(e^s)$. 
+We remark that \citet{dalalyan:12} show that, even under the product distribution,
+variable selection is achievable under traditional smoothness constraints only if $n > O(e^s)$. 
 Here we demonstrate that convexity yields the scaling $n =

### 2015-05-18 tex/scam/additive_faithful.tex
a

@@
 relevant variable being incorrectly marked as irrelevant. Such
-mistakes are inherent to the approximation and may persist even in
+mistakes are inherent in the approximation and may persist even in
 the population setting.  In this section we give
@@
 
-We note that $\E[ f(X) -\sum_{k'\neq k} f^*_{k'}(X_{k'}) | x_k] - \E f(X)$ has mean zero as a function of $x_k$, which shows that $f^*_k$'s are feasible.
-
+We note that $\E[ f(X) -\sum_{k'\neq k} f^*_{k'}(X_{k'}) | x_k] - \E
+f(X)$ has mean zero as a function of $x_k$, which shows that the $f^*_k$s
+are feasible.
 \end{proof}
@@
 characterize below, convex multivariate functions are additively
-faithful. To simplify presentation, we restrict our attention to densities bounded away from $0/\infty$, that is, $0 < \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) < \infty$.
+faithful. To simplify the presentation, we restrict our attention to
+densities bounded away from $0/\infty$, that is, $0 < \inf
+p(\mathbf{x}) \leq \sup p(\mathbf{x}) < \infty$.
 
@@
 both close to the same boundary point. It is thus much more general
-than product densities. Boundary flatness is a weak condition because
-it affects only an $\epsilon$-small region around the boundary;
-$p(\mathbf{x}_{-j} \given x_j)$ can take arbitrary shapes away from
-the boundary. Boundary flatness also allows arbitrary correlation
-structure between the variables (provided $p(\mathbf{x}) >0$). In
-Section~\ref{sec:boundary_flat}, we give a detailed discussion of the
-boundary flatness condition and show examples of boundary flat
-densities. In particular, we show that any density supported on a
-compact set can be approximated arbitrarily well by boundary flat
-densities.
+than requiring the density to be a product density. Boundary flatness
+is a weak condition because it affects only an $\epsilon$-small region
+around the boundary; $p(\mathbf{x}_{-j} \given x_j)$ can take
+arbitrary shapes away from the boundary. Boundary flatness also allows
+arbitrary correlation structure between the variables (provided
+$p(\mathbf{x}) >0$). In Section~\ref{sec:boundary_flat}, we give a
+detailed discussion of the boundary flatness condition and show
+examples of boundary flat densities. In particular, we show that any
+density supported on a compact set can be approximated arbitrarily
+well by boundary flat densities.
 
@@
 \label{thm:convex_faithful}
-Let $p(\mathbf{x})$ be a density supported on $C=[0,1]^p$ and bounded away from $0/\infty$ that satisfies the boundary flatness property.
-
-Suppose $f$ is a convex with a bounded second derivative on an open set containing $C$, then $f$ is additively faithful under $p(\mathbf{x})$.
+Let $p(\mathbf{x})$ be a density supported on $C=[0,1]^p$ and bounded
+away from $0/\infty$ that satisfies the boundary flatness property.  
+Suppose $f$ is a convex function with bounded second derivatives on an
+open set containing $C$. Then $f$ is additively faithful under $p(\mathbf{x})$.
 \end{theorem}
 
-We let the domain of $f$ be slightly larger than $C$ for a technical reason--it is so we can say in the proof that the Hessian of $f$ is positive semidefinite even at the boundary of $C$.
+We let the domain of $f$ be slightly larger than $C$ for a technical
+reason--it is so we can say in the proof that the Hessian of $f$ is
+positive semidefinite even at the boundary of $C$.
 
@@
 
-We differentiate with respect to $x_k$ at $x_k = 0,1$ under the integral.
-The detail necessary to verify the validity of this operation is technical and given in Section~\ref{sec:dominated_condition} of the supplementary material.
+We differentiate with respect to $x_k$ at $x_k = 0,1$ under the
+integral. The details necessary to verify the validity of this
+operation are technical and given in
+Section~\ref{sec:dominated_condition} of the supplementary material.
 
@@
 \label{ex:joint_density_flat}
-Boundary flatness is satisfied if the joint density becomes flat at the boundary. To be precise, let $p(\mathbf{x})$ be a joint density bounded away from $0/\infty$ with a bounded second derivative.
-
+Boundary flatness is satisfied if the joint density becomes flat at
+the boundary. To be precise, let $p(\mathbf{x})$ be a joint density
+bounded away from $0/\infty$ with a bounded second derivative.
 Suppose also, for all $j$,
@@
 \partial_{x_j} p(x_j,\mathbf{x}_{-j}) =
-\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0\quad  \trm{at $x_j = 0, 1$,}.
-$$
-It is then straightforward to show boundary flatness.
-One can first verify that the derivatives of the marginal density $p(x_j)$ vanishes at $x_j = 0,1$ and then apply the quotient rule on $\frac{p(x_j,\mathbf{x}_{-j}}{p(x_j)}$ to show that $\partial_{x_j} p(\mathbf{x}_{-j} \given x_j) = \partial_{x_j}^2 p(\mathbf{x}_{-j} \given x_j) = 0$ at $x_j = 0,1$ as well.
+\partial_{x_j}^2 p(x_j, \mathbf{x}_{-j}) = 0\quad  \trm{at $x_j = 0, 1$}.
+$$ It is then straightforward to show boundary flatness. One can first
+verify that the derivatives of the marginal density $p(x_j)$ vanish
+at $x_j = 0,1$ and then apply the quotient rule on
+$\frac{p(x_j, \mathbf{\scriptstyle x}_{-j})}{p(x_j)}$ to show that $\partial_{x_j}
+p(\mathbf{x}_{-j} \given x_j) = \partial_{x_j}^2 p(\mathbf{x}_{-j}
+\given x_j) = 0$ at $x_j = 0,1$ as well.
 \end{example}
 
-The next example shows that any bounded density over a hypercube can be approximated arbitrarily well by boundary flat densities.
+The next example shows that any bounded density over a hypercube can
+be approximated arbitrarily well by boundary flat densities.
 
@@
 \label{ex:mixture_approx}
-Suppose $p_\epsilon(\mathbf{x})$ is a bounded density over $[\epsilon, 1-\epsilon]^p$ for some $0 < \epsilon < 1/2$.
-Let $q(\mathbf{x})$ be an arbitrary boundary flat density over $[0,1]^p$ (one can take the uniform density for instance).
-Define a mixture $p_{\lambda, \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda) p_\epsilon(\mathbf{x})$ where $0 < \lambda \leq 1$, then $p_{\lambda, \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
+Suppose $p_\epsilon(\mathbf{x})$ is a bounded density over $[\epsilon,
+  1-\epsilon]^p$ for some $0 < \epsilon < 1/2$. Let $q(\mathbf{x})$ be
+an arbitrary boundary flat density over $[0,1]^p$ (one can take the
+uniform density for instance). Define a mixture $p_{\lambda,
+  \epsilon}(\mathbf{x}) = \lambda q(\mathbf{x}) + (1-\lambda)
+p_\epsilon(\mathbf{x})$ where $0 < \lambda \leq 1$; then $p_{\lambda,
+  \epsilon}(\mathbf{x})$ is boundary flat over $[0,1]^p$.
 
-Now, let $p(\mathbf{x})$ be a bounded density over $[0,1]^p$.
-Let $p_\epsilon(\mathbf{x})$ be the density formed from truncating $p(\mathbf{x})$ in $[\epsilon, 1-\epsilon]^p$.
-The corresponding mixture $p_{\lambda,\epsilon}(\mathbf{x})$ then approximates $p(\mathbf{x})$ when $\lambda$ and $\epsilon$ are both small.
+Now, let $p(\mathbf{x})$ be a bounded density over $[0,1]^p$. Let
+$p_\epsilon(\mathbf{x})$ be the density formed from truncating
+$p(\mathbf{x})$ in $[\epsilon, 1-\epsilon]^p$. The corresponding
+mixture $p_{\lambda,\epsilon}(\mathbf{x})$ then approximates
+$p(\mathbf{x})$ when $\lambda$ and $\epsilon$ are both small.
 
-Since $p_{\lambda,\epsilon}(\mathbf{x})$ remains boundary flat for arbitrarily small $\epsilon$ and $\lambda$, $p(\mathbf{x})$ can be approximated arbitrarily well (in $L_1$ for example) by boundary flat densities.
+Since $p_{\lambda,\epsilon}(\mathbf{x})$ remains boundary flat for
+arbitrarily small $\epsilon$ and $\lambda$, $p(\mathbf{x})$ can be
+approximated arbitrarily well (in $L_1$ for example) by boundary flat
+densities.
 \end{example}
@@
 
-If $p(\mathbf{x})$ is a product density, then $\E[ f(X) \given x_k]$ is convex in $x_k$ and the additive projection is simultaneously the convex additive projection.
-Thus, in this case, additive faithfulness trivially holds for the convex additive projection.
-For a general boundary flat density $p(\mathbf{x})$ however, the additive projection need not be convex and we thus cannot say anything about additive faithfulness of the convex additive projection.
+If $p(\mathbf{x})$ is a product density, then $\E[ f(X) \given x_k]$
+is convex in $x_k$ and the additive projection is simultaneously the
+convex additive projection. Thus, in this case, additive faithfulness
+trivially holds for the convex additive projection.  For a general
+boundary flat density $p(\mathbf{x})$ however, the additive projection
+need not be convex and we thus cannot say anything about additive
+faithfulness of the convex additive projection.
 
-Luckily, we can restore faithfulness by coupling the $f^*_k$'s with a set of univariate concave fits on the \emph{residual} $f - f^*$:
+Luckily, we can restore faithfulness by coupling the $f^*_k$s with a set of univariate concave fits on the \emph{residual} $f - f^*$:
 \begin{equation}
@@
 \eqref{eqn:convex_additive} and \eqref{eqn:concave_postprocess}, then
-the $f^*_k$'s and the $g^*_k$'s are unique. Furthermore, $f^*_k = 0$
+the $f^*_k$s and the $g^*_k$s are unique. Furthermore, $f^*_k = 0$
 and $g^*_k = 0$ implies that $\partial_{x_k} f(\mathbf{x}) = 0$, that
@@
 
-We denote $h^*_k(x_k) = \E[ f(X) - \phi(X_{-k}) \given x_k]$.
-$f(\mathbf{x})$ and $\phi(\mathbf{x}_{-k})$ are both bounded and so $h^*_k(x_k)$ is bounded as well.
-Therefore, $h^*_k$ is square integrable and there exists a Fourier series $s_n(x_k)$ convergent to $h^*_k$ in $L_2$.
-Since $p(\mathbf{x})$ is bounded, $$\lim_{n \rightarrow \infty} \E \left( s_n(X_k) - h^*_k(X_k ) \right)^2 \rightarrow 0$$ as well.
+We denote $h^*_k(x_k) = \E[ f(X) - \phi(X_{-k}) \given
+  x_k]$.  Since $f(\mathbf{x})$ and $\phi(\mathbf{x}_{-k})$ are both bounded,
+$h^*_k(x_k)$ is bounded as well. Therefore, $h^*_k$ is square
+integrable and there exists a Fourier series $s_n(x_k)$ convergent to
+$h^*_k$ in $L_2$. Since $p(\mathbf{x})$ is bounded, $$\lim_{n
+  \rightarrow \infty} \E \left( s_n(X_k) - h^*_k(X_k ) \right)^2
+\rightarrow 0$$ as well.
 
@@
 
-If we can show that $\E h^*_k(X_k)^2 = 0$, we would apply Lemma~\ref{cor:faithfulness_extension} and finish the proof. So let us suppose for sake of contradiction that $\E h^*_k(X_k)^2 > 0$.\\
+If we can show that $\E h^*_k(X_k)^2 = 0$, we can apply
+Lemma~\ref{cor:faithfulness_extension} and finish the proof. So let us
+suppose for sake of contradiction that $\E h^*_k(X_k)^2 > 0$.
 
 Let $0 < \epsilon < 1$ be fixed and let $n$ be large enough such that $\E( s_n(X_k) - h^*_k(X_k))^2 \leq \epsilon \E h^*_k(X_k)^2 $.
-
-Since $s_n(x_k)$ is twice-differentiable and has a second derivative bounded away from $-\infty$, there exist some positive scalar $\alpha$ such that $s_n(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second derivative and is thus convex.
+Since $s_n(x_k)$ is twice-differentiable and has a second derivative
+bounded away from $-\infty$, there exists a positive scalar $\alpha$
+such that $s_n(x_k) + \alpha(x_k^2 - m_k^2)$ has a non-negative second
+derivative and is thus convex.
 
@@
 \]
-This is because $c\big( s_n(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered function.
+This is because $c\big( s_n(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is
+convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered
+function.
 
@@
 
-Now we turn to uniqueness.
-Suppose for sake of contradiction that $f^*$ and $\tilde{f}$ are optimal solutions to (\ref{eqn:convex_additive}) and $\E (\tilde{f} - f^*)^2 > 0$.
-$f^* + \lambda ( \tilde{f}  - f^*)$ for any $\lambda \in [0,1]$ must then also be an optimal solution by convexity of the objective and constraint.
-However, the second derivative of the objective $\E( f - f^* - \lambda(\tilde{f} - f^*))^2$ with respect to $\lambda$ is $2 \E( \tilde{f} - f^*)^2 > 0$.
-The objective is thus strongly convex and $\E(f^* - \tilde{f})^2 = 0$.
-We now apply Lemma~\ref{lem:additive_uniqueness} by letting $\phi_k = f^*_k - \tilde{f}_k$.
-We conclude that $\E (f^*_k - \tilde{f}_k)^2 = 0$ for all $k$.
-The uniqueness of $g^*$ is proved similarly.
+Now we turn to uniqueness. Suppose for sake of contradiction that
+$f^*$ and $\tilde{f}$ are optimal solutions to
+(\ref{eqn:convex_additive}) and $\E (\tilde{f} - f^*)^2 > 0$.  $f^* +
+\lambda ( \tilde{f} - f^*)$ for any $\lambda \in [0,1]$ must then also
+be an optimal solution by convexity of the objective and
+constraint. However, the second derivative of the objective $\E( f -
+f^* - \lambda(\tilde{f} - f^*))^2$ with respect to $\lambda$ is $2 \E(
+\tilde{f} - f^*)^2 > 0$. The objective is thus strongly convex and
+$\E(f^* - \tilde{f})^2 = 0$. We now apply
+Lemma~\ref{lem:additive_uniqueness} by letting $\phi_k = f^*_k -
+\tilde{f}_k$. We conclude that $\E (f^*_k - \tilde{f}_k)^2 = 0$ for
+all $k$. The uniqueness of $g^*$ is proved similarly.
 \end{proof}

### 2015-05-18 tex/scam/sparsistency.tex
a

@@
 
-Our goal is to show that variable screening consistency.
-That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Figure~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.
+Our goal is to show variable screening consistency. That is, as
+$n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0
+where $\hat{S}$ is the set of variables output by AC/DC in the
+finite sample setting (Figure~\ref{fig:backfitting:algo}) and $S$ is
+the set of variables output in the population
+setting~\eqref{eqn:acdc_vars_pop}.
 
@@
 deterministic condition for consistency of the sparsity pattern
-screening procedure.  We then consider the stochastic setting and argue that the 
-deterministic conditions hold with high probability. Note that in all of our results 
-and analysis, we let $c,
-C$ represent absolute constants; the actual values of $c,C$ may change from line to line.
-We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$.
-Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis.
-We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{\mu}$ from our estimation procedure.
+screening procedure.  We then consider the stochastic setting and
+argue that the deterministic conditions hold with high
+probability. Note that in all of our results and analysis, we let $c,
+C$ represent absolute constants; the actual values of $c,C$ may change
+from line to line. We derived two equivalent optimizations for AC/DC:
+\eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and
+\eqref{opt:alternate_opt} outputs the second derivatives
+$\hat{d}_k$. Their equivalence is established in
+Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and
+$\hat{f}_k$ in our analysis. We will also assume in this section that
+the true regression function $f_0$ has mean-zero and therefore, we
+will omit the intercept term $\hat{\mu}$ in our estimation
+procedure.
 
-In our analysis, we assume that an upper bound $B$ to $\| \hat{f}_k \|_\infty$ 
-is imposed in the optimization procedure, where $B$ is chosen to also upper bound $\| f^*_k \|_\infty$ (same $B$ as in Assumption A3 in Section~\ref{sec:probabilistic_setting}).
-This $B$-boundedness constraint is added so that we may use the convex function bracketing results from~\cite{kim2014global} to establish uniform convergence between the empirical risk and the population risk.
-We emphasize that this constraint is not needed in practice and we do not use it for any of our simulations.
+In our analysis, we assume that an upper bound $B$ to $\| \hat{f}_k
+\|_\infty$ is imposed in the optimization procedure, where $B$ is
+chosen to also upper bound $\| f^*_k \|_\infty$ (same $B$ as in
+Assumption A3 in Section~\ref{sec:probabilistic_setting}). This
+$B$-boundedness constraint is added so that we may use the convex
+function bracketing results from~\cite{kim2014global} to establish
+uniform convergence between the empirical risk and the population
+risk. We emphasize that this constraint is not needed in practice and
+we do not use it for any of our simulations.
 
@@
 
-Theorem~\ref{thm:deterministic} states that the estimator produces no false positive so long as $\lambda_n$ upper bounds the partial sums of the residual $\hat{r}$ and that the maximum gap between ordered values of $X_k$ is small.
+Theorem~\ref{thm:deterministic} states that the estimator produces no
+false positive so long as $\lambda_n$ upper bounds the partial sums of
+the residual $\hat{r}$ and that the maximum gap between ordered values
+of $X_k$ is small.
 
-This result holds regardless of whether or not we impose the boundedness conditions in optimization~\eqref{opt:alternate_opt} and~\eqref{opt:alternate_opt_concave}.
-The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.
-We allow $S$ in Theorem~\ref{thm:deterministic} to be any set containing the relevant variables; in Lasso analysis, $S$ is taken to be the set of relevant variables; we will take $S$ to be the set of variables chosen by the additive convex and decoupled concave procedure in the population setting, which is guaranteed to contain the relevant variables because of additive faithfulness.
+This result holds regardless of whether or not we impose the
+boundedness conditions in optimization~\eqref{opt:alternate_opt}
+and~\eqref{opt:alternate_opt_concave}.  The full proof of
+Theorem~\ref{thm:deterministic} is in
+Section~\ref{sec:deterministic_proof} of the Appendix. We allow $S$ in
+Theorem~\ref{thm:deterministic} to be any set containing the relevant
+variables; in Lasso analysis, $S$ is taken to be the set of relevant
+variables; we will take $S$ to be the set of variables chosen by the
+additive convex and decoupled concave procedure in the population
+setting, which is guaranteed to contain the relevant variables because
+of additive faithfulness.
 
@@
 \end{equation}
-The $\hat{g}_k$'s are unique minimizers as well.
-We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$.
-By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$.
-In some cases, such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
+The $\hat{g}_k$s are unique minimizers as well. We let $S = \{ k =
+1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s =
+|S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it
+must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases,
+such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
 Each of our theorems will use a subset of the following assumptions:
@@
 \end{align}
-$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$.
-$\alpha_+$ is achieved by some $f \neq f^*$ because the set $\{f\in \mathcal{C}_1^p\,:\, \trm{supp}(f) \subsetneq \textrm{supp}(f^*)\}$ is a finite union of closed convex sets.
-$\alpha_+ > 0$ since $f^*$ is the unique risk minimizer.
-Likewise, $\alpha_-$ lower bounds the excess risk of any decoupled concave fit of the residual $f_0 - f^*$ that is strictly more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$; $\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well.
-These quantities play the role of the absolute value of the smallest nonzero coefficient in the true linear model in lasso theory.
-Intuitively, if
-$\alpha_{+}$ is small, then it is easier to make a false omission in the
-additive convex stage of the procedure. If $\alpha_{-}$ is small, then
-it is easier to make a false omission in the decoupled concave stage
-of the procedure. If $X$ is independent, then $\alpha_+$ can be simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and $\alpha_-$ becomes unnecessary.
+The term $\alpha_+$ is a lower bound on the excess risk incurred by
+any additive convex function whose support is strictly smaller than
+$f^*$. $\alpha_+$ is achieved by some $f \neq f^*$ because the set
+$\{f\in \mathcal{C}_1^p\,:\, \trm{supp}(f) \subsetneq
+\textrm{supp}(f^*)\}$ is a finite union of closed convex
+sets. $\alpha_+ > 0$ since $f^*$ is the unique risk
+minimizer. Likewise, $\alpha_-$ lower bounds the excess risk of any
+decoupled concave fit of the residual $f_0 - f^*$ that is strictly
+more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$;
+$\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well. These
+quantities play the role of the absolute value of the smallest nonzero
+coefficient in the true linear model in lasso theory.  Intuitively, if
+$\alpha_{+}$ is small, then it is easier to make a false omission in
+the additive convex stage of the procedure. If $\alpha_{-}$ is small,
+then it is easier to make a false omission in the decoupled concave
+stage of the procedure. If $X$ is independent, then $\alpha_+$ can be
+simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and
+$\alpha_-$ becomes unnecessary.
 

### 2015-05-18 tex/scam/experiments.tex
a

@@
 \end{equation}
-Here $\x_{i}$ denotes data sample $i$ drawn from some distribution $P$. $f_0$ is the true regression function. $\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=s$, where $S$
+Here $\x_{i}$ denotes data sample $i$ drawn from some distribution
+$P$, and$f_0$ is the true regression function. The variables $\x_{iS}$ are a subset of $\x_i$ with dimension $|S|=s$, where $S$
 represents the set of relevant variables, and 

### 2015-05-18 tex/scam/experiments.tex
a

--- 2015-05-15 tex/scam/experiments.tex
@@
 \begin{equation}\nonumber
-         Y_i = f_o(\x_{iS}) + \epsilon_i \quad (i=1,2,\ldots,n).
+         Y_i = f_0(\x_{iS}) + \epsilon_i \quad (i=1,2,\ldots,n).
 \end{equation}
-Here $\x_{i}$ denotes data sample $i$ drawn from some distribution $P$. $f_0$ is the true regression function. $\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=s$, where $S$
-represents the set of relevant variables, and 
-$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,\sigma)$. For 
-all simulations, we set $\sigma$ such that the signal-to-noise ratio(SNR, $\frac{\trm{std}(Y)}{\sigma}$) is 5.
-Also, for all simulations except the sixth, we choose the set of relevant variables $S$ uniformly at random among all variables $\{1,...,p\}$.
+Here $\x_{i}$ denotes data sample $i$ drawn from some distribution
+$P$, and $f_0$ is the true regression function. The variables
+$\x_{iS}$ are a subset of $\x_i$ with dimension $|S|=s$, where $S$
+represents the set of relevant variables, and $\epsilon_i$ is additive
+noise drawn from $\mathcal{N}(0,\sigma^2)$. For all simulations, we set
+$\sigma^2$ so that the signal-to-noise ratio(SNR,
+$\frac{\trm{std}(Y)}{\sigma}$) is 5. Also, for all simulations except
+the sixth, we choose the set of relevant variables $S$ uniformly at
+random among all variables $\{1,...,p\}$.
 
-We study both the independent case where $P = N(0, I_p)$ and the correlated case where $P$ is a correlated Gaussian Copula modified slightly to satisfy the boundary flatness condition.
-We measure the probability of exact selection in the independent case and the probability of screening in the correlated case.
-We also study both cases where the regression function is parametric (quadratic) and cases where the regression function is nonparametric (softmax of linear forms).
-In all our experiments, we mark a variable as selected if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate $\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$.
-We set $\lambda = 0.5 \sqrt{\frac{\log^2 np}{n}}$ for all the simulations.
+We study both the independent case where $P = N(0, I_p)$ and the
+correlated case where $P$ is a correlated Gaussian Copula modified
+slightly to satisfy the boundary flatness condition. We measure the
+probability of exact selection in the independent case and the
+probability of screening in the correlated case. We also study both
+cases where the regression function is parametric (quadratic) and
+cases where the regression function is nonparametric (softmax of
+linear forms). In all our experiments, we mark a variable as selected
+if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate
+$\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$. We set $\lambda =
+0.5 \sqrt{\frac{\log^2 np}{n}}$ for all the simulations.
 
-For the first three simulations, we will use the quadratic form as our true regression function.
+For the first three simulations, we use a quadratic form as the true regression function,
 \[
-f_0(x_{iS}) = x_{iS}^\tran \Q x_{iS}
+f_0(x_{iS}) = x_{iS}^\tran \Q x_{iS}.
 \]
-
 The matrix $\Q$ is a symmetric positive definite matrix of dimension $s \times{} s$. 
@@
 
-In the \textbf{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$.
+\subsubsection{First simulation}
+In the \textrm{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$.
 We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$ and $512$.
@@
 
-In the \textbf{second simulation} (Figure~\ref{Support}b,c), we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive.
+\subsubsection{Second simulation}
+In the \textrm{second simulation} (Figure~\ref{Support}b,c), we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive.
 We generate four $\Q$ matrices
@@
 
-In the \textbf{third simulation} (Figure~\ref{Support}d,e), we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
+\subsubsection{Third simulation}
+In the \textrm{third simulation} (Figure~\ref{Support}d,e), we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
 We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128, s=5$.
@@
 
-For the \textbf{fourth simulation} (Figure~\ref{Support}f,g), we let $f_0$ be the softmax function and let $X$ be drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$.
+\subsubsection{Fourth simulation}
+For the \textrm{fourth simulation} (Figure~\ref{Support}f,g), we let $f_0$ be the softmax function and let $X$ be drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$.
 We set $s=5$ and vary $p=128,256,512$.
@@
 
-For the \textbf{fifth simulation} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
+\subsubsection{Fifth simulation}
+For the \textrm{fifth simulation} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
 We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.
@@
 
-\begin{figure*}
+\begin{figure*}[t]
 \begin{center}

### 2015-05-18 tex/scam/experiments.tex
a

@@
 \subsubsection{First simulation}
-In the \textrm{first simulation} (Figure~\ref{Support}a), we vary the ambient dimension $p$.
-We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$ and $512$.
-We draw $X \sim N(0, I_p)$.
-For each $(n,p)$ combination, we generate $100$ independent trials. 
-In Figure~\ref{Support}(a), we plot the probability of exact
-support recovery. We observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
-sense of the running speed, for a 
-data set with $n=1000$ and $p=512$, the code runs in roughly two 
-minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.
+In the \textrm{first simulation} (Figure~\ref{Support}a), we vary the
+ambient dimension $p$. We set $Q$ to be one on the diagonal and $1/2$ on
+the off-diagonal with $0.5$ probability, set $s=5$, and $p=64,128,256$
+and $512$. We draw $X \sim N(0, I_p)$.  For each $(n,p)$ combination,
+we generate $100$ independent trials.  In Figure~\ref{Support}(a), we
+plot the probability of exact support recovery. We observe that the
+algorithm performs consistent variable selection even if the
+dimensionality is large. To give the reader a sense of the running
+speed, for a dataset with $n=1,000$ and $p=512$, the code runs in
+roughly two minutes on a machine with a 2.3 GHz Intel Core i5 CPU and 4
+GB memory.
 

### 2015-05-18 tex/scam/experiments.tex
a

@@
 \subsubsection{Second simulation}
-In the \textrm{second simulation} (Figure~\ref{Support}b,c), we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive.
-We generate four $\Q$ matrices
-plotted in Figure \ref{Support}(c), where the diagonal elements are all one and
-the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
-($\alpha=0,0.2,0.5,1$ for the four cases). We show the 4 $\Q$ matrices we used in Figure~\ref{Support}(c).
-We fix $p=128$, $s=5$, and $X \sim N(0,I_p)$.  We again run the AC/DC optimization on $100$
-independent trials and plot the probability of exact recovery
-in Figure \ref{Support}(b). The results demonstrate that AC/DC performs
-consistent variable selection even if the true function is not additive (but
-still convex).
+In the \textrm{second simulation} (Figure~\ref{Support}b,c), we vary
+the sparsity of the $Q$ matrix, thus varying the extent to which
+the true function is non-additive. We generate four $\Q$ matrices
+plotted in Figure \ref{Support}(c), where the diagonal elements are
+all one and the off-diagonal elements are $\frac{1}{2}$ with
+probability $\alpha$ ($\alpha=0,0.2,0.5,1$ for the four cases). We
+show the four $\Q$ matrices we used in Figure~\ref{Support}(c).  We fix
+$p=128$, $s=5$, and $X \sim N(0,I_p)$.  We again run the AC/DC
+optimization on $100$ independent trials and plot the probability of
+exact recovery in Figure \ref{Support}(b). The results demonstrate
+that AC/DC performs consistent variable selection even if the true
+function is not additive (but still convex).
 
@@
 We generate $X$ from a non-Gaussian boundary flat distribution with covariance $\Sigma$.
-The distribution we used is a mixture of a uniform distribution and a Gaussian Copula.
+The distribution we used is a mixture of a uniform distribution and a Gaussian copula,
 \[
-X \sim \gamma U([-2, 2]^p) + (1-\gamma) \trm{Copula}(0, \Sigma, F)
+X \sim \gamma U([-2, 2]^p) + (1-\gamma) \trm{Copula}(0, \Sigma, F).
 \]
-The Gaussian Copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the same covariance.
-Gaussian Copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each of the variables of a Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new marginal distribution.
-In all our experiments, we set $\gamma = 0.05$ and set the marginal CDF $F$ so that marginal density of the Copula is bimodal and supported on $[-1.8, 1.8]$.
+The Gaussian copula is a way to customize the marginal distributions of a Gaussian random variable while maintaining the same covariance.
+Gaussian copula results when one applies a monotone transformation $F^{-1} \Phi$ onto each of the variables of a Gaussian random vector where $\Phi$ is the normal CDF and $F$ is the CDF of the new marginal distribution.
+In all our experiments, we set $\gamma = 0.05$ and set the marginal CDF $F$ so that marginal density of the copula is bimodal and supported on $[-1.8, 1.8]$.
 The resulting marginal density of the mixture is shown in Figure~\ref{fig:copula_marginal}.

### 2015-05-18 tex/scam/experiments.tex
a

@@
 the sixth, we choose the set of relevant variables $S$ uniformly at
-random among all variables $\{1,...,p\}$.
+random among all variables $\{1,\ldots,p\}$.
 
@@
 dimensionality is large. To give the reader a sense of the running
-speed, for a dataset with $n=1,000$ and $p=512$, the code runs in
+speed, for a dataset with $n=1{,}000$ and $p=512$, the code runs in
 roughly two minutes on a machine with a 2.3 GHz Intel Core i5 CPU and 4
@@
 
-In the third, fourth, and fifth simulation, we use a correlated design.
-We generate $X$ from a non-Gaussian boundary flat distribution with covariance $\Sigma$.
-The distribution we used is a mixture of a uniform distribution and a Gaussian copula,
+In the third, fourth, and fifth simulation, we use a correlated
+design. We generate $X$ from a non-Gaussian boundary flat distribution
+with covariance $\Sigma$. The distribution we used is a mixture of a
+uniform distribution and a Gaussian copula,
 \[
@@
 \subsubsection{Third simulation}
-In the \textrm{third simulation} (Figure~\ref{Support}d,e), we use the non-Gaussian distribution described above and set the covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$.
-We use the non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$ and fix $p=128, s=5$.
-We measure success not through exact recovery but through faithful recovery.
-We say that a trial is a successful if (1) all relevant variables were recovered and (2) fewer than $20$ variables were marked as relevant overall (true sparsity $s=5$).
-We use the same $\lambda$ as before.
-The probabilities of success are computed from 40 independent trials and plotted against various values of $\nu$ in Figure~\ref{Support}(d).
-Additionally, for $\nu = 0.5$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(e).
-As seen, for small to moderate correlations, AC/DC can successfully recover the relevant variables with only a small number of false positives.
+In the \textrm{third simulation} (Figure~\ref{Support}d,e), we use the
+non-Gaussian distribution described above and set the covariance
+to be $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0, 0.2, 0.5, 0.9$. We use the
+non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$
+and fix $p=128, s=5$. We measure success not through exact recovery
+but through faithful recovery. We say that a trial is a successful if
+(1) all relevant variables were recovered and (2) fewer than $20$
+variables were marked as relevant overall (true sparsity $s=5$). We
+use the same $\lambda$ as before. The probabilities of success are
+computed from 40 independent trials and plotted against various values
+of $\nu$ in Figure~\ref{Support}(d). Additionally, for $\nu = 0.5$, we
+show the number of selected variables versus the sample size as a
+box plot in Figure~\ref{Support}(e). As seen, for small to
+moderate correlations, AC/DC can successfully recover the relevant
+variables with only a small number of false positives.
 
-In the fourth and fifth simulation, we use a softmax function as the ground truth
+In the fourth and fifth simulation, we use a softmax function as the ground truth,
 \begin{align}
-f_0(x_{iS}) = \log \left( \sum_{k=1}^K \exp( \beta_k^\tran x_{iS} ) \right) - \mu
+f_0(x_{iS}) = \log \left( \sum_{k=1}^K \exp( \beta_k^\tran x_{iS} ) \right) - \mu.
 \end{align}
-We generate random unit vectors as $\{\beta_k \in \R^s\}_{k=1,...,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
+We generate random unit vectors as $\{\beta_k \in \R^s\}_{k=1,\ldots,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
 
 \subsubsection{Fourth simulation}
-For the \textrm{fourth simulation} (Figure~\ref{Support}f,g), we let $f_0$ be the softmax function and let $X$ be drawn from the boundary flat mixture distribution described earlier with the Toeplitz covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$.
-We set $s=5$ and vary $p=128,256,512$.
-We use the same faithful recovery criteria as the third simulation and plot the probability of faithful recovery against the number of samples in Figure~\ref{Support}(f).
-The probabilities are computed over 30 independent trials.
-Also, for $p=256$, we show the number of selected variables versus the sample size as a box-and-whisker plot in Figure~\ref{Support}(g).
-The softmax function is more challenging to estimate than the quadratic function; the softmax function requires about $n > 1500$ to achieve the same success probability as the quadratic function with $n=1000$.
-Regardless, we see that increasing the ambient dimension $p$ does not significantly affect the recovery probability.
+For the \textrm{fourth simulation} (Figure~\ref{Support}f,g), we let
+$f_0$ be the softmax function and let $X$ be drawn from the boundary
+flat mixture distribution described earlier with the Toeplitz
+covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$. We set $s=5$ and
+vary $p=128,256,512$. We use the same faithful recovery criteria as in
+the third simulation and plot the probability of faithful recovery
+against the number of samples in Figure~\ref{Support}(f). The
+probabilities are computed over 30 independent trials. Also, for
+$p=256$, we show the number of selected variables versus the sample
+size as a box plot in Figure~\ref{Support}(g). The softmax function is
+more challenging to estimate than the quadratic function; the softmax
+function requires about $n > 1{,}500$ samples to achieve the same success
+probability as the quadratic function with $n=1{,}000$. Regardless, we
+see that increasing the ambient dimension $p$ does not significantly
+affect the recovery probability.
 
@@
 \subsubsection{Fifth simulation}
-For the \textrm{fifth simulation} (Figure~\ref{fig:ac_v_dc}), we compare the variables selected via the AC stage and the variables selected via the DC stage.
-We use the softmax regression function and $X$ drawn from the boundary flat mixture distribution with a Toeplitz covariance and correlation level $\nu = -0.7$.
-We set $s=5, n=500, p=128$.
-We perform 30 independent trials and plot the frequency of variable selection in Figure~\ref{fig:ac_v_dc}.
-The true variables are $X_j$ for $j=5,6,7,8,9,10$.
-We plot the frequency of selection among only the first 20 variables, that is, $X_j$ for $j=1,...,20$.
-We do not plot selection frequencies for variables 21 to 128 because they are almost never selected by either AC or DC.
-As can be seen, the DC stage is slightly helpful in recovering the true variables but its effect is not significant.
-We thus believe that the DC stage, though important in theory, is not as important in practice; it may be omitted without significant detriment to the overall result.
+For the \textrm{fifth simulation} (Figure~\ref{fig:ac_v_dc}), we
+compare the variables selected via the AC stage and the variables
+selected via the DC stage. We use the softmax regression function and
+$X$ drawn from the boundary flat mixture distribution with a Toeplitz
+covariance and correlation level $\nu = -0.7$. We set $s=5$, $n=500$,
+and $p=128$. We perform 30 independent trials and plot the frequency of
+variable selection in Figure~\ref{fig:ac_v_dc}. The true variables are
+$X_j$ for $j=5,6,7,8,9,10$. We plot the frequency of selection among
+only the first 20 variables, that is, $X_j$ for $j=1,\ldots,20$. We do
+not plot selection frequencies for variables 21 to 128 because they
+are almost never selected by either the AC or DC stage. As can be
+seen, the DC stage is slightly helpful in recovering the true
+variables but its effect is not significant. We thus believe that the
+DC stage, though important in theory, is not as important in practice;
+it may be omitted without significant detriment to the overall result.
 
@@
 \includegraphics[width=0.5\textwidth]{figs/ACvDC}
-\caption{Frequency of variable selection among the first 20 variables ($X_j$ for $j=1,...,20$) in the AC stage vs. in the DC stage. The true variables are [5,6,7,8,9,10].}
+\caption{Frequency of variable selection among the first 20 variables ($X_j$ for $j=1,\ldots,20$) in the AC stage vs. in the DC stage. The true variables are [5,6,7,8,9,10].}
 \label{fig:ac_v_dc}
@@
 
-We next use the Boston housing data rather than simulated data. This data set
-contains 13 covariates, 506 samples and one response variable
-indicating housing values in suburbs of Boston. The data and detailed description
-can be found on the UCI Machine Learning Repository website\footnote{\url{http://archive.ics.uci.edu/ml/datasets/Housing}}.
+We next use the Boston housing data rather than simulated data. This
+data set contains 13 covariates, 506 samples and one response variable
+indicating housing values in suburbs of Boston. The data and a
+detailed description can be found on the UCI Machine Learning
+Repository
+website\footnote{\url{http://archive.ics.uci.edu/ml/datasets/Housing}}.
 
@@
 Next, in order to quantitatively study the predictive performance, we
-run 3 times 5-fold cross validation, following the same procedure
+run 5-fold cross validation three times, following the same procedure
 described above---training, variable selection and refitting.  A plot

### 2015-05-19 tex/scam/supplement.tex
a
minor fixes

@@
 We choose $\epsilon = \left( \frac{(sB)^2 (s
-    K^{**} (sBc_u)^{1/2})}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our results. It is easy to verify that
+    K^{**} (sBc_u)^{1/2})}{n} \right)^{2/5}$. This choice of $\epsilon$ is not optimal but it is convenient and it is sufficient for our results. It is easy to verify that
 if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
-  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n B +
+  c B^2 \sigma \sqrt{ \frac{c_u^{1/2}}{n^{4/5}} \log \frac{Cn}{\delta} }+ \lambda_n B +
   c B^3 \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta} } \\
- &\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n B
+ &\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta}}+ \lambda_n B
 \end{align*}
@@
 \| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
-\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ 
+\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta}}+ 
     c s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
@@
 -4sB\epsilon - 
-(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
- \| h \|_n^2 - \| h \|_P^2 \leq
-4sB\epsilon + 
+(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } &\leq 
+ \| h \|_n^2 - \| h \|_P^2 \\
+& \leq 4sB\epsilon + 
 (2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
@@
 
-We choose $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBc_u)^{1/2}}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our result.
+We choose $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBc_u)^{1/2}}{n} \right)^{2/5}$. This choice of $\epsilon$ is not optimal but it is convenient and it is sufficient for our result.
 
@@
 Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$.
-Let $f(\mathbf{x}) = \sum_{j=1}^p f_j(x_j)$ and $h(\mathbf{x}) = \sum_{j=1}^d h_j(x_j)$ be two additive functions such that $\E( f(X) - h(X) )^2 = 0$.
+Let $f(\mathbf{x}) = \sum_{j=1}^p f_j(x_j)$ and $h(\mathbf{x}) = \sum_{j=1}^p h_j(x_j)$ be two additive functions such that $\E( f(X) - h(X) )^2 = 0$.
 Suppose also that $\E f_j(X_j) = 0, \E h_j(X_j) = 0$ for all $j$.
@@
 Let $P$ be the probability measure induced by the density $p(\mathbf{x})$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure.
-Since $p > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well.
+Since $p(\mathbf{x}) > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well.
 \\

### 2015-05-19 tex/scam/experiments.tex
a

@@
 We study both the independent case where $P = N(0, I_p)$ and the
-correlated case where $P$ is a correlated Gaussian Copula modified
+correlated case where $P$ is a correlated Gaussian copula modified
 slightly to satisfy the boundary flatness condition. We measure the
@@
 \includegraphics[width=.4\textwidth]{figs/copula_marginal}
-\caption{Marginal density of the Gaussian Copula and Uniform Mixture}
+\caption{Marginal density of the Gaussian copula and uniform mixture}
 \label{fig:copula_marginal}

### 2015-11-19 tex/scam/additive_faithful.tex
a
minor revisions

@@
 Therefore $f$ does not depend on $x_k$.
+\end{proof}
 % Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:
-
 % \begin{align*}
@@
 % We thus have that $f(x_k, \mathbf{x}_{-k}) = f(x'_k, \mathbf{x}_{-k})$ for all $\mathbf{x}_{-k}$ and all pairs $x_k, x'_k \in (0,1)$. This proves that $f$ does not depend on $x_k$.
-\end{proof}
 
@@
 \beta$. The optimal linear function in the population setting is
-$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma$ is the
-covariance matrix. Suppose the $X$s are independent, have a
+$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma = X^\tran X$ is the
+covariance matrix. Suppose the $X$'s are independent, centered, and have a
 symmetric distribution with unit variance, and suppose $f(\mathbf{x})
@@
 $p_\epsilon(\mathbf{x})$ be the density formed from truncating
-$p(\mathbf{x})$ in $[\epsilon, 1-\epsilon]^p$. The corresponding
+$p(\mathbf{x})$ in $[\epsilon, 1-\epsilon]^p$ and proper re-normalization. The corresponding
 mixture $p_{\lambda,\epsilon}(\mathbf{x})$ then approximates
@@
 densities supported and positive on the hypercube $[0,1]^p$ to
-minimize extraneous technical details. It may be possible to extend
+minimize extraneous technical details. It may also be possible to extend
 the analysis to densities whose support is a convex and compact set so
@@
 
-\begin{figure*}[htp]
+\begin{figure*}[t]
 \vskip-10pt
@@
 %additional smoothing bandwidth.
-Since the true regression function $f$ is convex, we approximate the additive model with a \emph{convex} additive model.
+Since the true regression function $f$ is convex, we approximate the additive model with a \emph{convex} additive model. Without loss of generality, we assume in this section that $\E f(X) = 0$.
+
 We abuse notation and, for the rest of the paper, use the notation $f^*_k$ to represent convex additive fits:
@@
  \begin{align}
-h^*_k = \arg\min_{f_k} \mathbb{E} \Bigl[\bigl( f(X) 
+h^*_k = \arg\min_{h_k} \mathbb{E} \Bigl[\bigl( f(X) 
            - \phi(X_{-k}) - h_k(X_k) \bigr)^2\Bigr]
@@
 $\E[ X_k^2 - m_k^2] = 0$.
-Since the optimum has a closed form $c^* = \frac{\E\big[(f(X) -\phi(X_{-k}))(X_k^2 - m^2_k)\big]}{\E X_k^2 - m^2_k}$, we deduce that
+Since the optimum has a closed form $c^* = \frac{\E\big[(f(X) -\phi(X_{-k}))(X_k^2 - m^2_k)\big]}{(\E X_k^2 - m^2_k)^2}$, we deduce that
 \begin{align*}
@@
 \argmin_{c \in \R} 
-\E\Big( f(X) - \phi(X_{-k}) - c\big( s_n(X_k) + \alpha(X_k^2 - m_k^2)\big) \Big)^2 = 0
+\E\Big( f(X) - \phi(X_{-k}) - c\big( s_n(X_k) - \E s_n(X_k) + \alpha(X_k^2 - m_k^2)\big) \Big)^2 = 0
 \]
-This is because $c\big( s_n(x_k) + \alpha(x_k^2 - m_k^2) \big)$ is
+This is because $c\big( s_n(x_k) - \E s_n(X_k) + \alpha(x_k^2 - m_k^2) \big)$ is
 convex for $c \geq 0$ and concave for $c \leq 0$ and it is a centered
@@
 Again, $c^* = \frac{\mathbb{E}[(f(X)-\phi(X_{-k}))\big( 
-           s_n(X_k) + \alpha (X_k^2 - m_k^2) \big)]}{\mathbb{E}
-       \big( s_n(X_k) + \alpha (X_k^2 - m_k^2) \big)^2} = 0$, so
+           s_n(X_k) - \E s_n(X_k)  + \alpha (X_k^2 - m_k^2) \big)]}{\mathbb{E}
+       \big( s_n(X_k) - \E s_n(X_k) + \alpha (X_k^2 - m_k^2) \big)^2} = 0$, so
 \begin{align*}
-\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( s_n(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
+\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( s_n(X_k)- \E s_n(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
 \mathbb{E}[ (f(X) - \phi(X_{-k})) s_n(X_k) ] \\
@@
 Lemma~\ref{cor:faithfulness_extension} with $\phi(\mathbf{x}_{-k}) =
-f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that
+\sum_{k' \neq k} f^*_{k'} (x_{k'})$ and conclude that
 $f^*_k = 0$ and $g^*_k = 0$ together imply that $f$ does not depend on $x_k$.\\

### 2015-11-19 tex/scam/experiments.tex
minor revisions

--- 2015-05-18 tex/scam/experiments.tex
@@
 \begin{equation}\nonumber
-         Y_i = f_0(\x_{iS}) + \epsilon_i \quad (i=1,2,\ldots,n).
+         Y_i = f_0(\x_{iS}) + w_i \quad (i=1,2,\ldots,n).
 \end{equation}
@@
 $\x_{iS}$ are a subset of $\x_i$ with dimension $|S|=s$, where $S$
-represents the set of relevant variables, and $\epsilon_i$ is additive
+represents the set of relevant variables, and $w_i$ is additive
 noise drawn from $\mathcal{N}(0,\sigma^2)$. For all simulations, we set
@@
 and fix $p=128, s=5$. We measure success not through exact recovery
-but through faithful recovery. We say that a trial is a successful if
+but through faithful recovery. We say that a trial is successful if
 (1) all relevant variables were recovered and (2) fewer than $20$

### 2015-11-19 tex/scam/sparsistency.tex
minor revisions

@@
 Our goal is to show variable screening consistency. That is, as
-$n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0
+$n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 1
 where $\hat{S}$ is the set of variables output by AC/DC in the
@@
 \item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
-\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
+\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t W} \leq e^{\sigma^2 t^2 / 2}$.
 \item[A5:] The density $p(\mathbf{x})$ satisfies the boundary flatness condition (Definition~\ref{defn:boundary-point}), and $0 < c_l \leq \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) \leq c_u < \infty$ for two constants $c_l, c_u$.
@@
 simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and
-$\alpha_-$ becomes unnecessary.
+$\alpha_-$ becomes unnecessary (see section~\ref{sec:prod_density_simplification} in the supplementary material).
 
@@
 Then with probability at least $ 1 - \frac{24}{n}$, for all $k \in
-S^c$, for all $i=1,\ldots,n$,
+S^c$, for all $i'=1,\ldots,n$,
 \begin{equation}
@@
 \end{theorem}
+Here, we use $\mathbf{1}_{(i':n)}$ to denote a vector that is 1 on the $i'$-th to the $n$-th coordinates and 0 elsewhere.
 

### 2015-11-19 tex/scam/summary.tex
minor revisions

@@
 In Section~\ref{sec:finitesample} 
-we analyze the finite sample variable selection consistency of AC/DC, without assuming that the true
+we analyze the finite sample variable selection consistency of AC/DC under the model
+\[
+y_i = f_0(X_i) + w_i \quad \textrm{for $i=1,...,n$, }
+\]
+without assuming that the true
 regression function $f_0$ is additive. Our analysis first establishes

### 2015-11-19 tex/scam/supplement.tex
minor revisions

@@
 
-Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{\pi_k(i+1)k} - X_{\pi_k(i)k}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
+Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{\pi_k(i+1)k} - X_{\pi_k(i)k}}{\mathsf{range}_k} \leq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.
 
@@
 \end{align}
-where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
+where $c_1$ is an absolute constant and $c, C$ are constants dependent on $b$.
 \end{theorem}
@@
 \begin{align*}
-\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g} \|_\infty &\leq
+\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g}_k \|_\infty &\leq
    \| y - \hat{f} - (g^*_k - \bar{g}^*_k) \|_n^2 + \lambda_n \| (g^*-\bar{g}^*_k) \|_\infty \\
@@
 The second supposition holds by assumption in the theorem.
-Once we calculate the proper values of $\epsilon$, we will verify that these first supposition holds under the assumption of the theorem also.
+Once we calculate the proper values of $\epsilon$, we will verify that the first supposition holds under the assumption of the theorem also.
 Under these two suppositions, we have
@@
 From the fact that $\lambda(A_j) > 0$, and that $A_j = A^1_j \times [0,1]^{p-1}$, $\lambda_1(A^1_j) > 0$.
-Same reasoning show that $\lambda_1(B^1_{j'}) > 0$ where $B^1_{j'}$ is similarly defined.\\
+Same reasoning shows that $\lambda_1(B^1_{j'}) > 0$ where $B^1_{j'}$ is similarly defined.\\
 
@@
 It is then simple to solve the system and verify that $a_1, a_2$ are as specified.
+\end{proof}
+
+\section{Simplifications when $p(\mathbf{x})$ is a product density}
+\label{sec:prod_density_simplification}
+
+If we assume that $p(\mathbf{x})$, the density over the covariates, is a product density, then some of the results can be strengthened and some can be simplified.
+Note that product densities satisfy the boundary flatness condition (definition~\ref{defn:boundary-point}) trivially and thus are settings under which convex functions are additively faithful.
+We suppose without loss of generality that the true function $f_0$ is convex and has mean-zero.
+
+First, we will show that the unconstrained additive projection is convex under a product density and thus, the DC stage of the algorithm is not necessary.
+Let $\{ f^*_k \}$ be the unconstrained additive projection components.
+\begin{align*}
+ f^*_k &= \E[ f_0(X) - \sum_{k' \neq k} f^*_{k'}(X_{k'}) \given x_k ] \quad 
+\textrm{(by Lemma~\ref{lem:general_int_reduction})} \\
+     &= \E[ f_0(X) \given x_k ] \quad \textrm{(by independence of $X_k, X_{k'}$)} \\
+  &= \int f_0(\mathbf{x}) p(\mathbf{x}_{-k} \given x_k ) d \mathbf{x}_{-k} \\
+  &= \int f_0(\mathbf{x}) p(\mathbf{x}_{-k}) d\mathbf{x}_{-k} \quad
+   \textrm{(by independence again)}
+\end{align*}
+
+If we see $f_0(\mathbf{x})$ as a set of functions $f_0(x_k, \mathbf{x}_{-k})$ of just $x_k$ indexed by $\mathbf{x}_{-k}$, we see that $f^*_k(x_k)$ is a weighted average of $f_0(x_k, \mathbf{x}_{-k})$'s and is thus convex.
+
+Therefore, the unconstrained additive projection and the convex additive projection yield the same solution.
+Thus, the convex additive projection is also faithful and no additional concave postprocessing is needed.
+
+Second, we can simplify the definition of the signal strength ($\alpha_+, \alpha_-$ from equation~\ref{eqn:signal_level_defn}) under a product density.
+$\alpha_-$ is no longer needed at all since the DC stage is unnecessary.
+As for $\alpha_+$, we have the following proposition:
+
+\begin{proposition}
+Let $\alpha_+$ be defined as in equation~\ref{eqn:signal_level_defn}. If $p(\mathbf{x})$ is a product density, then $\alpha_+ = \min_{k \,:\, f^*_k \neq 0} \E f^*_k(X_k)^2$. 
+\end{proposition}
+
+\begin{proof}
+
+For any convex additive function $f$, we have that
+\[
+\alpha_+ = \E (f_0(X) - f(X))^2 - \E (f_0(X) - f^*(X))^2 \geq \E (f(X) - f^*(X))^2
+\]
+because $f^*$ is the orthogonal projection of $f_0$ onto the set of convex additive functions, which is itself a convex set.
+
+Next, suppose that $f$ is a convex additive function such that $\supp(f) \subsetneq \supp(f^*)$, i.e., $f_k \neq 0 \Rightarrow f^*_k \neq 0$ but there exists some $k$ such that $f^*_k \neq 0$ and $f_k = 0$.
+\begin{align*}
+\E (f(X) - f^*(X))^2 & = \E \left( \sum_{k=1}^p f_k(X_k) - f^*_k(X_k) \right)^2 \\
+   &= \sum_{k=1}^p \E (f_k(X) - f^*_k(X))^2  \quad \textrm{(since $X_k, \perp X_{k'}$ for $k \neq k'$)} \\
+   &\geq \min_{k \,:\, f^*_k \neq 0} \E f^*_k(X_k)^2 
+\end{align*}
+
+Now, let $k^* = \arg\min_k \E f^*_k(X_k)^2$ and let $f(\mathbf{x}) = \sum_{k\neq k^*} f_k^*(x_k)$. Then,
+
+\begin{align*}
+& \E (f_0(X) - f(X))^2 - \E (f_0(X) - f^*(X))^2 \\
+ &=
+   \E \big(f_0(X) - f^*(X) + f^*_{k^*}(X_{k^*}) \big)^2 - \E( f_0(X) - f^*(X))^2 \\
+ &= \E \big[ 2(f_0(X) - f^*(X)) f^*_{k^*} (X_{k^*}) \big] + \E f^*_{k^*}(X_{k^*})^2 \\
+ &= \E\big[ \E[ 2(f_0(X) - f^*(X)) \given X_{k^*}] f^*_{k^*}(X_{k^*}) \big] + \E f^*_{k^*}(X_{k^*})^2 \\
+ &= \E f^*_{k^*}(X_{k^*})^2 
+\end{align*}
+
+In the second to last equality, we used the fact that $\E[ f_0(X) - f^*(X) \given X_{k^*}] = 0$ since $f^*_{k^*}(X_{k^*}) = \E[ f_0(X) \given X_{k^*} ]$ under a product density.
+
+Thus, we have shown that $\alpha_+ \geq \min_{k \,:\, f^*_k \neq 0} \E f_k^*(X_k)^2$ and that equality is attained with $f(\mathbf{x}) = \sum_{k\neq k^*} f_k^*(x_k)$.
+
 \end{proof}

### 2015-11-19 code/paper_exp/C.m

@@ -7,7 +7,7 @@ function C(version)
 %
 addpath('../simdata');
 
-clc; close all; format long; randn('state',0); rand('state',0); 
+clc; close all; format long; randn('state',1); rand('state',1); 
 switch version
     case 01, n = 200; v = 0.0;
     case 02, n = 400; v = 0.0;
@@ -51,8 +51,8 @@ lambda = 0.5*sqrt(1/n)*log(n*p); % MODIFY
 
 alpha = 0.5;
 
-maxit = 20; tol = 10^-6;
-nrun = 40; % MODIFY
+maxit = 50; tol = 10^-8;
+nrun = 60; % MODIFY
 J = ones(p,nrun)==0; Ln = zeros(p,nrun); 
 
 
@@ -109,7 +109,7 @@ for version = 1:num_versions
     load(['mat/C_' num2str(version) '.mat']);
     nrun = size(Ln,2); suc = 0; 
     for run = 1:nrun
-        cur_supp = sum(Ln(:,run) > 1e-5);
+        cur_supp = sum(Ln(:,run) > 1e-5); %was 1e-5
         if min(Ln(J(:,run),run)) > epsil && ...
             cur_supp < success_supp
             suc = suc + 1;

### 2015-11-19 tex/scam/reviews-v1/response-v1.tex

@@
 We thank the reviewers for their careful reading of our paper and many
-helpful comments. We have carefully addressed all these comments. The
+helpful comments. We have carefully addressed all of these comments. The
 following describes the revisions made to the manuscript, with 
@@
 that convex functions are additively faithful under a product
-density. Next observed that the behavior of a convex function is constrained
+density. Next observe that the behavior of a convex function is constrained
 by its behavior at the boundary; in particular, it is identically zero
@@
 If the true regression function is a convex additive function, then
-additive faithfulness holds----the best additive approximation
+additive faithfulness holds---the best additive approximation
 to an additive function is the function itself. The estimation
@@
 
-We have removed the old equation (2.3), and moved discussion of convex
+We have removed the old equation (2.3), and moved the discussion of convex
 additive models to after AC/DC has been introduced, on page 6.

### 2015-11-30 tex/scam/experiments.tex
new support size plots

@@
 \subsubsection{Third simulation}
-In the \textrm{third simulation} (Figure~\ref{Support}d,e), we use the
+In the \textrm{third simulation} (figure~\ref{Support}d, figure~\ref{fig:support_size}f), we use the
 non-Gaussian distribution described above and set the covariance
@@
 non-additive $\Q$, same as in the first experiment, with $\alpha=0.5$
-and fix $p=128, s=5$. We measure success not through exact recovery
-but through faithful recovery. We say that a trial is successful if
-(1) all relevant variables were recovered and (2) fewer than $20$
-variables were marked as relevant overall (true sparsity $s=5$). We
+and fix $p=128, s=5$. In figure~\ref{Support}d, we say that a trial is successful 
+if all relevant variables were recovered, i.e., there are no false negatives.
+In figure~\ref{fig:support_size}f, we also show the total number of selected variables versus the sample size as boxplots; since the true sparsity level is 5, these plots show the number of false positives.
+We
 use the same $\lambda$ as before. The probabilities of success are
 computed from 40 independent trials and plotted against various values
-of $\nu$ in Figure~\ref{Support}(d). Additionally, for $\nu = 0.5$, we
-show the number of selected variables versus the sample size as a
-box plot in Figure~\ref{Support}(e). As seen, for small to
-moderate correlations, AC/DC can successfully recover the relevant
+of $\nu$ in Figure~\ref{Support}(d). As seen, for all correlation levels, AC/DC can successfully recover the relevant
 variables with only a small number of false positives.
+For $\nu = 0, 0.2, 0.5$, the number of false positives steadily decrease with the sample size, but for $\nu = 0.9$, the number of false positives stays roughly constant.
+The latter phenomenon does not contradict our theory, which assumes $X_S \perp X_{S^c}$ for some set $S \supset S_0$, but it does demonstrate a weakness of our method when the design is highly correlated.
 
@@
 \end{align}
-We generate random unit vectors as $\{\beta_k \in \R^s\}_{k=1,\ldots,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
+We generate $K$ random unit vectors $\{\beta_k \in \R^s\}_{k=1,\ldots,K}$ and choose $\mu$ so that $f_0$ has mean-zero. We set $K = 7$ for all the experiments.
 
 \subsubsection{Fourth simulation}
-For the \textrm{fourth simulation} (Figure~\ref{Support}f,g), we let
+For the \textrm{fourth simulation} (figure~\ref{Support}e, figure~\ref{fig:support_size}g), we let
 $f_0$ be the softmax function and let $X$ be drawn from the boundary
@@
 covariance $\Sigma_{ij}=\nu^{|i-j|}$ for $\nu = 0.5$. We set $s=5$ and
-vary $p=128,256,512$. We use the same faithful recovery criteria as in
+vary $p=128,256,512$. We use the same faithful recovery criterion as in
 the third simulation and plot the probability of faithful recovery
-against the number of samples in Figure~\ref{Support}(f). The
-probabilities are computed over 30 independent trials. Also, for
-$p=256$, we show the number of selected variables versus the sample
-size as a box plot in Figure~\ref{Support}(g). The softmax function is
-more challenging to estimate than the quadratic function; the softmax
-function requires about $n > 1{,}500$ samples to achieve the same success
-probability as the quadratic function with $n=1{,}000$. Regardless, we
+against the number of samples in Figure~\ref{Support}(e). The
+probabilities are computed over 30 independent trials. Also, we show the number of selected variables versus the sample
+size as boxplots in Figure~\ref{fig:support_size}(g). The softmax function is
+more challenging to estimate than the quadratic function, regardless, we
 see that increasing the ambient dimension $p$ does not significantly
-affect the recovery probability.
+affect the recovery probability. We also see from figure~\ref{fig:support_size}(g) that larger $p$ does not lead to more number of false positives.
 
@@
 (c) four $\Q$ matrices used in (b) & (d) quadratic $f_0$, correlated $X$, varying correlation $\nu$ \\
-\includegraphics[width=.42\textwidth]{figs/C_support_box} & 
-\includegraphics[width=.42\textwidth]{figs/CurveS}\\
-(e) recovered support size for $\nu=0.5$ in (d) & (f) softmax $f_0$, correlated $X$, varying $p$ \\
+%\multicolumn{2}{c}{\includegraphics[width=.8\textwidth]{figs/C_support_box}}\\
+%\multicolumn{2}{c}{(e) recovered support size in (d)} \\
+\multicolumn{2}{c}{\includegraphics[width=.42\textwidth]{figs/CurveS}} \\
+\multicolumn{2}{c}{(e) softmax $f_0$, correlated $X$, varying $p$} \\
 %\includegraphics[width=0.42\textwidth]{figs/S_support_box} & \\
@@
 \vskip10pt
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\begin{tabular}{c}
+\includegraphics[width=.84\textwidth]{figs/C_support_box}\\
+(f) recovered support sizes for figure~\ref{Support}(d) \\
+\includegraphics[width=0.84\textwidth]{figs/S_support_box}\\
+(g) recovered support sizes for figure~\ref{Support}(e)
+\end{tabular}
+\end{center}
+\caption{Recovered support size in correlated design cases}
+\label{fig:support_size}
 \end{figure*}

### 2015-11-30 code/paper_exp/C.m

@@ -98,18 +98,20 @@ return
 %% Reading the result:
 %clc; clear all; close all; 
 num_versions = 28;
+nrun = 40;
 prob = zeros(1,num_versions); 
 supp = zeros(nrun, num_versions);
 
-success_supp = 20;
+success_supp = 128;
 
 epsil = 1e-6;
 
 for version = 1:num_versions
     load(['mat/C_' num2str(version) '.mat']);
+    
     nrun = size(Ln,2); suc = 0; 
     for run = 1:nrun
-        cur_supp = sum(Ln(:,run) > 1e-5); %was 1e-5
+        cur_supp = sum(Ln(:,run) > 1e-4); %was 1e-5
         if min(Ln(J(:,run),run)) > epsil && ...
             cur_supp < success_supp
             suc = suc + 1;
@@ -119,8 +121,12 @@ for version = 1:num_versions
     prob(version) = suc/nrun;
 end
 
+nrun_cut = 40
+supp = supp(1:nrun_cut, :)
 
 samples = 200:200:1400;
+
+%% begin plots
 
 % much of the figures still need to be edited
 figure(2); set(gca,'FontSize',14); 
@@ -153,36 +159,46 @@ set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
 h = gcf;
 saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/CurveC.pdf');
 
+
 %% box plots
 figure;
-set(gca,'FontSize',14);
+set(gca,'FontSize',16); 
 
-boxplot(supp(:,15:21));
-set(gca, 'XTick', 1:7);
-set(gca, 'XTickLabel', {'200','400','600','800','1000','1200','1400'});
+G = []
+v1 = []
+v2 = []
+
+for ii = 1:4
+    
+    for jj = 1:7
+        G = [G, supp(:, jj + (7*(ii-1)))']
+        v1 = [v1, repmat(samples(jj), 1, 40)]
+    end
+end
+
+v2 = [repmat({'v=0'}, 1, 280), repmat({'v=0.2'}, 1, 280), ...
+      repmat({'v=0.5'}, 1, 280), repmat({'v=0.9'}, 1, 280)]  
+  
+boxplot(G', {v2'; v1'}, 'factorseparator',1, 'factorgap',5,...
[…]

### 2015-11-30 code/paper_exp/S.m

@@ -44,7 +44,7 @@ SNR = 5;
 
 maxit = 20; tol = 10^-6;
 
-nrun = 15; % MODIFY
+nrun = 30; % MODIFY
 
 J = ones(p,nrun)==0; Ln = zeros(p,nrun); 
 
@@ -96,7 +96,7 @@ prob = zeros(1,num_versions);
 supp = zeros(nrun, num_versions);
 epsil = 1e-6;
 
-success_supp = 20;
+success_supp = 1e5;
 
 for version = 1:num_versions
     load(['mat/S_' num2str(version) '.mat']);
@@ -112,11 +112,8 @@ for version = 1:num_versions
     prob(version) = suc/nrun;
 end
 
-% correction
-prob(5) = 0.9;
 
 % figures need to be edited
-
 samples = [200,500,800,1100,1500,2000];
 
 figure(2); set(gca,'FontSize',14); 
@@ -181,6 +178,55 @@ set(gcf, 'PaperUnits','centimeters');
 set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
 set(gcf, 'PaperPositionMode', 'manual');
 set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+
+h = gcf;
+saveas(h, '/Users/minxu/dropbox/minx/research/convex_regr/tex/scam/figs/S_support_box.pdf');
+
+%% better box plot
+
+samples = [200, 500, 800, 1100, 1500, 2000];
+%% box plots
+figure;
+set(gca,'FontSize',16); 
+
+G = []
+v1 = []
+v2 = []
+
+% 3 lines
+for ii = 1:3
+    
+    % 6 different sample sizes to try
+    for jj = 1:6
+        G = [G, supp(:, jj + (6*(ii-1)))']
+        % 15 nruns
+        v1 = [v1, repmat(samples(jj), 1, 30)]
+    end
+end
+
+v2 = [repmat({'p=128'}, 1, 180), repmat({'p=256'}, 1, 180), ...
+      repmat({'p=512'}, 1, 180)]
+  
+boxplot(G', {v2'; v1'}, 'factorseparator',1, 'factorgap',5,...
+    'colorgroup',v2', 'labelverbosity','majorminor')
+
+title('Number of selected variables')
+
+
+
+
[…]

### 2015-12-01 tex/scam/reviews-v2/response_v2.tex
response v2

\documentclass[pdftex,12pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{graphicx,subfigure}
\usepackage[pdftex]{color}
\usepackage{epic,eepic,eepicemu}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{graphics}
\usepackage{psfrag,latexsym}
\usepackage{times}
\newcommand{\thetamin}{\ensuremath{\theta^*_{min}}}
\newcommand{\mutinc}{\ensuremath{\alpha}}
\bibliographystyle{abbrv}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\degmax{d}
\def\pdim{p}
\def\numobs{n}
\let\hat\widehat
\definecolor{blue}{rgb}{0.01,0.01,0.75}
\def\rc#1{{\it\textcolor{blue}{#1}}\smallskip}
\parindent0pt
\parskip12pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.02}

\begin{document}

\vspace*{5pt}

As with before, we are grateful to the reviewers for the careful reading and very helpful editing and suggestions. We have fixed all the typos found by the reviewers. We also have improved the paper in other minor aspects in response to the review -- these changes are described below.

\subsection*{Review 4}

\begin{enumerate}
\item \rc{On page 30, I did not understand : ”we set $K = 7$ for all the experiments”, and then ”We set $s = 5$” and ”the true variables are $X_j$ for $j = 5,6,7,8,9,10$”.}

Here, the true function is a soft-max of linear forms $\beta_k^T x$, i.e., 
$f_0(x) = \log \left( \sum_{k=1}^K \exp( \beta_k^T x) \right) - \mu$ where the $\beta_k$'s are randomly generated unit vectors. $K$ is the number of linear pieces $\beta_k$'s and $s$ is the number of relevant variables. We have clarified this a bit more in section 6 of the paper.  
\end{enumerate}

\subsection*{Reviewer 5}

\begin{enumerate}
\item \rc{In Section 2.3, the authors preview their main results concerning variable selection consistency in a finite-sample setting. However, at this point, the “true regression function” $f_0$ has not yet been defined (it is defined later in Section 5.2). It would be helpful if the authors were to state the model generating the data in this section.}

We have stated the model in the beginning of Section 2.3.

\item \rc{In Example 3.3, the authors describe a method for approximating any bounded density over a hypercube arbitrarily well using boundary flat densities. The second paragraph mentions truncating the density to the hypercube $[\epsilon, 1−\epsilon]^p$—since the truncated function isn’t a density, it should technically also be rescaled.}

This has been fixed.

\item \rc{In Assumption A4 at the bottom of page 25, the moment generating function should read $\E e^{tW}$ rather than $\E e^{t \epsilon}$. There is some change in notation in Section 6.1, where $W$ is replaced by $\epsilon$; perhaps it would be better to keep the notation consistent.}

We have changed $\epsilon$ to $W$ across the paper to keep the notations consistent.

\item \rc{The last sentence of the first paragraph on page 26 is a bit hard to follow. What does “if $X$ is independent” mean (does this mean $p(x)$ is a product distribution)? I did not understand where the simplification came from.}

``$X$ is independent'' does mean that $p(x)$ is a product distribution; we have clarified this in the paper. We have also added a new section to the supplement (Section 11, Proposition 11.1) that explains and derives the simplification.

\item \rc{The $\nu = 0.9$ curve in Figure 5(d) is rather ill-behaved compared to the other curves. However, if my understanding is correct, the probability of successful screening should still tend to 1 in this case. Perhaps the authors could consider plotting more samples to show eventual consistency for this curve, as well (and also take an average over more trials, since the behavior of the curve is somewhat noisy).}

The probability of successful screening does tend to 1. That was not reflected in the old plot because the old plot describes the probability both that the number of false positives is 0 (successful screening) and that the number of false positives is less than 20. It was because of this latter criterion that the $\nu =0.9$ curve did not tend to 1 in the old plot. The threshold of 20 was arbitrarily chosen and we have revised the plots to remove it. The updated figures 5(d) and 5(e) show only the probability that the number of false negatives is 0; the number of false positives is reflected in the newly added figures 6(f) and 6(g), which show that total number of variables selected in the experiments that correspond to figures 5(d) and 5(e). We have also updated the discussion in section 6.1.3 and 6.1.4.

\end{enumerate}

\vspace*{10pt}

Sincerely,

Min Xu, Minhua Chen, and John Lafferty\\[1pt]
\today{}

\bibliography{local}
\end{document}

### 2015-12-01 tex/scam/sparsistency.tex
response v2

@@
 then it is easier to make a false omission in the decoupled concave
-stage of the procedure. If $X$ is independent, then $\alpha_+$ can be
+stage of the procedure. If $p(\mathbf{x})$ is a product density, then $\alpha_+$ can be
 simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and

### 2015-12-01 tex/scam/supplement.tex
response v2

@@
 \begin{align*}
-\Delta_k^\tran \mathbf{u}]_j &= \sum_{i > j} (X_{ik} - X_{jk}) \mathbf{u}_i \\
+[\Delta_k^\tran \mathbf{u}]_j &= \sum_{i > j} (X_{ik} - X_{jk}) \mathbf{u}_i \\
   &= \mathbf{u}_{i^*} (X_{i^*k} - X_{jk}) \delta_{i^* \geq j} + \mathbf{u}_n (X_{nk} - X_{jk})\\ 
@@
 In the second to last equality, we used the fact that $\E[ f_0(X) - f^*(X) \given X_{k^*}] = 0$ since $f^*_{k^*}(X_{k^*}) = \E[ f_0(X) \given X_{k^*} ]$ under a product density.
+(See the discussion right before the statement of the proposition)
 

### 2015-12-01 code/paper_exp/C.m

@@ -121,8 +121,8 @@ for version = 1:num_versions
     prob(version) = suc/nrun;
 end
 
-nrun_cut = 40
-supp = supp(1:nrun_cut, :)
+nrun_cut = 40;
+supp = supp(1:nrun_cut, :);
 
 samples = 200:200:1400;
 

### 2015-12-07 tex/scam/reviews-v2/response_v2.tex
minor edits

@@
 
-As with before, we are grateful to the reviewers for the careful reading and very helpful editing and suggestions.
-We have fixed all the typos found by the reviewers.
-We also have improved the paper in other minor aspects in response to the review -- these changes are described below.
+As before, we are grateful to the reviewers for their careful reading
+and very helpful editing and suggestions. We have fixed all of the typos
+found by the reviewers. We also have improved the paper in other minor
+aspects in response to the reviews---these changes are described
+below.
 
@@
 Here, the true function is a soft-max of linear forms $\beta_k^T x$, i.e., 
-$f_0(x) = \log \left( \sum_{k=1}^K \exp( \beta_k^T x) \right) - \mu$ where the $\beta_k$'s are randomly generated unit vectors.
-$K$ is the number of linear pieces $\beta_k$'s and $s$ is the number of relevant variables.
-We have clarified this a bit more in section 6 of the paper.
+$$f_0(x) = \log \left( \sum_{k=1}^K \exp( \beta_k^T x) \right) - \mu$$
+where the $\beta_k$s are randomly generated unit vectors. $K$ is the
+number of linear pieces and $s$ is the number of relevant
+variables. We have clarified this a bit more in Section 6 of the
+paper.
 \end{enumerate}
@@
 
-We have changed $\epsilon$ to $W$ across the paper to keep the notations consistent.
+We have changed $\epsilon$ to $W$ across the paper to keep the notation consistent.
 
@@
 
-The probability of successful screening does tend to 1.
-That was not reflected in the old plot because the old plot describes the probability both that the number of false positives is 0 (successful screening) and that the number of false positives is less than 20.
-It was because of this latter criterion that the $\nu =0.9$ curve did not tend to 1 in the old plot.
-The threshold of 20 was arbitrarily chosen and we have revised the plots to remove it.
-The updated figures 5(d) and 5(e) show only the probability that the number of false negatives is 0; the number of false positives is reflected in the newly added figures 6(f) and 6(g), which show that total number of variables selected in the experiments that correspond to figures 5(d) and 5(e).
-We have also updated the discussion in section 6.1.3 and 6.1.4.
+The probability of successful screening does tend to one. That was not
+reflected in the old plot because the old plot describes the
+probability both that the number of false positives is zero (successful
+screening) and that the number of false positives is less than 20. It
+was because of this latter criterion that the $\nu =0.9$ curve did not
+tend to one in the old plot. The threshold of 20 was arbitrarily
+chosen; we have removed this restriction and revised the plots. The updated figures
+5(d) and 5(e) show only the probability that the number of false
+negatives is zero; the number of false positives is reflected in the
+newly added figures 6(f) and 6(g), which show that total number of
+variables selected in the experiments that correspond to figures 5(d)
+and 5(e). We have also updated the discussion in Sections 6.1.3 and
+6.1.4.
 

### 2015-12-07 tex/scam/paper-submit.tex
minor
a
new support size plots
response v2
acknowledge
minor edits

@@
 \usepackage{graphicx}
-\usepackage[hscale=0.7,vscale=0.8]{geometry}
+%\usepackage[hscale=0.7,vscale=0.8]{geometry}
+\usepackage[text={6.0in,8.6in},centering]{geometry}
 \usepackage{subfigure}
@@
 \usepackage{yhmath}
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{shadecolor}{gray}{0.9}
+\definecolor{shadecolor}{gray}{0.9}
+\hypersetup{citecolor=MidnightBlue}
+\hypersetup{linkcolor=MidnightBlue}
+\hypersetup{urlcolor=MidnightBlue}
+\usepackage{enumerate}
+\usepackage{multirow}
 
-\renewcommand{\baselinestretch}{1.05}
+\renewcommand{\baselinestretch}{1.045}
 %\parskip12pt
@@
 \section*{Acknowledgements}
-Research supported in part by NSF grants IIS-1116730, 
-AFOSR grant FA9550-09-1-0373, ONR grant
-N000141210762, and an Amazon AWS in Education Machine Learning
-Research grant.
+Research supported in part by NSF grants IIS-1116730 and DMS-1513594,
+AFOSR grant FA9550-09-1-0373, ONR grant N000141210762, and an Amazon
+AWS in Education Machine Learning Research grant. The authors 
+thank  Ming Yuan for valuable discussions and suggestions
+on this research. The authors are also grateful to the anonymous
+reviewers whose careful proofreading and helpful comments significantly
+improved the quality of the paper.
 
-\clearpage
+%\clearpage
 \bibliographystyle{imsart-nameyear}
@@
 
-\clearpage
+%\clearpage
 \input{supplement}

### 2015-12-07 tex/scam/sparsistency.tex
minor edits

--- 2015-11-19 tex/scam/sparsistency.tex
@@
 then it is easier to make a false omission in the decoupled concave
-stage of the procedure. If $X$ is independent, then $\alpha_+$ can be
+stage of the procedure. If $p(\mathbf{x})$ is a product density, then $\alpha_+$ can be
 simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and
-$\alpha_-$ becomes unnecessary (see section~\ref{sec:prod_density_simplification} in the supplementary material).
+$\alpha_-$ becomes unnecessary (see Section~\ref{sec:prod_density_simplification} in the supplementary material).
 

### 2015-12-07 tex/scam/sparsistency.tex
mods for supplement

@@
 Theorem~\ref{thm:deterministic} is in
-Section~\ref{sec:deterministic_proof} of the Appendix. We allow $S$ in
+Section~\ref{sec:deterministic_proof} of the supplementary material \citep{supplement}. We allow $S$ in
 Theorem~\ref{thm:deterministic} to be any set containing the relevant
@@
 The details of the proof are given in
-Section~\ref{sec:deterministic_proof} of the Appendix.
+Section~\ref{sec:deterministic_proof} of the supplementary material \citep{supplement}.
 
@@
 used. The full proof of Theorem~\ref{thm:false_positive} is in
-Section~\ref{sec:false_positive_proof} of the Appendix.
+Section~\ref{sec:false_positive_proof} of the supplementary material \citep{supplement}.
 
@@
 Theorem~\ref{thm:false_negative} to use our additive faithfulness
-result, Theorem~\ref{thm:convex_faithful}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.
+result, Theorem~\ref{thm:convex_faithful}. The full proof of
+Theorem~\ref{thm:false_negative} is in
+Section~\ref{sec:false_negative_proof} of the supplement \citep{supplement}.
 

### 2015-12-07 tex/scam/supplement.tex
mods for supplement

@@
-\section{Supplement:  Proofs of Technical Results}
+\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
+%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
+
+\RequirePackage[OT1]{fontenc}
+\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
+\RequirePackage{hypernat}
+\usepackage[ruled,section]{algorithm}
+\usepackage[noend]{algorithmic}
+\usepackage{graphicx}
+%\usepackage[hscale=0.7,vscale=0.8]{geometry}
+\usepackage[text={6.0in,8.6in},centering]{geometry}
+\usepackage{subfigure}
+\usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{yhmath}
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{shadecolor}{gray}{0.9}
+\definecolor{shadecolor}{gray}{0.9}
+\hypersetup{citecolor=MidnightBlue}
+\hypersetup{linkcolor=MidnightBlue}
+\hypersetup{urlcolor=MidnightBlue}
+\usepackage{enumerate}
+\usepackage{multirow}
+\usepackage{xr}
+\externaldocument{main}
+
+\renewcommand{\baselinestretch}{1.00}
+%\parskip12pt
+%\parindent0pt
+\setcounter{tocdepth}{2}
+
+\input{macros}
+\begin{document}
+
+\begin{supplement}
+%\sname{Supplement A}
+\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
+\slink[doi]{doi}
+\sdatatype{.pdf}
+\sdescription{We provide detailed proofs of certain technical results,
+together with further explanation of the Gaussian example
+and simplifications when the density is a product.}
+\end{supplement}
+
+\section{Proofs of Technical Results}
 
@@
 We restate Theorem~\ref{thm:deterministic} first for convenience. 
-The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at the beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).
+The following holds regardless of whether we impose the
+$B$-boundedness condition  $\|f_k^*\|_\infty \leq B$
+used in the consistency analysis.
 
@@
 %%% End: ***
+
+\bibliographystyle{imsart-nameyear}
+\bibliography{local}
+
+\end{document}

### 2015-12-07 tex/scam/main.tex
initial commit

--- 2015-12-07 tex/scam/paper-submit.tex
@@
-\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
+\documentclass[12pt,pdftex,aos,addressasfootnote,noinfoline]{imsart}
+%\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
 %\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
@@
 \usepackage{multirow}
+\usepackage{xr}
+\externaldocument{supplement}
 
-\renewcommand{\baselinestretch}{1.045}
+\renewcommand{\baselinestretch}{1.00}
 %\parskip12pt
@@
 \input{macros}
-\arxiv{1411.1805}
 
@@
 \author{\fnms{John}
-  \snm{Lafferty${}^\dag$}\ead[label=e3]{lafferty@galton.uchicago.edu}}
-\address{${}^*$Machine Learning Department, Carnegie Mellon University,
-  Pittsburgh PA 15213}
-\address{${}^\dag$Department of Statistics, University of Chicago, Chicago IL 60637}
+  \snm{Lafferty${}^\ddag$}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+\address{${}^*$Statistics Department,
+The Wharton School,
+University of Pennsylvania,
+Philadelphia, PA 19104}
+\address{${}^\dag$Amazon, Seattle, WA 98109}
+\address{${}^\ddag$Department of Statistics, University of Chicago, Chicago IL 60637}
 \end{aug}
@@
 %\clearpage
-\input{supplement}
+%\input{supplement}
 

### 2015-12-07 tex/scam/supplement.tex
minor

@@
 \setcounter{tocdepth}{2}
+\setattribute{journal}{name}{}
 
@@
 
-\begin{supplement}
-%\sname{Supplement A}
-\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
-\slink[doi]{doi}
-\sdatatype{.pdf}
-\sdescription{We provide detailed proofs of certain technical results,
+\begin{frontmatter}
+\title{Supplement to Faithful Variable Screening for\\ High-Dimensional Convex Regression}
+\runtitle{Supplement to Faithful Variable Screening for Convex Regression}
+\end{frontmatter}
+
+In this supplement we provide detailed proofs of certain technical results,
 together with further explanation of the Gaussian example
-and simplifications when the density is a product.}
-\end{supplement}
+and simplifications when the density is a product.
 

### 2016-03-08 tex/scam/faithful.tex
edits for final version

@@
-\documentclass[12pt,pdftex,aos]{imsart}
-%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
+\documentclass[pdftex,aos]{imsart}
 
 \RequirePackage[OT1]{fontenc}
-\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math}
-\RequirePackage{hypernat}
-\usepackage[ruled,section]{algorithm}
-\usepackage[noend]{algorithmic}
-\usepackage{graphicx}
-\usepackage[hscale=0.7,vscale=0.8]{geometry}
+\RequirePackage{amsthm,amsmath}
+\usepackage{amsfonts,mathtools,custom_math,amssymb}
+\RequirePackage[numbers]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
 \usepackage{subfigure}
 \usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{yhmath}
+\usepackage{enumerate}
+\usepackage{multirow}
+\usepackage{xr}
+\externaldocument{supplement}
 
-\renewcommand{\baselinestretch}{1.1}
-%\parskip12pt
-%\parindent0pt
-\setcounter{tocdepth}{2}
+% settings
+%\pubyear{2005}
+%\volume{0}
+%\issue{0}
+%\firstpage{1}
+%\lastpage{8}
+\arxiv{arXiv:0000.0000}
+
+\startlocaldefs
+\numberwithin{equation}{section}
+\theoremstyle{plain}
+\newtheorem{thm}{Theorem}[section]
+\endlocaldefs
 
@@
 \begin{aug}
-\vskip10pt
-\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
-\comma 
-\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
+\author{\fnms{Min} \snm{Xu}\thanksref{t1,m1}\ead[label=e1]{min.cut@gmail.com}},
+\author{\fnms{Minhua} \snm{Chen}\thanksref{m2}\ead[label=e2]{minhua@somewhere.com}}
 \and
-\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
-\address{
-\begin{tabular}{ccc}
-\\[10pt]
-Machine Learning Department & Department of Statistics & Department of Statistics\\
-Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
-& & University of Chicago
-\end{tabular}
-%\\[20pt]
-%\printead{e1,e2,e3}
+\author{\fnms{John} \snm{Lafferty}\thanksref{t1,m3}\ead[label=e3]{lafferty@galton.uchicago.edu}}
+
+\thankstext{t1}{Research supported in part by NSF grants IIS-1116730 and DMS-1513594,
+AFOSR grant FA9550-09-1-0373, ONR grant N00014-12-10762, and an Amazon
+AWS in Education Machine Learning Research grant.}
+\runauthor{M.~Xu, M.~Chen and J.~Lafferty}
+
+\affiliation{University of Pennsylvania\thanksmark{m1}, Amazon.com\thanksmark{m2}, and University of Chicago\thanksmark{m3}}
+
+\address{Address of M.~Xu\\
+Department of Statistics\\
+The Wharton School\\
+University of Pennsylvania\\
+Philadelphia, Pennsylvania 19104\\
+USA\\
+\printead{e1}\\
 }
+
+\address{Address of M.~Chen\\
+Amazon.com\\
+410 Terry Avenue North\\
+Seattle, Washington 98109\\
+USA\\
+\printead{e2}\\}
+
+\address{Address of J.~Lafferty\\
+Department of Statistics\\
+University of Chicago\\
+5734 South University Avenue\\
+Chicago, Illinois 60637\\
+USA\\
+\printead{e3}\\}
+
 \end{aug}
 
-\input{abstract}
-%\tableofcontents
-\vskip20pt
+\begin{abstract}
+  We study the problem of variable selection in convex nonparametric
+  regression.  Under the assumption that the true regression function
+  is convex and sparse, we develop a screening procedure to select a
+  subset of variables that contains the relevant variables. Our
+  approach is a two-stage quadratic programming method that estimates
+  a sum of one-dimensional convex functions, followed by
+  one-dimensional concave regression fits on the residuals.  In
+  contrast to previous methods for sparse additive models, the
+  optimization is finite dimensional and requires no tuning parameters
+  for smoothness. Under appropriate assumptions, we prove that the
+  procedure is faithful in the population setting, yielding no false
+  negatives.  We give a finite sample statistical analysis, and
+  introduce algorithms for efficiently carrying out the required
+  quadratic programs. The approach leads to computational and
+  statistical advantages over fitting a full model, and provides an
+  effective, practical approach to variable screening in convex
+  regression.
+\end{abstract}
+
+\begin{keyword}[class=MSC]
+\kwd[Primary ]{62G08}
+\kwd[; secondary ]{52A41}
+\end{keyword}
+
+\begin{keyword}
+\kwd{nonparametric regression}
+\kwd{convex regression}
+\kwd{variable selection}
+\kwd{quadratic programming}
+\kwd{additive model}
+\end{keyword}
+
 \end{frontmatter}
-
-\maketitle
-\vskip10pt
-
-%\tableofcontents
 
@@
 
-\clearpage
+\section*{Acknowledgements}
+The authors thank  Ming Yuan for valuable discussions and suggestions
+on this research. The authors are also grateful to the anonymous
+reviewers whose careful proofreading and helpful comments significantly
+improved the quality of the paper.
 
-\newpage
-\input{appendix}
-%\newpage
-%\input{notes}
+\begin{supplement}[id=suppA]
+%\sname{Supplement A}
+\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
+\slink[doi]{doi}
+\sdatatype{.pdf}
+\sdescription{The supplement provides detailed proofs of certain technical results,
+together with further explanation of the Gaussian example
+and simplifications when the density is a product.}
+\end{supplement}
 
-\section*{Acknowledgements}
-Research supported in part by NSF grants IIS-1116730, 
-AFOSR grant FA9550-09-1-0373, ONR grant
-N000141210762, and an Amazon AWS in Education Machine Learning
-Research grant.
-
+%\clearpage
 \bibliographystyle{imsart-nameyear}

### 2016-03-08 tex/scam/introduction.tex
mods for supplement
edits for final version

@@
 
-Recently, there has been increased research activity on shape-constrained estimation.
-\cite{guntusen:13} analyze univariate convex regression and show surprisingly that the risk of the MLE is adaptive to the complexity of the true function.
-\cite{seijo2011nonparametric} and \cite{Lim:12} study maximum likelihood estimation of multivariate convex regression and independently establish its consistency.
-\cite{Cule:10} and \cite{kim2014global} analyze log-concave density estimation and prove consistency of the MLE; the latter further show that log-concave density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$ for $d \geq 2$, refuting a common notion that the condition of convexity is equivalent, in estimation difficulty, to the condition of having two bounded derivatives.
-Additive shape-constrained estimation has also been studied; \cite{pya2014shape} propose a penalized B-spline estimator while \cite{chen2014generalised} show the consistency of the MLE.
-To the best of our knowledge however, there has been no work on variable selection and estimation of high-dimensional convex functions.
+Recently, there has been increased research activity on
+shape-constrained estimation. \citet{guntusen:13} analyze univariate
+convex regression and show surprisingly that the risk of the MLE is
+adaptive to the complexity of the true
+function. \citet{seijo2011nonparametric} and \citet{Lim:12} study
+maximum likelihood estimation of multivariate convex regression and
+independently establish its consistency. \citet{Cule:10} and
+\citet{kim2014global} analyze log-concave density estimation and prove
+consistency of the MLE; the latter further show that log-concave
+density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$
+for $d \geq 2$, refuting a common notion that the condition of
+convexity is equivalent, in estimation difficulty, to the condition of
+having two bounded derivatives. Additive shape-constrained estimation
+has also been studied; \citet{pya2014shape} propose a penalized
+B-spline estimator while \citet{chen2014generalised} show the
+consistency of the MLE. To the best of our knowledge however, there
+has been no work on variable selection and estimation of
+high-dimensional convex functions.
 
@@
 Perhaps more closely related to the present work is the framework
-studied by \cite{Raskutti:12} for sparse additive models, where sparse
+studied by \citet{Raskutti:12} for sparse additive models, where sparse
 regression is considered under an additive assumption, with each
@@
 and theory.  The full proofs are
-given in a technical appendix.
+given in the supplementary material \citep{supplement}.
 

### 2016-03-08 tex/scam/additive_faithful.tex
mods for supplement
fixed some long equation breaks

@@
 &\arg\min \left\{ \E \Bigl( f(X) - \mu - \sum_{k=1}^p f_k(X_k)\Bigr)^2 \,:\,
-f_k \in L^2(P),\, \E f_k(X_k) = 0,\; k=1,\ldots, p \right\}.
+f_k \in L^2(P),\, \E f_k(X_k) = 0,\; \forall k\right\}.
 \end{align*}
@@
 
-To prove uniqueness, suppose $\tilde{f} = \sum_{j=1}^p \tilde{f}_j$ is another additive function that achieves the same square error.
-Let $\nu \in [0,1]$, consider $\E\left( f(X) - \mu^* - (f^* + \nu (\tilde{f} - f^*)) \right)^2$ as a function of $\nu$.
-The objective is strongly convex if $\E (\tilde{f} - f^*)^2$, and so $\E( \tilde{f} - f^*)^2 = 0$ by the assumption that $f^*$ and $\tilde{f}$ are both optimal solutions.
-By Lemma~\ref{lem:additive_uniqueness}, we conclude that $\E( f^*_j - \tilde{f}_j )^2 = 0$ as well and thus, $f^*_j = \tilde{f}_j$ almost everywhere.
+To prove uniqueness, suppose $\tilde{f} = \sum_{j=1}^p \tilde{f}_j$ is
+another additive function that achieves the same square error. Let
+$\nu \in [0,1]$, and consider the expectation $\E\left( f(X) - \mu^* - (f^* + \nu
+(\tilde{f} - f^*)) \right)^2$ as a function of $\nu$. The objective is
+strongly convex if $\E (\tilde{f} - f^*)^2$, and so $\E( \tilde{f} -
+f^*)^2 = 0$ by the assumption that $f^*$ and $\tilde{f}$ are both
+optimal solutions. By Lemma~\ref{lem:additive_uniqueness}, we conclude
+that $\E( f^*_j - \tilde{f}_j )^2 = 0$ as well and thus, $f^*_j =
+\tilde{f}_j$ almost everywhere.
 
@@
 \big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) 
-    + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
+   + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) \\
+\nonumber \mbox{\ } +
 p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 .
@@
 Consider a two dimensional quadratic function $f( \mathbf{x}) = \mathbf{x}^\tran H \mathbf{x} + c$ with zero mean where $H = \begin{pmatrix} H_{11} & H_{12} \\ H_{12} & H_{22}\end{pmatrix}$ is positive definite and a Gaussian distribution $X \sim N(0, \Sigma)$ where $\Sigma = \begin{pmatrix}1 & \alpha \\ \alpha & 1 \end{pmatrix}$.
-As we show in Section~\ref{sec:gaussian_example} of the Appendix, the additive approximation has the
+As we show in Section~\ref{sec:gaussian_example} of the supplementary
+material \citep{supplement}, the additive approximation has the
 following closed form.
@@
 \begin{align*}
-\E \big[ (f(X) - \phi(X_{-k})) &(X_k^2 - m_k^2) \big] \\
-   &= \E[ (f(X) - \phi(X_{-k})) X^2_k] = 
- \E[ \E[ f(X) - \phi(X_{-k}) \given X_k] X^2_k] = 0
+\E \big[ (f(X) - \phi(X_{-k})) (X_k^2 - m_k^2) \big] 
+   &= \E[ (f(X) - \phi(X_{-k})) X^2_k] \\
+&= \E[ \E[ f(X) - \phi(X_{-k}) \given X_k] X^2_k] = 0.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}[ (f(X)-\phi(X_{-k})) \big( s_n(X_k)- \E s_n(X_k) + \alpha (X_k^2-m_k^2) \big) ] &= 
+\mathbb{E}[ (f(X)-\phi(X_{-k}))& \big( s_n(X_k)- \E s_n(X_k) + \alpha
+  (X_k^2-m_k^2) \big) ] \\
+& = 
 \mathbb{E}[ (f(X) - \phi(X_{-k})) s_n(X_k) ] \\

### 2016-03-08 tex/scam/optimization.tex
major paper revisions
fixed some long equation breaks

@@
        & \;\; \sum_{i=1}^{n}f_{ik}=0,\\
-       & \;\; \beta_{\perm{i+1} k} \geq \beta_{\perm{i} k}\;\textrm{for $i=1,\ldots, n-1$}.
+       & \;\; \beta_{\perm{i+1} k} \geq \beta_{\perm{i} k}\;\textrm{for $i=1,\ldots, n-2$}.
 \end{split}
@@
 Here $f_k$ denotes the vector $f_k = (f_{1k}, f_{2_k}\ldots, f_{nk})^T\in\reals^n$
-and $\{\perm{1},\perm{2},\ldots,\perm{n}\}$ are the indices in the sorted ordering
+and the indices $\{\perm{1},\perm{2},\ldots,\perm{n}\}$ are from the sorted ordering
 of the values of coordinate $k$:
@@
 KKT conditions
-and the constraints $\sum_i f_{ki} = 0$.
+and the constraints $\sum_i f_{ik} = 0$.
 % It is easy to verify that the constraints in \eqref{np} satisfy the
@@
 f_k(x_{\perm{i}k}) = & f_k(x_{\perm{i-1}k}) + \beta_{\perm{i-1}k}(x_{\perm{i}k} - x_{\perm{i-1}k}) \\
- =& f_k(x_{\perm{1}k}) + \sum_{j < i} \beta_{\perm{j}k} (x_{\perm{j}k} - x_{\perm{j-1}k}) \\
- =& f_k(x_{\perm{1}k}) + \sum_{j < i} \sum_{j' \leq j} d_{\perm{j'}k} (x_{\perm{j}k} - x_{\perm{j-1}k})\\
- =& f_k(x_{\perm{1}k}) + \sum_{j' < i} d_{\perm{j'}k} \sum_{i > j \geq j'} (x_{\perm{j}k} - x_{\perm{j-1}k}) \\
+ =& f_k(x_{\perm{1}k}) + \sum_{j < i} \beta_{\perm{j}k} (x_{\perm{j+1}k} - x_{\perm{j}k}) \\
+ =& f_k(x_{\perm{1}k}) + \sum_{j < i} \sum_{j' \leq j} d_{\perm{j'}k} (x_{\perm{j+1}k} - x_{\perm{j}k})\\
+ =& f_k(x_{\perm{1}k}) + \sum_{j' < i} d_{\perm{j'}k} \sum_{i > j \geq j'} (x_{\perm{j+1}k} - x_{\perm{j}k}) \\
  =& f_k(x_{\perm{1}k}) + \sum_{j' < i} d_{\perm{j'}k} (x_{\perm{i}k} - x_{\perm{j'}k}).
@@
 \left[ \begin{array}{c}
-f_k(x_{\perm{1}k}) \\
-f_k(x_{\perm{2}k}) \\
+f_k(x_{1k}) \\
+f_k(x_{2k}) \\
 \vdots \\
-f_k(x_{\perm{n}k})
+f_k(x_{nk})
 \end{array} \right] &=
@@
 Because $f_k$ has to be centered, $\mu_k = - \frac{1}{n}
-\mathbf{1}_n^\tran \Delta_k d_k$, and therefore
+\mathbf{1}_n \mathbf{1}_n^\tran \Delta_k d_k$, and therefore
 \begin{equation}
-\Delta_k d_k + \mu_k \mathbf{1}_n = 
+\Delta_k d_k + \mu_k  = 
    \Delta_k d_k - \frac{1}{n} \mathbf{1}_n \mathbf{1}_n^\tran \Delta_k d_k = 

### 2016-03-08 tex/scam/supplement.tex
fixed some long equation breaks

@@
-\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
-%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}
+\documentclass[pdftex,aos]{imsart}
 
 \RequirePackage[OT1]{fontenc}
-\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
-\RequirePackage{hypernat}
-\usepackage[ruled,section]{algorithm}
-\usepackage[noend]{algorithmic}
-\usepackage{graphicx}
-%\usepackage[hscale=0.7,vscale=0.8]{geometry}
-\usepackage[text={6.0in,8.6in},centering]{geometry}
+\RequirePackage{amsthm,amsmath}
+\usepackage{amsfonts,mathtools,custom_math,amssymb}
+\RequirePackage[numbers]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
 \usepackage{subfigure}
 \usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{yhmath}
-\usepackage[usenames,dvipsnames]{xcolor}
-\definecolor{shadecolor}{gray}{0.9}
-\definecolor{shadecolor}{gray}{0.9}
-\hypersetup{citecolor=MidnightBlue}
-\hypersetup{linkcolor=MidnightBlue}
-\hypersetup{urlcolor=MidnightBlue}
 \usepackage{enumerate}
@@
 \usepackage{xr}
-\externaldocument{main}
-
-\renewcommand{\baselinestretch}{1.00}
-%\parskip12pt
-%\parindent0pt
-\setcounter{tocdepth}{2}
-\setattribute{journal}{name}{}
+\externaldocument{faithful}
 
@@
 \begin{frontmatter}
-\title{Supplement to Faithful Variable Screening for\\ High-Dimensional Convex Regression}
+\title{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
 \runtitle{Supplement to Faithful Variable Screening for Convex Regression}
@@
 
-\textbf{Step 2.} We now bound term 3.
-\begin{align*}
-\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
+\textbf{Step 2.} We now bound term 3, by writing
+\begin{align*}
+\| f_0 - & \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 \\
+& \leq 
     \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle_P

### 2016-03-09 tex/scam/additive_faithful.tex
minor typo

@@
 \beta$. The optimal linear function in the population setting is
-$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma = X^\tran X$ is the
+$\beta^* = \Sigma^{-1} \trm{Cov}(X, f(X))$ where $\Sigma = \E X^\tran X$ is the
 covariance matrix. Suppose the $X$'s are independent, centered, and have a

### 2016-03-14 tex/scam/faithful.tex
minor ref fixes
supplement correction

@@
 \begin{aug}
-\author{\fnms{Min} \snm{Xu}\thanksref{t1,m1}\ead[label=e1]{min.cut@gmail.com}},
-\author{\fnms{Minhua} \snm{Chen}\thanksref{m2}\ead[label=e2]{minhua@somewhere.com}}
+\author{\fnms{Min} \snm{Xu}\thanksref{t1,m1}\ead[label=e1]{minx@wharton.upenn.edu}},
+\author{\fnms{Minhua} \snm{Chen}\thanksref{m2}}
 \and
@@
 Seattle, Washington 98109\\
-USA\\
-\printead{e2}\\}
+USA}
 
